### 2016-07-05 paper/icse2017/intro.tex
Added ICSE17 files

\section{Introduction}

\sloppy Testing is important...Test execution is
expensive...\Fix{examples}...Several approaches have been proposed to
mitigate this problem...In the literature, research has focused mostly
in test selection\Fix{cite}, test reduction \Fix{cite}, and test
prioritization \Fix{cite}.  This work focuses on an orthogonal
dimension to optimize regression testing~--~parallelization, which
intuitively enables regression testing to scale with computing
capacity.

Given the proliferation of multicore machines it is not surprising
that popular testing frameworks provide today support for parallel
test execution (e.g., JUnit since version 4.?  \Fix{cite}, TestNG
since version \Fix{cite}, and \Fix{??NUnit??} since version \Fix{??}
\Fix{cite}).  Unfortunately, unrestricted parallel execution of tests
can produce non-deterministic results as developers typically do not
provision protection from concurrent accesses originated from
arbitrary program points (\ie{}, tests)\footnote{Testing frameworks
  document this limitation on the parallel execution
  feature~\Fix{cite}}.  We refer to this problem as Parallel Execution
Flakiness (\pef{}).  To illustrate the \pef{} problem and discuss
potential solutions, we conducted a feasibility study involving
\Fix{M} subject programs containing test suites with at least
\Fix{X,000} tests and observed the following:

\Fix{move this!}Furthermore, we observed that parallel test execution can
significantly speedup regression testing.  The speedup obtained with
parallel test execution of the test suites we analyzed ranges from
\Fix{A} to \Fix{B}\%.

%% Furthermore,
%% provisioning for such flexibility would create a significant burden on
%% developers and certainly produce hard-to-maintain code.

\begin{itemize}
\item \textbf{\pef{} is prevalent.} For a given subject program, we ran
  the test suite in parallel multiple times.  \pef{} was observed in N of
  the M cases we considered.
\item \textbf{\pef{} affects a small but significant amount of tests.}
  Of the N cases where we observed \pef{}, the outcome of X\% of the
  tests, on average, was non-deterministic.
\end{itemize}

These observations indicate that \pef{} is an important obstacle to
enable parallel test execution: it is important to enable reliable
execution of all tests in addition to executing tests efficiently.  It
is also important to shed some light on the practical value of
speeding up test execution.  In large IT companies (e.g.,
Groupon~\Fix{cite}, Google~\Fix{cite}, and Microsoft~\Fix{cite})
testing costs can be much higher compared to the costs we observed in
open-source projects, where test execution time ranged from \Fix{XXm}
to \Fix{YYm}.  Assigning worker machines from a server farm to execute
distinct subsets of test suites is not
uncommon\Fix{data!!}\footnote{Ideally, each part of the test suite
  would have cost proportional to the capacity of the assigned
  machine.}.  We conjecture that lighter weight solutions that use
commodity hardware to optimize test execution are also important.  For
the scenario above, these solutions could leverage the computing power
on each individual node of a server farm in addition to the aggregate
processing power of the farm.  Lighter weight solutions fits
particularly well relatively smaller lower-budget projects with
relatively high testing costs such as those that we observed in this
preliminary study.

It is important to note that previous work investigated test flakiness
manifested in sequential executions [cite cite].  For example, a test
case can fail because of a broken test dependency caused when ... or
because of an implicit ordering assumption was broken in a
multi-threaded test (under a sequential execution of the test suite).
Treating this source of flakiness is important but complementary to
this work: parallel execution flakiness can arise even without
sequential execution flakiness.  Discovering and fixing this source of
flakiness is challenging and essential to enable test parallelization.

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi

### 2016-07-05 paper/icse2017/prelim-study.tex
Added ICSE17 files

\section{Preliminary Study}

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \multirow{2}{*}{\emph{Subject}} & \multirow{2}{*}{\emph{\# Tests}} &  \multicolumn{2}{c|}{\emph{Time}}\\
    \cline{3-4}
    & & Seq & Par \\
    \hline
    jgit & - & - & - \\
    \hline
  \end{tabular}
  \caption{\label{table:cost}...}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    \emph{Subject} & Fail-Par. & Fail-Ind. \\
    \hline
    jgit & - & - \\
    \hline
  \end{tabular}
  \caption{\label{table:failures}...}
\end{table}

Iterative Test Execution (ITE) provides a means to reveal flakiness in
test runs caused by non-determinism.  In ITE the developer determines
a bound N for the number of re-executions.  Only tests that fail in
one given iteration (consequently, failed in all previous iterations)
are scheduled for re-execution in the next iteration.  At the end of
the process, a test is considered passing if it passed in the first
iteration, a test is considered failing if it fails in all iterations,
and it is considered flaky if it fails in all iterations but the last
it executed.  The process terminates when all tests eventually pass or
when the the bound N is reached.\Fix{illustrate with small
  figure...}~To note that ITE is supported by the popular maven
surefire plugin [cite].

### 2016-07-07 paper/icse2017/intro.tex
pass on intro

@@
 expensive...\Fix{examples}...Several approaches have been proposed to
-mitigate this problem...In the literature, research has focused mostly
-in test selection\Fix{cite}, test reduction \Fix{cite}, and test
-prioritization \Fix{cite}.  This work focuses on an orthogonal
-dimension to optimize regression testing~--~parallelization, which
-intuitively enables regression testing to scale with computing
-capacity.
+mitigate this problem... Research has focused mostly on test
+selection~\Fix{cite}, test reduction~\Fix{cite}, and test
+prioritization~\Fix{cite}.
 
-Given the proliferation of multicore machines it is not surprising
-that popular testing frameworks provide today support for parallel
-test execution (e.g., JUnit since version 4.?  \Fix{cite}, TestNG
-since version \Fix{cite}, and \Fix{??NUnit??} since version \Fix{??}
-\Fix{cite}).  Unfortunately, unrestricted parallel execution of tests
-can produce non-deterministic results as developers typically do not
-provision protection from concurrent accesses originated from
-arbitrary program points (\ie{}, tests)\footnote{Testing frameworks
-  document this limitation on the parallel execution
-  feature~\Fix{cite}}.  We refer to this problem as Parallel Execution
-Flakiness (\pef{}).  To illustrate the \pef{} problem and discuss
-potential solutions, we conducted a feasibility study involving
-\Fix{M} subject programs containing test suites with at least
-\Fix{X,000} tests and observed the following:
+This work focuses on an orthogonal dimension to optimize regression
+testing~--~parallelization, which intuitively enables regression
+testing to scale with computing capacity.  Given the proliferation of
+multicore machines it is not surprising that popular testing
+frameworks and build systems provide today support for parallel test
+execution~\Fix{cite}.  Unfortunately, these solutions can't be used
+out-of-the-box: unrestricted parallel execution can produce
+non-deterministic results as developers typically do not provision
+protection to concurrent accesses originated from arbitrary program
+points (\ie{}, tests).  We refer to this problem as Parallel Execution
+Flakiness (\pef{}).
 
-\Fix{move this!}Furthermore, we observed that parallel test execution can
-significantly speedup regression testing.  The speedup obtained with
-parallel test execution of the test suites we analyzed ranges from
-\Fix{A} to \Fix{B}\%.
+To illustrate the importance of parallel test execution and the
+problem of \pef{} let's consider the case of the ``core'' module from
+the Apache Camel project~\cite{apache-camel-web}.  This module
+contains 5,679 test cases, declared in \Fix{NN} test classes.  We ran
+those tests in a machine with 16GB of memory and 8 virtual CPUs (4
+cores with 2 native threads each).  Sequential test execution takes
+24m50s to run this test set.  Execution of the same test set takes
+2m28s when we consider a parallel execution configuration that spawns
+a JVM on each CPU and forks a thread per test class allocated to a
+given JVM.  Note that this is an order of magnitude (10.07x)
+speedup\Fix{Should we expect something close to 7x as opposed to
+  10x?}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of the 5,679)
+of the tests fail when executed in parallel.  It is important to
+notice that the ratio of failures varies with the project as it
+depends on factors such as length of test cases and amount of shared
+state across tests, for example.
 
-%% Furthermore,
-%% provisioning for such flexibility would create a significant burden on
-%% developers and certainly produce hard-to-maintain code.
+This paper reports an empirical study to evaluate the impact of
+parallelization options on test execution speedup and \pef{}. Based on
+these results, we proposed different low-cost strategies to avoid
+\pef{}.
 
-\begin{itemize}
-\item \textbf{\pef{} is prevalent.} For a given subject program, we ran
-  the test suite in parallel multiple times.  \pef{} was observed in N of
-  the M cases we considered.
-\item \textbf{\pef{} affects a small but significant amount of tests.}
-  Of the N cases where we observed \pef{}, the outcome of X\% of the
-  tests, on average, was non-deterministic.
-\end{itemize}
+%% To illustrate the \pef{} problem and discuss potential solutions, we
+%% conducted a feasibility study involving \Fix{M} subject programs
+%% containing test suites with at least \Fix{X,000} tests and observed
+%% the following:
+
+%% \Fix{move this!}Furthermore, we observed that parallel test execution can
+%% significantly speedup regression testing.  The speedup obtained with
+%% parallel test execution of the test suites we analyzed ranges from
+%% \Fix{A} to \Fix{B}\%.
+
+%% %% Furthermore,
+%% %% provisioning for such flexibility would create a significant burden on
+%% %% developers and certainly produce hard-to-maintain code.
+
+%% \begin{itemize}
+%% \item \textbf{\pef{} is prevalent.} For a given subject program, we ran
+%%   the test suite in parallel multiple times.  \pef{} was observed in N of
+%%   the M cases we considered.
+%% \item \textbf{\pef{} affects a small but significant amount of tests.}
+%%   Of the N cases where we observed \pef{}, the outcome of X\% of the
+%%   tests, on average, was non-deterministic.
+%% \end{itemize}
+
+\Fix{-- I am here...}
+
+\Fix{Move the following pars. somewhere else...}
 

### 2016-07-08 paper/icse2017/anatomy.tex
changes in text

--- 2016-07-05 paper/icse2017/intro.tex
@@
-\section{Introduction}
+\section{Anatomy of \pef{} failure}
 
-\sloppy Testing is important...Test execution is
-expensive...\Fix{examples}...Several approaches have been proposed to
-mitigate this problem...In the literature, research has focused mostly
-in test selection\Fix{cite}, test reduction \Fix{cite}, and test
-prioritization \Fix{cite}.  This work focuses on an orthogonal
-dimension to optimize regression testing~--~parallelization, which
-intuitively enables regression testing to scale with computing
-capacity.
-
-Given the proliferation of multicore machines it is not surprising
-that popular testing frameworks provide today support for parallel
-test execution (e.g., JUnit since version 4.?  \Fix{cite}, TestNG
-since version \Fix{cite}, and \Fix{??NUnit??} since version \Fix{??}
-\Fix{cite}).  Unfortunately, unrestricted parallel execution of tests
-can produce non-deterministic results as developers typically do not
-provision protection from concurrent accesses originated from
-arbitrary program points (\ie{}, tests)\footnote{Testing frameworks
-  document this limitation on the parallel execution
-  feature~\Fix{cite}}.  We refer to this problem as Parallel Execution
-Flakiness (\pef{}).  To illustrate the \pef{} problem and discuss
-potential solutions, we conducted a feasibility study involving
-\Fix{M} subject programs containing test suites with at least
-\Fix{X,000} tests and observed the following:
-
-\Fix{move this!}Furthermore, we observed that parallel test execution can
-significantly speedup regression testing.  The speedup obtained with
-parallel test execution of the test suites we analyzed ranges from
-\Fix{A} to \Fix{B}\%.
-
-%% Furthermore,
-%% provisioning for such flexibility would create a significant burden on
-%% developers and certainly produce hard-to-maintain code.
-
-\begin{itemize}
-\item \textbf{\pef{} is prevalent.} For a given subject program, we ran
-  the test suite in parallel multiple times.  \pef{} was observed in N of
-  the M cases we considered.
-\item \textbf{\pef{} affects a small but significant amount of tests.}
-  Of the N cases where we observed \pef{}, the outcome of X\% of the
-  tests, on average, was non-deterministic.
-\end{itemize}
-
-These observations indicate that \pef{} is an important obstacle to
-enable parallel test execution: it is important to enable reliable
-execution of all tests in addition to executing tests efficiently.  It
-is also important to shed some light on the practical value of
-speeding up test execution.  In large IT companies (e.g.,
-Groupon~\Fix{cite}, Google~\Fix{cite}, and Microsoft~\Fix{cite})
-testing costs can be much higher compared to the costs we observed in
-open-source projects, where test execution time ranged from \Fix{XXm}
-to \Fix{YYm}.  Assigning worker machines from a server farm to execute
-distinct subsets of test suites is not
-uncommon\Fix{data!!}\footnote{Ideally, each part of the test suite
-  would have cost proportional to the capacity of the assigned
-  machine.}.  We conjecture that lighter weight solutions that use
-commodity hardware to optimize test execution are also important.  For
-the scenario above, these solutions could leverage the computing power
-on each individual node of a server farm in addition to the aggregate
-processing power of the farm.  Lighter weight solutions fits
-particularly well relatively smaller lower-budget projects with
-relatively high testing costs such as those that we observed in this
-preliminary study.
+\Fix{...}
 
@@
 flakiness is challenging and essential to enable test parallelization.
-
-%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
-%%  LocalWords:  Groupon parallelizing multi

### 2016-07-08 paper/icse2017/intro.tex
changes in text

@@
 
-\sloppy Testing is important...Test execution is
-expensive...\Fix{examples}...Several approaches have been proposed to
-mitigate this problem... Research has focused mostly on test
-selection~\Fix{cite}, test reduction~\Fix{cite}, and test
-prioritization~\Fix{cite}.
+Optimizing regression testing is important.  As software evolves the
+size of test sets (both in number and length of tests) increases,
+potentially leading to increasing disruption of the development
+process caused by late reports of test failures.  This problem
+manifests more dramatically at large IT companies (e.g.,\Comment{
+  Groupon~\Fix{cite},} Google~\Fix{cite} and Microsoft~\Fix{cite})
+where the size of test sets often exceeds the size of the code base.
+Several approaches have been proposed to optimize test execution.
+Research has focused mostly on test selection~\Fix{cite}, test
+reduction~\Fix{cite}, and test prioritization~\Fix{cite}.  Although
+these approaches can also be applied in industrial settings, the focus
+in industry has been mostly in parallelizing test execution with
+server farms, where worker machines from the farm are assigned to
+execute distinct subsets of the original test suite.
 
-This work focuses on an orthogonal dimension to optimize regression
-testing~--~parallelization, which intuitively enables regression
-testing to scale with computing capacity.  Given the proliferation of
-multicore machines it is not surprising that popular testing
-frameworks and build systems provide today support for parallel test
-execution~\Fix{cite}.  Unfortunately, these solutions can't be used
-out-of-the-box: unrestricted parallel execution can produce
-non-deterministic results as developers typically do not provision
-protection to concurrent accesses originated from arbitrary program
-points (\ie{}, tests).  We refer to this problem as Parallel Execution
-Flakiness (\pef{}).
+Given the proliferation of multicore machines it is not surprising
+that popular testing frameworks and build systems provide today
+support for parallel test execution~\Fix{cite}.  These solutions
+attempt to maximize CPU usage in individual machines with the goal of
+running tests more efficiently.  In the case of the Java language, it
+is possible to explore parallelism across JVMs and within the JVM.  We
+conjecture that such lower-level solutions that use commodity hardware
+to optimize test execution are also important (compared to
+higher-level parallelism from server farms).  For the scenario of
+large IT organizations, lower-level parallelization schemes leverage
+the computing power on each individual node of a server farm in
+addition to the aggregate processing power of the farm.  Lower-level
+parallelization fits particularly well smaller organizations
+(/projects) with relatively high testing costs but lower budgets.
 
-To illustrate the importance of parallel test execution and the
-problem of \pef{} let's consider the case of the ``core'' module from
-the Apache Camel project~\cite{apache-camel-web}.  This module
+Unfortunately, these solutions can't be used out-of-the-box:
+unrestricted parallel execution of tests can produce non-deterministic
+results as developers typically do not provision protection to
+concurrent accesses originated from arbitrary program points (\ie{},
+tests).  We refer to this problem as Parallel Execution Flakiness
+(\pef{}).  To illustrate the importance of parallel test execution and
+the problem of \pef{} let's consider the case of the ``core'' module
+from the Apache Camel project~\cite{apache-camel-web}.  This module
 contains 5,679 test cases, declared in \Fix{NN} test classes.  We ran
@@
 24m50s to run this test set.  Execution of the same test set takes
-2m28s when we consider a parallel execution configuration that spawns
-a JVM on each CPU and forks a thread per test class allocated to a
-given JVM.  Note that this is an order of magnitude (10.07x)
-speedup\Fix{Should we expect something close to 7x as opposed to
-  10x?}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of the 5,679)
-of the tests fail when executed in parallel.  It is important to
-notice that the ratio of failures varies with the project as it
-depends on factors such as length of test cases and amount of shared
-state across tests, for example.
+2m28s when we configured parallel execution to spawn a JVM on each CPU
+and fork a thread per test class, uniquely allocated to one JVM.  Note
+that this is an order of magnitude (10.07x) speedup\Fix{Need to
+  understand why this is 10x as opposed to something closer to 7x}.
+Unfortunately, due to \pef{}, $\sim$2\% (114 of 5,679) of the tests
+fail when executed in parallel.  It is important to notice that the
+ratio of failures varies with the project as it depends on factors
+such as length of test cases and amount of shared state across tests,
+for example.  \pef{} is an important obstacle to enable parallel test
+execution: it is important to execute tests efficiently without
+sacrificing reliability.  Conceptually, higher parallelization can
+result in higher chances of concurrency-related problems.
 
@@
 parallelization options on test execution speedup and \pef{}. Based on
-these results, we proposed different low-cost strategies to avoid
-\pef{}.
-
-%% To illustrate the \pef{} problem and discuss potential solutions, we
-%% conducted a feasibility study involving \Fix{M} subject programs
-%% containing test suites with at least \Fix{X,000} tests and observed
-%% the following:
-
-%% \Fix{move this!}Furthermore, we observed that parallel test execution can
-%% significantly speedup regression testing.  The speedup obtained with
-%% parallel test execution of the test suites we analyzed ranges from
-%% \Fix{A} to \Fix{B}\%.
-
-%% %% Furthermore,
-%% %% provisioning for such flexibility would create a significant burden on
-%% %% developers and certainly produce hard-to-maintain code.
-
-%% \begin{itemize}
-%% \item \textbf{\pef{} is prevalent.} For a given subject program, we ran
-%%   the test suite in parallel multiple times.  \pef{} was observed in N of
-%%   the M cases we considered.
-%% \item \textbf{\pef{} affects a small but significant amount of tests.}
-%%   Of the N cases where we observed \pef{}, the outcome of X\% of the
-%%   tests, on average, was non-deterministic.
-%% \end{itemize}
-
-\Fix{-- I am here...}
-
-\Fix{Move the following pars. somewhere else...}
-
-These observations indicate that \pef{} is an important obstacle to
-enable parallel test execution: it is important to enable reliable
-execution of all tests in addition to executing tests efficiently.  It
-is also important to shed some light on the practical value of
-speeding up test execution.  In large IT companies (e.g.,
-Groupon~\Fix{cite}, Google~\Fix{cite}, and Microsoft~\Fix{cite})
-testing costs can be much higher compared to the costs we observed in
-open-source projects, where test execution time ranged from \Fix{XXm}
-to \Fix{YYm}.  Assigning worker machines from a server farm to execute
-distinct subsets of test suites is not
-uncommon\Fix{data!!}\footnote{Ideally, each part of the test suite
-  would have cost proportional to the capacity of the assigned
-  machine.}.  We conjecture that lighter weight solutions that use
-commodity hardware to optimize test execution are also important.  For
-the scenario above, these solutions could leverage the computing power
-on each individual node of a server farm in addition to the aggregate
-processing power of the farm.  Lighter weight solutions fits
-particularly well relatively smaller lower-budget projects with
-relatively high testing costs such as those that we observed in this
-preliminary study.
-
-It is important to note that previous work investigated test flakiness
-manifested in sequential executions [cite cite].  For example, a test
-case can fail because of a broken test dependency caused when ... or
-because of an implicit ordering assumption was broken in a
-multi-threaded test (under a sequential execution of the test suite).
-Treating this source of flakiness is important but complementary to
-this work: parallel execution flakiness can arise even without
-sequential execution flakiness.  Discovering and fixing this source of
-flakiness is challenging and essential to enable test parallelization.
+these results, we proposed different low-cost synchronization
+strategies to avoid \pef{}.
 

### 2016-07-08 paper/icse2017/intro.tex
another pass

@@
 Optimizing regression testing is important.  As software evolves the
-size of test sets (both in number and length of tests) increases,
-potentially leading to increasing disruption of the development
-process caused by late reports of test failures.  This problem
-manifests more dramatically at large IT companies (e.g.,\Comment{
-  Groupon~\Fix{cite},} Google~\Fix{cite} and Microsoft~\Fix{cite})
-where the size of test sets often exceeds the size of the code base.
-Several approaches have been proposed to optimize test execution.
-Research has focused mostly on test selection~\Fix{cite}, test
-reduction~\Fix{cite}, and test prioritization~\Fix{cite}.  Although
-these approaches can also be applied in industrial settings, the focus
-in industry has been mostly in parallelizing test execution with
-server farms, where worker machines from the farm are assigned to
-execute distinct subsets of the original test suite.
+size of test sets increases, potentially leading to disruption of the
+development process caused by late reports of test failures.  This
+problem manifests more dramatically at large IT companies
+(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
+Microsoft~\Fix{cite}) where the size of test sets often exceeds the
+size of the code base.  Several approaches have been proposed to
+optimize regression testing.  Research has focused mostly on test
+selection~\Fix{cite}, test reduction~\Fix{cite}, and test
+prioritization~\Fix{cite}.  Although these approaches can also be
+applied in industrial settings, the focus in industry has been mostly
+in parallelizing execution of tests using server farms, where worker
+machines from the farm are assigned to execute distinct subsets of the
+original test suite.
 
@@
 that popular testing frameworks and build systems provide today
-support for parallel test execution~\Fix{cite}.  These solutions
-attempt to maximize CPU usage in individual machines with the goal of
-running tests more efficiently.  In the case of the Java language, it
-is possible to explore parallelism across JVMs and within the JVM.  We
-conjecture that such lower-level solutions that use commodity hardware
-to optimize test execution are also important (compared to
-higher-level parallelism from server farms).  For the scenario of
-large IT organizations, lower-level parallelization schemes leverage
-the computing power on each individual node of a server farm in
-addition to the aggregate processing power of the farm.  Lower-level
-parallelization fits particularly well smaller organizations
-(/projects) with relatively high testing costs but lower budgets.
+support for parallel test execution with the goal of running tests
+more efficiently~\cite{junit-org,testng,nunit,maven-surefire-plugin}.
+These solutions use commodity hardware to maximize CPU usage in
+individual machines.  In the case of the Java language, it is possible
+to explore parallelism across JVMs and within the JVM.  The
+lower-level parallelism enabled through build systems is an important
+complement to the higher-level parallelism enabled through server
+farms.  For the scenario of large IT organizations, lower-level
+parallelization schemes leverage the computing power on each
+individual node of a server farm in addition to the aggregate
+processing power of the farm.  Lower-level parallelism fits
+particularly well smaller organizations (/projects) with relatively
+high testing costs but lower budgets.
 

### 2016-07-08 paper/icse2017/modes.tex
pass on text; adding figure

\section{Modes of Parallel Execution}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.4\textwidth]{figs/parallel-levels.pdf}
  \caption{\label{fig:levels}Levels of parallelism.}
\end{figure}

\Fix{write a short paragraph to explain this figure.  explain why
  user/forked thread that run in a (logical) cpu can help speedup?
  assuming i/o?}

\Fix{...explain different modes of parallel execution offered by build
  system and or testing framework...(don't use much more than a column
  of space)}

Modern build systems provides a means to reveal test flakiness.  The
typical approach is to iteratively execute the test suite multiple
times and to mark tests that produce both pass and failing outputs.
More precisely, the developer determines a bound N for the number of
re-executions of the test suite.  Only tests that fail in one given
iteration (consequently, failed in all previous iterations) are
scheduled for re-execution in the next iteration.  At the end of the
process, a test is considered passing if it passes in the first
iteration, a test is considered failing if it fails in all iterations,
and it is considered flaky if it fails in all iterations but the last
it executed.  The process terminates when all tests eventually pass or
when bound N is reached.  Note that every iteration runs a subset of
the test from the previous iteration so execution cost is lower
compared to executing the suite N times.  To note that ITE is
supported by the popular maven surefire
plugin~\cite{maven-surefire-plugin}.\Fix{mention which
  flag/parameter...} ITE provides a means to acknowledge the presence
of test flakiness, including \pef{}s.  Ideally, one would like to
eliminate \pef{}s and avoid the need for ITE.

### 2016-07-08 paper/icse2017/prelim-study.tex
[Paper] Updated table I and II
pass on text; adding figure

@@
     \hline
-    jgit & - & - & - \\
+    jgit & 3364 & 04:12 min & 53.003 s \\
+    \hline
+    jetty (client) & 5679 & 04:15 min & 18.752 s \\
+    \hline
+    camel (core) & 527 & 24:50 min & 02:28 min \\
     \hline
@@
     \hline
-    jgit & - & - \\
+    jgit & 239 & 4 \\
+    \hline
+    jetty (client) & 232 & - \\
+    \hline
+    camel (core) & 142 & - \\
     \hline
@@
 \end{table}
-
-Iterative Test Execution (ITE) provides a means to reveal flakiness in
-test runs caused by non-determinism.  In ITE the developer determines
-a bound N for the number of re-executions.  Only tests that fail in
-one given iteration (consequently, failed in all previous iterations)
-are scheduled for re-execution in the next iteration.  At the end of
-the process, a test is considered passing if it passed in the first
-iteration, a test is considered failing if it fails in all iterations,
-and it is considered flaky if it fails in all iterations but the last
-it executed.  The process terminates when all tests eventually pass or
-when the the bound N is reached.\Fix{illustrate with small
-  figure...}~To note that ITE is supported by the popular maven
-surefire plugin [cite].

### 2016-07-08 paper/icse2017/anatomy.tex
polish text

@@
-\section{Anatomy of \pef{} failure}
+\section{Anatomy of a \pef{} failure}
 
@@
 manifested in sequential executions [cite cite].  For example, a test
-case can fail because of a broken test dependency caused when ... or
-because of an implicit ordering assumption was broken in a
-multi-threaded test (under a sequential execution of the test suite).
-Treating this source of flakiness is important but complementary to
-this work: parallel execution flakiness can arise even without
-sequential execution flakiness.  Discovering and fixing this source of
-flakiness is challenging and essential to enable test parallelization.
+case can fail because an implicit ordering assumption from a
+multi-threaded test was broken under a sequential execution of the
+test suite.  Treating this source of flakiness is important but
+orthogonal to this work: parallel execution flakiness can arise even
+without sequential execution flakiness.

### 2016-07-08 paper/icse2017/modes.tex
adjusting tables

@@
 
-Modern build systems provides a means to reveal test flakiness.  The
-typical approach is to iteratively execute the test suite multiple
-times and to mark tests that produce both pass and failing outputs.
-More precisely, the developer determines a bound N for the number of
-re-executions of the test suite.  Only tests that fail in one given
-iteration (consequently, failed in all previous iterations) are
-scheduled for re-execution in the next iteration.  At the end of the
-process, a test is considered passing if it passes in the first
-iteration, a test is considered failing if it fails in all iterations,
-and it is considered flaky if it fails in all iterations but the last
-it executed.  The process terminates when all tests eventually pass or
-when bound N is reached.  Note that every iteration runs a subset of
-the test from the previous iteration so execution cost is lower
-compared to executing the suite N times.  To note that ITE is
-supported by the popular maven surefire
-plugin~\cite{maven-surefire-plugin}.\Fix{mention which
-  flag/parameter...} ITE provides a means to acknowledge the presence
-of test flakiness, including \pef{}s.  Ideally, one would like to
-eliminate \pef{}s and avoid the need for ITE.
+Modern build systems provide a means to reveal test flakiness.  The
+typical approach is to execute the test suite multiple times and
+iteratively mark as flaky those tests that produce both pass and
+failing outputs.  More precisely, the process starts with the
+developer determining a bound N for the number of re-executions of the
+test suite.  Only tests that fail in one given iteration
+(consequently, failed in all previous iterations) are scheduled for
+re-execution in the next iteration.  At the end of the process, a test
+is considered passing if it passes in the first iteration, a test is
+considered failing if it fails in all iterations, and it is considered
+flaky if it fails in all iterations but the last it executed.  The
+process terminates when all tests eventually pass or when the bound N
+is reached.  Note that every iteration runs a subset of the test from
+the previous iteration so execution cost is lower compared to
+executing the entire test suite N times.  To note that this iterative
+process is supported by the popular maven surefire
+plugin~\cite{maven-surefire-plugin}.\Fix{others?  mention which
+  flag/parameter...}  Ideally, one would like to eliminate \pef{}s and
+avoid the need for re-executing the test suite multiple times.

### 2016-07-11 paper/icse2017/anatomy.tex
pass on text

@@
 multi-threaded test was broken under a sequential execution of the
-test suite.  Treating this source of flakiness is important but
-orthogonal to this work: parallel execution flakiness can arise even
-without sequential execution flakiness.
+test suite.  \Fix{or a test case can fail...} Treating this source of
+flakiness is important but orthogonal to this work: parallel execution
+flakiness can arise even without sequential execution flakiness.
+
+Modern build systems provide a means to reveal test flakiness.  The
+typical approach is to execute the test suite multiple times and
+iteratively mark as flaky those tests that produce both pass and
+failing outputs.  More precisely, the process starts with the
+developer determining a bound N for the number of re-executions of the
+test suite.  Only tests that fail in one given iteration
+(consequently, failed in all previous iterations) are scheduled for
+re-execution in the next iteration.  At the end of the process, a test
+is considered passing if it passes in the first iteration, a test is
+considered failing if it fails in all iterations, and it is considered
+flaky if it fails in all iterations but the last it executed.  The
+process terminates when all tests eventually pass or when the bound N
+is reached.  Note that every iteration runs a subset of the tests from
+the previous iteration so execution cost is lower compared to
+executing the entire test suite N times.  To note that this iterative
+process is supported by the popular maven surefire
+plugin~\cite{maven-surefire-plugin}.\Fix{others?  mention which
+  flag/parameter...}  Ideally, one would like to eliminate \pef{}s and
+avoid the need for re-executing the test suite multiple times.

### 2016-07-11 paper/icse2017/anatomy.tex
adjusting macros

--- 2016-07-08 paper/icse2017/anatomy.tex
@@
 \section{Anatomy of a \pef{} failure}
+
+It is important to note that previous work investigated test flakiness
+manifested in sequential executions\Fix{cite cite}.  For example, a
+test case can fail because a timing assumption of an asynchronous test
+was broken.  Treating this source of flakiness is important but
+orthogonal to this work: parallel execution flakiness can arise even
+without sequential execution flakiness.  In the following we explain
+how \pef{}s come to be.
 
@@
 
-It is important to note that previous work investigated test flakiness
-manifested in sequential executions [cite cite].  For example, a test
-case can fail because an implicit ordering assumption from a
-multi-threaded test was broken under a sequential execution of the
-test suite.  Treating this source of flakiness is important but
-orthogonal to this work: parallel execution flakiness can arise even
-without sequential execution flakiness.
+\noindent\textbf{Detecting flakiness.}  Modern build systems provide
+mechanisms to reveal test flakiness. The typical approach is to
+iteratively re-execute the test suite marking as flaky those tests
+that produce both pass and failing outputs.  Considering the
+Maven\Fix{is this maven or maven's surefire
+  plugin~\cite{maven-surefire-plugin}?}  build system, the process
+starts with the developer determining a bound N for the number of
+re-executions of the test suite.  Only tests that fail in one given
+iteration are scheduled for re-execution in the next iteration.  At
+the end of the process, a test is considered passing if it passes in
+the first iteration, a test is considered failing if it fails in all
+iterations, and it is considered flaky if it fails in all iterations
+but the last it executed.  The process terminates when all tests
+eventually pass or when the bound N is reached.  Note that every
+iteration runs a subset of the tests from the previous iteration so
+execution cost is lower compared to executing the entire test suite N
+times.
+
+\Fix{Ideally, one would like to eliminate \pef{}s and avoid the need
+  for re-executing the test suite multiple times.}

### 2016-07-11 paper/icse2017/intro.tex

@@
 Optimizing regression testing is important.  As software evolves the
-size of test sets increases, potentially leading to disruption of the
+size of test sets increases, potentially leading to disruption in the
 development process caused by late reports of test failures.  This
@@
 Given the proliferation of multicore machines it is not surprising
-that popular testing frameworks and build systems provide today
+that popular build systems and testing frameworks provide today
 support for parallel test execution with the goal of running tests
 more efficiently~\cite{junit-org,testng,nunit,maven-surefire-plugin}.
-These solutions use commodity hardware to maximize CPU usage in
-individual machines.  In the case of the Java language, it is possible
-to explore parallelism across JVMs and within the JVM.  The
-lower-level parallelism enabled through build systems is an important
-complement to the higher-level parallelism enabled through server
-farms.  For the scenario of large IT organizations, lower-level
-parallelization schemes leverage the computing power on each
-individual node of a server farm in addition to the aggregate
+The lower-level parallelism enabled through build systems and testing
+frameworks is an important complement to the higher-level parallelism
+enabled through server farms.  These solutions enable the use of
+commodity hardware to maximize CPU usage\footnote{In the case of the
+  Java language, for example, it is possible to explore parallelism
+  across and within JVMs.}.  For the scenario of large IT
+organizations, lower-level parallelization schemes could leverage the
+computing power of server nodes in addition to the aggregate
 processing power of the farm.  Lower-level parallelism fits
 particularly well smaller organizations (/projects) with relatively
-high testing costs but lower budgets.
+high testing costs but lower budgets.  Unfortunately, these solutions
+can't be used out-of-the-box: unrestricted parallel execution of tests
+can produce non-deterministic results as developers typically do not
+provision protection to concurrent accesses originated from arbitrary
+program points (\ie{}, tests).  We refer to this problem as Parallel
+Execution Flakiness (\pef{}).
 
-Unfortunately, these solutions can't be used out-of-the-box:
-unrestricted parallel execution of tests can produce non-deterministic
-results as developers typically do not provision protection to
-concurrent accesses originated from arbitrary program points (\ie{},
-tests).  We refer to this problem as Parallel Execution Flakiness
-(\pef{}).  To illustrate the importance of parallel test execution and
-the problem of \pef{} let's consider the case of the ``core'' module
-from the Apache Camel project~\cite{apache-camel-web}.  This module
+To illustrate the importance of parallel test execution and the
+problem of \pef{} let's consider the case of the ``core'' module from
+the Apache Camel project~\cite{apache-camel-web}.  This module
 contains 5,679 test cases, declared in \Fix{NN} test classes.  We ran
@@
 24m50s to run this test set.  Execution of the same test set takes
-2m28s when we configured parallel execution to spawn a JVM on each CPU
-and fork a thread per test class, uniquely allocated to one JVM.  Note
-that this is an order of magnitude (10.07x) speedup\Fix{Need to
-  understand why this is 10x as opposed to something closer to 7x}.
+2m28s when we configured parallel execution to fork a JVM per CPU and
+execute test classes, uniquely allocated to that JVM, sequentially but
+running test methods from each class in separate threads.  Note that
+this is an order of magnitude speedup (10.07x)\Fix{Need to understand
+  why this is 10x as opposed to something closer to 7x}.
 Unfortunately, due to \pef{}, $\sim$2\% (114 of 5,679) of the tests
@@
 ratio of failures varies with the project as it depends on factors
-such as length of test cases and amount of shared state across tests,
-for example.  \pef{} is an important obstacle to enable parallel test
-execution: it is important to execute tests efficiently without
-sacrificing reliability.  Conceptually, higher parallelization can
-result in higher chances of concurrency-related problems.
+such as length of test cases and amount of shared state across tests.
+
+\pef{} is an important obstacle to enable parallel test execution.
+Conceptually, higher parallelization can result in higher chances of
+concurrency-related problems.  It is important to execute tests
+efficiently without sacrificing reliability
+\Fix{gap between pars??}
 

### 2016-07-11 paper/icse2017/modes.tex

--- 2016-07-08 paper/icse2017/modes.tex
@@
 
-\Fix{write a short paragraph to explain this figure.  explain why
-  user/forked thread that run in a (logical) cpu can help speedup?
-  assuming i/o?}
+Parallelism in test execution can be achieved at different levels.
+Figure~\ref{fig:levels} illustrates that.\Fix{...}  This paper focuses
+at lower-level parallelism that can be achieved through build systems
+and testing frameworks.  In the following we elaborate relevant
+features of these components focusing on Java, Maven, and JUnit but
+the discussion can be generalized to other languages, build systems,
+and testing frameworks.
 
-\Fix{...explain different modes of parallel execution offered by build
-  system and or testing framework...(don't use much more than a column
-  of space)}
+\subsection{Build Systems}
+Build systems, such as Maven\footnote{\url{maven.apache.org}},
+typically provide the option to \emph{fork} JVM instances
+proportionally to available cores in the machine.  If the option
+``fork JVM'' is enabled, Maven will allocate a user-provided number of
+JVM instances to each core in the machine and will allocate each test
+class to exactly one JVM.  Note that there is no guarantee to
+uniformly distribute load to each JVM given that the build system uses
+classes as the unit to specify test tasks.\Fix{we need to know how
+  Maven allocates test classes to JVMs}
 
-Modern build systems provides a means to reveal test flakiness.  The
-typical approach is to iteratively execute the test suite multiple
-times and to mark tests that produce both pass and failing outputs.
-More precisely, the developer determines a bound N for the number of
-re-executions of the test suite.  Only tests that fail in one given
-iteration (consequently, failed in all previous iterations) are
-scheduled for re-execution in the next iteration.  At the end of the
-process, a test is considered passing if it passes in the first
-iteration, a test is considered failing if it fails in all iterations,
-and it is considered flaky if it fails in all iterations but the last
-it executed.  The process terminates when all tests eventually pass or
-when bound N is reached.  Note that every iteration runs a subset of
-the test from the previous iteration so execution cost is lower
-compared to executing the suite N times.  To note that ITE is
-supported by the popular maven surefire
-plugin~\cite{maven-surefire-plugin}.\Fix{mention which
-  flag/parameter...} ITE provides a means to acknowledge the presence
-of test flakiness, including \pef{}s.  Ideally, one would like to
-eliminate \pef{}s and avoid the need for ITE.
+\subsection{Testing Framework}
+
+The list below shortly describes the choices to control parallelism
+within each JVM.
+
+\newcommand{\Seq}{L0}
+\newcommand{\ParClassSeqMeth}{L1}
+\newcommand{\SeqClassParMeth}{L2}
+\newcommand{\ParClassParMeth}{L3}
+
+\begin{itemize}
+\item \textbf{Sequential (\Seq).}~This configuration results in
+  sequential execution of test classes and their methods, according to
+  the order defined in the testing framework\Fix{cite}.  For JUnit
+  this is the default configuration.
+\item \textbf{Sequential classes; parallel methods
+  (\ParClassSeqMeth{}).} This configuration results in the sequential
+  execution of the test classes assigned to the JVM.  However, within
+  each class, test methods run in parallel.\Fix{are there options to
+    limit number of threads or a thread per test method?  Do they use
+    thread pools?  etc....}
+\item \textbf{Parallel classes; sequential methods
+  (\SeqClassParMeth{}).}  This configuration results in the parallel
+  execution of test classes but test methods of any given class are
+  executed sequentially.\Fix{one thread per class?  if not, what
+    classes are scheduled to execute first?}
+\item \textbf{Parallel methods (\ParClassParMeth).} This configuration
+  results in parallel execution of any given test method of any class.
+\end{itemize}
+
+\Fix{We need a par. providing rationale in to explain (points in favor/against) these choices.}

### 2016-07-13 paper/icse2017/intro.tex
[Paper] - Added number of test classes from camel
[Paper] Questions about introduction

@@
 prioritization~\Fix{cite}.  Although these approaches can also be
-applied in industrial settings, the focus in industry has been mostly
-in parallelizing execution of tests using server farms, where worker
-machines from the farm are assigned to execute distinct subsets of the
-original test suite.
+applied in industrial settings, \Fix{the focus in industry has been
+mostly in parallelizing execution of tests using server farms, /Is
+this an assumption? Is there any evidence?} where worker machines
+from the farm are assigned to execute distinct subsets of the original
+test suite.
 
@@
 the Apache Camel project~\cite{apache-camel-web}.  This module
-contains 5,679 test cases, declared in \Fix{NN} test classes.  We ran
+contains 5,679 test cases, declared in 2,356 test classes.  We ran
 those tests in a machine with 16GB of memory and 8 virtual CPUs (4
@@
 this is an order of magnitude speedup (10.07x)\Fix{Need to understand
-  why this is 10x as opposed to something closer to 7x}.
+  why this is 10x as opposed to something closer to 7x - I didn't get
+  your concern here}.
 Unfortunately, due to \pef{}, $\sim$2\% (114 of 5,679) of the tests
@@
 efficiently without sacrificing reliability
-\Fix{gap between pars??}
+\Fix{gap between pars?? What gap?}
 

### 2016-07-13 experiments/motivation-experiment/experiment.sh
Updated scripts (worked on it yesterday but didnt commit)

@@ -22,8 +22,12 @@ rm -rf "$SAMPLE_HOME"
 
 echo "Running Experiment on subject \"$NAME\""
 for version in `ls $SAMPLE_HOME`; do
-    echo -e "\n\t* Running setup \"$version\""
-    echo -e "\t* Started: `date`\n"
-    ./flakiness_experiment.py "$NAME" "$SAMPLE_HOME/$version" "$TEST_PATH"
-    echo -e "\n\t* Finished: `date`\n"
+    OUTPUT_FILE="$BASE_DIR/$NAME-$version-summary.txt"
+    echo -e "\n\t* Running setup \"$version\"" >> $OUTPUT_FILE
+    echo -e "\t* Started: `date`\n" >> $OUTPUT_FILE
+    ./flakiness_experiment.py "$NAME" "$SAMPLE_HOME/$version" "$TEST_PATH" >> $OUTPUT_FILE
+    echo -e "\n\t* Finished: `date`\n" >> $OUTPUT_FILE
 done
+
+[[ ! -d outputs ]] && mkdir outputs
+mv *testLog* outputs

### 2016-07-13 experiments/motivation-experiment/main.sh

@@ -12,7 +12,7 @@ if [ ! -d "$SUBJECTS_HOME" ]; then
     exit 1
 fi
 
-./experiment.sh "$SUBJECTS_HOME/retrofit" "retrofit"
+#./experiment.sh "$SUBJECTS_HOME/retrofit" "retrofit"
 ./experiment.sh "$SUBJECTS_HOME/jgit" "org.eclipse.jgit.test"
 ./experiment.sh "$SUBJECTS_HOME/graphhopper" "core"
 ./experiment.sh "$SUBJECTS_HOME/jetty.project" "jetty-client"

### 2016-10-11 paper/conclusions.tex
Renamed paper directory and updated .gitignore file

\section{Conclusions}

\Fix{...}

These tools can be used out-of-the-box to support \emph{system}
testing of applications that have been designed to handle concurrent
user accesses\cite{selenium-hq}.

### 2016-10-11 paper/intro.tex
Renamed paper directory and updated .gitignore file

--- 2016-07-13 paper/icse2017/intro.tex
@@
 prioritization~\Fix{cite}.  Although these approaches can also be
-applied in industrial settings, \Fix{the focus in industry has been
-mostly in parallelizing execution of tests using server farms, /Is
+applied in industrial settings, the focus in industry has been
+mostly in parallelizing execution of tests using server
+farms,\Fix{@Jean: Is
 this an assumption? Is there any evidence?} where worker machines
@@
 %%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
-%%  LocalWords:  Groupon parallelizing multi
+%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM

### 2016-10-11 experiments/test-regression-cost-eval/driver.py
Experiment to evaluate regression test cost

@@ -1,0 +1,52 @@
+#!/usr/bin/python3
+#
+# Author: Jeanderson Candido
+#
+import os
+import json
+import urllib.request
+from subprocess import call, Popen, CalledProcessError, PIPE
+
+from ghwrappers.search import RepositoryQuery
+
+
+def run(queryable):
+    with urllib.request.urlopen(queryable.query()) as response:
+        return json.loads(response.read().decode())
+
+
+def run_tests_from(project):
+    print("Trying to run tests from {name}".format(name=project))
+    working_dir = os.path.abspath(os.curdir)
+    os.chdir(project)
+
+    # FIXME: consider detecting build system instead of assuming Maven
+    p = Popen(["mvn", "clean", "test"], stderr=PIPE, stdout=PIPE)
+    stdout, stderr = p.communicate()
+
+    stderr = stderr.decode()
+    stdout = stdout.decode()
+    with open("stderr-log.txt", "w") as log:
+        log.write(stderr)
+    with open("stdout-log.txt", "w") as log:
+        log.write(stdout)
+
+    os.chdir(working_dir)
+
+
+if not os.path.exists("subjects"):
+    os.mkdir("subjects")
+
+os.chdir("subjects")
+
+data = run(RepositoryQuery().lang("java").stars(">=100"))
+print("Total items from criteria:", data["total_count"])
+for item in data["items"]:
+    proj_name = item["name"]
+    git_url = item["html_url"]
+
+    if not os.path.exists(proj_name):
+        call(["git", "clone", git_url])
+
+    run_tests_from(proj_name)
+

### 2016-10-13 paper/evaluation.tex
Adjusted layout and started to work on eval

\section{Evaluation}

We pose the following research questions:

\newcommand{\RQONE}{\textbf{RQ1.}}
\newcommand{\rqOne}{\RQONE{}~\Fix{Regression-test cost}}

\begin{itemize}
    \item \rqOne
\end{itemize}

The first research question \Fix{...}

\subsection{Subjects}
\label{sec:subjects}

We used the Github's Search API to fetch the top 1.000 projects in
Java with at least 100 stars. The number of stars indicates the
interest and appreciation from the community to a project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation for relevant projects
to conduct our study. From the 1.000 downloaded projects, \Fix{N}
compiled.  \Fix{...}

%% We downloaded the first 1.000 relevant projects from GitHub in Java
%% ranked by the number of \emph{stars}. On Github, the number of stars
%% indicate by the number of stars: each project We believe that this
%% criteria, although subjective, is an approximation for relevant
%% projects to conduct our study: the number of stars indicate popularity
%% and the number of forks is an indicator of collaborators.

### 2016-10-15 paper/evaluation.tex
added description of cost execution

@@
 Java with at least 100 stars. The number of stars indicates the
-interest and appreciation from the community to a project.
+interest and appreciation from the community to a given project.
 \Comment{(https://help.github.com/articles/about-stars/)} Although our
 criteria is subjective, it is an approximation for relevant projects
-to conduct our study. From the 1.000 downloaded projects, \Fix{N}
-compiled.  \Fix{...}
+to conduct our study. For each project, we detected the build manager
+system based on the files located in the root directory from the
+project in the following precedence: \textsc{Maven} if there is a
+\emph{pom.xml} file; \textsc{Gradle} if there is a \emph{gradlew}
+file; \textsc{Ant} if there is a \emph{build.xml} file;. From the
+1.000 downloaded projects, we automatically detected the build system
+from 806 subjects and selected \Fix{154} projects that we were able to
+compile.  The full list of subjects is publicly available at
+\Fix{...}.
 
-%% We downloaded the first 1.000 relevant projects from GitHub in Java
-%% ranked by the number of \emph{stars}. On Github, the number of stars
-%% indicate by the number of stars: each project We believe that this
-%% criteria, although subjective, is an approximation for relevant
-%% projects to conduct our study: the number of stars indicate popularity
-%% and the number of forks is an indicator of collaborators.
+\subsection{Cost of regression test}
+\label{sec:timecost}
+
+To evaluate the cost of test execution, we first compiled the project
+and test source files, later, we measured the elapsed time to run the
+tests via the build system. We ignored non-related tasks such as
+\emph{javadoc} generation.  We grouped the resulting time from test
+execution in four different groups: (1) tests that ran in less than
+one minute, (2) one to five minutes, (3) five to ten minutes, and (4)
+more than ten minutes to execute. Figure \Fix{x} shows the
+distribution of subjects per group. It is important to mention that
+Figure \Fix{x} represents a lower bound for elapsed time: since the
+subjects were tested in a potentially unstable revision, some tests
+may fail, interrupting the execution.
+
+\Fix{Histogram to appear}

### 2016-10-15 paper/evaluation.tex
Added barplot image

@@
 \emph{javadoc} generation.  We grouped the resulting time from test
-execution in four different groups: (1) tests that ran in less than
-one minute, (2) one to five minutes, (3) five to ten minutes, and (4)
-more than ten minutes to execute. Figure \Fix{x} shows the
-distribution of subjects per group. It is important to mention that
-Figure \Fix{x} represents a lower bound for elapsed time: since the
-subjects were tested in a potentially unstable revision, some tests
-may fail, interrupting the execution.
+execution in four different groups: tests that ran in less than one
+minute (group A), one to five minutes (group B), five to ten minutes
+(group C), and more than ten minutes to execute (group D).
+Figure~\ref{fig:timecost-barplot} shows the distribution of subjects
+per group. It is important to mention that
+Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
+time: since the subjects were tested in a potentially unstable
+revision, some tests may fail, interrupting the execution.
 
-\Fix{Histogram to appear}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
+    \caption{\Fix{...}}
+    \label{fig:timecost-barplot}
+\end{figure}

### 2016-10-15 paper/evaluation.tex
Adjustments

@@
 and test source files, later, we measured the elapsed time to run the
-tests via the build system. We ignored non-related tasks such as
-\emph{javadoc} generation.  We grouped the resulting time from test
-execution in four different groups: tests that ran in less than one
+tests via the build system ignoring non-related tasks (\eg,
+\emph{javadoc} generation).  We grouped the resulting time from test
+executions in four different groups: tests that ran in less than one
 minute (group A), one to five minutes (group B), five to ten minutes

### 2016-10-15 experiments/test-regression-cost-eval/helpers.py
Added /usr/bin/time to inspect test execution

@@ -40,9 +40,11 @@ class Maven(Builder):
 
     def test(self):
         init = time()
-        p = Popen(["mvn", "test", "-Dmaven.javadoc.skip=true"],
+        p = Popen(["/usr/bin/time" "-ao", "statistics-exec.txt", "-v",
+                   "mvn", "test", "-Dmaven.javadoc.skip=true"],
                    stdout=PIPE, stderr=PIPE)
-        print("Testing. PID =", p.pid)
+
+        print("Testing (use 'pstree -p $PID' to inspect). PID =", p.pid)
         stdout_raw, stderr_raw = p.communicate()
         self._test_time = time() - init
 

### 2016-10-17 paper/plots/timecost-barplot/genplot.sh
small adjustments on image

@@ -1,3 +1,3 @@
 #!/bin/bash
-DATA_PATH=$1
+DATA_PATH="timecost-groups.csv"
 R --vanilla < script.r --args $DATA_PATH

### 2016-10-17 paper/plots/timecost-barplot/main.sh

@@ -5,4 +5,4 @@ if [ -z $RAW_DATA_PATH ]; then
     exit 1
 fi
 ./gendata.py "$RAW_DATA_PATH"
-./genplot.sh "timecost-groups.csv"
+./genplot.sh

### 2016-10-17 paper/plots/timecost-barplot/script.r

@@ -2,11 +2,12 @@ args <- commandArgs(trailingOnly = TRUE)
 
 pdf(paste("timecost-barplot",".pdf",sep=""),
     width=3,
-    height=5)
+    height=3)
 
 name <- args[1]
 data <- read.table(name, header=F)
 barplot(table(data),
         ylab="Frequency",
-        xlab="Elapsed time groups")
+        xlab="Elapsed time groups",
+        space=0)
 

### 2016-10-18 paper/evaluation.tex
small adjustments on image
Updates on text and plots

@@
 \section{Evaluation}
+\label{sec:eval}
 
-We pose the following research questions:
+We evaluated the characteristics of regression tests in open-source
+development from a sample set of Java projects from Github. We pose
+the following research questions:
 
 \newcommand{\RQONE}{\textbf{RQ1.}}
-\newcommand{\rqOne}{\RQONE{}~\Fix{Regression-test cost}}
+\newcommand{\rqOne}{\RQONE{} \Fix{How prevalent is the occurence of costly
+regression tests?}}
+
+\newcommand{\RQTWO}{\textbf{RQ2.}}
+\newcommand{\rqTwo}{\RQTWO{} \Fix{...}}
+
+\newcommand{\RQTHREE}{\textbf{RQ3.}}
+\newcommand{\rqThree}{\RQTHREE{} \Fix{...}}
+
+\newcommand{\RQFOUR}{\textbf{RQ4.}}
+\newcommand{\rqFour}{\RQFOUR{} How often developers use \Fix{...} to
+improve performance on test execution?}
+
+\newcommand{\RQFIVE}{\textbf{RQ5.}}
+\newcommand{\rqFive}{\RQFIVE{} \Fix{...}}
 
@@
     \item \rqOne
+    \item \rqTwo
+    \item \rqThree
+    \item \rqFour
+    \item \rqFive
 \end{itemize}
 
-The first research question \Fix{...}
+\Fix{describe what I'm looking for with these RQs}
 
@@
 to conduct our study. For each project, we detected the build manager
-system based on the files located in the root directory from the
-project in the following precedence: \textsc{Maven} if there is a
-\emph{pom.xml} file; \textsc{Gradle} if there is a \emph{gradlew}
-file; \textsc{Ant} if there is a \emph{build.xml} file;. From the
-1.000 downloaded projects, we automatically detected the build system
-from 806 subjects and selected \Fix{154} projects that we were able to
+system based on the files located in the root directory (\eg,
+\emph{pom.xml}) from the project in the following precedence:
+\textsc{Maven}, \textsc{Gradle}, and \textsc{Ant}. From the 1.000
+downloaded projects, we automatically detected the build system from
+806 subjects and selected the \Fix{154} projects that we were able to
 compile.  The full list of subjects is publicly available at
@@
 
-\subsection{Cost of regression test}
-\label{sec:timecost}
+\subsection{Results}
+\label{sec:results}
 
-To evaluate the cost of test execution, we first compiled the project
-and test source files, later, we measured the elapsed time to run the
-tests via the build system ignoring non-related tasks (\eg,
+\RQONE{} To evaluate the frequency of costly \Jbc{How to define
+"costly" in terms of time?}regression tests, we first compiled the
+project and test source files, later, we measured the elapsed time to
+run the tests via the build system ignoring non-related tasks (\eg,
 \emph{javadoc} generation).  We grouped the resulting time from test
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
     \centering
     \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
-    \caption{\Fix{...}}
-    \label{fig:timecost-barplot}
+    \caption{\label{fig:timecost-barplot} \Fix{Subjects grouped by
+        elapsed time on test execution ($t$): group A ($t < 1m$), group B
+        ($1m \leq t < 5m$), group C ($5m \leq t < 10m$), group D ($10m \leq t$)}}
 \end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots/teststime-scatter/timetests-scatter.pdf}
+    \caption{\label{fig:timetests-scatter} \Fix{...}}
+\end{figure}
+
+\RQTWO{} \Fix{to appear...}
+
+\RQTHREE{} \Fix{to appear...}
+
+\RQFOUR{} \Fix{to appear...}
+
+\RQFIVE{} \Fix{to appear...}

### 2016-10-18 paper/plots/teststime-scatter/gendata.py

@@ -1,0 +1,23 @@
+#!/usr/bin/python3
+import csv
+import os
+
+from sys import argv
+
+if __name__ == "__main__":
+    raw_data_path = argv[1]
+    if not os.path.exists(raw_data_path):
+        print("Path \"{}\" does not exist!".format(raw_data_path))
+        exit(1)
+
+    with open(raw_data_path, newline='') as f:
+        reader = csv.DictReader(f)
+        with open("timetests-data.csv", "w") as out:
+            out.write("SUBJECT,TESTS,ELAPSED_T")
+            out.write("\n")
+            for row in reader:
+                if not (row["TESTS"] == "N/A" or row["TESTS"] == "0"):
+                    columns = [row["SUBJECT"], row["TESTS"], row["ELAPSED_T"]]
+                    out.write(",".join(columns))
+                    out.write("\n")
+

### 2016-10-18 paper/plots/teststime-scatter/genplot.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+DATA_PATH="timetests-data.csv"
+R --vanilla < script.r --args $DATA_PATH

### 2016-10-18 paper/plots/teststime-scatter/main.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+RAW_DATA_PATH=../../../experiments/test-regression-cost-eval/timecost.csv
+if [ -z $RAW_DATA_PATH ]; then
+    echo "Missing raw data path!"
+    exit 1
+fi
+./gendata.py "$RAW_DATA_PATH"
+./genplot.sh

### 2016-10-18 paper/plots/teststime-scatter/script.r

@@ -1,0 +1,9 @@
+args <- commandArgs(trailingOnly = TRUE)
+
+pdf(paste("timetests-scatter",".pdf",sep=""))
+
+name <- args[1]
+data <- read.table(name, header=T, sep=",")
+plot(data$ELAPSED_T, data$TESTS,
+     xlab="Elapsed time (in secs)",
+     ylab="# of tests")

### 2016-10-18 paper/plots/timecost-barplot/gendata.py

@@ -15,14 +15,7 @@ if __name__ == "__main__":
         reader = csv.DictReader(f)
         for row in reader:
             if row["COMPILED"] == "True":
-                elapsed_time_raw = row["ELAPSED_TIME"]
-
-                time = elapsed_time_raw.replace("s","")
-                if "m" in elapsed_time_raw:
-                    tfields = time.split("m")
-                    seconds = (int(tfields[0]) * 60) + int(tfields[1])
-                else:
-                    seconds = int(time)
+                seconds = float(row["ELAPSED_T"])
                 
                 # Group 1: t < 1m
                 if seconds < 60:

### 2016-10-18 paper/plots/updateall.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+BASEDIR=$(pwd)
+for d in $(ls .); do
+    if [ -f "$d/main.sh" ]; then
+        cd $d
+        ./main.sh
+        cd $BASEDIR
+    fi
+done

### 2016-10-19 paper/evaluation.tex
Reorganizing the eval section and working on RQs

@@
 We evaluated the characteristics of regression tests in open-source
-development from a sample set of Java projects from Github. We pose
-the following research questions:
+development from a sample set of Java projects from Github. We are
+interested in opportunities to improve performance of test execution
+with parallelism \Jbc{Should we use the term parallelism indistinctly
+to refer to multi-process and multi-threaded execution?}, measure the
+obtained gain (if any), and discuss the major concerns that affect
+performance based on the obtained findings.  We pose the following
+research questions:
 
-\newcommand{\RQONE}{\textbf{RQ1.}}
-\newcommand{\rqOne}{\RQONE{} \Fix{How prevalent is the occurence of costly
-regression tests?}}
+\newcommand{\RQONE}{How prevalent is the occurence of costly
+regression tests?}
+\newcommand{\rqOne}{\textbf{RQ1.} \RQONE}
 
-\newcommand{\RQTWO}{\textbf{RQ2.}}
-\newcommand{\rqTwo}{\RQTWO{} \Fix{...}}
+\newcommand{\RQTWO}{\Fix{...}}
+\newcommand{\rqTwo}{\textbf{RQ2.} \RQTWO{}}
 
-\newcommand{\RQTHREE}{\textbf{RQ3.}}
-\newcommand{\rqThree}{\RQTHREE{} \Fix{...}}
+\newcommand{\RQTHREE}{\Fix{...}}
+\newcommand{\rqThree}{\textbf{RQ3.} \RQTHREE{}}
 
-\newcommand{\RQFOUR}{\textbf{RQ4.}}
-\newcommand{\rqFour}{\RQFOUR{} How often developers use \Fix{...} to
+\newcommand{\RQFOUR}{How often developers use \Fix{...} to
 improve performance on test execution?}
+\newcommand{\rqFour}{\textbf{RQ4.} \RQFOUR{}}
 
-\newcommand{\RQFIVE}{\textbf{RQ5.}}
-\newcommand{\rqFive}{\RQFIVE{} \Fix{...}}
+\newcommand{\RQFIVE}{\Fix{...}}
+\newcommand{\rqFive}{\textbf{RQ5.} \RQFIVE{}}
 
@@
 
-\subsection{Results}
-\label{sec:results}
+\subsection{Answering research question RQ1}
+\label{sec:rqone}
 
-\RQONE{} To evaluate the frequency of costly \Jbc{How to define
-"costly" in terms of time?}regression tests, we first compiled the
-project and test source files, later, we measured the elapsed time to
-run the tests via the build system ignoring non-related tasks (\eg,
+\begin{itemize}
+    \item \RQONE
+\end{itemize}
+
+To evaluate the frequency of costly \Jbc{How to define "costly" in
+terms of time?}regression tests, we first compiled the project and
+test source files, later, we measured the elapsed time to run the
+tests via the build system ignoring non-related tasks (\eg,
 \emph{javadoc} generation).  We grouped the resulting time from test
@@
 \end{figure}
-
-\RQTWO{} \Fix{to appear...}
-
-\RQTHREE{} \Fix{to appear...}
-
-\RQFOUR{} \Fix{to appear...}
-
-\RQFIVE{} \Fix{to appear...}

### 2016-10-19 paper/intro.tex
Cleanup intro and added it to the paper

@@
 prioritization~\Fix{cite}.  Although these approaches can also be
-applied in industrial settings, the focus in industry has been
-mostly in parallelizing execution of tests using server
-farms,\Fix{@Jean: Is
-this an assumption? Is there any evidence?} where worker machines
-from the farm are assigned to execute distinct subsets of the original
-test suite.
+applied in industrial settings, the focus in industry has been mostly
+in parallelizing execution of tests using server farms,\Jbc{Is this an
+assumption? Is there any evidence?} where worker machines from the
+farm are assigned to execute distinct subsets of the original test
+suite.
 
@@
 Java language, for example, it is possible to explore parallelism
-  across and within JVMs.}.  For the scenario of large IT
-organizations, lower-level parallelization schemes could leverage the
-computing power of server nodes in addition to the aggregate
-processing power of the farm.  Lower-level parallelism fits
-particularly well smaller organizations (/projects) with relatively
-high testing costs but lower budgets.  Unfortunately, these solutions
-can't be used out-of-the-box: unrestricted parallel execution of tests
-can produce non-deterministic results as developers typically do not
-provision protection to concurrent accesses originated from arbitrary
-program points (\ie{}, tests).  We refer to this problem as Parallel
-Execution Flakiness (\pef{}).
+across and within JVMs.}.  For the scenario of large IT organizations,
+lower-level parallelization schemes could leverage the computing power
+of server nodes in addition to the aggregate processing power of the
+farm.  Lower-level parallelism fits particularly well smaller
+organizations (/projects) with relatively high testing costs but lower
+budgets.  \Comment{Unfortunately, these solutions can't be used out-of-the-box:
+unrestricted parallel execution of tests can produce non-deterministic
+results as developers typically do not provision protection to
+concurrent accesses originated from arbitrary program points (\ie{},
+tests).  We refer to this problem as Parallel Execution Flakiness
+(\pef{}).}
 
-To illustrate the importance of parallel test execution and the
-problem of \pef{} let's consider the case of the ``core'' module from
-the Apache Camel project~\cite{apache-camel-web}.  This module
+To illustrate the importance of parallel test execution, \Jbc{TODO -
+Write a paragraph motivating this paper.}
+
+\Comment{
+To illustrate the importance of parallel test execution and
+the problem of \pef{} let's consider the case of the ``core'' module
+from the Apache Camel project~\cite{apache-camel-web}.  This module
 contains 5,679 test cases, declared in 2,356 test classes.  We ran
@@
 why this is 10x as opposed to something closer to 7x - I didn't get
-  your concern here}.
-Unfortunately, due to \pef{}, $\sim$2\% (114 of 5,679) of the tests
-fail when executed in parallel.  It is important to notice that the
-ratio of failures varies with the project as it depends on factors
-such as length of test cases and amount of shared state across tests.
+your concern here}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of
+5,679) of the tests fail when executed in parallel.  It is important
+to notice that the ratio of failures varies with the project as it
+depends on factors such as length of test cases and amount of shared
+state across tests.
 
@@
 
+}
+
 This paper reports an empirical study to evaluate the impact of
-parallelization options on test execution speedup and \pef{}. Based on
-these results, we proposed different low-cost synchronization
-strategies to avoid \pef{}.
+parallelization options on test execution speedup \Fix{...}\Jbc{TODO -
+Summary of the contributions of this paper} .
 

### 2016-10-20 paper/evaluation.tex
Working on RQs

@@
 
-\newcommand{\RQONE}{How prevalent is the occurence of costly
-regression tests?}
-\newcommand{\rqOne}{\textbf{RQ1.} \RQONE}
+\newcommand{\RQONE}{How prevalent is the occurence of time-consuming
+regression tests in open-source projects?}
+\newcommand{\RQTWO}{What is the distribution of CPU and IO bound
+regression tests from the sample set?}
+\newcommand{\RQTHREE}{What is the proportion of \Fix{time-consuming?}
+test cases per project?}
+\newcommand{\RQFOUR}{How often developers use the parallelism features
+from build manager systems to improve performance on test execution?}
 
-\newcommand{\RQTWO}{\Fix{...}}
-\newcommand{\rqTwo}{\textbf{RQ2.} \RQTWO{}}
-
-\newcommand{\RQTHREE}{\Fix{...}}
-\newcommand{\rqThree}{\textbf{RQ3.} \RQTHREE{}}
-
-\newcommand{\RQFOUR}{How often developers use \Fix{...} to
-improve performance on test execution?}
-\newcommand{\rqFour}{\textbf{RQ4.} \RQFOUR{}}
-
-\newcommand{\RQFIVE}{\Fix{...}}
-\newcommand{\rqFive}{\textbf{RQ5.} \RQFIVE{}}
+\newcommand{\rqA}{\textbf{RQ1.} \RQONE}
+\newcommand{\rqB}{\textbf{RQ2.} \RQTWO}
+\newcommand{\rqC}{\textbf{RQ3.} \RQTHREE}
+\newcommand{\rqD}{\textbf{RQ4.} \RQFOUR}
 
 \begin{itemize}
-    \item \rqOne
-    \item \rqTwo
-    \item \rqThree
-    \item \rqFour
-    \item \rqFive
+    \item \rqA
+    \item \rqB
+    \item \rqC
+    \item \rqD
 \end{itemize}
 
-\Fix{describe what I'm looking for with these RQs}
+The first research question addresses the distribution of subjects per
+elapsed time to execute regression tests. We are interested on
+identifying time-consuming test suites for further investigation. The
+second research question addresses addresses \Fix{...}. The third
+research question addresses the distribution of \Fix{...}. Finally,
+the fourth research question investigates the relevance of supporting
+parallel execution on builder tools.
 
@@
 system based on the files located in the root directory (\eg,
-\emph{pom.xml}) from the project in the following precedence:
-\textsc{Maven}, \textsc{Gradle}, and \textsc{Ant}. From the 1.000
-downloaded projects, we automatically detected the build system from
-806 subjects and selected the \Fix{154} projects that we were able to
-compile.  The full list of subjects is publicly available at
-\Fix{...}.
+\emph{pom.xml}) from the project in the following precedence: Maven,
+Gradle, and Ant. From the 1.000 downloaded projects, we automatically
+detected the build system from 806 subjects and selected the \Fix{154}
+projects that we were able to compile.
+
+\subsection{Setup and Replication}
+\label{sec:setup}
+
+To run our experiments we used a Core i7-4790 (3.60GHz) Intel
+processor machine with 8 virtual CPUs (4 cores with 2 native threads
+each) and 16GB of memory, running on Ubuntu 14.04 LTS (64-bit
+version). \Fix{add Vagrantfile with software settings} All the source
+artifacts, including supporting scripts (\eg, the script that test
+subjects and generates the raw data), and the full list of projects
+are publicly available at \Fix{...}.
 
@@
 
-\begin{itemize}
-    \item \RQONE
-\end{itemize}
+%% \begin{itemize}
+%%     \item \RQONE
+%% \end{itemize}
 
-To evaluate the frequency of costly \Jbc{How to define "costly" in
-terms of time?}regression tests, we first compiled the project and
-test source files, later, we measured the elapsed time to run the
-tests via the build system ignoring non-related tasks (\eg,
-\emph{javadoc} generation).  We grouped the resulting time from test
-executions in four different groups: tests that ran in less than one
-minute (group A), one to five minutes (group B), five to ten minutes
-(group C), and more than ten minutes to execute (group D).
-Figure~\ref{fig:timecost-barplot} shows the distribution of subjects
-per group. It is important to mention that
+To evaluate the frequency of costly regression tests, we first
+compiled the project and test source files, later, we measured the
+elapsed time to run the tests via the build system ignoring
+non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
+resulting time from test executions into four different groups: tests
+that ran in less than one minute (\emph{short execution}), one to five
+minutes (\emph{normal execution}), five to ten minutes (\emph{long
+execution}), and more than ten minutes to execute (\emph{very long
+execution}).  Figure~\ref{fig:timecost-barplot} shows the distribution
+of subjects per group. It is important to mention that
 Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
@@
 \end{figure}
+
+\subsection{Answering research question RQ2}
+\label{sec:rqtwo}
+
+%% \begin{itemize}
+%%     \item \RQTWO
+%% \end{itemize}
+
+\Fix{to appear...}
+
+\subsection{Answering research question RQ3}
+\label{sec:rqthree}
+
+%% \begin{itemize}
+%%     \item \RQTHREE
+%% \end{itemize}
+
+\Fix{to appear...}
+
+\subsection{Answering research question RQ4}
+\label{sec:rqfour}
+
+%% \begin{itemize}
+%%     \item \RQFOUR
+%% \end{itemize}
+
+\Fix{to appear...}

### 2016-10-20 paper/evaluation.tex
Updated answer of RQ1

@@
 
-To evaluate the frequency of costly regression tests, we first
+To evaluate the frequency of time-consuming regression tests, we first
 compiled the project and test source files, later, we measured the
@@
     \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
-    \caption{\label{fig:timecost-barplot} \Fix{Subjects grouped by
-        elapsed time on test execution ($t$): group A ($t < 1m$), group B
-        ($1m \leq t < 5m$), group C ($5m \leq t < 10m$), group D ($10m \leq t$)}}
+    \caption{\label{fig:timecost-barplot} Subjects grouped by elapsed
+    time on test execution ($t$): short execution ($t < 1m$), normal
+    execution ($1m \leq t < 5m$), and long execution ($5m \leq t <
+    10m$), very long execution ($10m \leq t$).}
 \end{figure}
+
+\Fix{Explain scatter plot}
 

### 2016-10-20 paper/evaluation.tex
comments to jean; adding initial title (to help keep the focus)

@@
 \label{sec:eval}
+
+\Mar{I think the high-level goal should be something along the lines
+  of understanding prevalence of long test runs and main sources of
+  cost in open-source Java projects.  Intuitively, the problem should
+  come before the solution :).  Based on that, we study
+  parallelization of testing frameworks.  More precisely, we
+  investigage how prevalent test parallelization is, the potential for
+  improving execution cost, issues of flakiness that hinders use of
+  parallelization, and how to address those issues.}
 
@@
 with parallelism \Jbc{Should we use the term parallelism indistinctly
-to refer to multi-process and multi-threaded execution?}, measure the
+to refer to multi-process and multi-threaded execution?}\Mar{I think I
+used the term low-level parallelism on intro to make this distiction.
+Please confirm if that is correct and coherent with what you want to
+say.  If yes, use this term.}, measure the
 obtained gain (if any), and discuss the major concerns that affect
-performance based on the obtained findings.  We pose the following
+performance based on the obtained findings. We pose the followinga
 research questions:

### 2016-10-21 paper/evaluation.tex
cleanup initial par from eval

@@
 
-We evaluated the characteristics of regression tests in open-source
-development from a sample set of Java projects from Github. We are
-interested in opportunities to improve performance of test execution
-with parallelism \Jbc{Should we use the term parallelism indistinctly
-to refer to multi-process and multi-threaded execution?}\Mar{I think I
-used the term low-level parallelism on intro to make this distiction.
-Please confirm if that is correct and coherent with what you want to
-say.  If yes, use this term.}, measure the
-obtained gain (if any), and discuss the major concerns that affect
-performance based on the obtained findings. We pose the followinga
-research questions:
+We evaluated the characteristics of regression tests in
+open-source development from a sample set of Java projects
+from Github. We are interested in understanding the preva-
+lence of long test runs, the main source of cost, and how
+often developers explore parallelism to improve execution
+performance. We pose the following research questions:
 

### 2016-10-25 paper/intro.tex

@@
 
-Optimizing regression testing is important.  As software evolves the
-size of test sets increases, potentially leading to disruption in the
-development process caused by late reports of test failures.  This
-problem manifests more dramatically at large IT companies
-(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
-Microsoft~\Fix{cite}) where the size of test sets often exceeds the
-size of the code base.  Several approaches have been proposed to
-optimize regression testing.  Research has focused mostly on test
-selection~\Fix{cite}, test reduction~\Fix{cite}, and test
-prioritization~\Fix{cite}.  Although these approaches can also be
-applied in industrial settings, the focus in industry has been mostly
-in parallelizing execution of tests using server farms,\Jbc{Is this an
-assumption? Is there any evidence?} where worker machines from the
-farm are assigned to execute distinct subsets of the original test
-suite.
+Optimizing regression testing is important.  As software evolves test
+sets become more complex (in number of tests or length of test runs),
+potentially leading to disruption in the development process caused by
+late reports of test failures. Several approaches have been
+proposed in the literature to optimize regression testing.  Research
+has focused mostly on test selection, test reduction, and test
+prioritization~\Fix{cite cite...}.
+
+Dealing with high testing costs is a common problem at large IT
+companies (e.g., Groupon~\cite{kim-etal-fse2013}).  \Mar{Ask Milos if
+  there is evidence on how prevalent regression testing is at
+  Microsoft and Google, if he can explain how they run tests, and how
+  prevalent is parallelization (in constrast to regression testing).}
+
+\Fix{...decide how to motivate this study after results are shown.}
+
+%% Although these approaches can also be
+%% applied in industrial settings, the focus in industry has been mostly
+%% in parallelizing execution of tests using server farms, where worker machines from the farm are
+%% assigned to execute distinct subsets of the original test suite.
 

### 2016-10-25 paper/results/cropall.sh
Merged cropall.sh into updateall.sh

@@ -1,8 +1,0 @@
-#!/bin/bash
-#
-# Utility script to crop blank spaces from pdf images
-#
-# Author: Jeanderson Candido
-for PDF in $(find . -name *.pdf); do
-    pdfcrop $PDF $PDF
-done;

### 2016-10-25 paper/results/updateall.sh

@@ -7,3 +7,8 @@ for d in $(ls .); do
         cd $BASEDIR
     fi
 done
+
+# Crop blank spaces
+for PDF in $(find . -name *.pdf); do
+    pdfcrop --margins '3 3 3 3' $PDF $PDF
+done;

### 2016-10-25 paper/intro.tex
pass on text

--- 2016-10-19 paper/intro.tex
@@
 
-Optimizing regression testing is important.  As software evolves the
-size of test sets increases, potentially leading to disruption in the
-development process caused by late reports of test failures.  This
-problem manifests more dramatically at large IT companies
-(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
-Microsoft~\Fix{cite}) where the size of test sets often exceeds the
-size of the code base.  Several approaches have been proposed to
-optimize regression testing.  Research has focused mostly on test
-selection~\Fix{cite}, test reduction~\Fix{cite}, and test
-prioritization~\Fix{cite}.  Although these approaches can also be
-applied in industrial settings, the focus in industry has been mostly
-in parallelizing execution of tests using server farms,\Jbc{Is this an
-assumption? Is there any evidence?} where worker machines from the
-farm are assigned to execute distinct subsets of the original test
-suite.
+As software evolves it is expected that the number of tests and the
+length of test runs increase.  Both elements can add up on the
+aggregate cost of running a test suite, leading to late reports of test
+failures, which can disrupt the development
+process~\cite{hilton-etal-ase2016}.  This is often referred to as the
+``regression testing problem''.  At large IT companies (e.g.,
+Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
+common problem .  \Mar{Ask Milos if he can share stories on how
+  prevalent regression testing is at Microsoft and Google, if he can
+  explain how they run tests, and how prevalent is parallelization (in
+  contrast to regression testing).}
+
+Several approaches have been proposed in the literature to optimize
+regression testing.  Research has focused mostly on test suite
+minimization, prioritization, reduction, and
+selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
+unsound (\ie{}, they do not guarantee that failure-revealing tests
+will be selected), however, more recently, sound techniques have been
+proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
+example, to obtain soundness,
+Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} runs a change-impact
+test analysis based on file dependencies computed and maintained at
+low cost.
+
+Although regression testing is a recognized problem in academia and at
+large IT organizations, to the best of our knowledge no prior work has
+investigated how prevalent the problem is in open-source projects.  We
+assume that the alternative of renting server farms (or even building
+one) to mitigate the problem is economically tempting for large IT
+organizations but not so for open-source projects and projects of
+smaller organizations with lower budgets for building a testing
+infrastructure.  As such, this paper studies (1) how relevant the
+problem of long-running test suites in open-source software really is,
+(2) what are the causes of high execution costs (\eg{}, IO or CPU),
+and (3) what is the impact of existing open-source sound approaches to
+reducing cost.
+
+\Fix{--------------}
 
@@
 %%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
-%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM
+%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
+%%  LocalWords:  Ekstazi

### 2016-10-25 paper/results/rq1/R/piechart.r
Updated plots

@@ -1,7 +1,7 @@
 args <- commandArgs(trailingOnly = TRUE)
 
 out_name <- args[2]
-pdf(paste(out_name,".pdf",sep=""))
+    pdf(paste(out_name,".pdf",sep=""), height=4)
 
 name <- args[1]
 data <- read.csv(name, sep=",", header=T)
@@ -13,7 +13,7 @@ pct <- round(slices / sum(slices) * 100)
 lbls <- paste(pct, "%", sep="")
 colors <- c("gray10", "gray30", "gray80", "white")
 
-pie(slices, labels=lbls, col=colors)
+pie(slices, radius=0.8, labels=lbls, col=colors)
 legend_lbls <- names(table(dist$Var1))
-legend("topright", legend_lbls, fill=colors)
+legend("topright", legend_lbls, fill=colors, cex=0.8)
 

### 2016-10-25 paper/results/updateall.sh

@@ -8,7 +8,10 @@ for d in $(ls .); do
     fi
 done
 
+# TODO: Move pdfcrop calls to R scripts so I can use
+#       different margins
+#
 # Crop blank spaces
 for PDF in $(find . -name *.pdf); do
-    pdfcrop --margins '3 3 3 3' $PDF $PDF
+    pdfcrop $PDF $PDF
 done;

### 2016-10-25 paper/evaluation.tex
Added piechirt

@@
 
-\begin{figure}[t!]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
+    \includegraphics[width=0.5\textwidth]{results/rq1/plots/piechart.pdf}
     \caption{\label{fig:timecost-barplot} Subjects grouped by elapsed
     time on test execution ($t$): short execution ($t < 1m$), normal
-    execution ($1m \leq t < 5m$), and long execution ($5m \leq t <
-    10m$), very long execution ($10m \leq t$).}
+    execution ($1m \leq t < 5m$), long execution ($5m \leq t <
+    10m$), and very long execution ($10m \leq t$).}
 \end{figure}
@@
 
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.5\textwidth]{plots/teststime-scatter/timetests-scatter.pdf}
-    \caption{\label{fig:timetests-scatter} \Fix{...}}
-\end{figure}
+%% \begin{figure}[t!]
+%%     \centering
+%%     \includegraphics[width=0.5\textwidth]{plots/teststime-scatter/timetests-scatter.pdf}
+%%     \caption{\label{fig:timetests-scatter} \Fix{...}}
+%% \end{figure}
 

### 2016-10-25 paper/evaluation.tex
Updated evaluation

@@
 
+\Fix{TODO: MERGE VERY LONG INTO LONG}
 To evaluate the frequency of time-consuming regression tests, we first
@@
 execution}), and more than ten minutes to execute (\emph{very long
-execution}).  Figure~\ref{fig:timecost-barplot} shows the distribution
+execution}).  Figure~\ref{fig:piechart-time} shows the distribution
 of subjects per group. It is important to mention that
-Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
+Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
 time: since the subjects were tested in a potentially unstable
@@
     \includegraphics[width=0.5\textwidth]{results/rq1/plots/piechart.pdf}
-    \caption{\label{fig:timecost-barplot} Subjects grouped by elapsed
+    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
     time on test execution ($t$): short execution ($t < 1m$), normal
@@
 
-%% \begin{figure}[t!]
-%%     \centering
-%%     \includegraphics[width=0.5\textwidth]{plots/teststime-scatter/timetests-scatter.pdf}
-%%     \caption{\label{fig:timetests-scatter} \Fix{...}}
-%% \end{figure}
+\begin{figure}[h!]%
+    \centering
+    \manpage{}
+    \subfigure[\Fix{normal}]{
+        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-norm.pdf}
+    }
+    \\
+    \subfigure[\Fix{long}]{
+        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-long.pdf}
+    }\\
+    \subfigure[\Fix{vlong}]{
+        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-vlong.pdf}
+    }
+    \\
+    \caption{\Fix{...}}
+\end{figure}
 

### 2016-10-25 paper/evaluation.tex
initial par on RQ2

@@
 
-\Fix{Explain scatter plot}
+We compared the execution time and number of tests for each subject. \Fix{...}
 
@@
     \centering
-    \manpage{}
+    \begin{minipage}{4.5in}%
         \subfigure[\Fix{normal}]{
             \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-norm.pdf}
-    }
-    \\
+        }%
         \subfigure[\Fix{long}]{
@@
             \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-vlong.pdf}
-    }
-    \\
+        }%
+    \end{minipage}
     \caption{\Fix{...}}
@@
 
-\Fix{to appear...}
+To evaluate the distribution of CPU and IO bound in regression tests
+from the sample set, we proposed the definition of \emph{cpuness}
+computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
+where \emph{user\_t} is the elapsed time of execution in \emph{user
+mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
+\emph{elapsed\_t} is the elapsed time to finish the execution. We
+measured the \emph{cpuness} of each regression test \Fix{...elaborate
+the meaning of cpuness} \Fix{Describe how I measured user, system and
+"wall" time}.  \Fix{Explain results}.  \Fix{show plots}
 

### 2016-10-25 paper/evaluation.tex
Updated plots and eval

@@
 
-\Fix{TODO: MERGE VERY LONG INTO LONG}
 To evaluate the frequency of time-consuming regression tests, we first
-compiled the project and test source files, later, we measured the
-elapsed time to run the tests via the build system ignoring
-non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
-resulting time from test executions into four different groups: tests
-that ran in less than one minute (\emph{short execution}), one to five
-minutes (\emph{normal execution}), five to ten minutes (\emph{long
-execution}), and more than ten minutes to execute (\emph{very long
-execution}).  Figure~\ref{fig:piechart-time} shows the distribution
-of subjects per group. It is important to mention that
-Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
-time: since the subjects were tested in a potentially unstable
-revision, some tests may fail, interrupting the execution.
+compiled source and test files, later, we measured the elapsed time to
+run the tests via the build system ignoring non-related tasks (\eg,
+\emph{javadoc} generation).  We grouped the subjects according to the
+execution time: tests that ran in less than one minute (\emph{short
+execution}), one to five minutes (\emph{medium execution}), and more
+than five minutes (\emph{long execution}).
+Figure~\ref{fig:piechart-time} shows the proportion of subjects per
+group. It is important to mention that Figure~\ref{fig:piechart-time}
+represents a lower bound for elapsed time: some tests may finish early
+due to a failure since the subjects were tested in a potentially
+unstable revision.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{results/rq1/plots/piechart.pdf}
+    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
     \caption{\label{fig:piechart-time} Subjects grouped by elapsed
-    time on test execution ($t$): short execution ($t < 1m$), normal
-    execution ($1m \leq t < 5m$), long execution ($5m \leq t <
-    10m$), and very long execution ($10m \leq t$).}
+    time on test execution ($t$): short execution ($t < 1m$), medium 
+    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).}
 \end{figure}
 
-We compared the execution time and number of tests for each subject. \Fix{...}
+For the subjects from the groups \emph{medium} and \emph{long}, we
+compared the execution time and the number of tests successfully
+executed. As expected, Figure~\ref{fig:scatters} reveals that the
+number of tests cases are not related to the elapsed time.
+\Fix{explain briefly what dominates a test execution/types of tests}.
+We ignored outliers for better visualization.
 
@@
     \centering
-    \begin{minipage}{4.5in}%
-        \subfigure[\Fix{normal}]{
-            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-norm.pdf}
+    \begin{minipage}{0.5\textwidth}
+        \subfigure[\Fix{medium}]{
+            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-med.pdf}
+        }\\
+        \subfigure[\Fix{long}]{
+            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-long.pdf}
         }%
-        \subfigure[\Fix{long}]{
-            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-long.pdf}
-        }\\
-        \subfigure[\Fix{vlong}]{
-            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-vlong.pdf}
-        }%
-    \end{minipage}
-    \caption{\Fix{...}}
+    \end{minipage}%
+    \caption{\Fix{...use minutes instead of secs...}}%
+    \label{fig:scatters}%
 \end{figure}

### 2016-10-26 paper/intro.tex
minor changes

@@
 selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
-unsound (\ie{}, they do not guarantee that failure-revealing tests
-will be selected), however, more recently, sound techniques have been
+unsound (\ie{}, they do not guarantee that fault-revealing tests will
+be selected), however, more recently, sound techniques have been
 proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
-example, to obtain soundness,
-Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} runs a change-impact
-test analysis based on file dependencies computed and maintained at
-low cost.
+example, to soundly select tests for execution,
+Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} analyzes which files
+that a given test depends on have been impacted by changes. File
+dependencies are computed and maintained at low cost.
 
@@
 investigated how prevalent the problem is in open-source projects.  We
-assume that the alternative of renting server farms (or even building
-one) to mitigate the problem is economically tempting for large IT
-organizations but not so for open-source projects and projects of
-smaller organizations with lower budgets for building a testing
-infrastructure.  As such, this paper studies (1) how relevant the
-problem of long-running test suites in open-source software really is,
-(2) what are the causes of high execution costs (\eg{}, IO or CPU),
-and (3) what is the impact of existing open-source sound approaches to
-reducing cost.
+understand that the alternative of renting server farms (or even
+building one) to mitigate the regression testing problem is a
+potential escape for large IT organizations but not as attractive for
+open-source projects and projects from smaller organizations with
+lower budgets for building testing infrastructures.  This paper
+studies (1) how relevant the problem of long-running test suites in
+open-source software is, (2) what are the causes of high execution
+cost (CPU vs. IO), and (3) what is the impact of existing open-source
+sound approaches to reducing cost.
 

### 2016-10-27 experiments/evaluation/analyzer.py
Added bash time and added %cpu on report

@@ -18,15 +18,16 @@ class ExecutionData:
         self.elapsed_t = 0
         self.system_t = 0
         self.user_t = 0
+        self.cpu_usage = 0
 
     def values(self):
         return [self.subject, self.builder_name, self.compiled, self.tests_pass, self.tests, self.skipped,
-                self.elapsed_t, self.system_t, self.user_t]
+                self.elapsed_t, self.system_t, self.user_t, self.cpu_usage]
 
     @staticmethod
     def header():
         return ["subject", "builder_name", "compiled", "tests_pass", "tests", "skipped",
-                "elapsed_t", "system_t", "user_t"]
+                "elapsed_t", "system_t", "user_t", "cpu_usage"]
 
 
 def inspect(subject):
@@ -42,8 +43,6 @@ def inspect(subject):
         execution_data.builder_name = builder.name
         if builder.compile():
             execution_data.compiled = True
-            # FIXME: How to deal when the project has multiple threads?
-            # One option would be dividing by # of CPUs
             execution_data.tests_pass = builder.test(execution_data)
 
     return execution_data
@@ -96,5 +95,5 @@ def main():
 
 
 if __name__ == "__main__":
-    main()
-    # print(inspect("retrofit"))
+    # main()
+    print(inspect("retrofit").values())

### 2016-10-27 experiments/evaluation/support/builders.py

@@ -34,10 +34,11 @@ class Maven(AbstractBuilder):
         self.test_args = ["mvn", "test", "-Dmaven.javadoc.skip=true"]
 
     def test(self, inspect_data=None):
-        args = ["time", "-o", "/tmp/timeinfo", "-f", "%e,%S,%U,%P"]
-        args.extend(self.test_args)
-        with open("/dev/null", "wb") as DEVNULL:
-            p = Popen(args, stdout=PIPE, stderr=DEVNULL)
+        flag = "ANALYZERTIMMESTAMP,"
+        os.environ["TIMEFORMAT"] = flag + "%R,%S,%U,%P"
+        args = ["bash", "-c", "time " + " ".join(self.test_args)]
+
+        p = Popen(args, stdout=PIPE, stderr=PIPE)
         print("Running tests - PID (use pstree):", p.pid)
         out, err = p.communicate()
         if inspect_data:
@@ -48,13 +49,13 @@ class Maven(AbstractBuilder):
                 inspect_data.tests += int(result[0])
                 inspect_data.skipped += int(result[3])
 
-            with open("/tmp/timeinfo") as f:
-                for line in f:
-                    if not line.startswith("Command"):
-                        output = line.strip().split(",")
-                        inspect_data.elapsed_t = float(output[0])
-                        inspect_data.system_t = float(output[1])
-                        inspect_data.user_t = float(output[2])
+            error = err.decode()
+            for m in re.finditer(r"{}.*".format(flag), error):
+                values = (m.group(0).split(","))
+                inspect_data.elapsed_t = float(values[1])
+                inspect_data.system_t = float(values[2])
+                inspect_data.user_t = float(values[3])
+                inspect_data.cpu_usage = float(values[4])
 
         return not p.returncode
 

### 2016-10-27 paper/intro.tex

@@
 open-source projects and projects from smaller organizations with
-lower budgets for building testing infrastructures.  This paper
-studies (1) how relevant the problem of long-running test suites in
-open-source software is, (2) what are the causes of high execution
-cost (CPU vs. IO), and (3) what is the impact of existing open-source
-sound approaches to reducing cost.
+lower budgets for building testing infrastructures.  As such, this
+paper studies (1) how relevant the problem of long-running test suites
+in open-source software really is, (2) what are the causes of high
+execution costs (\eg{}, IO or CPU), and (3) what is the impact of
+existing open-source sound approaches to reducing cost.
 

### 2016-10-30 paper/evaluation.tex
Updated subject section

@@
 criteria is subjective, it is an approximation for relevant projects
-to conduct our study. For each project, we detected the build manager
-system based on the files located in the root directory (\eg,
+to conduct our study.\Jbc{Subject selection is currently OK but I will
+use another way (eg Google BigQuery) to have access to more subjects.} To
+scale the study, we considered only Maven projects with a
+\emph{pom.xml} file located in the project's root directory. We could
+also include support to other popular build manager systems but we
+noticed that they are commonly related to a particular platform (\eg,
+Gradle and Android) or the build process is based on user-defined
+tasks (\eg, Ant).  \Comment{For each project, we detected the build
+manager system based on the files located in the root directory (\eg,
 \emph{pom.xml}) from the project in the following precedence: Maven,
-Gradle, and Ant. From the 1.000 downloaded projects, we automatically
-detected the build system from 806 subjects and selected the \Fix{154}
-projects that we were able to compile.
+Gradle, and Ant.} From the 1.000 downloaded projects, we selected the
+154 projects that we were able to compile. \Jbc{Remember to update
+those numbers (download + projects) after updating the subject
+selection approach.}
 

### 2016-10-30 paper/evaluation.tex
Updated setup section and added more comments/reminders

@@
 
-We evaluated the characteristics of regression tests in
-open-source development from a sample set of Java projects
-from Github. We are interested in understanding the preva-
-lence of long test runs, the main source of cost, and how
-often developers explore parallelism to improve execution
-performance. We pose the following research questions:
+We evaluated the characteristics of regression tests in open-source
+development from a sample set of Java projects from
+Github\Jbc{Remember to update the previous sentence after updating the
+subject section}. We are interested in understanding the preva- lence
+of long test runs, the main source of cost, and how often developers
+explore parallelism to improve execution performance. We pose the
+following research questions:
 
@@
 
-To run our experiments we used a Core i7-4790 (3.60GHz) Intel
+To run our experiments we used a Core i7-4790 (3.60 GHz) Intel
 processor machine with 8 virtual CPUs (4 cores with 2 native threads
-each) and 16GB of memory, running on Ubuntu 14.04 LTS (64-bit
-version). \Fix{add Vagrantfile with software settings} All the source
-artifacts, including supporting scripts (\eg, the script that test
-subjects and generates the raw data), and the full list of projects
-are publicly available at \Fix{...}.
+each) and 16GB of memory, running on Ubuntu 14.04 LTS Trusty Tahr
+(64-bit version). We provided a \emph{Vagrantfile} to emulate our
+hardware and software setup and dependency settings for replication.
+All the source artifacts, including supporting scripts (\eg, the
+script that test subjects and generates the raw data), and the full
+list of projects are publicly available at \Fix{create gh-pages}.
 

### 2016-10-31 paper/evaluation.tex
Working on RQ2

@@
 
-\newcommand{\RQONE}{How prevalent is the occurence of time-consuming
+\newcommand{\RQA}{How prevalent is the occurence of time-consuming
 regression tests in open-source projects?}
-\newcommand{\RQTWO}{What is the distribution of CPU and IO bound
+\newcommand{\RQB}{What is the distribution of CPU and IO bound
 regression tests from the sample set?}
-\newcommand{\RQTHREE}{What is the proportion of \Fix{time-consuming?}
-test cases per project?}
-\newcommand{\RQFOUR}{How often developers use the parallelism features
+\newcommand{\RQC}{How the execution time is distributed among test
+cases?}
+\newcommand{\RQD}{How often developers use the parallelism features
 from build manager systems to improve performance on test execution?}
 
-\newcommand{\rqA}{\textbf{RQ1.} \RQONE}
-\newcommand{\rqB}{\textbf{RQ2.} \RQTWO}
-\newcommand{\rqC}{\textbf{RQ3.} \RQTHREE}
-\newcommand{\rqD}{\textbf{RQ4.} \RQFOUR}
+\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
+\newcommand{\rqTwo}{\textbf{RQ2.} \RQC}
+\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
+\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
 
 \begin{itemize}
-    \item \rqA
-    \item \rqB
-    \item \rqC
-    \item \rqD
+    \item \rqOne
+    \item \rqTwo
+    \item \rqThree
+    \item \rqFour
 \end{itemize}
@@
 identifying time-consuming test suites for further investigation. The
-second research question addresses addresses \Fix{...}. The third
-research question addresses the distribution of \Fix{...}. Finally,
-the fourth research question investigates the relevance of supporting
-parallel execution on builder tools.
+second research question addresses the distribution of execution time
+per test case for each project. The rationale is that if the time cost
+of a regression test is equally distributed among test cases, the
+execution cost could be potentially improved by running tests in
+parallel (in contrast to the scenario where only one test case
+dominates most of the execution time).
 
@@
 
-%% \begin{itemize}
-%%     \item \RQONE
-%% \end{itemize}
+\begin{itemize}
+    \item \RQA
+\end{itemize}
 
@@
 \subsection{Answering research question RQ2}
-\label{sec:rqtwo}
+\label{sec:rqTwo}
 
-%% \begin{itemize}
-%%     \item \RQTWO
-%% \end{itemize}
+\begin{itemize}
+    \item \RQC
+\end{itemize}
+
+To evaluate the distribution of execution time, we collected from the
+test report (\ie, Surefire XML file) the elapsed time to execute
+each test case and \Fix{...to be continued...}.
+
+\subsection{Answering research question RQ3}
+\label{sec:rqThree}
+
+\begin{itemize}
+    \item \RQB
+\end{itemize}
 
@@
 
-\subsection{Answering research question RQ3}
-\label{sec:rqthree}
-
-%% \begin{itemize}
-%%     \item \RQTHREE
-%% \end{itemize}
-
-\Fix{to appear...}
-
 \subsection{Answering research question RQ4}

### 2016-10-31 experiments/evaluation/analysis.py
Updated scripts

@@ -1,0 +1,48 @@
+import os
+
+from support import maven
+
+
+class ExecutionData:
+    def __init__(self, subject="N/A"):
+        self.subject = subject
+        self.builder_name = "N/A"
+        self.compiled = False
+        self.tests_pass = False
+        self.tests = 0
+        self.skipped = 0
+        self.elapsed_t = 0
+        self.system_t = 0
+        self.user_t = 0
+        self.cpu_usage = 0
+
+    def values(self):
+        return [self.subject, self.builder_name, self.compiled, self.tests_pass, self.tests, self.skipped,
+                self.elapsed_t, self.system_t, self.user_t, self.cpu_usage]
+
+    @staticmethod
+    def header():
+        return ["subject", "builder_name", "compiled", "tests_pass", "tests", "skipped",
+                "elapsed_t", "system_t", "user_t", "cpu_usage"]
+
+
+def main(subject_name, subjects_home=os.curdir):
+    subject_dir = os.path.join(subjects_home, subject_name)
+    if not os.path.exists(subject_dir):
+        print("Missing path:", subject_dir)
+        return
+
+    output_data = ExecutionData(subject_name)
+
+    os.chdir(subject_dir)
+    if maven.is_maven_project():
+        output_data.builder_name = "Maven"
+        if maven.build():
+            output_data.compiled = True
+            output_data.tests_pass = maven.test(output_data)
+            data = maven.collect_surefire_data()
+
+    return output_data
+
+if __name__ == "__main__":
+    pass

### 2016-10-31 experiments/evaluation/support/builders.py

@@ -1,100 +1,0 @@
-# Helper classes
-#
-# Author: Jeanderson Candido
-#
-import os
-import re
-from subprocess import call, Popen, PIPE, TimeoutExpired
-
-
-class AbstractBuilder:
-    def __init__(self):
-        self.name = None
-        self.compile_args = None
-        self.test_args = None
-
-    def compile(self):
-        """ Returns True if finished successfully """
-        with open("/dev/null", "wb") as DEVNULL:
-            try:
-                result = not call(self.compile_args, stdout=DEVNULL, timeout=900)
-            except TimeoutExpired:
-                result = False
-        return result
-
-    def test(self):
-        pass
-
-
-class Maven(AbstractBuilder):
-    def __init__(self):
-        super().__init__()
-        self.name = "Maven"
-        self.compile_args = ["mvn", "clean", "install", "-DskipTests", "-Dmaven.javadoc.skip=true"]
-        self.test_args = ["mvn", "test", "-Dmaven.javadoc.skip=true"]
-
-    def test(self, inspect_data=None):
-        flag = "ANALYZERTIMMESTAMP,"
-        os.environ["TIMEFORMAT"] = flag + "%R,%S,%U,%P"
-        args = ["bash", "-c", "time " + " ".join(self.test_args)]
-
-        p = Popen(args, stdout=PIPE, stderr=PIPE)
-        print("Running tests - PID (use pstree):", p.pid)
-        out, err = p.communicate()
-        if inspect_data:
-            output = out.decode()
-            pattern = re.compile(r"Results :\n\nTests run: .*", re.MULTILINE)
-            for m in re.finditer(pattern, output):
-                result = re.findall("\d+", m.group(0))
-                inspect_data.tests += int(result[0])
-                inspect_data.skipped += int(result[3])
-
-            error = err.decode()
-            for m in re.finditer(r"{}.*".format(flag), error):
-                values = (m.group(0).split(","))
-                inspect_data.elapsed_t = float(values[1])
-                inspect_data.system_t = float(values[2])
-                inspect_data.user_t = float(values[3])
-                inspect_data.cpu_usage = float(values[4])
-
-        return not p.returncode
-
-
-class Ant(AbstractBuilder):
-    # TODO Feel free to implement Ant support
-    def __init__(self):
-        super().__init__()
-        self.name = "Ant"
-
-    def compile(self):
-        pass
-
-
-class Gradle(AbstractBuilder):
-    # TODO Feel free to implement Gradle support
-    def __init__(self):
-        super().__init__()
[…]

### 2016-10-31 experiments/evaluation/support/maven.py

@@ -1,0 +1,85 @@
+# Helper classes
+#
+# Author: Jeanderson Candido
+#
+import os
+import re
+from collections import namedtuple, Counter
+from subprocess import call, Popen, PIPE, TimeoutExpired, check_output
+from xml.etree import ElementTree
+
+
+def build():
+    with open(os.devnull, "wb") as DEVNULL:
+        compile_command = ["mvn", "clean", "install", "-DskipTests", "-Dmaven.javadoc.skip=true"]
+        try:
+            result = not call(compile_command, stdout=DEVNULL, timeout=900)
+        except TimeoutExpired:
+            result = False
+    return result
+
+
+def test(inspect_data=None):
+    flag = "ANALYZERTIMMESTAMP,"
+    test_command = ["mvn", "test", "-Dmaven.javadoc.skip=true"]
+
+    os.environ["TIMEFORMAT"] = flag + "%R,%S,%U,%P"
+    args = ["bash", "-c", "time " + " ".join(test_command)]
+
+    p = Popen(args, stdout=PIPE, stderr=PIPE)
+    print("Running tests - PID (use pstree):", p.pid)
+    out, err = p.communicate()
+    if inspect_data:
+        output = out.decode()
+        pattern = re.compile(r"Results :\n\nTests run: .*", re.MULTILINE)
+        for m in re.finditer(pattern, output):
+            result = re.findall("\d+", m.group(0))
+            inspect_data.tests += int(result[0])
+            inspect_data.skipped += int(result[3])
+
+        error = err.decode()
+        for m in re.finditer(r"{}.*".format(flag), error):
+            values = (m.group(0).split(","))
+            inspect_data.elapsed_t = float(values[1])
+            inspect_data.system_t = float(values[2])
+            inspect_data.user_t = float(values[3])
+            inspect_data.cpu_usage = float(values[4])
+
+    return not p.returncode
+
+
+def collect_surefire_data():
+    """
+    Collect data from surefire reports.
+    Returns a Data tuple with statistics counter and a list of test cases data.
+    """
+    output = check_output(["find", ".", "-name", "TEST-*.xml"]).decode()
+
+    TestCase = namedtuple("TestCase", "name, time")
+    counter = Counter(tests=0, skipped=0, failure=0, time=0.0)
+    test_cases = []
+
+    for xml_path in output.splitlines():
+        test_suite = ElementTree.parse(xml_path).getroot()
+
[…]

### 2016-10-31 paper/evaluation.tex
some text related to time distribution

@@
 
-To evaluate the distribution of execution time, we collected from the
-test report (\ie, Surefire XML file) the elapsed time to execute
-each test case and \Fix{...to be continued...}.
+To evaluate the distribution of execution time, we calculated the cost
+from 90\% of test cases ordered by execution time and compared the
+resulting value to the total time.  We collected the elapsed time from
+test cases for each generated report. Maven Surefire generates an XML
+report with execution information (\eg, number of skipped tests and
+elapsed time) per test suite \Jbc{Should I use the previous sentence
+as a footnote or should I delete it?}. We noticed that some test
+cases reported an elapsed time of zero: since the reported time is in
+milliseconds, some tests may execute in a shorter time.
 

### 2016-10-31 experiments/evaluation/support/maven.py
updated maven script

@@ -57,22 +57,26 @@ def collect_surefire_data():
     Returns a Data tuple with statistics counter and a list of test cases data.
     """
     output = check_output(["find", ".", "-name", "TEST-*.xml"]).decode()
-
-    counter = Counter(tests=0, skipped=0, failure=0, time=0.0)
+    total_counter = Counter(tests=0, skipped=0, failure=0, time=0.0)
     test_cases = []
 
     for xml_path in output.splitlines():
         test_suite = ElementTree.parse(xml_path).getroot()
 
-        counter += Counter(failure=int(test_suite.get("errors")) + int(test_suite.get("failures")),
-                           tests=int(test_suite.get("tests")), skipped=int(test_suite.get("skipped")),
-                           time=float(test_suite.get("time")))
+        failure_cnt = get_value_from(test_suite, "failures", default_value=0, cast_type=int)
+        error_cnt = get_value_from(test_suite, "errors", default_value=0, cast_type=int)
+        tests_cnt = get_value_from(test_suite, "tests", default_value=0, cast_type=int)
+        skipped_cnt = get_value_from(test_suite, "skipped", default_value=0, cast_type=int)
+        time_cnt = get_value_from(test_suite, "time", default_value=0.0, cast_type=float)
+
+        total_counter.update(Counter(tests=tests_cnt, skipped=skipped_cnt, time=time_cnt,
+                                     failure=(failure_cnt + error_cnt)))
 
         for test_case in test_suite.iter("testcase"):
             test_name = "%s.%s" % (test_case.get("classname"), test_case.get("name"))
             test_cases.append(TestCase(name=test_name, time=float(test_case.get("time"))))
 
-    return SurefireData(items=test_cases, statistics=counter)
+    return SurefireData(items=test_cases, statistics=total_counter)
 
 
 def is_maven_project():
@@ -80,7 +84,6 @@ def is_maven_project():
     return os.path.exists("pom.xml")
 
 
-# FIXME remove this temporary code...
-if __name__ == "__main__":
-    os.chdir("../subjects/retrofit")
-    print(collect_surefire_data())
+def get_value_from(xml_node, attribute, default_value, cast_type):
+    """ Auxiliary function from collect_surefire_data """
+    return default_value if not xml_node.get(attribute) else cast_type(xml_node.get(attribute))

### 2016-10-31 experiments/evaluation/analysis.py
Added temp code to output data and added function to compute time distrib

@@ -26,22 +26,17 @@ class ExecutionData:
                 "elapsed_t", "system_t", "user_t", "cpu_usage"]
 
 
-# FIXME test this!
 def compute_time_distribution(data):
+    if not data.statistics['time']:
+        return -1
     test_cases = sorted(data.items, key=lambda t: t.time)
-    total_time = data.statistics['time']
-    coverage = 0.9
+    size = len(test_cases)
+    time_counter = 0
+    for i in range(round(size * 0.9)):
+        time_counter += test_cases[i].time
 
-    threshold = total_time * coverage
-    counter = 0
-    current_time = 0.0
-    for tc in test_cases:
-        current_time += tc.time
-        counter += 1
-        print(" ", threshold, current_time)
-        if current_time >= threshold:
-            break
-    print(data.statistics, threshold, counter, current_time)
+    # FIXME: this computation is not much accurate
+    return (time_counter / data.statistics['time']) * 100
 
 
 def main(subject_name, subjects_home=os.curdir):
@@ -65,5 +60,11 @@ def main(subject_name, subjects_home=os.curdir):
     return output_data
 
 if __name__ == "__main__":
-    os.chdir("./subjects/storm")
-    compute_time_distribution(maven.collect_surefire_data())
+    output_file = os.path.join(os.path.abspath(os.curdir), "distrib.csv")
+    base_dir = os.path.join(os.path.abspath(os.curdir), "subjects")
+    for p in os.listdir(base_dir):
+        os.chdir(os.path.join(base_dir, p))
+        if maven.is_maven_project():
+            d = compute_time_distribution(maven.collect_surefire_data())
+            with open(output_file, "a") as csv:
+                csv.write("%s, %.2f\n" % (p, d))

### 2016-10-31 paper/intro.tex
minor changes to intro

--- 2016-10-26 paper/intro.tex
@@
 As software evolves it is expected that the number of tests and the
-length of test runs increase.  Both elements can add up on the
+length of test runs increase.  Both elements can add up to the
 aggregate cost of running a test suite, leading to late reports of test
 failures, which can disrupt the development
-process~\cite{hilton-etal-ase2016}.  This is often referred to as the
-``regression testing problem''.  At large IT companies (e.g.,
+process~\cite{hilton-etal-ase2016}.\Comment{  This is often referred to as the
+``regression testing problem''.}  At large IT companies (e.g.,
 Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
@@
 large IT organizations, to the best of our knowledge no prior work has
-investigated how prevalent the problem is in open-source projects.  We
-understand that the alternative of renting server farms (or even
-building one) to mitigate the regression testing problem is a
-potential escape for large IT organizations but not as attractive for
-open-source projects and projects from smaller organizations with
-lower budgets for building testing infrastructures.  This paper
+investigated how prevalent the problem is in open-source projects.
+For large IT organizations, the alternative of renting server farms,
+or even building one, is a potential escape to mitigate the regression
+testing problem.  However, for open-source projects and projects from
+smaller organizations with lower budgets for building testing
+infrastructures, this alternative is not as attractive.  This paper
 studies (1) how relevant the problem of long-running test suites in

### 2016-10-31 experiments/evaluation/analysis.py
work in progress - added barplot from RQ2

@@ -30,13 +30,20 @@ def compute_time_distribution(data):
     if not data.statistics['time']:
         return -1
     test_cases = sorted(data.items, key=lambda t: t.time)
-    size = len(test_cases)
-    time_counter = 0
-    for i in range(round(size * 0.9)):
-        time_counter += test_cases[i].time
+    total_time = data.statistics['time']
+    total_tests = data.statistics['tests']  # - data.statistics['skipped']
 
-    # FIXME: this computation is not much accurate
-    return (time_counter / data.statistics['time']) * 100
+    threshold = round(total_time * 0.9)
+    size = len(test_cases)
+
+    time_counter = test_counter = 0
+    for i in range(size):
+        time_counter += test_cases[i].time
+        test_counter += 1
+        if (i < size - 1) and (time_counter + test_cases[i + 1].time > threshold):
+            break
+
+    return round((test_counter / total_tests) * 100)
 
 
 def main(subject_name, subjects_home=os.curdir):
@@ -63,8 +70,20 @@ if __name__ == "__main__":
     output_file = os.path.join(os.path.abspath(os.curdir), "distrib.csv")
     base_dir = os.path.join(os.path.abspath(os.curdir), "subjects")
     for p in os.listdir(base_dir):
-        os.chdir(os.path.join(base_dir, p))
-        if maven.is_maven_project():
-            d = compute_time_distribution(maven.collect_surefire_data())
-            with open(output_file, "a") as csv:
-                csv.write("%s, %.2f\n" % (p, d))
+        if os.path.isdir(os.path.join(base_dir, p)):
+            os.chdir(os.path.join(base_dir, p))
+            if maven.is_maven_project():
+                d = compute_time_distribution(maven.collect_surefire_data())
+                if 0 <= d < 20:
+                    d = "0%-20%"
+                elif 20 <= d < 40:
+                    d = "20%-40%"
+                elif 40 <= d < 60:
+                    d = "40%-60%"
+                elif 60 <= d < 80:
+                    d = "60%-80%"
+                elif 80 <= d:
+                    d = "80%-100%"
+
+                with open(output_file, "a") as csv:
+                    csv.write("%s,%s\n" % (p, d))

### 2016-10-31 experiments/evaluation/support/maven.py

@@ -86,4 +86,4 @@ def is_maven_project():
 
 def get_value_from(xml_node, attribute, default_value, cast_type):
     """ Auxiliary function from collect_surefire_data """
-    return default_value if not xml_node.get(attribute) else cast_type(xml_node.get(attribute))
+    return default_value if not xml_node.get(attribute) else cast_type(xml_node.get(attribute).replace(",", ""))

### 2016-11-01 paper/evaluation.tex
work in progress - added barplot from RQ2
Pass on eval - Subjects and Setup

@@
 
-We used the Github's Search API to fetch the top 1.000 projects in
-Java with at least 100 stars. The number of stars indicates the
-interest and appreciation from the community to a given project.
+We used the Github's Search API to fetch the top 1,000 Java projects
+with at least 100 stars. The number of stars indicates the interest
+and appreciation from the community to a given project.
 \Comment{(https://help.github.com/articles/about-stars/)} Although our
-criteria is subjective, it is an approximation for relevant projects
-to conduct our study.\Jbc{Subject selection is currently OK but I will
-use another way (eg Google BigQuery) to have access to more subjects.} To
-scale the study, we considered only Maven projects with a
-\emph{pom.xml} file located in the project's root directory. We could
-also include support to other popular build manager systems but we
-noticed that they are commonly related to a particular platform (\eg,
-Gradle and Android) or the build process is based on user-defined
-tasks (\eg, Ant).  \Comment{For each project, we detected the build
-manager system based on the files located in the root directory (\eg,
-\emph{pom.xml}) from the project in the following precedence: Maven,
-Gradle, and Ant.} From the 1.000 downloaded projects, we selected the
-154 projects that we were able to compile. \Jbc{Remember to update
-those numbers (download + projects) after updating the subject
-selection approach.}
+criteria is subjective, it is an approximation to find relevant
+projects to conduct our study.\Jbc{Subject selection is currently OK
+    but I will use another way (eg Google BigQuery) to have access to
+more subjects.} For each project, we detected the build manager system
+based on the files located in the root directory from the project in
+the following precedence: Maven (\emph{pom.xml)}, Gradle
+(\emph{gradlew}), and Ant (\emph{build.xml}). From the 1,000
+downloaded projects (composed by \Fix{X} Maven, \Fix{Y} Gradle,
+\Fix{W} Ant, and \Fix{W} unknown projects), we selected the 154 Maven
+projects that we were able to compile\Jbc{Remember to update those
+numbers (download + projects) after updating the subject selection
+approach.}. We noticed that we are unable to compile other subjects
+because other build systems are commonly related to a particular
+platform (\eg, Gradle implied Android), the build process is based on
+user-defined tasks (\eg, Ant), or the project has unsolved
+dependencies.
 
@@
 
-To run our experiments we used a Core i7-4790 (3.60 GHz) Intel
+To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
 processor machine with 8 virtual CPUs (4 cores with 2 native threads
-each) and 16GB of memory, running on Ubuntu 14.04 LTS Trusty Tahr
-(64-bit version). We provided a \emph{Vagrantfile} to emulate our
-hardware and software setup and dependency settings for replication.
-All the source artifacts, including supporting scripts (\eg, the
-script that test subjects and generates the raw data), and the full
-list of projects are publicly available at \Fix{create gh-pages}.
+each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
+(64-bit version). Our evaluation scripts depends on \Fix{specify:
+unix-based tools} to measure CPU usage and \emph{Python 3.4} (or
+later). For replication, we provide all the source artifacts publicly
+available at \Fix{create gh-pages}, including supporting scripts (\eg,
+the script that test subjects and generates the raw data), the full
+list of projects, and a \emph{Vagrantfile} to emulate our hardware and
+software setup and dependency settings .
 
@@
 elapsed time) per test suite \Jbc{Should I use the previous sentence
-as a footnote or should I delete it?}. We noticed that some test
-cases reported an elapsed time of zero: since the reported time is in
-milliseconds, some tests may execute in a shorter time.
+as a footnote or should I delete it?}. We noticed that some test cases
+reported an elapsed time of zero: since the reported time is in
+milliseconds, some tests may execute in a shorter time. \Fix{..to be
+continued...}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{figs/tcdistrib.pdf}
+    \caption{\Fix{...}}
+\end{figure}
 

### 2016-11-01 paper/evaluation.tex
Updated eval text

@@
 
-We used the Github's Search API to fetch the top 1,000 Java projects
-with at least 100 stars. The number of stars indicates the interest
-and appreciation from the community to a given project.
+\Jbc{Subject selection is currently OK but I will use another way (eg
+Google BigQuery) to have access to more subjects.}We used the Github's
+Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
+    Search API imposes the limit of 1,000 results regardless of the
+total number of matches from a search criteria.} Java projects with at
+least 100 stars. The number of stars indicates the interest and
+appreciation from the community to a given project.
 \Comment{(https://help.github.com/articles/about-stars/)} Although our
 criteria is subjective, it is an approximation to find relevant
-projects to conduct our study.\Jbc{Subject selection is currently OK
-    but I will use another way (eg Google BigQuery) to have access to
-more subjects.} For each project, we detected the build manager system
+projects to conduct our study. We detected the build manager system
 based on the files located in the root directory from the project in
 the following precedence: Maven (\emph{pom.xml)}, Gradle
-(\emph{gradlew}), and Ant (\emph{build.xml}). From the 1,000
-downloaded projects (composed by \Fix{X} Maven, \Fix{Y} Gradle,
-\Fix{W} Ant, and \Fix{W} unknown projects), we selected the 154 Maven
-projects that we were able to compile\Jbc{Remember to update those
-numbers (download + projects) after updating the subject selection
-approach.}. We noticed that we are unable to compile other subjects
-because other build systems are commonly related to a particular
-platform (\eg, Gradle implied Android), the build process is based on
-user-defined tasks (\eg, Ant), or the project has unsolved
-dependencies.
+(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
+the following values after updating the subject selection approach.}
+From the 1,000 downloaded projects, we detected the build system of
+801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
+and considered \Fix{154} projects that we were able to compile.
+\Fix{We noticed that we are unable to compile other subjects because of
+unsolved dependencies, other build systems are commonly related to a
+particular platform (\eg, Gradle implied Android), or the build
+process is based on user-defined tasks (\eg, Ant).}
 

### 2016-11-02 paper/evaluation.tex
minor change

@@
     Search API imposes the limit of 1,000 results regardless of the
-total number of matches from a search criteria.} Java projects with at
+number of matches from a search criteria.} Java projects with at
 least 100 stars. The number of stars indicates the interest and

### 2016-11-02 experiments/evaluation/thirdparty.sh
minor update on provisioning script

@@ -1,6 +1,7 @@
 #!/bin/bash
 #
-# Installs required third-party packages
+# Installs required third-party packages for vagrant provisioning.
+#
 # Author: Jeanderson Candido
 BASE_DIR=$(pwd)
 THIRDPARTY_HOME=$BASE_DIR/thirdparty

### 2016-11-02 paper/intro.tex
pass on intro and modes

--- 2016-10-26 paper/intro.tex
@@
 
+%% . which can disrupt the development
+%% process~\cite{hilton-etal-ase2016}.\Comment{  This is often referred to as the
+%% ``regression testing problem''.}
+
 As software evolves it is expected that the number of tests and the
-length of test runs increase.  Both elements can add up on the
-aggregate cost of running a test suite, leading to late reports of test
-failures, which can disrupt the development
-process~\cite{hilton-etal-ase2016}.  This is often referred to as the
-``regression testing problem''.  At large IT companies (e.g.,
+length of test runs increase.  Both elements can add up to the
+aggregate cost of running a test suite, which can lead to late reports of test
+failures.  At large IT companies (e.g.,
 Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
@@
 example, to soundly select tests for execution,
-Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} analyzes which files
-that a given test depends on have been impacted by changes. File
-dependencies are computed and maintained at low cost.
+Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
+computes which tests have been impacted by changes.  It analyzes, for
+each test, which file dependencies have been change impacted.
+
+%; these
+%dependencies are computed and maintained at low cost.
 
@@
 large IT organizations, to the best of our knowledge no prior work has
-investigated how prevalent the problem is in open-source projects.  We
-understand that the alternative of renting server farms (or even
-building one) to mitigate the regression testing problem is a
-potential escape for large IT organizations but not as attractive for
-open-source projects and projects from smaller organizations with
-lower budgets for building testing infrastructures.  This paper
-studies (1) how relevant the problem of long-running test suites in
-open-source software is, (2) what are the causes of high execution
-cost (CPU vs. IO), and (3) what is the impact of existing open-source
-sound approaches to reducing cost.
+investigated how prevalent the problem is in open-source projects.
+For large IT organizations, the alternative of renting server farms,
+or even building one, is a potential escape to the regression testing
+problem.  However, for open-source projects and for projects of
+smaller organizations with lower budgets for building testing
+infrastructures, this alternative may not be as attractive.
+
+\newcommand{\numSubjs}{143}
+
+Motivated by this potential gap in regression testing practice, this
+paper studies (1) how prevalent long-running test suites are in
+open-source software projects.  To conduct this experiment we selected
+\numSubjs{} Java projects from github that are highly-popular and use
+the Maven build system.  (Section~\ref{sec:eval} details our selection
+criteria.)  Our experimental results indicate that long-running test
+suites (taking longer than 5m\Fix{check if Ekstazi paper also used
+  this value and cite} to complete) are not rare (\Fix{17\%} of the
+projects).  From this result we investigated (2) how frequently
+long-running test suites use parallelization.  Our results indicate
+that \Fix{80\%} of the long-running projects do use parallelization to
+speedup execution.  Given the popularity of this solution, we further
+studied: (3) what are the causes of high execution cost in individual
+tests (CPU vs. IO) and (4) how uniformly cost is distributed across
+tests.  These questions help to assess the impact of parallelization
+in each of these projects.  Intuitively, IO-intensive test suites and
+test suites with uneven distribution of cost per test are factors that
+limit the effects of parallelization.  Results indicate that \Fix{...}
+Finally, we investigated (5) what are the limitations related with
+parallelization that could justify adoption resistance.
 
@@
 
-Given the proliferation of multicore machines it is not surprising
-that popular build systems and testing frameworks provide today
-support for parallel test execution with the goal of running tests
-more efficiently~\cite{junit-org,testng,nunit,maven-surefire-plugin}.
-The lower-level parallelism enabled through build systems and testing
-frameworks is an important complement to the higher-level parallelism
-enabled through server farms.  These solutions enable the use of
-commodity hardware to maximize CPU usage\footnote{In the case of the
-Java language, for example, it is possible to explore parallelism
-across and within JVMs.}.  For the scenario of large IT organizations,
-lower-level parallelization schemes could leverage the computing power
-of server nodes in addition to the aggregate processing power of the
-farm.  Lower-level parallelism fits particularly well smaller
-organizations (/projects) with relatively high testing costs but lower
-budgets.  \Comment{Unfortunately, these solutions can't be used out-of-the-box:
-unrestricted parallel execution of tests can produce non-deterministic
-results as developers typically do not provision protection to
-concurrent accesses originated from arbitrary program points (\ie{},
-tests).  We refer to this problem as Parallel Execution Flakiness
-(\pef{}).}
-
 To illustrate the importance of parallel test execution, \Jbc{TODO -
 Write a paragraph motivating this paper.}
-
-\Comment{
-To illustrate the importance of parallel test execution and
-the problem of \pef{} let's consider the case of the ``core'' module
-from the Apache Camel project~\cite{apache-camel-web}.  This module
-contains 5,679 test cases, declared in 2,356 test classes.  We ran
-those tests in a machine with 16GB of memory and 8 virtual CPUs (4
-cores with 2 native threads each).  Sequential test execution takes
-24m50s to run this test set.  Execution of the same test set takes
-2m28s when we configured parallel execution to fork a JVM per CPU and
-execute test classes, uniquely allocated to that JVM, sequentially but
-running test methods from each class in separate threads.  Note that
-this is an order of magnitude speedup (10.07x)\Fix{Need to understand
-why this is 10x as opposed to something closer to 7x - I didn't get
-your concern here}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of
-5,679) of the tests fail when executed in parallel.  It is important
-to notice that the ratio of failures varies with the project as it
-depends on factors such as length of test cases and amount of shared
-state across tests.
-
-\pef{} is an important obstacle to enable parallel test execution.
-Conceptually, higher parallelization can result in higher chances of
-concurrency-related problems.  It is important to execute tests
-efficiently without sacrificing reliability
-\Fix{gap between pars?? What gap?}
-
-}
 
@@
 %%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
-%%  LocalWords:  Ekstazi
+%%  LocalWords:  Ekstazi github

### 2016-11-02 paper/modes.tex
pass on intro and modes

--- 2016-07-11 paper/icse2017/modes.tex
@@
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figs/parallel-levels.pdf}
-  \caption{\label{fig:levels}Levels of parallelism.}
-\end{figure}
+%%, potentially using commodity hardware
 
-Parallelism in test execution can be achieved at different levels.
-Figure~\ref{fig:levels} illustrates that.\Fix{...}  This paper focuses
-at lower-level parallelism that can be achieved through build systems
-and testing frameworks.  In the following we elaborate relevant
-features of these components focusing on Java, Maven, and JUnit but
-the discussion can be generalized to other languages, build systems,
-and testing frameworks.
+Parallelism in test execution can be obtained at different levels.
+Figure~\ref{fig:levels} illustrates some of these levels.  This paper
+focuses at lower-level parallelism, obtained with parallel computation
+at cpus and threads in a given machine.  This kind of parallelism is
+enabled through build systems and testing frameworks.  Given the
+proliferation of multicore machines it is not surprising that testing
+frameworks provide today support for parallel test execution with the
+goal of running tests more efficiently~\cite{junit-org,testng,nunit}.
+Build systems wrap the features of these frameworks to facilitate the
+use of such technology\cite{maven-surefire-plugin}.  In the following
+we elaborate relevant features of these components focusing on Java,
+Maven, and JUnit but the discussion can be generalized to other
+languages, build systems, and testing frameworks.
+
+Note that lower-level parallelism is a complement to higher-level
+parallelism that could be enabled through server farms.  For the
+scenario of large IT organizations, lower-level parallelization
+schemes could leverage the computing power of server nodes in addition
+to the aggregate processing power of the farm.  Lower-level
+parallelism fits particularly well smaller organizations (/projects)
+with relatively high testing costs but lower budgets.
+\Comment{Unfortunately, these solutions can't be used out-of-the-box:
+  unrestricted parallel execution of tests can produce
+  non-deterministic results as developers typically do not provision
+  protection to concurrent accesses originated from arbitrary program
+  points (\ie{}, tests).  We refer to this problem as Parallel
+  Execution Flakiness (\pef{}).}
+
+%% These solutions enable the
+%% use of commodity hardware to maximize CPU usage\footnote{In the case
+%%   of the Java language, for example, it is possible to explore
+%%   parallelism across and within JVMs.}.
+
+\Comment{
+To illustrate the importance of parallel test execution and
+the problem of \pef{} let's consider the case of the ``core'' module
+from the Apache Camel project~\cite{apache-camel-web}.  This module
+contains 5,679 test cases, declared in 2,356 test classes.  We ran
+those tests in a machine with 16GB of memory and 8 virtual CPUs (4
+cores with 2 native threads each).  Sequential test execution takes
+24m50s to run this test set.  Execution of the same test set takes
+2m28s when we configured parallel execution to fork a JVM per CPU and
+execute test classes, uniquely allocated to that JVM, sequentially but
+running test methods from each class in separate threads.  Note that
+this is an order of magnitude speedup (10.07x)\Fix{Need to understand
+why this is 10x as opposed to something closer to 7x - I didn't get
+your concern here}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of
+5,679) of the tests fail when executed in parallel.  It is important
+to notice that the ratio of failures varies with the project as it
+depends on factors such as length of test cases and amount of shared
+state across tests.
+
+\pef{} is an important obstacle to enable parallel test execution.
+Conceptually, higher parallelization can result in higher chances of
+concurrency-related problems.  It is important to execute tests
+efficiently without sacrificing reliability
+\Fix{gap between pars?? What gap?}
+
+}
 
@@
 within each JVM.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figs/parallel-levels.pdf}
+  \caption{\label{fig:levels}Levels of parallelism.}
+\end{figure}
 

### 2016-11-03 paper/evaluation.tex
updated setup sec

@@
 each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
-(64-bit version). Our evaluation scripts depends on \Fix{specify:
-unix-based tools} to measure CPU usage and \emph{Python 3.4} (or
-later). For replication, we provide all the source artifacts publicly
-available at \Fix{create gh-pages}, including supporting scripts (\eg,
-the script that test subjects and generates the raw data), the full
-list of projects, and a \emph{Vagrantfile} to emulate our hardware and
-software setup and dependency settings .
+(64-bit version). Software settings include the Linux \emph{sysstat}
+package to measure performance, \emph{git} to fetch subjects,
+\emph{Java 8} to build and test subjects, and \emph{Python 3.4} to run
+our evaluation scripts. For replication, we provide all the source
+artifacts publicly available at \Fix{create gh-pages}, including
+supporting scripts (\eg, the script that test subjects and generates
+the raw data), the full list of projects, and a \emph{Vagrantfile} to
+emulate our hardware and all software dependencies properly configured.
 

### 2016-11-03 experiments/evaluation/thirdparty.sh
Added links about sysstat

@@ -14,4 +14,11 @@ cd "$THIRDPARTY_HOME"
 wget http://ftp.unicamp.br/pub/apache/maven/maven-3/3.3.9/binaries/apache-maven-3.3.9-bin.tar.gz
 wget http://mirror.nbtelecom.com.br/apache//ant/binaries/apache-ant-1.9.7-bin.tar.gz
 
-# TODO INSTALL MAVEN/ANT/JAVA
+# TODO INSTALL MAVEN/ANT/JAVA/etc.... SYSSTAT
+#
+# About sysstat:
+#   https://www.blackmoreops.com/2014/06/18/sysstat-sar-examples-usage/
+#   http://www.thegeekstuff.com/2014/11/pidstat-examples/
+#   http://www.cyberciti.biz/tips/identifying-linux-bottlenecks-sar-graphs-with-ksar.html#more-6165
+#   http://www.thegeekstuff.com/2011/03/sar-examples/?utm_source=feedburner
+

### 2016-11-03 paper/evaluation.tex
Updated explation about why we couldn't compile more subjs

@@
 Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
-    Search API imposes the limit of 1,000 results regardless of the
-number of matches from a search criteria.} Java projects with at
-least 100 stars. The number of stars indicates the interest and
-appreciation from the community to a given project.
+Search API imposes the limit of 1,000 results regardless of the number
+of matches from a search criteria.} Java projects with at least 100
+stars. The number of stars indicates the interest and appreciation
+from the community to a given project.
 \Comment{(https://help.github.com/articles/about-stars/)} Although our
@@
 801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
-and considered \Fix{154} projects that we were able to compile.
-\Fix{We noticed that we are unable to compile other subjects because of
-unsolved dependencies, other build systems are commonly related to a
-particular platform (\eg, Gradle implied Android), or the build
-process is based on user-defined tasks (\eg, Ant).}
+and considered 164 projects that we were able to compile (153 Maven
+and 9 Ant projects).  We were unable to compile other subjects because
+some are related to a particular platform (\eg, Gradle implied
+Android), unsolved dependencies, or the build process is based on
+user-defined tasks (\eg, we considered the name \emph{compile} on Ant
+projects).
 

### 2016-11-03 paper/evaluation.tex
pass on RQ1

@@
 Github\Jbc{Remember to update the previous sentence after updating the
-subject section}. We are interested in understanding the preva- lence
-of long test runs, the main source of cost, and how often developers
-explore parallelism to improve execution performance. We pose the
-following research questions:
+subject section}. We are interested in understanding the prevalence
+of long test runs, the main sources of cost, and how often developers
+explore parallelism to improve execution performance. More
+specifically, we pose the following research questions:
 
 \newcommand{\RQA}{How prevalent is the occurence of time-consuming
-regression tests in open-source projects?}
+regression test suites in open-source projects?}
+
 \newcommand{\RQB}{What is the distribution of CPU and IO bound
@@
 elapsed time to execute regression tests. We are interested on
-identifying time-consuming test suites for further investigation. The
+identifying time-consuming test suites \Jbc{do we have a better
+argument than this?}for further investigation. The
 second research question addresses the distribution of execution time
@@
 
-To evaluate the frequency of time-consuming regression tests, we first
-compiled source and test files, later, we measured the elapsed time to
-run the tests via the build system ignoring non-related tasks (\eg,
-\emph{javadoc} generation).  We grouped the subjects according to the
-execution time: tests that ran in less than one minute (\emph{short
-execution}), one to five minutes (\emph{medium execution}), and more
-than five minutes (\emph{long execution}).
-Figure~\ref{fig:piechart-time} shows the proportion of subjects per
-group. It is important to mention that Figure~\ref{fig:piechart-time}
-represents a lower bound for elapsed time: some tests may finish early
-due to a failure since the subjects were tested in a potentially
-unstable revision.
+To evaluate the frequency of time-consuming regression tests, we
+considered \Fix{X} Maven and \Fix{Y} Ant projects (\Fix{X+Y} total)
+that we were able to run the tests. For each subject, we first
+compiled the source and later, tested and collected the elapsed time
+reported from the build system using regular expressions. To avoid
+inflating the reported time, we run the tests ignoring non-related
+tasks (\eg, \emph{javadoc} generation). In case of \emph{Maven}
+projects, use \Jbc{How to show the following command?} \Fix{mvn test
+-Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant} projects, we
+used \Fix{ant test} and manually inspected the test execution to
+ignore any non-related tasks, if any.
+
+We grouped the subjects according to the execution time: tests that
+ran in less than one minute (\emph{short execution}), one to five
+minutes (\emph{medium execution}), and more than five minutes
+(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
+proportion of subjects per group. It is important to mention that
+Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
+time: some tests may finish early due to a failure since the subjects
+were tested in a potentially unstable revision. \Fix{Results indicate
+that a relatively high number of projects...}.
 

### 2016-11-03 paper/intro.tex
quick pass in text

@@
 Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
-computes which tests have been impacted by changes.  It analyzes, for
-each test, which file dependencies have been change impacted.
+computes which tests have been impacted by changes.  To that end
+Ekstazi analyzes, for each test, which test-dependent files have
+changed.
 
@@
 
-Motivated by this potential gap in regression testing practice, this
-paper studies (1) how prevalent long-running test suites are in
+Motivated by this potential gap in regression testing practice, we
+first studied (1) how prevalent long-running test suites are in
 open-source software projects.  To conduct this experiment we selected
@@
 suites (taking longer than 5m\Fix{check if Ekstazi paper also used
-  this value and cite} to complete) are not rare (\Fix{17\%} of the
-projects).  From this result we investigated (2) how frequently
-long-running test suites use parallelization.  Our results indicate
-that \Fix{80\%} of the long-running projects do use parallelization to
-speedup execution.  Given the popularity of this solution, we further
-studied: (3) what are the causes of high execution cost in individual
-tests (CPU vs. IO) and (4) how uniformly cost is distributed across
-tests.  These questions help to assess the impact of parallelization
-in each of these projects.  Intuitively, IO-intensive test suites and
-test suites with uneven distribution of cost per test are factors that
-limit the effects of parallelization.  Results indicate that \Fix{...}
-Finally, we investigated (5) what are the limitations related with
-parallelization that could justify adoption resistance.
+  this value and cite} to complete) are not rare~--~\Fix{17\%} of the
+projects we analyzed contain long-running test suites.  From this
+result we investigated (2) how frequently long-running test suites use
+parallelization\Mar{justify why parallelization}.  Our results
+indicate that \Fix{80\%} of the long-running test suites do use
+parallelization to speedup execution.  Given the popularity of this
+solution, we further studied: (3) what are the causes of high
+execution cost in individual tests (CPU vs. IO) and (4) how uniformly
+cost is distributed across tests.  These questions help to assess the
+impact of parallelization in each of these projects.  Intuitively,
+IO-intensive test suites and test suites with uneven distribution of
+cost per test are factors that limit the effects of parallelization.
+Results indicate that \Fix{...}  Finally, we investigated (5) what are
+the limitations related with parallelization that could justify
+adoption resistance.
 

### 2016-11-03 paper/modes.tex
quick pass in text

@@
-\section{Modes of Parallel Execution}
+\section{Parallel Execution of Test Suites}
 
-%%, potentially using commodity hardware
+\Mar{add a sentence to introduce this section at a higher abstraction
+  level.}  Parallelism in test execution can be obtained at different
+levels.  Figure~\ref{fig:levels} illustrates some of these levels.
 
-Parallelism in test execution can be obtained at different levels.
-Figure~\ref{fig:levels} illustrates some of these levels.  This paper
-focuses at lower-level parallelism, obtained with parallel computation
-at cpus and threads in a given machine.  This kind of parallelism is
-enabled through build systems and testing frameworks.  Given the
-proliferation of multicore machines it is not surprising that testing
-frameworks provide today support for parallel test execution with the
-goal of running tests more efficiently~\cite{junit-org,testng,nunit}.
-Build systems wrap the features of these frameworks to facilitate the
-use of such technology\cite{maven-surefire-plugin}.  In the following
-we elaborate relevant features of these components focusing on Java,
+This paper focuses at lower-level parallelism, obtained with parallel
+computation at cpus and threads in a given machine.  This kind of
+parallelism is enabled through build systems and testing frameworks.
+Given the proliferation of multicore machines it is not surprising
+that testing frameworks provide today support for parallel test
+execution with the goal of running tests more
+efficiently~\cite{junit-org,testng,nunit}.  Build systems wrap
+parallel features offered by testing frameworks to facilitate the use
+of such technology\cite{maven-surefire-plugin}.  In the following we
+elaborate relevant features of these components focusing on Java,
 Maven, and JUnit but the discussion can be generalized to other

### 2016-11-04 paper/evaluation.tex
pass on eval

@@
 regression tests from the sample set?}
-\newcommand{\RQC}{How the execution time is distributed among test
-cases?}
+
+\newcommand{\RQC}{How uniformly distributed is the execution time
+across test cases in costly projects?}
+
 \newcommand{\RQD}{How often developers use the parallelism features
@@
 The first research question addresses the distribution of subjects per
-elapsed time to execute regression tests. We are interested on
-identifying time-consuming test suites \Jbc{do we have a better
-argument than this?}for further investigation. The
-second research question addresses the distribution of execution time
-per test case for each project. The rationale is that if the time cost
+time cost. We are interested on identifying time-consuming test suites
+to investigate further their characteristics (\eg, type of application
+and bottlenecks from execution) \Jbc{do we have a better arguments?}.
+The second research question addresses the distribution of execution
+time per test case. For each subject identified in the first research
+question, we are interested in understanding how balanced is the cost
+of the test suite in contrast to the cost of test cases and if there
+are subjects where the time cost is mostly dominated by a small
+fraction of test cases.
+
+\Comment{The rationale is that if the time cost
 of a regression test is equally distributed among test cases, the
@@
 parallel (in contrast to the scenario where only one test case
-dominates most of the execution time).
+dominates most of the execution time).}
 
@@
 considered \Fix{X} Maven and \Fix{Y} Ant projects (\Fix{X+Y} total)
-that we were able to run the tests. For each subject, we first
-compiled the source and later, tested and collected the elapsed time
-reported from the build system using regular expressions. To avoid
-inflating the reported time, we run the tests ignoring non-related
-tasks (\eg, \emph{javadoc} generation). In case of \emph{Maven}
-projects, use \Jbc{How to show the following command?} \Fix{mvn test
--Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant} projects, we
-used \Fix{ant test} and manually inspected the test execution to
-ignore any non-related tasks, if any.
+that we were able to test. For each subject, we first compiled the
+source files and later, we ran the tests and used regular expressions
+to collect the elapsed time reported from the build system. To avoid
+inflating the time cost from test execution, we ignored non-related
+tasks (\eg, \emph{javadoc} generation). \Fix{elaborate: In case of
+\emph{Maven} projects, we use \Jbc{How to show the following command?}
+\Fix{mvn test -Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant}
+projects, we used \Fix{ant test} and manually inspected the test
+execution to ignore any non-related tasks, if any}.
 
@@
 time: some tests may finish early due to a failure since the subjects
-were tested in a potentially unstable revision. \Fix{Results indicate
-that a relatively high number of projects...}.
+were tested in a potentially unstable revision. Results indicate
+that a relatively high number of projects from the sample set requires
+at least five minutes to execute. The longest execution takes \Fix{x}
+to finish.
 
@@
 
-For the subjects from the groups \emph{medium} and \emph{long}, we
-compared the execution time and the number of tests successfully
-executed. As expected, Figure~\ref{fig:scatters} reveals that the
-number of tests cases are not related to the elapsed time.
-\Fix{explain briefly what dominates a test execution/types of tests}.
-We ignored outliers for better visualization.
+Considering the groups \emph{medium} and \emph{long}, we investigated
+the relation between number of tests cases and time cost from
+subjects.  \Fix{elaborate: As expected, Figure~\ref{fig:scatters}
+reveals that the number of tests cases are not related to the elapsed
+time.  \Fix{explain briefly what dominates a test execution/types of
+tests}.  We ignored outliers for better visualization.} Results
+indicate that \Fix{...conclusion...}.
 

### 2016-11-04 paper/intro.tex
quick pass on intro

@@
 smaller organizations with lower budgets for building testing
-infrastructures, this alternative may not be as attractive.
+infrastructures, this alternative is not as attractive.
 
+%% eventually move this to macros.tex
 \newcommand{\numSubjs}{143}
+\newcommand{\numLongRunning}{\Fix{17\%}}
+\newcommand{\percentParallelForLongRunning}{\Fix{80\%}}
 
@@
 the Maven build system.  (Section~\ref{sec:eval} details our selection
-criteria.)  Our experimental results indicate that long-running test
-suites (taking longer than 5m\Fix{check if Ekstazi paper also used
-  this value and cite} to complete) are not rare~--~\Fix{17\%} of the
-projects we analyzed contain long-running test suites.  From this
-result we investigated (2) how frequently long-running test suites use
-parallelization\Mar{justify why parallelization}.  Our results
-indicate that \Fix{80\%} of the long-running test suites do use
-parallelization to speedup execution.  Given the popularity of this
+methodology.)  Our experimental results indicate that long-running
+test suites (taking longer than 5m to complete\Fix{check if Ekstazi
+  paper also used this value and cite}) are not
+rare~--~\numLongRunning{} of the projects we analyzed contain
+long-running test suites.  From this result we investigated (2) how
+frequently the projects we considered use parallelization to speedup
+test runs.  We parsed build files of projects to identify usage of
+parallelism. \Mar{justify parallelization}.  Our results indicate that
+\percentParallelForLongRunning{} of long-running test suites do use
+parallelism to speedup execution.  Given the popularity of this
 solution, we further studied: (3) what are the causes of high
@@
 cost is distributed across tests.  These questions help to assess the
-impact of parallelization in each of these projects.  Intuitively,
+impact of parallelization in test suite execution.  Intuitively,
 IO-intensive test suites and test suites with uneven distribution of

### 2016-11-04 paper/evaluation.tex
Updated eval section

@@
 \newcommand{\RQB}{What is the distribution of CPU and IO bound
-regression tests from the sample set?}
+regression test suites from the sample set?}
 
@@
 \newcommand{\RQD}{How often developers use the parallelism features
-from build manager systems to improve performance on test execution?}
+from build systems to improve runtime performance?}
 
@@
 to investigate further their characteristics (\eg, type of application
-and bottlenecks from execution) \Jbc{do we have a better arguments?}.
-The second research question addresses the distribution of execution
-time per test case. For each subject identified in the first research
-question, we are interested in understanding how balanced is the cost
-of the test suite in contrast to the cost of test cases and if there
-are subjects where the time cost is mostly dominated by a small
-fraction of test cases.
+and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
+second research question addresses the distribution of execution time
+per test case. For each subject identified in the first research
+question, we investigate how balanced is the cost of the test suite in
+contrast to the cost of test cases and if there are subjects where the
+time cost is mostly dominated by a small fraction of test cases. The
+third research question addresses the distribution of regression tests
+according to the use of computational resources. We are interested in
+investigating if regression test suites are CPU intensive and if there
+are opportunities to improve performance. The RQ4 addresses
+\Fix{...elaborate...}
 
@@
 
-To evaluate the distribution of execution time, we calculated the cost
-from 90\% of test cases ordered by execution time and compared the
-resulting value to the total time.  We collected the elapsed time from
-test cases for each generated report. Maven Surefire generates an XML
-report with execution information (\eg, number of skipped tests and
-elapsed time) per test suite \Jbc{Should I use the previous sentence
-as a footnote or should I delete it?}. We noticed that some test cases
-reported an elapsed time of zero: since the reported time is in
-milliseconds, some tests may execute in a shorter time. \Fix{..to be
-continued...}
+To evaluate the distribution of execution time per project, we sorted
+the test cases by increasing order of elapsed time and calculated the
+number of tests executed in 90\% of the total time. Later, we reported
+the \Fix{balance} of execution time by dividing the number of tests
+that represents 90\% of the execution time by the number of tests
+cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
+collected the elapsed time from test cases for each generated report.
+Maven Surefire generates an XML report with execution information
+(\eg, number of skipped tests and elapsed time) per test suite
+\Jbc{Should I use the previous sentence as a footnote or should I
+delete it?}. We noticed that some test cases reported an elapsed time
+of zero: since the reported time is in milliseconds, some tests may
+execute in a shorter time. \Fix{..to be continued...}}. Results
+indicate that \Fix{...}.
 
@@
 
-To evaluate the distribution of CPU and IO bound in regression tests
-from the sample set, we proposed the definition of \emph{cpuness}
+To evaluate the distribution of CPU and IO intensive test suites from
+the sample set, we used the command \emph{sar} to monitor the system
+activity in background while tests ran. \emph{Sar} is a command that
+collects and reports statistics (\eg, percentage of IO waiting and
+usage of CPU in user mode) based on the kernel activity and it is
+highly configurable to collect detailed information (\eg, usage of a
+specific processor core or percentage of network interface
+utilization). We configured \emph{sar} to report \Fix{...explain how
+we executed and what fields we are interested}. \Fix{explain fields}.
+Figure \Fix{A} shows the distribution of subjects grouped in intervals
+of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}
+
+\Comment{we proposed the definition of \emph{cpuness}
 computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
@@
 the meaning of cpuness} \Fix{Describe how I measured user, system and
-"wall" time}.  \Fix{Explain results}.  \Fix{show plots}
+"wall" time}.  \Fix{Explain results}.  \Fix{show plots}}
 
@@
 
-%% \begin{itemize}
-%%     \item \RQFOUR
-%% \end{itemize}
+\begin{itemize}
+    \item \RQD
+\end{itemize}
 

### 2016-11-04 experiments/evaluation/main.py
updated output data

@@ -16,7 +16,7 @@ with open(INPUT_FILE, newline="") as f:
         if row["COMPILED"] == "true":
             subjects.append(row["SUBJECT"])
 
-print("subject,elapsed_t,tests,balance,cpu_usage")  # TODO define an output format
+print("subject,elapsed_t,tests,balance,cpu_usage,iowait,cpu_idle")  # TODO define an output format
 for subject in subjects:
     subject_path = os.path.join(SUBJECTS_HOME, subject)
     os.chdir(subject_path)
@@ -29,10 +29,10 @@ for subject in subjects:
         try:
             tests = report_data.statistics['tests']
             balance = utils.compute_time_distribution(report_data)
-            cpu_usage = utils.check_cpu_usage()
+            kernel_data = utils.check_resources_usage()
 
             # TODO define an output format
-            print(",".join([subject, str(t), str(tests), str(balance), str(cpu_usage)]))
+            print("{},{}".format(",".join([subject, str(t), str(tests), str(balance)]), ",".join(kernel_data)))
         except Exception as err:
             with open(os.path.join(BASE_DIR, "main-errors.txt"), "a") as log:
                 log.write("{} - {}\n".format(subject, err))

### 2016-11-04 experiments/evaluation/support/utils.py
Extracting kernel statistics from rawdata

@@ -81,7 +81,6 @@ def compute_time_distribution(data):
             break
         counter.update(Counter(tests=1, time=tc.time))
 
-    print(counter, threshold, data.statistics)
     return round((counter['tests'] / len(test_cases)) * 100, 2)
 
 
@@ -104,6 +103,11 @@ def check_test_reports(subject_path=os.curdir):
         return builder.test_report_inspector()
 
 
-def check_cpu_usage():
-    # TODO implement function to read data from 'performance.evaluate' output file and return %CPU
-    return 0
+def check_resources_usage(subject_path=os.curdir):
+    performance_log_path = os.path.join(subject_path, PERFORMANCE_LOG_TXT)
+    if os.path.exists(performance_log_path):
+        statistics_raw = check_output(["tail", "-n", "1", performance_log_path])
+        statistics = re.sub("\s+", " ", statistics_raw.decode().strip()).split(" ")
+        return [str(round(float(statistics[2]) + float(statistics[3]) + float(statistics[4]), 2)),
+                statistics[5], statistics[7]]
+    return []

### 2016-11-04 paper/evaluation.tex
reorganized par from rq1
fixed text to decrease order

@@
 (\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
-proportion of subjects per group. It is important to mention that
-Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
-time: some tests may finish early due to a failure since the subjects
-were tested in a potentially unstable revision. Results indicate
-that a relatively high number of projects from the sample set requires
-at least five minutes to execute. The longest execution takes \Fix{x}
-to finish.
+proportion of subjects per group.  Results indicate that a relatively
+high number of projects from the sample set requires at least five
+minutes to execute. The longest execution takes \Fix{x} to finish. It
+is important to mention that Figure~\ref{fig:piechart-time} represents
+a lower bound for elapsed time: some tests may finish early due to a
+failure since the subjects were tested in a potentially unstable
+revision.
 
@@
 To evaluate the distribution of execution time per project, we sorted
-the test cases by increasing order of elapsed time and calculated the
+the test cases by decreasing order of elapsed time and calculated the
 number of tests executed in 90\% of the total time. Later, we reported

### 2016-11-07 paper/results/barplot.r
added balance and cpuness barplots

@@ -1,0 +1,10 @@
+args <- commandArgs(trailingOnly = TRUE)
+
+out_name <- args[2]
+pdf(paste(out_name,".pdf",sep=""))
+
+name <- args[1]
+data <- read.csv(name, sep=",", header=T)
+
+barplot(table(data$label),
+        space=0)

### 2016-11-07 paper/results/gendata.py

@@ -1,0 +1,62 @@
+#!/usr/bin/python3
+import csv
+from sys import argv
+
+
+def gen_balance(row, fname):
+    balance = float(row["balance"])
+    intervals = [(0, 5, "0-5"),
+                 (5, 10, "5-10"),
+                 (10, 15, "10-15"),
+                 (15, 20, "15-20"),
+                 (20, 25, "20-25"),
+                 (25, 30, "25-30"),
+                 (30, 35, "30-35"),
+                 (35, 40, "35-40"),
+                 (40, 45, "40-45"),
+                 (45, 50, "45-40"),
+                 (50, 100, "50-100")]
+    for i in intervals:
+        if i[0] <= balance < i[1]:
+            with open(fname, "a") as f:
+                f.write(",".join([row["subject"], row["balance"], i[2]]))
+                f.write("\n")
+
+
+def gen_cpuness(row, fname):
+    cpu_usage = float(row["cpu_usage"])
+    intervals = [(0, 5, "0-5"),
+                 (5, 10, "5-10"),
+                 (10, 15, "10-15"),
+                 (15, 20, "15-20"),
+                 (20, 25, "20-25"),
+                 (25, 30, "25-30"),
+                 (30, 35, "30-35"),
+                 (35, 40, "35-40"),
+                 (40, 45, "40-45"),
+                 (45, 50, "45-40"),
+                 (50, 55, "50-55"),
+                 (55, 60, "55-60"),
+                 (60, 100, "60-100")]
+    for i in intervals:
+        if i[0] <= cpu_usage < i[1]:
+            with open(fname, "a") as f:
+                f.write(",".join([row["subject"], row["cpu_usage"], i[2]]))
+                f.write("\n")
+
+raw_data = argv[1]
+
+with open("balance.csv", "w") as f:
+    f.write(",".join(["subject", "balance", "label"]))
+    f.write("\n")
+with open("cpuness.csv", "w") as f:
+    f.write(",".join(["subject", "cpuness", "label"]))
+    f.write("\n")
+
+with open(raw_data, newline="") as data:
+    reader = csv.DictReader(data)
+    for row in reader:
+        if int(row["elapsed_t"]) >= 300:
+            gen_balance(row, "balance.csv")
+            gen_cpuness(row, "cpuness.csv")
+

### 2016-11-09 paper/evaluation.tex
added balance and cpuness barplots
wip - research question 2

--- 2016-11-04 paper/evaluation.tex
@@
 
-\newcommand{\RQB}{What is the distribution of CPU and IO bound
-regression tests from the sample set?}
+\newcommand{\RQB}{How often do developers use low-level parallelism
+to improve runtime performance?}
 
-\newcommand{\RQC}{How uniformly distributed is the execution time
-across test cases in costly projects?}
-
-\newcommand{\RQD}{How often developers use the parallelism features
-from build manager systems to improve performance on test execution?}
+%%\newcommand{\RQB}{What is the distribution of CPU and IO bound
+%%regression test suites from the sample set?}
+%%
+%%\newcommand{\RQC}{How uniformly distributed is the execution time
+%%across test cases in costly projects?}
+%%
+%%\newcommand{\RQD}{How often developers use the parallelism features
+%%from build systems to improve runtime performance?}
 
 \newcommand{\rqOne}{\textbf{RQ1.} \RQA}
-\newcommand{\rqTwo}{\textbf{RQ2.} \RQC}
-\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
-\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
+\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
+%%\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
+%%\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
 
@@
     \item \rqTwo
-    \item \rqThree
-    \item \rqFour
 \end{itemize}
@@
 to investigate further their characteristics (\eg, type of application
-and bottlenecks from execution) \Jbc{do we have a better arguments?}.
-The second research question addresses the distribution of execution
-time per test case. For each subject identified in the first research
-question, we are interested in understanding how balanced is the cost
-of the test suite in contrast to the cost of test cases and if there
-are subjects where the time cost is mostly dominated by a small
-fraction of test cases.
+and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
+second research question addresses our interest in understanding if
+developers are aware of parallelism features from testing frameworks
+available out-of-the-box through build systems (\eg, JUnit and TestNG
+with Maven Surefire) and what setting are often used.
+
+\Fix{distribution of execution
+    time per test case. For each subject identified in the first
+    research question, we investigate how balanced is the cost of the
+    test suite in contrast to the cost of test cases and if there are
+    subjects where the time cost is mostly dominated by a small
+fraction of test cases.} \Fix{The third research question addresses
+    the distribution of regression tests according to the use of
+    computational resources.  We are interested in investigating if
+regression test suites are CPU intensive and if there are
+opportunities to improve performance. The RQ4 addresses}
+\Fix{...elaborate...}
 
@@
 \begin{itemize}
-    \item \RQC
+    \item \RQB
 \end{itemize}
 
-To evaluate the distribution of execution time, we calculated the cost
-from 90\% of test cases ordered by execution time and compared the
-resulting value to the total time.  We collected the elapsed time from
-test cases for each generated report. Maven Surefire generates an XML
-report with execution information (\eg, number of skipped tests and
-elapsed time) per test suite \Jbc{Should I use the previous sentence
-as a footnote or should I delete it?}. We noticed that some test cases
-reported an elapsed time of zero: since the reported time is in
-milliseconds, some tests may execute in a shorter time. \Fix{..to be
-continued...}
+To evaluate how often developers use low-level parallelism, we
+considered 216 Maven projects and analyzed \Fix{x} configurations
+files. \Fix{For each subject, we parsed all \emph{pom.xml} files from the
+project (including submodules) and searched for all \emph{surefire}
+settings on each XML file. Figure \Fix{...} illustrates how a
+developer can explore parallelism via Surefire settings.}
+
+\begin{center}
+\lstset{language=XML}
+\begin{lstlisting}
+ <plugin>
+     <groupId>org.apache.maven.plugins</groupId>
+     <artifactId>maven-surefire-plugin</artifactId>
+     <configuration>
+         <parallel>methods</parallel>
+         <threadCount>2</threadCount>
+         <perCoreThreadCount>true</perCoreThreadCount>
+     </configuration>
+</plugin>
+\caption{\Fix{...}}
+\end{lstlisting}
+\label{code:surefire}
+\end{center}
 
@@
    \centering
-    \includegraphics[width=0.4\textwidth]{figs/tcdistrib.pdf}
+   \includegraphics[width=0.4\textwidth]{results/plots/parallelism-settings.pdf}
    \caption{\Fix{...}}
@@
 
-\subsection{Answering research question RQ3}
-\label{sec:rqThree}
+%%To evaluate the distribution of execution time per project, we sorted
+%%the test cases by decreasing order of elapsed time and calculated the
+%%number of tests executed in 90\% of the total time. Later, we reported
+%%the \Fix{balance} of execution time by dividing the number of tests
+%%that represents 90\% of the execution time by the number of tests
+%%cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
+%%collected the elapsed time from test cases for each generated report.
+%%Maven Surefire generates an XML report with execution information
+%%(\eg, number of skipped tests and elapsed time) per test suite
+%%\Jbc{Should I use the previous sentence as a footnote or should I
+%%delete it?}. We noticed that some test cases reported an elapsed time
+%%of zero: since the reported time is in milliseconds, some tests may
+%%execute in a shorter time. \Fix{..to be continued...}}. Results
+%%indicate that \Fix{...}.
+%%
+%%\begin{figure}[h!]
+%%    \centering
+%%    \includegraphics[width=0.4\textwidth]{results/plots/balance.pdf}
+%%    \caption{\Fix{balance}}
+%%\end{figure}
 
-\begin{itemize}
-    \item \RQB
-\end{itemize}
-
-To evaluate the distribution of CPU and IO bound in regression tests
-from the sample set, we proposed the definition of \emph{cpuness}
-computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
-where \emph{user\_t} is the elapsed time of execution in \emph{user
-mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
-\emph{elapsed\_t} is the elapsed time to finish the execution. We
-measured the \emph{cpuness} of each regression test \Fix{...elaborate
-the meaning of cpuness} \Fix{Describe how I measured user, system and
-"wall" time}.  \Fix{Explain results}.  \Fix{show plots}
-
-\subsection{Answering research question RQ4}
-\label{sec:rqfour}
-
+%% \subsection{Answering research question RQ3}
+%% \label{sec:rqThree}
+%% 
 %% \begin{itemize}
-%%     \item \RQFOUR
+%%     \item \RQB
 %% \end{itemize}
-
-\Fix{to appear...}
+%% 
+%% To evaluate the distribution of CPU and IO intensive test suites from
+%% the sample set, we used the command \emph{sar} to monitor the system
+%% activity in background while tests ran. \emph{Sar} is a command that
+%% collects and reports statistics (\eg, percentage of IO waiting and
+%% usage of CPU in user mode) based on the kernel activity and it is
+%% highly configurable to collect detailed information (\eg, usage of a
+%% specific processor core or percentage of network interface
+%% utilization). We configured \emph{sar} to report \Fix{...explain how
+%% we executed and what fields we are interested}. \Fix{explain fields}.
+%% Figure \Fix{A} shows the distribution of subjects grouped in intervals
+%% of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}
+%% 
+%% \begin{figure}[h!]
+%%     \centering
+%%     \includegraphics[width=0.4\textwidth]{results/plots/cpuness.pdf}
+%%     \caption{\Fix{cpu usage}}
+%% \end{figure}
+%% 
+%% \Comment{we proposed the definition of \emph{cpuness}
+%% computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
+%% where \emph{user\_t} is the elapsed time of execution in \emph{user
+%% mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
+%% \emph{elapsed\_t} is the elapsed time to finish the execution. We
+%% measured the \emph{cpuness} of each regression test \Fix{...elaborate
+%% the meaning of cpuness} \Fix{Describe how I measured user, system and
+%% "wall" time}.  \Fix{Explain results}.  \Fix{show plots}}
+%% 
+%% \subsection{Answering research question RQ4}
+%% \label{sec:rqfour}
+%% 
+%% \begin{itemize}
+%%     \item \RQD
+%% \end{itemize}
+%% 
+%% \Fix{to appear...}
+%%

### 2016-11-09 paper/results/parallelism-data.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python3
+import csv
+
+RAW_DATA = "parallel-settings-recursive.csv"
+
+data = []
+values = ["L1", "L2", "L3"]
+with open(RAW_DATA, newline="") as f:
+    reader = csv.DictReader(f)
+    for row in reader:
+        print(row)
+        for v in values:
+            for i in range(int(row[v])):
+                data.append(v)
+
+
+with open("parallelism-data.csv", "w") as f:
+    f.write("label\n")
+    for v in data:
+        f.write("%s\n" % v)
+

### 2016-11-10 paper/evaluation.tex
Updated RQs

@@
 
-\newcommand{\RQB}{How often do developers use low-level parallelism
-to improve runtime performance?}
+\newcommand{\RQB}{How often do developers use parallelism to improve
+runtime performance?}
+
+\newcommand{\RQC}{What is the impact of parallalelization?}
+
+\newcommand{\RQD}{What factors contribute to improve performance
+through parallelization?\Jbc{Previously as "When does parallelization
+works and when it does not so great?"}}
+
+\newcommand{\RQE}{What are the limitations of parallelization?}
+
+\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
+\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
+\newcommand{\rqThree}{\textbf{RQ3.} \RQC}
+\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
+\newcommand{\rqFive}{\textbf{RQ5.} \RQE}
+
+\begin{itemize}
+    \item \rqOne
+    \item \rqTwo
+    \item \rqThree
+    \item \rqFour
+    \item \rqFive
+\end{itemize}
 
@@
 
-\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
-\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
-%%\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
-%%\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
-
-\begin{itemize}
-    \item \rqOne
-    \item \rqTwo
-\end{itemize}
-
 The first research question addresses the distribution of subjects per
-time cost. We are interested on identifying time-consuming test suites
+time cost. We are interested in identifying time-consuming test suites
 to investigate further their characteristics (\eg, type of application
@@
 developers are aware of parallelism features from testing frameworks
-available out-of-the-box through build systems (\eg, JUnit and TestNG
-with Maven Surefire) and what setting are often used.
+available out-of-the-box through build systems (\eg, run JUnit test
+cases in parallel using Maven Surefire) and what setting are often
+used. The third research question addresses the impact of parallelism
+on the regression tests from our sample set. We are interested in
+compare the execution performance with different parallel settings
+(see Section~\ref{sec:modes}). The fourth research question addresses
+the characteristics of regression tests from the previous experiment.
+More specifically, we want to investigate if there is a relation
+between the balance of test execution (\ie, how uniformly distributed
+is the execution time across tests cases) and the usage of
+computational resources (\ie, if tests are mostly CPU or IO intense)
+that impacts the effectiveness of parallelization. Finally, the fifth
+research question discusses the limitations and insights to overcome
+the pitfalls of parallelization.
 
-\Fix{distribution of execution
-    time per test case. For each subject identified in the first
-    research question, we investigate how balanced is the cost of the
-    test suite in contrast to the cost of test cases and if there are
-    subjects where the time cost is mostly dominated by a small
-fraction of test cases.} \Fix{The third research question addresses
-    the distribution of regression tests according to the use of
-    computational resources.  We are interested in investigating if
-regression test suites are CPU intensive and if there are
-opportunities to improve performance. The RQ4 addresses}
+\Comment{
+    \Fix{distribution of execution time per test case. For each subject
+    identified in the first research question, we investigate how
+    balanced is the cost of the test suite in contrast to the cost of
+    test cases and if there are subjects where the time cost is mostly
+    dominated by a small fraction of test cases.} \Fix{The third research
+    question addresses the distribution of regression tests according
+    to the use of computational resources.  We are interested in
+    investigating if regression test suites are CPU intensive and if there
+    are opportunities to improve performance. The RQ4 addresses}
     \Fix{...elaborate...}
 
-\Comment{The rationale is that if the time cost
-of a regression test is equally distributed among test cases, the
-execution cost could be potentially improved by running tests in
-parallel (in contrast to the scenario where only one test case
-dominates most of the execution time).}
+    The rationale is that if the time cost of a regression test is equally
+    distributed among test cases, the execution cost could be potentially
+    improved by running tests in parallel (in contrast to the scenario
+    where only one test case dominates most of the execution time).
+}
 

### 2016-11-10 paper/modes.tex
Updated RQs
Updated parallel modes

@@
 \section{Parallel Execution of Test Suites}
+\label{sec:modes}
 
@@
 This paper focuses at lower-level parallelism, obtained with parallel
-computation at cpus and threads in a given machine.  This kind of
+computation at CPUs and threads in a given machine.  This kind of
 parallelism is enabled through build systems and testing frameworks.
@@
 with relatively high testing costs but lower budgets.
-\Comment{Unfortunately, these solutions can't be used out-of-the-box:
+\Comment{
+    Unfortunately, these solutions can't be used out-of-the-box:
     unrestricted parallel execution of tests can produce
@@
     points (\ie{}, tests).  We refer to this problem as Parallel
-  Execution Flakiness (\pef{}).}
+    Execution Flakiness (\pef{}).
 
@@
 
-\Comment{
     To illustrate the importance of parallel test execution and
@@
     \Fix{gap between pars?? What gap?}
-
 }
-
-\subsection{Build Systems}
-Build systems, such as Maven\footnote{\url{maven.apache.org}},
-typically provide the option to \emph{fork} JVM instances
-proportionally to available cores in the machine.  If the option
-``fork JVM'' is enabled, Maven will allocate a user-provided number of
-JVM instances to each core in the machine and will allocate each test
-class to exactly one JVM.  Note that there is no guarantee to
-uniformly distribute load to each JVM given that the build system uses
-classes as the unit to specify test tasks.\Fix{we need to know how
-  Maven allocates test classes to JVMs}
 
@@
 The list below shortly describes the choices to control parallelism
-within each JVM.
+within a JVM.
 
@@
 \item \textbf{Sequential (\Seq).}~This configuration results in
-  sequential execution of test classes and their methods, according to
-  the order defined in the testing framework\Fix{cite}.  For JUnit
-  this is the default configuration.
+    sequential execution of test classes and their methods, according
+    to a given order defined in the testing framework (\eg, the order
+    of methods returned by Java Reflection
+    API)~\cite{junit-test-order}. For JUnit, this is the default
+    configuration.
+
 \item \textbf{Sequential classes; parallel methods
@@
   execution of the test classes assigned to the JVM.  However, within
-  each class, test methods run in parallel.\Fix{are there options to
-    limit number of threads or a thread per test method?  Do they use
-    thread pools?  etc....}
+  each class, test methods run in parallel. In JUnit,
+  \emph{ParallelComputer} provides support to parallel execution; it
+  instantiates a test runner with a \emph{ExecutorService} from the
+  Java Concurrent API. Each test method is executed in a separated
+  thread as the thread pool creates new threads on-demand and reuse
+  them if any thread is available.
+
+\Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
+
 \item \textbf{Parallel classes; sequential methods
@@
   execution of test classes but test methods of any given class are
-  executed sequentially.\Fix{one thread per class?  if not, what
-    classes are scheduled to execute first?}
+  executed sequentially. As in \ParClassSeqMeth, the runner has a
+  cached thread poll. However, instead of executing test methods from
+  a single test class, the test suite runner executes classes in
+  separated threads and methods in sequence within each thread.
+
 \item \textbf{Parallel methods (\ParClassParMeth).} This configuration
   results in parallel execution of any given test method of any class.
+  \Jbc{I need to confirm this but AFAIK this is how it happens}
+  It is the union of \ParClassSeqMeth and \SeqClassParMeth: there is a
+  thread pool for execution classes on separated threads and within
+  each test class, there is a runner with a \emph{ExecutorService} to
+  run test methods in parallel.
 \end{itemize}
 
-\Fix{We need a par. providing rationale in to explain (points in favor/against) these choices.}
+\Jbc{I have to understand better how Surefire executes tests. I'm
+    afraid it has its own wrapper classes and reuse JUnit core
+    functionalities. I'm saying this because JUnit does not offer a
+    finer control over thread numbers while this configuration is
+possible with Surefire} For example, Figure~\ref{fig:surefire}
+illustrates how to configure Maven to execute classes sequentially
+(default behavior) and test methods in parallel. Although the setting
+are configured on the build file (\eg, \emph{pom.xml} on Maven}, these
+settings are forwarded to the underlying testing framework (\eg,
+JUnit). In case of JUnit,
+
+\begin{figure}[h!]
+    \centering
+    \lstset{language=XML}
+    \begin{lstlisting}
+    <plugin>
+        <groupId>org.apache.maven.plugins</groupId>
+        <artifactId>maven-surefire-plugin</artifactId>
+        <configuration>
+            <parallel>methods</parallel>
+            <threadCount>2</threadCount>
+            <perCoreThreadCount>true</perCoreThreadCount>
+        </configuration>
+    </plugin>
+    \end{lstlisting}
+    \caption{\label{fig:surefire}\Fix{...}}
+\end{figure}
+
+\Fix{We need a par. providing rationale in to explain (points in
+favor/against) these choices.}
+
+\subsection{Build Systems}
+Build systems, such as Maven\footnote{\url{maven.apache.org}},
+typically provide the option to \emph{fork} JVM instances
+proportionally to available cores in the machine.  If the option
+``fork JVM'' is enabled, Maven will allocate a user-provided number of
+JVM instances to each core in the machine and will allocate each test
+class to exactly one JVM.  Note that there is no guarantee to
+uniformly distribute load to each JVM given that the build system uses
+classes as the unit to specify test tasks.\Fix{we need to know how
+Maven allocates test classes to JVMs}

### 2016-11-10 paper/evaluation.tex
Updated parallel modes
fix compile/syntax Latex error

@@
 based on the files located in the root directory from the project in
-the following precedence: Maven (\emph{pom.xml)}, Gradle
+the following precedence: Maven (\emph{pom.xml}), Gradle
 (\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
@@
 
-\begin{center}
-\lstset{language=XML}
-\begin{lstlisting}
- <plugin>
-     <groupId>org.apache.maven.plugins</groupId>
-     <artifactId>maven-surefire-plugin</artifactId>
-     <configuration>
-         <parallel>methods</parallel>
-         <threadCount>2</threadCount>
-         <perCoreThreadCount>true</perCoreThreadCount>
-     </configuration>
-</plugin>
-\caption{\Fix{...}}
-\end{lstlisting}
-\label{code:surefire}
-\end{center}
-
 \begin{figure}[h!]

### 2016-11-10 paper/modes.tex
fix compile/syntax Latex error

@@
 (default behavior) and test methods in parallel. Although the setting
-are configured on the build file (\eg, \emph{pom.xml} on Maven}, these
+are configured on the build file (\eg, \emph{pom.xml} on Maven), these
 settings are forwarded to the underlying testing framework (\eg,

### 2016-11-14 paper/intro.tex
pass on intro; move text to related work

@@
 length of test runs increase.  Both elements can add up to the
-aggregate cost of running a test suite, which can lead to late reports of test
-failures.  At large IT companies (e.g.,
-Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
-common problem .  \Mar{Ask Milos if he can share stories on how
-  prevalent regression testing is at Microsoft and Google, if he can
-  explain how they run tests, and how prevalent is parallelization (in
-  contrast to regression testing).}
+aggregate cost of running a test suite, which can lead to late reports
+of test failures.  At large IT organizations, dealing with high
+testing costs is a common problem.  The Google TAP
+system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
+system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence about
+the importance of speeding up test execution in industry.  This
+problem is not specific for giants like Microsoft and Google; it also
+occur in other domains.  For example, a recent paper from the
+automotive industry reported that test suites can take days to
+run~\cite{artl-etal-icst2015}.
+
+%% papers also indicate the important of speeding up the testing process
+%% in other industrial domain, e.g., in 
+%% \Mar{Ask Milos if he can share stories on how prevalent regression
+%%   testing is at Microsoft and Google, if he can explain how they run
+%%   tests, and how prevalent is parallelization (in contrast to
+%%   regression testing).}
 
@@
 minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
-unsound (\ie{}, they do not guarantee that fault-revealing tests will
-be selected), however, more recently, sound techniques have been
-proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
-example, to soundly select tests for execution,
-Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
-computes which tests have been impacted by changes.  To that end
-Ekstazi analyzes, for each test, which test-dependent files have
-changed.
-
-%; these
-%dependencies are computed and maintained at low cost.
-
-Although regression testing is a recognized problem in academia and at
-large IT organizations, to the best of our knowledge no prior work has
-investigated how prevalent the problem is in open-source projects.
-For large IT organizations, the alternative of renting server farms,
-or even building one, is a potential escape to the regression testing
-problem.  However, for open-source projects and for projects of
-smaller organizations with lower budgets for building testing
-infrastructures, this alternative is not as attractive.
+selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
+a recognized problem in academia and at large organizations, to the
+best of our knowledge no prior work has investigated how prevalent the
+problem is in open-source projects.  In large organizations, the
+alternative of renting a cloud
+service\footnote{\url{https://clutch.co/cloud}}, or even building a
+server farm (for increased security), is a potential escape to the
+regression testing problem.  Considering open-source projects and
+lower-budget projects, the alternative of building or using high-end
+infrastructures is not as attractive but it is unclear how relevant
+regression testing is in this scenario.
 
@@
 
-Motivated by this potential gap in regression testing practice, we
-first studied (1) how prevalent long-running test suites are in
-open-source software projects.  To conduct this experiment we selected
-\numSubjs{} Java projects from github that are highly-popular and use
-the Maven build system.  (Section~\ref{sec:eval} details our selection
-methodology.)  Our experimental results indicate that long-running
-test suites (taking longer than 5m to complete\Fix{check if Ekstazi
-  paper also used this value and cite}) are not
+Motivated by this potential gap in regression testing, we studied (1)
+how prevalent long-running test suites are in open-source software
+projects.  To conduct this experiment we selected \numSubjs{} Java
+projects from github that are highly-popular and use the Maven build
+system.  (Section~\ref{sec:eval} details our selection methodology.)
+Our experimental results indicate that long-running test suites
+(taking longer than 5m to complete\Fix{check if Ekstazi paper also
+  used this value to indicate long runs and cite}) are not
 rare~--~\numLongRunning{} of the projects we analyzed contain
-long-running test suites.  From this result we investigated (2) how
-frequently the projects we considered use parallelization to speedup
-test runs.  We parsed build files of projects to identify usage of
-parallelism. \Mar{justify parallelization}.  Our results indicate that
-\percentParallelForLongRunning{} of long-running test suites do use
-parallelism to speedup execution.  Given the popularity of this
-solution, we further studied: (3) what are the causes of high
+long-running test suites.  \Mar{missing connection. why parallelism?}
+From this result we investigated (2) how frequently the projects we
+considered use parallelization to speedup test runs.  Our results
+indicate that \percentParallelForLongRunning{} of long-running test
+suites do use parallelism to speedup execution.  Given the popularity
+of this solution, we further studied: (3) what are the causes of high
 execution cost in individual tests (CPU vs. IO) and (4) how uniformly
@@
 IO-intensive test suites and test suites with uneven distribution of
-cost per test are factors that limit the effects of parallelization.
+cost per test are factors that limit the benefits of parallelization.
 Results indicate that \Fix{...}  Finally, we investigated (5) what are
-the limitations related with parallelization that could justify
-adoption resistance.
+the limitations related to parallelization that could justify adoption
+resistance.
 
@@
 %%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
-%%  LocalWords:  Ekstazi github
+%%  LocalWords:  Ekstazi github CloudBuild

### 2016-11-14 paper/related.tex
pass on intro; move text to related work

\section{Related Work}
\label{sec:related}

\Fix{elaborate...}

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that fault-revealing tests will
be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
computes which tests have been impacted by changes.  A test is
discarded for execution if it does not depend on any changed file.
Similar approach to regression test selection has been recently
applied in the context of the GCC~\cite{gcc} configurable
system~\cite{souto-damorim-jss}.

### 2016-11-15 paper/intro.tex
pass on intro

@@
 system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
-system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence about
-the importance of speeding up test execution in industry.  This
-problem is not specific for giants like Microsoft and Google; it also
-occur in other domains.  For example, a recent paper from the
-automotive industry reported that test suites can take days to
-run~\cite{artl-etal-icst2015}.
+system~\cite{prasad-shulte-ieee-microsoft-ci} evidence the importance
+of speeding up test execution in industry.  This problem, however, is
+not specific to industrial giants like Microsoft and Google.  For
+example, a recent paper from the automotive industry reported that
+test suites can take days to run~\cite{artl-etal-icst2015}.
 
@@
 selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
-a recognized problem in academia and at large organizations, to the
-best of our knowledge no prior work has investigated how prevalent the
-problem is in open-source projects.  In large organizations, the
-alternative of renting a cloud
+a recognized problem both in industry and academia, to the best of our
+knowledge no prior work has investigated how prevalent the problem is
+in open-source projects.  Renting a cloud
 service\footnote{\url{https://clutch.co/cloud}}, or even building a
-server farm (for increased security), is a potential escape to the
-regression testing problem.  Considering open-source projects and
-lower-budget projects, the alternative of building or using high-end
-infrastructures is not as attractive but it is unclear how relevant
-regression testing is in this scenario.
+server farm (for increased security), is a popular approach to
+mitigate the regression testing problem in large organizations.  This
+alternative can be used irrespective of complementary approaches to
+save testing costs (e.g., test selection).  For example, as of August
+2013, the Groupon PWA system, which powers the \url{groupon.com}
+website, included over 19K tests.  To run all those tests, Groupon
+used a cluster of 4 computers with 24 cores
+each~\cite{kim-etal-fse2013}.  This approach, however, is unlikely to
+be attractive for open-source and lower-budget projects.
 
@@
 
-Motivated by this potential gap in regression testing, we studied (1)
-how prevalent long-running test suites are in open-source software
+%Motivated by this potential gap in regression testing,
+
+This paper focuses on the problem of understanding how critical the
+regression testing problem is in open-source projects and what are the
+potential benefits and shortcomings of using the parallelization
+features of build systems and testing frameworks, which are very
+popular today\Fix{cite cite cite}.  More precisely, we studied (1) how
+prevalent long-running test suites are in open-source software
 projects.  To conduct this experiment we selected \numSubjs{} Java
@@
 %%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
-%%  LocalWords:  Ekstazi github CloudBuild
+%%  LocalWords:  Ekstazi github CloudBuild PWA groupon

### 2016-11-15 paper/intro.tex
another pass on intro

@@
 As software evolves it is expected that the number of tests and the
-length of test runs increase.  Both elements can add up to the
+length of test runs increase.  Both components can add up to the
 aggregate cost of running a test suite, which can lead to late reports
-of test failures.  At large IT organizations, dealing with high
-testing costs is a common problem.  The Google TAP
+of test failures.  Dealing with high testing costs is not uncommon at
+large IT organizations.  The Google TAP
 system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
-system~\cite{prasad-shulte-ieee-microsoft-ci} evidence the importance
-of speeding up test execution in industry.  This problem, however, is
-not specific to industrial giants like Microsoft and Google.  For
-example, a recent paper from the automotive industry reported that
-test suites can take days to run~\cite{artl-etal-icst2015}.
+system~\cite{prasad-shulte-ieee-microsoft-ci} show that efficiently
+building and testing the software are a critically important process
+at Google and Microsoft.  The regression testing problem is, however,
+not specific to industrial giants.  For example, a recent paper from
+the automotive industry reported that test suites can take days to
+run~\cite{artl-etal-icst2015}.
 
@@
 a recognized problem both in industry and academia, to the best of our
-knowledge no prior work has investigated how prevalent the problem is
-in open-source projects.  Renting a cloud
-service\footnote{\url{https://clutch.co/cloud}}, or even building a
-server farm (for increased security), is a popular approach to
-mitigate the regression testing problem in large organizations.  This
-alternative can be used irrespective of complementary approaches to
-save testing costs (e.g., test selection).  For example, as of August
-2013, the Groupon PWA system, which powers the \url{groupon.com}
-website, included over 19K tests.  To run all those tests, Groupon
-used a cluster of 4 computers with 24 cores
-each~\cite{kim-etal-fse2013}.  This approach, however, is unlikely to
-be attractive for open-source and lower-budget projects.
+knowledge no prior work has investigated the regression testing
+problem in open-source projects.  The alternative of renting a cloud
+service\footnote{\url{https://clutch.co/cloud}} to automate testing or
+even building a server farm (for increased security), can be a
+legitimate approach to mitigate the regression testing problem at
+large organizations.  Note that this alternative can be used
+irrespective of complementary approaches to save testing costs (e.g.,
+test selection).  For example, as of August 2013, the Groupon PWA
+system, which powers the \url{groupon.com} website, included over 19K
+tests.  To run all those tests under 10m, Groupon used a cluster of 4
+computers with 24 cores each~\cite{kim-etal-fse2013}.  For open-source
+projects and lower-budget projects, it is still important to run test
+suites efficiently in commodity hardware.
 

### 2016-11-16 paper/intro.tex
pass in intro

@@
 aggregate cost of running a test suite, which can lead to late reports
-of test failures.  Dealing with high testing costs is not uncommon at
-large IT organizations.  The Google TAP
-system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
-system~\cite{prasad-shulte-ieee-microsoft-ci} show that efficiently
-building and testing the software are a critically important process
-at Google and Microsoft.  The regression testing problem is, however,
-not specific to industrial giants.  For example, a recent paper from
-the automotive industry reported that test suites can take days to
-run~\cite{artl-etal-icst2015}.
+of test failures.  Dealing with high testing costs is particularly
+critical at large IT organizations, with massive code and test bases.
+The Google TAP system~\cite{google-tap,google-ci} and the Microsoft
+CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci} provide
+evidence on the criticality of the build and testing processes at
+these organizations.  Note, however, that the regression testing
+problem is not specific to giants from the IT sector.  For example, a
+recent paper from the automotive industry reported that test suites
+can take days to run~\cite{artl-etal-icst2015}.
 
@@
 tests.  To run all those tests under 10m, Groupon used a cluster of 4
-computers with 24 cores each~\cite{kim-etal-fse2013}.  For open-source
-projects and lower-budget projects, it is still important to run test
-suites efficiently in commodity hardware.
+computers with 24 cores each~\cite{kim-etal-fse2013}.  This paper
+assumes that, especially considering open-source projects and
+lower-budget projects, running test suites efficiently using commodity
+hardware is important.
 

### 2016-11-16 paper/modes.tex
Added Fix tag about parallel settings with Maven

@@
 afraid it has its own wrapper classes and reuse JUnit core
-    functionalities. I'm saying this because JUnit does not offer a
-    finer control over thread numbers while this configuration is
-possible with Surefire} For example, Figure~\ref{fig:surefire}
-illustrates how to configure Maven to execute classes sequentially
-(default behavior) and test methods in parallel. Although the setting
-are configured on the build file (\eg, \emph{pom.xml} on Maven), these
-settings are forwarded to the underlying testing framework (\eg,
-JUnit). In case of JUnit,
+functionalities. I'm saying this because JUnit does not offer a finer
+control over thread numbers while this configuration is possible with
+Surefire} For example, Figure~\ref{fig:surefire} illustrates how to
+configure Maven to execute classes sequentially (default behavior) and
+test methods in parallel. Although this configuration is defined in
+the build file (\eg, \emph{pom.xml} on Maven), \Fix{these settings are
+forwarded to the underlying testing framework (\eg, JUnit). In case of
+JUnit,}
 

### 2016-11-16 paper/evaluation.tex
work in progress - fixes and updates on RQ1

@@
 the following precedence: Maven (\emph{pom.xml}), Gradle
-(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
-the following values after updating the subject selection approach.}
-From the 1,000 downloaded projects, we detected the build system of
-801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
-and considered 164 projects that we were able to compile (153 Maven
-and 9 Ant projects).  We were unable to compile other subjects because
-some are related to a particular platform (\eg, Gradle implied
-Android), unsolved dependencies, or the build process is based on
-user-defined tasks (\eg, we considered the name \emph{compile} on Ant
-projects).
+(\emph{*.gradle} file), and Ant (\emph{build.xml}).\Jbc{Remember to
+update the following values after updating the subject selection
+approach.} From the 1,000 downloaded projects, we detected the build
+system of \Fix{801} subjects (composed by 216 Maven, \Fix{564} Gradle,
+and 21 Ant projects) and considered \Fix{164} Maven projects that we
+were able to compile and test.  We were unable to compile other
+subjects because some of them are related to a particular platform
+(\eg, Gradle implied Android), has unsolved dependencies (\eg, package
+no longer available from the Maven public repository), or the build
+process is based on user-defined tasks (\eg, Ant projects).
 
@@
 \begin{itemize}
-    \item \RQA
+    \item \emph{\RQA}
 \end{itemize}
@@
 To evaluate the frequency of time-consuming regression tests, we
-considered \Fix{X} Maven and \Fix{Y} Ant projects (\Fix{X+Y} total)
-that we were able to test. For each subject, we first compiled the
-source files and later, we ran the tests and used regular expressions
-to collect the elapsed time reported from the build system. To avoid
-inflating the time cost from test execution, we ignored non-related
-tasks (\eg, \emph{javadoc} generation). \Fix{elaborate: In case of
-\emph{Maven} projects, we use \Jbc{How to show the following command?}
-\Fix{mvn test -Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant}
-projects, we used \Fix{ant test} and manually inspected the test
-execution to ignore any non-related tasks, if any}.
+considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
+and compared the elapsed time to run their tests.  To avoid inflating
+the measured time, we first compile the sources files (see
+Figure~\ref{fig:mvn-execution}, line 1) and later (see
+Figure~\ref{fig:mvn-execution}, line 2), we ran the tests ignoring
+non-related tasks (\eg, \emph{javadoc} generation). In addition, when
+we run a subject's test suite, we operate Maven in offline mode to
+limit the network access, avoiding any unnecessary package update as
+all required \emph{jars} are available locally. After the test
+execution, we use a simple regular expression over the builder output
+to extract the elapsed time.
+
+\begin{figure}[h!]
+\centering
+\scriptsize
+\lstset{
+    escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
+    deletekeywords={true}
+}
+\begin{lstlisting}
+mvn clean install -DskipTests -Dmaven.javadoc.skip=true
+mvn -o test -Dmaven.javadoc.skip=true
+\end{lstlisting}
+\caption{\label{fig:mvn-execution} Compiling and testing a Maven
+    subject: line 1 compiles all subject's source artifacts and make
+    them available in a local repository (\ie, directory \emph{.m2} in
+    the user's home directory); line 2 runs the tests in offline mode
+    ignoring javadoc generation.}
+\end{figure}
 
@@
 proportion of subjects per group.  Results indicate that a relatively
-high number of projects from the sample set requires at least five
-minutes to execute. The longest execution takes \Fix{x} to finish. It
-is important to mention that Figure~\ref{fig:piechart-time} represents
-a lower bound for elapsed time: some tests may finish early due to a
-failure since the subjects were tested in a potentially unstable
-revision.
+high number of projects from the sample set (\ie, 17\%) requires at
+least five minutes to execute. The longest execution takes \Fix{x} to
+finish. It is important to mention that Figure~\ref{fig:piechart-time}
+represents a lower bound for elapsed time: some tests may finish early
+due to a failure since the subjects were tested in a potentially
+unstable revision.
 

### 2016-11-16 paper/intro.tex
pass on intro

@@
 aggregate cost of running a test suite, which can lead to late reports
-of test failures.  Dealing with high testing costs is particularly
-critical at large IT organizations, with massive code and test bases.
-The Google TAP system~\cite{google-tap,google-ci} and the Microsoft
+of test failures.  Dealing with high testing costs is critical at
+large IT organizations, with massive code and test bases.  The impact
+of the Google TAP system~\cite{google-tap,google-ci} and the Microsoft
 CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci} provide
@@
 can take days to run~\cite{artl-etal-icst2015}.
+
+Several approaches have been proposed in the literature to address the
+regression testing problem.  Research has focused mostly on test suite
+minimization, prioritization, reduction, and
+selection~\cite{yoo-harman-stvr2012}.  It is important to note,
+however, that balancing the workload, either within or across
+machines, is a popular and sound approach to address cost associated
+with regression testing.  Furtheremore, this approach is complementary
+to those proposed in the literature.
 
@@
 
-Several approaches have been proposed in the literature to optimize
-regression testing.  Research has focused mostly on test suite
-minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
-a recognized problem both in industry and academia, to the best of our
-knowledge no prior work has investigated the regression testing
-problem in open-source projects.  The alternative of renting a cloud
-service\footnote{\url{https://clutch.co/cloud}} to automate testing or
-even building a server farm (for increased security), can be a
-legitimate approach to mitigate the regression testing problem at
-large organizations.  Note that this alternative can be used
-irrespective of complementary approaches to save testing costs (e.g.,
-test selection).  For example, as of August 2013, the Groupon PWA
-system, which powers the \url{groupon.com} website, included over 19K
-tests.  To run all those tests under 10m, Groupon used a cluster of 4
-computers with 24 cores each~\cite{kim-etal-fse2013}.  This paper
-assumes that, especially considering open-source projects and
-lower-budget projects, running test suites efficiently using commodity
-hardware is important.
+Although regression testing is a recognized problem both in industry
+and academia, to the best of our knowledge no prior work has
+investigated the regression testing problem in open-source projects.
+The alternative of renting a cloud
+service\footnote{\url{https://clutch.co/cloud}} or even building a
+server farm (for increased security) to automate the testing process
+may be a legitimate approach to mitigate the regression testing
+problem at large organizations.  However, building such infrastructure
+may not be feasibile for open-source and low-budget projects.  For
+example, as of August 2013, the Groupon PWA system, which powers the
+\url{groupon.com} website, included over 19K tests.  To run all those
+tests under 10m, Groupon used a cluster of 4 computers with 24 cores
+each~\cite{kim-etal-fse2013}.  This paper assumes that, given that it
+is not rare for open-source projects to face high testing costs, it is
+important to run test suites efficiently using commodity hardware.
 

### 2016-11-16 paper/evaluation.tex
added content from sequential execution

@@
 limit the network access, avoiding any unnecessary package update as
-all required \emph{jars} are available locally. After the test
-execution, we use a simple regular expression over the builder output
-to extract the elapsed time.
+all required \emph{jars} are available locally. We also considered the
+execution of all subjects enforcing sequential execution to avoid
+having the real time cost masked by the use of any parallel setting
+mentioned in Section~\ref{sec:modes}.  After the test execution, we
+use a simple regular expression over the builder output to extract the
+elapsed time.
 
@@
     ignoring javadoc generation.}
+\vspace{-3ex}
 \end{figure}
@@
 (\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
-proportion of subjects per group.  Results indicate that a relatively
-high number of projects from the sample set (\ie, 17\%) requires at
-least five minutes to execute. The longest execution takes \Fix{x} to
-finish. It is important to mention that Figure~\ref{fig:piechart-time}
-represents a lower bound for elapsed time: some tests may finish early
-due to a failure since the subjects were tested in a potentially
-unstable revision.
+proportion of subjects per group: on the left side, the pie chart
+reports the results enforcing sequential execution; on the right side,
+the results for the default execution.  Results indicate that a
+relatively high number of projects from the sample set (\ie, 17\%)
+requires at least five minutes to execute. The longest execution takes
+\Fix{x} to finish. It is important to mention that
+Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
+time: some tests may finish early due to a failure since the subjects
+were tested in a potentially unstable revision.
 
@@
     time on test execution ($t$): short execution ($t < 1m$), medium 
-    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).}
+    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).
+    \Fix{On the left side, results from sequential execution; the right side,
+    results from default execution.}}
 \end{figure}

### 2016-11-16 paper/modes.tex
updated listing and some descriptions about par modes

@@
 \begin{itemize}
-\item \textbf{Sequential (\Seq).}~This configuration results in
-    sequential execution of test classes and their methods, according
-    to a given order defined in the testing framework (\eg, the order
-    of methods returned by Java Reflection
+\item
+    \textbf{Sequential (\Seq).}~This configuration results in
+        sequential execution of test classes and their methods,
+        according to a given order defined in the testing framework
+        (\eg, the order of methods returned by Java Reflection
         API)~\cite{junit-test-order}. For JUnit, this is the default
         configuration.
-
-\item \textbf{Sequential classes; parallel methods
-  (\ParClassSeqMeth{}).} This configuration results in the sequential
-  execution of the test classes assigned to the JVM.  However, within
-  each class, test methods run in parallel. In JUnit,
-  \emph{ParallelComputer} provides support to parallel execution; it
-  instantiates a test runner with a \emph{ExecutorService} from the
-  Java Concurrent API. Each test method is executed in a separated
-  thread as the thread pool creates new threads on-demand and reuse
-  them if any thread is available.
-
+\item
+    \textbf{Sequential classes; parallel methods
+        (\ParClassSeqMeth{}).}~This configuration results in the
+        sequential execution of the test classes assigned to the JVM.
+        However, within each class, test methods run in parallel. In
+        JUnit, \emph{ParallelComputer} provides support to parallel
+        execution: it instantiates a test runner with an
+        \emph{ExecutorService} from the Java Concurrent API. Each test
+        method is executed in a separated thread as the thread pool
+        creates new threads on-demand and reuse them if any thread is
+        available.
     \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
-
-\item \textbf{Parallel classes; sequential methods
-  (\SeqClassParMeth{}).}  This configuration results in the parallel
-  execution of test classes but test methods of any given class are
-  executed sequentially. As in \ParClassSeqMeth, the runner has a
-  cached thread poll. However, instead of executing test methods from
-  a single test class, the test suite runner executes classes in
-  separated threads and methods in sequence within each thread.
-
-\item \textbf{Parallel methods (\ParClassParMeth).} This configuration
-  results in parallel execution of any given test method of any class.
-  \Jbc{I need to confirm this but AFAIK this is how it happens}
-  It is the union of \ParClassSeqMeth and \SeqClassParMeth: there is a
-  thread pool for execution classes on separated threads and within
-  each test class, there is a runner with a \emph{ExecutorService} to
-  run test methods in parallel.
+\item
+    \textbf{Parallel classes; sequential methods
+        (\SeqClassParMeth{}).}~This configuration results in the
+        parallel execution of test classes and sequential test
+        methods. As in \ParClassSeqMeth, the test runner has a cached
+        thread poll but instead of executing test methods from a
+        single test class, the test suite runner executes classes in
+        separated threads and methods sequentially within each thread.
+\item
+    \textbf{Parallel methods (\ParClassParMeth).}~This configuration
+        results in the parallel execution of any test method from any
+        class.  \Jbc{I need to confirm this but AFAIK this is how it
+        happens} As in \SeqClassParMeth, classes execute on separated
+        threads but test methods are also executed in parallel. More
+        precisely, there is a thread pool to execute classes in
+        separated threads (\ie, like in \ParClassSeqMeth) and, within
+        each class runner, there is an \emph{ExecutorService} to run
+        test methods in parallel (\ie, like in \SeqClassParMeth).
 \end{itemize}
@@
 \centering
-    \lstset{language=XML}
+\scriptsize
+\lstset{
+    escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+    morekeywords={parallel, threadCount, perCoreThreadCount},
+    deletekeywords={true}
+}
 \begin{lstlisting}
@@
 \end{lstlisting}
-    \caption{\label{fig:surefire}\Fix{...}}
+\caption{\label{fig:surefire} Example of Maven Surefire configuration:
+    test methods in parallel (\emph{parallel} parameter) using two
+    threads (\emph{threadCount} parameter) per core (boolean flag
+    \emph{perCoreThreadCount}).}
 \end{figure}

### 2016-11-16 paper/intro.tex
minor change in intro

@@
 service\footnote{\url{https://clutch.co/cloud}} or even building a
-server farm (for increased security) to automate the testing process
-may be a legitimate approach to mitigate the regression testing
-problem at large organizations.  However, building such infrastructure
-may not be feasibile for open-source and low-budget projects.  For
+server farm (for increased security) may be a legitimate approach to
+mitigate the regression testing problem at large organizations.  For
 example, as of August 2013, the Groupon PWA system, which powers the
@@
 tests under 10m, Groupon used a cluster of 4 computers with 24 cores
-each~\cite{kim-etal-fse2013}.  This paper assumes that, given that it
-is not rare for open-source projects to face high testing costs, it is
-important to run test suites efficiently using commodity hardware.
+each~\cite{kim-etal-fse2013}.  Given that it is not rare for
+open-source projects to face high testing costs, this paper assumes
+that it is not economically viable for these projects to build
+high-end testing infrastructure.  Consequently, it is important to run
+test suites efficiently using commodity hardware in these scenarios.
 

### 2016-11-17 paper/evaluation.tex
fixes

@@
     ignoring javadoc generation.}
-\vspace{-3ex}
 \end{figure}
@@
     execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).
-    \Fix{On the left side, results from sequential execution; the right side,
-    results from default execution.}}
+    \Fix{On the left side, results from sequential execution; on the
+    right side, results from default execution.}}
 \end{figure}
 
-Considering the groups \emph{medium} and \emph{long}, we investigated
-the relation between number of tests cases and time cost from
-subjects.  \Fix{elaborate: As expected, Figure~\ref{fig:scatters}
-reveals that the number of tests cases are not related to the elapsed
-time.  \Fix{explain briefly what dominates a test execution/types of
-tests}.  We ignored outliers for better visualization.} Results
-indicate that \Fix{...conclusion...}.
+Considering the groups \emph{medium} and \emph{long} (\Fix{X}
+subjects), we investigated the relationship between the number of
+tests cases and the time cost from subjects.  Figure~\ref{fig:scatter}
+shows two scatter plots with We created a scatter plot for each group
+and computed the correlation of time cost and number of tests.
+\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that
+the number of tests cases are not related to the elapsed time.
+\Fix{explain briefly what dominates a test execution/types of tests}.
+We ignored outliers for better visualization.} Results indicate that
+\Fix{...conclusion...}.
 

### 2016-11-17 paper/evaluation.tex
fixed piecharts and updated plots

@@
     \centering
-    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
-    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
-    time on test execution ($t$): short execution ($t < 1m$), medium 
-    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).
-    \Fix{On the left side, results from sequential execution; on the
-    right side, results from default execution.}}
+    \includegraphics[width=0.48\textwidth]{results/plots/piechart-timecost.pdf}
+    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
+    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
+    5m$), and long execution ($5m \leq t$).  On the left side, results from
+    sequential execution; on the right side, results from default execution.}
 \end{figure}
@@
 subjects), we investigated the relationship between the number of
-tests cases and the time cost from subjects.  Figure~\ref{fig:scatter}
+tests cases and the time cost from subjects.  Figure~\ref{fig:scatters}
 shows two scatter plots with We created a scatter plot for each group
@@
     \centering
-    \begin{minipage}{0.5\textwidth}
-        \subfigure[\Fix{medium}]{
-            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-med.pdf}
-        }\\
-        \subfigure[\Fix{long}]{
-            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-long.pdf}
-        }%
-    \end{minipage}%
+    \Fix{scatter top, scatter bottom, legend r-value regression}
     \caption{\Fix{...use minutes instead of secs...}}%
@@
 \begin{itemize}
-    \item \RQB
+    \item \emph{\RQB}
 \end{itemize}
@@
    \centering
-   \includegraphics[width=0.4\textwidth]{results/plots/parallelism-settings.pdf}
    \caption{\Fix{...}}

### 2016-11-17 paper/results/piechart-timecost.r

@@ -1,0 +1,28 @@
+args <- commandArgs(trailingOnly = TRUE)
+
+out_name <- args[2]
+out_path <- paste(out_name,".pdf",sep="")
+pdf(out_path, height=3.5, width=5)
+
+name <- args[1]
+data <- read.csv(name, sep=",", header=T)
+
+dist <- as.data.frame(table(data$group))
+colors <- c("gray30", "gray50", "gray90")
+
+par(mfrow=c(1,3), mar=c(1,1,1,1), oma=c(0,0,0,0), xpd=T)
+
+sequential_t <- dist$Freq
+pct <- round(sequential_t / sum(sequential_t) * 100)
+lbls <- paste(pct, "%", sep="")
+pie(sequential_t, radius=0.8, labels=lbls, col=colors)
+
+default_t <- dist$Freq
+pct <- round(default_t / sum(default_t) * 100)
+lbls <- paste(pct, "%", sep="")
+pie(default_t, radius=0.8, labels=lbls, col=colors)
+
+plot.new()
+legend_lbls <- names(table(dist$Var1))
+legend("topleft", inset=c(0, 0.35), legend_lbls, fill=colors)
+

### 2016-11-17 paper/results/updateall.sh

@@ -1,17 +1,17 @@
 #!/bin/bash
 BASEDIR=$(pwd)
-for d in $(ls .); do
-    if [ -f "$d/main.sh" ]; then
-        cd $d
-        ./main.sh
-        cd $BASEDIR
-    fi
-done
+#for d in $(ls .); do
+#    if [ -f "$d/main.sh" ]; then
+#        cd $d
+#        ./main.sh
+#        cd $BASEDIR
+#    fi
+#done
 
 # TODO: Move pdfcrop calls to R scripts so I can use
 #       different margins
 #
 # Crop blank spaces
-for PDF in $(find . -name *.pdf); do
+for PDF in $(find plots/ -name *.pdf); do
     pdfcrop $PDF $PDF
 done;

### 2016-11-17 paper/evaluation.tex
added reminder about piechart
wip - correlation from scatter plots

@@
     execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
-    5m$), and long execution ($5m \leq t$).  On the left side, results from
-    sequential execution; on the right side, results from default execution.}
+    5m$), and long execution ($5m \leq t$).  \Fix{On the left side, results from
+    sequential execution}; on the right side, results from default execution.}
 \end{figure}
 
-Considering the groups \emph{medium} and \emph{long} (\Fix{X}
-subjects), we investigated the relationship between the number of
-tests cases and the time cost from subjects.  Figure~\ref{fig:scatters}
-shows two scatter plots with We created a scatter plot for each group
-and computed the correlation of time cost and number of tests.
-\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that
-the number of tests cases are not related to the elapsed time.
-\Fix{explain briefly what dominates a test execution/types of tests}.
-We ignored outliers for better visualization.} Results indicate that
+Considering the groups \emph{medium} and \emph{long} (\Fix{X} subjects), we
+investigated the relationship between the number of tests cases and the time
+cost from subjects. \Fix{Explain what is correlation and how it is computed.}
+\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that the number
+of tests cases are not related to the elapsed time.  \Fix{explain briefly what
+dominates a test execution/types of tests}.Results indicate that
 \Fix{...conclusion...}.

### 2016-11-17 paper/intro.tex
another pass on intro

@@
 CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci} provide
-evidence on the criticality of the build and testing processes at
+evidence on the criticality of the build and the testing processes at
 these organizations.  Note, however, that the regression testing
@@
 selection~\cite{yoo-harman-stvr2012}.  It is important to note,
-however, that balancing the workload, either within or across
-machines, is a popular and sound approach to address cost associated
-with regression testing.  Furtheremore, this approach is complementary
-to those proposed in the literature.
+however, that balancing the test workload, either within or across
+machines, is a popular, sound, and practical approach to address
+testing cost and can't be neglected.  Furtheremore, this approach is
+complementary to those proposed in the literature. For example, as of
+August 2013, the Groupon PWA system, which powers the
+\url{groupon.com} website, included over 19K tests.  To run all those
+tests under 10m, Groupon used a cluster of 4 computers with 24 cores
+each~\cite{kim-etal-fse2013}.  As additional examples, The Google TAP
+system and the Microsoft CloudBuild system distribute the test
+workload in the cloud, which is part of their infrastructure.  Note,
+that the alternative of renting a cloud
+service\footnote{\url{https://clutch.co/cloud}} or even building a
+server farm (for increased security) can be a legitimate approach to
+mitigate the regression testing problem at large organizations.
+However, this solution may not be economically viable for smaller
+projects.
 
@@
 
-Although regression testing is a recognized problem both in industry
-and academia, to the best of our knowledge no prior work has
-investigated the regression testing problem in open-source projects.
-The alternative of renting a cloud
-service\footnote{\url{https://clutch.co/cloud}} or even building a
-server farm (for increased security) may be a legitimate approach to
-mitigate the regression testing problem at large organizations.  For
-example, as of August 2013, the Groupon PWA system, which powers the
-\url{groupon.com} website, included over 19K tests.  To run all those
-tests under 10m, Groupon used a cluster of 4 computers with 24 cores
-each~\cite{kim-etal-fse2013}.  Given that it is not rare for
-open-source projects to face high testing costs, this paper assumes
-that it is not economically viable for these projects to build
-high-end testing infrastructure.  Consequently, it is important to run
-test suites efficiently using commodity hardware in these scenarios.
+This paper focuses on optimizing regression testing of open-source
+projects using commodity hardware.  This is an important problem
+assuming that it is not rare for open-source projects to face high
+testing costs.  \Fix{mention similar but different work} To the best
+of our knowledge no prior work investigated this problem.
+
+---- aqui
 

### 2016-11-17 paper/intro.tex
minor changes to intro

@@
 of test failures.  Dealing with high testing costs is critical at
-large IT organizations, with massive code and test bases.  The impact
-of the Google TAP system~\cite{google-tap,google-ci} and the Microsoft
-CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci} provide
-evidence on the criticality of the build and the testing processes at
-these organizations.  Note, however, that the regression testing
-problem is not specific to giants from the IT sector.  For example, a
-recent paper from the automotive industry reported that test suites
-can take days to run~\cite{artl-etal-icst2015}.
+large IT organizations, with massive code and test bases.  The Google
+TAP system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
+system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence on the
+criticality of the build and the testing processes at these
+organizations.  Note, however, that the regression testing problem is
+not specific to giants from the IT sector.  For example, a recent
+paper from the automotive industry reported that test suites can take
+days to run~\cite{artl-etal-icst2015}.
 
@@
 tests under 10m, Groupon used a cluster of 4 computers with 24 cores
-each~\cite{kim-etal-fse2013}.  As additional examples, The Google TAP
-system and the Microsoft CloudBuild system distribute the test
-workload in the cloud, which is part of their infrastructure.  Note,
-that the alternative of renting a cloud
+each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
+and Microsoft's CloudBuild distribute task workloads in the cloud.
+Note, that the alternative of renting a cloud
 service\footnote{\url{https://clutch.co/cloud}} or even building a
-server farm (for increased security) can be a legitimate approach to
+server farm (for increased security) is a legitimate approach to
 mitigate the regression testing problem at large organizations.

### 2016-11-17 experiments/evaluation/main.py
Bug fixes and support to multiple profiles

@@ -2,14 +2,80 @@
 import argparse
 import csv
 import os
+from subprocess import call, DEVNULL, PIPE, Popen
 
-from support import performance, utils
+import re
+
+from support import maven
 
 BASE_DIR = os.path.abspath(os.curdir)
 SUBJECTS_HOME = os.path.join(BASE_DIR, "subjects")
 
 
+def measure_test_cost(override=False):
+    # RQ1
+    call(maven.resolve_dependencies_task(), stdout=DEVNULL, stderr=DEVNULL)
+    test_log_default = "test-log-default.txt"
+    test_log_sequential = "test-log-sequential.txt"
+    if not os.path.exists(test_log_default) or override:
+        with open(test_log_default, "w") as log_file:
+            call(maven.test_task("-o", "-Dmaven.javadoc.skip=true"),
+                 stdout=log_file, stderr=DEVNULL)
+    if not os.path.exists(test_log_sequential) or override:
+        with open(test_log_sequential, "w") as log_file:
+            call(maven.test_task("-o", "-Dmaven.javadoc.skip=true", "-P", "tests-seq"),
+                 stdout=log_file, stderr=DEVNULL)
+    timestamps = {test_log_default: None, test_log_sequential: None}
+    for log in timestamps.keys():
+        cat = Popen(["cat", log], stdout=PIPE)
+        grep = Popen(["grep", "Total time:"], stdin=cat.stdout, stdout=PIPE)
+        cat.stdout.close()
+        out, err = grep.communicate()
+
+        # normalize reported time
+        reported_time = re.sub(r".*: ", "", out.decode().replace("s", "").strip())
+        if "min" in reported_time:
+            reported_time = reported_time.replace("min", "").split(":")
+            reported_time = (60 * int(reported_time[0])) + int(reported_time[1])
+            # FIXME test subjects with reported time > 60min
+
+        timestamps[log] = round(float(reported_time))
+
+    return timestamps
+
+
+def experiment(subject_path, override=False):
+    """
+    Runs the experiment for a Maven subject from the given path
+    :param subject_path: the path to the subject
+    :param override: flag indicating whether existing data should be overridden
+    :return: None
+    """
+    subject_name = os.path.basename(subject_path)
+    if not os.path.exists(subject_path):
+        print("Missing subject \"{}\". Skipping...".format(subject_name))
+        return
+
+    if not maven.is_valid_project(subject_path):
+        print("Subject \"{}\" is not a Maven project. Skipping...".format(subject_name))
[…]

### 2016-11-17 experiments/evaluation/support/maven.py

@@ -1,0 +1,32 @@
+import os
+
+
+def build_task(*additional_args):
+    args = ["mvn", "clean", "install"]
+    if additional_args:
+        args.extend(additional_args)
+    return args
+
+
+def test_task(*additional_args):
+    args = ["mvn", "test"]
+    if additional_args:
+        args.extend(additional_args)
+    return args
+
+
+def resolve_dependencies_task():
+    """
+    Task arguments to ensure dependencies are resolved before running in offline mode
+    :return: List of arguments to run in a system call
+    """
+    return ["mvn", "dependency:go-offline"]
+
+
+def is_valid_project(subject_path):
+    """
+    Checks if the informed path is a valid Maven project
+    :param subject_path: the path to verify
+    :return: true if the informed path contains a pom.xml file (false otherwise).
+    """
+    return os.path.exists(os.path.join(subject_path, "pom.xml"))

### 2016-11-17 paper/evaluation.tex
fixed latex error - missing enclosing }
Updated description of maven commands

@@
 package to measure performance, \emph{git} to fetch subjects,
-\emph{Java 8} to build and test subjects, and \emph{Python 3.4} to run
-our evaluation scripts. For replication, we provide all the source
-artifacts publicly available at \Fix{create gh-pages}, including
-supporting scripts (\eg, the script that test subjects and generates
-the raw data), the full list of projects, and a \emph{Vagrantfile} to
-emulate our hardware and all software dependencies properly configured.
+\emph{Java 8} and \emph{Maven 3} to build and test subjects, and
+\emph{Python 3.4} to run our evaluation scripts. For replication, we
+provide all the source artifacts publicly available at \Fix{create
+gh-pages}, including supporting scripts (\eg, the script that test
+subjects and generates the raw data), the full list of projects, and a
+\emph{Vagrantfile} to emulate our hardware and all software
+dependencies properly configured.
 
@@
 considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
-and compared the elapsed time to run their tests.  To avoid inflating
-the measured time, we first compile the sources files (see
-Figure~\ref{fig:mvn-execution}, line 1) and later (see
-Figure~\ref{fig:mvn-execution}, line 2), we ran the tests ignoring
-non-related tasks (\eg, \emph{javadoc} generation). In addition, when
-we run a subject's test suite, we operate Maven in offline mode to
-limit the network access, avoiding any unnecessary package update as
-all required \emph{jars} are available locally. We also considered the
-execution of all subjects enforcing sequential execution to avoid
-having the real time cost masked by the use of any parallel setting
-mentioned in Section~\ref{sec:modes}.  After the test execution, we
-use a simple regular expression over the builder output to extract the
-elapsed time.
+and compared the elapsed time to run their tests.
+Figure~\ref{fig:mvn-execution} illustrates the commands used in our
+scripts to test each subject.  To avoid inflating the measured time,
+we first compile the sources files (line 1) and later, we ran the
+tests ignoring non-related tasks (line 3).  In addition, when we run a
+subject's test suite, we operate Maven in offline mode to limit the
+network access, avoiding any unnecessary package update as all
+required \emph{jars} are available locally (line 2). We also
+considered the execution of all subjects enforcing sequential
+execution to avoid having the real time cost masked by the use of any
+parallel setting mentioned in Section~\ref{sec:modes} (line 4).  After
+the test execution, we use a simple regular expression over the
+builder output to extract the elapsed time.
 
@@
     basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
+    morekeywords={o, DskipTests, Dmaven, javadoc, skip, go, offline, P},
     deletekeywords={true}
@@
 mvn clean install -DskipTests -Dmaven.javadoc.skip=true
+mvn dependency:go-offline
 mvn -o test -Dmaven.javadoc.skip=true
+mvn -o test -Dmaven.javadoc.skip=true -P tests-seq
 \end{lstlisting}
-\caption{\label{fig:mvn-execution} Compiling and testing a Maven
-    subject: line 1 compiles all subject's source artifacts and make
-    them available in a local repository (\ie, directory \emph{.m2} in
-    the user's home directory); line 2 runs the tests in offline mode
-    ignoring javadoc generation.}
+\caption{\label{fig:mvn-execution} Maven commands to test a subject:
+    line 1 compiles all subject's source artifacts and make them
+    available in a local repository (\ie, directory \emph{.m2} in the
+    user's home directory); line 2 ensures all dependencies are
+    resolved; line 3 runs the tests in offline mode ignoring javadoc
+    generation; line 4 runs the tests using our \emph{tests-seq}
+    profile to ensure sequential execution.}
 \end{figure}
@@
 dominates a test execution/types of tests}.Results indicate that
-\Fix{...conclusion...}.
+\Fix{...conclusion...}.}
 

### 2016-11-21 paper/intro.tex
minor changes

@@
 machines, is a popular, sound, and practical approach to address
-testing cost and can't be neglected.  Furtheremore, this approach is
+testing cost and can't be neglected.  Furthermore, this approach is
 complementary to those proposed in the literature. For example, as of
@@
 However, this solution may not be economically viable for smaller
-projects.
+projects with heavy testing loads.
 
@@
 %%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
-%%  LocalWords:  Ekstazi github CloudBuild PWA groupon
+%%  LocalWords:  Ekstazi github CloudBuild PWA groupon criticality

### 2016-11-23 experiments/evaluation/data/Main.R
computing elapsed time in hours

@@ -96,4 +96,5 @@ rawdata <- read.csv(name)
 rq1_timecost(rawdata, "plots/piechart-timecost.pdf")
 rq1_tests_time(rawdata, "plots/scatter-tests-time.pdf")
 
-print(paste("Experiment cost:", sum(rawdata$elapsed_time), "s"))
+print(paste("Experiment cost:",
+            round(sum(rawdata$elapsed_time)) / 3600, "hr"))

### 2016-11-24 paper/intro.tex
minor changes

@@
 and Microsoft's CloudBuild distribute task workloads in the cloud.
-Note, that the alternative of renting a cloud
+The alternative of renting a cloud
 service\footnote{\url{https://clutch.co/cloud}} or even building a
 server farm (for increased security) is a legitimate approach to
-mitigate the regression testing problem at large organizations.
-However, this solution may not be economically viable for smaller
-projects with heavy testing loads.
+mitigate the regression testing problem at large organizations.  This
+paper assumes, however, that this solution is not economically viable
+for smaller projects with heavy testing loads.
 

### 2016-12-10 paper/evaluation.tex
Updated plots with existing data
Updated subject section

@@
 subject section}. We are interested in understanding the prevalence
-of long test runs, the main sources of cost, and how often developers
+of long test runs, the main sources of cost, and how do developers
 explore parallelism to improve execution performance. More
@@
 
-\newcommand{\RQB}{How often do developers use parallelism to improve
-runtime performance?}
+\newcommand{\RQB}{\Fix{How often do developers use parallelism to improve
+runtime performance?}}
 
@@
 to investigate further their characteristics (\eg, type of application
-and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
-second research question addresses our interest in understanding if
-developers are aware of parallelism features from testing frameworks
-available out-of-the-box through build systems (\eg, run JUnit test
-cases in parallel using Maven Surefire) and what setting are often
-used. The third research question addresses the impact of parallelism
-on the regression tests from our sample set. We are interested in
-compare the execution performance with different parallel settings
-(see Section~\ref{sec:modes}). The fourth research question addresses
-the characteristics of regression tests from the previous experiment.
+and bottlenecks from execution).  The second research question
+addresses our interest in understanding if developers are aware of
+parallelism features from testing frameworks available out-of-the-box
+through build systems (\eg, run JUnit test cases in parallel using
+Maven Surefire) and what setting are often used. The third research
+question addresses the impact of parallelism on the regression tests
+from our sample set. We are interested in compare the execution
+performance with different parallel settings (see
+Section~\ref{sec:modes}). The fourth research question addresses the
+characteristics of regression tests from the previous experiment.
 More specifically, we want to investigate if there is a relation
@@
 
-\Jbc{Subject selection is currently OK but I will use another way (eg
-Google BigQuery) to have access to more subjects.}We used the Github's
-Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
-Search API imposes the limit of 1,000 results regardless of the number
-of matches from a search criteria.} Java projects with at least 100
-stars. The number of stars indicates the interest and appreciation
-from the community to a given project.
+We used the Github's Search API~\cite{githubsearch} to fetch Java
+projects based on Maven according to the following criteria: primary
+language must be Java\footnote{In case of projects in multiple
+languages, the Github API considers the predominant language as the
+primary language.}; project with at least 100 stars; latest update on
+(or after) January 1st, 2016; contains the string \emph{mvn} in the
+\emph{README} file.  The number of stars indicates the interest and
+appreciation from the community to a given project.
 \Comment{(https://help.github.com/articles/about-stars/)} Although our
 criteria is subjective, it is an approximation to find relevant
-projects to conduct our study. We detected the build manager system
-based on the files located in the root directory from the project in
-the following precedence: Maven (\emph{pom.xml}), Gradle
-(\emph{*.gradle} file), and Ant (\emph{build.xml}).\Jbc{Remember to
-update the following values after updating the subject selection
-approach.} From the 1,000 downloaded projects, we detected the build
-system of \Fix{801} subjects (composed by 216 Maven, \Fix{564} Gradle,
-and 21 Ant projects) and considered \Fix{164} Maven projects that we
-were able to compile and test. We were unable to compile other
-subjects because some of them are related to a particular platform
-(\eg, Gradle implied Android), has unsolved dependencies (\eg, package
-no longer available from the Maven public repository), or the build
-process is based on user-defined tasks (\eg, Ant projects).
+projects to conduct our study.  Figure~\ref{fig:subject-query}
+illustrates the query.
+
+\begin{figure}[h!]
+\centering
+\scriptsize
+\lstset{
+    escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+    morekeywords={stars,language,pushed,in},
+    deletekeywords={true}
+}
+\begin{lstlisting}
+https://api.github.com/search/repositories?q=
+    stars:>=100+language:java+mvn%20in:readme+
+    pushed:>=2016-01-01+sort:stars&page=1&per_page=100
+
+\end{lstlisting}
+\caption{\label{fig:subject-query} Query to the Github API for
+    projects in Java with at least 100 stars, updated on January 1st,
+    2016 (or later), and contains the string \emph{mvn} in the
+    \emph{README} file.}
+\end{figure}
+
+As in December 12th, 2016, our search criteria returned 589 subjects.
+From the 589 downloaded projects, we considered 312 projects that we
+were able to compile and test. The others 277 could not be considered
+because 39 were not Maven projects, 26 could not fetch all required
+dependencies, 125 could not be compiled, and 87 could not execute the
+tests. In addition, we first attempted to consider Gradle and Ant
+projects but most of Gradle projects were related to Android apps and
+libraries and adding support to Ant would require to parse the
+\emph{build.xml} to identify the compilation and test commands since
+the build process is based on user-defined tasks.
 
@@
     \centering
-    \includegraphics[width=0.48\textwidth]{results/plots/piechart-timecost.pdf}
+    \includegraphics[width=0.48\textwidth]{plots/piechart-timecost.pdf}
     \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
@@
     \centering
-    \Fix{scatter top, scatter bottom, legend r-value regression}
+    \Comment{scatter top, scatter bottom, legend r-value regression}
     \caption{\Fix{...use minutes instead of secs...}}%

### 2016-12-10 paper/evaluation.tex
updating rq1

@@
 To evaluate the frequency of time-consuming regression tests, we
-considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
-and compared the elapsed time to run their tests.
+considered the 321 subjects from Section~\ref{sec:subjects} and
+compared the elapsed time to run their tests.
 Figure~\ref{fig:mvn-execution} illustrates the commands used in our
@@
 network access, avoiding any unnecessary package update as all
-required \emph{jars} are available locally (line 2). We also
-considered the execution of all subjects enforcing sequential
-execution to avoid having the real time cost masked by the use of any
-parallel setting mentioned in Section~\ref{sec:modes} (line 4).  After
-the test execution, we use a simple regular expression over the
-builder output to extract the elapsed time.
+required \emph{jars} are available locally (line 2).  After the test
+execution, we use a simple regular expression over the builder output
+to extract the elapsed time.
 
@@
 mvn -o test -Dmaven.javadoc.skip=true
-mvn -o test -Dmaven.javadoc.skip=true -P tests-seq
 \end{lstlisting}
@@
     resolved; line 3 runs the tests in offline mode ignoring javadoc
-    generation; line 4 runs the tests using our \emph{tests-seq}
-    profile to ensure sequential execution.}
+    generation.}
 \end{figure}

### 2016-12-10 experiments/evaluation/analytics/Helper.R
adjusted plots

@@ -25,10 +25,10 @@ piechart_timecost <- function(df) {
     })
   )
   # bring pie title down
-  title(main = "Distribution of Subject Groups", line = -3)
+  # title(main = "Distribution of Subject Groups", line = -3)
   legend(
     "topright",
-    inset = c(0, 0.2),
+    inset = c(0, 0.3),
     c("Long", "Medium", "Short"),
     fill = cols
   )
@@ -50,7 +50,7 @@ table(ds$group)
 
 # BOX PLOTS - TIMECOST
 output_name <- paste(output_dir, "boxplots-timecost.pdf", sep="/")
-pdf(output_name, height = 3.5, width = 4)
+pdf(output_name, height = 3, width = 4)
 par(mfrow = c(1, 3),
     mar = c(5, 5, 0, 0),
     las = 1)

### 2016-12-10 paper/evaluation.tex
updated rq1

@@
 We evaluated the characteristics of regression tests in open-source
-development from a sample set of Java projects from
-Github\Jbc{Remember to update the previous sentence after updating the
-subject section}. We are interested in understanding the prevalence
-of long test runs, the main sources of cost, and how do developers
-explore parallelism to improve execution performance. More
-specifically, we pose the following research questions:
+development from a sample set of Java projects from Github. We are
+interested in understanding the prevalence of long test runs, the main
+sources of cost, and how do developers explore parallelism to improve
+execution performance. More specifically, we pose the following
+research questions:
 
@@
 (\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
-proportion of subjects per group: on the left side, the pie chart
-reports the results enforcing sequential execution; on the right side,
-the results for the default execution.  Results indicate that a
-relatively high number of projects from the sample set (\ie, 17\%)
-requires at least five minutes to execute. The longest execution takes
-\Fix{x} to finish. It is important to mention that
+proportion of subjects per group and Figure~\ref{fig:boxplots-time}
+shows the distribution of elapsed time for each group (boxplots).
+
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{2in}%
+    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
+    \end{minipage}%
+    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
+    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
+    5m$), and long execution ($5m \leq t$).}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{2.5in}%
+    \includegraphics[width=\textwidth]{plots/boxplots-timecost.pdf}
+    \end{minipage}%
+    \caption{\label{fig:boxplots-time} Distribution of time execution
+    per group. Outliers from \emph{Long} are ignored for better
+    readability.}
+\end{figure}
+
+Results indicate that a relatively high number of projects from the
+sample set (\ie, 29,2\%) requires at least five minutes to execute.
+The boxplot for the \emph{long} group reveals \Fix{dissect the
+boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
+group}.  It is important to mention that
 Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
@@
 were tested in a potentially unstable revision.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.48\textwidth]{plots/piechart-timecost.pdf}
-    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
-    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
-    5m$), and long execution ($5m \leq t$).  \Fix{On the left side, results from
-    sequential execution}; on the right side, results from default execution.}
-\end{figure}
-
-Considering the groups \emph{medium} and \emph{long} (\Fix{X} subjects), we
-investigated the relationship between the number of tests cases and the time
-cost from subjects. \Fix{Explain what is correlation and how it is computed.}
-\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that the number
-of tests cases are not related to the elapsed time.  \Fix{explain briefly what
-dominates a test execution/types of tests}.Results indicate that
-\Fix{...conclusion...}.}
-
-\begin{figure}[h!]%
-    \centering
-    \Comment{scatter top, scatter bottom, legend r-value regression}
-    \caption{\Fix{...use minutes instead of secs...}}%
-    \label{fig:scatters}%
-\end{figure}
 
@@
 
-To evaluate how often developers use low-level parallelism, we
+\Fix{To evaluate how often developers use low-level parallelism, we
 considered 216 Maven projects and analyzed \Fix{x} configurations
-files. \Fix{For each subject, we parsed all \emph{pom.xml} files from the
+files. For each subject, we parsed all \emph{pom.xml} files from the
 project (including submodules) and searched for all \emph{surefire}
@@
 developer can explore parallelism via Surefire settings.}
-
-\begin{figure}[h!]
-   \centering
-   \caption{\Fix{...}}
-\end{figure}
 

### 2016-12-12 paper/evaluation.tex
text from RQ2

@@
 
-\Fix{To evaluate how often developers use low-level parallelism, we
-considered 216 Maven projects and analyzed \Fix{x} configurations
-files. For each subject, we parsed all \emph{pom.xml} files from the
-project (including submodules) and searched for all \emph{surefire}
-settings on each XML file. Figure \Fix{...} illustrates how a
-developer can explore parallelism via Surefire settings.}
+To evaluate the  use of low-level parallelism, we considered the
+subjects from the groups \emph{long} and \emph{medium} identified in
+Section~\ref{sec:rqone}. In an initial exploration, we searched for
+evidences of low-level parallelism settings on configuration files
+(\ie, \emph{pom.xml}) from each subject (\emph{long} and \emph{medium}
+groups). Initially, our script finds recursively all \emph{pom.xml}
+files from the project directory. For each file, we use the
+command-line tool \emph{grep} to highlight the presence of the
+keywords \emph{forkMode}, \emph{forkCount}, and \emph{parallel}. Any
+of these keywords are present in all possible parallel settings (see
+Section~\ref{sec:modes}).  We discovered that \Fix{X}\% and \Fix{y}\%
+of subjects (\emph{long} and \emph{medium}, respectively) did not have
+any evidence of low-level parallelism. It is important to mention that
+this result an upper bound limit since the keyword highlighted could
+not be part of a real configuration (\eg, part of a comment). To
+investigate further the projects reported by our script, we manually
+inspected \Fix{X} configuration files to eliminate false-positives.
+\Fix{...elaborate...}
 

### 2016-12-13 paper/evaluation.tex
Updating rq2

--- 2016-12-10 paper/evaluation.tex
@@
 To evaluate the frequency of time-consuming regression tests, we
-considered the 321 subjects from Section~\ref{sec:subjects} and
+considered the 312 subjects from Section~\ref{sec:subjects} and
 compared the elapsed time to run their tests.
@@
 
-\Fix{To evaluate how often developers use low-level parallelism, we
-considered 216 Maven projects and analyzed \Fix{x} configurations
-files. For each subject, we parsed all \emph{pom.xml} files from the
-project (including submodules) and searched for all \emph{surefire}
-settings on each XML file. Figure \Fix{...} illustrates how a
-developer can explore parallelism via Surefire settings.}
+To evaluate the  use of low-level parallelism, we considered the 91
+subjects from the groups \emph{long} and \emph{medium} identified in
+Section~\ref{sec:rqone}. In an initial exploration, we searched for
+evidences of low-level parallelism settings on configuration files
+(\ie, \emph{pom.xml}) from each subject using a semi-automated
+approach: we use a script to find all subjects with evidences of
+parallel settings and then we manually inspect each configuration file
+to eliminate false-positives. Given a list of subjects, our script
+searches recursively all \emph{pom.xml} files from the project
+directory and uses the command-line tool \emph{grep} to highlight the
+presence of the keywords \emph{forkMode}, \emph{forkCount}, and
+\emph{parallel}. Any of these keywords exist in any possible
+combination of parallel settings (see Section~\ref{sec:modes}). Before
+the manual inspection, we found that 37.14\% (13 out of 35) and 62.5\%
+(35 out of 56) of subjects from the \emph{long} and \emph{medium}
+groups did not have any of the keywords. After the manual inspection
+\Fix{...elaborate...}
+
+\Fix{We discovered that \Fix{X}\% and \Fix{y}\%
+of subjects (\emph{long} and \emph{medium}, respectively) did not have
+any evidence of low-level parallelism. It is important to mention that
+this result an upper bound limit since the keyword highlighted could
+not be part of a real configuration (\eg, part of a comment). To
+investigate further the projects reported by our script, we manually
+inspected \Fix{X} configuration files to eliminate false-positives.}
+\Fix{...elaborate...}
 

### 2016-12-13 experiments/evaluation/py/parallel-settings.py
added support to max param

@@ -14,6 +14,7 @@ args = parser.parse_args()
 subjects_home = os.path.abspath(args.subjects)
 base_dir = os.path.abspath(os.curdir)
 min_limit = 0 if not args.min else args.min
+max_limit = args.max
 
 
 def inspect(paths):
@@ -28,13 +29,14 @@ with open(args.input, newline="") as f:
     reader = csv.DictReader(f)
     for row in reader:
         if float(row["elapsed_time"]) >= min_limit:
-            os.chdir(os.path.join(subjects_home, row["name"]))
-            xml_paths = subprocess.check_output(["find", ".", "-path", "*/pom.xml"]).decode().splitlines()
-            subj = inspect(xml_paths)
-            if subj:
-                print(subj)
-                found += 1
-            counter += 1
+            if not max_limit or float(row["elapsed_time"]) < max_limit:
+                os.chdir(os.path.join(subjects_home, row["name"]))
+                xml_paths = subprocess.check_output(["find", ".", "-path", "*/pom.xml"]).decode().splitlines()
+                subj = inspect(xml_paths)
+                if subj:
+                    print(subj)
+                    found += 1
+                counter += 1
 
 print("--------------------")
 print("{} subjects verified".format(counter))

### 2016-12-13 paper/evaluation.tex
updated rq2

@@
 parallel settings and then we manually inspect each configuration file
-to eliminate false-positives. Given a list of subjects, our script
-searches recursively all \emph{pom.xml} files from the project
-directory and uses the command-line tool \emph{grep} to highlight the
-presence of the keywords \emph{forkMode}, \emph{forkCount}, and
-\emph{parallel}. Any of these keywords exist in any possible
-combination of parallel settings (see Section~\ref{sec:modes}). Before
-the manual inspection, we found that 37.14\% (13 out of 35) and 62.5\%
-(35 out of 56) of subjects from the \emph{long} and \emph{medium}
-groups did not have any of the keywords. After the manual inspection
-\Fix{...elaborate...}
+to eliminate false-positives. In addition, we are interested in
+understanding how these parallel settings are used. Given a list of
+subjects, our script searches recursively all \emph{pom.xml} files
+from the project directory and uses the command-line tool \emph{grep}
+to highlight the presence of the keywords \emph{forkMode},
+\emph{forkCount}, and \emph{parallel}.  Any of these keywords exist in
+any possible combination of parallel settings (see
+Section~\ref{sec:modes}). From the 91 subjects, our script detected 43
+subjects with evidence of parallel settings. After the inspection of
+130 configuration files, we confirmed that \Fix{X} settings are real
+parallel configurations.  These settings are related to \Fix{Y}
+subjects. It is important to notice that, \Fix{X}\% of the subjects
+(\emph{medium} and \emph{long} aggregated) did not explore low-level
+parallelism according to our criteria of matching keywords. After the
+inspection, this rate raises to \Fix{Y}\%. \Fix{elaborate: some
+projects doesn't use parallel features, so what?}
+Table~\ref{tab:inspection-table} summarizes our initial findings.
 
-\Fix{We discovered that \Fix{X}\% and \Fix{y}\%
-of subjects (\emph{long} and \emph{medium}, respectively) did not have
-any evidence of low-level parallelism. It is important to mention that
-this result an upper bound limit since the keyword highlighted could
-not be part of a real configuration (\eg, part of a comment). To
-investigate further the projects reported by our script, we manually
-inspected \Fix{X} configuration files to eliminate false-positives.}
-\Fix{...elaborate...}
+\begin{table}[h!]\footnotesize
+    \centering
+    \begin{tabular*}{0.5\textwidth}{cccc}
+        \toprule
+        Group  & Subjects with Evidence & Config. Files & Config. Confirmed\\
+        \midrule
+        Long   & 22 / 35    & 77 / 1981       & \Fix{X} / 77\\%
+        Medium & 21 / 56    & 53 / 491        & \Fix{X} / 53\\%
+        \midrule 
+        Total  & 43 / 91    & 130 / 2472      & \Fix{X} / 130\\
+        \bottomrule
+    \end{tabular*}
+    \caption{\Fix{to-be-defined}}
+    \label{tab:inspection-table} 
+\end{table}
+
+\Fix{elaborate: write about the subjects that use parallelism - How do
+they use them? Would it be possible to measure the benefits? How the
+configs from Section~\ref{sec:modes} are distributed?}
 

### 2016-12-13 experiments/evaluation/py/parallel-settings.py
added some statistics

@@ -29,6 +29,7 @@ def filter_relevant_paths(paths):
 def main():
     counter = 0
     found = 0
+    relevant_files_counter = 0
     files_counter = 0
     with open(args.input, newline="") as f:
         reader = csv.DictReader(f)
@@ -40,14 +41,20 @@ def main():
                     paths = filter_relevant_paths(xml_paths)
                     if paths:
                         print("{} ({}/{} relevant files)".format(row["name"], len(paths), len(xml_paths)))
-                        files_counter += len(paths)
+                        relevant_files_counter += len(paths)
+                        files_counter += len(xml_paths)
                         found += 1
                     counter += 1
+
     print("--------------------")
     print("{} subjects verified".format(counter))
     print("{} subjects found".format(found))
-    print("{} files to inspect".format(files_counter))
     print("%.2f%%" % (found / counter * 100))
+
+    print("{} files to found".format(files_counter))
+    print("{} files to inspect".format(relevant_files_counter))
+    print("%.2f%%" % (relevant_files_counter/ files_counter* 100))
+
 
 if __name__ == "__main__":
     main()

### 2016-12-16 paper/intro.tex
minor pass on intro

--- 2016-11-21 paper/intro.tex
@@
 of test failures.  Dealing with high testing costs is critical at
-large IT organizations, with massive code and test bases.  The Google
-TAP system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
-system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence on the
-criticality of the build and the testing processes at these
-organizations.  Note, however, that the regression testing problem is
-not specific to giants from the IT sector.  For example, a recent
-paper from the automotive industry reported that test suites can take
-days to run~\cite{artl-etal-icst2015}.
+large IT organizations, with massive code and test bases.  Evidence on
+the criticality of running the build and testing processes efficiently
+include the Google's TAP system~\cite{google-tap,google-ci} and
+Microsoft's CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}.
+Note, however, that the regression testing problem is not specific to
+giants from the IT sector.  For example, a recent paper from the
+automotive industry reported that test suites can take days to
+run~\cite{artl-etal-icst2015}.
 
@@
 minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  It is important to note,
-however, that balancing the test workload, either within or across
-machines, is a popular, sound, and practical approach to address
-testing cost and can't be neglected.  Furthermore, this approach is
-complementary to those proposed in the literature. For example, as of
-August 2013, the Groupon PWA system, which powers the
-\url{groupon.com} website, included over 19K tests.  To run all those
-tests under 10m, Groupon used a cluster of 4 computers with 24 cores
-each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
-and Microsoft's CloudBuild distribute task workloads in the cloud.
-Note, that the alternative of renting a cloud
+selection~\cite{yoo-harman-stvr2012}.  These approaches reduce cost by
+reducing the amount of tests that require execution.  It is important
+to bring to light, however, that the complementary approach of
+balancing the test workload, either within or across machines, is
+sound (as selection techniques such as
+Ekstazi~\cite{gligoric-etal-issta2015}) and very popular in industry.
+For example, as of August 2013, the Groupon PWA system, which powers
+the \url{groupon.com} website, included over 19K tests.  To run all
+those tests under 10m, Groupon used a cluster of 4 computers with 24
+cores each~\cite{kim-etal-fse2013}.
+
+%% As additional examples, Google's
+%% TAP and Microsoft's CloudBuild distribute task workloads in the cloud.
+
+The alternative of renting a cloud
 service\footnote{\url{https://clutch.co/cloud}} or even building a
-server farm (for increased security) is a legitimate approach to
+private server farm for increased security is a legitimate approach to
 mitigate the regression testing problem at large organizations.
-However, this solution may not be economically viable for smaller
-projects with heavy testing loads.
+However, for projects with low budgets yet moderate or heavy testing
+workloads, this solution may not be economically viable.\Mar{can you
+  please estimate cost?  what about free services?  what about
+  jenkins?}
 
@@
 
-This paper focuses on optimizing regression testing of open-source
-projects using commodity hardware.  This is an important problem
-assuming that it is not rare for open-source projects to face high
-testing costs.  \Fix{mention similar but different work} To the best
-of our knowledge no prior work investigated this problem.
+The amount of serious open-source project under development today is
+impressive.\Mar{give example, provide stats.}  This paper focuses on
+optimizing regression testing of open-source projects using commodity
+hardware.  This is an important problem assuming that it is not rare
+for open-source projects to face high testing costs.  \Fix{mention
+  similar but different work} To the best of our knowledge no prior
+work investigated this problem.
 
@@
 %%  LocalWords:  Ekstazi github CloudBuild PWA groupon criticality
+
+%%% Local Variables:
+%%% TeX-master: "main"
+%%% End:

### 2016-12-16 paper/intro.tex
pass on intro

--- 2016-11-21 paper/intro.tex
@@
 of test failures.  Dealing with high testing costs is critical at
-large IT organizations, with massive code and test bases.  The Google
-TAP system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
-system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence on the
-criticality of the build and the testing processes at these
-organizations.  Note, however, that the regression testing problem is
-not specific to giants from the IT sector.  For example, a recent
-paper from the automotive industry reported that test suites can take
-days to run~\cite{artl-etal-icst2015}.
+large IT organizations, with massive code and test bases.
 
@@
 minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  It is important to note,
-however, that balancing the test workload, either within or across
-machines, is a popular, sound, and practical approach to address
-testing cost and can't be neglected.  Furthermore, this approach is
-complementary to those proposed in the literature. For example, as of
-August 2013, the Groupon PWA system, which powers the
+selection~\cite{yoo-harman-stvr2012}.  These approaches reduce testing
+cost by reducing the amount of tests for execution.  It is important
+to bring to light that the \emph{complementary alternative} of
+balancing the test workload across work units is sound (\ie{}, it
+cannot miss fault-revealing tests) and very popular in industry.
+Evidence of this are the Google TAP system~\cite{google-tap,google-ci}
+and Microsoft's CloudBuild
+system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
+distributed infrastructures to efficienctly build massive amounts of
+code and run tests.  Note, however, that the regression testing
+problem is not specific to giants from the IT sector.  For example, as
+of August 2013, the Groupon PWA system, which powers the
 \url{groupon.com} website, included over 19K tests.  To run all those
 tests under 10m, Groupon used a cluster of 4 computers with 24 cores
-each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
-and Microsoft's CloudBuild distribute task workloads in the cloud.
-Note, that the alternative of renting a cloud
-service\footnote{\url{https://clutch.co/cloud}} or even building a
-server farm (for increased security) is a legitimate approach to
-mitigate the regression testing problem at large organizations.
-However, this solution may not be economically viable for smaller
-projects with heavy testing loads.
+each~\cite{kim-etal-fse2013}.
+
+%% As additional examples, Google's
+%% TAP and Microsoft's CloudBuild distribute task workloads in the cloud.
+
+At large organizations, the alternative of renting a cloud
+service\footnote{\url{https://clutch.co/cloud}} or even building
+proprietary infrastructures for running tests is a legitimate approach
+to mitigate the regression testing problem.  However, for projects
+with low budgets and yet moderate or heavy testing workloads, this
+solution may not be economically viable.  The amount of serious
+open-source project under development today is impressive.\Mar{give
+  examples, provide stats.}  Optimizing existing computational
+resources in this context saves money or time.  \Mar{what about free
+  services (jenkins)?  how much can you scale execution and how
+  expensive would that be?}
 
@@
 
-This paper focuses on optimizing regression testing of open-source
-projects using commodity hardware.  This is an important problem
-assuming that it is not rare for open-source projects to face high
-testing costs.  \Fix{mention similar but different work} To the best
-of our knowledge no prior work investigated this problem.
-
----- aqui
-
-%% eventually move this to macros.tex
-\newcommand{\numSubjs}{143}
-\newcommand{\numLongRunning}{\Fix{17\%}}
-\newcommand{\percentParallelForLongRunning}{\Fix{80\%}}
+\sloppy This paper focuses on the problem of understanding how
+critical the regression testing problem is in open-source projects.
+To the best of our knowledge no prior work investigated this problem,
+which is important given the tremendous popularity of open-source
+development and the wide impact of regression testing optimization
+techniques in this setting.
 
 %Motivated by this potential gap in regression testing,
+%% More specifically, we studied how often long-running test suites occur
+%% in this setting, how frequently parallelization features are used, if
+%% not used why, and what are the associated drawbacks.
 
-This paper focuses on the problem of understanding how critical the
-regression testing problem is in open-source projects and what are the
-potential benefits and shortcomings of using the parallelization
-features of build systems and testing frameworks, which are very
-popular today\Fix{cite cite cite}.  More precisely, we studied (1) how
-prevalent long-running test suites are in open-source software
-projects.  To conduct this experiment we selected \numSubjs{} Java
-projects from github that are highly-popular and use the Maven build
-system.  (Section~\ref{sec:eval} details our selection methodology.)
-Our experimental results indicate that long-running test suites
-(taking longer than 5m to complete\Fix{check if Ekstazi paper also
-  used this value to indicate long runs and cite}) are not
-rare~--~\numLongRunning{} of the projects we analyzed contain
-long-running test suites.  \Mar{missing connection. why parallelism?}
-From this result we investigated (2) how frequently the projects we
-considered use parallelization to speedup test runs.  Our results
-indicate that \percentParallelForLongRunning{} of long-running test
-suites do use parallelism to speedup execution.  Given the popularity
-of this solution, we further studied: (3) what are the causes of high
-execution cost in individual tests (CPU vs. IO) and (4) how uniformly
-cost is distributed across tests.  These questions help to assess the
-impact of parallelization in test suite execution.  Intuitively,
-IO-intensive test suites and test suites with uneven distribution of
-cost per test are factors that limit the benefits of parallelization.
-Results indicate that \Fix{...}  Finally, we investigated (5) what are
-the limitations related to parallelization that could justify adoption
-resistance.
+More precisely, we studied (1) how prevalent long-running test suites
+are in open-source software projects.  To that end, we selected from
+\github{} \numSubjs{} highly-popular Java projects containing Maven
+build files.  (Section~\ref{sec:eval} details our selection
+methodology.)  To run this experiment we used the default Maven
+configuration to run a project's test suite and a 16GB memory i7-4790
+Intel processor machine, which we carefully isolated.  Our results
+indicate that the test suite of nearly one in every five projects from
+our set (\percentMedLongRunning) takes at least 5m to run.  On
+average, one of those test suites take \averageMedLongRunning{} to
+run.  These results suggest that open-source projects often contain
+long running test suites.
+
+\Mar{missing connection. why
+  parallelism?}  From this result we investigated (2) how frequently
+the projects we considered use parallelization to speedup test runs.
+Our results indicate that \percentParallelForLongRunning{} of
+long-running test suites do use parallelism to speedup execution.
+Given the popularity of this solution, we further studied: (3) what
+are the causes of high execution cost in individual tests (CPU vs. IO)
+and (4) how uniformly cost is distributed across tests.  These
+questions help to assess the impact of parallelization in test suite
+execution.  Intuitively, IO-intensive test suites and test suites with
+uneven distribution of cost per test are factors that limit the
+benefits of parallelization.  Results indicate that \Fix{...}
+Finally, we investigated (5) what are the limitations related to
+parallelization that could justify adoption resistance.
 

### 2016-12-26 paper/evaluation.tex
updated subjects and setup sections

@@
 
-We used the Github's Search API~\cite{githubsearch} to fetch Java
-projects based on Maven according to the following criteria: primary
-language must be Java\footnote{In case of projects in multiple
-languages, the Github API considers the predominant language as the
-primary language.}; project with at least 100 stars; latest update on
-(or after) January 1st, 2016; contains the string \emph{mvn} in the
-\emph{README} file.  The number of stars indicates the interest and
-appreciation from the community to a given project.
-\Comment{(https://help.github.com/articles/about-stars/)} Although our
-criteria is subjective, it is an approximation to find relevant
-projects to conduct our study.  Figure~\ref{fig:subject-query}
-illustrates the query.
+We are interested to evaluate non-trivial test suites on popular
+projects that are in activity. In addition, we used Maven as a
+reference due to its popularity on Java projects and to automate our
+evaluation. We used the Github's Search API~\cite{githubsearch} to
+fetch Java projects with Maven support according to the following
+criteria: (1) the primary language must be Java\footnote{In case of
+projects in multiple languages, the Github API considers the
+predominant language as the primary language.}; (2) the project has at
+least 100 stars; (3) latest update on (or after) January 1st, 2016;
+(4) the \emph{readme} file contains the string \emph{mvn}.
+
+On Github, when a user adds a star to a project, s/he demonstrated
+appreciation and bookmarked it for later
+reference~\cite{github-stars}.  Although there is not a specific range
+for the number of stars, our criteria is an estimation to avoid
+trivial subjects. The fourth criteria is an approximation to find
+projects with Maven support. The rationale is that if the string
+\emph{mvn} exists in the \emph{readme} file, it may represents a Maven
+call in the instructions on how to compile (or test) the project.
+Figure~\ref{fig:subject-query} illustrates the query.
 
@@
     projects in Java with at least 100 stars, updated on January 1st,
-    2016 (or later), and contains the string \emph{mvn} in the
-    \emph{README} file.}
+    2016 (or later), and \emph{readme} file contains the string
+    \emph{mvn}. Output listed in descending order of stars}
 \end{figure}
 
-As in December 12th, 2016, our search criteria returned 589 subjects.
+As of December 12th 2016, our search criteria returned 589 subjects.
 From the 589 downloaded projects, we considered 312 projects that we
@@
 dependencies, 125 could not be compiled, and 87 could not execute the
-tests. In addition, we first attempted to consider Gradle and Ant
-projects but most of Gradle projects were related to Android apps and
-libraries and adding support to Ant would require to parse the
-\emph{build.xml} to identify the compilation and test commands since
-the build process is based on user-defined tasks.
+tests.
 
@@
 each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
-(64-bit version). Software settings include the Linux \emph{sysstat}
-package to measure performance, \emph{git} to fetch subjects,
-\emph{Java 8} and \emph{Maven 3} to build and test subjects, and
-\emph{Python 3.4} to run our evaluation scripts. For replication, we
-provide all the source artifacts publicly available at \Fix{create
-gh-pages}, including supporting scripts (\eg, the script that test
-subjects and generates the raw data), the full list of projects, and a
+(64-bit version). Software settings include \Comment{the Linux
+\emph{sysstat} package to measure performance, }\emph{git} to fetch
+subjects, \emph{Java 8} and \emph{Maven 3} to build and test subjects,
+and \emph{Python 3.4} to run our evaluation scripts. For replication,
+all source artifacts are publicly available at \Fix{create gh-pages},
+including supporting scripts (\eg, the script that test subjects and
+generates the raw data), the full list of projects, and a
 \emph{Vagrantfile} to emulate our hardware and all software
-dependencies properly configured.
+dependencies.
 

### 2016-12-30 paper/evaluation.tex
WIP - updating subjects section

@@
 We are interested to evaluate non-trivial test suites on popular
-projects that are in activity. In addition, we used Maven as a
-reference due to its popularity on Java projects and to automate our
-evaluation. We used the Github's Search API~\cite{githubsearch} to
-fetch Java projects with Maven support according to the following
-criteria: (1) the primary language must be Java\footnote{In case of
-projects in multiple languages, the Github API considers the
+projects that are in activity. We used the Github's Search
+API~\cite{githubsearch} to fetch Java projects according to the
+following criteria: (1) the primary language must be Java\footnote{In
+case of projects in multiple languages, the Github API considers the
 predominant language as the primary language.}; (2) the project has at
@@
 for the number of stars, our criteria is an estimation to avoid
-trivial subjects. The fourth criteria is an approximation to find
-projects with Maven support. The rationale is that if the string
-\emph{mvn} exists in the \emph{readme} file, it may represents a Maven
-call in the instructions on how to compile (or test) the project.
-Figure~\ref{fig:subject-query} illustrates the query.
+trivial subjects: we assumed that Github users are likely to
+demonstrate interest on well-tested projects. The third criteria is a
+constraint to skip projects without recent activity. The fourth
+criteria is an approximation to find projects with Maven support. We
+used Maven as a reference due to its popularity on Java projects and
+to automate our evaluation scripts. The rationale is that if the
+string \emph{mvn} exists in the \emph{readme} file, it may represent a
+Maven call (\eg, to compile or test the project).
+Figure~\ref{fig:subject-query} illustrates the query as an HTTP
+request.
 
@@
     basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    morekeywords={stars,language,pushed,in},
     deletekeywords={true}
@@
     stars:>=100+language:java+mvn%20in:readme+
-    pushed:>=2016-01-01+sort:stars&page=1&per_page=100
+    pushed:>=2016-01-01+sort:stars
 
@@
 \caption{\label{fig:subject-query} Query to the Github API for
-    projects in Java with at least 100 stars, updated on January 1st,
-    2016 (or later), and \emph{readme} file contains the string
-    \emph{mvn}. Output listed in descending order of stars}
+    projects with the following criteria: (1) Java, (2) at least 100
+    stars, (3) updated on January 1st, 2016 (or later), (4) contains
+    the string \emph{mvn} in the \emph{readme} file. Output is
+    paginated in descending order of stars.}
 \end{figure}
 
-As of December 12th 2016, our search criteria returned 589 subjects.
-From the 589 downloaded projects, we considered 312 projects that we
+As of December 30th 2016, our search criteria returned 615 subjects.
+From the 615 downloaded projects, \Fix{we considered 312 projects that we
 were able to compile and test. The others 277 could not be considered
@@
 dependencies, 125 could not be compiled, and 87 could not execute the
-tests.
+tests.}
 

### 2016-12-31 paper/evaluation.tex
update

@@
 
-As of December 30th 2016, our search criteria returned 615 subjects.
-From the 615 downloaded projects, \Fix{we considered 312 projects that we
-were able to compile and test. The others 277 could not be considered
-because 39 were not Maven projects, 26 could not fetch all required
-dependencies, 125 could not be compiled, and 87 could not execute the
-tests.}
+A Maven project may contain several submodules with multiple
+\emph{pom.xml} files. We considered only projects with a
+\emph{pom.xml} file located in the root directory.  As of December
+30th 2016, our search criteria returned 615 subjects. From the 615
+downloaded projects, 46 were not Maven projects, 25 were unable to fetch
+all dependencies (\eg, due to the usage of a private library), and 128
+were in an unstable revision. Our final set consists in 416 subjects.
 
@@
 To evaluate the frequency of time-consuming regression tests, we
-considered the 312 subjects from Section~\ref{sec:subjects} and
+considered the 416 subjects from Section~\ref{sec:subjects} and
 compared the elapsed time to run their tests.
-Figure~\ref{fig:mvn-execution} illustrates the commands used in our
-scripts to test each subject.  To avoid inflating the measured time,
-we first compile the sources files (line 1) and later, we ran the
-tests ignoring non-related tasks (line 3).  In addition, when we run a
-subject's test suite, we operate Maven in offline mode to limit the
-network access, avoiding any unnecessary package update as all
-required \emph{jars} are available locally (line 2).  After the test
-execution, we use a simple regular expression over the builder output
-to extract the elapsed time.
+Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
+to test each subject. The main loop (line 12) iterates over the list
+of subjects and invokes the wrapper function \emph{run} to execute
+Maven in separated steps (lines 14-16). To avoid inflating the
+measured time, we first fetch all dependencies (line 14), compile the
+source and test files (line 15) and later, we invoke Maven in offline
+mode (line 16) to avoid package updates. In addition we randomly
+selected 100 Maven logs to inspect and identify non-related tasks
+(\eg, \emph{javadoc} generation and static analysis). We created a
+list of plugins (lines 1-5) to ignore them during the test execution.
+After the test execution, we use a simple regular expression over
+the builder output to extract the elapsed time.
 
@@
     basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    morekeywords={o, DskipTests, Dmaven, javadoc, skip, go, offline, P},
-    deletekeywords={true}
 }
-\begin{lstlisting}
-mvn clean install -DskipTests -Dmaven.javadoc.skip=true
-mvn dependency:go-offline
-mvn -o test -Dmaven.javadoc.skip=true
+\begin{lstlisting}[language=Python]
+MAVEN_IGNORES = [
+   "-Drat.skip=true", "-Dmaven.javadoc.skip=true",
+   "-Djacoco.skip=true", "-Dcheckstyle.skip=true",
+   "-Dfindbugs=true", "-Dcobertura.skip=true"
+]
+
+def run(cmds, opts=None):
+   if opts not None:
+      cmds.extend(opts)
+   subprocess.call(cmds)
+
+for subject in SUBJECTS:
+   os.chdir(subject)
+   run(["mvn", "dependency:go-offline"])
+   run(["mvn", "clean", "install", "-DskipTests"])
+   run(["mvn", "-o", "test"], MAVEN_IGNORES)
 \end{lstlisting}
-\caption{\label{fig:mvn-execution} Maven commands to test a subject:
-    line 1 compiles all subject's source artifacts and make them
-    available in a local repository (\ie, directory \emph{.m2} in the
-    user's home directory); line 2 ensures all dependencies are
-    resolved; line 3 runs the tests in offline mode ignoring javadoc
-    generation.}
+\caption{\label{fig:mvn-execution} Python script to evaluate the
+    time cost of test suites. For each subject, we fetch all
+    dependencies, compile the source and test files, and execute the
+    tests in offline mode ignoring non-related tasks.}
 \end{figure}

### 2017-01-01 paper/evaluation.tex
created macro for th # of stable subjects

@@
 
+\newcommand{\SubjCnt}{412}
+
 A Maven project may contain several submodules with multiple
@@
 30th 2016, our search criteria returned 615 subjects. From the 615
-downloaded projects, 46 were not Maven projects, 25 were unable to fetch
-all dependencies (\eg, due to the usage of a private library), and 128
-were in an unstable revision. Our final set consists in 416 subjects.
+downloaded projects, 46 were not Maven projects, 26 were unable to
+fetch all dependencies (\eg, due to the usage of a private library),
+and 131 were in an unstable revision. Our final set consists in
+\SubjCnt{} subjects.
 
@@
 To evaluate the frequency of time-consuming regression tests, we
-considered the 416 subjects from Section~\ref{sec:subjects} and
+considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
 compared the elapsed time to run their tests.
@@
 list of plugins (lines 1-5) to ignore them during the test execution.
-After the test execution, we use a simple regular expression over
-the builder output to extract the elapsed time.
+After the test execution, we use a simple regular expression over the
+builder output to extract the elapsed time.
 

### 2017-01-02 paper/evaluation.tex
Updated maven version

@@
 \emph{sysstat} package to measure performance, }\emph{git} to fetch
-subjects, \emph{Java 8} and \emph{Maven 3} to build and test subjects,
+subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
 and \emph{Python 3.4} to run our evaluation scripts. For replication,

### 2017-01-02 paper/evaluation.tex
fixed execution order

@@
 
-\newcommand{\SubjCnt}{412}
+\newcommand{\SubjCnt}{411}
 
@@
 30th 2016, our search criteria returned 615 subjects. From the 615
-downloaded projects, 46 were not Maven projects, 26 were unable to
+downloaded projects, 46 were not Maven projects, 27 were unable to
 fetch all dependencies (\eg, due to the usage of a private library),
@@
 including supporting scripts (\eg, the script that test subjects and
-generates the raw data), the full list of projects, and a
+generates the raw data), and the full list of projects. \Comment{, and a
 \emph{Vagrantfile} to emulate our hardware and all software
-dependencies.
+dependencies.}
 
@@
 Maven in separated steps (lines 14-16). To avoid inflating the
-measured time, we first fetch all dependencies (line 14), compile the
-source and test files (line 15) and later, we invoke Maven in offline
+measured time, we first compile the source and test files (line 14),
+fetch all dependencies (line 15) and later, we run the tests in offline
 mode (line 16) to avoid package updates. In addition we randomly
@@
 list of plugins (lines 1-5) to ignore them during the test execution.
-After the test execution, we use a simple regular expression over the
-builder output to extract the elapsed time.
+Finally, we use a simple regular expression over the test output to
+extract the elapsed time.
 
@@
    os.chdir(subject)
+   run(["mvn", "clean", "install", "-DskipTests"])
    run(["mvn", "dependency:go-offline"])
-   run(["mvn", "clean", "install", "-DskipTests"])
    run(["mvn", "-o", "test"], MAVEN_IGNORES)
 \end{lstlisting}
-\caption{\label{fig:mvn-execution} Python script to evaluate the
-    time cost of test suites. For each subject, we fetch all
-    dependencies, compile the source and test files, and execute the
-    tests in offline mode ignoring non-related tasks.}
+\caption{\label{fig:mvn-execution} Python script to evaluate the time cost of
+    test suites. For each subject, we compile the source and test files, fetch
+    all dependencies, and execute the tests in offline mode ignoring
+    non-related tasks.}
 \end{figure}
@@
 minutes (\emph{medium execution}), and more than five minutes
-(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
-proportion of subjects per group and Figure~\ref{fig:boxplots-time}
-shows the distribution of elapsed time for each group (boxplots).
+(\emph{long execution}). A previous work used a similar categorization
+except for the \emph{medium} group \cite{gligoric-etal-issta2015}.  We
+added a new group because \Fix{justify or use the same
+classification}.  Figure~\ref{fig:piechart-time} shows the proportion
+of subjects per group and Figure~\ref{fig:boxplots-time} shows the
+distribution of elapsed time for each group (boxplots).
 

### 2017-01-02 paper/evaluation.tex
updated listing and explanation

@@
 compared the elapsed time to run their tests.
-Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
-to test each subject. The main loop (line 12) iterates over the list
-of subjects and invokes the wrapper function \emph{run} to execute
-Maven in separated steps (lines 14-16). To avoid inflating the
-measured time, we first compile the source and test files (line 14),
-fetch all dependencies (line 15) and later, we run the tests in offline
-mode (line 16) to avoid package updates. In addition we randomly
-selected 100 Maven logs to inspect and identify non-related tasks
-(\eg, \emph{javadoc} generation and static analysis). We created a
-list of plugins (lines 1-5) to ignore them during the test execution.
-Finally, we use a simple regular expression over the test output to
-extract the elapsed time.
+Figure~\ref{fig:mvn-execution} shows the commands used in our script
+to test each subject. The main loop (lines 6-12) iterates over the
+list of subjects and invokes Maven in separated steps (lines 8-10). To
+avoid inflating the measured time, we first compile the source and
+test files (line 8), fetch all dependencies (line 9) and later, we
+run the tests in offline mode (line 10) to avoid package updates. In
+addition we randomly selected 100 Maven logs to inspect and identify
+non-related tasks (\eg, \emph{javadoc} generation and static
+analysis). We created a list of plugins (lines 1-4) to ignore them
+during the test execution.  Finally, we use a simple regular
+expression over the test output to extract the elapsed time (line 13).
 
@@
     basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+    showstringspaces=false
 }
-\begin{lstlisting}[language=Python]
-MAVEN_IGNORES = [
-   "-Drat.skip=true", "-Dmaven.javadoc.skip=true",
-   "-Djacoco.skip=true", "-Dcheckstyle.skip=true",
-   "-Dfindbugs=true", "-Dcobertura.skip=true"
-]
+\begin{lstlisting}[language=Bash]
+MAVEN_IGNORES="-Dmaven.javadoc.skip=true \
+    -Drat.skip=true -Djacoco.skip=true \
+    -Dcheckstyle.skip=true -Dfindbugs=true \
+    -Dcobertura.skip=true"
 
-def run(cmds, opts=None):
-   if opts not None:
-      cmds.extend(opts)
-   subprocess.call(cmds)
-
-for subject in SUBJECTS:
-   os.chdir(subject)
-   run(["mvn", "clean", "install", "-DskipTests"])
-   run(["mvn", "dependency:go-offline"])
-   run(["mvn", "-o", "test"], MAVEN_IGNORES)
+for subj in ${SUBJECTS}; do
+    cd ${SUBJECTS_HOME}/${subj}
+    mvn clean install -DskipTests ${MAVEN_IGNORES}
+    mvn dependency:go-offline
+    mvn -o test ${MAVEN_IGNORES} &> ${LOG}
+    cat ${LOG} | grep "\[INFO\] Total time:"
+done
 \end{lstlisting}
-\caption{\label{fig:mvn-execution} Python script to evaluate the time cost of
+\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
     test suites. For each subject, we compile the source and test files, fetch
     all dependencies, and execute the tests in offline mode ignoring
-    non-related tasks.}
+    non-related tasks. Unnecessary commands are omitted for simplicity.}
 \end{figure}

### 2017-01-02 paper/evaluation.tex
pass on rq description

@@
 regression test suites in open-source projects?}
-
-\newcommand{\RQB}{\Fix{How often do developers use parallelism to improve
-runtime performance?}}
-
+\newcommand{\RQB}{How often are parallelization features in build
+files?}
 \newcommand{\RQC}{What is the impact of parallalelization?}
@@
 
-The first research question addresses the distribution of subjects per
-time cost. We are interested in identifying time-consuming test suites
-to investigate further their characteristics (\eg, type of application
-and bottlenecks from execution).  The second research question
+The first research question addresses the prevalence of long-running
+test suites. We are interested to know if costly test suites are
+common in open-source projects.  The second research question
 addresses our interest in understanding if developers are aware of
-parallelism features from testing frameworks available out-of-the-box
-through build systems (\eg, run JUnit test cases in parallel using
-Maven Surefire) and what setting are often used. The third research
-question addresses the impact of parallelism on the regression tests
-from our sample set. We are interested in compare the execution
-performance with different parallel settings (see
+parallelization features from testing frameworks available
+out-of-the-box through build systems (\eg, run JUnit test cases in
+parallel using Maven Surefire) and what setting are more often used.
+The third research question addresses the impact of parallelism on the
+regression tests from our sample set. We are interested in compare the
+execution performance with different parallel settings (see
 Section~\ref{sec:modes}). The fourth research question addresses the
@@
 avoid inflating the measured time, we first compile the source and
-test files (line 8), fetch all dependencies (line 9) and later, we
-run the tests in offline mode (line 10) to avoid package updates. In
+test files (line 8), fetch all dependencies (line 9) and later, we run
+the tests in offline mode (line 10) to avoid package updates. In
 addition we randomly selected 100 Maven logs to inspect and identify
@@
 expression over the test output to extract the elapsed time (line 13).
+We executed this experiment \Fix{X} times in our dedicated server
+remotely via SSH with the operating system running only essential
+services (\eg, the SSH server).
 

### 2017-01-03 paper/evaluation.tex
pass on rq2

@@
 regression test suites in open-source projects?}
-\newcommand{\RQB}{How often are parallelization features in build
-files?}
+\newcommand{\RQB}{How often are parallelization features present in
+build files?}
 \newcommand{\RQC}{What is the impact of parallalelization?}
@@
 
-To evaluate the  use of low-level parallelism, we considered the 91
-subjects from the groups \emph{long} and \emph{medium} identified in
-Section~\ref{sec:rqone}. In an initial exploration, we searched for
+To evaluate the presence of parallelization settings, we considered
+the \Fix{91} subjects from the groups \emph{long} and \emph{medium}
+identified in Section~\ref{sec:rqone}. We focused in these two groups
+because they represent costly test suites and are more likely that the
+developers may have used strategies to reduce the execution cost (\eg,
+running parts of the tests in different threads). We computed the
+frequence of the parallelism modes (see Section \ref{sec:modes}) using
+a partially manual approach: we first discover automatically the
+relevant configuration files and then we manually inspect to eliminate
+false-positves (\eg, commented configuration).
+
+\Fix{---------------------}
+
+In an initial exploration, we searched for
 evidences of low-level parallelism settings on configuration files

### 2017-01-03 paper/evaluation.tex
pass on rq2 and added macro CodeIn

@@
 frequence of the parallelism modes (see Section \ref{sec:modes}) using
-a partially manual approach: we first discover automatically the
-relevant configuration files and then we manually inspect to eliminate
-false-positves (\eg, commented configuration).
+a semi-automatic approach: we first discover automatically the
+relevant configuration files and then we manually inspect them to
+eliminate false-positves (\eg, commented configuration).  Figure
+\Fix{N} describes the discovery step. We first list the paths of all
+build file and then we filter only the build files that contain any of
+the keywords, \CodeIn{forkMode}, \CodeIn{forkCount}, or
+\CodeIn{parallel}.
+
+\begin{figure}[h!]
+\centering
+\scriptsize
+\lstset{
+    escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+    showstringspaces=false
+}
+\begin{lstlisting}[language=Bash]
+for subj in ${SUBJECTS}; do
+    subject_path=${SUBJECTS_HOME}/${subj}
+    build_files=`find $subject_path -name pom.xml`
+done
+\end{lstlisting}
+\caption{\label{fig:discovery-step} Bash script \Fix{to do
+         something...}. Unnecessary commands are omitted for simplicity.}
+\end{figure}
 

### 2017-01-03 paper/evaluation.tex
Fixed existing macro

@@
 
-\newcommand{\SubjCnt}{411}
-
 A Maven project may contain several submodules with multiple
@@
 and 131 were in an unstable revision. Our final set consists in
-\SubjCnt{} subjects.
+\numSubjs{} subjects.
 
@@
 To evaluate the frequency of time-consuming regression tests, we
-considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
+considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
 compared the elapsed time to run their tests.

### 2017-01-03 paper/evaluation.tex
added reminder on RQ1
added caption to bash script

--- 2017-01-03 paper/evaluation.tex
@@
 remotely via SSH with the operating system running only essential
-services (\eg, the SSH server).
+services (\eg, the SSH server). \Fix{Describe CPU isolation}
 
@@
 
-for subj in ${SUBJECTS}; do
-    cd ${SUBJECTS_HOME}/${subj}
-    mvn clean install -DskipTests ${MAVEN_IGNORES}
+for subj in $SUBJECTS; do
+    cd $SUBJECTS_HOME/$subj
+    mvn clean install -DskipTests $MAVEN_IGNORES
     mvn dependency:go-offline
-    mvn -o test ${MAVEN_IGNORES} &> ${LOG}
-    cat ${LOG} | grep "\[INFO\] Total time:"
+    mvn -o test $MAVEN_IGNORES &> $LOG
+    cat $LOG | grep "\[INFO\] Total time:"
 done
@@
 To evaluate the presence of parallelization settings, we considered
-the \Fix{91} subjects from the groups \emph{long} and \emph{medium}
-identified in Section~\ref{sec:rqone}. We focused in these two groups
-because they represent costly test suites and are more likely that the
-developers may have used strategies to reduce the execution cost (\eg,
-running parts of the tests in different threads). We computed the
-frequence of the parallelism modes (see Section \ref{sec:modes}) using
-a partially manual approach: we first discover automatically the
-relevant configuration files and then we manually inspect to eliminate
-false-positves (\eg, commented configuration).
+the \numSubjsRqTwo{} subjects from the groups \emph{long} and
+\emph{medium} identified in Section~\ref{sec:rqone}. We focused in
+these two groups because they represent costly test suites and are
+more likely that the developers may have used strategies to reduce the
+execution cost (\eg, running parts of the tests in different threads).
+We computed the frequence of the parallelism modes (see Section
+\ref{sec:modes}) using a semi-automatic approach: we first discover
+automatically the relevant configuration files and then we manually
+inspect them to eliminate false-positves (\eg, commented
+configuration).  Figure \Fix{N} describes the discovery step. We first
+list the paths of all build file and then we filter only the build
+files that contain any of the keywords, \CodeIn{forkMode},
+\CodeIn{forkCount}, or \CodeIn{parallel}. Notice that, for Maven
+projects, these any keywords exist in any possible parallelism
+configuration \Fix{cite surefire doc}.
+
+\begin{figure}[h!]
+\centering
+\scriptsize
+\lstset{
+    escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+    showstringspaces=false
+}
+\begin{lstlisting}[language=Bash]
+for subj in $SUBJECTS; do
+    subject_path="$SUBJECTS_HOME/$subj"
+    build_files=`find $subject_path -name pom.xml`
+    for build_file in $build_files; do
+        output=`cat $build_file | grep "parallel\
+                \|forkMode\|forkCount"`
+        if [ -z $output ]; then
+            echo $build_file
+        fi
+done
+\end{lstlisting}
+    \caption{\label{fig:discovery-step} Bash script to filter
+    build files (\ie, \emph{pom.xml}) with potentially parallelization
+    settings. We first list all build files from a subject (line 3).
+    Then, we list the content of the file (\CodeIn{cat} command) and
+    redirect the output to filter only the lines that contains any of
+    the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
+    \CodeIn{forkCount} (\CodeIn{grep} command). If output is not empty
+    (line 7), we print the path from the current \emph{pom.xml} file.}
+\end{figure}
+
+From the \numSubjsRqTwo{} subjects, there was a total of \Fix{X} build
+files and \Fix{Y} to inspect.
 
@@
 
-In an initial exploration, we searched for
-evidences of low-level parallelism settings on configuration files
-(\ie, \emph{pom.xml}) from each subject using a semi-automated
-approach: we use a script to find all subjects with evidences of
-parallel settings and then we manually inspect each configuration file
-to eliminate false-positives. In addition, we are interested in
-understanding how these parallel settings are used. Given a list of
-subjects, our script searches recursively all \emph{pom.xml} files
-from the project directory and uses the command-line tool \emph{grep}
-to highlight the presence of the keywords \emph{forkMode},
-\emph{forkCount}, and \emph{parallel}.  Any of these keywords exist in
-any possible combination of parallel settings (see
-Section~\ref{sec:modes}). From the 91 subjects, our script detected 43
-subjects with evidence of parallel settings. After the inspection of
-130 configuration files, we confirmed that \Fix{X} settings are real
-parallel configurations.  These settings are related to \Fix{Y}
-subjects. It is important to notice that, \Fix{X}\% of the subjects
-(\emph{medium} and \emph{long} aggregated) did not explore low-level
-parallelism according to our criteria of matching keywords. After the
-inspection, this rate raises to \Fix{Y}\%. \Fix{elaborate: some
-projects doesn't use parallel features, so what?}
-Table~\ref{tab:inspection-table} summarizes our initial findings.
+From the 91 subjects, our script detected 43 subjects with evidence of
+parallel settings. After the inspection of 130 configuration files, we
+confirmed that \Fix{X} settings are real parallel configurations.
+These settings are related to \Fix{Y} subjects. It is important to
+notice that, \Fix{X}\% of the subjects (\emph{medium} and \emph{long}
+aggregated) did not explore low-level parallelism according to our
+criteria of matching keywords. After the inspection, this rate raises
+to \Fix{Y}\%. \Fix{elaborate: some projects doesn't use parallel
+features, so what?} Table~\ref{tab:inspection-table} summarizes our
+initial findings.
 

### 2017-01-03 paper/evaluation.tex
removed unnecessary word
pass on text

@@
 We evaluated the characteristics of regression tests in open-source
-development from a sample set of Java projects from Github. We are
+development from a sample set of Java projects from \github{}. We are
 interested in understanding the prevalence of long test runs, the main
@@
 regression test suites in open-source projects?}
-\newcommand{\RQB}{How often are parallelization features present in
+\newcommand{\RQB}{How often are parallelization features in
 build files?}
@@
 We are interested to evaluate non-trivial test suites on popular
-projects that are in activity. We used the Github's Search
+projects that are in activity. We used the \github{}'s search
 API~\cite{githubsearch} to fetch Java projects according to the
 following criteria: (1) the primary language must be Java\footnote{In
-case of projects in multiple languages, the Github API considers the
+case of projects in multiple languages, the \github{} API considers the
 predominant language as the primary language.}; (2) the project has at
@@
 
-On Github, when a user adds a star to a project, s/he demonstrated
+On \github{}, when a user adds a star to a project, s/he demonstrated
 appreciation and bookmarked it for later
@@
 for the number of stars, our criteria is an estimation to avoid
-trivial subjects: we assumed that Github users are likely to
+trivial subjects: we assumed that \github{} users are likely to
 demonstrate interest on well-tested projects. The third criteria is a
@@
 \end{lstlisting}
-\caption{\label{fig:subject-query} Query to the Github API for
+    \caption{\label{fig:subject-query} Query to the \github{} API for
     projects with the following criteria: (1) Java, (2) at least 100
@@
 inspect them to eliminate false-positves (\eg, commented
-configuration).  Figure \Fix{N} describes the discovery step. We first
-list the paths of all build file and then we filter only the build
-files that contain any of the keywords, \CodeIn{forkMode},
-\CodeIn{forkCount}, or \CodeIn{parallel}. Notice that, for Maven
-projects, these any keywords exist in any possible parallelism
-configuration \Fix{cite surefire doc}.
+configuration).  Figure~\ref{fig:discovery-step} describes the
+discovery step. We first list the paths of all build file and then we
+filter only the build files that contain any of the keywords,
+\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
+that, for Maven projects, these any keywords exist in any possible
+parallelism configuration \Fix{cite surefire doc}.
 

### 2017-01-03 paper/codes/discovery.tex
pass on text and refactoring

--- 2017-01-03 paper/evaluation.tex
@@
-\section{Evaluation}
-\label{sec:eval}
-
-\Mar{I think the high-level goal should be something along the lines
-  of understanding prevalence of long test runs and main sources of
-  cost in open-source Java projects.  Intuitively, the problem should
-  come before the solution :).  Based on that, we study
-  parallelization of testing frameworks.  More precisely, we
-  investigage how prevalent test parallelization is, the potential for
-  improving execution cost, issues of flakiness that hinders use of
-  parallelization, and how to address those issues.}
-
-We evaluated the characteristics of regression tests in open-source
-development from a sample set of Java projects from Github. We are
-interested in understanding the prevalence of long test runs, the main
-sources of cost, and how do developers explore parallelism to improve
-execution performance. More specifically, we pose the following
-research questions:
-
-\newcommand{\RQA}{How prevalent is the occurence of time-consuming
-regression test suites in open-source projects?}
-\newcommand{\RQB}{How often are parallelization features present in
-build files?}
-\newcommand{\RQC}{What is the impact of parallalelization?}
-
-\newcommand{\RQD}{What factors contribute to improve performance
-through parallelization?\Jbc{Previously as "When does parallelization
-works and when it does not so great?"}}
-
-\newcommand{\RQE}{What are the limitations of parallelization?}
-
-\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
-\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
-\newcommand{\rqThree}{\textbf{RQ3.} \RQC}
-\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
-\newcommand{\rqFive}{\textbf{RQ5.} \RQE}
-
-\begin{itemize}
-    \item \rqOne
-    \item \rqTwo
-    \item \rqThree
-    \item \rqFour
-    \item \rqFive
-\end{itemize}
-
-%%\newcommand{\RQB}{What is the distribution of CPU and IO bound
-%%regression test suites from the sample set?}
-%%
-%%\newcommand{\RQC}{How uniformly distributed is the execution time
-%%across test cases in costly projects?}
-%%
-%%\newcommand{\RQD}{How often developers use the parallelism features
-%%from build systems to improve runtime performance?}
-
-The first research question addresses the prevalence of long-running
-test suites. We are interested to know if costly test suites are
-common in open-source projects.  The second research question
-addresses our interest in understanding if developers are aware of
-parallelization features from testing frameworks available
-out-of-the-box through build systems (\eg, run JUnit test cases in
-parallel using Maven Surefire) and what setting are more often used.
-The third research question addresses the impact of parallelism on the
-regression tests from our sample set. We are interested in compare the
-execution performance with different parallel settings (see
-Section~\ref{sec:modes}). The fourth research question addresses the
-characteristics of regression tests from the previous experiment.
-More specifically, we want to investigate if there is a relation
-between the balance of test execution (\ie, how uniformly distributed
-is the execution time across tests cases) and the usage of
-computational resources (\ie, if tests are mostly CPU or IO intense)
-that impacts the effectiveness of parallelization. Finally, the fifth
-research question discusses the limitations and insights to overcome
-the pitfalls of parallelization.
-
-\Comment{
-    \Fix{distribution of execution time per test case. For each subject
-    identified in the first research question, we investigate how
-    balanced is the cost of the test suite in contrast to the cost of
-    test cases and if there are subjects where the time cost is mostly
-    dominated by a small fraction of test cases.} \Fix{The third research
-    question addresses the distribution of regression tests according
-    to the use of computational resources.  We are interested in
-    investigating if regression test suites are CPU intensive and if there
-    are opportunities to improve performance. The RQ4 addresses}
-    \Fix{...elaborate...}
-
-    The rationale is that if the time cost of a regression test is equally
-    distributed among test cases, the execution cost could be potentially
-    improved by running tests in parallel (in contrast to the scenario
-    where only one test case dominates most of the execution time).
-}
-
-\subsection{Subjects}
-\label{sec:subjects}
-
-We are interested to evaluate non-trivial test suites on popular
-projects that are in activity. We used the Github's Search
-API~\cite{githubsearch} to fetch Java projects according to the
-following criteria: (1) the primary language must be Java\footnote{In
-case of projects in multiple languages, the Github API considers the
-predominant language as the primary language.}; (2) the project has at
-least 100 stars; (3) latest update on (or after) January 1st, 2016;
-(4) the \emph{readme} file contains the string \emph{mvn}.
-
-On Github, when a user adds a star to a project, s/he demonstrated
-appreciation and bookmarked it for later
-reference~\cite{github-stars}.  Although there is not a specific range
-for the number of stars, our criteria is an estimation to avoid
-trivial subjects: we assumed that Github users are likely to
-demonstrate interest on well-tested projects. The third criteria is a
-constraint to skip projects without recent activity. The fourth
-criteria is an approximation to find projects with Maven support. We
-used Maven as a reference due to its popularity on Java projects and
-to automate our evaluation scripts. The rationale is that if the
-string \emph{mvn} exists in the \emph{readme} file, it may represent a
-Maven call (\eg, to compile or test the project).
-Figure~\ref{fig:subject-query} illustrates the query as an HTTP
-request.
-
-\begin{figure}[h!]
-\centering
-\scriptsize
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    deletekeywords={true}
-}
-\begin{lstlisting}
-https://api.github.com/search/repositories?q=
-    stars:>=100+language:java+mvn%20in:readme+
-    pushed:>=2016-01-01+sort:stars
-
-\end{lstlisting}
-\caption{\label{fig:subject-query} Query to the Github API for
-    projects with the following criteria: (1) Java, (2) at least 100
-    stars, (3) updated on January 1st, 2016 (or later), (4) contains
-    the string \emph{mvn} in the \emph{readme} file. Output is
-    paginated in descending order of stars.}
-\end{figure}
-
-A Maven project may contain several submodules with multiple
-\emph{pom.xml} files. We considered only projects with a
-\emph{pom.xml} file located in the root directory.  As of December
-30th 2016, our search criteria returned 615 subjects. From the 615
-downloaded projects, 46 were not Maven projects, 27 were unable to
-fetch all dependencies (\eg, due to the usage of a private library),
-and 131 were in an unstable revision. Our final set consists in
-\numSubjs{} subjects.
-
-\subsection{Setup and Replication}
-\label{sec:setup}
-
-To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
-processor machine with 8 virtual CPUs (4 cores with 2 native threads
-each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
-(64-bit version). Software settings include \Comment{the Linux
-\emph{sysstat} package to measure performance, }\emph{git} to fetch
-subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
-and \emph{Python 3.4} to run our evaluation scripts. For replication,
-all source artifacts are publicly available at \Fix{create gh-pages},
-including supporting scripts (\eg, the script that test subjects and
-generates the raw data), and the full list of projects. \Comment{, and a
-\emph{Vagrantfile} to emulate our hardware and all software
-dependencies.}
-
-\subsection{Answering research question RQ1}
-\label{sec:rqone}
-
-\begin{itemize}
-    \item \emph{\RQA}
-\end{itemize}
-
-To evaluate the frequency of time-consuming regression tests, we
-considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
-compared the elapsed time to run their tests.
-Figure~\ref{fig:mvn-execution} shows the commands used in our script
-to test each subject. The main loop (lines 6-12) iterates over the
-list of subjects and invokes Maven in separated steps (lines 8-10). To
-avoid inflating the measured time, we first compile the source and
-test files (line 8), fetch all dependencies (line 9) and later, we run
-the tests in offline mode (line 10) to avoid package updates. In
-addition we randomly selected 100 Maven logs to inspect and identify
-non-related tasks (\eg, \emph{javadoc} generation and static
-analysis). We created a list of plugins (lines 1-4) to ignore them
-during the test execution.  Finally, we use a simple regular
-expression over the test output to extract the elapsed time (line 13).
-We executed this experiment \Fix{X} times in our dedicated server
-remotely via SSH with the operating system running only essential
-services (\eg, the SSH server). \Fix{Describe CPU isolation}
-
-\begin{figure}[h!]
-\centering
-\scriptsize
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    showstringspaces=false
-}
-\begin{lstlisting}[language=Bash]
-MAVEN_IGNORES="-Dmaven.javadoc.skip=true \
-    -Drat.skip=true -Djacoco.skip=true \
-    -Dcheckstyle.skip=true -Dfindbugs=true \
-    -Dcobertura.skip=true"
-
-for subj in $SUBJECTS; do
-    cd $SUBJECTS_HOME/$subj
-    mvn clean install -DskipTests $MAVEN_IGNORES
-    mvn dependency:go-offline
-    mvn -o test $MAVEN_IGNORES &> $LOG
-    cat $LOG | grep "\[INFO\] Total time:"
-done
-\end{lstlisting}
-\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
-    test suites. For each subject, we compile the source and test files, fetch
-    all dependencies, and execute the tests in offline mode ignoring
-    non-related tasks. Unnecessary commands are omitted for simplicity.}
-\end{figure}
-
-We grouped the subjects according to the execution time: tests that
-ran in less than one minute (\emph{short execution}), one to five
-minutes (\emph{medium execution}), and more than five minutes
-(\emph{long execution}). A previous work used a similar categorization
-except for the \emph{medium} group \cite{gligoric-etal-issta2015}.  We
-added a new group because \Fix{justify or use the same
-classification}.  Figure~\ref{fig:piechart-time} shows the proportion
-of subjects per group and Figure~\ref{fig:boxplots-time} shows the
-distribution of elapsed time for each group (boxplots).
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{2in}%
-    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
-    \end{minipage}%
-    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
-    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
-    5m$), and long execution ($5m \leq t$).}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{2.5in}%
-    \includegraphics[width=\textwidth]{plots/boxplots-timecost.pdf}
-    \end{minipage}%
-    \caption{\label{fig:boxplots-time} Distribution of time execution
-    per group. Outliers from \emph{Long} are ignored for better
-    readability.}
-\end{figure}
-
-Results indicate that a relatively high number of projects from the
-sample set (\ie, 29,2\%) requires at least five minutes to execute.
-The boxplot for the \emph{long} group reveals \Fix{dissect the
-boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
-group}.  It is important to mention that
-Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
-time: some tests may finish early due to a failure since the subjects
-were tested in a potentially unstable revision.
-
-\subsection{Answering research question RQ2}
-\label{sec:rqTwo}
-
-\begin{itemize}
-    \item \emph{\RQB}
-\end{itemize}
-
-To evaluate the presence of parallelization settings, we considered
-the \numSubjsRqTwo{} subjects from the groups \emph{long} and
-\emph{medium} identified in Section~\ref{sec:rqone}. We focused in
-these two groups because they represent costly test suites and are
-more likely that the developers may have used strategies to reduce the
-execution cost (\eg, running parts of the tests in different threads).
-We computed the frequence of the parallelism modes (see Section
-\ref{sec:modes}) using a semi-automatic approach: we first discover
-automatically the relevant configuration files and then we manually
-inspect them to eliminate false-positves (\eg, commented
-configuration).  Figure \Fix{N} describes the discovery step. We first
-list the paths of all build file and then we filter only the build
-files that contain any of the keywords, \CodeIn{forkMode},
-\CodeIn{forkCount}, or \CodeIn{parallel}. Notice that, for Maven
-projects, these any keywords exist in any possible parallelism
-configuration \Fix{cite surefire doc}.
-
 \begin{figure}[h!]
@@
     build files (\ie, \emph{pom.xml}) with potentially parallelization
-    settings. We first list all build files from a subject (line 3).
-    Then, we list the content of the file (\CodeIn{cat} command) and
-    redirect the output to filter only the lines that contains any of
-    the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
-    \CodeIn{forkCount} (\CodeIn{grep} command). If output is not empty
-    (line 7), we print the path from the current \emph{pom.xml} file.}
+    settings. We first find all build files from a subject (line 3).
+    Then, we iterate over each path (line 4), list the file content
+    (\CodeIn{cat} command), and redirect the output to filter only the
+    lines that contain any of the keywords \CodeIn{parallel},
+    \CodeIn{forkMode}, or \CodeIn{forkCount} (\CodeIn{grep} command).
+    If the output is not empty (line 7), we print the path from the
+    current \emph{pom.xml} file to inspect it later.}
 \end{figure}
-
-From the \numSubjsRqTwo{} subjects, there was a total of \Fix{X} build
-files and \Fix{Y} to inspect.
-
-\Fix{---------------------}
-
-From the 91 subjects, our script detected 43 subjects with evidence of
-parallel settings. After the inspection of 130 configuration files, we
-confirmed that \Fix{X} settings are real parallel configurations.
-These settings are related to \Fix{Y} subjects. It is important to
-notice that, \Fix{X}\% of the subjects (\emph{medium} and \emph{long}
-aggregated) did not explore low-level parallelism according to our
-criteria of matching keywords. After the inspection, this rate raises
-to \Fix{Y}\%. \Fix{elaborate: some projects doesn't use parallel
-features, so what?} Table~\ref{tab:inspection-table} summarizes our
-initial findings.
-
-\begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular*}{0.5\textwidth}{cccc}
-        \toprule
-        Group  & Subjects with Evidence & Config. Files & Config. Confirmed\\
-        \midrule
-        Long   & 22 / 35    & 77 / 1981       & \Fix{X} / 77\\%
-        Medium & 21 / 56    & 53 / 491        & \Fix{X} / 53\\%
-        \midrule 
-        Total  & 43 / 91    & 130 / 2472      & \Fix{X} / 130\\
-        \bottomrule
-    \end{tabular*}
-    \caption{\Fix{to-be-defined}}
-    \label{tab:inspection-table} 
-\end{table}
-
-\Fix{elaborate: write about the subjects that use parallelism - How do
-they use them? Would it be possible to measure the benefits? How the
-configs from Section~\ref{sec:modes} are distributed?}
-
-%%To evaluate the distribution of execution time per project, we sorted
-%%the test cases by decreasing order of elapsed time and calculated the
-%%number of tests executed in 90\% of the total time. Later, we reported
-%%the \Fix{balance} of execution time by dividing the number of tests
-%%that represents 90\% of the execution time by the number of tests
-%%cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
-%%collected the elapsed time from test cases for each generated report.
-%%Maven Surefire generates an XML report with execution information
-%%(\eg, number of skipped tests and elapsed time) per test suite
-%%\Jbc{Should I use the previous sentence as a footnote or should I
-%%delete it?}. We noticed that some test cases reported an elapsed time
-%%of zero: since the reported time is in milliseconds, some tests may
-%%execute in a shorter time. \Fix{..to be continued...}}. Results
-%%indicate that \Fix{...}.
-%%
-%%\begin{figure}[h!]
-%%    \centering
-%%    \includegraphics[width=0.4\textwidth]{results/plots/balance.pdf}
-%%    \caption{\Fix{balance}}
-%%\end{figure}
-
-%% \subsection{Answering research question RQ3}
-%% \label{sec:rqThree}
-%% 
-%% \begin{itemize}
-%%     \item \RQB
-%% \end{itemize}
-%% 
-%% To evaluate the distribution of CPU and IO intensive test suites from
-%% the sample set, we used the command \emph{sar} to monitor the system
-%% activity in background while tests ran. \emph{Sar} is a command that
-%% collects and reports statistics (\eg, percentage of IO waiting and
-%% usage of CPU in user mode) based on the kernel activity and it is
-%% highly configurable to collect detailed information (\eg, usage of a
-%% specific processor core or percentage of network interface
-%% utilization). We configured \emph{sar} to report \Fix{...explain how
-%% we executed and what fields we are interested}. \Fix{explain fields}.
-%% Figure \Fix{A} shows the distribution of subjects grouped in intervals
-%% of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}
-%% 
-%% \begin{figure}[h!]
-%%     \centering
-%%     \includegraphics[width=0.4\textwidth]{results/plots/cpuness.pdf}
-%%     \caption{\Fix{cpu usage}}
-%% \end{figure}
-%% 
-%% \Comment{we proposed the definition of \emph{cpuness}
-%% computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
-%% where \emph{user\_t} is the elapsed time of execution in \emph{user
-%% mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
-%% \emph{elapsed\_t} is the elapsed time to finish the execution. We
-%% measured the \emph{cpuness} of each regression test \Fix{...elaborate
-%% the meaning of cpuness} \Fix{Describe how I measured user, system and
-%% "wall" time}.  \Fix{Explain results}.  \Fix{show plots}}
-%% 
-%% \subsection{Answering research question RQ4}
-%% \label{sec:rqfour}
-%% 
-%% \begin{itemize}
-%%     \item \RQD
-%% \end{itemize}
-%% 
-%% \Fix{to appear...}
-%%

### 2017-01-03 paper/codes/evaluation.tex
pass on text and refactoring

--- 2017-01-03 paper/evaluation.tex
@@
-\section{Evaluation}
-\label{sec:eval}
-
-\Mar{I think the high-level goal should be something along the lines
-  of understanding prevalence of long test runs and main sources of
-  cost in open-source Java projects.  Intuitively, the problem should
-  come before the solution :).  Based on that, we study
-  parallelization of testing frameworks.  More precisely, we
-  investigage how prevalent test parallelization is, the potential for
-  improving execution cost, issues of flakiness that hinders use of
-  parallelization, and how to address those issues.}
-
-We evaluated the characteristics of regression tests in open-source
-development from a sample set of Java projects from Github. We are
-interested in understanding the prevalence of long test runs, the main
-sources of cost, and how do developers explore parallelism to improve
-execution performance. More specifically, we pose the following
-research questions:
-
-\newcommand{\RQA}{How prevalent is the occurence of time-consuming
-regression test suites in open-source projects?}
-\newcommand{\RQB}{How often are parallelization features present in
-build files?}
-\newcommand{\RQC}{What is the impact of parallalelization?}
-
-\newcommand{\RQD}{What factors contribute to improve performance
-through parallelization?\Jbc{Previously as "When does parallelization
-works and when it does not so great?"}}
-
-\newcommand{\RQE}{What are the limitations of parallelization?}
-
-\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
-\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
-\newcommand{\rqThree}{\textbf{RQ3.} \RQC}
-\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
-\newcommand{\rqFive}{\textbf{RQ5.} \RQE}
-
-\begin{itemize}
-    \item \rqOne
-    \item \rqTwo
-    \item \rqThree
-    \item \rqFour
-    \item \rqFive
-\end{itemize}
-
-%%\newcommand{\RQB}{What is the distribution of CPU and IO bound
-%%regression test suites from the sample set?}
-%%
-%%\newcommand{\RQC}{How uniformly distributed is the execution time
-%%across test cases in costly projects?}
-%%
-%%\newcommand{\RQD}{How often developers use the parallelism features
-%%from build systems to improve runtime performance?}
-
-The first research question addresses the prevalence of long-running
-test suites. We are interested to know if costly test suites are
-common in open-source projects.  The second research question
-addresses our interest in understanding if developers are aware of
-parallelization features from testing frameworks available
-out-of-the-box through build systems (\eg, run JUnit test cases in
-parallel using Maven Surefire) and what setting are more often used.
-The third research question addresses the impact of parallelism on the
-regression tests from our sample set. We are interested in compare the
-execution performance with different parallel settings (see
-Section~\ref{sec:modes}). The fourth research question addresses the
-characteristics of regression tests from the previous experiment.
-More specifically, we want to investigate if there is a relation
-between the balance of test execution (\ie, how uniformly distributed
-is the execution time across tests cases) and the usage of
-computational resources (\ie, if tests are mostly CPU or IO intense)
-that impacts the effectiveness of parallelization. Finally, the fifth
-research question discusses the limitations and insights to overcome
-the pitfalls of parallelization.
-
-\Comment{
-    \Fix{distribution of execution time per test case. For each subject
-    identified in the first research question, we investigate how
-    balanced is the cost of the test suite in contrast to the cost of
-    test cases and if there are subjects where the time cost is mostly
-    dominated by a small fraction of test cases.} \Fix{The third research
-    question addresses the distribution of regression tests according
-    to the use of computational resources.  We are interested in
-    investigating if regression test suites are CPU intensive and if there
-    are opportunities to improve performance. The RQ4 addresses}
-    \Fix{...elaborate...}
-
-    The rationale is that if the time cost of a regression test is equally
-    distributed among test cases, the execution cost could be potentially
-    improved by running tests in parallel (in contrast to the scenario
-    where only one test case dominates most of the execution time).
-}
-
-\subsection{Subjects}
-\label{sec:subjects}
-
-We are interested to evaluate non-trivial test suites on popular
-projects that are in activity. We used the Github's Search
-API~\cite{githubsearch} to fetch Java projects according to the
-following criteria: (1) the primary language must be Java\footnote{In
-case of projects in multiple languages, the Github API considers the
-predominant language as the primary language.}; (2) the project has at
-least 100 stars; (3) latest update on (or after) January 1st, 2016;
-(4) the \emph{readme} file contains the string \emph{mvn}.
-
-On Github, when a user adds a star to a project, s/he demonstrated
-appreciation and bookmarked it for later
-reference~\cite{github-stars}.  Although there is not a specific range
-for the number of stars, our criteria is an estimation to avoid
-trivial subjects: we assumed that Github users are likely to
-demonstrate interest on well-tested projects. The third criteria is a
-constraint to skip projects without recent activity. The fourth
-criteria is an approximation to find projects with Maven support. We
-used Maven as a reference due to its popularity on Java projects and
-to automate our evaluation scripts. The rationale is that if the
-string \emph{mvn} exists in the \emph{readme} file, it may represent a
-Maven call (\eg, to compile or test the project).
-Figure~\ref{fig:subject-query} illustrates the query as an HTTP
-request.
-
-\begin{figure}[h!]
-\centering
-\scriptsize
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    deletekeywords={true}
-}
-\begin{lstlisting}
-https://api.github.com/search/repositories?q=
-    stars:>=100+language:java+mvn%20in:readme+
-    pushed:>=2016-01-01+sort:stars
-
-\end{lstlisting}
-\caption{\label{fig:subject-query} Query to the Github API for
-    projects with the following criteria: (1) Java, (2) at least 100
-    stars, (3) updated on January 1st, 2016 (or later), (4) contains
-    the string \emph{mvn} in the \emph{readme} file. Output is
-    paginated in descending order of stars.}
-\end{figure}
-
-A Maven project may contain several submodules with multiple
-\emph{pom.xml} files. We considered only projects with a
-\emph{pom.xml} file located in the root directory.  As of December
-30th 2016, our search criteria returned 615 subjects. From the 615
-downloaded projects, 46 were not Maven projects, 27 were unable to
-fetch all dependencies (\eg, due to the usage of a private library),
-and 131 were in an unstable revision. Our final set consists in
-\numSubjs{} subjects.
-
-\subsection{Setup and Replication}
-\label{sec:setup}
-
-To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
-processor machine with 8 virtual CPUs (4 cores with 2 native threads
-each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
-(64-bit version). Software settings include \Comment{the Linux
-\emph{sysstat} package to measure performance, }\emph{git} to fetch
-subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
-and \emph{Python 3.4} to run our evaluation scripts. For replication,
-all source artifacts are publicly available at \Fix{create gh-pages},
-including supporting scripts (\eg, the script that test subjects and
-generates the raw data), and the full list of projects. \Comment{, and a
-\emph{Vagrantfile} to emulate our hardware and all software
-dependencies.}
-
-\subsection{Answering research question RQ1}
-\label{sec:rqone}
-
-\begin{itemize}
-    \item \emph{\RQA}
-\end{itemize}
-
-To evaluate the frequency of time-consuming regression tests, we
-considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
-compared the elapsed time to run their tests.
-Figure~\ref{fig:mvn-execution} shows the commands used in our script
-to test each subject. The main loop (lines 6-12) iterates over the
-list of subjects and invokes Maven in separated steps (lines 8-10). To
-avoid inflating the measured time, we first compile the source and
-test files (line 8), fetch all dependencies (line 9) and later, we run
-the tests in offline mode (line 10) to avoid package updates. In
-addition we randomly selected 100 Maven logs to inspect and identify
-non-related tasks (\eg, \emph{javadoc} generation and static
-analysis). We created a list of plugins (lines 1-4) to ignore them
-during the test execution.  Finally, we use a simple regular
-expression over the test output to extract the elapsed time (line 13).
-We executed this experiment \Fix{X} times in our dedicated server
-remotely via SSH with the operating system running only essential
-services (\eg, the SSH server). \Fix{Describe CPU isolation}
-
 \begin{figure}[h!]
@@
 \end{figure}
-
-We grouped the subjects according to the execution time: tests that
-ran in less than one minute (\emph{short execution}), one to five
-minutes (\emph{medium execution}), and more than five minutes
-(\emph{long execution}). A previous work used a similar categorization
-except for the \emph{medium} group \cite{gligoric-etal-issta2015}.  We
-added a new group because \Fix{justify or use the same
-classification}.  Figure~\ref{fig:piechart-time} shows the proportion
-of subjects per group and Figure~\ref{fig:boxplots-time} shows the
-distribution of elapsed time for each group (boxplots).
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{2in}%
-    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
-    \end{minipage}%
-    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
-    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
-    5m$), and long execution ($5m \leq t$).}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{2.5in}%
-    \includegraphics[width=\textwidth]{plots/boxplots-timecost.pdf}
-    \end{minipage}%
-    \caption{\label{fig:boxplots-time} Distribution of time execution
-    per group. Outliers from \emph{Long} are ignored for better
-    readability.}
-\end{figure}
-
-Results indicate that a relatively high number of projects from the
-sample set (\ie, 29,2\%) requires at least five minutes to execute.
-The boxplot for the \emph{long} group reveals \Fix{dissect the
-boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
-group}.  It is important to mention that
-Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
-time: some tests may finish early due to a failure since the subjects
-were tested in a potentially unstable revision.
-
-\subsection{Answering research question RQ2}
-\label{sec:rqTwo}
-
-\begin{itemize}
-    \item \emph{\RQB}
-\end{itemize}
-
-To evaluate the presence of parallelization settings, we considered
-the \numSubjsRqTwo{} subjects from the groups \emph{long} and
-\emph{medium} identified in Section~\ref{sec:rqone}. We focused in
-these two groups because they represent costly test suites and are
-more likely that the developers may have used strategies to reduce the
-execution cost (\eg, running parts of the tests in different threads).
-We computed the frequence of the parallelism modes (see Section
-\ref{sec:modes}) using a semi-automatic approach: we first discover
-automatically the relevant configuration files and then we manually
-inspect them to eliminate false-positves (\eg, commented
-configuration).  Figure \Fix{N} describes the discovery step. We first
-list the paths of all build file and then we filter only the build
-files that contain any of the keywords, \CodeIn{forkMode},
-\CodeIn{forkCount}, or \CodeIn{parallel}. Notice that, for Maven
-projects, these any keywords exist in any possible parallelism
-configuration \Fix{cite surefire doc}.
-
-\begin{figure}[h!]
-\centering
-\scriptsize
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    showstringspaces=false
-}
-\begin{lstlisting}[language=Bash]
-for subj in $SUBJECTS; do
-    subject_path="$SUBJECTS_HOME/$subj"
-    build_files=`find $subject_path -name pom.xml`
-    for build_file in $build_files; do
-        output=`cat $build_file | grep "parallel\
-                \|forkMode\|forkCount"`
-        if [ -z $output ]; then
-            echo $build_file
-        fi
-done
-\end{lstlisting}
-    \caption{\label{fig:discovery-step} Bash script to filter
-    build files (\ie, \emph{pom.xml}) with potentially parallelization
-    settings. We first list all build files from a subject (line 3).
-    Then, we list the content of the file (\CodeIn{cat} command) and
-    redirect the output to filter only the lines that contains any of
-    the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
-    \CodeIn{forkCount} (\CodeIn{grep} command). If output is not empty
-    (line 7), we print the path from the current \emph{pom.xml} file.}
-\end{figure}
-
-From the \numSubjsRqTwo{} subjects, there was a total of \Fix{X} build
-files and \Fix{Y} to inspect.
-
-\Fix{---------------------}
-
-From the 91 subjects, our script detected 43 subjects with evidence of
-parallel settings. After the inspection of 130 configuration files, we
-confirmed that \Fix{X} settings are real parallel configurations.
-These settings are related to \Fix{Y} subjects. It is important to
-notice that, \Fix{X}\% of the subjects (\emph{medium} and \emph{long}
-aggregated) did not explore low-level parallelism according to our
-criteria of matching keywords. After the inspection, this rate raises
-to \Fix{Y}\%. \Fix{elaborate: some projects doesn't use parallel
-features, so what?} Table~\ref{tab:inspection-table} summarizes our
-initial findings.
-
-\begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular*}{0.5\textwidth}{cccc}
-        \toprule
-        Group  & Subjects with Evidence & Config. Files & Config. Confirmed\\
-        \midrule
-        Long   & 22 / 35    & 77 / 1981       & \Fix{X} / 77\\%
-        Medium & 21 / 56    & 53 / 491        & \Fix{X} / 53\\%
-        \midrule 
-        Total  & 43 / 91    & 130 / 2472      & \Fix{X} / 130\\
-        \bottomrule
-    \end{tabular*}
-    \caption{\Fix{to-be-defined}}
-    \label{tab:inspection-table} 
-\end{table}
-
-\Fix{elaborate: write about the subjects that use parallelism - How do
-they use them? Would it be possible to measure the benefits? How the
-configs from Section~\ref{sec:modes} are distributed?}
-
-%%To evaluate the distribution of execution time per project, we sorted
-%%the test cases by decreasing order of elapsed time and calculated the
-%%number of tests executed in 90\% of the total time. Later, we reported
-%%the \Fix{balance} of execution time by dividing the number of tests
-%%that represents 90\% of the execution time by the number of tests
-%%cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
-%%collected the elapsed time from test cases for each generated report.
-%%Maven Surefire generates an XML report with execution information
-%%(\eg, number of skipped tests and elapsed time) per test suite
-%%\Jbc{Should I use the previous sentence as a footnote or should I
-%%delete it?}. We noticed that some test cases reported an elapsed time
-%%of zero: since the reported time is in milliseconds, some tests may
-%%execute in a shorter time. \Fix{..to be continued...}}. Results
-%%indicate that \Fix{...}.
-%%
-%%\begin{figure}[h!]
-%%    \centering
-%%    \includegraphics[width=0.4\textwidth]{results/plots/balance.pdf}
-%%    \caption{\Fix{balance}}
-%%\end{figure}
-
-%% \subsection{Answering research question RQ3}
-%% \label{sec:rqThree}
-%% 
-%% \begin{itemize}
-%%     \item \RQB
-%% \end{itemize}
-%% 
-%% To evaluate the distribution of CPU and IO intensive test suites from
-%% the sample set, we used the command \emph{sar} to monitor the system
-%% activity in background while tests ran. \emph{Sar} is a command that
-%% collects and reports statistics (\eg, percentage of IO waiting and
-%% usage of CPU in user mode) based on the kernel activity and it is
-%% highly configurable to collect detailed information (\eg, usage of a
-%% specific processor core or percentage of network interface
-%% utilization). We configured \emph{sar} to report \Fix{...explain how
-%% we executed and what fields we are interested}. \Fix{explain fields}.
-%% Figure \Fix{A} shows the distribution of subjects grouped in intervals
-%% of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}
-%% 
-%% \begin{figure}[h!]
-%%     \centering
-%%     \includegraphics[width=0.4\textwidth]{results/plots/cpuness.pdf}
-%%     \caption{\Fix{cpu usage}}
-%% \end{figure}
-%% 
-%% \Comment{we proposed the definition of \emph{cpuness}
-%% computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
-%% where \emph{user\_t} is the elapsed time of execution in \emph{user
-%% mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
-%% \emph{elapsed\_t} is the elapsed time to finish the execution. We
-%% measured the \emph{cpuness} of each regression test \Fix{...elaborate
-%% the meaning of cpuness} \Fix{Describe how I measured user, system and
-%% "wall" time}.  \Fix{Explain results}.  \Fix{show plots}}
-%% 
-%% \subsection{Answering research question RQ4}
-%% \label{sec:rqfour}
-%% 
-%% \begin{itemize}
-%%     \item \RQD
-%% \end{itemize}
-%% 
-%% \Fix{to appear...}
-%%

### 2017-01-03 paper/evaluation.tex
pass on text and refactoring

@@
 
-\begin{figure}[h!]
-\centering
-\scriptsize
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    showstringspaces=false
-}
-\begin{lstlisting}[language=Bash]
-MAVEN_IGNORES="-Dmaven.javadoc.skip=true \
-    -Drat.skip=true -Djacoco.skip=true \
-    -Dcheckstyle.skip=true -Dfindbugs=true \
-    -Dcobertura.skip=true"
-
-for subj in $SUBJECTS; do
-    cd $SUBJECTS_HOME/$subj
-    mvn clean install -DskipTests $MAVEN_IGNORES
-    mvn dependency:go-offline
-    mvn -o test $MAVEN_IGNORES &> $LOG
-    cat $LOG | grep "\[INFO\] Total time:"
-done
-\end{lstlisting}
-\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
-    test suites. For each subject, we compile the source and test files, fetch
-    all dependencies, and execute the tests in offline mode ignoring
-    non-related tasks. Unnecessary commands are omitted for simplicity.}
-\end{figure}
+\input{codes/evaluation}
 
@@
 the \numSubjsRqTwo{} subjects from the groups \emph{long} and
-\emph{medium} identified in Section~\ref{sec:rqone}. We focused in
-these two groups because they represent costly test suites and are
-more likely that the developers may have used strategies to reduce the
-execution cost (\eg, running parts of the tests in different threads).
-We computed the frequence of the parallelism modes (see Section
-\ref{sec:modes}) using a semi-automatic approach: we first discover
-automatically the relevant configuration files and then we manually
+\emph{medium} identified in Section~\ref{sec:rqone}. We focused on
+these two groups because given that costly test suites exist, we
+wanted to analyze if their maintainers are aware of parallelization
+settings and how they use these settings.  We computed the
+frequency of the parallelism modes (see Section \ref{sec:modes}) using
+a semi-automatic approach: we first discover automatically the
+relevant build files (\ie, \emph{pom.xml} files) and then we manually
 inspect them to eliminate false-positves (\eg, commented
 configuration).  Figure~\ref{fig:discovery-step} describes the
-discovery step. We first list the paths of all build file and then we
+discovery step: first, we list the paths of all build file and then we
 filter only the build files that contain any of the keywords,
 \CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
-that, for Maven projects, these any keywords exist in any possible
+that, for Maven projects, any of these keywords exist in any possible
 parallelism configuration \Fix{cite surefire doc}.
 
-\begin{figure}[h!]
-\centering
-\scriptsize
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    showstringspaces=false
-}
-\begin{lstlisting}[language=Bash]
-for subj in $SUBJECTS; do
-    subject_path="$SUBJECTS_HOME/$subj"
-    build_files=`find $subject_path -name pom.xml`
-    for build_file in $build_files; do
-        output=`cat $build_file | grep "parallel\
-                \|forkMode\|forkCount"`
-        if [ -z $output ]; then
-            echo $build_file
-        fi
-done
-\end{lstlisting}
-    \caption{\label{fig:discovery-step} Bash script to filter
-    build files (\ie, \emph{pom.xml}) with potentially parallelization
-    settings. We first list all build files from a subject (line 3).
-    Then, we list the content of the file (\CodeIn{cat} command) and
-    redirect the output to filter only the lines that contains any of
-    the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
-    \CodeIn{forkCount} (\CodeIn{grep} command). If output is not empty
-    (line 7), we print the path from the current \emph{pom.xml} file.}
-\end{figure}
+\input{codes/discovery}
 
-From the \numSubjsRqTwo{} subjects, there was a total of \Fix{X} build
-files and \Fix{Y} to inspect.
+From the \numSubjsRqTwo{} subjects, the discovery step checked \Fix{X}
+files and yielded \Fix{Y} files to inspect (distributed in \Fix{A}
+subjects). \Jbc{How many were valid configurations? Show a contingency
+table summarizing results for Medium/Long when we have the results}
+\Jbc{Show a histogram with the distribution of parallel modes}.
+
+\subsection{Answering research question RQ3}
+\label{sec:rqThree}
+
+\begin{itemize}
+    \item \emph{\RQC}
+\end{itemize}
+
+\Jbc{describe}.\Jbc{relevance}. \Jbc{methodology}.
 
 \Fix{---------------------}
-
-From the 91 subjects, our script detected 43 subjects with evidence of
-parallel settings. After the inspection of 130 configuration files, we
-confirmed that \Fix{X} settings are real parallel configurations.
-These settings are related to \Fix{Y} subjects. It is important to
-notice that, \Fix{X}\% of the subjects (\emph{medium} and \emph{long}
-aggregated) did not explore low-level parallelism according to our
-criteria of matching keywords. After the inspection, this rate raises
-to \Fix{Y}\%. \Fix{elaborate: some projects doesn't use parallel
-features, so what?} Table~\ref{tab:inspection-table} summarizes our
-initial findings.
-
-\begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular*}{0.5\textwidth}{cccc}
-        \toprule
-        Group  & Subjects with Evidence & Config. Files & Config. Confirmed\\
-        \midrule
-        Long   & 22 / 35    & 77 / 1981       & \Fix{X} / 77\\%
-        Medium & 21 / 56    & 53 / 491        & \Fix{X} / 53\\%
-        \midrule 
-        Total  & 43 / 91    & 130 / 2472      & \Fix{X} / 130\\
-        \bottomrule
-    \end{tabular*}
-    \caption{\Fix{to-be-defined}}
-    \label{tab:inspection-table} 
-\end{table}
-
-\Fix{elaborate: write about the subjects that use parallelism - How do
-they use them? Would it be possible to measure the benefits? How the
-configs from Section~\ref{sec:modes} are distributed?}
 

### 2017-01-03 paper/evaluation.tex
Reworked the purpose of RQ3
Updated evaluation motivation

@@
 
-\Mar{I think the high-level goal should be something along the lines
-  of understanding prevalence of long test runs and main sources of
-  cost in open-source Java projects.  Intuitively, the problem should
-  come before the solution :).  Based on that, we study
-  parallelization of testing frameworks.  More precisely, we
-  investigage how prevalent test parallelization is, the potential for
-  improving execution cost, issues of flakiness that hinders use of
-  parallelization, and how to address those issues.}
-
-We evaluated the characteristics of regression tests in open-source
-development from a sample set of Java projects from \github{}. We are
-interested in understanding the prevalence of long test runs, the main
-sources of cost, and how do developers explore parallelism to improve
-execution performance. More specifically, we pose the following
-research questions:
+We are interested in understanding the prevalence of time-consuming
+test suites and main sources of cost. We want to understand how the
+execution cost is distributed on test cases withing a test suite and
+how developers approach test execution. Based on that, we study
+parallelization of testing frameworks.  More precisely, we investigate
+how prevalent test parallelization is, the potential for improving
+execution cost, issues of flakiness that hinders use of
+parallelization, and how to address those issues.  More specifically,
+we pose the following research questions:
 
@@
 The third research question addresses the impact of parallelism on the
-regression tests from our sample set. We are interested in compare the
-execution performance with different parallel settings (see
-Section~\ref{sec:modes}). The fourth research question addresses the
+regression tests from our sample set. For subjects that use
+parallelization settings, we are interested in compare the execution
+performance when these settings are activated and deactivated (\ie,
+sequential execution). The fourth research question addresses the
 characteristics of regression tests from the previous experiment.
@@
 
-We are interested to evaluate non-trivial test suites on popular
-projects that are in activity. We used the \github{}'s search
+We evaluated the characteristics of regression tests in open-source
+development from a sample set of Java projects from \github{}.  We are
+interested to evaluate non-trivial test suites on popular projects
+that are in activity. We used the \github{}'s search
 API~\cite{githubsearch} to fetch Java projects according to the
 following criteria: (1) the primary language must be Java\footnote{In
-case of projects in multiple languages, the \github{} API considers the
-predominant language as the primary language.}; (2) the project has at
-least 100 stars; (3) latest update on (or after) January 1st, 2016;
-(4) the \emph{readme} file contains the string \emph{mvn}.
+case of projects in multiple languages, the \github{} API considers
+the predominant language as the primary language.}; (2) the project
+has at least 100 stars; (3) latest update on (or after) January 1st,
+2016; (4) the \emph{readme} file contains the string \emph{mvn}.
 

### 2017-01-03 paper/evaluation.tex
Added research question
Fixed RQs ordering

@@
 regression test suites in open-source projects?}
-\newcommand{\RQB}{How often are parallelization features in
+\newcommand{\RQB}{How the time cost from a test suite is distributed
+among the test cases?}
+\newcommand{\RQC}{How often are parallelization features in
 build files?}
-\newcommand{\RQC}{What is the impact of parallalelization?}
-
-\newcommand{\RQD}{What factors contribute to improve performance
+\newcommand{\RQD}{What is the impact of parallalelization?}
+\newcommand{\RQE}{What factors contribute to improve performance
 through parallelization?\Jbc{Previously as "When does parallelization
 works and when it does not so great?"}}
+\newcommand{\RQF}{What are the limitations of parallelization?}
 
-\newcommand{\RQE}{What are the limitations of parallelization?}
-
-\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
-\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
-\newcommand{\rqThree}{\textbf{RQ3.} \RQC}
-\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
-\newcommand{\rqFive}{\textbf{RQ5.} \RQE}
+\newcommand{\rqA}{\textbf{RQ1.} \RQA}
+\newcommand{\rqB}{\textbf{RQ2.} \RQB}
+\newcommand{\rqC}{\textbf{RQ3.} \RQC}
+\newcommand{\rqD}{\textbf{RQ4.} \RQD}
+\newcommand{\rqE}{\textbf{RQ5.} \RQE}
+\newcommand{\rqF}{\textbf{RQ6.} \RQF}
 
 \begin{itemize}
-    \item \rqOne
-    \item \rqTwo
-    \item \rqThree
-    \item \rqFour
-    \item \rqFive
+    \item \rqA
+    \item \rqB
+    \item \rqC
+    \item \rqD
+    \item \rqE
+    \item \rqF
 \end{itemize}
@@
 test suites. We are interested to know if costly test suites are
-common in open-source projects.  The second research question
-addresses our interest in understanding if developers are aware of
-parallelization features from testing frameworks available
-out-of-the-box through build systems (\eg, run JUnit test cases in
-parallel using Maven Surefire) and what setting are more often used.
-The third research question addresses the impact of parallelism on the
-regression tests from our sample set. For subjects that use
-parallelization settings, we are interested in compare the execution
-performance when these settings are activated and deactivated (\ie,
-sequential execution). The fourth research question addresses the
-characteristics of regression tests from the previous experiment.
-More specifically, we want to investigate if there is a relation
-between the balance of test execution (\ie, how uniformly distributed
-is the execution time across tests cases) and the usage of
-computational resources (\ie, if tests are mostly CPU or IO intense)
-that impacts the effectiveness of parallelization. Finally, the fifth
-research question discusses the limitations and insights to overcome
-the pitfalls of parallelization.
+common in open-source projects. The second research question addresses
+the balance of regression tests. We want to investigate how the time
+cost of a test suite is distributed among test cases. The third
+research question addresses our interest in understanding if
+developers are aware of parallelization features from testing
+frameworks available out-of-the-box through build systems (\eg, run
+JUnit test cases in parallel using Maven Surefire) and what setting
+are more often used.  The fourth research question addresses the
+impact of parallelism on the regression tests from our sample set. For
+subjects that use parallelization settings, we are interested in
+compare the execution performance when these settings are activated
+and deactivated (\ie, sequential execution). The fifth research
+question addresses the characteristics of regression tests from the
+previous experiment.  More specifically, we want to investigate if
+there is a relation between the balance of test execution (\ie, how
+uniformly distributed is the execution time across tests cases) and
+the usage of computational resources (\ie, if tests are mostly CPU or
+IO intense) that impacts the effectiveness of parallelization.
+Finally, the sixth research question discusses the limitations and
+insights to overcome the pitfalls of parallelization.
 
@@
 \subsection{Answering research question RQ2}
-\label{sec:rqTwo}
+\label{sec:rqB}
 
@@
 
+\Fix{to appear}
+
+\subsection{Answering research question RQ3}
+\label{sec:rqC}
+
+\begin{itemize}
+    \item \emph{\RQC}
+\end{itemize}
+
 To evaluate the presence of parallelization settings, we considered
 the \numSubjsRqTwo{} subjects from the groups \emph{long} and
-\emph{medium} identified in Section~\ref{sec:rqone}. We focused on
+\emph{medium} identified in Section~\ref{sec:rqA}. We focused on
 these two groups because given that costly test suites exist, we
@@
 
-\subsection{Answering research question RQ3}
-\label{sec:rqThree}
+\subsection{Answering research question RQ4}
+\label{sec:rqD}
 
 \begin{itemize}
-    \item \emph{\RQC}
+    \item \emph{\RQD}
 \end{itemize}

### 2017-01-03 paper/evaluation.tex
Fixed typos and added some reminders

@@
 how prevalent test parallelization is, the potential for improving
-execution cost, issues of flakiness that hinders use of
+execution cost, issues of flakiness that hinders the use of
 parallelization, and how to address those issues.  More specifically,
@@
 build files?}
-\newcommand{\RQD}{What is the impact of parallalelization?}
+\newcommand{\RQD}{What is the impact of parallelization?}
 \newcommand{\RQE}{What factors contribute to improve performance
@@
 common in open-source projects. The second research question addresses
-the balance of regression tests. We want to investigate how the time
-cost of a test suite is distributed among test cases. The third
+the balance of regression tests: we want to investigate how the time
+cost is distributed among test cases. The third
 research question addresses our interest in understanding if
@@
 frameworks available out-of-the-box through build systems (\eg, run
-JUnit test cases in parallel using Maven Surefire) and what setting
+JUnit test cases in parallel using Maven Surefire) and what settings
 are more often used.  The fourth research question addresses the
@@
 compare the execution performance when these settings are activated
-and deactivated (\ie, sequential execution). The fifth research
-question addresses the characteristics of regression tests from the
-previous experiment.  More specifically, we want to investigate if
-there is a relation between the balance of test execution (\ie, how
-uniformly distributed is the execution time across tests cases) and
-the usage of computational resources (\ie, if tests are mostly CPU or
-IO intense) that impacts the effectiveness of parallelization.
-Finally, the sixth research question discusses the limitations and
-insights to overcome the pitfalls of parallelization.
+and deactivated (\ie, sequential execution) to evaluate the benefits.
+\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
+addresses the characteristics of regression tests from the previous
+experiment.  More specifically, we want to investigate if there is a
+relation between the balance of test execution (\ie, how uniformly
+distributed is the execution time across tests cases) and the usage of
+computational resources (\ie, if tests are mostly CPU or IO intense)
+that impacts the effectiveness of parallelization}.  Finally, the
+sixth research question discusses the limitations and insights to
+overcome the pitfalls of parallelization.
 

### 2017-01-04 paper/evaluation.tex
Fixed subsection label
rephrased RQ
fixed typo

@@
 among the test cases?}
-\newcommand{\RQC}{How often are parallelization features in
+\newcommand{\RQC}{How often parallelization features appear in
 build files?}
@@
 \subsection{Answering research question RQ1}
-\label{sec:rqone}
+\label{sec:rqA}
 
@@
 relevant build files (\ie, \emph{pom.xml} files) and then we manually
-inspect them to eliminate false-positves (\eg, commented
+inspect them to eliminate false-positives (\eg, commented
 configuration).  Figure~\ref{fig:discovery-step} describes the

### 2017-01-04 paper/evaluation.tex
working on the RQ added

@@
 
-\Fix{to appear}
+We analyzed the distribution of time execution to investigate if most
+of the cost is dominated by a small subset of test cases or if the
+cost is nearly equally distributed. Regression tests that are well
+distributed may benefit from parallelism since more tests executes at
+the same time while the opposite scenario may require a different
+approach. In the later scenario, executing tests in parallel may have
+insignificant impact since a small subset of test cases dominates the
+execution.
+
+To evaluate the distribution of execution cost among test cases, we
+proposed the \emph{balance} statistic to indicate how equally
+distributed is the test execution. \Fix{show formula}.  \Fix{explain
+formula}
+
+Results indicated that \Fix{...elaborate...}. Figure~\Fix{N}
+summarizes the results. \Fix{show a histogram with the frequency of
+balance for the subjects analyzed}
 
@@
 %%
-%% \subsection{Answering research question RQ4}
-%% \label{sec:rqfour}
-%% 
-%% \begin{itemize}
-%%     \item \RQD
-%% \end{itemize}
-%% 
-%% \Fix{to appear...}
-%%

### 2017-01-04 paper/evaluation.tex
Reworke content from RQ2

--- 2017-01-04 paper/evaluation.tex
@@
 
-\Fix{to appear}
+We analyzed the distribution of time execution to investigate if most
+of the cost is dominated by a small subset of test cases or if the
+cost is nearly equally distributed. \Jbc{I shouldn't introduce
+parallelization arguments here... May I just proceed to the
+methodology?} \Fix{Regression tests that are well distributed may
+benefit from parallelism since more tests executes at the same time
+while the opposite scenario may require a different approach. In the
+later scenario, executing tests in parallel may have insignificant
+impact since a small subset of test cases dominates the execution.}
+
+To evaluate how uniformly distribution the execution cost is among
+test cases, we \Fix{...elaborate methodology...}
+
+Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
+different groups of subjects (\eg, test suites that are more equally
+distributed than others) I think the results from this RQ should be
+towards this direction}
 

### 2017-01-04 paper/evaluation.tex
Remainders....

@@
 
+\Jbc{Ensure to describe that: I re-executed the experiment 3 times (1
+remaining!), subjects that could not run the tests due to incompatible
+testing environment were removed (likely to happen for subjects that
+rely on database systems and other external factors), the exit status
+for all executions are consistent and removed the unstable subjects
+(flakiness)}
+
 We grouped the subjects according to the execution time: tests that
@@
 distribution of elapsed time for each group (boxplots).
+
+\Jbc{I will rework the results and plots}
 

### 2017-01-06 paper/evaluation.tex
pass on text

@@
 constraint to skip projects without recent activity. The fourth
-criteria is an approximation to find projects with Maven support. We
-used Maven as a reference due to its popularity on Java projects and
-to automate our evaluation scripts. The rationale is that if the
-string \emph{mvn} exists in the \emph{readme} file, it may represent a
-Maven call (\eg, to compile or test the project).
+criteria is an approximation to find projects with Maven support. The
+rationale is that if the string \emph{mvn} exists in the \emph{readme}
+file, it may represent a Maven call (\eg, to compile or test the
+project). We used Maven as a reference due to its popularity on Java
+projects and to automate our evaluation scripts.
 Figure~\ref{fig:subject-query} illustrates the query as an HTTP
@@
 30th 2016, our search criteria returned 615 subjects. From the 615
-downloaded projects, 46 were not Maven projects, 27 were unable to
-fetch all dependencies (\eg, due to the usage of a private library),
-and 131 were in an unstable revision. Our final set consists in
-\numSubjs{} subjects.
+downloaded projects, 46 were not Maven projects and 159 were in a
+unstable revision. From these 159 unstable subjects, \Jbc{elaborate
+what is unstable (eg, (1) how many could not resolve dependencies? (2)
+how many could not compile sources and tests? (3) could not run tests
+due to incompatible testing environment?}. Our final set consists in
+\numSubjs{} testable subjects.
 
@@
 \emph{sysstat} package to measure performance, }\emph{git} to fetch
-subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
-and \emph{Python 3.4} to run our evaluation scripts. For replication,
-all source artifacts are publicly available at \Fix{create gh-pages},
-including supporting scripts (\eg, the script that test subjects and
-generates the raw data), and the full list of projects. \Comment{, and a
+subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
+subjects. Our evaluation scripts depends on \emph{Python 3.4} and
+\emph{Bash} to execute.  For replication, all source artifacts are
+publicly available at \Fix{create gh-pages}, including supporting
+scripts (\eg, the script that test subjects and generates the raw
+data), and the full list of projects. \Comment{, and a
 \emph{Vagrantfile} to emulate our hardware and all software
@@
 non-related tasks (\eg, \emph{javadoc} generation and static
-analysis). We created a list of plugins (lines 1-4) to ignore them
+analysis). We created a list of plugins (lines 1-4) to ignore
 during the test execution.  Finally, we use a simple regular

### 2017-01-06 paper/evaluation.tex
updating rq1

@@
 expression over the test output to extract the elapsed time (line 13).
-We executed this experiment \Fix{X} times in our dedicated server
-remotely via SSH with the operating system running only essential
-services (\eg, the SSH server). \Fix{Describe CPU isolation}
+To avoid noise from OS events, we executed this experiment in our
+dedicated server remotely via SSH with the operating system running
+only essential services (\eg, the SSH server). \Fix{Describe CPU
+isolation}.
 
@@
 
-We grouped the subjects according to the execution time: tests that
-ran in less than one minute (\emph{short execution}), one to five
-minutes (\emph{medium execution}), and more than five minutes
-(\emph{long execution}). A previous work used a similar categorization
-except for the \emph{medium} group \cite{gligoric-etal-issta2015}.  We
-added a new group because \Fix{justify or use the same
-classification}.  Figure~\ref{fig:piechart-time} shows the proportion
-of subjects per group and Figure~\ref{fig:boxplots-time} shows the
-distribution of elapsed time for each group (boxplots).
-
-\Jbc{I will rework the results and plots}
+We grouped the subjects according the execution time (in average)
+using the same criteria of a previous work
+\cite{gligoric-etal-issta2015}: subjects that run in less than one
+minute were classified as \emph{short execution} and \emph{long
+execution} otherwise. Figure~\ref{fig:piechart-time} shows the
+proportion of subjects per group and figure~\ref{fig:boxplots-time}
+shows the distribution of elapsed time for each group (boxplots).
 
@@
     \end{minipage}%
-    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
-    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
-    5m$), and long execution ($5m \leq t$).}
+    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
+    time on test execution ($t$): short execution ($t < 1m$) and long
+    execution ($1m \leq t$).}
 \end{figure}

### 2017-01-06 paper/codes/discovery.tex
adjusted codes

@@
     for build_file in $build_files; do
-        output=`cat $build_file | grep "parallel\
-                \|forkMode\|forkCount"`
-        if [ -z $output ]; then
-            echo $build_file
-        fi
+        output=`cat $build_file | grep "parallel\|forkMode\|forkCount"`
+        if [ -z $output ]; then echo $build_file; fi
 done

### 2017-01-06 paper/codes/evaluation.tex
adjusted codes

@@
 \begin{lstlisting}[language=Bash]
-MAVEN_IGNORES="-Dmaven.javadoc.skip=true \
-    -Drat.skip=true -Djacoco.skip=true \
-    -Dcheckstyle.skip=true -Dfindbugs=true \
-    -Dcobertura.skip=true"
+MAVEN_IGNORES="-Dmaven.javadoc.skip=true -Drat.skip=true \
+    -Djacoco.skip=true -Dcheckstyle.skip=true \
+    -Dfindbugs=true -Dcobertura.skip=true"
 

### 2017-01-07 paper/evaluation.tex
Added new plots

@@
 Figure~\ref{fig:mvn-execution} shows the commands used in our script
-to test each subject. The main loop (lines 6-12) iterates over the
-list of subjects and invokes Maven in separated steps (lines 8-10). To
-avoid inflating the measured time, we first compile the source and
-test files (line 8), fetch all dependencies (line 9) and later, we run
-the tests in offline mode (line 10) to avoid package updates. In
-addition we randomly selected 100 Maven logs to inspect and identify
-non-related tasks (\eg, \emph{javadoc} generation and static
-analysis). We created a list of plugins (lines 1-4) to ignore
-during the test execution.  Finally, we use a simple regular
-expression over the test output to extract the elapsed time (line 13).
-To avoid noise from OS events, we executed this experiment in our
-dedicated server remotely via SSH with the operating system running
-only essential services (\eg, the SSH server). \Fix{Describe CPU
-isolation}.
+to test each subject. The main loop (lines 5-11) iterates over the
+list of subjects and invokes Maven in separated steps (lines 7-9). To
+avoid inflating the measured time we executed Maven in different
+steps: we first compiled the source and test files (line 7), made all
+dependencies available locally (line 8) and later, we ran the tests in
+offline mode (line 9) to bypass package updates. After the execution,
+we used a regular expression on the output log to extract the elapsed
+time (line 10). Before collecting the time cost, we executed all
+subjects and randomly selected 100 logs to inspect and identify
+non-related tasks (\eg, \emph{javadoc} generation and static analysis)
+to ignore during the experiment (lines 1-3).  To avoid noise from
+operating system events, we used a dedicated server remotely via SSH
+with the operating system running only essential services (\eg, the
+SSH server). In addition, we \Fix{describe CPU isolation with Kernel
+settings}.
 
@@
 
-We grouped the subjects according the execution time (in average)
-using the same criteria of a previous work
-\cite{gligoric-etal-issta2015}: subjects that run in less than one
-minute were classified as \emph{short execution} and \emph{long
-execution} otherwise. Figure~\ref{fig:piechart-time} shows the
-proportion of subjects per group and figure~\ref{fig:boxplots-time}
-shows the distribution of elapsed time for each group (boxplots).
+%% We grouped the subjects according the execution time (in average)
+%% using the same criteria of a previous work
+%% \cite{gligoric-etal-issta2015}: subjects that run in less than one
+%% minute were classified as \emph{short execution} and \emph{long
+%% execution} otherwise. Figure~\ref{fig:piechart-time} shows the
+%% proportion of subjects per group and figure~\ref{fig:boxplots-time}
+%% shows the distribution of elapsed time for each group (boxplots).
+%%
 
-\begin{figure}[h!]
+\begin{figure}[ht]
     \centering
-    \begin{minipage}{2in}%
-    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
-    \end{minipage}%
-    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
-    time on test execution ($t$): short execution ($t < 1m$) and long
-    execution ($1m \leq t$).}
+    \begin{subfigure}{0.21\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
+        \caption{\label{fig:rq1-barplot}}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}{0.25\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
+        \caption{\label{fig:rq1-boxplot}}
+
+    \end{subfigure}
+    \caption{Caption place holder}
 \end{figure}
 
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{2.5in}%
-    \includegraphics[width=\textwidth]{plots/boxplots-timecost.pdf}
-    \end{minipage}%
-    \caption{\label{fig:boxplots-time} Distribution of time execution
-    per group. Outliers from \emph{Long} are ignored for better
-    readability.}
-\end{figure}
-
-Results indicate that a relatively high number of projects from the
-sample set (\ie, 29,2\%) requires at least five minutes to execute.
-The boxplot for the \emph{long} group reveals \Fix{dissect the
-boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
-group}.  It is important to mention that
-Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
-time: some tests may finish early due to a failure since the subjects
-were tested in a potentially unstable revision.
+%% Results indicate that a relatively high number of projects from the
+%% sample set (\ie, 29,2\%) requires at least five minutes to execute.
+%% The boxplot for the \emph{long} group reveals \Fix{dissect the
+%% boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
+%% group}.  It is important to mention that
+%% Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
+%% time: some tests may finish early due to a failure since the subjects
+%% were tested in a potentially unstable revision.
 

### 2017-01-07 paper/evaluation.tex
updated rq1

@@
 
-\Jbc{Ensure to describe that: I re-executed the experiment 3 times (1
-remaining!), subjects that could not run the tests due to incompatible
-testing environment were removed (likely to happen for subjects that
-rely on database systems and other external factors), the exit status
-for all executions are consistent and removed the unstable subjects
-(flakiness)}
+\Jbc{Ensure to describe that: subjects that could not run the tests
+due to incompatible testing environment were removed (likely to happen
+for subjects that rely on database systems and other external
+factors), the exit status for all executions are consistent and
+removed the unstable subjects (flakiness)}
 
-%% We grouped the subjects according the execution time (in average)
-%% using the same criteria of a previous work
-%% \cite{gligoric-etal-issta2015}: subjects that run in less than one
-%% minute were classified as \emph{short execution} and \emph{long
-%% execution} otherwise. Figure~\ref{fig:piechart-time} shows the
-%% proportion of subjects per group and figure~\ref{fig:boxplots-time}
-%% shows the distribution of elapsed time for each group (boxplots).
-%%
+We ran each subject's tests three times and grouped them according to
+the time cost (in average): tests that run in less than a minute
+(\emph{short} group), tests than run in one minute and less than five
+minutes (\emph{medium} group), and tests that run in five (or more)
+minutes (\emph{long} group). We based our classification from a
+previous work \cite{gligoric-etal-issta2015} and added the
+\emph{medium} group due to the variability of the time cost from
+subjects out of the \emph{short} group. Figure~\ref{fig:rq1-boxplot}
+shows the time cost distribution of each group: the \emph{short} group
+is the most right skewed distribution with outliers closed to the
+\emph{medium} group and 50\% of the subjects run in less than 15
+seconds; the average from the \emph{medium} group is nearly two minutes
+and most of the subjects run in less than four minutes; most of the
+\emph{long} group runs in less than 25 minutes but has outliers that
+require more than 50 minutes to execute. Figure~\ref{fig:rq1-barplot}
+summarizes the proportion of subjects from each group.
 
@@
         \caption{\label{fig:rq1-boxplot}}
-
-    \end{subfigure}
-    \caption{Caption place holder}
+    \end{subfigure}%
+    \caption{(a) Subjects grouped by time cost ($t$): short run ($t <
+    1m$), medium run ($1m \le t < 5m$), and long run ($5m \le t$); (b)
+    Distribution of time cost by group.}
 \end{figure}
 
-%% Results indicate that a relatively high number of projects from the
-%% sample set (\ie, 29,2\%) requires at least five minutes to execute.
-%% The boxplot for the \emph{long} group reveals \Fix{dissect the
-%% boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
-%% group}.  It is important to mention that
-%% Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
-%% time: some tests may finish early due to a failure since the subjects
-%% were tested in a potentially unstable revision.
+Given that 19.3\% of the projects (\ie, \Fix{X} projects) are costly,
+we concluded that time-consuming regression test suites are relatively
+frequent in open-source projects.  It is important to mention that
+Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
+some tests may finish early due to a failure since the subjects were
+tested in a potentially unstable revision. \Jbc{How many executed
+completely? From the failed subjects, how much of the test suite was
+executed?}
 

### 2017-01-07 paper/evaluation.tex
Updated value

@@
 
-Given that 19.3\% of the projects (\ie, \Fix{X} projects) are costly,
+Given that 19.3\% of the projects (\ie, 61 projects) are costly,
 we concluded that time-consuming regression test suites are relatively

### 2017-01-07 paper/evaluation.tex
updated reminder

@@
 for subjects that rely on database systems and other external
-factors), the exit status for all executions are consistent and
-removed the unstable subjects (flakiness)}
+factors), the exit status for all executions are consistent and I
+removed flaky projs}
 

### 2017-01-07 paper/evaluation.tex
correcting myself: it's MEDIAN not AVG/MEAN, duhbash

@@
 \emph{medium} group and 50\% of the subjects run in less than 15
-seconds; the average from the \emph{medium} group is nearly two minutes
+seconds; the median from the \emph{medium} group is nearly two minutes
 and most of the subjects run in less than four minutes; most of the

### 2017-01-07 paper/evaluation.tex
updated eval

@@
 
-Given that 19.3\% of the projects (\ie, 61 projects) are costly,
+Given that 19.3\% of the projects (\ie, 82 projects) are costly,
 we concluded that time-consuming regression test suites are relatively
@@
 Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
-some tests may finish early due to a failure since the subjects were
-tested in a potentially unstable revision. \Jbc{How many executed
-completely? From the failed subjects, how much of the test suite was
-executed?}
+some tests may finish early due to a failure since a subject may be
+tested in a potentially unstable revision. From the \numSubjs{}
+projects, 286 passed all tests and 118 had failures.
 

### 2017-01-08 paper/evaluation.tex
Added CPU isolation

@@
 To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
-processor machine with 8 virtual CPUs (4 cores with 2 native threads
-each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
-(64-bit version). Software settings include \Comment{the Linux
-\emph{sysstat} package to measure performance, }\emph{git} to fetch
-subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
+processor machine with eight virtual CPUs (four cores with two native
+threads each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS
+Trusty Tahr} (64-bit version). Software settings include \Comment{the
+Linux \emph{sysstat} package to measure performance, }\emph{git} to
+fetch subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
 subjects. Our evaluation scripts depends on \emph{Python 3.4} and
@@
 with the operating system running only essential services (\eg, the
-SSH server). In addition, we \Fix{describe CPU isolation with Kernel
-settings}.
+SSH server). In addition, we configured the \CodeIn{isolcpus} option
+from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
+to execute our experiment and the remaining CPUs to run the operating
+system. By isolating a set of virtual CPUs, we prevent
+context-switching from the experiment processes and OS-related
+process.
 

### 2017-01-08 paper/codes/discovery.tex
Pass on text

@@
 \end{lstlisting}
-    \caption{\label{fig:discovery-step} Bash script to filter
-    build files (\ie, \emph{pom.xml}) with potentially parallelization
-    settings. We first find all build files from a subject (line 3).
-    Then, we iterate over each path (line 4), list the file content
-    (\CodeIn{cat} command), and redirect the output to filter only the
-    lines that contain any of the keywords \CodeIn{parallel},
-    \CodeIn{forkMode}, or \CodeIn{forkCount} (\CodeIn{grep} command).
-    If the output is not empty (line 7), we print the path from the
-    current \emph{pom.xml} file to inspect it later.}
+    \caption{\label{fig:discovery-step} Bash script to filter build
+    files for inspeciton: line 3 lists all \emph{pom.xml} files from a
+    subject; for each path, the  \CodeIn{cat} command lists the file
+    content and uses \CodeIn{grep} to filter only the matching lines
+    with the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
+    \CodeIn{forkCount} (lines 5-6); if the output is not empty (line
+    7), we print the current path.}
 \end{figure}

### 2017-01-08 paper/evaluation.tex
Pass on text

@@
 regression test suites in open-source projects?}
-\newcommand{\RQB}{How the time cost from a test suite is distributed
+\newcommand{\RQB}{How the time cost from a regression-test is distributed
 among the test cases?}
@@
 \emph{pom.xml} file located in the root directory.  As of December
-30th 2016, our search criteria returned 615 subjects. From the 615
-downloaded projects, 46 were not Maven projects and 159 were in a
-unstable revision. From these 159 unstable subjects, \Jbc{elaborate
-what is unstable (eg, (1) how many could not resolve dependencies? (2)
-how many could not compile sources and tests? (3) could not run tests
-due to incompatible testing environment?}. Our final set consists in
-\numSubjs{} testable subjects.
+30th 2016, our search criteria returned 615 subjects. From the
+\numSubjsTotal{} downloaded projects, 46 were not Maven projects and
+159 were in a unstable revision. From these 159 unstable subjects,
+\Jbc{elaborate what is unstable (eg, (1) how many could not resolve
+dependencies? (2) how many could not compile sources and tests? (3)
+could not run tests due to incompatible testing environment?}. Our
+final set consists in \numSubjs{} testable subjects.
 
@@
 
-To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
+To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
 processor machine with eight virtual CPUs (four cores with two native
-threads each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS
-Trusty Tahr} (64-bit version). Software settings include \Comment{the
-Linux \emph{sysstat} package to measure performance, }\emph{git} to
-fetch subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
-subjects. Our evaluation scripts depends on \emph{Python 3.4} and
-\emph{Bash} to execute.  For replication, all source artifacts are
-publicly available at \Fix{create gh-pages}, including supporting
-scripts (\eg, the script that test subjects and generates the raw
-data), and the full list of projects. \Comment{, and a
-\emph{Vagrantfile} to emulate our hardware and all software
-dependencies.}
+threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
+(64-bit version). Software settings include \Comment{the Linux
+\emph{sysstat} package to measure performance, }git to fetch subjects,
+Java 8 and Maven 3.3.9 to build and test subjects. Our evaluation
+scripts depends on Python 3.4 and Bash to execute and R to analyze the
+data. For replication, all source artifacts are publicly available at
+\Fix{create gh-pages}, including supporting scripts (\eg, the script
+that test subjects and generates the raw data), and the full list of
+projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
+and all software dependencies.}
 
@@
 system. By isolating a set of virtual CPUs, we prevent
-context-switching from the experiment processes and OS-related
-process.
+context-switching from experiment processes and OS-related processes.
 
@@
 
-\Jbc{Ensure to describe that: subjects that could not run the tests
+\Comment{\Jbc{Ensure to describe that: subjects that could not run the tests
 due to incompatible testing environment were removed (likely to happen
@@
 factors), the exit status for all executions are consistent and I
-removed flaky projs}
+removed flaky projs}}
 
@@
 the time cost (in average): tests that run in less than a minute
-(\emph{short} group), tests than run in one minute and less than five
-minutes (\emph{medium} group), and tests that run in five (or more)
-minutes (\emph{long} group). We based our classification from a
-previous work \cite{gligoric-etal-issta2015} and added the
-\emph{medium} group due to the variability of the time cost from
-subjects out of the \emph{short} group. Figure~\ref{fig:rq1-boxplot}
-shows the time cost distribution of each group: the \emph{short} group
-is the most right skewed distribution with outliers closed to the
-\emph{medium} group and 50\% of the subjects run in less than 15
-seconds; the median from the \emph{medium} group is nearly two minutes
-and most of the subjects run in less than four minutes; most of the
-\emph{long} group runs in less than 25 minutes but has outliers that
-require more than 50 minutes to execute. Figure~\ref{fig:rq1-barplot}
-summarizes the proportion of subjects from each group.
+(\shortg{} group), tests than run in one minute and less than five
+minutes (\medg{} group), and tests that run in five (or more) minutes
+(\longg{} group). We based our classification from a previous work
+\cite{gligoric-etal-issta2015} and added the \medg{} group due to the
+variability of the time cost from subjects out of the \shortg{} group.
+Figure~\ref{fig:rq1-boxplot} shows the time cost distribution of each
+group: the \shortg{} group is the most right skewed distribution with
+outliers closed to the \medg{} group and 50\% of the subjects run in
+less than 15 seconds; the median from the \medg{} group is nearly two
+minutes and most of the subjects run in less than four minutes; most
+of the \longg{} group runs in less than 25 minutes but has outliers
+that require more than 50 minutes to execute.
+Figure~\ref{fig:rq1-barplot} summarizes the proportion of subjects
+from each group.
 
@@
 
-Given that 19.3\% of the projects (\ie, 82 projects) are costly,
-we concluded that time-consuming regression test suites are relatively
-frequent in open-source projects.  It is important to mention that
+Given that \percentMedLongRunning{} of the projects are costly (\ie,
+\numMedLong{} projects from \medg{} and \longg{}), we concluded that
+time-consuming regression test suites are relatively frequent in
+open-source projects.  It is important to mention that
 Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
@@
 tested in a potentially unstable revision. From the \numSubjs{}
-projects, 286 passed all tests and 118 had failures.
+projects, 286 passed all tests and 118 had failures. \Jbc{elaborate
+failed subjects: how much \% of the tests failed?}
 
@@
 
-We analyzed the distribution of time execution to investigate if most
-of the cost is dominated by a small subset of test cases or if the
-cost is nearly equally distributed. \Jbc{I shouldn't introduce
-parallelization arguments here... May I just proceed to the
-methodology?} \Fix{Regression tests that are well distributed may
-benefit from parallelism since more tests executes at the same time
-while the opposite scenario may require a different approach. In the
-later scenario, executing tests in parallel may have insignificant
-impact since a small subset of test cases dominates the execution.}
-
-To evaluate how uniformly distribution the execution cost is among
-test cases, we \Fix{...elaborate methodology...}
+To evaluate the distribution of time cost, we analyzed the execution
+time of each test case from the \numMedLong{} subjects from the
+\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
+are interested to know whether most of the execution cost of a subject
+is dominated by a small subset of test cases or if the cost is nearly
+equally distributed. For each subject we calculated the relative
+standard deviation of the test cases: we collected the elapsed time of
+each individual test, calculated the standard deviation, and divided
+by the mean. \Jbc{I need to clarify the relationship
+"well/bad-balanced" regression test and relative standard deviation}
 
 Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
-different groups of subjects (\eg, test suites that are more equally
-distributed than others) I think the results from this RQ should be
-towards this direction}
+different groups of subjects}
+
+\Jbc{I shouldn't introduce parallelization arguments here but we have
+to address this at some point:
+Regression tests that are well distributed may benefit from
+parallelism since more tests executes at the same time while the
+opposite scenario may require a different approach. In the later
+scenario, executing tests in parallel may have insignificant impact
+since a small subset of test cases dominates the execution.}
 
@@
 To evaluate the presence of parallelization settings, we considered
-the \numSubjsRqTwo{} subjects from the groups \emph{long} and
-\emph{medium} identified in Section~\ref{sec:rqA}. We focused on
-these two groups because given that costly test suites exist, we
-wanted to analyze if their maintainers are aware of parallelization
-settings and how they use these settings.  We computed the
-frequency of the parallelism modes (see Section \ref{sec:modes}) using
-a semi-automatic approach: we first discover automatically the
-relevant build files (\ie, \emph{pom.xml} files) and then we manually
-inspect them to eliminate false-positives (\eg, commented
-configuration).  Figure~\ref{fig:discovery-step} describes the
-discovery step: first, we list the paths of all build file and then we
-filter only the build files that contain any of the keywords,
-\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
-that, for Maven projects, any of these keywords exist in any possible
-parallelism configuration \Fix{cite surefire doc}.
+the \numMedLong{} subjects from the \longg{} and \medg{} groups
+identified in Section~\ref{sec:rqA}. We focused on these two groups
+because given that costly test suites exist, we wanted to analyze if
+their maintainers are aware of parallelization settings and how they
+use these settings.  We computed the frequency of the parallelism
+modes (see Section \ref{sec:modes}) using a semi-automatic approach:
+we first discover automatically the relevant build files (\ie,
+\emph{pom.xml} files) and then we manually inspect the files to
+eliminate false-positives (\eg, a false-positive may occur if the file
+contains a commented configuration).  Figure~\ref{fig:discovery-step}
+describes the discovery step: first, we list the paths of all build
+file and then we filter only the build files that contain any of the
+keywords, \CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.
+Notice that, for Maven projects, any of these keywords exist in any
+possible parallelism configuration \Fix{cite surefire doc}.
 
@@
 
-From the \numSubjsRqTwo{} subjects, the discovery step checked \Fix{X}
+From the \numMedLong{} subjects, the discovery step checked \Fix{X}
 files and yielded \Fix{Y} files to inspect (distributed in \Fix{A}

### 2017-01-09 paper/evaluation.tex
updates

@@
 among the test cases?}
-\newcommand{\RQC}{How often parallelization features appear in
+\newcommand{\RQC}{How often parallelization settings appear in
 build files?}
@@
 \begin{lstlisting}
-https://api.github.com/search/repositories?q=
-    stars:>=100+language:java+mvn%20in:readme+
-    pushed:>=2016-01-01+sort:stars
-
+https://api.github.com/search/repositories?q=language:java
+        +stars:>=100+pushed:>=2016-01-01
+        +mvn%20in:readme+sort:stars
 \end{lstlisting}
@@
 
-A Maven project may contain several submodules with multiple
-\emph{pom.xml} files. We considered only projects with a
-\emph{pom.xml} file located in the root directory.  As of December
-30th 2016, our search criteria returned 615 subjects. From the
-\numSubjsTotal{} downloaded projects, 46 were not Maven projects and
-159 were in a unstable revision. From these 159 unstable subjects,
-\Jbc{elaborate what is unstable (eg, (1) how many could not resolve
-dependencies? (2) how many could not compile sources and tests? (3)
-could not run tests due to incompatible testing environment?}. Our
-final set consists in \numSubjs{} testable subjects.
+A Maven project may contain several sub-modules with multiple \pomf{}
+files. We considered only projects with a \pomf{} file located in the
+root directory.  As of December 30th 2016, our search criteria
+returned \numSubjsTotal{} subjects. From the \numSubjsTotal{}
+downloaded projects, 46 were not Maven projects (or did not have a
+\pomf{} in the root directory) and 159 were in a unstable revision.
+From these 159 unstable subjects, \Jbc{elaborate what is unstable (eg,
+(1) how many could not resolve dependencies? (2) how many could not
+compile sources and tests? (3) could not run tests due to incompatible
+testing environment?}. Our final set consists in \numSubjs{} testable
+subjects.
 
@@
 some tests may finish early due to a failure since a subject may be
-tested in a potentially unstable revision. From the \numSubjs{}
-projects, 286 passed all tests and 118 had failures. \Jbc{elaborate
-failed subjects: how much \% of the tests failed?}
+tested in a failing revision. From the \numSubjs{} projects, 286
+passed all tests and 118 had failures. \Jbc{elaborate failed subjects:
+how much \% of the tests failed?}
 
@@
 
-To evaluate the presence of parallelization settings, we considered
-the \numMedLong{} subjects from the \longg{} and \medg{} groups
-identified in Section~\ref{sec:rqA}. We focused on these two groups
-because given that costly test suites exist, we wanted to analyze if
-their maintainers are aware of parallelization settings and how they
-use these settings.  We computed the frequency of the parallelism
-modes (see Section \ref{sec:modes}) using a semi-automatic approach:
-we first discover automatically the relevant build files (\ie,
-\emph{pom.xml} files) and then we manually inspect the files to
-eliminate false-positives (\eg, a false-positive may occur if the file
-contains a commented configuration).  Figure~\ref{fig:discovery-step}
-describes the discovery step: first, we list the paths of all build
-file and then we filter only the build files that contain any of the
-keywords, \CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.
-Notice that, for Maven projects, any of these keywords exist in any
-possible parallelism configuration \Fix{cite surefire doc}.
+\Jbc{I'm currently considering only the long group but as soon as I
+have the remaining results, I will update the plots} To evaluate the
+presence of parallelization settings, we considered the \numMedLong{}
+subjects from the \longg{} and \medg{} groups identified in
+Section~\ref{sec:rqA}. We focused on these two groups because given
+that costly test suites exist, we wanted to investigate if their
+maintainers are aware of parallelization settings and how they use
+these settings (see Section \ref{sec:modes}).  We computed the
+frequency of the parallelism modes using a two-steps approach: the
+first step (discovery) automatically finds relevant build files
+(\ie, \pomf{} files with parallelization settings); the second step
+(inspection) consists in a manual inspection to confirm the presence
+of parallelism settings in the build file and classify them according
+to the parallelism level (see Section \ref{sec:modes}).
+Figure~\ref{fig:discovery-step} describes the discovery step: we list
+the paths of all build files and filter only the files that contain
+any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
+\CodeIn{parallel}.  Notice that, for Maven projects, any of these
+keywords exist in any possible parallel setting \Fix{cite surefire
+doc}. Our first step is complete but is not sound since the line that
+matches one of keywords may not represent part of a real setting (\eg,
+comments).  We eliminate false-positives in the confirmation step.
+From the \numMedLong{} subjects, the discovery step found 2853 files
+and filtered 109 relevant files. Later, from the 109 relevant files,
+we confirmed \Fix{M} valid settings from \Fix{X} subjects.
+Table~\ref{tab:inspection-table} summarizes the results from the file
+inspection and Figure~\ref{fig:freqmodes} shows the distribution of
+parallelism modes from the \Fix{M} settings.
 
@@
 
-From the \numMedLong{} subjects, the discovery step checked \Fix{X}
-files and yielded \Fix{Y} files to inspect (distributed in \Fix{A}
-subjects). \Jbc{How many were valid configurations? Show a contingency
-table summarizing results for Medium/Long when we have the results}
-\Jbc{Show a histogram with the distribution of parallel modes}.
+\begin{table}[h!]
+    \centering
+    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccccc}
+        \toprule%
+        Group  & Build Files & Filtered files & Settings & Subjects \\%
+        \midrule%
+        Long   & 1613 & 79 & \Fix{X} & \Fix{X}\\%
+        Medium & 1240 & 30 & \Fix{X} & \Fix{X}\\%
+        \midrule%
+        Total  & 2853 & 109 & \Fix{X} & \Fix{X}\\%
+        \bottomrule%
+    \end{tabular*}
+    \caption{\Fix{to-be-defined}}
+    \label{tab:inspection-table} 
+\end{table}
+
+\begin{figure}[h!]
+    \centering
+    \Fix{to appear}
+    \caption{\label{fig:freqmodes}Distribution of parallelism modes
+    identified in \Fix{M} }
+\end{figure}
 

### 2017-01-09 paper/evaluation.tex
updated rq3

@@
 
-\Jbc{I'm currently considering only the long group but as soon as I
-have the remaining results, I will update the plots} To evaluate the
-presence of parallelization settings, we considered the \numMedLong{}
-subjects from the \longg{} and \medg{} groups identified in
-Section~\ref{sec:rqA}. We focused on these two groups because given
-that costly test suites exist, we wanted to investigate if their
-maintainers are aware of parallelization settings and how they use
-these settings (see Section \ref{sec:modes}).  We computed the
-frequency of the parallelism modes using a two-steps approach: the
-first step (discovery) automatically finds relevant build files
-(\ie, \pomf{} files with parallelization settings); the second step
+To evaluate the presence of parallelization settings, we considered
+the \numMedLong{} subjects from the \longg{} and \medg{} groups
+identified in Section~\ref{sec:rqA}. We focused on these two groups
+because given that costly test suites exist, we wanted to investigate
+if their maintainers are aware of parallelization settings and how
+they use these settings (see Section \ref{sec:modes}).  We computed
+the frequency of the parallelism modes using a two-steps approach: the
+first step (discovery) automatically finds relevant build files (\ie,
+\pomf{} files with parallelization settings); the second step
 (inspection) consists in a manual inspection to confirm the presence
@@
 we confirmed \Fix{M} valid settings from \Fix{X} subjects.
+\Jbc{Elaborate results}
 Table~\ref{tab:inspection-table} summarizes the results from the file
@@
 
-\begin{table}[h!]
+\begin{table}[ht!]
     \centering
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
-    \Fix{to appear}
+    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
     \caption{\label{fig:freqmodes}Distribution of parallelism modes
-    identified in \Fix{M} }
+    identified in \Fix{M} \Jbc{Currently mocked data}}
 \end{figure}
+
+\Jbc{Conclusion and relate the results to the
+RQ...........................................}
 

### 2017-01-09 paper/evaluation.tex
pass on text

@@
 Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
-different groups of subjects}
+different groups of subjects}\Fix{TODO: collect data + compute the
+statistic, create a scatter plot to identify groups of subjects}
 
@@
 comments).  We eliminate false-positives in the confirmation step.
+
 From the \numMedLong{} subjects, the discovery step found 2853 files
@@
 we confirmed \Fix{M} valid settings from \Fix{X} subjects.
-\Jbc{Elaborate results}
-Table~\ref{tab:inspection-table} summarizes the results from the file
-inspection and Figure~\ref{fig:freqmodes} shows the distribution of
-parallelism modes from the \Fix{M} settings.
+\Jbc{Elaborate results} Table~\ref{tab:inspection-table} summarizes
+the results from the file inspection and Figure~\ref{fig:freqmodes}
+shows the distribution of parallelism modes from the \Fix{M} settings.
 
@@
     \caption{\label{fig:freqmodes}Distribution of parallelism modes
-    identified in \Fix{M} \Jbc{Currently mocked data}}
+    identified in \Fix{M} projects\Jbc{Currently mocked data}}
 \end{figure}

### 2017-01-10 paper/evaluation.tex
updating RQ3
updated plot from rq3
adjusted table and updated macros

@@
 to the parallelism level (see Section \ref{sec:modes}).
-Figure~\ref{fig:discovery-step} describes the discovery step: we list
+Figure \Fix{removed} describes the discovery step: we list
 the paths of all build files and filter only the files that contain
@@
 
-\input{codes/discovery}
-
 \begin{table}[ht!]
     \centering
-    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccccc}
-        \toprule%
-        Group  & Build Files & Filtered files & Settings & Subjects \\%
+    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
+        \toprule
+        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
+                               &                             &  / false-positives &       / total\\%
         \midrule%
-        Long   & 1613 & 79 & \Fix{X} & \Fix{X}\\%
-        Medium & 1240 & 30 & \Fix{X} & \Fix{X}\\%
+        Long   & 1613 & 79/\Fix{z} & \Fix{X}/\numLong{}\\%
+        Medium & 1240 & 30/\Fix{y} & 22/\numMed{}\\%
         \midrule%
-        Total  & 2853 & 109 & \Fix{X} & \Fix{X}\\%
+        Total  & 2853 & 109/\Fix{z+y} & \Fix{w}/\numMedLong{}\\%
         \bottomrule%
@@
     \caption{\label{fig:freqmodes}Distribution of parallelism modes
-    identified in \Fix{M} projects\Jbc{Currently mocked data}}
+    identified in \Fix{M} projects\Jbc{Currently medium and partially
+    the long group...}}
 \end{figure}

### 2017-01-10 paper/evaluation.tex
updated columns
Updated values from table 1
updated notation
updated table
updates and pass on rq3

@@
 
-To evaluate the presence of parallelization settings, we considered
-the \numMedLong{} subjects from the \longg{} and \medg{} groups
-identified in Section~\ref{sec:rqA}. We focused on these two groups
-because given that costly test suites exist, we wanted to investigate
-if their maintainers are aware of parallelization settings and how
-they use these settings (see Section \ref{sec:modes}).  We computed
-the frequency of the parallelism modes using a two-steps approach: the
-first step (discovery) automatically finds relevant build files (\ie,
-\pomf{} files with parallelization settings); the second step
-(inspection) consists in a manual inspection to confirm the presence
-of parallelism settings in the build file and classify them according
-to the parallelism level (see Section \ref{sec:modes}).
-Figure \Fix{removed} describes the discovery step: we list
-the paths of all build files and filter only the files that contain
-any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
-\CodeIn{parallel}.  Notice that, for Maven projects, any of these
-keywords exist in any possible parallel setting \Fix{cite surefire
-doc}. Our first step is complete but is not sound since the line that
-matches one of keywords may not represent part of a real setting (\eg,
-comments).  We eliminate false-positives in the confirmation step.
+To evaluate the presence of parallelization settings (see Section
+\ref{sec:modes}), we considered the \numMedLong{} subjects from the
+\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
+focused in these two groups because given that costly test suites
+exist, we investigated if the maintainers are aware of parallelization
+settings.
 
-From the \numMedLong{} subjects, the discovery step found 2853 files
-and filtered 109 relevant files. Later, from the 109 relevant files,
-we confirmed \Fix{M} valid settings from \Fix{X} subjects.
-\Jbc{Elaborate results} Table~\ref{tab:inspection-table} summarizes
-the results from the file inspection and Figure~\ref{fig:freqmodes}
-shows the distribution of parallelism modes from the \Fix{M} settings.
+\Jbc{methodology is poorly described...}
+\Fix{
+We computed the frequency of the
+parallelism modes using a two-steps approach: the first step
+(discovery) automatically finds relevant build files (\ie, \pomf{}
+files with parallelization settings); the second step (inspection)
+consists in a manual inspection to confirm the presence of parallelism
+settings in the build file and classify them according to the
+parallelism level.  Figure \Fix{removed}
+describes the discovery step: we list the paths of all build files and
+filter only the files that contain any of the keywords
+\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.  Notice
+that, for Maven projects, any of these keywords exist in any possible
+parallel setting \Fix{cite surefire doc}. Our first step is complete
+but is not sound since the line that matches one of keywords may not
+represent part of a real setting (\eg, comments).  We eliminate
+false-positives in the confirmation step.
+}
+
+\newcommand{\pomMedLong}{2851}
+
+\Jbc{results from table}From the \numMedLong{} subjects, we found
+\pomMedLong{} \pomf{} files and selected the 109 files that matched
+with any of the configuration keywords (\ie, \CodeIn{forkCount},
+\CodeIn{forkMode}, and \CodeIn{parallel}).  From these 109 build
+files, we eliminated six false-positives: two were names of project
+modules (\eg, \emph{camel-cookbook-parallel-processing}); one was part
+of a comment; three were commented configurations. The 106 build files
+with valid configurations are distributed in 41 projects from our
+sample.  Table~\ref{tab:inspection-table} summarizes our results.
 
@@
         \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
-                               &                             &  / false-positives &       / total\\%
+                               &                             &  (false-positives) &       / total\\%
         \midrule%
-        Long   & 1613 & 79/\Fix{z} & \Fix{X}/\numLong{}\\%
-        Medium & 1240 & 30/\Fix{y} & 22/\numMed{}\\%
+        Long   & 1613 & 79 (1) & 19/\numLong{}\\%
+        Medium & 1238 & 30 (5) & 22/\numMed{}\\%
         \midrule%
-        Total  & 2853 & 109/\Fix{z+y} & \Fix{w}/\numMedLong{}\\%
+        Total  & \pomMedLong{} & 109 (6) & 41/\numMedLong{}\\%
         \bottomrule%
     \end{tabular*}
-    \caption{\Fix{to-be-defined}}
+    \caption{Presence of parallel configurations in build files from
+    projects with time-consuming tests. \Fix{explain columns}}
     \label{tab:inspection-table} 

### 2017-01-10 paper/evaluation.tex
pass on RQ3

@@
 To evaluate the presence of parallelization settings (see Section
-\ref{sec:modes}), we considered the \numMedLong{} subjects from the
-\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
-focused in these two groups because given that costly test suites
-exist, we investigated if the maintainers are aware of parallelization
-settings.
+\ref{sec:modes}), we considered all projects classified as \medg{} and
+\longg{}-running, a total of \numMedLong{} subjects (see
+Figure~\ref{fig:rq1-barplot}). To reduce noise we did not consider
+projects with \shortg{}-running test suites as we observed\Mar{please,
+  confirm} that those projects often\Mar{adjust} do not use
+parallelism; including them would favor sequential execution in our
+analysis.
 
-\Jbc{methodology is poorly described...}
-\Fix{
-We computed the frequency of the
-parallelism modes using a two-steps approach: the first step
-(discovery) automatically finds relevant build files (\ie, \pomf{}
-files with parallelization settings); the second step (inspection)
-consists in a manual inspection to confirm the presence of parallelism
-settings in the build file and classify them according to the
-parallelism level.  Figure \Fix{removed}
-describes the discovery step: we list the paths of all build files and
-filter only the files that contain any of the keywords
-\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.  Notice
-that, for Maven projects, any of these keywords exist in any possible
-parallel setting \Fix{cite surefire doc}. Our first step is complete
-but is not sound since the line that matches one of keywords may not
-represent part of a real setting (\eg, comments).  We eliminate
-false-positives in the confirmation step.
-}
+%% We
+%% focused in these two groups because given that costly test suites
+%% exist, we investigated if the maintainers are aware of parallelization
+%% settings.
 
-\newcommand{\pomMedLong}{2851}
+To answer RQ3\Mar{use macro} we initially mined build files (\ie,
+\pomf{}) that contain parallelization keywords, namely
+\CodeIn{forkMode}, \CodeIn{forkCount}, and \CodeIn{parallel}.
+According to the Maven surefire documentation\Fix{cite surefire doc},
+any configuration to run tests in parallel must contain one of these
+keywords. This mining step, however, is not sound as a matching
+project may not indicate a project with a valid configuration for
+running tests in parallel.  False positive can happen because of
+comments, for instance.  To eliminate the cases of false positives and
+also to categorize true positive cases, we complemented the initial
+mining step with a manual inspection of files.
 
-\Jbc{results from table}From the \numMedLong{} subjects, we found
-\pomMedLong{} \pomf{} files and selected the 109 files that matched
-with any of the configuration keywords (\ie, \CodeIn{forkCount},
-\CodeIn{forkMode}, and \CodeIn{parallel}).  From these 109 build
-files, we eliminated six false-positives: two were names of project
-modules (\eg, \emph{camel-cookbook-parallel-processing}); one was part
-of a comment; three were commented configurations. The 106 build files
-with valid configurations are distributed in 41 projects from our
-sample.  Table~\ref{tab:inspection-table} summarizes our results.
+%% settings); the second step (inspection) consists in a manual
+%% inspection to confirm the presence of parallelism settings in the
+%% build file and classify them according to the parallelism level.
+%% Figure \Fix{removed} describes the discovery step: we list the paths
+%% of all build files and filter only the files that contain any of the
 
-\begin{table}[ht!]
+Figure~\ref{tab:inspection-table} summarizes our results.  Column
+``Group'' indicates the group of projects according to their time
+cost.\Mar{quickly explain other columns}
+
+%% summarize observations...
+From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
+where 109\Mar{use macro} of those files match one of the keywords
+mentioned above.  From these 109\Mar{use macro} build files, we
+eliminated six false-positives: two were names of project modules
+(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
+comment, and three were commented configurations. The 106\Fix{fix
+  this} build files with valid configurations are distributed across
+41\Mar{use macro} projects from our sample.  \emph{From these results
+  we found that $\sim$51\% of medium and long-running projects do not
+  use parallel features to run test suites.}\Mar{please make it
+  consistent with research question}\Mar{explain this is
+  over(under)-estimated...}
+
+\begin{figure}[ht!]
     \centering
@@
     \label{tab:inspection-table} 
-\end{table}
+\end{figure}
 
-\begin{figure}[ht!]
+\subsubsection{Distribution of parallel modes}
+
+\Jbc{Conclusion and relate the results to the
+  RQ...........................................}
+
+\begin{figure}[h!]
     \centering
@@
 \end{figure}
-
-\Jbc{Conclusion and relate the results to the
-RQ...........................................}
 

### 2017-01-11 paper/evaluation.tex
pass in RQ2 (not done)

@@
 
-To evaluate the distribution of time cost, we analyzed the execution
-time of each test case from the \numMedLong{} subjects from the
-\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
-are interested to know whether most of the execution cost of a subject
-is dominated by a small subset of test cases or if the cost is nearly
-equally distributed. For each subject we calculated the relative
-standard deviation of the test cases: we collected the elapsed time of
-each individual test, calculated the standard deviation, and divided
-by the mean. \Jbc{I need to clarify the relationship
-"well/bad-balanced" regression test and relative standard deviation}
+Section~\ref{sec:rqA} showed that medium and long-running projects are
+not uncommon; they account to nearly \percentMedLongRunning{} of the
+\numSubjsTotal{} projects we analyzed.  A key factor to determine if
+low-level parallelism will be effective to speedup test execution is
+to identify whether or not a small fraction of tests dominate test
+suite execution time.  If that is the case, it is unlikely that test
+suite parallelization will help as a test artifact is the smallest
+working unit in test frameworks (see Section~\ref{sec:frameworks}).
+Ideally, one would hope that time is distributed uniformly across
+tests in the suite.
+
+%% We are interested to know whether
+%% most of the execution cost of a subject is dominated by a small subset
+%% of test cases or if the cost is nearly equally distributed.
+
+To evaluate the distribution of time, we analyzed the execution time
+for the \numMedLong{} projects from the \longg{} and \medg{} groups
+(see Section~\ref{sec:rqA}).
+
+For each subject we calculated the
+relative standard deviation of the test cases: we collected the
+elapsed time of each individual test, calculated the standard
+deviation, and divided by the mean. \Jbc{I need to clarify the
+  relationship "well/bad-balanced" regression test and relative
+  standard deviation}
 

### 2017-01-11 paper/evaluation.tex
pass on RQ2

@@
   regression test suites in open-source projects?}
-\newcommand{\RQB}{How the time cost from a regression-test is distributed
-among the test cases?}
-\newcommand{\RQC}{How often parallelization settings appear in
-build files?}
-\newcommand{\RQD}{What is the impact of parallelization?}
+\newcommand{\RQB}{How time is distributed across test cases?}
+\newcommand{\RQC}{How often parallelization settings appear in build
+  files?}  \newcommand{\RQD}{What is the impact of parallelization?}
 \newcommand{\RQE}{What factors contribute to improve performance
-through parallelization?\Jbc{Previously as "When does parallelization
-works and when it does not so great?"}}
+  through parallelization?\Jbc{Previously as "When does
+    parallelization works and when it does not so great?"}}
 \newcommand{\RQF}{What are the limitations of parallelization?}
@@
 not uncommon; they account to nearly \percentMedLongRunning{} of the
-\numSubjsTotal{} projects we analyzed.  A key factor to determine if
-low-level parallelism will be effective to speedup test execution is
-to identify whether or not a small fraction of tests dominate test
-suite execution time.  If that is the case, it is unlikely that test
-suite parallelization will help as a test artifact is the smallest
-working unit in test frameworks (see Section~\ref{sec:frameworks}).
-Ideally, one would hope that time is distributed uniformly across
-tests in the suite.
+\numSubjsTotal{} projects we analyzed.  However, use of parallelism
+does not assure speedups on those projects.  We analyzed one sensible
+factor that is critical to the effectiveness of parallelism: the
+amount of tests that dominate execution time.  In the limit, if cost
+is dominated by a single test, it is unlikely that parallelization
+will be beneficial as a test method is the smallest working unit in
+test frameworks (see Section~\ref{sec:frameworks}).
 
@@
 
-To evaluate the distribution of time, we analyzed the execution time
-for the \numMedLong{} projects from the \longg{} and \medg{} groups
-(see Section~\ref{sec:rqA}).
+We evaluated the dispersion of time distributions (one distribution
+per project) to aswer research question RQ2.  To measure dispersion
+\emph{across} projects we used Relative Standard Deviation
+(RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were to
+analyze each project in isolation, the standard deviation of a
+distribution ($\sigma$) would suffice to quantify how dispersed the
+(time) distribution is.  However, in our case, we would like to be
+able to compare and summarize dispersion across projects.  The RSD,
+which is obtained dividing the standard deviation by the mean ($\mu$)
+of a distribution, provides such normalization effect.  This metric
+provides a lower bound (zero) but not an upper bound (somewhere close
+to 1).  The smaller (larger) the value of RSD the more (less) uniform
+the distribution is.  Consequently, ignoring other factors that affect
+performance of parallelization (e.g., CPU/IO ratio), the lower the
+value of RSD the more parallelizable a test suite should be.
 
-For each subject we calculated the
-relative standard deviation of the test cases: we collected the
-elapsed time of each individual test, calculated the standard
-deviation, and divided by the mean. \Jbc{I need to clarify the
-  relationship "well/bad-balanced" regression test and relative
-  standard deviation}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.5\textwidth]{R/relativeSD.pdf}  
+  \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
+    across projects.\Fix{update (mocked) data}}
+\end{figure}
 
-Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
-different groups of subjects}\Fix{TODO: collect data + compute the
-statistic, create a scatter plot to identify groups of subjects}
+Figure~\ref{fig:relativesd} shows the distribution of RSD across
+medium and long-running projects.  Results show that the distribution
+is skewed to the right indicating that test costs are relatively well
+distributed in most costly projects we analyzed \Fix{$\leftarrow$
+  confirm}.
 
-\Jbc{I shouldn't introduce parallelization arguments here but we have
-to address this at some point:
-Regression tests that are well distributed may benefit from
-parallelism since more tests executes at the same time while the
-opposite scenario may require a different approach. In the later
-scenario, executing tests in parallel may have insignificant impact
-since a small subset of test cases dominates the execution.}
+%% analyzed the execution time
+%% for the \numMedLong{} projects from the \longg{} and \medg{} groups
+%% (see Section~\ref{sec:rqA}).
+%% For each subject we calculated the
+%% relative standard deviation of the test cases: we collected the
+%% elapsed time of each individual test, calculated the standard
+%% deviation, and divided by the mean. \Jbc{I need to clarify the
+%%   relationship "well/bad-balanced" regression test and relative
+%%   standard deviation}
+
+%% Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
+%% different groups of subjects}\Fix{TODO: collect data + compute the
+%% statistic, create a scatter plot to identify groups of subjects}
+
+%% \Jbc{I shouldn't introduce parallelization arguments here but we have
+%% to address this at some point:
+%% Regression tests that are well distributed may benefit from
+%% parallelism since more tests executes at the same time while the
+%% opposite scenario may require a different approach. In the later
+%% scenario, executing tests in parallel may have insignificant impact
+%% since a small subset of test cases dominates the execution.}
 

### 2017-01-11 paper/R/genplot.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+# R --vanilla < effort.r --args  effort2.data
+# mv Rplots.pdf effort2.pdf
+
+NAME="relativeSD"
+R --vanilla < ${NAME}.r
+

### 2017-01-11 paper/R/relativeSD.r

@@ -1,0 +1,17 @@
+library(ggplot2)
+
+pdf(file = "relativeSD.pdf", width = 5, height = 1.5)
+
+dat <- read.table("relativeSD.data", sep = "", header = TRUE) 
+
+p <- ggplot(dat, aes(factor(dummy), RSD))
+
+p +
+geom_boxplot() +
+coord_flip() +
+theme(axis.title.y=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks.y=element_blank()
+)
+
+aux <- dev.off()

### 2017-01-12 paper/evaluation.tex
Conflict resolved and added explanation on RQ3

@@
 
+\newcommand{\numRQA}{RQ1}
+\newcommand{\numRQB}{RQ2}
+\newcommand{\numRQC}{RQ3}
+\newcommand{\numRQD}{RQ4}
+\newcommand{\numRQE}{RQ5}
+\newcommand{\numRQF}{RQ6}
+
 \newcommand{\RQA}{How prevalent is the occurence of time-consuming
@@
 \newcommand{\RQC}{How often parallelization settings appear in build
-  files?}  \newcommand{\RQD}{What is the impact of parallelization?}
+  files?}
+\newcommand{\RQD}{What is the impact of parallelization?}
 \newcommand{\RQE}{What factors contribute to improve performance
@@
 
-\newcommand{\rqA}{\textbf{RQ1.} \RQA}
-\newcommand{\rqB}{\textbf{RQ2.} \RQB}
-\newcommand{\rqC}{\textbf{RQ3.} \RQC}
-\newcommand{\rqD}{\textbf{RQ4.} \RQD}
-\newcommand{\rqE}{\textbf{RQ5.} \RQE}
-\newcommand{\rqF}{\textbf{RQ6.} \RQF}
-
 \begin{itemize}
-    \item \rqA
-    \item \rqB
-    \item \rqC
-    \item \rqD
-    \item \rqE
-    \item \rqF
+    \item \textbf{\numRQA.} \RQA
+    \item \textbf{\numRQB.} \RQB
+    \item \textbf{\numRQC.} \RQC
+    \item \textbf{\numRQD.} \RQD
+    \item \textbf{\numRQE.} \RQE
+    \item \textbf{\numRQF.} \RQF
 \end{itemize}
@@
 
-\subsection{Answering research question RQ1}
+\subsection{Answering research question \numRQA{}}
 \label{sec:rqA}
@@
 
-\subsection{Answering research question RQ2}
+\subsection{Answering research question \numRQB{}}
 \label{sec:rqB}
@@
 
-\subsection{Answering research question RQ3}
+\subsection{Answering research question \numRQC{}}
 \label{sec:rqC}
@@
 projects with \shortg{}-running test suites as we observed\Mar{please,
-  confirm} that those projects often\Mar{adjust} do not use
-parallelism; including them would favor sequential execution in our
-analysis.
+confirm} that those projects often\Mar{adjust} do not use parallelism;
+including them would favor sequential execution in our analysis.
 
-%% We
-%% focused in these two groups because given that costly test suites
-%% exist, we investigated if the maintainers are aware of parallelization
-%% settings.
-
-To answer RQ3\Mar{use macro} we initially mined build files (\ie,
-\pomf{}) that contain parallelization keywords, namely
-\CodeIn{forkMode}, \CodeIn{forkCount}, and \CodeIn{parallel}.
-According to the Maven surefire documentation\Fix{cite surefire doc},
-any configuration to run tests in parallel must contain one of these
-keywords. This mining step, however, is not sound as a matching
-project may not indicate a project with a valid configuration for
-running tests in parallel.  False positive can happen because of
-comments, for instance.  To eliminate the cases of false positives and
-also to categorize true positive cases, we complemented the initial
-mining step with a manual inspection of files.
+To answer \numRQC{} we initially mined build files (\ie, \pomf{}) that
+contain parallelization keywords, namely \CodeIn{forkMode},
+\CodeIn{forkCount}, and \CodeIn{parallel}.  According to the Maven
+surefire documentation\Fix{cite surefire doc}, any configuration to
+run tests in parallel must contain one of these keywords. This mining
+step, however, is not sound as a matching project may not indicate a
+project with a valid configuration for running tests in parallel.
+False positive can happen because of comments, for instance.  To
+eliminate the cases of false positives and also to categorize true
+positive cases, we complemented the initial mining step with a manual
+inspection of files.
 
@@
 
-Figure~\ref{tab:inspection-table} summarizes our results.  Column
-``Group'' indicates the group of projects according to their time
-cost.\Mar{quickly explain other columns}
+Figure~\ref{tab:inspection-table} summarizes our results. The first
+column indicates the group of projects according to their time cost.
+The second column indicates the number of build files per group.  The
+third column is a subset from the previous column and represents the
+number of build files found in the mining step (including
+false-positives highlighted in parentheses). The last column indicates
+the ratio of projects with parallelization settings.
 
-%% summarize observations...
 From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
-where 109\Mar{use macro} of those files match one of the keywords
-mentioned above.  From these 109\Mar{use macro} build files, we
+where \numPomMatched{} of those files match one of the keywords
+mentioned above.  From these \numPomMatched{} build files, we
 eliminated six false-positives: two were names of project modules
 (\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
-comment, and three were commented configurations. The 106\Fix{fix
-  this} build files with valid configurations are distributed across
-41\Mar{use macro} projects from our sample.  \emph{From these results
-  we found that $\sim$51\% of medium and long-running projects do not
-  use parallel features to run test suites.}\Mar{please make it
-  consistent with research question}\Mar{explain this is
-  over(under)-estimated...}
+comment, and three were commented configurations. The
+\numPomMatchedValid{} build files with valid configurations are
+distributed across \numProjectsPar{} projects from our sample.
+\emph{From these results we found that $\sim$51\% of medium and
+long-running projects do not use parallel features to run test
+suites.}\Mar{please make it consistent with research
+question}\Mar{explain this is over(under)-estimated...}
 
@@
         \toprule
-        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
-                               &                             &  (false-positives) &       / total\\%
+        \multirow{2}{*}{Group}
+            & \multirow{2}{*}{\# \pomf{}}
+            & \# \pomf{} matched
+            & \# projects matched\\%
+        % 2nd row - empty cell
+            & % empty cell
+            & (false-positives)
+            & / total\\%
         \midrule%
-        Long   & 1613 & 79 (1) & 19/\numLong{}\\%
-        Medium & 1238 & 30 (5) & 22/\numMed{}\\%
+        Long   & 1613 & 79 (1) & 19 / \numLong{}\\%
+        Medium & 1238 & 30 (5) & 22 / \numMed{}\\%
         \midrule%
-        Total  & \pomMedLong{} & 109 (6) & 41/\numMedLong{}\\%
+        Total & \pomMedLong{} & \numPomMatched{} (6) & \numProjectsPar{} / \numMedLong{}\\%
         \bottomrule%
     \end{tabular*}
-    \caption{Presence of parallel configurations in build files from
-    projects with time-consuming tests. \Fix{explain columns}}
+    \caption{Presence of parallelization settings in build files: the
+    first column indicates the group of projects according to their
+    time cost; the second column indicates the number of build files;
+    the third column is the subset of files with parallelization
+    keywords; the last column indicates the ratio of projects with
+    parallelism support.}
     \label{tab:inspection-table} 
@@
 
-\Jbc{Conclusion and relate the results to the
-  RQ...........................................}
+From the \numProjectsPar{} projects identified above, we investigated
+further the \numPomMatchedValid{} build files with parallel settings.
+We analyzed the support and distribution of parallel modes from this
+subset of projects. To calculate the distribution of parallel modes,
+we considered only the presence of the mode in at least one of the
+project settings.  Recall that a build file may contain more than one
+parallel setting and a project may contain several sub-modules with
+build files.  In case the value of a parallel option is resolved
+dynamically (\eg, via command-line argument or system variable) we
+compute all modes related to the option. For instance, depending on
+the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
+\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
+(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
+Figure~\ref{fig:freqmodes} summarizes our findings.
 
@@
     \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
-    \caption{\label{fig:freqmodes}Distribution of parallelism modes
-    identified in \Fix{M} projects\Jbc{Currently medium and partially
-    the long group...}}
+    \caption{\label{fig:freqmodes}Distribution of parallel modes
+    identified in a subset of \numProjectsPar{} projects. A single
+    project may have support to more than one parallel mode.}
 \end{figure}
 
-\subsection{Answering research question RQ4}
+\subsection{Answering research question \numRQD{}}
 \label{sec:rqD}

### 2017-01-12 paper/evaluation.tex
fixes and pass on text

@@
 root directory.  As of December 30th 2016, our search criteria
-returned \numSubjsTotal{} subjects. From the \numSubjsTotal{}
-downloaded projects, 46 were not Maven projects (or did not have a
-\pomf{} in the root directory) and 159 were in a unstable revision.
-From these 159 unstable subjects, \Jbc{elaborate what is unstable (eg,
-(1) how many could not resolve dependencies? (2) how many could not
-compile sources and tests? (3) could not run tests due to incompatible
-testing environment?}. Our final set consists in \numSubjs{} testable
-subjects.
+returned 615 subjects. From the 615 downloaded projects, 46 were not
+Maven projects (or did not have a \pomf{} in the root directory) and
+159 were in a unstable revision.  From these 159 unstable subjects,
+\Jbc{elaborate what is unstable (\eg, (1) how many could not resolve
+dependencies? (2) how many could not compile sources and tests? (3)
+could not run tests due to incompatible testing environment?}. Our
+final set consists in \numSubjs{} testable subjects.
 
@@
 To evaluate the frequency of time-consuming regression tests, we
-considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
-compared the elapsed time to run their tests.
-Figure~\ref{fig:mvn-execution} shows the commands used in our script
-to test each subject. The main loop (lines 5-11) iterates over the
-list of subjects and invokes Maven in separated steps (lines 7-9). To
-avoid inflating the measured time we executed Maven in different
-steps: we first compiled the source and test files (line 7), made all
-dependencies available locally (line 8) and later, we ran the tests in
-offline mode (line 9) to bypass package updates. After the execution,
-we used a regular expression on the output log to extract the elapsed
-time (line 10). Before collecting the time cost, we executed all
-subjects and randomly selected 100 logs to inspect and identify
-non-related tasks (\eg, \emph{javadoc} generation and static analysis)
-to ignore during the experiment (lines 1-3).  To avoid noise from
-operating system events, we used a dedicated server remotely via SSH
-with the operating system running only essential services (\eg, the
-SSH server). In addition, we configured the \CodeIn{isolcpus} option
-from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
-to execute our experiment and the remaining CPUs to run the operating
-system. By isolating a set of virtual CPUs, we prevent
-context-switching from experiment processes and OS-related processes.
+considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
+and compared the elapsed time to run their tests. \Jbc{Be clear about
+checking the elapsed time }.  Figure~\ref{fig:mvn-execution} shows the
+commands used in our script to test each subject. The main loop (lines
+5-11) iterates over the list of subjects and invokes Maven in
+separated steps (lines 7-9). To avoid inflating the measured time we
+executed Maven in different steps: we first compiled the source and
+test files (line 7), made all dependencies available locally (line 8)
+and later, we ran the tests in offline mode (line 9) to bypass package
+updates. After the execution, we used a regular expression on the
+output log to extract the elapsed time (line 10). Before collecting
+the time cost, we executed all subjects and randomly selected 100 logs
+to inspect and identify non-related tasks (\eg, \emph{javadoc}
+generation and static analysis) to ignore during the experiment (lines
+1-3).  To avoid noise from operating system events, we used a
+dedicated server remotely via SSH with the operating system running
+only essential services (\eg, the SSH server). In addition, we
+configured the \CodeIn{isolcpus} option from the Linux Kernel
+\cite{linux-kernel} to isolate six virtual CPUs to execute our
+experiment and the remaining CPUs to run the operating system. By
+isolating a set of virtual CPUs, we prevent context-switching from
+experiment processes and OS-related processes.
 
@@
 not uncommon; they account to nearly \percentMedLongRunning{} of the
-\numSubjsTotal{} projects we analyzed.  However, use of parallelism
+\numSubjs{} projects we analyzed.  However, use of parallelism
 does not assure speedups on those projects.  We analyzed one sensible
@@
 We evaluated the dispersion of time distributions (one distribution
-per project) to aswer research question RQ2.  To measure dispersion
-\emph{across} projects we used Relative Standard Deviation
+per project) to answer research question \numRQB{}.  To measure
+dispersion \emph{across} projects we used Relative Standard Deviation
 (RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were to
@@
         \toprule
-        \multirow{2}{*}{Group}
+        \multirow{2}{*}{Group} %1st row, 1st cell
             & \multirow{2}{*}{\# \pomf{}}
@@
         \midrule%
-        Total & \pomMedLong{} & \numPomMatched{} (6) & \numProjectsPar{} / \numMedLong{}\\%
+        Total % last row, first cell
+            & \pomMedLong{}
+            & \numPomMatched{} (6)
+            & \numProjectsPar{} / \numMedLong{}\\%
         \bottomrule%
@@
 (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
-Figure~\ref{fig:freqmodes} summarizes our findings.
+Figure~\ref{fig:freqmodes} summarizes our findings. \Jbc{Given that we
+checked each configuration, we could elaborate how these settings are
+used.} \Fix{Missing conclusion: Fork the most used configuration}
 
@@
     \caption{\label{fig:freqmodes}Distribution of parallel modes
-    identified in a subset of \numProjectsPar{} projects. A single
-    project may have support to more than one parallel mode.}
+    identified in a subset of \numProjectsPar{} projects (unused modes
+    omitted). A single project may have support to more than one
+    parallel mode.}
 \end{figure}

### 2017-01-13 paper/R/relativeSD.r
updated RSD plot

@@ -2,9 +2,9 @@ library(ggplot2)
 
 pdf(file = "relativeSD.pdf", width = 5, height = 1.5)
 
-dat <- read.table("relativeSD.data", sep = "", header = TRUE) 
+dat <- read.csv("RSD.csv", header = F) 
 
-p <- ggplot(dat, aes(factor(dummy), RSD))
+p <- ggplot(dat, aes(x="", y=dat$V2))
 
 p +
 geom_boxplot() +
@@ -12,6 +12,7 @@ coord_flip() +
 theme(axis.title.y=element_blank(),
       axis.text.y=element_blank(),
       axis.ticks.y=element_blank()
-)
+) +
+labs(y="Relative Standard Deviation (RSD)")
 
 aux <- dev.off()

### 2017-01-16 paper/R/genplot.sh
boxplot prepared (on request)

@@ -1,8 +1,5 @@
 #!/bin/bash
 
-# R --vanilla < effort.r --args  effort2.data
-# mv Rplots.pdf effort2.pdf
-
-NAME="relativeSD"
+NAME="testcost"
 R --vanilla < ${NAME}.r
 

### 2017-01-16 paper/R/relativeSD.r

@@ -1,10 +1,10 @@
 library(ggplot2)
 
-pdf(file = "relativeSD.pdf", width = 5, height = 1.5)
+pdf(file = "relativeSD.pdf", width = 5, height = 2.5)
 
-dat <- read.csv("RSD.csv", header = F) 
+dat <- read.csv("testcost.csv", header = T) 
 
-p <- ggplot(dat, aes(x="", y=dat$V2))
+p <- ggplot(dat, aes(x=", y=dat$V2))
 
 p +
 geom_boxplot() +

### 2017-01-16 paper/R/testcost.r

@@ -1,0 +1,16 @@
+library(ggplot2)
+
+pdf(file = "testcost.pdf", width = 5, height = 2.5)
+
+dat <- read.csv("testcost.csv", header = T) 
+
+p <- ggplot(dat, aes(x=factor(project), y=time))
+
+p + geom_boxplot() +
+theme(axis.title.x=element_blank(),
+      axis.text.x=element_blank(),
+      axis.ticks.x=element_blank()
+) +
+labs(y="Time (s)")
+
+aux <- dev.off()

### 2017-01-16 paper/intro.tex
pass on intro

@@
 aggregate cost of running a test suite, which can lead to late reports
-of test failures.  Dealing with high testing costs is critical at
-large IT organizations, with massive code and test bases.
+of test failures.  Dealing with high testing costs is important.
 
 Several approaches have been proposed in the literature to address the
-regression testing problem.  Research has focused mostly on test suite
+regression testing problem, with the focus mainly on test suite
 minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  These approaches reduce testing
-cost by reducing the amount of tests for execution.  It is important
-to bring to light that the \emph{complementary alternative} of
-balancing the test workload across work units is sound (\ie{}, it
-cannot miss fault-revealing tests) and very popular in industry.
-Evidence of this are the Google TAP system~\cite{google-tap,google-ci}
-and Microsoft's CloudBuild
-system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
-distributed infrastructures to efficienctly build massive amounts of
-code and run tests.  Note, however, that the regression testing
-problem is not specific to giants from the IT sector.  For example, as
-of August 2013, the Groupon PWA system, which powers the
+selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
+mainly on distributing testing workloads.  Evidence of this are the
+Google TAP system~\cite{google-tap,google-ci} and Microsoft's
+CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
+provide distributed infrastructures to efficienctly build massive
+amounts of code and run tests.  Building server clusters is also a
+popular mechanism to distribute testing workloads.  For example, as of
+August 2013, the Groupon PWA system, which powers the
 \url{groupon.com} website, included over 19K tests.  To run all those
@@
 each~\cite{kim-etal-fse2013}.
-
-%% As additional examples, Google's
-%% TAP and Microsoft's CloudBuild distribute task workloads in the cloud.
 
@@
 to mitigate the regression testing problem.  However, for projects
-with low budgets and yet moderate or heavy testing workloads, this
-solution may not be economically viable.  The amount of serious
-open-source project under development today is impressive.\Mar{give
-  examples, provide stats.}  Optimizing existing computational
-resources in this context saves money or time.  \Mar{what about free
-  services (jenkins)?  how much can you scale execution and how
-  expensive would that be?}
+with low budgets and yet relatively heavy testing workloads, this
+solution may not be economically viable.  This paper focuses on the
+problem of understanding how critical the regression testing problem
+is in open-source projects.  To the best of our knowledge no prior
+work investigated this problem, which is becoming more important given
+the tremendous popularity of open-source development.
 
@@
 
-\sloppy This paper focuses on the problem of understanding how
-critical the regression testing problem is in open-source projects.
-To the best of our knowledge no prior work investigated this problem,
-which is important given the tremendous popularity of open-source
-development and the wide impact of regression testing optimization
-techniques in this setting.
-
 %Motivated by this potential gap in regression testing,
@@
 %% not used why, and what are the associated drawbacks.
+
+\Fix{---------------- parei aqui...}
 
@@
 
+\Mar{what about free services (jenkins)?  how much can you scale
+  execution and how expensive would that be?}
+
 To illustrate the importance of parallel test execution, \Jbc{TODO -

### 2017-01-16 paper/evaluation.tex
Updated data
bugfix
boxplot prepared (on request)
initial sentences on RQ4

@@
   \centering
-  \includegraphics[width=0.5\textwidth]{R/relativeSD.pdf}  
+  \includegraphics[width=0.5\textwidth]{R/testcost.pdf}  
   \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
-    across projects.\Fix{update (mocked) data}}
+    across projects.}
 \end{figure}
@@
 
-\Jbc{describe}.\Jbc{relevance}. \Jbc{methodology}.
+To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
+parallelization settings identified in \numRQC{} and compared their
+time cost with sequential execution. \Jbc{should have a sentence to
+motivate this RQ} 
+\Jbc{explain methodology}.
 

### 2017-01-16 paper/intro.tex
pass on intro

@@
 length of test runs increase.  Both components can add up to the
-aggregate cost of running a test suite, which can lead to late reports
-of test failures.  Dealing with high testing costs is important.
+aggregate cost of running a test suite.  Dealing with high testing
+costs is an important problem in software engineering research and
+practice (as to reduce late test failure reports).
 
-Several approaches have been proposed in the literature to address the
-regression testing problem, with the focus mainly on test suite
-minimization, prioritization, reduction, and
+Several approaches have been proposed in the research literature to
+address the regression testing problem, with the focus mainly on test
+suite minimization, prioritization, reduction, and
 selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
-mainly on distributing testing workloads.  Evidence of this are the
-Google TAP system~\cite{google-tap,google-ci} and Microsoft's
+mainly on distributing the testing workloads.  Evidence of this are
+the Google TAP system~\cite{google-tap,google-ci} and Microsoft's
 CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
@@
 
-At large organizations, the alternative of renting a cloud
-service\footnote{\url{https://clutch.co/cloud}} or even building
-proprietary infrastructures for running tests is a legitimate approach
-to mitigate the regression testing problem.  However, for projects
-with low budgets and yet relatively heavy testing workloads, this
-solution may not be economically viable.  This paper focuses on the
-problem of understanding how critical the regression testing problem
-is in open-source projects.  To the best of our knowledge no prior
-work investigated this problem, which is becoming more important given
-the tremendous popularity of open-source development.
+At large organizations, the alternative of renting cloud
+services\footnote{List of popular cloud services:
+  \url{https://clutch.co/cloud}} or even building proprietary
+infrastructures for running tests is a legitimate approach to mitigate
+the regression testing problem.  However, for projects with low
+budgets and yet relatively heavy testing workloads, this solution may
+not be economically viable.  This paper reports on a study we
+conducted analyzing three orthogonal dimensions of regression testing
+in open-source projects.  We argue that this an important problem
+given the tremendous popularity of open-source development and
+regression testing research.  The dimensions of analysis are as
+follows.
+
+\begin{itemize}
+\item \textbf{Prevalence of long-running test suites.}
+\item \textbf{Usage of test suite parallelization.}  
+\item \textbf{Impact (and issues) of parallelization.}  
+\end{itemize}
 
@@
 
-\Fix{---------------- parei aqui...}
+%% RQ1 + RQ2
+To assess how prevalent long-running test suites are in open-source
+projects, we selected \numSubjs{} popular Java projects from \github{}
+containing Maven build files~\cite{maven}.  (Section~\ref{sec:eval}
+details our selection methodology.)  To run each test suite, we used a
+16GB memory Intel i7 machine\Comment{ i7-4790 Intel processor} with
+eight virtual CPUs (four cores with two native threads each) and the
+default Maven configuration of each project.  Our results indicate
+that \percentMedLongRunning{} of the test suites take at least 1m to
+run and nearly 8\% of the test suites take more than 5m to run.
+Including medium and long-running test suites ($>$1m), a test suite
+takes \averageMedLongRunning{} to run, on average.  These results
+indicate that open-source projects often contain long running test
+suites.  Furthermore, we found that although \Fix{...time
+  distribution...}
 
-More precisely, we studied (1) how prevalent long-running test suites
-are in open-source software projects.  To that end, we selected from
-\github{} \numSubjs{} highly-popular Java projects containing Maven
-build files.  (Section~\ref{sec:eval} details our selection
-methodology.)  To run this experiment we used the default Maven
-configuration to run a project's test suite and a 16GB memory i7-4790
-Intel processor machine, which we carefully isolated.  Our results
-indicate that the test suite of nearly one in every five projects from
-our set (\percentMedLongRunning) takes at least 5m to run.  On
-average, one of those test suites take \averageMedLongRunning{} to
-run.  These results suggest that open-source projects often contain
-long running test suites.
-
-\Mar{missing connection. why
-  parallelism?}  From this result we investigated (2) how frequently
-the projects we considered use parallelization to speedup test runs.
-Our results indicate that \percentParallelForLongRunning{} of
-long-running test suites do use parallelism to speedup execution.
-Given the popularity of this solution, we further studied: (3) what
-are the causes of high execution cost in individual tests (CPU vs. IO)
-and (4) how uniformly cost is distributed across tests.  These
-questions help to assess the impact of parallelization in test suite
-execution.  Intuitively, IO-intensive test suites and test suites with
-uneven distribution of cost per test are factors that limit the
-benefits of parallelization.  Results indicate that \Fix{...}
-Finally, we investigated (5) what are the limitations related to
-parallelization that could justify adoption resistance.
+\Mar{missing connection. why parallelism?}  From these results we
+investigated (2) how frequently the projects we considered use
+parallelization to speedup test runs.  Our results indicate that
+\percentParallelForLongRunning{} of long-running test suites do use
+parallelism to speedup execution.  Given the popularity of this
+solution, we further studied: (3) what are the causes of high
+execution cost in individual tests (CPU vs. IO) and (4) how uniformly
+cost is distributed across tests.  These questions help to assess the
+impact of parallelization in test suite execution.  Intuitively,
+IO-intensive test suites and test suites with uneven distribution of
+cost per test are factors that limit the benefits of parallelization.
+Results indicate that \Fix{...}  Finally, we investigated (5) what are
+the limitations related to parallelization that could justify adoption
+resistance.
 

### 2017-01-17 paper/intro.tex
pass on intro

@@
 CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
-provide distributed infrastructures to efficienctly build massive
+provide distributed infrastructures to efficiently build massive
 amounts of code and run tests.  Building server clusters is also a
@@
 budgets and yet relatively heavy testing workloads, this solution may
-not be economically viable.  This paper reports on a study we
-conducted analyzing three orthogonal dimensions of regression testing
-in open-source projects.  We argue that this an important problem
-given the tremendous popularity of open-source development and
-regression testing research.  The dimensions of analysis are as
-follows.
+not be economically viable.  The relatively-recent proliferation of
+multi-core machines and testing frameworks with a rich support for
+parallelization enabled test suites to increase CPU usage (and execute
+faster) while using existing resources available in commodity hardware
+(see Section~\ref{sec:modes}).  This paper reports on an empirical
+study we conducted to analyze importance of test suite parallelization
+to speedup testing of open-source projects.  We argue that this a
+relevant problem given the tremendous popularity of open-source
+development and regression testing research.  The dimensions of
+analysis in this study are as follows.
 
@@
 %%% End:
+%%  LocalWords:  jenkins

### 2017-01-17 paper/R/testcost.r
Updated plots from RQ2

@@ -1,11 +1,20 @@
 library(ggplot2)
 
-pdf(file = "testcost.pdf", width = 5, height = 2.5)
-
-dat <- read.csv("testcost.csv", header = F) 
-
+pdf(file = "testcost-long.pdf", width = 5, height = 2)
+dat <- read.csv("testcost-long.csv", header = F) 
 p <- ggplot(dat, aes(x=factor(V1), y=V2))
+p + geom_boxplot() +
+theme(axis.title.x=element_blank(),
+      axis.text.x=element_blank(),
+      axis.ticks.x=element_blank()
+) +
+labs(y="Time (s)")
 
+aux <- dev.off()
+
+pdf(file = "testcost-med.pdf", width = 5, height = 2)
+dat <- read.csv("testcost-med.csv", header = F) 
+p <- ggplot(dat, aes(x=factor(V1), y=V2))
 p + geom_boxplot() +
 theme(axis.title.x=element_blank(),
       axis.text.x=element_blank(),

### 2017-01-17 paper/evaluation.tex
Updated plots from RQ2
adjusting plots (per request)

@@
 not uncommon; they account to nearly \percentMedLongRunning{} of the
-\numSubjs{} projects we analyzed.  However, use of parallelism
-does not assure speedups on those projects.  We analyzed one sensible
-factor that is critical to the effectiveness of parallelism: the
-amount of tests that dominate execution time.  In the limit, if cost
-is dominated by a single test, it is unlikely that parallelization
-will be beneficial as a test method is the smallest working unit in
-test frameworks (see Section~\ref{sec:frameworks}).
+\numSubjs{} projects we analyzed.  However, parallelism by itself does
+not assure speedups on those projects.  One sensible factor that is
+critical to the effectiveness of parallelism is the distribution of
+test costs in the test suite.  In the limit, if cost is dominated by a
+single test, it is unlikely that parallelization will be beneficial as
+a test method is the smallest working unit in test frameworks (see
+Section~\ref{sec:frameworks}).
+
+\Fix{...elaborate...}
 
@@
 
-We evaluated the dispersion of time distributions (one distribution
-per project) to answer research question \numRQB{}.  To measure
-dispersion \emph{across} projects we used Relative Standard Deviation
-(RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were to
-analyze each project in isolation, the standard deviation of a
-distribution ($\sigma$) would suffice to quantify how dispersed the
-(time) distribution is.  However, in our case, we would like to be
-able to compare and summarize dispersion across projects.  The RSD,
-which is obtained dividing the standard deviation by the mean ($\mu$)
-of a distribution, provides such normalization effect.  This metric
-provides a lower bound (zero) but not an upper bound (somewhere close
-to 1).  The smaller (larger) the value of RSD the more (less) uniform
-the distribution is.  Consequently, ignoring other factors that affect
-performance of parallelization (e.g., CPU/IO ratio), the lower the
-value of RSD the more parallelizable a test suite should be.
+%% We also evaluated the dispersion of time distributions (one
+%% distribution per project) to answer research question \numRQB{}.  To
+%% measure dispersion \emph{across} projects we used Relative Standard
+%% Deviation (RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were
+%% to analyze each project in isolation, the standard deviation of a
+%% distribution ($\sigma$) would suffice to quantify how dispersed the
+%% (time) distribution is.  However, in our case, we would like to be
+%% able to compare and summarize dispersion across projects.  The RSD,
+%% which is obtained dividing the standard deviation by the mean ($\mu$)
+%% of a distribution, provides such normalization effect.  This metric
+%% provides a lower bound (zero) but not an upper bound (somewhere close
+%% to 1).  The smaller (larger) the value of RSD the more (less) uniform
+%% the distribution is.  Consequently, the lower the value of RSD the
+%% more parallelizable a test suite should be.
 
-\begin{figure}[h!]
+\begin{figure}[ht]
     \centering
-  \includegraphics[width=0.5\textwidth]{R/testcost.pdf}  
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{R/testcost-med.pdf}
+        \caption{\label{fig:medtcost}}
+    \end{subfigure}\\
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{R/testcost-long.pdf}
+        \caption{\label{fig:longtcost}}
+    \end{subfigure}%
     \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
@@
 
-Figure~\ref{fig:relativesd} shows the distribution of RSD across
-medium and long-running projects.  Results show that the distribution
-is skewed to the right indicating that test costs are relatively well
-distributed in most costly projects we analyzed \Fix{$\leftarrow$
-  confirm}.
+%% \begin{figure}[h!]
+%%   \centering
+%%   \includegraphics[width=0.5\textwidth]{R/testcost.pdf}  
+%%   \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
+%%     across projects.}
+%% \end{figure}
+
+%% Figure~\ref{fig:relativesd} shows the distribution of RSD across
+%% medium and long-running projects.  Results show that the distribution
+%% is skewed to the right indicating that test costs are relatively well
+%% distributed in most costly projects we analyzed \Fix{$\leftarrow$
+%%   confirm}.
 

### 2017-01-17 paper/R/genplot.sh

@@ -1,5 +1,6 @@
 #!/bin/bash
 
 NAME="testcost"
-R --vanilla < ${NAME}.r
+Rscript --vanilla ${NAME}.r "testcost-med"
+Rscript --vanilla ${NAME}.r "testcost-long"
 

### 2017-01-17 paper/R/testcost.r

@@ -1,28 +1,33 @@
+#!/usr/bin/env Rscript
+
 library(ggplot2)
 
-pdf(file = "testcost-long.pdf", width = 5, height = 2)
-dat <- read.csv("testcost-long.csv", header = F) 
+args = commandArgs(trailingOnly=TRUE)
+
+if (length(args)==0) {
+  stop("At least one argument must be supplied (input file).n", call.=FALSE)
+} else if (length(args)==1) {
+  name = args[1]
+}
+
+pdf(file=paste(name,".pdf",sep=""), width = 5, height = 2)
+
+dat <- read.csv(paste(name,".csv",sep=""), header = F)
+
+## to compute mean across plots
+datasel <- aggregate(dat[, 2:2], list(dat$V1), mean)
+
 p <- ggplot(dat[dat$V2>1,], aes(x=factor(V1), y=V2))
+
 p + geom_boxplot(outlier.shape=NA) +
 theme(axis.title.x=element_blank(),
       axis.text.x=element_blank(),
       axis.ticks.x=element_blank()
 ) +
 labs(y="Time (s)")+
-coord_cartesian(ylim = c(1,150))
+geom_hline(aes(yintercept=mean(datasel$x, linetype = 2, colour = "red")))+
+coord_cartesian(ylim = c(1,25))
 
 aux <- dev.off()
 
-pdf(file = "testcost-med.pdf", width = 5, height = 2)
-dat <- read.csv("testcost-med.csv", header = F) 
-p <- ggplot(dat[dat$V2>1,], aes(x=factor(V1), y=V2))
-p + geom_boxplot(outlier.shape=NA) +
-theme(axis.title.x=element_blank(),
-      axis.text.x=element_blank(),
-      axis.ticks.x=element_blank()
-) +
-labs(y="Time (s)") +
-coord_cartesian(ylim = c(1,90))
 
-p <- ggplot(dat, aes(x=factor(V1), y=V2), outlier.shape=NA)
-aux <- dev.off()

### 2017-01-18 paper/evaluation.tex
pass on RQ2

@@
 test suites and main sources of cost. We want to understand how the
-execution cost is distributed on test cases withing a test suite and
+execution cost is distributed on test cases within a test suite and
 how developers approach test execution. Based on that, we study
@@
 not assure speedups on those projects.  One sensible factor that is
-critical to the effectiveness of parallelism is the distribution of
-test costs in the test suite.  In the limit, if cost is dominated by a
-single test, it is unlikely that parallelization will be beneficial as
-a test method is the smallest working unit in test frameworks (see
-Section~\ref{sec:frameworks}).
+important to the effectiveness of low-level parallelism is the
+distribution of test costs in the test suite.  In the limit, if cost
+is dominated by a single test, it is unlikely that parallelization
+will be beneficial as a test method is the smallest working unit in
+test frameworks (see Section~\ref{sec:frameworks}).
 
-\Fix{...elaborate...}
+\begin{figure}[ht]
+    \centering
+
+    \begin{subfigure}{0.5\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{R/testcost-med.pdf}
+      \caption{\label{fig:medtcost}Medium}
+    \end{subfigure}\\
+
+    \begin{subfigure}{0.5\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{R/testcost-long.pdf}
+      \caption{\label{fig:longtcost}Long}
+    \end{subfigure}%
+
+    \begin{subfigure}{0.5\textwidth}
+      \centering
+      \begin{tabular}{rrrr}
+        \toprule
+        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
+        \midrule    
+        Medium & 17 & 20 & 7 \\
+        Long   &  9 & 14 & 5 \\
+        \bottomrule
+      \end{tabular}
+      \caption{\label{fig:sd}...\Fix{Looks like there are missing
+        projects...}}    
+    \end{subfigure}%
+
+    \caption{\label{fig:time-distributions}Distribution of time cost per project.}    
+\end{figure}
+
+\sloppy Figures~\ref{fig:medtcost} and~\ref{fig:longtcost} show the
+time distribution of tests per project.  We observed that the average
+median value of execution cost for a test was relatively small (dashed
+horizontal red lines), namely 0.41s for \medg{} projects and 0.23s for
+\longg{} projects.  Note that correlation between cost of test suites
+and cost of their individual tests is not to be expected.  The
+standard deviation ($\sigma$) associated with each ditribution was
+relatively low.  Figure~\ref{fig:sd} shows the number of projects
+within specific ranges of $\sigma$ values.  We also observed that
+projects with very high standard deviations may or may not be
+indicative of monopolization of execution by a small number of tests.
+For example, the highest value of $\sigma$ ocurred in project
+\CodeIn{wildfly-swarm}, whose test suite was classified as
+long-running.  This project contains only 65 tests, 62 of which take
+less than 0.5s to run, 1 of which takes nearly 3s to run, and 2 of
+which take 40m to run.  This is an example where test suite
+parallelization may not be very beneficial as $>$99\% execution cost
+is dominated by only 3\% of the tests.  Without these two tests this
+project would have been classified as short-running.  A closer
+inspection in the data indicates that the project
+\CodeIn{wildfly-swarm} was an extreme case; we did not find projects
+with similar characteristics of time monopolization.  Project
+\CodeIn{jenkinsci.gerrit-trigger-plugin} is also classified as
+long-running and has the second highest value of $\sigma$.  For this
+project, however, cost is distributed more smoothly across 529 tests,
+of which 119 take more than 1s to run.
+
+Overall, results indicate that projects with a very small number of
+tests monopolizing the CPU were not predominant.
+
+\begin{table}[h!]
+
+\end{table}
 
@@
 %% more parallelizable a test suite should be.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{R/testcost-med.pdf}
-        \caption{\label{fig:medtcost}}
-    \end{subfigure}\\
-    \begin{subfigure}{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{R/testcost-long.pdf}
-        \caption{\label{fig:longtcost}}
-    \end{subfigure}%
-    \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
-        across projects.}
-\end{figure}
 

### 2017-01-18 paper/R/testcost.r

@@ -1,6 +1,7 @@
 #!/usr/bin/env Rscript
 
 library(ggplot2)
+library(raster)
 
 args = commandArgs(trailingOnly=TRUE)
 
@@ -10,14 +11,21 @@ if (length(args)==0) {
   name = args[1]
 }
 
-pdf(file=paste(name,".pdf",sep=""), width = 5, height = 2)
+# ## coefficient of variation function
+# co.var <- function(x,na.rm=TRUE) sd(x,na.rm=na.rm)/mean(x,na.rm=na.rm)
+
+pdf(file=paste(name,".pdf",sep=""), width = 5, height = 1.5)
 
 dat <- read.csv(paste(name,".csv",sep=""), header = F)
 
-## to compute mean across plots
-datasel <- aggregate(dat[, 2:2], list(dat$V1), mean)
+## to compute median values across plots
+median <- aggregate(dat[, 2:2], list(dat$V1), median)
 
-p <- ggplot(dat[dat$V2>1,], aes(x=factor(V1), y=V2))
+print("==sd==>")
+sd <- aggregate(dat[, 2:2], list(dat$V1), sd)
+print(sd)
+
+p <- ggplot(dat, aes(x=factor(V1), y=V2))
 
 p + geom_boxplot(outlier.shape=NA) +
 theme(axis.title.x=element_blank(),
@@ -25,8 +33,8 @@ theme(axis.title.x=element_blank(),
       axis.ticks.x=element_blank()
 ) +
 labs(y="Time (s)")+
-geom_hline(aes(yintercept=mean(datasel$x, linetype = 2, colour = "red")))+
-coord_cartesian(ylim = c(1,25))
+geom_hline(aes(yintercept=mean(median$x)), colour = "red", linetype = 2)+
+coord_cartesian(ylim = c(0,7.5))
 
 aux <- dev.off()
 

### 2017-01-18 paper/intro.tex
pass on intro

@@
 budgets and yet relatively heavy testing workloads, this solution may
-not be economically viable.  The relatively-recent proliferation of
-multi-core machines and testing frameworks with a rich support for
-parallelization enabled test suites to increase CPU usage (and execute
-faster) while using existing resources available in commodity hardware
-(see Section~\ref{sec:modes}).  This paper reports on an empirical
-study we conducted to analyze importance of test suite parallelization
-to speedup testing of open-source projects.  We argue that this a
-relevant problem given the tremendous popularity of open-source
-development and regression testing research.  The dimensions of
-analysis in this study are as follows.
+not be economically viable.  The proliferation of multi-core CPUs in
+commodity hardware and the popularization of testing frameworks with a
+rich support for parallelization (see Section~\ref{sec:modes}) enables
+test suites to increase CPU usage.  This paper reports on an empirical
+study we conducted to analyze importance of low-level parallelization
+(\ie{}, parallel features available within each machine) to speedup
+testing of open-source projects.  This is a relevant problem given the
+tremendous popularity of open-source development and regression
+testing research.
+
+The dimensions of analysis in this study are as follows.
 
@@
 
+%% To run each test suite, we used a
+%% 16GB memory Intel i7 machine\Comment{ i7-4790 Intel processor} with
+%% eight virtual CPUs (four cores with two native threads each) and the
+%% default Maven configuration of each project.
+
 %% RQ1 + RQ2
-To assess how prevalent long-running test suites are in open-source
-projects, we selected \numSubjs{} popular Java projects from \github{}
-containing Maven build files~\cite{maven}.  (Section~\ref{sec:eval}
-details our selection methodology.)  To run each test suite, we used a
-16GB memory Intel i7 machine\Comment{ i7-4790 Intel processor} with
-eight virtual CPUs (four cores with two native threads each) and the
-default Maven configuration of each project.  Our results indicate
-that \percentMedLongRunning{} of the test suites take at least 1m to
-run and nearly 8\% of the test suites take more than 5m to run.
-Including medium and long-running test suites ($>$1m), a test suite
-takes \averageMedLongRunning{} to run, on average.  These results
-indicate that open-source projects often contain long running test
-suites.  Furthermore, we found that although \Fix{...time
-  distribution...}
+We selected \numSubjs{} popular Java projects from \github{}
+containing Maven build files~\cite{maven} to assess how prevalent
+long-running test suites are.  Section~\ref{sec:eval} details our
+methodology to select subjects and to isolate our experiments from
+environmental noise.  In summary, results indicate that $\sim$21\% of
+the test suites take at least 1m to run and $\sim$8\% of the test
+suites take at least 5m to run.  Considering all the \numMedLong{}
+projects (\percentMedLongRunning{} of
+\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.} in the
+$>$1m group, the average execution time is \averageMedLongRunning{}.
+Results also show that individual tests are typically short-running,
+taking often less than half a second to run.  Furthermore, we found
+that only in rare cases few test cases monopolize execution cost
+associated with each test suite.  Overall, these results suggest that
+test suite parallelization has the potential to optimize these test
+suites.
 

### 2017-01-19 paper/intro.tex
pass on intro

@@
 suites take at least 5m to run.  Considering all the \numMedLong{}
-projects (\percentMedLongRunning{} of
-\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.} in the
-$>$1m group, the average execution time is \averageMedLongRunning{}.
-Results also show that individual tests are typically short-running,
-taking often less than half a second to run.  Furthermore, we found
-that only in rare cases few test cases monopolize execution cost
-associated with each test suite.  Overall, these results suggest that
-test suite parallelization has the potential to optimize these test
-suites.
+projects in the $>$1m group (\percentMedLongRunning{} of
+\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.}, the
+average execution time is \averageMedLongRunning{}.  Results also show
+that individual tests are typically short-running, taking often less
+than half a second to run.  Furthermore, we found that only in rare
+cases few test cases monopolize execution cost associated with each
+test suite.  Overall, these results suggest that test suite
+parallelization has the potential to optimize these test suites.
 
-\Mar{missing connection. why parallelism?}  From these results we
-investigated (2) how frequently the projects we considered use
-parallelization to speedup test runs.  Our results indicate that
-\percentParallelForLongRunning{} of long-running test suites do use
-parallelism to speedup execution.  Given the popularity of this
-solution, we further studied: (3) what are the causes of high
-execution cost in individual tests (CPU vs. IO) and (4) how uniformly
-cost is distributed across tests.  These questions help to assess the
-impact of parallelization in test suite execution.  Intuitively,
-IO-intensive test suites and test suites with uneven distribution of
-cost per test are factors that limit the benefits of parallelization.
-Results indicate that \Fix{...}  Finally, we investigated (5) what are
-the limitations related to parallelization that could justify adoption
-resistance.
+%%RQ3
+Given the high execution cost associated with a significant number of
+\github{} projects, we decided to investigate practical usage of test
+suite parallelization.  It is important to note that modern build
+systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
+accelerate test execution (see Section~\ref{sec:modes}).  To find how
+popular are these features in practice, we first analyzed build files
+\emph{statically}.  Considering the +1m group of projects
+(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
+them use some parallelization option.  Considering those projects that
+take more than 5m to run (\numLong{} in total), usage of parallelism
+increases to 59\% (19/\numLong{}).  Furthermore, we found that
+``forking'' virtual machines was the most prevalent parallel mode used
+in practice.  It appeared twice as much as any other mode.  This
+result suggests that datarace flakiness~\cite{luo-etal-fse2014} may be
+a concern to users as ``forking'' creates different independent
+processes (\ie{}, Java VM instances) to speedup test execution.  It
+does not exploit thread-level concurrency within each VM, which can be
+an important source of
+contention~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.
+\Mar{why 32-19 did not use parallelization?} \Mar{what about free
+  services (jenkins)?  how much can you scale execution and how
+  expensive would that be?}
 
-\Fix{--------------}
+\Fix{...Discuss impact...}
 
-\Mar{what about free services (jenkins)?  how much can you scale
-  execution and how expensive would that be?}
+%% \Mar{missing connection. why parallelism?}  From these results we
+%% investigated (2) how frequently the projects we considered use
+%% parallelization to speedup test runs.  Our results indicate that
+%% \percentParallelForLongRunning{} of long-running test suites do use
+%% parallelism to speedup execution.  Given the popularity of this
+%% solution, we further studied: (3) what are the causes of high
+%% execution cost in individual tests (CPU vs. IO) and (4) how uniformly
+%% cost is distributed across tests.  These questions help to assess the
+%% impact of parallelization in test suite execution.  Intuitively,
+%% IO-intensive test suites and test suites with uneven distribution of
+%% cost per test are factors that limit the benefits of parallelization.
+%% Results indicate that \Fix{...}  Finally, we investigated (5) what are
+%% the limitations related to parallelization that could justify adoption
+%% resistance.
 
-To illustrate the importance of parallel test execution, \Jbc{TODO -
-Write a paragraph motivating this paper.}
+%% To illustrate the importance of parallel test execution, \Jbc{TODO -
+%% Write a paragraph motivating this paper.}
 
-This paper reports an empirical study to evaluate the impact of
-parallelization options on test execution speedup \Fix{...}\Jbc{TODO -
-Summary of the contributions of this paper} .
+%% This paper reports an empirical study to evaluate the impact of
+%% parallelization options on test execution speedup \Fix{...}\Jbc{TODO -
+%% Summary of the contributions of this paper} .
 

### 2017-01-19 paper/intro.tex
pass on intro

@@
 costs is an important problem in software engineering research and
-practice (as to reduce late test failure reports).
+industrial practice.
 
@@
 selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
-mainly on distributing the testing workloads.  Evidence of this are
-the Google TAP system~\cite{google-tap,google-ci} and Microsoft's
+mainly on distributing the testing workload.  Evidence of this are the
+Google TAP system~\cite{google-tap,google-ci} and the Microsoft
 CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
@@
 budgets and yet relatively heavy testing workloads, this solution may
-not be economically viable.  The proliferation of multi-core CPUs in
-commodity hardware and the popularization of testing frameworks with a
-rich support for parallelization (see Section~\ref{sec:modes}) enables
-test suites to increase CPU usage.  This paper reports on an empirical
-study we conducted to analyze importance of low-level parallelization
-(\ie{}, parallel features available within each machine) to speedup
-testing of open-source projects.  This is a relevant problem given the
-tremendous popularity of open-source development and regression
-testing research.
+not be economically viable.  For these cases, the use of commodity
+hardware, perhaps existing hardware, emerges as an attractive solution
+for running tests.  The proliferation of multi-core CPUs and the
+increasing popularization of testing frameworks with a rich support
+for parallelization enables test suite speedups through increased CPU
+usage~(see Section~\ref{sec:modes}).  This paper reports on an
+empirical study we conducted to analyze importance of low-level
+parallelization to speedup testing of open-source projects.  This is a
+relevant problem given the tremendous popularity of open-source
+development and regression testing research.
 
@@
 \item \textbf{Usage of test suite parallelization.}  
-\item \textbf{Impact (and issues) of parallelization.}  
+\item \textbf{Impact of parallelization.}
+\item \textbf{Issues with parallelization.}    
 \end{itemize}

### 2017-01-19 paper/modes.tex
pass in RQ2 (not done)
pass on section 2

@@
 
-\Mar{add a sentence to introduce this section at a higher abstraction
-  level.}  Parallelism in test execution can be obtained at different
-levels.  Figure~\ref{fig:levels} illustrates some of these levels.
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}
+  \vspace{-1ex}
+  \caption{\label{fig:levels}Levels of parallelism.}
+\end{figure}
 
-This paper focuses at lower-level parallelism, obtained with parallel
-computation at CPUs and threads in a given machine.  This kind of
-parallelism is enabled through build systems and testing frameworks.
-Given the proliferation of multicore machines it is not surprising
-that testing frameworks provide today support for parallel test
-execution with the goal of running tests more
-efficiently~\cite{junit-org,testng,nunit}.  Build systems wrap
-parallel features offered by testing frameworks to facilitate the use
-of such technology\cite{maven-surefire-plugin}.  In the following we
-elaborate relevant features of these components focusing on Java,
-Maven, and JUnit but the discussion can be generalized to other
-languages, build systems, and testing frameworks.
+%\Mar{add a sentence to introduce this section at a higher abstraction
+%  level.}
 
-Note that lower-level parallelism is a complement to higher-level
-parallelism that could be enabled through server farms.  For the
-scenario of large IT organizations, lower-level parallelization
-schemes could leverage the computing power of server nodes in addition
-to the aggregate processing power of the farm.  Lower-level
-parallelism fits particularly well smaller organizations (/projects)
-with relatively high testing costs but lower budgets.
+This section provides some background on parallel test execution.
+
+Parallelism in test execution can be obtained at different levels.
+Figure~\ref{fig:levels} illustrates relevant levels for this paper.
+The highest level indicates parallelism that can be obtained through
+different machines on the network.  For examples, using machines from
+a cloud service.  The machine space sits under the ``network space'',
+and is responsible to provide low-level parallelism.  In that case,
+computation can be offloaded on different CPUs within a machine and on
+different threads within each CPU.  Note that all these levels are
+complementary.  For the scenario of large IT organizations, for
+example, lower-level parallelization schemes could leverage the
+computing power of server nodes in addition to the aggregate
+processing power of the farm.
+
+%% Lower-level parallelism fits
+%% particularly well smaller organizations (/projects) with relatively
+%% high testing costs but lower budgets.
+
+This paper focuses at lower-level parallelism, which can be enabled
+through build systems and testing frameworks.  Given the proliferation
+of multi-core machines it is not surprising that testing frameworks
+provide today support for parallel test
+execution~\cite{junit-org,testng,nunit}.  Build systems wrap parallel
+features offered by testing frameworks to facilitate the use of such
+technology~\cite{maven-surefire-plugin}.  In the following we elaborate
+relevant features of these components focusing on Java, Maven, and
+JUnit but the discussion can be generalized to other languages, build
+systems, and testing frameworks.
+
 \Comment{
@@
 
+\Mar{----------------------- estou aqui.}
+
 \subsection{Testing Framework}
+\label{sec:frameworks}
 
@@
 within a JVM.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figs/parallel-levels.pdf}
-  \caption{\label{fig:levels}Levels of parallelism.}
-\end{figure}
 

### 2017-01-19 paper/evaluation.tex
pass on intro
Added note about subjects that require additional arguments to run all tests

@@
 open-source projects.  It is important to mention that
-Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
-some tests may finish early due to a failure since a subject may be
-tested in a failing revision. From the \numSubjs{} projects, 286
-passed all tests and 118 had failures. \Jbc{elaborate failed subjects:
-how much \% of the tests failed?}
+Figure~\ref{fig:rq1-barplot} represents a lower bound estimation for
+time cost because some projects omit long-running tests on their
+default execution. For instance, it is necessary to invoke Maven with
+additional parameters to run integration tests from project
+\CodeIn{apache.maven-surefire} (nearly 30 min in our environment).
+Also, some tests may finish earlier than expected due to existing bugs
+on the ongoing revision.  From the \numSubjs{} compiled projects, 286
+successfully executed all tests and 118 reported test failures.
+\Jbc{elaborate failed subjects: how much \% of the tests failed?}
 
@@
 Overall, results indicate that projects with a very small number of
-tests monopolizing the CPU were not predominant.
+tests monopolizing end-to-end execution time were rare.
 

### 2017-01-20 paper/intro.tex
pass on section 2

@@
 usage~(see Section~\ref{sec:modes}).  This paper reports on an
-empirical study we conducted to analyze importance of low-level
-parallelization to speedup testing of open-source projects.  This is a
+empirical study we conducted to analyze the impact of low-level
+parallelization to speedup testing in open-source projects.  This is a
 relevant problem given the tremendous popularity of open-source
@@
 \item \textbf{Usage of test suite parallelization.}  
-\item \textbf{Impact of parallelization.}
+\item \textbf{Speedups of parallelization modes.}
 \item \textbf{Issues with parallelization.}    
@@
 ``forking'' virtual machines was the most prevalent parallel mode used
-in practice.  It appeared twice as much as any other mode.  This
-result suggests that datarace flakiness~\cite{luo-etal-fse2014} may be
-a concern to users as ``forking'' creates different independent
-processes (\ie{}, Java VM instances) to speedup test execution.  It
-does not exploit thread-level concurrency within each VM, which can be
-an important source of
-contention~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.
-\Mar{why 32-19 did not use parallelization?} \Mar{what about free
-  services (jenkins)?  how much can you scale execution and how
-  expensive would that be?}
+in practice.  This mode is used twice as much as any other mode used.
+Important to note that ``forking VMs'' is perhaps the simplest of the
+parallelization modes~--~it is provided by the build system as opposed
+to the testing framework.  This result suggests that datarace
+flakiness~\cite{luo-etal-fse2014} may be a concern to users as
+``forking'' does not exploit thread-level concurrency within each VM,
+which can create contention on data reachable from the static
+area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
+creates independent processes (\ie{}, Java VM instances) and executes
+tests sequentially within each process. \Mar{why 32-19 did not use
+  parallelization?} \Mar{what about free services (jenkins)?  how much
+  can you scale execution and how expensive would that be?}
 

### 2017-01-20 paper/modes.tex
pass on section 2

@@
 Parallelism in test execution can be obtained at different levels.
-Figure~\ref{fig:levels} illustrates relevant levels for this paper.
-The highest level indicates parallelism that can be obtained through
-different machines on the network.  For examples, using machines from
-a cloud service.  The machine space sits under the ``network space'',
-and is responsible to provide low-level parallelism.  In that case,
-computation can be offloaded on different CPUs within a machine and on
-different threads within each CPU.  Note that all these levels are
-complementary.  For the scenario of large IT organizations, for
-example, lower-level parallelization schemes could leverage the
-computing power of server nodes in addition to the aggregate
-processing power of the farm.
+Figure~\ref{fig:levels} illustrates relevant levels.  The highest
+level indicates parallelism that can be obtained through different
+machines on the network.  For examples, using virtual machines from a
+cloud service.  The machine space sits under the ``network space'' and
+provides \emph{low-level parallelism}.  In that case, computation can
+be offloaded at different CPUs within a machine and at different
+threads within each CPU.  Note that all these levels are
+complementary.  For example, lower-level parallelization schemes could
+leverage the computing power of server nodes in addition to the
+aggregate processing power of the farm.
 
@@
 of multi-core machines it is not surprising that testing frameworks
-provide today support for parallel test
-execution~\cite{junit-org,testng,nunit}.  Build systems wrap parallel
-features offered by testing frameworks to facilitate the use of such
-technology~\cite{maven-surefire-plugin}.  In the following we elaborate
-relevant features of these components focusing on Java, Maven, and
-JUnit but the discussion can be generalized to other languages, build
-systems, and testing frameworks.
+provide today support for parallel test execution (e.g.,
+JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
+Build systems wrap parallel features offered by testing frameworks to
+facilitate the use of such technology~\cite{maven-surefire-plugin}.
+In the following we elaborate relevant features of these components
+focusing on Java, Maven, and JUnit but the discussion can be
+generalized to other languages, build systems, and testing frameworks.
 
@@
 
-\Mar{----------------------- estou aqui.}
-
-\subsection{Testing Framework}
+\subsection{Testing Frameworks}
 \label{sec:frameworks}
@@
 \item
-    \textbf{Sequential (\Seq).}~This configuration results in
-        sequential execution of test classes and their methods,
-        according to a given order defined in the testing framework
-        (\eg, the order of methods returned by Java Reflection
-        API)~\cite{junit-test-order}. For JUnit, this is the default
-        configuration.
+    \textbf{Sequential (\Seq).}~This configuration corresponds to the
+    sequential execution of test classes and, for each class,
+    sequential execution of their methods.  The execution order (of
+    classes and methods) is determined by the testing framework (\eg,
+    the order of methods returned by the Java Reflection
+    API)~\cite{junit-test-order}.
 \item
     \textbf{Sequential classes; parallel methods
-        (\ParClassSeqMeth{}).}~This configuration results in the
+      (\ParClassSeqMeth{}).}~This configuration corresponds to the
     sequential execution of the test classes assigned to the JVM.
-        However, within each class, test methods run in parallel. In
-        JUnit, \emph{ParallelComputer} provides support to parallel
-        execution: it instantiates a test runner with an
-        \emph{ExecutorService} from the Java Concurrent API. Each test
-        method is executed in a separated thread as the thread pool
-        creates new threads on-demand and reuse them if any thread is
-        available.
-    \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
+    However, within each class, test methods run in parallel.
 \item
     \textbf{Parallel classes; sequential methods
-        (\SeqClassParMeth{}).}~This configuration results in the
-        parallel execution of test classes and sequential test
-        methods. As in \ParClassSeqMeth, the test runner has a cached
-        thread poll but instead of executing test methods from a
-        single test class, the test suite runner executes classes in
-        separated threads and methods sequentially within each thread.
+      (\SeqClassParMeth{}).}~This configuration corresponds to the
+    parallel execution of test classes with sequential execution of
+    their test methods.
 \item
     \textbf{Parallel methods (\ParClassParMeth).}~This configuration
-        results in the parallel execution of any test method from any
-        class.  \Jbc{I need to confirm this but AFAIK this is how it
-        happens} As in \SeqClassParMeth, classes execute on separated
-        threads but test methods are also executed in parallel. More
-        precisely, there is a thread pool to execute classes in
-        separated threads (\ie, like in \ParClassSeqMeth) and, within
-        each class runner, there is an \emph{ExecutorService} to run
-        test methods in parallel (\ie, like in \SeqClassParMeth).
+    corresponds to the parallel execution of any test method from any
+    class.
 \end{itemize}
+
+\Seq{} is the default configuration.  In constrast to the other modes,
+it does not use parallelism.  Considering use of parallelism,
+\ParClassParMeth{} is the most agressive mode, with \ParClassSeqMeth{}
+and \SeqClassParMeth{} lying between \Seq{} and \ParClassParMeth{}.
+\ParClassSeqMeth{} and \SeqClassParMeth{} run sequentially either
+classes or methods.  Intuititvely, fixing one of these dimensions
+enables developers to better organize their test suites as to avoid
+dataraces~\Fix{cite}.  JUnit implements these modes through a set of
+customized classes (e.g., \CodeIn{ParalllelComputer} and
+\CodeIn{ExecutorService}).
+
+%% \Fix{-----}
+%% In JUnit, \emph{ParallelComputer} provides support to parallel
+%% execution: it instantiates a test runner with an
+%% \emph{ExecutorService} from the Java Concurrent API. Each test method
+%% is executed in a separated thread as the thread pool creates new
+%% threads on-demand and reuse them if any thread is available.
+%% \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
+
+%% As in \ParClassSeqMeth, the test runner has a cached thread poll but
+%% instead of executing test methods from a single test class, the test
+%% suite runner executes classes in separated threads and methods
+%% sequentially within each thread.
+
+%% \Jbc{I need to confirm this but AFAIK this is how it happens} As in
+%% \SeqClassParMeth, classes execute on separated threads but test
+%% methods are also executed in parallel. More precisely, there is a
+%% thread pool to execute classes in separated threads (\ie, like in
+%% \ParClassSeqMeth) and, within each class runner, there is an
+%% \emph{ExecutorService} to run test methods in parallel (\ie, like in
+%% \SeqClassParMeth).
+
+%% \Fix{-----}
+
+\subsection{Build Systems}
+
+\Fix{--------------------- estou aqui}
 
@@
 
-\subsection{Build Systems}
 Build systems, such as Maven\footnote{\url{maven.apache.org}},

### 2017-01-20 paper/modes.tex
pass on section 2

@@
 JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
-Build systems wrap parallel features offered by testing frameworks to
-facilitate the use of such technology~\cite{maven-surefire-plugin}.
-In the following we elaborate relevant features of these components
-focusing on Java, Maven, and JUnit but the discussion can be
-generalized to other languages, build systems, and testing frameworks.
+In the following we elaborate relevant features of testing frameworks
+and builds systems.  We focused on Java, Maven, and JUnit but the
+discussion can be generalized to other language and tools.
 
@@
 
-\Seq{} is the default configuration.  In constrast to the other modes,
-it does not use parallelism.  Considering use of parallelism,
-\ParClassParMeth{} is the most agressive mode, with \ParClassSeqMeth{}
-and \SeqClassParMeth{} lying between \Seq{} and \ParClassParMeth{}.
+\Seq{} is the default configuration for JUnit.  It does not use
+parallelism, in constrast to the other execution modes.  Considering
+use of parallelism, \ParClassParMeth{} is the most agressive mode.
 \ParClassSeqMeth{} and \SeqClassParMeth{} run sequentially either
@@
 dataraces~\Fix{cite}.  JUnit implements these modes through a set of
-customized classes (e.g., \CodeIn{ParalllelComputer} and
-\CodeIn{ExecutorService}).
+customized classes (e.g., \CodeIn{ParallelComputer}).
 
@@
 
-\Fix{--------------------- estou aqui}
+Build systems delegate functionalities to the testing framework they
+use~\cite{maven-surefire-plugin}.  Figure~\ref{fig:surefire}
+illustrates how to configure Maven for mode
+\ParClassSeqMeth{}~--~classes sequentially (default) and test methods
+in parallel. Although this configuration is defined in the build file
+(\eg, \emph{pom.xml} on Maven), these settings are forwarded to the
+underlying testing framework (in this case, JUnit).
 
-\Jbc{I have to understand better how Surefire executes tests. I'm
-afraid it has its own wrapper classes and reuse JUnit core
-functionalities. I'm saying this because JUnit does not offer a finer
-control over thread numbers while this configuration is possible with
-Surefire} For example, Figure~\ref{fig:surefire} illustrates how to
-configure Maven to execute classes sequentially (default behavior) and
-test methods in parallel. Although this configuration is defined in
-the build file (\eg, \emph{pom.xml} on Maven), \Fix{these settings are
-forwarded to the underlying testing framework (\eg, JUnit). In case of
-JUnit,}
+%% \Jbc{I have to understand better how Surefire executes tests. I'm
+%% afraid it has its own wrapper classes and reuse JUnit core
+%% functionalities. I'm saying this because JUnit does not offer a finer
+%% control over thread numbers while this configuration is possible with
+%% Surefire} For example,
 
@@
 \end{lstlisting}
-\caption{\label{fig:surefire} Example of Maven Surefire configuration:
-    test methods in parallel (\emph{parallel} parameter) using two
-    threads (\emph{threadCount} parameter) per core (boolean flag
-    \emph{perCoreThreadCount}).}
+\caption{\label{fig:surefire} Example of Maven configuration: test
+  methods run in parallel (\CodeIn{parallel} parameter) using two
+  threads (\CodeIn{threadCount} parameter) per available core (flag
+  \CodeIn{perCoreThreadCount}).}
 \end{figure}
 
-\Fix{We need a par. providing rationale in to explain (points in
-  favor/against) these choices.}
+\subsubsection*{Forking JVMs}~
+Build systems often rovide the option to \emph{fork} JVM instances
+proportionally to available cores in the machine.  For Maven, the
+options \CodeIn{forkCount} and \CodeIn{reuseForks} control this
+feature~\cite{fork-and-parallel-execution-maven}.  Note that Maven
+allocates each test class to exactly one JVM and there is no guarantee
+to uniformly distribute load to each JVM given that the build system
+uses classes as the unit to specify test tasks.  Consequently, only
+combinations of fork with modes \Fix{??} are valid.
 
-Build systems, such as Maven\footnote{\url{maven.apache.org}},
-typically provide the option to \emph{fork} JVM instances
-proportionally to available cores in the machine.  If the option
-``fork JVM'' is enabled, Maven will allocate a user-provided number of
-JVM instances to each core in the machine and will allocate each test
-class to exactly one JVM.  Note that there is no guarantee to
-uniformly distribute load to each JVM given that the build system uses
-classes as the unit to specify test tasks.\Fix{we need to know how
-Maven allocates test classes to JVMs}
+%\Fix{we
+%  need to know how Maven allocates test classes to JVMs}

### 2017-03-08 paper/intro.tex
pass

@@
 Given the high execution cost associated with a significant number of
-\github{} projects, we decided to investigate practical usage of test
-suite parallelization.  It is important to note that modern build
+\github{} projects, we decided to investigate usage of test
+suite parallelization in practice.  It is important to note that modern build
 systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
 accelerate test execution (see Section~\ref{sec:modes}).  To find how
-popular are these features in practice, we first analyzed build files
-\emph{statically}.  Considering the +1m group of projects
+popular these features are in practice, we first analyzed build files
+\emph{statically}.  Considering the $>$1m group of projects
 (\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
@@
 tests sequentially within each process. \Mar{why 32-19 did not use
-  parallelization?} \Mar{what about free services (jenkins)?  how much
-  can you scale execution and how expensive would that be?}
+  parallelization?}
 
-\Fix{...Discuss impact...}
+\Fix{...Discuss impact...}\Mar{what about free services (jenkins)?
+  how much can you scale execution and how expensive would that be?}
 

### 2017-03-17 paper/modes.tex
pass on modes

@@
 level indicates parallelism that can be obtained through different
-machines on the network.  For examples, using virtual machines from a
-cloud service.  The machine space sits under the ``network space'' and
-provides \emph{low-level parallelism}.  In that case, computation can
-be offloaded at different CPUs within a machine and at different
-threads within each CPU.  Note that all these levels are
-complementary.  For example, lower-level parallelization schemes could
-leverage the computing power of server nodes in addition to the
-aggregate processing power of the farm.
+machines on the network.  For instance, using virtual machines from a
+cloud service to perform a distributed execution.  The machine space
+sits under the ``network space'' and provides a \emph{lower-level}
+parallelism.  In this case, computation can be offloaded at different
+CPUs within a machine and at different threads within each CPU.  Note
+that all these levels are complementary:  lower-level parallelization
+schemes could leverage the computing power of server nodes in addition
+to the aggregate processing power of the farm.
 
@@
 JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
-In the following we elaborate relevant features of testing frameworks
-and builds systems.  We focused on Java, Maven, and JUnit but the
+In the following we elaborate relevant features of build systems and
+testing frameworks.  We focused on Java, Maven, and JUnit but the
 discussion can be generalized to other language and tools.
@@
 }
+
+\subsection{Build Systems}
+\label{sec:builder}
+
+Several build systems support the execution of test suites in forked
+processes running a Java virtual machine (JVM).  Each spawned process
+runs an individual test suite and the builder outputs the aggregated
+reports. When the testing framework finishes the execution, the forked
+process can be reused for the next test suite in the queue. In this
+level, the number of forked processes must be proportional to the
+number of available CPUs otherwise, the high degree of concurrency
+may affect the execution performance.  For instance, if the underlying
+machine has four CPUs available, the builder could be configured to
+spawn one process on each core to favor parallelism (in contrast to
+several processes competing for a single core).
+
+%%Build systems delegate functionalities to the testing framework they
+%%use~\cite{maven-surefire-plugin}.  Figure~\ref{fig:surefire}
+%%illustrates how to configure Maven for mode
+%%\ParClassSeqMeth{}~--~classes sequentially (default) and test methods
+%%in parallel. Although this configuration is defined in the build file
+%%(\eg, \emph{pom.xml} on Maven), these settings are forwarded to the
+%%underlying testing framework (in this case, JUnit).
+
+%% \Jbc{I have to understand better how Surefire executes tests. I'm
+%% afraid it has its own wrapper classes and reuse JUnit core
+%% functionalities. I'm saying this because JUnit does not offer a finer
+%% control over thread numbers while this configuration is possible with
+%% Surefire} For example,
+
+%\Fix{we
+%  need to know how Maven allocates test classes to JVMs}
 
@@
 
-%% \Fix{-----}
-%% In JUnit, \emph{ParallelComputer} provides support to parallel
-%% execution: it instantiates a test runner with an
-%% \emph{ExecutorService} from the Java Concurrent API. Each test method
-%% is executed in a separated thread as the thread pool creates new
-%% threads on-demand and reuse them if any thread is available.
-%% \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
-
-%% As in \ParClassSeqMeth, the test runner has a cached thread poll but
-%% instead of executing test methods from a single test class, the test
-%% suite runner executes classes in separated threads and methods
-%% sequentially within each thread.
-
-%% \Jbc{I need to confirm this but AFAIK this is how it happens} As in
-%% \SeqClassParMeth, classes execute on separated threads but test
-%% methods are also executed in parallel. More precisely, there is a
-%% thread pool to execute classes in separated threads (\ie, like in
-%% \ParClassSeqMeth) and, within each class runner, there is an
-%% \emph{ExecutorService} to run test methods in parallel (\ie, like in
-%% \SeqClassParMeth).
-
-%% \Fix{-----}
-
-\subsection{Build Systems}
-
-Build systems delegate functionalities to the testing framework they
-use~\cite{maven-surefire-plugin}.  Figure~\ref{fig:surefire}
-illustrates how to configure Maven for mode
-\ParClassSeqMeth{}~--~classes sequentially (default) and test methods
-in parallel. Although this configuration is defined in the build file
-(\eg, \emph{pom.xml} on Maven), these settings are forwarded to the
-underlying testing framework (in this case, JUnit).
-
-%% \Jbc{I have to understand better how Surefire executes tests. I'm
-%% afraid it has its own wrapper classes and reuse JUnit core
-%% functionalities. I'm saying this because JUnit does not offer a finer
-%% control over thread numbers while this configuration is possible with
-%% Surefire} For example,
+\subsubsection*{Example}~ \Fix{The list below shortly describes
+the choices to control parallelism within a JVM.}
 
@@
 
-\subsubsection*{Forking JVMs}~
-Build systems often rovide the option to \emph{fork} JVM instances
-proportionally to available cores in the machine.  For Maven, the
-options \CodeIn{forkCount} and \CodeIn{reuseForks} control this
-feature~\cite{fork-and-parallel-execution-maven}.  Note that Maven
-allocates each test class to exactly one JVM and there is no guarantee
-to uniformly distribute load to each JVM given that the build system
-uses classes as the unit to specify test tasks.  Consequently, only
-combinations of fork with modes \Fix{??} are valid.
+%% \Fix{-----}
+%% In JUnit, \emph{ParallelComputer} provides support to parallel
+%% execution: it instantiates a test runner with an
+%% \emph{ExecutorService} from the Java Concurrent API. Each test method
+%% is executed in a separated thread as the thread pool creates new
+%% threads on-demand and reuse them if any thread is available.
+%% \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
 
-%\Fix{we
-%  need to know how Maven allocates test classes to JVMs}
+%% As in \ParClassSeqMeth, the test runner has a cached thread poll but
+%% instead of executing test methods from a single test class, the test
+%% suite runner executes classes in separated threads and methods
+%% sequentially within each thread.
+
+%% \Jbc{I need to confirm this but AFAIK this is how it happens} As in
+%% \SeqClassParMeth, classes execute on separated threads but test
+%% methods are also executed in parallel. More precisely, there is a
+%% thread pool to execute classes in separated threads (\ie, like in
+%% \ParClassSeqMeth) and, within each class runner, there is an
+%% \emph{ExecutorService} to run test methods in parallel (\ie, like in
+%% \SeqClassParMeth).
+
+%% \Fix{-----}

### 2017-03-20 paper/modes.tex
pass on modes

@@
+\newcommand{\Seq}{L0}
+\newcommand{\SeqClassParMeth}{L1}
+\newcommand{\ParClassSeqMeth}{L2}
+\newcommand{\ParClassParMeth}{L3}
+\newcommand{\Fork}{F}
+\newcommand{\ForkSeq}{\Fork{}\Seq{}}
+\newcommand{\ForkParMeth}{\Fork{}\SeqClassParMeth{}}
+
 \section{Parallel Execution of Test Suites}
@@
 JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
-In the following we elaborate relevant features of build systems and
-testing frameworks.  We focused on Java, Maven, and JUnit but the
-discussion can be generalized to other language and tools.
+In the following we elaborate relevant features of and testing
+frameworks build systems.  We focused on Java, Maven, and JUnit but
+the discussion can be generalized to other language and tools.
 
@@
 
-\subsection{Build Systems}
-\label{sec:builder}
-
-Several build systems support the execution of test suites in forked
-processes running a Java virtual machine (JVM).  Each spawned process
-runs an individual test suite and the builder outputs the aggregated
-reports. When the testing framework finishes the execution, the forked
-process can be reused for the next test suite in the queue. In this
-level, the number of forked processes must be proportional to the
-number of available CPUs otherwise, the high degree of concurrency
-may affect the execution performance.  For instance, if the underlying
-machine has four CPUs available, the builder could be configured to
-spawn one process on each core to favor parallelism (in contrast to
-several processes competing for a single core).
-
 %%Build systems delegate functionalities to the testing framework they
@@
 
-\newcommand{\Seq}{L0}
-\newcommand{\ParClassSeqMeth}{L1}
-\newcommand{\SeqClassParMeth}{L2}
-\newcommand{\ParClassParMeth}{L3}
+\begin{itemize}
+\item
+    \textbf{Sequential (\Seq).}~This configuration corresponds to the
+        default behaviour in a test execution. No parallelism is
+        involved.
+\item
+    \textbf{Sequential classes; parallel methods
+        (\SeqClassParMeth{}).}~At this level of parallelism, the
+        testing framework uses threads to run methods in parallel from
+        the assigned test class. Each test class runs sequentially.
+\item
+    \textbf{Parallel classes; sequential methods
+        (\ParClassSeqMeth{}).}~~At this level of parallelism, the
+        testing framework uses threads to run classes in parallel and
+        each test method runs sequentially within each thread.
+\item
+    \textbf{Parallel classes; Parallel methods
+        (\ParClassParMeth).}~This configuration corresponds
+        conceptually to the union of \ParClassSeqMeth{} and
+        \SeqClassParMeth{}: the testing framework runs test methods
+        from several classes in parallel.
+\end{itemize}
+
+Testing frameworks usually execute tests sequentially (\Seq{}) and may
+allow the developer to use an ordering criteria (\eg, test name).  For
+the \SeqClassParMeth{} setting, \Fix{elaborate and give example...}.
+For the \ParClassSeqMeth{} setting, \Fix{elaborate and give
+example...}. Finally, the \ParClassParMeth{} setting
+\Fix{...elaborate...}.
+
+\subsection{Build Systems}
+\label{sec:builder}
+
+Several build systems support the execution of test classes in forked
+processes running a Java virtual machine (JVM). Each spawned process
+runs a test class at time. In addition, the builder can reuse these
+processes to execute the next test classes in the queue according to
+the developer's preference. For instance, one might want the builder
+to spawn a new process for each test class to ensure maximum
+isolation.  To exploit parallelism at this level, the number of forked
+processes must be proportional to the number of available CPUs,
+otherwise, the high frequency of context-switching and concurrency
+(\ie, processes competing for a CPU time-slice) may affect the
+performance.  For instance, if the underlying machine has four CPUs
+available, the builder could be configured to spawn one process on
+each core in contrast to several processes competing for a single
+core.
+
+Builder-level parallelism can also complement some testing framework
+parallelism levels. For instance, \Fix{elaborate...}.  However, some
+settings may not take effect since only one test class can run in a
+forked process at time. For instance, \Fix{elaborate...}. To the best
+of our knowledge, we are unaware of any build system capable of
+running multiple classes at time within a forked process.
+
+In this paper, we use the prefix ``\Fork{}'' to indicate that a given
+testing configuration has the feature of spawning JVMs to run test
+classes enabled. The list below shortly describes the choices to
+control parallelism:
 
@@
 \item
-    \textbf{Sequential (\Seq).}~This configuration corresponds to the
-    sequential execution of test classes and, for each class,
-    sequential execution of their methods.  The execution order (of
-    classes and methods) is determined by the testing framework (\eg,
-    the order of methods returned by the Java Reflection
-    API)~\cite{junit-test-order}.
+    \textbf{Forked classes; sequential methods (\ForkSeq).}~\Fix{todo}
 \item
-    \textbf{Sequential classes; parallel methods
-      (\ParClassSeqMeth{}).}~This configuration corresponds to the
-    sequential execution of the test classes assigned to the JVM.
-    However, within each class, test methods run in parallel.
-\item
-    \textbf{Parallel classes; sequential methods
-      (\SeqClassParMeth{}).}~This configuration corresponds to the
-    parallel execution of test classes with sequential execution of
-    their test methods.
-\item
-    \textbf{Parallel methods (\ParClassParMeth).}~This configuration
-    corresponds to the parallel execution of any test method from any
-    class.
+    \textbf{Forked classes; parallel methods (\ForkParMeth).}~\Fix{todo}
 \end{itemize}
 
-\Seq{} is the default configuration for JUnit.  It does not use
-parallelism, in constrast to the other execution modes.  Considering
-use of parallelism, \ParClassParMeth{} is the most agressive mode.
-\ParClassSeqMeth{} and \SeqClassParMeth{} run sequentially either
-classes or methods.  Intuititvely, fixing one of these dimensions
-enables developers to better organize their test suites as to avoid
-dataraces~\Fix{cite}.  JUnit implements these modes through a set of
-customized classes (e.g., \CodeIn{ParallelComputer}).
-
-\subsubsection*{Example}~ \Fix{The list below shortly describes
-the choices to control parallelism within a JVM.}
+\subsubsection*{Illustration}~\Fix{elaborate}
 
@@
     basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    morekeywords={parallel, threadCount, perCoreThreadCount},
+    morekeywords={parallel, threadCount, perCoreThreadCount,
+    forkCount, reuseFork},
     deletekeywords={true}
@@
     <configuration>
+        <forkCount>1C</forkCount>
+        <reuseFork>true</true>
         <parallel>methods</parallel>
-        <threadCount>2</threadCount>
+        <threadCount>1</threadCount>
         <perCoreThreadCount>true</perCoreThreadCount>
@@
 \end{lstlisting}
-\caption{\label{fig:surefire} Example of Maven configuration: test
-  methods run in parallel (\CodeIn{parallel} parameter) using two
-  threads (\CodeIn{threadCount} parameter) per available core (flag
+    \caption{\label{fig:surefire} Maven configured with an
+    \Fork{}\SeqClassParMeth{} setting: test methods run in parallel
+    (\CodeIn{parallel} parameter) using two threads
+    (\CodeIn{threadCount} parameter) per available core (flag
     \CodeIn{perCoreThreadCount}).}

### 2017-03-23 paper/evaluation.tex
Quick fix

@@
 Figure~\ref{fig:rq1-barplot}). To reduce noise we did not consider
-projects with \shortg{}-running test suites as we observed\Mar{please,
-confirm} that those projects often\Mar{adjust} do not use parallelism;
+projects with \shortg{}-running test suites as we observed that
+\percentShortSequential{} of those projects do not use parallelism;
 including them would favor sequential execution in our analysis.
@@
 project with a valid configuration for running tests in parallel.
-False positive can happen because of comments, for instance.  To
-eliminate the cases of false positives and also to categorize true
+False positive can happen because of comments, for instance.  
+To eliminate the cases of false positives and also to categorize true
 positive cases, we complemented the initial mining step with a manual

### 2017-03-23 paper/plots/old/main.r
updated plots

@@ -1,0 +1,91 @@
+library("dplyr")
+library("ggplot2")
+
+TO_PDF <- T
+
+plot_timecost <- function(df) {
+  # Cost groups barplot
+  if (TO_PDF) {
+    pdf("barplot-timecost.pdf",
+        height = 3,
+        width = 2.3)
+  }
+  ggplot(data = df, aes(x = group, fill = test_success)) +
+    geom_bar(width = .8, position = "dodge") +
+    geom_text(
+      position = position_dodge(width = .75),
+      stat = "count",
+      aes(label = ..count.. , y = ..count.. + 5)
+    ) +
+    labs(y = "Frequency", x = "Group")
+  
+  # Time cost boxplots
+  if (TO_PDF) {
+    pdf("boxplot-timecost.pdf",
+        height = 3,
+        width = 2.7)
+  }
+  ggplot(data = df, aes(x = group, y = tmin, fill = test_success)) +
+    geom_boxplot() +  theme(strip.text = element_blank(),
+                            strip.background = element_blank()) +
+    facet_wrap( ~ group, scales = "free") +
+    labs(y = "Time cost (in minutes)", x = "Group")
+}
+
+# df <- read.csv(file.choose())
+df <- read.csv("dataset.csv")
+
+summarise(
+  group_by(df, test_success),
+  n = length(project_path),
+  tmin_xml = min(xml_test_time),
+  tmax_xml = max(xml_test_time),
+  tmin_mvn = min(maven_test_time),
+  tmax_mvn = max(maven_test_time)
+)
+
+print("Investigate: Build success but builder time = 0")
+select(filter(df, test_success == "true" &
+                maven_test_time <= 0),
+       project_path)
+print("Investigate: build success but xml time = 0")
+count(select(
+  filter(df, test_success == "true" &
+           xml_test_time <= 0),
+  project_path
+))
+
+df <- df %>% mutate(tmin = round(xml_test_time / 60, 2),
+                    group = sapply(xml_test_time, function(v) {
+                      if (v < 60) {
+                        return("short")
+                      }
+                      else if (v < 5 * 60) {
+                        return("medium")
+                      }
+                      return("long")
+                    }))
+
+plot_timecost(filter(df, xml_test_time > 0))
+
+#ggplot(data = df, aes(x = overhead_time)) +
[…]

### 2017-03-23 paper/modes.tex
pass on sec2

@@
 CPUs within a machine and at different threads within each CPU.  Note
-that all these levels are complementary:  lower-level parallelization
+that all these levels are complementary:  low-level parallelization
 schemes could leverage the computing power of server nodes in addition
@@
 
-This paper focuses at lower-level parallelism, which can be enabled
-through build systems and testing frameworks.  Given the proliferation
-of multi-core machines it is not surprising that testing frameworks
-provide today support for parallel test execution (e.g.,
-JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
-In the following we elaborate relevant features of and testing
-frameworks build systems.  We focused on Java, Maven, and JUnit but
-the discussion can be generalized to other language and tools.
+This paper focuses at low-level parallelism (\ie, machine and CPU
+space), which can be enabled through build systems and testing
+frameworks.  Given the proliferation of multi-core machines it is not
+surprising that testing frameworks provide today support for parallel
+test execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng},
+and NUnit~\cite{nunit}).  In the following we elaborate relevant
+features of and testing frameworks build systems.  We focused on Java,
+Maven, and JUnit but the discussion can be generalized to other
+language and tools.
 
@@
     \textbf{Sequential classes; parallel methods
-        (\SeqClassParMeth{}).}~At this level of parallelism, the
-        testing framework uses threads to run methods in parallel from
-        the assigned test class. Each test class runs sequentially.
+        (\SeqClassParMeth).}~When running a test class, the testing
+        framework executes methods on multiple threads. Each class
+        runs sequentially.
 \item
     \textbf{Parallel classes; sequential methods
-        (\ParClassSeqMeth{}).}~~At this level of parallelism, the
-        testing framework uses threads to run classes in parallel and
-        each test method runs sequentially within each thread.
+        (\ParClassSeqMeth{}).}~The testing framework runs test classes
+        on multiple threads and methods run sequentially within each
+        thread.
 \item
@@
         \SeqClassParMeth{}: the testing framework runs test methods
-        from several classes in parallel.
+        from several classes on multiple threads.
 \end{itemize}
 
-Testing frameworks usually execute tests sequentially (\Seq{}) and may
-allow the developer to use an ordering criteria (\eg, test name).  For
-the \SeqClassParMeth{} setting, \Fix{elaborate and give example...}.
-For the \ParClassSeqMeth{} setting, \Fix{elaborate and give
-example...}. Finally, the \ParClassParMeth{} setting
-\Fix{...elaborate...}.
+Typically, testing frameworks executes tests in sequence by default
+(\Seq{}) and may allow the developer to use an ordering criteria (\eg,
+test name).  For the \SeqClassParMeth{} setting, \Fix{elaborate...}.
+For the \ParClassSeqMeth{} setting, \Fix{elaborate...}. Finally, the
+\ParClassParMeth{} setting \Fix{...elaborate...}.
 
@@
         <parallel>methods</parallel>
-        <threadCount>1</threadCount>
-        <perCoreThreadCount>true</perCoreThreadCount>
+        <threadCount>5</threadCount>
     </configuration>
@@
 \end{lstlisting}
-    \caption{\label{fig:surefire} Maven configured with an
-    \Fork{}\SeqClassParMeth{} setting: test methods run in parallel
-    (\CodeIn{parallel} parameter) using two threads
-    (\CodeIn{threadCount} parameter) per available core (flag
-    \CodeIn{perCoreThreadCount}).}
+    \caption{\label{fig:surefire} Maven with a \ForkParMeth{}
+    configuration. Maven forks one JVM per core (\CodeIn{forkCount}
+    parameter) and \Jbc{check this $\rightarrow$} uses five threads
+    (\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
+    parameter) within each test class.}
+
+%%    test methods run in parallel (\CodeIn{parallel}
+%%    parameter) using two threads (\CodeIn{threadCount} parameter) per
+%%    available core (flag \CodeIn{perCoreThreadCount}).}
 \end{figure}

### 2017-03-24 paper/evaluation.tex
updated plots
pass on subjs

@@
 \newcommand{\numRQD}{RQ4}
-\newcommand{\numRQE}{RQ5}
-\newcommand{\numRQF}{RQ6}
+%%\newcommand{\numRQE}{RQ5}
+\newcommand{\numRQF}{RQ5}
 
@@
   regression test suites in open-source projects?}
-\newcommand{\RQB}{How time is distributed across test cases?}
+\newcommand{\RQB}{How the time cost is distributed across test cases?}
 \newcommand{\RQC}{How often parallelization settings appear in build
@@
 \newcommand{\RQD}{What is the impact of parallelization?}
-\newcommand{\RQE}{What factors contribute to improve performance
-  through parallelization?\Jbc{Previously as "When does
-    parallelization works and when it does not so great?"}}
-\newcommand{\RQF}{What are the limitations of parallelization?}
+%%\newcommand{\RQE}{What factors contribute to improve performance
+%%  through parallelization?\Jbc{Previously as "When does
+%%    parallelization works and when it does not so great?"}}
+\newcommand{\RQF}{What are the limitations of low-level parallelism?}
 
@@
     \item \textbf{\numRQD.} \RQD
-    \item \textbf{\numRQE.} \RQE
+%%    \item \textbf{\numRQE.} \RQE
     \item \textbf{\numRQF.} \RQF
@@
 test suites. We are interested to know if costly test suites are
-common in open-source projects. The second research question addresses
-the balance of regression tests: we want to investigate how the time
-cost is distributed among test cases. The third
-research question addresses our interest in understanding if
-developers are aware of parallelization features from testing
-frameworks available out-of-the-box through build systems (\eg, run
-JUnit test cases in parallel using Maven Surefire) and what settings
-are more often used.  The fourth research question addresses the
-impact of parallelism on the regression tests from our sample set. For
-subjects that use parallelization settings, we are interested in
-compare the execution performance when these settings are activated
-and deactivated (\ie, sequential execution) to evaluate the benefits.
-\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
-addresses the characteristics of regression tests from the previous
-experiment.  More specifically, we want to investigate if there is a
-relation between the balance of test execution (\ie, how uniformly
-distributed is the execution time across tests cases) and the usage of
-computational resources (\ie, if tests are mostly CPU or IO intense)
-that impacts the effectiveness of parallelization}.  Finally, the
-sixth research question discusses the limitations and insights to
-overcome the pitfalls of parallelization.
+common in open-source projects.  The second research question
+addresses the relationship of test cases and the overall execution
+cost: we are interested to investigate how the time cost is
+distributed among test cases.  In the third research question, we are
+in understanding if developers are aware of low-level parallelism
+features available out-of-the-box through build systems (\eg,
+configuring Maven to use JUnit with multiple threads to speedup test
+execution). In addition, we want to identify which configurations are
+often used and why they more popular (if any).  The fourth research
+question addresses the impact of low-level parallelism on the
+regression tests from our sample set. For subjects that use
+parallelization settings, we are interested to compare the execution
+performance when these settings are activated and deactivated (\ie,
+tests run sequentially).
+%%\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
+%%addresses the characteristics of regression tests from the previous
+%%experiment.  More specifically, we want to investigate if there is a
+%%relation between the balance of test execution (\ie, how uniformly
+%%distributed is the execution time across tests cases) and the usage of
+%%computational resources (\ie, if tests are mostly CPU or IO intense)
+%%that impacts the effectiveness of parallelization}.
+Finally, the fifth research question discusses the limitations and
+insights to overcome the pitfalls of parallelization.
 
@@
 the predominant language as the primary language.}; (2) the project
-has at least 100 stars; (3) latest update on (or after) January 1st,
-2016; (4) the \emph{readme} file contains the string \emph{mvn}.
+has at least 100 stars; (3) latest update on (or after) March 1st,
+2017; (4) the \emph{readme} file contains the string \emph{mvn}.
 
@@
 https://api.github.com/search/repositories?q=language:java
-        +stars:>=100+pushed:>=2016-01-01
+        +stars:>=100+pushed:>=2017-03-01
         +mvn%20in:readme+sort:stars
@@
     projects with the following criteria: (1) Java, (2) at least 100
-    stars, (3) updated on January 1st, 2016 (or later), (4) contains
+    stars, (3) updated on March 1st, 2017 (or later), (4) contains
     the string \emph{mvn} in the \emph{readme} file. Output is
@@
 files. We considered only projects with a \pomf{} file located in the
-root directory.  As of December 30th 2016, our search criteria
-returned 615 subjects. From the 615 downloaded projects, 46 were not
-Maven projects (or did not have a \pomf{} in the root directory) and
-159 were in a unstable revision.  From these 159 unstable subjects,
-\Jbc{elaborate what is unstable (\eg, (1) how many could not resolve
-dependencies? (2) how many could not compile sources and tests? (3)
-could not run tests due to incompatible testing environment?}. Our
-final set consists in \numSubjs{} testable subjects.
+root directory.  As of March 24th 2017, our search criteria returned
+\Fix{615} subjects. From the \Fix{615} downloaded projects, \Fix{46}
+were not Maven projects (or did not have a \pomf{} in the root
+directory) and 159 were in a unstable revision.  From these 159
+unstable subjects, \Jbc{elaborate what is unstable (\eg, (1) how many
+could not resolve dependencies? (2) how many could not compile sources
+and tests? (3) could not run tests due to incompatible testing
+environment?}. Our final set consists in \numSubjs{} testable
+subjects.
 
@@
 considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
-and compared the elapsed time to run their tests. \Jbc{Be clear about
-checking the elapsed time }.  Figure~\ref{fig:mvn-execution} shows the
-commands used in our script to test each subject. The main loop (lines
-5-11) iterates over the list of subjects and invokes Maven in
-separated steps (lines 7-9). To avoid inflating the measured time we
-executed Maven in different steps: we first compiled the source and
-test files (line 7), made all dependencies available locally (line 8)
-and later, we ran the tests in offline mode (line 9) to bypass package
-updates. After the execution, we used a regular expression on the
-output log to extract the elapsed time (line 10). Before collecting
-the time cost, we executed all subjects and randomly selected 100 logs
-to inspect and identify non-related tasks (\eg, \emph{javadoc}
-generation and static analysis) to ignore during the experiment (lines
-1-3).  To avoid noise from operating system events, we used a
-dedicated server remotely via SSH with the operating system running
-only essential services (\eg, the SSH server). In addition, we
-configured the \CodeIn{isolcpus} option from the Linux Kernel
-\cite{linux-kernel} to isolate six virtual CPUs to execute our
-experiment and the remaining CPUs to run the operating system. By
-isolating a set of virtual CPUs, we prevent context-switching from
-experiment processes and OS-related processes.
+and compared the elapsed time to run their tests.
+Figure~\ref{fig:mvn-execution} shows the commands used in our script
+to test each subject. The main loop (lines 5-11) iterates over the
+list of subjects and invokes Maven in separated steps (lines 7-9). To
+avoid inflating the measured time we executed Maven in different
+steps: we first compiled the source and test files (line 7), made all
+dependencies available locally (line 8) and later, we ran the tests in
+offline mode (line 9) to bypass package updates. After the execution,
+we used a regular expression on the output log to extract the elapsed
+time (line 10). Before collecting the time cost, we executed all
+subjects and randomly selected 100 logs to inspect and identify
+non-related tasks (\eg, \emph{javadoc} generation and static analysis)
+to ignore during the experiment (lines 1-3).  Also, measured the
+approximated overhead from the build system after skipping non-related
+tasks. We identified the generated test reports and compared the
+difference between the elapsed time reported from Maven and the sum of
+all test cases executed.
+To avoid noise from operating system events, we used a dedicated
+server remotely via SSH with the operating system running only
+essential services (\eg, the SSH server). In addition, we configured
+the \CodeIn{isolcpus} option from the Linux Kernel \cite{linux-kernel}
+to isolate six virtual CPUs to execute our experiment and the
+remaining CPUs to run the operating system. By isolating a set of
+virtual CPUs, we prevent context-switching from experiment processes
+and OS-related processes.
 
@@
     \centering
-    \begin{subfigure}{0.21\textwidth}
+    \begin{subfigure}{0.4\textwidth}
         \centering
@@
     \end{subfigure}%
-    ~ 
-    \begin{subfigure}{0.25\textwidth}
+    \qquad
+    \begin{subfigure}{0.4\textwidth}
         \centering
@@
     \centering
-    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
+    \includegraphics[width=0.32\textwidth]{plots/parallel-modes.pdf}
     \caption{\label{fig:freqmodes}Distribution of parallel modes

### 2017-03-24 paper/evaluation.tex
pass on text

@@
 variability of the time cost from subjects out of the \shortg{} group.
+\Jbc{these results will be updated $\rightarrow$}
 Figure~\ref{fig:rq1-boxplot} shows the time cost distribution of each
@@
     \centering
-    \begin{subfigure}{0.4\textwidth}
+    \begin{subfigure}{0.24\textwidth}
         \centering
@@
     \end{subfigure}%
-    \qquad
-    \begin{subfigure}{0.4\textwidth}
+    ~
+    \begin{subfigure}{0.24\textwidth}
         \centering
@@
 
-Given that \percentMedLongRunning{} of the projects are costly (\ie,
-\numMedLong{} projects from \medg{} and \longg{}), we concluded that
-time-consuming regression test suites are relatively frequent in
-open-source projects.  It is important to mention that
-Figure~\ref{fig:rq1-barplot} represents a lower bound estimation for
-time cost because some projects omit long-running tests on their
-default execution. For instance, it is necessary to invoke Maven with
-additional parameters to run integration tests from project
-\CodeIn{apache.maven-surefire} (nearly 30 min in our environment).
-Also, some tests may finish earlier than expected due to existing bugs
-on the ongoing revision.  From the \numSubjs{} compiled projects, 286
-successfully executed all tests and 118 reported test failures.
-\Jbc{elaborate failed subjects: how much \% of the tests failed?}
+\Jbc{these results will be updated $\rightarrow$}
+It is important to mention that Figure~\ref{fig:rq1-barplot}
+represents a lower bound estimation for time cost because some
+projects omit long-running tests on their default execution. For
+instance, it is necessary to invoke Maven with additional parameters
+to run integration tests from project \CodeIn{apache.maven-surefire}
+(nearly 30 min in our environment).  Also, some tests may finish
+earlier than expected due to existing bugs on the ongoing revision.
+From the \numSubjs{} compiled projects, 286 successfully executed
+all tests and 118 reported test failures.
+
+\begin{center}
+\fbox{
+\begin{minipage}{8cm}
+    \textit{Answering \numRQA{}:}~\emph{Given that
+    \percentMedLongRunning{} of the projects are costly (\ie,
+    \numMedLong{} projects from \medg{} and \longg{}), we concluded
+    that time-consuming regression test suites are relatively frequent
+    in open-source projects.}
+\end{minipage}
+}
+\end{center}
 
@@
 
+\Jbc{pending updates! $\rightarrow$}
 Section~\ref{sec:rqA} showed that medium and long-running projects are
@@
 
-Overall, results indicate that projects with a very small number of
-tests monopolizing end-to-end execution time were rare.
-
-\begin{table}[h!]
-
-\end{table}
+\begin{center}
+\fbox{
+\begin{minipage}{8cm}
+    \textit{Answering \numRQB{}:}~\emph{Overall, results indicate that
+    projects with a very small number of tests monopolizing end-to-end
+    execution time were rare.}
+\end{minipage}
+}
+\end{center}
 

### 2017-03-25 paper/evaluation.tex

@@
 the predominant language as the primary language.}; (2) the project
-has at least 100 stars; (3) latest update on (or after) March 1st,
-2017; (4) the \emph{readme} file contains the string \emph{mvn}.
+has at least 100 stars; (3) latest update on (or after) January 1st,
+2016; (4) the \emph{readme} file contains the string \emph{mvn}.
 
@@
 https://api.github.com/search/repositories?q=language:java
-        +stars:>=100+pushed:>=2017-03-01
+        +stars:>=100+pushed:>=2016-01-01
         +mvn%20in:readme+sort:stars
@@
     projects with the following criteria: (1) Java, (2) at least 100
-    stars, (3) updated on March 1st, 2017 (or later), (4) contains
+    stars, (3) updated on January 1st, 2016 (or later), (4) contains
     the string \emph{mvn} in the \emph{readme} file. Output is
@@
 files. We considered only projects with a \pomf{} file located in the
-root directory.  As of March 24th 2017, our search criteria returned
-\Fix{615} subjects. From the \Fix{615} downloaded projects, \Fix{46}
-were not Maven projects (or did not have a \pomf{} in the root
-directory) and 159 were in a unstable revision.  From these 159
-unstable subjects, \Jbc{elaborate what is unstable (\eg, (1) how many
-could not resolve dependencies? (2) how many could not compile sources
-and tests? (3) could not run tests due to incompatible testing
-environment?}. Our final set consists in \numSubjs{} testable
-subjects.
+root directory.  As of March 25th 2017, our search criteria returned
+\SubjectsGithub{} subjects.  From the \SubjectsGithub{} downloaded
+projects, \SubjectsGithubNotMaven{} were not Maven projects (or did
+not have a \pomf{} in the root directory) and
+\SubjectsGithubNotTestable{} were in an untestable revision (\eg,
+missing dependencies or incompatible testing environment). To ensure
+that our sample set is stable, we retested the remaining subjects to
+eliminate flaky tests (total of \SubjectsGithubFlaky{} subjects). Our
+final set consists in \numSubjs{} testable subjects.
 

### 2017-03-26 paper/evaluation.tex
Updating machine specs

@@
 
-To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
-processor machine with eight virtual CPUs (four cores with two native
-threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
-(64-bit version). Software settings include \Comment{the Linux
-\emph{sysstat} package to measure performance, }git to fetch subjects,
-Java 8 and Maven 3.3.9 to build and test subjects. Our evaluation
-scripts depends on Python 3.4 and Bash to execute and R to analyze the
-data. For replication, all source artifacts are publicly available at
+%To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
+%processor machine with eight virtual CPUs (four cores with two native
+%threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
+
+To run our experiments, we used a Virtual Machine with four cores and
+4 GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).
+Software settings include \Comment{the Linux \emph{sysstat} package
+to measure performance, }git to fetch subjects, Java 8 and Maven
+3.3.9 to build and test subjects. Our evaluation scripts depends on
+Python 3.4 and Bash to execute and R to analyze the data.
+For replication, all source artifacts are publicly available at
 \Fix{create gh-pages}, including supporting scripts (\eg, the script

### 2017-03-27 paper/evaluation.tex
Placeholder

@@
 
-\subsubsection{Distribution of parallel modes}
+\subsubsection{ \Luis{Static $\rightarrow$} Distribution of parallel
+modes}
 
@@
 checked each configuration, we could elaborate how these settings are
-used.} \Fix{Missing conclusion: Fork the most used configuration}
+used.} \Fix{Missing conclusion: Fork with class parallelism is the 
+most used configuration}
+
+\subsubsection{Dynamic distribution of parallel modes}
+
+\Luis{placeholder}
 

### 2017-03-27 paper/evaluation.tex
reworked rq3

--- 2017-03-26 paper/evaluation.tex
@@
 \newcommand{\RQB}{How the time cost is distributed across test cases?}
-\newcommand{\RQC}{How often parallelization settings appear in build
-  files?}
+\newcommand{\RQC}{How often developers add support to parallel
+execution of test suites?}
 \newcommand{\RQD}{What is the impact of parallelization?}
@@
 
-To evaluate the presence of parallelization settings (see Section
-\ref{sec:modes}), we considered all projects classified as \medg{} and
-\longg{}-running, a total of \numMedLong{} subjects (see
-Figure~\ref{fig:rq1-barplot}). To reduce noise we did not consider
-projects with \shortg{}-running test suites as we observed that
-\percentShortSequential{} of those projects do not use parallelism;
-including them would favor sequential execution in our analysis.
+To evaluate the support of parallelization in test suites, we
+considered all projects classified as \medg{} and \longg{}-running, a
+total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
+reduce noise we did not consider projects with \shortg{}-running test
+suites as we observed that \percentShortSequential{} of those projects
+do not use parallelism; including them would favor sequential
+execution in our analysis.
 
-To answer \numRQC{} we initially mined build files (\ie, \pomf{}) that
-contain parallelization keywords, namely \CodeIn{forkMode},
-\CodeIn{forkCount}, and \CodeIn{parallel}.  According to the Maven
-surefire documentation\Fix{cite surefire doc}, any configuration to
-run tests in parallel must contain one of these keywords. This mining
-step, however, is not sound as a matching project may not indicate a
-project with a valid configuration for running tests in parallel.
-False positive can happen because of comments, for instance.  
-To eliminate the cases of false positives and also to categorize true
-positive cases, we complemented the initial mining step with a manual
-inspection of files.
+To answer \numRQC{} we initially configured Maven to output
+configuration settings and re-executed the tests to collect and
+classify the test suites according to its level of parallelization
+(see Section \ref{sec:modes}).  The rationale is that if a test suite
+is configured to run in parallel, Maven is going to display the
+configuration and we can classify it according to its parallelization
+level.  We are interested to know how frequent are parallel executions
+and what configurations are more popular.  According to Maven's
+documentation\Fix{cite surefire doc}, the set of parameters to run
+tests in parallel is described as follows: \CodeIn{parallel} defines
+the parallelism granularity within a JVM (\eg, methods or classes);
+\CodeIn{threadCounter} defines the size of the thread pool; and
+\CodeIn{forkCount} defines the number of forked JVMs. Additional
+options exists and depends on theses parameters to take effect. To
+avoid waiting all tests to terminate, we just run the bootstrap phase
+and we skip the actual test execution. \Jbc{Missing: explain how we
+mapped the configurations to parallel level.}
+Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
+    \caption{\label{fig:freqmodes-dynamic}Distribution of parallel modes 
+    identified dynamically in a subset of \numProjectsPar{} projects.
+    A project may have support to more than one parallel mode. Also,
+    a project may run only a subset tests in parallel by default.}
+\end{figure}
+
+\Fix{Elaborate findings....}
+
+\subsubsection{Support of parallelization configuration in build files}
+
+We complemented our previous investigation with a static analysis of
+several \pomf{} files from the \numMedLong{} subjects. The rationale
+is that some projects might not enable parallelism in the default
+execution. \Jbc{Remember to explain that we need the previous analysis
+because some configurations are unreachable statically when inherited
+from some external module}.
+
+%% To answer \numRQC{} we initially mined build files (\ie, \pomf{}) .
+%% must contain one of these keywords that
+%% contain parallelization keywords, namely \CodeIn{forkMode},
+%% \CodeIn{forkCount}, and \CodeIn{parallel}.
+
+This mining step, however, is not sound as a matching project may not
+indicate a project with a valid configuration for running tests in
+parallel.  False positive can happen because of comments, for
+instance.  To eliminate the cases of false positives and also to
+categorize true positive cases, we complemented the initial mining
+step with a manual inspection of files.
 
@@
 
-\subsubsection{Distribution of parallel modes}
-
 From the \numProjectsPar{} projects identified above, we investigated
@@
 (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
-Figure~\ref{fig:freqmodes} summarizes our findings. \Jbc{Given that we
+Figure~\ref{fig:freqmodes-static} summarizes our findings. \Jbc{Given that we
 checked each configuration, we could elaborate how these settings are
@@
     \centering
-    \includegraphics[width=0.32\textwidth]{plots/parallel-modes.pdf}
-    \caption{\label{fig:freqmodes}Distribution of parallel modes
-    identified in a subset of \numProjectsPar{} projects (unused modes
-    omitted). A single project may have support to more than one
-    parallel mode.}
+    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
+    \caption{\label{fig:freqmodes-static}Distribution of parallel modes 
+    identified statically in a subset of \numProjectsPar{} projects.
+    A project may have support to more than one parallel mode.}
 \end{figure}
+
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
+      that \Jbc{summarize results from both parts (static and
+      dynamic)}.} 
+  \end{minipage}
+}
+\end{center}
 
@@
 
-\Fix{---------------------}
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+      \textit{Answering \numRQD{}:}~\emph{\Jbc{summarize
+      findings.....}}
+  \end{minipage}
+}
+\end{center}
 

### 2017-03-28 paper/modes.tex
Sec 2: reorganized + commented unnecessary details + removed some TODOs

@@
 The list below shortly describes the choices to control parallelism
-within a JVM.
+within a Java virtual machine (JVM).
 
@@
 
-Several build systems support the execution of test classes in forked
-processes running a Java virtual machine (JVM). Each spawned process
-runs a test class at time. In addition, the builder can reuse these
-processes to execute the next test classes in the queue according to
-the developer's preference. For instance, one might want the builder
-to spawn a new process for each test class to ensure maximum
-isolation.  To exploit parallelism at this level, the number of forked
-processes must be proportional to the number of available CPUs,
-otherwise, the high frequency of context-switching and concurrency
-(\ie, processes competing for a CPU time-slice) may affect the
-performance.  For instance, if the underlying machine has four CPUs
-available, the builder could be configured to spawn one process on
-each core in contrast to several processes competing for a single
-core.
-
-Builder-level parallelism can also complement some testing framework
-parallelism levels. For instance, \Fix{elaborate...}.  However, some
-settings may not take effect since only one test class can run in a
-forked process at time. For instance, \Fix{elaborate...}. To the best
-of our knowledge, we are unaware of any build system capable of
-running multiple classes at time within a forked process.
-
-In this paper, we use the prefix ``\Fork{}'' to indicate that a given
-testing configuration has the feature of spawning JVMs to run test
-classes enabled. The list below shortly describes the choices to
-control parallelism:
+The list below shortly describes the choices to control parallelism
+through build systems:
 
@@
 \item
-    \textbf{Forked classes; sequential methods (\ForkSeq).}~\Fix{todo}
+    \textbf{Forked classes; sequential methods (\ForkSeq).}~This
+        configuration corresponds to the parallel execution of test
+        classes on different JVMs and test methods run sequentially
+        within each JVM.
 \item
-    \textbf{Forked classes; parallel methods (\ForkParMeth).}~\Fix{todo}
+    \textbf{Forked classes; parallel methods (\ForkParMeth).}~This
+        configuration corresponds to the parallel execution of test
+        classes on different JVMs and test methods run on multiple
+        threads within each JVM.
 \end{itemize}
 
-\subsubsection*{Illustration}~\Fix{elaborate}
+Several build systems support the execution of test classes in forked
+processes running a JVM. In the \ForkSeq{} configuration, each spawned
+process runs a different test class at time and the builder merges the
+results from each execution. In the \ForkParMeth{} configuration, the
+build system forwards settings to the underlying testing framework to
+enable parallel execution within each process in addition to running
+test classes on different processes.  However, some configurations
+(\eg, \ParClassSeqMeth) may not take effect since only one test class
+can run in a forked process at time.  To the best of our knowledge, we
+are unaware of any build system capable of running multiple classes at
+time within a forked process.  \Comment{In addition, the builder can
+reuse these processes to execute the next test classes in the queue
+according to the developer's preference. For instance, one might want
+the builder to spawn a new process for each test class to ensure
+maximum isolation. Notice that to exploit parallelism at build system
+level, the number of forked processes must be proportional to the
+number of available CPUs, otherwise, the high frequency of
+context-switching and processes competing for a CPU may degrade the
+execution performance  \Jbc{$\leftarrow$ I'm not sure if we should
+keep this. We can remove it if necessary}.}
+
+%% In this paper, we use the prefix ``\Fork{}'' to indicate that a given
+%% testing configuration has the feature of spawning JVMs to run test
+%% classes enabled.
+
+\subsubsection*{Illustration}~\Fix{elaborate the following example to
+conclude this section}
 
@@
         <forkCount>1C</forkCount>
-        <reuseFork>true</true>
         <parallel>methods</parallel>
@@
     (\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
-    parameter) within each test class.}
+    parameter) within each JVM.}
 

### 2017-03-28 paper/modes.tex
removed reminder (solved)

@@
     configuration.  Maven forks one JVM per core (\CodeIn{forkCount}
-    parameter) and \Jbc{check this $\rightarrow$} uses five threads
-    (\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
-    parameter) within each JVM.}
+    parameter) and uses five threads (\CodeIn{threadCount} parameter)
+    to run methods (\CodeIn{parallel} parameter) within each JVM.}
 

### 2017-03-28 paper/evaluation.tex
pass on eval RQs and motivation

@@
 We are interested in understanding the prevalence of time-consuming
-test suites and main sources of cost. We want to understand how the
-execution cost is distributed on test cases within a test suite and
-how developers approach test execution. Based on that, we study
-parallelization of testing frameworks.  More precisely, we investigate
-how prevalent test parallelization is, the potential for improving
-execution cost, issues of flakiness that hinders the use of
-parallelization, and how to address those issues.  More specifically,
-we pose the following research questions:
+test suites and main sources of execution cost. We want to understand
+how the execution cost is distributed on test cases within a test
+suite and how developers approach test execution. Based on that, we
+study parallelization of testing frameworks and build systems.  More
+precisely, we investigate how prevalent test parallelization is, the
+potential for improving execution cost, issues of flakiness that
+hinders the use of parallelization, and how to address those issues.
+More specifically, we pose the following research questions:
 
@@
 \newcommand{\RQB}{How the time cost is distributed across test cases?}
-\newcommand{\RQC}{How often developers add support to parallel
-execution of test suites?}
+\newcommand{\RQC}{How often developers provides support to parallel
+execution to amortize the execution cost?}
 \newcommand{\RQD}{What is the impact of parallelization?}
@@
 addresses the relationship of test cases and the overall execution
-cost: we are interested to investigate how the time cost is
-distributed among test cases.  In the third research question, we are
-in understanding if developers are aware of low-level parallelism
-features available out-of-the-box through build systems (\eg,
-configuring Maven to use JUnit with multiple threads to speedup test
-execution). In addition, we want to identify which configurations are
-often used and why they more popular (if any).  The fourth research
-question addresses the impact of low-level parallelism on the
-regression tests from our sample set. For subjects that use
-parallelization settings, we are interested to compare the execution
-performance when these settings are activated and deactivated (\ie,
-tests run sequentially).
+cost: we are interested to investigate how the execution time is
+distributed among test cases.  In the third research question, we
+investigate if developers consider low-level parallelism features
+available out-of-the-box (see Section~\ref{sec:modes}). In addition,
+we want to identify what configurations are often used and why they
+are more popular (if any).  The fourth research question addresses the
+impact of low-level parallelism on test execution from projects in our
+sample set. We want to identify subjects that already use test
+parallelization and compare their performance in contrast to
+sequential execution. In addition, we are interested in evaluating the
+performance of sequential test suites with different parallelization
+settings.
 %%\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
@@
 parallelization settings identified in \numRQC{} and compared their
-time cost with sequential execution. \Jbc{should have a sentence to
-motivate this RQ} 
+time cost with sequential execution. We are interested in measuring the
+execution speedup (if any) when the parallelization settings are
+activated.
 \Jbc{explain methodology}.

### 2017-03-29 paper/evaluation.tex
pass on text and added subjects piechart

@@
 project). We used Maven as a reference due to its popularity on Java
-projects and to automate our evaluation scripts.
-Figure~\ref{fig:subject-query} illustrates the query as an HTTP
-request.
+projects and to automate our evaluation scripts. A Maven project may
+contain several sub-modules with multiple \pomf{} files. We considered
+only projects with a \pomf{} file located in the root directory.
+Figure~\ref{fig:subject-query} illustrates the query to the \github{}
+API as an HTTP request.
 
@@
 
-A Maven project may contain several sub-modules with multiple \pomf{}
-files. We considered only projects with a \pomf{} file located in the
-root directory.  As of March 25th 2017, our search criteria returned
-\SubjectsGithub{} subjects.  From the \SubjectsGithub{} downloaded
-projects, \SubjectsGithubNotMaven{} were not Maven projects (or did
-not have a \pomf{} in the root directory) and
-\SubjectsGithubNotTestable{} were in an untestable revision (\eg,
-missing dependencies or incompatible testing environment). To ensure
-that our sample set is stable, we retested the remaining subjects to
-eliminate flaky tests (total of \SubjectsGithubFlaky{} subjects). Our
-final set consists in \numSubjs{} testable subjects.
+As of March 25th 2017, our search criteria returned \SubjectsGithub{}
+subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
+the \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
+were not Maven projects (or did not have a \pomf{} in the root
+directory) and \SubjectsGithubNotTestable{} were in an untestable
+revision (\eg, missing dependencies or incompatible testing
+environment). To ensure that our sample set is stable, we retested the
+remaining subjects to eliminate flaky tests (total of
+\SubjectsGithubFlaky{} subjects). Our final set consists in
+\numSubjs{} testable subjects.
+
+\vspace{-3ex}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.25\textwidth]{plots/subjects/subjects.pdf}
+    \caption{\label{fig:subjects}\Fix{this is mocked data!}}
+\end{figure}
+\vspace{-2ex}
 
@@
 
-To run our experiments, we used a Virtual Machine with four cores and
-4 GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).
-Software settings include \Comment{the Linux \emph{sysstat} package
-to measure performance, }git to fetch subjects, Java 8 and Maven
-3.3.9 to build and test subjects. Our evaluation scripts depends on
-Python 3.4 and Bash to execute and R to analyze the data.
-For replication, all source artifacts are publicly available at
+To run our experiments, we used a dedicated server with eight cores
+and 16 GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit
+version).  Software settings include \Comment{the Linux \emph{sysstat}
+package to measure performance, }git to fetch subjects, Java 8 and
+Maven 3.3.9 to build and test subjects. Our evaluation scripts depends
+on Python 3.4 and Bash to execute and R to analyze the data.  For
+replication, all source artifacts are publicly available at
 \Fix{create gh-pages}, including supporting scripts (\eg, the script

### 2017-03-29 paper/evaluation.tex
fixed sardine specs

@@
 
-%To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
-%processor machine with eight virtual CPUs (four cores with two native
-%threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
-
-To run our experiments, we used a dedicated server with eight cores
-and 16 GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit
-version).  Software settings include \Comment{the Linux \emph{sysstat}
-package to measure performance, }git to fetch subjects, Java 8 and
-Maven 3.3.9 to build and test subjects. Our evaluation scripts depends
-on Python 3.4 and Bash to execute and R to analyze the data.  For
-replication, all source artifacts are publicly available at
+To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
+processor machine with eight virtual CPUs (four cores with two native
+threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
+(64-bit version).  Software settings include \Comment{the Linux
+\emph{sysstat} package to measure performance, }git to fetch subjects,
+Java 8 and Maven 3.3.9 to build and test subjects. Our evaluation
+scripts depends on Python 3.4 and Bash to execute and R to analyze the
+data.  For replication, all source artifacts are publicly available at
 \Fix{create gh-pages}, including supporting scripts (\eg, the script

### 2017-03-29 paper/evaluation.tex
added missing plot

@@
     \centering
-    \includegraphics[width=0.25\textwidth]{plots/subjects/subjects.pdf}
+    \includegraphics[width=0.25\textwidth]{plots/plot-subjects/subjs.pdf}
     \caption{\label{fig:subjects}\Fix{this is mocked data!}}
@@
 considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
-and compared the elapsed time to run their tests.
+and compared the elapsed time to run their tests. \Jbc{The following
+steps may change $\rightarrow$}
 Figure~\ref{fig:mvn-execution} shows the commands used in our script
@@
 non-related tasks (\eg, \emph{javadoc} generation and static analysis)
-to ignore during the experiment (lines 1-3).  Also, measured the
-approximated overhead from the build system after skipping non-related
-tasks. We identified the generated test reports and compared the
-difference between the elapsed time reported from Maven and the sum of
-all test cases executed.
-To avoid noise from operating system events, we used a dedicated
-server remotely via SSH with the operating system running only
-essential services (\eg, the SSH server). In addition, we configured
-the \CodeIn{isolcpus} option from the Linux Kernel \cite{linux-kernel}
-to isolate six virtual CPUs to execute our experiment and the
-remaining CPUs to run the operating system. By isolating a set of
-virtual CPUs, we prevent context-switching from experiment processes
-and OS-related processes.
+to ignore during the experiment (lines 1-3).  To avoid noise from
+operating system events, we used a dedicated server remotely via SSH
+with the operating system running only essential services (\eg, the
+SSH server). In addition, we configured the \CodeIn{isolcpus} option
+from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
+to execute our experiment and the remaining CPUs to run the operating
+system. By isolating a set of virtual CPUs, we prevent
+context-switching from experiment processes and OS-related processes.
 

### 2017-03-29 paper/evaluation.tex
pass on text

@@
 
-\Jbc{these results will be updated $\rightarrow$}
-It is important to mention that Figure~\ref{fig:rq1-barplot}
-represents a lower bound estimation for time cost because some
+\Jbc{these results will be updated $\rightarrow$} It is important to
+mention that Figure~\ref{fig:rq1-barplot} represents a lower bound
+estimation for time cost because some tests may finish earlier than
+expected due to existing bugs on the ongoing revision.  From the
+\numSubjs{} compiled projects, \numSubjsPass{} successfully executed
+all tests and \numSubjsFail{} reported test failures.  Also, some
 projects omit long-running tests on their default execution. For
@@
 to run integration tests from project \CodeIn{apache.maven-surefire}
-(nearly 30 min in our environment).  Also, some tests may finish
-earlier than expected due to existing bugs on the ongoing revision.
-From the \numSubjs{} compiled projects, 286 successfully executed
-all tests and 118 reported test failures.
+(nearly 30 min in our environment).
 
@@
 
-To evaluate the support of parallelization in test suites, we
-considered all projects classified as \medg{} and \longg{}-running, a
-total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
-reduce noise we did not consider projects with \shortg{}-running test
-suites as we observed that \percentShortSequential{} of those projects
-do not use parallelism; including them would favor sequential
-execution in our analysis.
+To evaluate the support of parallelization to run tests, we
+investigate if there are projects with parallel execution enabled by
+default and what configurations are more popular. In addition, we
+complement our investigation by analyzing several build files (\ie,
+\pomf{}) to identify projects that supports parallel execution but
+require additional execution parameters to enable this feature.  We
+describe our approach as follows:
 
-To answer \numRQC{} we initially configured Maven to output
-configuration settings and re-executed the tests to collect and
-classify the test suites according to its level of parallelization
-(see Section \ref{sec:modes}).  The rationale is that if a test suite
-is configured to run in parallel, Maven is going to display the
-configuration and we can classify it according to its parallelization
-level.  We are interested to know how frequent are parallel executions
-and what configurations are more popular.  According to Maven's
-documentation\Fix{cite surefire doc}, the set of parameters to run
-tests in parallel is described as follows: \CodeIn{parallel} defines
-the parallelism granularity within a JVM (\eg, methods or classes);
-\CodeIn{threadCounter} defines the size of the thread pool; and
-\CodeIn{forkCount} defines the number of forked JVMs. Additional
-options exists and depends on theses parameters to take effect. To
-avoid waiting all tests to terminate, we just run the bootstrap phase
-and we skip the actual test execution. \Jbc{Missing: explain how we
-mapped the configurations to parallel level.}
-Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.
+\subsubsection{Test execution with parallelism enabled by default}
+\label{sec:rqC-1}
+
+Initially, we configured Maven to output all configuration variables.
+The rationale is that, for each project's module, we can capture
+relevant configurations and classify their parallelization level (see
+Section \ref{sec:modes}) based on their values. To avoid waiting all
+tests to terminate, we just run the bootstrap phase and we skip the
+actual test execution.
+
+According to Maven's documentation \Fix{cite surefire doc}, any
+parallelization setting depends either on (1) \CodeIn{parallel} to
+define the parallelism level within a JVM followed by
+\CodeIn{threadCounter} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
+in older versions) to define the number of forked JVMs. For each test
+execution, we look for theses parameters and their values to classify
+them.  \Jbc{Missing: explain how we mapped the configurations to
+parallel level.} Figure~\ref{fig:freqmodes-dynamic} summarizes our
+findings.
 
@@
     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
-    \caption{\label{fig:freqmodes-dynamic}Distribution of parallel modes 
-    identified dynamically in a subset of \numProjectsPar{} projects.
-    A project may have support to more than one parallel mode. Also,
-    a project may run only a subset tests in parallel by default.}
+    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
+    caption}Distribution of parallel modes identified dynamically in a
+    subset of \numProjectsPar{} projects.  A project may have support
+    to more than one parallel mode. Also, a project may run only a
+    subset tests in parallel by default.}
 \end{figure}
@@
 \subsubsection{Support of parallelization configuration in build files}
+\label{sec:rqC-2}
 
-We complemented our previous investigation with a static analysis of
-several \pomf{} files from the \numMedLong{} subjects. The rationale
-is that some projects might not enable parallelism in the default
-execution. \Jbc{Remember to explain that we need the previous analysis
-because some configurations are unreachable statically when inherited
-from some external module}.
+% considered all projects classified as \medg{} and \longg{}-running, a
+% total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
+% reduce noise we did not consider projects with \shortg{}-running test
+% suites as we observed that \percentShortSequential{} of those projects
+% do not use parallelism; including them would favor sequential
+% execution in our analysis.
 
-%% To answer \numRQC{} we initially mined build files (\ie, \pomf{}) .
-%% must contain one of these keywords that
-%% contain parallelization keywords, namely \CodeIn{forkMode},
-%% \CodeIn{forkCount}, and \CodeIn{parallel}.
-
-This mining step, however, is not sound as a matching project may not
-indicate a project with a valid configuration for running tests in
-parallel.  False positive can happen because of comments, for
-instance.  To eliminate the cases of false positives and also to
-categorize true positive cases, we complemented the initial mining
-step with a manual inspection of files.
+To extend our initial investigation, we mined several \pomf{} files
+must contain one of these keywords that contain parallelization
+keywords, namely \CodeIn{forkMode}, \CodeIn{forkCount}, and
+\CodeIn{parallel}.  This mining step, however, is not sound as a
+matching project may not indicate a project with a valid configuration
+for running tests in parallel.  False positive can happen because of
+comments, for instance.  To eliminate the cases of false positives and
+also to categorize true positive cases, we complemented the initial
+mining step with a manual inspection of files.
 
@@
 distributed across \numProjectsPar{} projects from our sample.
-\emph{From these results we found that $\sim$51\% of medium and
-long-running projects do not use parallel features to run test
-suites.}\Mar{please make it consistent with research
-question}\Mar{explain this is over(under)-estimated...}
+% 
+% \emph{From these results we found that $\sim$51\% of medium and
+% long-running projects do not use parallel features to run test
+% suites.}\Mar{please make it consistent with research
+% question}\Mar{explain this is over(under)-estimated...}
 
@@
 To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
-parallelization settings identified in \numRQC{} and compared their
-time cost with sequential execution. We are interested in measuring the
-execution speedup (if any) when the parallelization settings are
-activated.
-\Jbc{explain methodology}.
+parallelization settings enabled by default identified in \numRQC{}
+and compared their time cost with sequential execution. We are
+interested in measuring the execution speedup (if any) when the
+parallelization settings are activated. It is important to mention
+that we ignored the remaining \Fix{??} subjects identified in
+Section~\ref{sec:rqC-2} because it would be impractical to execute
+each subject on specific conditions to measure the impact of
+parallelization.
+
+To enforce sequential execution, \Jbc{explain methodology}.
 

### 2017-03-30 paper/plots/plot-subjects/script.r
updated subjs data

@@ -1,12 +1,0 @@
-library("dplyr")
-library("ggplot2")
-
-df <- read.csv("mocked-data.csv")
-pdf("subjs.pdf", width = 2.8, height = 2)
-
-df <- summarise(group_by(df, group), length = length(group)) 
-ggplot(df, aes(x = factor(1), y = length, fill = group)) +
-    theme_void() +
-    geom_bar(stat = "identity", width = 1) +
-    geom_text(aes(label = length), position = position_stack(vjust = 0.5)) +
-    coord_polar("y")

### 2017-03-30 paper/evaluation.tex
updated subjs data
RQ4 brief methodology

@@
 
-\vspace{-3ex}
+\vspace{-1ex}
 \begin{figure}[ht]
     \centering
-    \includegraphics[width=0.25\textwidth]{plots/plot-subjects/subjs.pdf}
+    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
     \caption{\label{fig:subjects}\Fix{this is mocked data!}}
@@
 To enforce sequential execution, \Jbc{explain methodology}.
+\Luis{
+Primeiro nos avaliamos os \pomf{} de alguns projetos long que 
+rodavam em paralelo.
+Constatamos que a maioria dos projetos possuiam um no configurando o 
+plugin do maven surefire, e alguns projetos ``herdavam'' as configurações
+de outros projetos.
+
+Nossa primeira acao foi forcar a execucao sequencial de forma manual
+colocando os parametros de configuracao sequencial em todos os \pomf{}
+dos projetos. 
+}
 

### 2017-03-30 paper/evaluation.tex
done with subj section

@@
 
-We evaluated the characteristics of regression tests in open-source
+We evaluated the characteristics of test suites in open-source
 development from a sample set of Java projects from \github{}.  We are
-interested to evaluate non-trivial test suites on popular projects
+interested to evaluate non-trivial test suites from popular projects
 that are in activity. We used the \github{}'s search
@@
 were not Maven projects (or did not have a \pomf{} in the root
-directory) and \SubjectsGithubNotTestable{} were in an untestable
-revision (\eg, missing dependencies or incompatible testing
-environment). To ensure that our sample set is stable, we retested the
-remaining subjects to eliminate flaky tests (total of
-\SubjectsGithubFlaky{} subjects). Our final set consists in
+directory) and we were unable to execute the tests from
+\SubjectsGithubNotTestable{} tests (\eg, missing dependencies or
+incompatible testing environment). To ensure that our sample set is
+stable, we retested the remaining subjects to eliminate flaky tests
+(total of \SubjectsGithubFlaky{} subjects). Our final set consists in
 \numSubjs{} testable subjects.
@@
     \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
-    \caption{\label{fig:subjects}\Fix{this is mocked data!}}
+    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
+    projects hosted on \github{}. From this initial sample, we ignored
+    \SubjectsGithubNotMaven{} projects without Maven support,
+    \SubjectsGithubNotTestable{} untestable projects, and
+    \SubjectsGithubFlaky{} projects with flaky tests. We considered
+    \numSubjs{} projects to conduct our study.}
 \end{figure}

### 2017-03-30 paper/evaluation.tex
Adjusted vspace and deleted unnecessary comment in RQ1
updated RQ1

@@
 
-\Comment{\Jbc{Ensure to describe that: subjects that could not run the tests
-due to incompatible testing environment were removed (likely to happen
-for subjects that rely on database systems and other external
-factors), the exit status for all executions are consistent and I
-removed flaky projs}}
-
 We ran each subject's tests three times and grouped them according to
@@
 
-\Jbc{these results will be updated $\rightarrow$} It is important to
-mention that Figure~\ref{fig:rq1-barplot} represents a lower bound
-estimation for time cost because some tests may finish earlier than
-expected due to existing bugs on the ongoing revision.  From the
-\numSubjs{} compiled projects, \numSubjsPass{} successfully executed
-all tests and \numSubjsFail{} reported test failures.  Also, some
-projects omit long-running tests on their default execution. For
-instance, it is necessary to invoke Maven with additional parameters
-to run integration tests from project \CodeIn{apache.maven-surefire}
-(nearly 30 min in our environment).
+It is important to mention that Figure~\ref{fig:rq1-barplot}
+represents a lower bound estimation for time cost because some tests
+may finish earlier than expected due to existing bugs on the ongoing
+revision.  From the \numSubjs{} compiled projects, \numSubjsPass{}
+successfully executed all tests and \numSubjsFail{} reported test
+failures.  Also, some projects may omit long-running tests on their
+default execution. For instance, the project
+\CodeIn{apache.maven-surefire} runs all unit tests in a few seconds in
+our environment.  According to our criteria, this project would be
+classified as \shortg{} but we noticed that by providing additional
+parameters from the subject, the integration tests are included during
+the execution.  After including the integration tests, the tests time
+increases to nearly 30 minutes.  Since it would be impractical to
+analyze each project, we considered only the tests executed by
+default.
 

### 2017-03-30 analysis/timecost.r
Added missing script

@@ -1,0 +1,103 @@
+library("dplyr")
+library("ggplot2")
+
+# df <- read.csv(file.choose())
+args <- commandArgs(trailingOnly = TRUE)
+rq1_df <- read.csv(args[1])
+#rq2_df <- read.csv(args[2], sep = ";")
+#rq3_df <- read.csv(args[3], sep = ",")
+
+###################
+# Analysis
+###################
+
+summarise(
+  group_by(rq1_df, test_success),
+  n = length(project_path),
+  tmin_xml = min(xml_test_time),
+  tmax_xml = max(xml_test_time),
+  tmin_mvn = min(maven_test_time),
+  tmax_mvn = max(maven_test_time)
+)
+
+###################
+# RQ1
+###################
+compute_group <- function(time) {
+    if (time <= 60) {
+        return("short")
+    }
+    else if (time <= (5 * 60)) {
+        return("medium")
+    }
+    return("long")
+}
+
+
+print("Investigate: Build success but builder time = 0")
+select(filter(rq1_df, test_success == "true" &
+                maven_test_time <= 0),
+       project_path)
+print("Investigate: build success but xml time = 0")
+select(filter(rq1_df, test_success == "true" &
+                xml_test_time <= 0),
+       project_path)
+
+rq1_df$group <- sapply(rq1_df$xml_test_time, FUN = compute_group)
+rq1_df$tmin <- sapply(rq1_df$xml_test_time, FUN = function(v) {return(v / 60)})
+rq1_df <- filter(rq1_df, xml_test_time > 0)
+
+# Cost groups barplot
+pdf("out/barplot-timecost.pdf", height = 3, width = 3)
+ggplot(data = rq1_df, aes(x = group, fill = test_success)) +
+  geom_bar(width = .8, position = "dodge") +
+  geom_text(
+    size = 2.5,
+    position = position_dodge(width = .75),
+    stat = "count",
+    aes(label = ..count.. , y = ..count.. + 5)
+  ) +
+  scale_fill_grey(start = 0.4, end = 0.7, labels = c("tests fail", "tests pass")) +
+  theme(legend.background = element_rect(),
+        legend.margin = margin(0),
+        legend.position = "top",
+        legend.title = element_blank()) +
+  labs(y = "Frequency", x = "Group")
+
+# Time cost boxplots
+pdf("out/boxplot-timecost.pdf", height = 3, width = 3)
+ggplot(data = rq1_df, aes(x = group, y = tmin, fill = test_success)) +
[…]

### 2017-03-30 paper/evaluation.tex
adjusted scripts from RQ2

@@
 
-\Jbc{pending updates! $\rightarrow$}
+\Jbc{Pending updates here}
 Section~\ref{sec:rqA} showed that medium and long-running projects are
@@
       \centering
-      \includegraphics[width=\textwidth]{R/testcost-med.pdf}
-      \caption{\label{fig:medtcost}Medium}
+      \includegraphics[width=\textwidth]{plots/testcost-med.pdf}
+      \caption{\label{fig:medtcost}Medium group}
     \end{subfigure}\\
@@
       \centering
-      \includegraphics[width=\textwidth]{R/testcost-long.pdf}
-      \caption{\label{fig:longtcost}Long}
-    \end{subfigure}%
+      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
+      \caption{\label{fig:longtcost}Long group}
+    \end{subfigure}\\
 
@@
       \end{tabular}
-      \caption{\label{fig:sd}...\Fix{Looks like there are missing
-        projects...}}    
+      \caption{\label{fig:sd}\Fix{missing caption}}    
     \end{subfigure}%
 
-    \caption{\label{fig:time-distributions}Distribution of time cost per project.}    
+    \caption{\label{fig:time-distributions}Distribution of test case
+    execution cost per project.}    
 \end{figure}

### 2017-03-30 analysis/testcost.r

@@ -1,7 +1,4 @@
-#!/usr/bin/env Rscript
-
 library(ggplot2)
-library(raster)
 
 args = commandArgs(trailingOnly=TRUE)
 
@@ -14,9 +11,11 @@ if (length(args)==0) {
 # ## coefficient of variation function
 # co.var <- function(x,na.rm=TRUE) sd(x,na.rm=na.rm)/mean(x,na.rm=na.rm)
 
-pdf(file=paste(name,".pdf",sep=""), width = 5, height = 1.5)
+output <- paste("out", name, sep="/")
+pdf(file=paste(output,".pdf",sep=""), width = 5, height = 1.5)
 
-dat <- read.csv(paste(name,".csv",sep=""), header = F)
+input <- paste("data", name, sep="/")
+dat <- read.csv(paste(input,".csv",sep=""), header = F)
 
 ## to compute median values across plots
 median <- aggregate(dat[, 2:2], list(dat$V1), median)
@@ -32,7 +31,7 @@ theme(axis.title.x=element_blank(),
       axis.text.x=element_blank(),
       axis.ticks.x=element_blank()
 ) +
-labs(y="Time (s)")+
+labs(y="Time cost (in secs)")+
 geom_hline(aes(yintercept=mean(median$x)), colour = "red", linetype = 2)+
 coord_cartesian(ylim = c(0,7.5))
 

### 2017-03-30 paper/evaluation.tex
pending some updates... vpn issues here

@@
 
-% considered all projects classified as \medg{} and \longg{}-running, a
-% total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
-% reduce noise we did not consider projects with \shortg{}-running test
-% suites as we observed that \percentShortSequential{} of those projects
-% do not use parallelism; including them would favor sequential
-% execution in our analysis.
-
 To extend our initial investigation, we mined several \pomf{} files
-must contain one of these keywords that contain parallelization
-keywords, namely \CodeIn{forkMode}, \CodeIn{forkCount}, and
-\CodeIn{parallel}.  This mining step, however, is not sound as a
-matching project may not indicate a project with a valid configuration
-for running tests in parallel.  False positive can happen because of
-comments, for instance.  To eliminate the cases of false positives and
-also to categorize true positive cases, we complemented the initial
-mining step with a manual inspection of files.
+from all \numMedLong{} projects classified as the \medg{} and
+\longg{}-running.
+\Jbc{rework this... $\rightarrow$}To reduce the number of build files
+to inspect, we consider only must contain one of these keywords that
+contain parallelization keywords, namely \CodeIn{forkMode},
+\CodeIn{forkCount}, and \CodeIn{parallel}.  This mining step, however,
+is not sound as a matching project may not indicate a project with a
+valid configuration for running tests in parallel.  False positive can
+happen because of comments, for instance.  To eliminate the cases of
+false positives and also to categorize true positive cases, we
+complemented the initial mining step with a manual inspection of
+files.
 
@@
 
-From the \numProjectsPar{} projects identified above, we investigated
-further the \numPomMatchedValid{} build files with parallel settings.
-We analyzed the support and distribution of parallel modes from this
-subset of projects. To calculate the distribution of parallel modes,
-we considered only the presence of the mode in at least one of the
-project settings.  Recall that a build file may contain more than one
-parallel setting and a project may contain several sub-modules with
-build files.  In case the value of a parallel option is resolved
-dynamically (\eg, via command-line argument or system variable) we
-compute all modes related to the option. For instance, depending on
-the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
+\Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
+identified above, we investigated further the \numPomMatchedValid{}
+build files with parallel settings.  We analyzed the support and
+distribution of parallel modes from this subset of projects. To
+calculate the distribution of parallel modes, we considered only the
+presence of the mode in at least one of the project settings.  Recall
+that a build file may contain more than one parallel setting and a
+project may contain several sub-modules with build files.  In case the
+value of a parallel option is resolved dynamically (\eg, via
+command-line argument or system variable) we compute all modes related
+to the option. For instance, depending on the value, the
+\CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
 \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
 (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
-Figure~\ref{fig:freqmodes-static} summarizes our findings. \Jbc{Given that we
-checked each configuration, we could elaborate how these settings are
-used.} \Fix{Missing conclusion: Fork the most used configuration}
+Figure~\ref{fig:freqmodes-static} summarizes our findings.
+\Fix{Missing conclusion: Fork the most used configuration}
 

### 2017-03-30 paper/intro.tex
pass on intro section

@@
 At large organizations, the alternative of renting cloud
-services\footnote{List of popular cloud services:
+services\footnote{List of popular hosting cloud services:
   \url{https://clutch.co/cloud}} or even building proprietary
-infrastructures for running tests is a legitimate approach to mitigate
+infrastructures to running tests is a legitimate approach to mitigate
 the regression testing problem.  However, for projects with low
@@
 not be economically viable.  For these cases, the use of commodity
-hardware, perhaps existing hardware, emerges as an attractive solution
-for running tests.  The proliferation of multi-core CPUs and the
-increasing popularization of testing frameworks with a rich support
-for parallelization enables test suite speedups through increased CPU
-usage~(see Section~\ref{sec:modes}).  This paper reports on an
-empirical study we conducted to analyze the impact of low-level
-parallelization to speedup testing in open-source projects.  This is a
-relevant problem given the tremendous popularity of open-source
-development and regression testing research.
+hardware (\eg{}, existing workstations), emerges as an attractive
+solution for running tests.  Furthermore, the proliferation of
+multi-core CPUs and the increasing popularization of testing
+frameworks and build systems, which today provide mature support for
+parallelization, enable test execution speedups through increased CPU
+usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
+for cost-effective test execution and supply of testing
+infrastructure~---~led us to investigate if and how parallelization
+features from testing frameworks and build systems are used in
+practice.
 
-The dimensions of analysis in this study are as follows.
+This paper reports on an empirical study we conducted to analyze the
+impact of low-level parallelization to speedup testing in open-source
+projects.  This is a relevant problem given the tremendous popularity
+of open-source development\Mar{Fan Long
+  (http://people.csail.mit.edu/fanl/) often uses a plot to show the
+  exponential rise of projects in github.  Please check if you can
+  find a reference to that or ask Fan Long what source he used (maybe
+  browsed with public API).} and regression testing
+research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
+considered in this study are as follows.
 
-\begin{itemize}
+\begin{enumerate}
 \item \textbf{Prevalence of long-running test suites.}
 \item \textbf{Usage of test suite parallelization.}  
-\item \textbf{Speedups of parallelization modes.}
-\item \textbf{Issues with parallelization.}    
-\end{itemize}
+\item \textbf{Speedups of parallelization.}
+\item \textbf{Issues versus benefits on using parallelization modes.}
+\end{enumerate}
+
+Each dimension focuses on one aspect of our study.  The first
+dimension measures to which extent open-source projects contain time
+costly test suites.  In the limit, parallelization will be fruitless
+if all project contain short-running test suites The second dimension
+measures how often open-source projects, irrespective of their
+associated testing costs, use parallelization schemes.  This dimension
+is concerned with popularity of parallelization.  The third aspect
+evaluates the observed impact of parallelization on cost.  Finally,
+the last dimension evaluates the issues and benefits associated with
+running test suites with different parallel configuration (/modes).
+Overall, the study of these dimensions help us layout the current
+state-of-the-practice in usage of parallelization in open-source
+projects.
+
+\Mar{organize according to each of these dimensions...$\rightarrow$}
 

### 2017-03-30 paper/intro.tex
pass on abstract; minor change in intro

@@
 for cost-effective test execution and supply of testing
-infrastructure~---~led us to investigate if and how parallelization
-features from testing frameworks and build systems are used in
-practice.
+infrastructure~---~led us to investigate the usage of parallelization
+features from testing frameworks and build systems in public
+open-source projects.
 

### 2017-03-30 paper/intro.tex
minor changes on intro

--- 2017-03-30 paper/intro.tex
@@
 usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
-for cost-effective test execution and supply of testing
-infrastructure~---~led us to investigate if and how parallelization
-features from testing frameworks and build systems are used in
-practice.
+for cost-effective test execution and supply of relatively inexpensive
+testing infrastructures~---~led us to investigate the usage of
+parallelism for running tests in public open-source projects.
 
@@
 costly test suites.  In the limit, parallelization will be fruitless
-if all project contain short-running test suites The second dimension
+if all projects contain short-running test suites. The second dimension
 measures how often open-source projects, irrespective of their
@@
 the last dimension evaluates the issues and benefits associated with
-running test suites with different parallel configuration (/modes).
+running test suites with different parallel configurations (/modes).
 Overall, the study of these dimensions help us layout the current
-state-of-the-practice in usage of parallelization in open-source
-projects.
+state-of-the-practice about the use and impact of parallelization in open-source
+projects, which presumably do not have large budgets.
 
@@
 %%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
-%%  LocalWords:  Ekstazi github CloudBuild PWA groupon criticality
+%%  LocalWords:  Ekstazi github CloudBuild PWA groupon criticality VM
 
@@
 %%% End:
-%%  LocalWords:  jenkins
+%%  LocalWords:  jenkins API VMs datarace

### 2017-03-30 paper/evaluation.tex
adjusted rq4 methodology

@@
 
-To enforce sequential execution, \Jbc{explain methodology}.
-\Luis{
-Primeiro nos avaliamos os \pomf{} de alguns projetos long que 
-rodavam em paralelo.
-Constatamos que a maioria dos projetos possuiam um no configurando o 
-plugin do maven surefire, e alguns projetos ``herdavam'' as configurações
-de outros projetos.
+To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
+analyzed the \numProjectsPar{} subjects looking for the parallelism 
+configuration inside the \pomf{} of each module. To run the subjects
+sequentially, we manually modified the Maven Surefire configuration
+from the \numPomMatchedValid{} identified before to not run in parallel.
+The Figure~\ref{fig:surefire-configuration} show the injected configuration
+in each \pomf{}.
 
-Nossa primeira acao foi forcar a execucao sequencial de forma manual
-colocando os parametros de configuracao sequencial em todos os \pomf{}
-dos projetos. 
-}
+\input{codes/surefire}
 

### 2017-03-30 analysis/testcost.r
Updated analysis scripts

@@ -14,27 +14,23 @@ if (length(args)==0) {
 output <- paste("out", name, sep="/")
 pdf(file=paste(output,".pdf",sep=""), width = 5, height = 1.5)
 
-input <- paste("data", name, sep="/")
-dat <- read.csv(paste(input,".csv",sep=""), header = F)
+input <- paste("gen", name, sep="/")
+dat <- read.csv(paste(input,".csv",sep=""), header = T)
 
-## to compute median values across plots
-median <- aggregate(dat[, 2:2], list(dat$V1), median)
-
+# to compute median values across plots
+median <- aggregate(dat$time, list(dat$project), median)
 print("==sd==>")
-sd <- aggregate(dat[, 2:2], list(dat$V1), sd)
+sd <- aggregate(dat$time, list(dat$project), sd)
 print(sd)
-
-p <- ggplot(dat, aes(x=factor(V1), y=V2))
-
-p + geom_boxplot(outlier.shape=NA) +
-theme(axis.title.x=element_blank(),
-      axis.text.x=element_blank(),
-      axis.ticks.x=element_blank()
-) +
-labs(y="Time cost (in secs)")+
-geom_hline(aes(yintercept=mean(median$x)), colour = "red", linetype = 2)+
-coord_cartesian(ylim = c(0,7.5))
-
+ 
+ggplot(dat, aes(x=factor(project), y=time)) +
+    geom_boxplot(outlier.shape=NA) +
+    theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) +
+    labs(y="Time cost (in secs)")+
+    geom_hline(aes(yintercept=mean(median$x)), colour = "red", linetype = 2)+
+    coord_cartesian(ylim = c(0,7.5))
+ 
 aux <- dev.off()
-
 

### 2017-03-30 analysis/timecost.r

@@ -23,17 +23,6 @@ summarise(
 ###################
 # RQ1
 ###################
-compute_group <- function(time) {
-    if (time <= 60) {
-        return("short")
-    }
-    else if (time <= (5 * 60)) {
-        return("medium")
-    }
-    return("long")
-}
-
-
 print("Investigate: Build success but builder time = 0")
 select(filter(rq1_df, test_success == "true" &
                 maven_test_time <= 0),
@@ -43,13 +32,12 @@ select(filter(rq1_df, test_success == "true" &
                 xml_test_time <= 0),
        project_path)
 
-rq1_df$group <- sapply(rq1_df$xml_test_time, FUN = compute_group)
 rq1_df$tmin <- sapply(rq1_df$xml_test_time, FUN = function(v) {return(v / 60)})
 rq1_df <- filter(rq1_df, xml_test_time > 0)
 
 # Cost groups barplot
 pdf("out/barplot-timecost.pdf", height = 3, width = 3)
-ggplot(data = rq1_df, aes(x = group, fill = test_success)) +
+ggplot(data = rq1_df, aes(x = timecost_group, fill = test_success)) +
   geom_bar(width = .8, position = "dodge") +
   geom_text(
     size = 2.5,
@@ -66,7 +54,7 @@ ggplot(data = rq1_df, aes(x = group, fill = test_success)) +
 
 # Time cost boxplots
 pdf("out/boxplot-timecost.pdf", height = 3, width = 3)
-ggplot(data = rq1_df, aes(x = group, y = tmin, fill = test_success)) +
+ggplot(data = rq1_df, aes(x = timecost_group, y = tmin, fill = test_success)) +
   geom_boxplot() +  theme(strip.text = element_blank(),
                           strip.background = element_blank(),
                           legend.background = element_rect(),
@@ -74,7 +62,7 @@ ggplot(data = rq1_df, aes(x = group, y = tmin, fill = test_success)) +
                           legend.title = element_blank(),
                           legend.position = "top") +
   scale_fill_grey(start = 0.5, end = 0.8, labels = c("tests fail", "tests pass")) +
-  facet_wrap( ~ group, scales = "free") +
+  facet_wrap( ~ timecost_group, scales = "free") +
   labs(y = "Time cost (in minutes)", x = "Group")
 
 ###################

### 2017-03-31 paper/evaluation.tex

@@
 
-\Jbc{Pending updates here}
 Section~\ref{sec:rqA} showed that medium and long-running projects are
@@
       \centering
-      \includegraphics[width=\textwidth]{plots/testcost-med.pdf}
+      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
       \caption{\label{fig:medtcost}Medium group}
     \end{subfigure}\\
-
+    \vspace{2.5ex}
     \begin{subfigure}{0.5\textwidth}
@@
     \end{subfigure}\\
-
+    \vspace{2.5ex}
     \begin{subfigure}{0.5\textwidth}
@@
       \end{tabular}
-      \caption{\label{fig:sd}\Fix{missing caption}}    
+      \caption{\label{fig:sd}\Fix{adjust values}}    
     \end{subfigure}%
@@
 median value of execution cost for a test was relatively small (dashed
-horizontal red lines), namely 0.41s for \medg{} projects and 0.23s for
-\longg{} projects.  Note that correlation between cost of test suites
-and cost of their individual tests is not to be expected.  The
-standard deviation ($\sigma$) associated with each ditribution was
-relatively low.  Figure~\ref{fig:sd} shows the number of projects
-within specific ranges of $\sigma$ values.  We also observed that
-projects with very high standard deviations may or may not be
-indicative of monopolization of execution by a small number of tests.
-For example, the highest value of $\sigma$ ocurred in project
+horizontal red lines), namely \Fix{0.41s} for \medg{} projects and
+\Fix{0.23s} for \longg{} projects.  Note that correlation between cost
+of test suites and cost of their individual tests is not to be
+expected.  The standard deviation ($\sigma$) associated with each
+distribution was relatively low.  Figure~\ref{fig:sd} shows the number
+of projects within specific ranges of $\sigma$ values.  We also
+observed that projects with very high standard deviations may or may
+not be indicative of monopolization of execution by a small number of
+tests.  For example, the highest value of $\sigma$ occurred in project
 \CodeIn{wildfly-swarm}, whose test suite was classified as
-long-running.  This project contains only 65 tests, 62 of which take
-less than 0.5s to run, 1 of which takes nearly 3s to run, and 2 of
-which take 40m to run.  This is an example where test suite
-parallelization may not be very beneficial as $>$99\% execution cost
-is dominated by only 3\% of the tests.  Without these two tests this
-project would have been classified as short-running.  A closer
-inspection in the data indicates that the project
-\CodeIn{wildfly-swarm} was an extreme case; we did not find projects
-with similar characteristics of time monopolization.  Project
-\CodeIn{jenkinsci.gerrit-trigger-plugin} is also classified as
-long-running and has the second highest value of $\sigma$.  For this
-project, however, cost is distributed more smoothly across 529 tests,
-of which 119 take more than 1s to run.
+long-running.  This project contains only \Fix{65} tests, \Fix{62} of
+which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
+\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
+an example where test suite parallelization may not be very beneficial
+as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
+tests.  Without these two tests this project would have been
+classified as short-running.  A closer inspection in the data
+indicates that the project \CodeIn{wildfly-swarm} was an extreme case;
+we did not find projects with similar characteristics of time
+monopolization.  Project \CodeIn{jenkinsci.gerrit-trigger-plugin} is
+also classified as long-running and has the second highest value of
+$\sigma$.  For this project, however, cost is distributed more
+smoothly across \Fix{529} tests, of which \Fix{119} take more than
+\Fix{1s} to run.
 

### 2017-03-31 paper/evaluation.tex
pass on text

@@
 
-According to Maven's documentation \Fix{cite surefire doc}, any
+According to Maven's documentation~\cite{maven-surefire-plugin}, any
 parallelization setting depends either on (1) \CodeIn{parallel} to

### 2017-03-31 paper/modes.tex
pass on text

@@
-\newcommand{\Seq}{L0}
-\newcommand{\SeqClassParMeth}{L1}
-\newcommand{\ParClassSeqMeth}{L2}
-\newcommand{\ParClassParMeth}{L3}
+\newcommand{\Seq}{C0}
+\newcommand{\SeqClassParMeth}{C1}
+\newcommand{\ParClassSeqMeth}{C2}
+\newcommand{\ParClassParMeth}{C3}
 \newcommand{\Fork}{F}
@@
 
-%\Mar{add a sentence to introduce this section at a higher abstraction
-%  level.}
-
-This section provides some background on parallel test execution.
+This section provides important background on parallel test execution.
 
 Parallelism in test execution can be obtained at different levels.
-Figure~\ref{fig:levels} illustrates relevant levels.  The highest
+Figure~\ref{fig:levels} illustrates these levels.  The highest
 level indicates parallelism that can be obtained through different
@@
 to the aggregate processing power of the farm.
-
-%% Lower-level parallelism fits
-%% particularly well smaller organizations (/projects) with relatively
-%% high testing costs but lower budgets.
 
@@
 
-\Comment{
-    Unfortunately, these solutions can't be used out-of-the-box:
-    unrestricted parallel execution of tests can produce
-    non-deterministic results as developers typically do not provision
-    protection to concurrent accesses originated from arbitrary program
-    points (\ie{}, tests).  We refer to this problem as Parallel
-    Execution Flakiness (\pef{}).
-
-    %% These solutions enable the
-    %% use of commodity hardware to maximize CPU usage\footnote{In the case
-    %%   of the Java language, for example, it is possible to explore
-    %%   parallelism across and within JVMs.}.
-
-    To illustrate the importance of parallel test execution and
-    the problem of \pef{} let's consider the case of the ``core'' module
-    from the Apache Camel project~\cite{apache-camel-web}.  This module
-    contains 5,679 test cases, declared in 2,356 test classes.  We ran
-    those tests in a machine with 16GB of memory and 8 virtual CPUs (4
-    cores with 2 native threads each).  Sequential test execution takes
-    24m50s to run this test set.  Execution of the same test set takes
-    2m28s when we configured parallel execution to fork a JVM per CPU and
-    execute test classes, uniquely allocated to that JVM, sequentially but
-    running test methods from each class in separate threads.  Note that
-    this is an order of magnitude speedup (10.07x)\Fix{Need to understand
-    why this is 10x as opposed to something closer to 7x - I didn't get
-    your concern here}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of
-    5,679) of the tests fail when executed in parallel.  It is important
-    to notice that the ratio of failures varies with the project as it
-    depends on factors such as length of test cases and amount of shared
-    state across tests.
-
-    \pef{} is an important obstacle to enable parallel test execution.
-    Conceptually, higher parallelization can result in higher chances of
-    concurrency-related problems.  It is important to execute tests
-    efficiently without sacrificing reliability
-    \Fix{gap between pars?? What gap?}
-}
-
-%%Build systems delegate functionalities to the testing framework they
-%%use~\cite{maven-surefire-plugin}.  Figure~\ref{fig:surefire}
-%%illustrates how to configure Maven for mode
-%%\ParClassSeqMeth{}~--~classes sequentially (default) and test methods
-%%in parallel. Although this configuration is defined in the build file
-%%(\eg, \emph{pom.xml} on Maven), these settings are forwarded to the
-%%underlying testing framework (in this case, JUnit).
-
-%% \Jbc{I have to understand better how Surefire executes tests. I'm
-%% afraid it has its own wrapper classes and reuse JUnit core
-%% functionalities. I'm saying this because JUnit does not offer a finer
-%% control over thread numbers while this configuration is possible with
-%% Surefire} For example,
-
-%\Fix{we
-%  need to know how Maven allocates test classes to JVMs}
-
 \subsection{Testing Frameworks}
@@
 
-The list below shortly describes the choices to control parallelism
-within a Java virtual machine (JVM).
+The list below shows the choices to control parallelism within a Java
+virtual machine (JVM) which runs in a single process of the CPU.
 
@@
 \item
-    \textbf{Sequential (\Seq).}~This configuration corresponds to the
-        default behaviour in a test execution. No parallelism is
-        involved.
+    \textbf{Sequential (\Seq).}~No parallelism is involved.
 \item
     \textbf{Sequential classes; parallel methods
-        (\SeqClassParMeth).}~When running a test class, the testing
-        framework executes methods on multiple threads. Each class
-        runs sequentially.
+        (\SeqClassParMeth).}~This configuration corresponds to the
+        sequential execution of test classes and test methods run in
+        multiple threads.
 \item
     \textbf{Parallel classes; sequential methods
-        (\ParClassSeqMeth{}).}~The testing framework runs test classes
-        on multiple threads and methods run sequentially within each
-        thread.
+        (\ParClassSeqMeth{}).}~This configuration corresponds to the
+        execution of test classes in multiple threads and tests run
+        sequentially within each thread.
 \item
@@
 
-Typically, testing frameworks executes tests in sequence by default
-(\Seq{}) and may allow the developer to use an ordering criteria (\eg,
-test name).  For the \SeqClassParMeth{} setting, \Fix{elaborate...}.
-For the \ParClassSeqMeth{} setting, \Fix{elaborate...}. Finally, the
-\ParClassParMeth{} setting \Fix{...elaborate...}.
+The configuration \Seq{} is a proper fit for short-running test suites
+since this is the default configuration and the execution provides
+feedback in an acceptable time. However, for costly suites, it is
+impractical for developers to wait long-running executions to take
+action.  In this scenario, the remaining configuration may help to
+amortize the execution cost depending on how the test suite was
+designed. For instance, the configuration \SeqClassParMeth{} may
+speedup the execution of test suites composed large test classes since
+the cost of running all test methods is amortized by a pool of
+threads. Similarly, the configuration \ParClassSeqMeth{} may speedup
+test suites composed by several small test classes. Notice that both
+configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
+data-race condition at different levels. For instance, if two test
+classes performs I/O operations to the same file, the configuration
+\SeqClassParMeth{} would be preferable. Finally, the configuration
+\ParClassParMeth{} does not impose any sequential execution but it is
+more likely to manifest data-races as methods from different classes
+run in parallel.
 
@@
 
-The list below shortly describes the choices to control parallelism
-through build systems:
+The list below shows the choices to control parallelism through build
+systems which uses multiple JVMs on different processes each:
 
@@
         configuration corresponds to the parallel execution of test
-        classes on different JVMs and test methods run sequentially
-        within each JVM.
+        classes on different JVMs with test methods running
+        sequentially within each JVM.
 \item
@@
         configuration corresponds to the parallel execution of test
-        classes on different JVMs and test methods run on multiple
-        threads within each JVM.
+        classes on different JVMs with test methods running on
+        multiple threads within each JVM.
 \end{itemize}
@@
 Several build systems support the execution of test classes in forked
-processes running a JVM. In the \ForkSeq{} configuration, each spawned
+processes running a JVM. In the configuration \ForkSeq{}, each spawned
 process runs a different test class at time and the builder merges the
-results from each execution. In the \ForkParMeth{} configuration, the
+results from each execution. In the configuration \ForkParMeth{}, the
 build system forwards settings to the underlying testing framework to
@@
 are unaware of any build system capable of running multiple classes at
-time within a forked process.  \Comment{In addition, the builder can
-reuse these processes to execute the next test classes in the queue
-according to the developer's preference. For instance, one might want
-the builder to spawn a new process for each test class to ensure
-maximum isolation. Notice that to exploit parallelism at build system
-level, the number of forked processes must be proportional to the
-number of available CPUs, otherwise, the high frequency of
-context-switching and processes competing for a CPU may degrade the
-execution performance  \Jbc{$\leftarrow$ I'm not sure if we should
-keep this. We can remove it if necessary}.}
+time within a forked process.
 
-%% In this paper, we use the prefix ``\Fork{}'' to indicate that a given
-%% testing configuration has the feature of spawning JVMs to run test
-%% classes enabled.
-
-\subsubsection*{Illustration}~\Fix{elaborate the following example to
-conclude this section}
+\subsubsection*{Illustration}~Figure~\ref{fig:surefire} illustrates
+the support of parallel execution with the configuration
+\ForkParMeth{} on Maven, a popular build system in Java projects.
+Maven uses a configuration file based on XML (known as \pomf{}) to
+define tasks related to the project building and these tasks are
+performed several plugins. \Jbc{falar do surefire e explicar a
+configuracao ilustrada - Surefire levanta uma JVM por core e cria uma
+pool de 5 threads em cada JVM para executar testes em paralelo.}
 
@@
 \end{lstlisting}
-    \caption{\label{fig:surefire} Maven with a \ForkParMeth{}
-    configuration.  Maven forks one JVM per core (\CodeIn{forkCount}
+    \caption{\label{fig:surefire} Maven setup with the configuration
+    \ForkParMeth{}.  Maven forks one JVM per core (\CodeIn{forkCount}
     parameter) and uses five threads (\CodeIn{threadCount} parameter)
     to run methods (\CodeIn{parallel} parameter) within each JVM.}
-
-%%    test methods run in parallel (\CodeIn{parallel}
-%%    parameter) using two threads (\CodeIn{threadCount} parameter) per
-%%    available core (flag \CodeIn{perCoreThreadCount}).}
 \end{figure}
-
-%% \Fix{-----}
-%% In JUnit, \emph{ParallelComputer} provides support to parallel
-%% execution: it instantiates a test runner with an
-%% \emph{ExecutorService} from the Java Concurrent API. Each test method
-%% is executed in a separated thread as the thread pool creates new
-%% threads on-demand and reuse them if any thread is available.
-%% \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
-
-%% As in \ParClassSeqMeth, the test runner has a cached thread poll but
-%% instead of executing test methods from a single test class, the test
-%% suite runner executes classes in separated threads and methods
-%% sequentially within each thread.
-
-%% \Jbc{I need to confirm this but AFAIK this is how it happens} As in
-%% \SeqClassParMeth, classes execute on separated threads but test
-%% methods are also executed in parallel. More precisely, there is a
-%% thread pool to execute classes in separated threads (\ie, like in
-%% \ParClassSeqMeth) and, within each class runner, there is an
-%% \emph{ExecutorService} to run test methods in parallel (\ie, like in
-%% \SeqClassParMeth).
-
-%% \Fix{-----}

### 2017-03-31 paper/evaluation.tex
removed old comments
pass on text

@@
 settings.
-%%\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
-%%addresses the characteristics of regression tests from the previous
-%%experiment.  More specifically, we want to investigate if there is a
-%%relation between the balance of test execution (\ie, how uniformly
-%%distributed is the execution time across tests cases) and the usage of
-%%computational resources (\ie, if tests are mostly CPU or IO intense)
-%%that impacts the effectiveness of parallelization}.
 Finally, the fifth research question discusses the limitations and
@@
 \begin{minipage}{8cm}
-    \textit{Answering \numRQA{}:}~\emph{Given that
-    \percentMedLongRunning{} of the projects are costly (\ie,
-    \numMedLong{} projects from \medg{} and \longg{}), we concluded
-    that time-consuming regression test suites are relatively frequent
-    in open-source projects.}
+    \textit{Answering \numRQA{}:}~\emph{We concluded that
+    time-consuming regression test suites are relatively frequent in
+    open-source projects given that \percentMedLongRunning{} of the
+    projects are costly (\ie, \numMedLong{} projects from \medg{} and
+    \longg{}).}
 \end{minipage}
@@
 
-    \begin{subfigure}{0.5\textwidth}
+    \begin{subfigure}{0.47\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
+      \caption{\label{fig:longtcost}Long group}
+    \end{subfigure}\\
+    \vspace{2.5ex}
+    \begin{subfigure}{0.47\textwidth}
       \centering
@@
       \caption{\label{fig:medtcost}Medium group}
-    \end{subfigure}\\
-    \vspace{2.5ex}
-    \begin{subfigure}{0.5\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
-      \caption{\label{fig:longtcost}Long group}
     \end{subfigure}\\
@@
         \midrule    
+        Long   &  9 & 14 & 5 \\
         Medium & 17 & 20 & 7 \\
-        Long   &  9 & 14 & 5 \\
         \bottomrule

### 2017-03-31 analysis/selection.py

@@ -7,7 +7,7 @@ def gen_testcost_data(group, testcases, selection):
         writer = csv.DictWriter(f, fieldnames=testcases[0].keys())
         writer.writeheader()
         for row in testcases:
-            if row["project"] in selection and row["project"] not in {"INRIA_spoon"}:
+            if row["project"] in selection:
                 try:
                     writer.writerow(row)
                 except:

### 2017-03-31 analysis/selection.r

@@ -9,7 +9,7 @@ df <- summarise(group_by(df, selection_group), length = length(selection_group))
 df
 ggplot(df, aes(x = factor(1), y = length, fill = selection_group)) +
     theme_void() +
-    scale_fill_grey(start = 0.3, end = 0.9, name = "") +
+    scale_fill_brewer(name = "") +
     geom_bar(stat = "identity", width = 1) +
     geom_text(aes(label = length), position = position_stack(vjust = 0.5)) +
     coord_polar("y")

### 2017-03-31 analysis/timecost.r

@@ -38,14 +38,14 @@ rq1_df <- filter(rq1_df, xml_test_time > 0)
 # Cost groups barplot
 pdf("out/barplot-timecost.pdf", height = 3, width = 3)
 ggplot(data = rq1_df, aes(x = timecost_group, fill = test_success)) +
-  geom_bar(width = .8, position = "dodge") +
+  geom_bar(width = .8, position = "dodge", colour = "black") +
   geom_text(
-    size = 2.5,
+    size = 3,
     position = position_dodge(width = .75),
     stat = "count",
-    aes(label = ..count.. , y = ..count.. + 5)
+    aes(label = ..count.. , y = ..count.. + 8)
   ) +
-  scale_fill_grey(start = 0.4, end = 0.7, labels = c("tests fail", "tests pass")) +
+  scale_fill_brewer(labels = c("tests fail", "tests pass")) +
   theme(legend.background = element_rect(),
         legend.margin = margin(0),
         legend.position = "top",
@@ -61,31 +61,6 @@ ggplot(data = rq1_df, aes(x = timecost_group, y = tmin, fill = test_success)) +
                           legend.margin = margin(0),
                           legend.title = element_blank(),
                           legend.position = "top") +
-  scale_fill_grey(start = 0.5, end = 0.8, labels = c("tests fail", "tests pass")) +
+  scale_fill_brewer(labels = c("tests fail", "tests pass")) +
   facet_wrap( ~ timecost_group, scales = "free") +
   labs(y = "Time cost (in minutes)", x = "Group")
-
-###################
-# RQ2
-###################
-# pdf("boxplot-timecost-dist.pdf", height = 2, width = 4)
-# ggplot(rq2_df, aes(x = project, y = time)) +
-#   geom_boxplot() +
-#   theme(axis.text.x =  element_blank())
-
-##################
-# RQ3
-###################
-
-# pdf("parallel-modes.pdf", height = 2, width = 3)
-# 
-# # pdf("parallel-modes.pdf", height = 2, width = 3)
-# ggplot(data = distinct(select(rq3_df, project, level)), aes(x = level)) +
-#   geom_bar(width = .8) +
-#   geom_text(
-#     size = 2.5,
-#     stat = "count",
-#     aes(label = ..count.. , y = ..count.. + 0.5)
-#   ) +
-#   labs(y = "Frequency", x = "Parallelism Level")
-# 

### 2017-03-31 paper/evaluation.tex
pass on text

@@
 \newcommand{\numRQD}{RQ4}
-%%\newcommand{\numRQE}{RQ5}
 \newcommand{\numRQF}{RQ5}
@@
 \newcommand{\RQC}{How often developers provides support to parallel
-execution to amortize the execution cost?}
+execution of test suites?}
 \newcommand{\RQD}{What is the impact of parallelization?}
-%%\newcommand{\RQE}{What factors contribute to improve performance
-%%  through parallelization?\Jbc{Previously as "When does
-%%    parallelization works and when it does not so great?"}}
 \newcommand{\RQF}{What are the limitations of low-level parallelism?}
@@
     \item \textbf{\numRQD.} \RQD
-%%    \item \textbf{\numRQE.} \RQE
     \item \textbf{\numRQF.} \RQF
@@
 investigate if developers consider low-level parallelism features
-available out-of-the-box (see Section~\ref{sec:modes}). In addition,
-we want to identify what configurations are often used and why they
-are more popular (if any).  The fourth research question addresses the
-impact of low-level parallelism on test execution from projects in our
-sample set. We want to identify subjects that already use test
-parallelization and compare their performance in contrast to
-sequential execution. In addition, we are interested in evaluating the
-performance of sequential test suites with different parallelization
-settings.
+available out-of-the-box to amortize test execution (see
+Section~\ref{sec:modes}). In addition, we want to identify what
+configurations are often used and why they are more popular (if any).
+The fourth research question addresses the impact of low-level
+parallelism on test execution from projects in our sample set. We want
+to identify subjects that already use test parallelization and compare
+their performance in contrast to sequential execution. In addition, we
+are interested in evaluating the performance of sequential test suites
+with different parallelization settings.
 Finally, the fifth research question discusses the limitations and
@@
 
-To evaluate the support of parallelization to run tests, we
-investigate if there are projects with parallel execution enabled by
-default and what configurations are more popular. In addition, we
-complement our investigation by analyzing several build files (\ie,
-\pomf{}) to identify projects that supports parallel execution but
-require additional execution parameters to enable this feature.  We
-describe our approach as follows:
+To evaluate the support of parallel execution of test suites, we
+considered the \numMedLong{} projects that ran in at least one minute
+identified in Section~\ref{sec:rqA} (\ie, \medg{} and \longg{}
+groups). We are interested to know if developers consider low-level
+parallelism features to amortize the execution cost. More precisely,
+we investigate if there are projects with parallelism configuration
+enabled by default or if developers configure this feature to run only
+on specific scenarios (\eg, dedicated server).  We describe our
+approach as follows:
 
@@
       \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
-      that \Jbc{summarize results from both parts (static and
-      dynamic)}.} 
+      that parallelism features are underused given that only \Fix{\%}
+      of projects supports parallel execution of test suites.}
   \end{minipage}

### 2017-03-31 analysis/selection.py

@@ -1,62 +1,0 @@
-#!/usr/bin/env python3
-import csv
-
-def gen_testcost_data(group, testcases, selection):
-    output = "gen/testcost-{}.csv".format(group)
-    with open(output, "w", newline="") as f:
-        writer = csv.DictWriter(f, fieldnames=testcases[0].keys())
-        writer.writeheader()
-        for row in testcases:
-            if row["project"] in selection:
-                try:
-                    writer.writerow(row)
-                except:
-                    # FIXME: it shouldn't have bad CSV rows...
-                    print(row)
-
-
-def csv_content(path, header=None):
-    with open(path, newline="") as f:
-        reader = csv.DictReader(f) if not header else csv.DictReader(f, header)
-        return [r for r in reader]
-
-
-def classify_subject_type(p):
-    return "testable" if float(p["xml_test_time"]) > 0 else "untestable"
-
-
-def classify_timecost(p):
-    exec_time = float(p["xml_test_time"])
-    if exec_time <= 60:
-        return "short"
-    elif exec_time <= (5 * 60):
-        return "medium"
-    return "long"
-
-    
-dataset1 = csv_content("data/execution-1.csv")
-
-# TODO merge datasets in a single dataset
-dataset = dataset1
-
-timecost_groups = {"medium": set({}), "long": set({})}
-for p in dataset:
-    p["selection_group"] = classify_subject_type(p)
-    p["timecost_group"] = classify_timecost(p)
-    if not p["timecost_group"] == "short":
-        timecost_groups[p["timecost_group"]].add(p["project_path"])
-
-with open("gen/selection.csv", "w", newline="") as f:
-    writer = csv.DictWriter(f, fieldnames = dataset[0].keys())
-    writer.writeheader()
-    writer.writerows(dataset)
-
-    # We know that 48 projects are not based on maven
-    for i in range(48):
-        writer.writerow({"selection_group": "not maven"})
-
-print("dataset size:", len(dataset))
-
-testcases = csv_content("data/test-cases-1.csv", ["project", "time"])
-gen_testcost_data("medium", testcases, timecost_groups["medium"])
-gen_testcost_data("long", testcases, timecost_groups["long"])

### 2017-03-31 analysis/selection.r

@@ -1,16 +1,0 @@
-library("dplyr")
-library("ggplot2")
-
-args <- commandArgs(trailingOnly = TRUE)
-df <- read.csv(args[1])
-pdf("out/subjs.pdf", width = 2.8, height = 2)
-
-df <- summarise(group_by(df, selection_group), length = length(selection_group)) 
-df
-ggplot(df, aes(x = factor(1), y = length, fill = selection_group)) +
-    theme_void() +
-    scale_fill_brewer(name = "") +
-    geom_bar(stat = "identity", width = 1) +
-    geom_text(aes(label = length), position = position_stack(vjust = 0.5)) +
-    coord_polar("y")
-

### 2017-03-31 analysis/testcost.r

@@ -1,36 +1,0 @@
-library(ggplot2)
-
-args = commandArgs(trailingOnly=TRUE)
-
-if (length(args)==0) {
-  stop("At least one argument must be supplied (input file).n", call.=FALSE)
-} else if (length(args)==1) {
-  name = args[1]
-}
-
-# ## coefficient of variation function
-# co.var <- function(x,na.rm=TRUE) sd(x,na.rm=na.rm)/mean(x,na.rm=na.rm)
-
-output <- paste("out", name, sep="/")
-pdf(file=paste(output,".pdf",sep=""), width = 5, height = 1.5)
-
-input <- paste("gen", name, sep="/")
-dat <- read.csv(paste(input,".csv",sep=""), header = T)
-
-# to compute median values across plots
-median <- aggregate(dat$time, list(dat$project), median)
-print("==sd==>")
-sd <- aggregate(dat$time, list(dat$project), sd)
-print(sd)
- 
-ggplot(dat, aes(x=factor(project), y=time)) +
-    geom_boxplot(outlier.shape=NA) +
-    theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) +
-    labs(y="Time cost (in secs)")+
-    geom_hline(aes(yintercept=mean(median$x)), colour = "red", linetype = 2)+
-    coord_cartesian(ylim = c(0,7.5))
- 
-aux <- dev.off()
-

### 2017-03-31 analysis/timecost.r

@@ -1,66 +1,0 @@
-library("dplyr")
-library("ggplot2")
-
-# df <- read.csv(file.choose())
-args <- commandArgs(trailingOnly = TRUE)
-rq1_df <- read.csv(args[1])
-#rq2_df <- read.csv(args[2], sep = ";")
-#rq3_df <- read.csv(args[3], sep = ",")
-
-###################
-# Analysis
-###################
-
-summarise(
-  group_by(rq1_df, test_success),
-  n = length(project_path),
-  tmin_xml = min(xml_test_time),
-  tmax_xml = max(xml_test_time),
-  tmin_mvn = min(maven_test_time),
-  tmax_mvn = max(maven_test_time)
-)
-
-###################
-# RQ1
-###################
-print("Investigate: Build success but builder time = 0")
-select(filter(rq1_df, test_success == "true" &
-                maven_test_time <= 0),
-       project_path)
-print("Investigate: build success but xml time = 0")
-select(filter(rq1_df, test_success == "true" &
-                xml_test_time <= 0),
-       project_path)
-
-rq1_df$tmin <- sapply(rq1_df$xml_test_time, FUN = function(v) {return(v / 60)})
-rq1_df <- filter(rq1_df, xml_test_time > 0)
-
-# Cost groups barplot
-pdf("out/barplot-timecost.pdf", height = 3, width = 3)
-ggplot(data = rq1_df, aes(x = timecost_group, fill = test_success)) +
-  geom_bar(width = .8, position = "dodge", colour = "black") +
-  geom_text(
-    size = 3,
-    position = position_dodge(width = .75),
-    stat = "count",
-    aes(label = ..count.. , y = ..count.. + 8)
-  ) +
-  scale_fill_brewer(labels = c("tests fail", "tests pass")) +
-  theme(legend.background = element_rect(),
-        legend.margin = margin(0),
-        legend.position = "top",
-        legend.title = element_blank()) +
-  labs(y = "Frequency", x = "Group")
-
-# Time cost boxplots
-pdf("out/boxplot-timecost.pdf", height = 3, width = 3)
-ggplot(data = rq1_df, aes(x = timecost_group, y = tmin, fill = test_success)) +
-  geom_boxplot() +  theme(strip.text = element_blank(),
-                          strip.background = element_blank(),
-                          legend.background = element_rect(),
-                          legend.margin = margin(0),
-                          legend.title = element_blank(),
[…]

### 2017-03-31 paper/modes.tex
pass on section II

@@
 configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
-data-race condition at different levels. For instance, if two test
-classes performs I/O operations to the same file, the configuration
-\SeqClassParMeth{} would be preferable. Finally, the configuration
-\ParClassParMeth{} does not impose any sequential execution but it is
-more likely to manifest data-races as methods from different classes
-run in parallel.
+data-race condition at different levels. \Luis{This is wrong $\rightarrow$} 
+For instance, if two test classes performs I/O operations to the same file,
+the configuration \SeqClassParMeth{} would be preferable. Finally, 
+the configuration \ParClassParMeth{} does not impose any sequential 
+execution but it is more likely to manifest data-races as methods 
+from different classes run in parallel.
 

### 2017-03-31 paper/intro.tex
pass on text

@@
 
+%% \Mar{Fan Long
+%%   (http://people.csail.mit.edu/fanl/) often uses a plot to show the
+%%   exponential rise of projects in github.  Please check if you can
+%%   find a reference to that or ask Fan Long what source he used (maybe
+%%   browsed with public API).}
+
 This paper reports on an empirical study we conducted to analyze the
@@
 projects.  This is a relevant problem given the tremendous popularity
-of open-source development\Mar{Fan Long
-  (http://people.csail.mit.edu/fanl/) often uses a plot to show the
-  exponential rise of projects in github.  Please check if you can
-  find a reference to that or ask Fan Long what source he used (maybe
-  browsed with public API).} and regression testing
+of open-source development and regression testing
 research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
@@
 \item \textbf{Prevalence of long-running test suites.}
-\item \textbf{Usage of test suite parallelization.}  
-\item \textbf{Speedups of parallelization.}
+\item \textbf{Prevalence of test suite parallelization.}
+\item \textbf{Developer's opinion (when parallelization not used).}    
+\item \textbf{Speedups of parallelization (when used).}
 \item \textbf{Issues versus benefits on using parallelization modes.}
@@
 Each dimension focuses on one aspect of our study.  The first
-dimension measures to which extent open-source projects contain time
-costly test suites.  In the limit, parallelization will be fruitless
-if all projects contain short-running test suites. The second dimension
+dimension measures to which extent open-source projects contain costly
+test suites.  In the limit, parallelization would be fruitless if all
+projects contained short-running test suites. The second dimension
 measures how often open-source projects, irrespective of their
-associated testing costs, use parallelization schemes.  This dimension
-is concerned with popularity of parallelization.  The third aspect
-evaluates the observed impact of parallelization on cost.  Finally,
-the last dimension evaluates the issues and benefits associated with
-running test suites with different parallel configurations (/modes).
-Overall, the study of these dimensions help us layout the current
-state-of-the-practice about the use and impact of parallelization in open-source
-projects, which presumably do not have large budgets.
+associated testing costs, use parallelization schemes.  The third
+dimension evaluates how developers involved in costly projects not
+using test suite parallelization perceive this technology.  The fourth
+dimension evaluates the observed impact of parallelization (when
+actually used) on cost.  Finally, the fifth dimension evaluates the
+issues and benefits associated with running test suites with different
+parallel configurations (/modes).  Overall, this study help us layout
+the current state-of-the-practice about usage and impact of test suite
+parallelization in open-source projects.
 

### 2017-03-31 paper/modes.tex
pass on section 2

@@
 
-This section provides important background on parallel test execution.
+Parallelism in test execution can be obtained at different levels.
+Figure~\ref{fig:levels} illustrates this.  The highest level indicates
+parallelism that can be obtained through different machines on the
+network.  For instance, using virtual machines from a cloud service to
+distribute test execution.  The lowest levels denote parallelism
+obtained within a single machine.  These levels are complementary:
+low-level parallelization leverages the computing power of server
+nodes whereas high-level schemes leverage the aggregate processing
+power of the farm.
 
-Parallelism in test execution can be obtained at different levels.
-Figure~\ref{fig:levels} illustrates these levels.  The highest
-level indicates parallelism that can be obtained through different
-machines on the network.  For instance, using virtual machines from a
-cloud service to perform a distributed execution.  The machine space
-sits under the ``network space'' and provides a \emph{lower-level}
-parallelism.  In this case, computation can be offloaded at different
-CPUs within a machine and at different threads within each CPU.  Note
-that all these levels are complementary:  low-level parallelization
-schemes could leverage the computing power of server nodes in addition
-to the aggregate processing power of the farm.
-
-This paper focuses at low-level parallelism (\ie, machine and CPU
-space), which can be enabled through build systems and testing
-frameworks.  Given the proliferation of multi-core machines it is not
-surprising that testing frameworks provide today support for parallel
-test execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng},
-and NUnit~\cite{nunit}).  In the following we elaborate relevant
-features of and testing frameworks build systems.  We focused on Java,
-Maven, and JUnit but the discussion can be generalized to other
-language and tools.
+This paper focuses at low-level parallelism, where computation can be
+offloaded at different CPUs within a machine and at different threads
+within each CPU.  This form of parallelism is enabled through build
+systems (spawning processes in different CPUs) and testing frameworks
+(spawning threads in a CPU).  It is important to note that a variety
+of testing frameworks provide today support for parallel test
+execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng}, and
+NUnit~\cite{nunit}) as to leverage the power of multi-core processors.
+In the following, we elaborate relevant features of testing frameworks
+and build systems.  We focused on Java, Maven, and JUnit but the
+discussion can be generalized to other language and tools.
 
@@
 \end{figure}
+
+%%  LocalWords:  parallelization CPUs JUnit TestNG NUnit multi JVM de
+%%  LocalWords:  JVMs falar explicar configuracao ilustrada levanta
+%%  LocalWords:  uma por cria cada executar paralelo escapeinside

### 2017-03-31 paper/evaluation.tex
pass on intro and evaluation (up to and including III.A)

@@
 
-We are interested in understanding the prevalence of time-consuming
-test suites and main sources of execution cost. We want to understand
-how the execution cost is distributed on test cases within a test
-suite and how developers approach test execution. Based on that, we
-study parallelization of testing frameworks and build systems.  More
-precisely, we investigate how prevalent test parallelization is, the
-potential for improving execution cost, issues of flakiness that
-hinders the use of parallelization, and how to address those issues.
-More specifically, we pose the following research questions:
+%% We are interested in understanding the prevalence of time-consuming
+%% test suites and main sources of execution cost. We want to understand
+%% how the execution cost is distributed on test cases within a test
+%% suite and how developers approach test execution. Based on that, we
+%% study parallelization of testing frameworks and build systems.  More
+%% precisely, we investigate how prevalent test parallelization is, the
+%% potential for improving execution cost, issues of flakiness that
+%% hinders the use of parallelization, and how to address those issues.
+%% More specifically, we pose the following research questions:
+
+%% The first research question addresses the prevalence of long-running
+%% test suites. We are interested to know if costly test suites are
+%% common in open-source projects.  The second research question
+%% addresses the relationship of test cases and the overall execution
+%% cost: we are interested to investigate how the execution time is
+%% distributed among test cases.  In the third research question, we
+%% investigate if developers consider low-level parallelism features
+%% available out-of-the-box to amortize test execution (see
+%% Section~\ref{sec:modes}). In addition, we want to identify what
+%% configurations are often used and why they are more popular (if any).
+%% The fourth research question addresses the impact of low-level
+%% parallelism on test execution from projects in our sample set. We want
+%% to identify subjects that already use test parallelization and compare
+%% their performance in contrast to sequential execution. In addition, we
+%% are interested in evaluating the performance of sequential test suites
+%% with different parallelization settings.
+%% Finally, the fifth research question discusses the limitations and
+%% insights to overcome the pitfalls of parallelization.
+
+%% \Comment{
+%%     \Fix{distribution of execution time per test case. For each subject
+%%     identified in the first research question, we investigate how
+%%     balanced is the cost of the test suite in contrast to the cost of
+%%     test cases and if there are subjects where the time cost is mostly
+%%     dominated by a small fraction of test cases.} \Fix{The third research
+%%     question addresses the distribution of regression tests according
+%%     to the use of computational resources.  We are interested in
+%%     investigating if regression test suites are CPU intensive and if there
+%%     are opportunities to improve performance. The RQ4 addresses}
+%%     \Fix{...elaborate...}
+
+%%     The rationale is that if the time cost of a regression test is equally
+%%     distributed among test cases, the execution cost could be potentially
+%%     improved by running tests in parallel (in contrast to the scenario
+%%     where only one test case dominates most of the execution time).
+%% }
+
+We pose the following research questions, organized by the dimensions
+presented in Section~\ref{sec:intro}.
 
@@
 \newcommand{\numRQD}{RQ4}
-\newcommand{\numRQF}{RQ5}
+\newcommand{\numRQE}{RQ5}
+\newcommand{\numRQF}{RQ6}
 
 \newcommand{\RQA}{How prevalent is the occurence of time-consuming
-  regression test suites in open-source projects?}
-\newcommand{\RQB}{How the time cost is distributed across test cases?}
-\newcommand{\RQC}{How often developers provides support to parallel
-execution of test suites?}
-\newcommand{\RQD}{What is the impact of parallelization?}
-\newcommand{\RQF}{What are the limitations of low-level parallelism?}
+  test suites\Comment{ in open-source projects}?}
+\newcommand{\RQB}{How time is distributed across test cases?}
+\newcommand{\RQC}{How prevalent is the use of test suite
+  parallelization\Comment{ in open-source projects}?}
+\newcommand{\RQD}{What are the speedups obtained with parallelization
+  (in projects that actually use it) on cost?}
+\newcommand{\RQE}{What are the main reasons that prevent developers
+  from using test suite parallelization?}
+\newcommand{\RQF}{How different configurations of parallel execution affect testing
+  cost and flakiness?}
 
+\begin{itemize}
+\item Potential
   \begin{itemize}
@@
   \item \textbf{\numRQB.} \RQB    
+  \end{itemize}    
+\item Usage
+  \begin{itemize}
   \item \textbf{\numRQC.} \RQC    
+  \end{itemize}
+\item Effectiveness
+  \begin{itemize}
   \item \textbf{\numRQD.} \RQD
+  \end{itemize}
+\item Perception
+  \begin{itemize}
+  \item \textbf{\numRQE.} \RQE
+  \end{itemize}
+\item Tradeoffs
+  \begin{itemize}
   \item \textbf{\numRQF.} \RQF    
+  \end{itemize}          
 \end{itemize}
@@
 
-The first research question addresses the prevalence of long-running
-test suites. We are interested to know if costly test suites are
-common in open-source projects.  The second research question
-addresses the relationship of test cases and the overall execution
-cost: we are interested to investigate how the execution time is
-distributed among test cases.  In the third research question, we
-investigate if developers consider low-level parallelism features
-available out-of-the-box to amortize test execution (see
-Section~\ref{sec:modes}). In addition, we want to identify what
-configurations are often used and why they are more popular (if any).
-The fourth research question addresses the impact of low-level
-parallelism on test execution from projects in our sample set. We want
-to identify subjects that already use test parallelization and compare
-their performance in contrast to sequential execution. In addition, we
-are interested in evaluating the performance of sequential test suites
-with different parallelization settings.
-Finally, the fifth research question discusses the limitations and
-insights to overcome the pitfalls of parallelization.
-
-\Comment{
-    \Fix{distribution of execution time per test case. For each subject
-    identified in the first research question, we investigate how
-    balanced is the cost of the test suite in contrast to the cost of
-    test cases and if there are subjects where the time cost is mostly
-    dominated by a small fraction of test cases.} \Fix{The third research
-    question addresses the distribution of regression tests according
-    to the use of computational resources.  We are interested in
-    investigating if regression test suites are CPU intensive and if there
-    are opportunities to improve performance. The RQ4 addresses}
-    \Fix{...elaborate...}
-
-    The rationale is that if the time cost of a regression test is equally
-    distributed among test cases, the execution cost could be potentially
-    improved by running tests in parallel (in contrast to the scenario
-    where only one test case dominates most of the execution time).
-}
-
 \subsection{Subjects}
@@
 
-We evaluated the characteristics of test suites in open-source
-development from a sample set of Java projects from \github{}.  We are
-interested to evaluate non-trivial test suites from popular projects
-that are in activity. We used the \github{}'s search
-API~\cite{githubsearch} to fetch Java projects according to the
-following criteria: (1) the primary language must be Java\footnote{In
-case of projects in multiple languages, the \github{} API considers
-the predominant language as the primary language.}; (2) the project
-has at least 100 stars; (3) latest update on (or after) January 1st,
-2016; (4) the \emph{readme} file contains the string \emph{mvn}.
+%% We evaluated the characteristics of test suites in open-source
+%% development from a sample set of Java projects from \github{}.  We are
+%% interested to evaluate non-trivial test suites from popular projects
+%% that are in activity.
 
-On \github{}, when a user adds a star to a project, s/he demonstrated
-appreciation and bookmarked it for later
-reference~\cite{github-stars}.  Although there is not a specific range
-for the number of stars, our criteria is an estimation to avoid
-trivial subjects: we assumed that \github{} users are likely to
-demonstrate interest on well-tested projects. The third criteria is a
-constraint to skip projects without recent activity. The fourth
-criteria is an approximation to find projects with Maven support. The
+%% , which is used on
+%% \github{} to indicate appreciation of a user to a
+%% project~\cite{github-stars},
+
+We used \github{}'s search API~\cite{githubsearch} to identify
+projects that satisfy the following criteria: (1) the primary language
+is Java\footnote{In case of projects in multiple languages, the
+  \github{} API considers the predominant language as the primary
+  language.}, (2) the project has at least 100 stars, (3) the latest
+update was on or after January 1st, 2016, and (4) the \emph{readme}
+file contains the string \emph{mvn}\footnote{As of now, \github{}'s
+  search API can only reflect contents from README file (not other
+  code elements).}.  We focused on Java for its popularity.  Although
+there is no clearcut limit on number of \github{}
+stars~\cite{github-stars} to define an interesting project, we
+observed that 100 was enough to eliminate trivial subjects. The third
+criteria is a constraint to skip projects without recent activity. The
+fourth criteria is an approximation to find Maven projects. The
 rationale is that if the string \emph{mvn} exists in the \emph{readme}
@@
 
+\vspace{1ex}
 \begin{figure}[h!]
@@
 subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
-the \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
-were not Maven projects (or did not have a \pomf{} in the root
-directory) and we were unable to execute the tests from
-\SubjectsGithubNotTestable{} tests (\eg, missing dependencies or
-incompatible testing environment). To ensure that our sample set is
-stable, we retested the remaining subjects to eliminate flaky tests
-(total of \SubjectsGithubFlaky{} subjects). Our final set consists in
+\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
+projects were not Maven (or did not have a \pomf{} in the root
+directory) and \SubjectsGithubNotTestable{} projects were untestable
+(because of missing dependencies or incompatible testing environment,
+for example). To ensure that our sample set was stable, we retested
+the remaining subjects to eliminate flaky tests (total of
+\SubjectsGithubFlaky{} subjects). Our final set consists in
 \numSubjs{} testable subjects.
 
-\vspace{-1ex}
 \begin{figure}[ht]
@@
 \end{figure}
-\vspace{-2ex}
 

### 2017-03-31 paper/intro.tex
pass on intro and evaluation (up to and including III.A)

@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
-considered in this study are as follows.
+considered in this study are as follows: potential, usage,
+effectiveness, perception, and tradeoffs.
 
-\begin{enumerate}
-\item \textbf{Prevalence of long-running test suites.}
-\item \textbf{Prevalence of test suite parallelization.}
-\item \textbf{Developer's opinion (when parallelization not used).}    
-\item \textbf{Speedups of parallelization (when used).}
-\item \textbf{Issues versus benefits on using parallelization modes.}
-\end{enumerate}
+%% \begin{enumerate}
+%% \item \textbf{Prevalence of long-running test suites.}
+%% \item \textbf{Prevalence of test suite parallelization.}
+%% \item \textbf{Developer's opinion (when parallelization not used).}    
+%% \item \textbf{Speedups of parallelization (when used).}
+%% \item \textbf{Issues versus benefits on using parallelization modes.}
+%% \end{enumerate}
 
-Each dimension focuses on one aspect of our study.  The first
-dimension measures to which extent open-source projects contain costly
-test suites.  In the limit, parallelization would be fruitless if all
-projects contained short-running test suites. The second dimension
-measures how often open-source projects, irrespective of their
-associated testing costs, use parallelization schemes.  The third
-dimension evaluates how developers involved in costly projects not
-using test suite parallelization perceive this technology.  The fourth
-dimension evaluates the observed impact of parallelization (when
-actually used) on cost.  Finally, the fifth dimension evaluates the
+Each dimension focuses on one aspect of our study.  The dimension
+\textbf{potential} measures the potential of parallelization to make
+an impact on testing costs.  In the limit, parallelization would be
+fruitless if all projects used short-running test suites or if the
+bulk of execution cost was dominated by a relatively small number of
+tests in the suite. The dimension \textbf{usage} measures how often
+open-source projects actually use parallelization schemes.  The
+dimension \textbf{effectiveness} measures the observed impact of
+parallelization (when used) on testing costs. The dimension
+\textbf{perception} focuses on how developers involved in costly
+projects not using test suite parallelization perceive this
+technology.  Finally, the dimension \textbf{tradeoffs} evaluates the
 issues and benefits associated with running test suites with different
-parallel configurations (/modes).  Overall, this study help us layout
-the current state-of-the-practice about usage and impact of test suite
-parallelization in open-source projects.
+parallel configurations (/modes).
 

### 2017-04-01 paper/intro.tex
pass on dimension

@@
 Each dimension focuses on one aspect of our study.  The dimension
-\textbf{potential} measures the potential of parallelization to make
-an impact on testing costs.  In the limit, parallelization would be
-fruitless if all projects used short-running test suites or if the
-bulk of execution cost was dominated by a relatively small number of
-tests in the suite. The dimension \textbf{usage} measures how often
-open-source projects actually use parallelization schemes.  The
-dimension \textbf{effectiveness} measures the observed impact of
-parallelization (when used) on testing costs. The dimension
-\textbf{perception} focuses on how developers involved in costly
-projects not using test suite parallelization perceive this
-technology.  Finally, the dimension \textbf{tradeoffs} evaluates the
-issues and benefits associated with running test suites with different
-parallel configurations (/modes).
+\textbf{potential} measures the potential of parallelization to reduce
+testing costs.  In the limit, parallelization would be fruitless if
+all projects used short-running test suites or if the bulk of
+execution cost was dominated by a relatively small number of tests in
+the suite.  The dimension \textbf{effectiveness} measures the observed
+impact of parallelization\Comment{~---~when used in selected
+  open-source projects~---~} on testing costs.  Intuitively, benefits
+are proportional to the cost reduction that parallelization brings.
+In the limit, the overhead of spawning virtual machines or threads can
+even result in added cost.  The dimension \textbf{adoption} evaluates
+(i) how often open-source projects use parallelization schemes and
+(ii) how developers involved in costly projects (not using test suite
+parallelization) perceive this technology.  It is important to measure
+resistance to the technology and its reasons.  Finally, the dimension
+\textbf{tradeoff} evaluates the issues and benefits associated
+with\Comment{running test suites with} different parallel
+configurations.  The configuration choice can affect both test cost
+and test flakiness.  Flakiness is caused by the non-determinism
+resulted from running tests in different
+schedulings. Paretto-efficient~\cite{hwang-masud-1979} configurations
+can guide future developments in this area.
 

### 2017-04-01 paper/evaluation.tex
pass on dimension
dimensions and rqs

@@
 We pose the following research questions, organized by the dimensions
-presented in Section~\ref{sec:intro}.
+of analysis we presented in Section~\ref{sec:intro}.
 
@@
 \newcommand{\numRQB}{RQ2}
-\newcommand{\numRQC}{RQ3}
-\newcommand{\numRQD}{RQ4}
+\newcommand{\numRQD}{RQ3}
+\newcommand{\numRQC}{RQ4}
 \newcommand{\numRQE}{RQ5}
@@
   from using test suite parallelization?}
-\newcommand{\RQF}{How different configurations of parallel execution affect testing
+\newcommand{\RQF}{To which extent parallel execution configurations affect testing
   cost and flakiness?}
@@
   \end{itemize}
-\item Usage
-  \begin{itemize}
-  \item \textbf{\numRQC.} \RQC    
-  \end{itemize}
 \item Effectiveness
@@
   \end{itemize}  
-\item Perception
+\item Adoption
   \begin{itemize}
+  \item \textbf{\numRQC.} \RQC    
   \item \textbf{\numRQE.} \RQE
   \end{itemize}
-\item Tradeoffs
+\item Tradeoff
   \begin{itemize}

### 2017-04-01 paper/intro.tex
tweaks on intro

@@
 
-This paper reports on an empirical study we conducted to analyze the
-impact of low-level parallelization to speedup testing in open-source
-projects.  This is a relevant problem given the tremendous popularity
-of open-source development and regression testing
-research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
-considered in this study are as follows: potential, usage,
-effectiveness, perception, and tradeoffs.
-
 %% \begin{enumerate}
@@
 
-Each dimension focuses on one aspect of our study.  The dimension
-\textbf{potential} measures the potential of parallelization to reduce
-testing costs.  In the limit, parallelization would be fruitless if
-all projects used short-running test suites or if the bulk of
-execution cost was dominated by a relatively small number of tests in
-the suite.  The dimension \textbf{effectiveness} measures the observed
-impact of parallelization\Comment{~---~when used in selected
-  open-source projects~---~} on testing costs.  Intuitively, benefits
-are proportional to the cost reduction that parallelization brings.
-In the limit, the overhead of spawning virtual machines or threads can
+This paper reports on an empirical study we conducted to analyze the
+impact of low-level parallelization to speedup testing in open-source
+projects.  This is a relevant problem given the tremendous popularity
+of open-source development and regression testing
+research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
+considered in this study are as follows: potential, effectiveness,
+adoption, and tradeoffs.  Each dimension focuses on one aspect of our
+study.  The dimension \textbf{potential} measures the potential of
+parallelization to reduce testing costs.  In the limit,
+parallelization would be fruitless if all projects used short-running
+test suites or if the bulk of execution cost was dominated by a
+relatively small number of tests in the suite.  The dimension
+\textbf{effectiveness} measures the observed impact of
+parallelization\Comment{~---~when used in selected open-source
+  projects~---~} on testing costs.  Intuitively, benefits are
+proportional to the cost reduction that parallelization brings.  In
+the limit, the overhead of spawning virtual machines or threads can
 even result in added cost.  The dimension \textbf{adoption} evaluates
@@
 with\Comment{running test suites with} different parallel
-configurations.  The configuration choice can affect both test cost
-and test flakiness.  Flakiness is caused by the non-determinism
-resulted from running tests in different
-schedulings. Paretto-efficient~\cite{hwang-masud-1979} configurations
-can guide future developments in this area.
+configurations.  Note that the configuration choice can affect both
+test cost and test flakiness, which is caused by the non-determinism
+resulted from running tests in different schedulings. Discovering
+Pareto-efficient~\cite{hwang-masud-1979} configurations is important
+to guide practitioners and future developments in this area.
 
@@
 %%% End:
-%%  LocalWords:  jenkins API VMs datarace
+%%  LocalWords:  jenkins API VMs datarace tradeoffs tradeoff Paretto
+%%  LocalWords:  schedulings

### 2017-04-01 paper/evaluation.tex
minor changes on description of setup: considering double-blindness and other minor tweaks

@@
 (64-bit version).  Software settings include \Comment{the Linux
-\emph{sysstat} package to measure performance, }git to fetch subjects,
-Java 8 and Maven 3.3.9 to build and test subjects. Our evaluation
-scripts depends on Python 3.4 and Bash to execute and R to analyze the
-data.  For replication, all source artifacts are publicly available at
-\Fix{create gh-pages}, including supporting scripts (\eg, the script
-that test subjects and generates the raw data), and the full list of
-projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
-and all software dependencies.}
+  \emph{sysstat} package to measure performance, }git to fetch
+subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
+Python 3.4, Bash, and R to process the data and generate plots.  All
+source artifacts are publicly available (on request) for
+replication\Comment{ at \Fix{create gh-pages}}.  This includes
+supporting scripts (\eg, the script that test subjects and generates
+the raw data), and the full list of projects. \Comment{, and a
+  \emph{Vagrantfile} to emulate our hardware and all software
+  dependencies.}
 

### 2017-04-01 paper/evaluation.tex
organizing eval
pass on eval

@@
 Python 3.4, Bash, and R to process the data and generate plots.  All
-source artifacts are publicly available (on request) for
-replication\Comment{ at \Fix{create gh-pages}}.  This includes
-supporting scripts (\eg, the script that test subjects and generates
-the raw data), and the full list of projects. \Comment{, and a
+source artifacts are publicly available for replication (on
+request)\Comment{ at \Fix{create gh-pages}}.  This includes supporting
+scripts (\eg, the script that test subjects and generates raw analysis
+data) and the full list of projects. \Comment{, and a
   \emph{Vagrantfile} to emulate our hardware and all software
@@
 
-\subsection{Answering research question \numRQA{}}
+\subsection{Potential}
 \label{sec:rqA}
+\label{sec:rqB}
 
 \begin{itemize}
-    \item \emph{\RQA}
+    \item \textbf{\RQA}
 \end{itemize}
 
-To evaluate the frequency of time-consuming regression tests, we
-considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
-and compared the elapsed time to run their tests. \Jbc{The following
-steps may change $\rightarrow$}
-Figure~\ref{fig:mvn-execution} shows the commands used in our script
-to test each subject. The main loop (lines 5-11) iterates over the
-list of subjects and invokes Maven in separated steps (lines 7-9). To
-avoid inflating the measured time we executed Maven in different
-steps: we first compiled the source and test files (line 7), made all
-dependencies available locally (line 8) and later, we ran the tests in
-offline mode (line 9) to bypass package updates. After the execution,
-we used a regular expression on the output log to extract the elapsed
-time (line 10). Before collecting the time cost, we executed all
-subjects and randomly selected 100 logs to inspect and identify
-non-related tasks (\eg, \emph{javadoc} generation and static analysis)
-to ignore during the experiment (lines 1-3).  To avoid noise from
-operating system events, we used a dedicated server remotely via SSH
-with the operating system running only essential services (\eg, the
-SSH server). In addition, we configured the \CodeIn{isolcpus} option
-from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
-to execute our experiment and the remaining CPUs to run the operating
+We considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
+to evaluate prevalence of projects with costly test suites.  To
+measure cost we used the following methodology. \Jbc{The following
+  steps may change $\rightarrow$} Figure~\ref{fig:mvn-execution} shows
+the commands used in our script to test each subject. The main loop
+(lines 5-11) iterates over the list of subjects and invokes Maven at
+different steps (lines 7-9) as to reduce measurement noise.  We first
+compiled the source and test files (line 7), made all dependencies
+available locally (line 8) and later, we ran the tests in offline mode
+(line 9) to bypass package updates. After the execution, we used a
+regular expression on the output log to extract the elapsed time (line
+10).
+
+Prior to running this script, we randomly selected a hundred projects
+to inspect corresponding execution logs.  The goal of the inspection
+was to identify tasks unrelated to testing (\eg, \emph{javadoc}
+generation and static analysis) that could interfere in our
+measurement.  These extra tasks were ignored from execution (lines
+1-3).  Furthermore, to avoid noise from operating system events, we
+configured our workstation to run only essential services.  The
+machine was dedicated to our experiments and we accessed it via
+SSH. In addition, we configured the \CodeIn{isolcpus} option from the
+Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs to
+execute our experiment and the remaining CPUs to run the operating
 system. By isolating a set of virtual CPUs, we prevent
-context-switching from experiment processes and OS-related processes.
+context-switching from experiment processes and OS-related
+processes.\Mar{can we cite this?}
 
@@
 
-We ran each subject's tests three times and grouped them according to
-the time cost (in average): tests that run in less than a minute
-(\shortg{} group), tests than run in one minute and less than five
-minutes (\medg{} group), and tests that run in five (or more) minutes
+We ran the test suite for each subject three times reporting their
+averages.  We grouped measurements in three time ranges: tests that
+run within a minute (\shortg{} group), tests that run in one to five
+minutes (\medg{} group), and tests that run in five or more minutes
 (\longg{} group). We based our classification from a previous work
@@
 
-\subsection{Answering research question \numRQB{}}
-\label{sec:rqB}
-
+\vspace{1ex}
 \begin{itemize}
-    \item \emph{\RQB}
+    \item \textbf{\RQB}
 \end{itemize}

### 2017-04-01 paper/evaluation.tex
fixing organization of section 3
fixing methodology and macros on RQX

@@
 
+\subsection{Answering research question \numRQD{}}
+\label{sec:rqD}
+
+\begin{itemize}
+    \item \emph{\RQD}
+\end{itemize}
+
+To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
+parallelization settings enabled by default identified in \numRQC{}
+and compared their time cost with sequential execution. We are
+interested in measuring the execution speedup (if any) when the
+parallelization settings are activated. It is important to mention
+that we ignored the remaining \Fix{??} subjects identified in
+Section~\ref{sec:rqC-2} because it would be impractical to execute
+each subject on specific conditions to measure the impact of
+parallelization.
+
+To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
+analyzed the \numProjectsPar{} subjects looking for the parallelism 
+configuration inside the \pomf{} of each module. To run the subjects
+sequentially, we manually modified the Maven Surefire configuration
+from the \numPomMatched{} identified before to not run in parallel.
+The Figure~\ref{fig:surefire-configuration} show the injected configuration
+in each \pomf{}.
+
+\input{codes/surefire}
+
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+      \textit{Answering \numRQD{}:}~\emph{\Jbc{summarize
+      findings.....}}
+  \end{minipage}
+}
+\end{center}
+
 \subsection{Answering research question \numRQC{}}
@@
 define the parallelism level within a JVM followed by
-\CodeIn{threadCounter} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
+\CodeIn{threadCount} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
 in older versions) to define the number of forked JVMs. For each test
@@
 \longg{}-running.
-\Jbc{rework this... $\rightarrow$}To reduce the number of build files
-to inspect, we consider only must contain one of these keywords that
-contain parallelization keywords, namely \CodeIn{forkMode},
-\CodeIn{forkCount}, and \CodeIn{parallel}.  This mining step, however,
-is not sound as a matching project may not indicate a project with a
-valid configuration for running tests in parallel.  False positive can
-happen because of comments, for instance.  To eliminate the cases of
-false positives and also to categorize true positive cases, we
-complemented the initial mining step with a manual inspection of
-files.
-
+\Luis{rework this... $\rightarrow$}To reduce the number of build files
+to inspect, we consider only \pomf{} files that contain the
+configuration node inside a \CodeIn{plugin} tag with a child tag named
+\CodeIn{artifactId} with the content \CodeIn{maven-surefire-plugin}.
+This mining step, however, is not sound as a matching project may not 
+indicate a project with a valid configuration for running tests in parallel.
+\Comment{
+False positive can happen because of comments, for instance.  
+To eliminate the cases of false positives and also to categorize 
+true positive cases, we complemented the initial mining step with a 
+manual inspection of files.
+}
 %% settings); the second step (inspection) consists in a manual
@@
 where \numPomMatched{} of those files match one of the keywords
-mentioned above.  From these \numPomMatched{} build files, we
-eliminated six false-positives: two were names of project modules
-(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
-comment, and three were commented configurations. The
-\numPomMatchedValid{} build files with valid configurations are
-distributed across \numProjectsPar{} projects from our sample.
+mentioned above.  From these \numPomMatched{} build filesi. The
+\numPomMatched{} configurations are distributed across \numProjectsPar{} 
+projects from our sample.
 % 
@@
     \centering
-    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
+    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
         \toprule
@@
             & \multirow{2}{*}{\# \pomf{}}
-            & \# \pomf{} matched
-            & \# projects matched\\%
+	    & \# \pomf{} matched\\
         % 2nd row - empty cell
             & % empty cell
-            & (false-positives)
             & / total\\%
         \midrule%
-        Long   & 1613 & 79 (1) & 19 / \numLong{}\\%
-        Medium & 1238 & 30 (5) & 22 / \numMed{}\\%
+	Long   & \numPomLong{} & 4 / \numLong{}\\%
+	Medium & \numPomMed{} & 6 / \numMed{}\\%
         \midrule%
@@
             & \pomMedLong{}
-            & \numPomMatched{} (6)
             & \numProjectsPar{} / \numMedLong{}\\%
@@
     first column indicates the group of projects according to their
-    time cost; the second column indicates the number of build files;
-    the third column is the subset of files with parallelization
+    time cost; the second column is the subset of files with parallelization
     keywords; the last column indicates the ratio of projects with
@@
 \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
-identified above, we investigated further the \numPomMatchedValid{}
+identified above, we investigated further the \numPomMatched{}
 build files with parallel settings.  We analyzed the support and
@@
       of projects supports parallel execution of test suites.}
-  \end{minipage}
-}
-\end{center}
-
-\subsection{Answering research question \numRQD{}}
-\label{sec:rqD}
-
-\begin{itemize}
-    \item \emph{\RQD}
-\end{itemize}
-
-To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
-parallelization settings enabled by default identified in \numRQC{}
-and compared their time cost with sequential execution. We are
-interested in measuring the execution speedup (if any) when the
-parallelization settings are activated. It is important to mention
-that we ignored the remaining \Fix{??} subjects identified in
-Section~\ref{sec:rqC-2} because it would be impractical to execute
-each subject on specific conditions to measure the impact of
-parallelization.
-
-To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
-analyzed the \numProjectsPar{} subjects looking for the parallelism 
-configuration inside the \pomf{} of each module. To run the subjects
-sequentially, we manually modified the Maven Surefire configuration
-from the \numPomMatchedValid{} identified before to not run in parallel.
-The Figure~\ref{fig:surefire-configuration} show the injected configuration
-in each \pomf{}.
-
-\input{codes/surefire}
-
-\begin{center}
-\fbox{
-  \begin{minipage}{8cm}
-      \textit{Answering \numRQD{}:}~\emph{\Jbc{summarize
-      findings.....}}
   \end{minipage}

### 2017-04-01 paper/evaluation.tex
Fix evaluation

@@
 
-From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
-where \numPomMatched{} of those files match one of the keywords
-mentioned above.  From these \numPomMatched{} build filesi. The
-\numPomMatched{} configurations are distributed across \numProjectsPar{} 
-projects from our sample.
+From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files.
+The \numPomMatched{} configurations are distributed across \numProjectsPar{} projects from our sample.
 % 

### 2017-04-01 paper/evaluation.tex
fix macros at evaluation

@@
       \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
-      that parallelism features are underused given that only \Fix{\%}
+      that parallelism features are underused given that only
+	  \percentParallel{}
       of projects supports parallel execution of test suites.}

### 2017-04-01 paper/modes.tex
Change example in section II
pass on paragraph example in section 2

@@
 configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
-data-race condition at different levels. \Luis{This is wrong $\rightarrow$} 
-For instance, if two test classes performs I/O operations to the same file,
-the configuration \SeqClassParMeth{} would be preferable. Finally, 
+data-race condition at different levels. For instance, if two test methods performs operations in a same variable, the configuration \SeqClassParMeth{} would be preferable. Finally, 
 the configuration \ParClassParMeth{} does not impose any sequential 
@@
 
-\subsubsection*{Illustration}~Figure~\ref{fig:surefire} illustrates
-the support of parallel execution with the configuration
-\ForkParMeth{} on Maven, a popular build system in Java projects.
-Maven uses a configuration file based on XML (known as \pomf{}) to
-define tasks related to the project building and these tasks are
-performed several plugins. \Jbc{falar do surefire e explicar a
-configuracao ilustrada - Surefire levanta uma JVM por core e cria uma
-pool de 5 threads em cada JVM para executar testes em paralelo.}
+%%  to
+%% define tasks related to the project building and these tasks are
+%% performed several plugins.This file
+%% contains defintions of tasks, which are implemented by a collection of
+%% plugins.
+
+%% \Jbc{falar do surefire e explicar a
+%% configuracao ilustrada - Surefire levanta uma JVM por core e cria uma
+%% pool de 5 threads em cada JVM para executar testes em paralelo.}
 
@@
 \end{lstlisting}
-    \caption{\label{fig:surefire} Maven setup with the configuration
-    \ForkParMeth{}.  Maven forks one JVM per core (\CodeIn{forkCount}
-    parameter) and uses five threads (\CodeIn{threadCount} parameter)
-    to run methods (\CodeIn{parallel} parameter) within each JVM.}
+    \caption{\label{fig:surefire} Configuration \ForkParMeth{} on Maven.}
 \end{figure}
+
+\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
+fragment of a Maven configuration file, known as \pomf{}, highlighting
+options to run tests using the parallel execution mode \ForkParMeth{}.
+With this configuration, Maven~---~through its test plugin
+Surefire~\cite{maven-surefire-plugin}~---~forks one JVM per core
+(\CodeIn{forkCount} parameter) and uses five threads
+(\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
+parameter) within each forked JVM.
 

### 2017-04-01 paper/modes.tex
minor tweak on firts two pars. in modes.tex

@@
 
-Parallelism in test execution can be obtained at different levels.
-Figure~\ref{fig:levels} illustrates this.  The highest level indicates
-parallelism that can be obtained through different machines on the
+Figure~\ref{fig:levels} illustrates the different levels where
+parallelism in test execution can be obtained.
+The highest level indicates
+parallelism obtained through different machines on the
 network.  For instance, using virtual machines from a cloud service to
@@
 obtained within a single machine.  These levels are complementary:
-low-level parallelization leverages the computing power of server
-nodes whereas high-level schemes leverage the aggregate processing
+the lowest levels leverage the computing power of server
+nodes whereas the highest level leverages the aggregate processing
 power of the farm.
 
-This paper focuses at low-level parallelism, where computation can be
+This paper focuses on low-level parallelism, where computation can be
 offloaded at different CPUs within a machine and at different threads
@@
 systems (spawning processes in different CPUs) and testing frameworks
-(spawning threads in a CPU).  It is important to note that a variety
+(spawning threads in one given CPU).  It is important to note that a variety
 of testing frameworks provide today support for parallel test
 execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng}, and
-NUnit~\cite{nunit}) as to leverage the power of multi-core processors.
+NUnit~\cite{nunit}) as to benefit from the available power of popular multi-core processors.
 In the following, we elaborate relevant features of testing frameworks

### 2017-04-02 paper/modes.tex
pass on modes.tex

@@
 
-The list below shows the choices to control parallelism within a Java
-virtual machine (JVM) which runs in a single process of the CPU.
+The list below shows the choices to control parallelism within one
+Java virtual machine (JVM), which runs in a single CPU process.  These
+options are offered by the testing framework, \eg{}, JUnit.
 
@@
     \textbf{Sequential classes; parallel methods
-        (\SeqClassParMeth).}~This configuration corresponds to the
-        sequential execution of test classes and test methods run in
-        multiple threads.
+      (\SeqClassParMeth).}~This configuration corresponds to running
+    test classes sequentially, but running test methods from those
+    classes concurrently.
 \item
     \textbf{Parallel classes; sequential methods
-        (\ParClassSeqMeth{}).}~This configuration corresponds to the
-        execution of test classes in multiple threads and tests run
-        sequentially within each thread.
+      (\ParClassSeqMeth{}).}~This configuration corresponds to running
+    test classes concurrently, but running test methods sequentially.
 \item
     \textbf{Parallel classes; Parallel methods
-        (\ParClassParMeth).}~This configuration corresponds
-        conceptually to the union of \ParClassSeqMeth{} and
-        \SeqClassParMeth{}: the testing framework runs test methods
-        from several classes on multiple threads.
+      (\ParClassParMeth).}~This configuration corresponds to the
+    combination of \SeqClassParMeth{} and \ParClassSeqMeth{}.  
 \end{itemize}
 
-The configuration \Seq{} is a proper fit for short-running test suites
-since this is the default configuration and the execution provides
-feedback in an acceptable time. However, for costly suites, it is
-impractical for developers to wait long-running executions to take
-action.  In this scenario, the remaining configuration may help to
-amortize the execution cost depending on how the test suite was
-designed. For instance, the configuration \SeqClassParMeth{} may
-speedup the execution of test suites composed large test classes since
-the cost of running all test methods is amortized by a pool of
-threads. Similarly, the configuration \ParClassSeqMeth{} may speedup
-test suites composed by several small test classes. Notice that both
-configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
-data-race condition at different levels. For instance, if two test methods performs operations in a same variable, the configuration \SeqClassParMeth{} would be preferable. Finally, 
-the configuration \ParClassParMeth{} does not impose any sequential 
-execution but it is more likely to manifest data-races as methods 
-from different classes run in parallel.
+%% The configuration \Seq{} is a proper fit for short-running test suites
+%% since this is the default configuration and the execution provides
+%% feedback in an acceptable time. However, for costly suites, it is
+%% impractical for developers to wait long-running executions to take
+%% action.  In this scenario, the remaining configuration may help to
+%% amortize the execution cost depending on how the test suite was
+%% designed. For instance,
+
+Notice that an important aspect in deciding which configuration to use
+(or in designing new test suites) is the possibility of race
+conditions on shared data during execution. For instance,
+configuration \ParClassSeqMeth{} may be preferable over
+\SeqClassParMeth{} when it is clear that several test methods in one
+class perform operations involving one given variable that is visible
+statically or within the scope of the test class.
+
+\Fix{unconvincing.  please, revise this.$\rightarrow$}Considering efficiency, the
+configuration \SeqClassParMeth{} may speedup the execution of test
+suites composed of large test classes since the cost of running all
+test methods is amortized by a pool of threads\Mar{$\leftarrow$
+  unclear to me.  you need to argument why one would prefer C1 over
+  C2.}. Similarly, the configuration \ParClassSeqMeth{} may speedup
+test suites composed by several small test classes.\Mar{$\leftarrow$
+  again, unclear to me (the reader).}  Finally, the configuration
+\ParClassParMeth{} does not impose any sequential execution but it is
+more likely to manifest data-races as methods from different classes
+run in parallel.
 

### 2017-04-02 paper/modes.tex
minor changes section 2

@@
 The list below shows the choices to control parallelism within one
-Java virtual machine (JVM), which runs in a single CPU process.  These
+Java Virtual Machine (JVM), which runs in a single CPU process.  These
 options are offered by the testing framework, \eg{}, JUnit.
@@
 
-The list below shows the choices to control parallelism through build
-systems which uses multiple JVMs on different processes each:
+The list below shows the choices to control parallelism through the
+build system, \eg{}, Maven.  The build system can spaw multiple JVMs,
+each running on its own OS process on a given CPU and handling a
+partition of the test set.
 
@@
     \textbf{Forked classes; sequential methods (\ForkSeq).}~This
-        configuration corresponds to the parallel execution of test
-        classes on different JVMs with test methods running
-        sequentially within each JVM.
+    configuration spawns multiple JVMs, assigning a partition of the
+    test set to each JVM.  Test methods run sequentially within each
+    JVM.
 \item
-    \textbf{Forked classes; parallel methods (\ForkParMeth).}~This
-        configuration corresponds to the parallel execution of test
-        classes on different JVMs with test methods running on
-        multiple threads within each JVM.
+    \textbf{Forked classes; parallel methods (\ForkParMeth).}~In
+    addition to forking multiple JVMs, as \ForkSeq{} does, this
+    configuration runs tests concurrently, as \SeqClassParMeth{} does.
 \end{itemize}

### 2017-04-02 paper/evaluation.tex
fix subsections to dimensions
updated plots
starting rq5

@@
     \vspace{2.5ex}
+    \begin{subfigure}{0.47\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{plots/boxplots-testcases.pdf}
+      \caption{\label{fig:medtcost}Distribution of test cases per group}
+    \end{subfigure}\\
+    \vspace{2.5ex}
     \begin{subfigure}{0.5\textwidth}
@@
 
-\subsection{Answering research question \numRQD{}}
+\subsection{Effectiveness}
 \label{sec:rqD}
@@
 \begin{itemize}
-    \item \emph{\RQD}
+    \item \textbf{\RQD}
 \end{itemize}
@@
 
-\subsection{Answering research question \numRQC{}}
+\subsection{Adoption}
 \label{sec:rqC}
+\label{sec:rqE}
 
@@
 
+\begin{itemize}
+	\item \textbf{\RQE{}}
+\end{itemize}
+
+\Luis{rework this $\rightarrow$}
+We considered the \numNonParallel{} subjects that do not use any
+parallel mode from Section~\ref{sec:rqC} and elaborated a
+quick survey to extent the comprehension about why developers do not
+use parallel configuration. \Luis{describe how we created the survey}.
+In total, we sent \emailsSent{} e-mails to developers that recently
+contributed to the project and received \emailsAnswered{} answers.
+
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+      \textit{Answering \numRQE{}:~\emph{\Luis{summarize
+	  findings...}}}
+  \end{minipage}
+}
+\end{center}
+
 %%To evaluate the distribution of execution time per project, we sorted

### 2017-04-02 paper/evaluation.tex
fixing rq4 methodology

@@
 \Luis{rework this... $\rightarrow$}To reduce the number of build files
-to inspect, we consider only \pomf{} files that contain the
-configuration node inside a \CodeIn{plugin} tag with a child tag named
-\CodeIn{artifactId} with the content \CodeIn{maven-surefire-plugin}.
-This mining step, however, is not sound as a matching project may not 
+to inspect, we consider only \pomf{} files that contain
+\CodeIn{plugin} tags with a child tag \CodeIn{artifactId} with the
+value \CodeIn{maven-surefire-plugin} and a \CodeIn{configuration}
+node. This mining step, however, is not sound as a matching project may not 
 indicate a project with a valid configuration for running tests in parallel.
-\Comment{
-False positive can happen because of comments, for instance.  
-To eliminate the cases of false positives and also to categorize 
-true positive cases, we complemented the initial mining step with a 
-manual inspection of files.
-}
+
+%False positive can happen because of comments, for instance.  
+%To eliminate the cases of false positives and also to categorize 
+%true positive cases, we complemented the initial mining step with a 
+%manual inspection of files.
 %% settings); the second step (inspection) consists in a manual
@@
 column indicates the group of projects according to their time cost.
-The second column indicates the number of build files per group.  The
-third column is a subset from the previous column and represents the
-number of build files found in the mining step (including
-false-positives highlighted in parentheses). The last column indicates
-the ratio of projects with parallelization settings.
+The second column indicates the number of build files per group. 
+The last column indicates the ratio of projects with parallelization settings.
 
@@
     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
-    \caption{\label{fig:freqmodes-static}Distribution of parallel modes
+	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
+	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
     identified statically in a subset of \numProjectsPar{} projects.

### 2017-04-03 paper/evaluation.tex
minor fixes

@@
 rationale is that if the string \emph{mvn} exists in the \emph{readme}
-file, it may represent a Maven call (\eg, to compile or test the
+file, it may represent a Maven call (\eg, to compile or to test the
 project). We used Maven as a reference due to its popularity on Java
-projects and to automate our evaluation scripts. A Maven project may
-contain several sub-modules with multiple \pomf{} files. We considered
-only projects with a \pomf{} file located in the root directory.
+projects and to assist one of our experiments. A Maven project may
+contain several sub-modules with multiple \pomf{} files but we only
+considered projects with a \pomf{} file located in the root directory.
 Figure~\ref{fig:subject-query} illustrates the query to the \github{}
@@
 \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
-projects were not Maven (or did not have a \pomf{} in the root
-directory) and \SubjectsGithubNotTestable{} projects were untestable
+projects were not Maven or did not have a \pomf{} in the root
+directory and \SubjectsGithubNotTestable{} projects were untestable
 (because of missing dependencies or incompatible testing environment,
 for example). To ensure that our sample set was stable, we retested
-the remaining subjects to eliminate flaky tests (total of
-\SubjectsGithubFlaky{} subjects). Our final set consists in
+the remaining subjects to eliminate projects with flaky tests (total of
+\SubjectsGithubFlaky{} subjects). Our final set consists of
 \numSubjs{} testable subjects.

### 2017-04-03 paper/evaluation.tex
adjustments
adjusting

--- 2017-04-02 paper/evaluation.tex
@@
 from the \numPomMatched{} identified before to not run in parallel.
-The Figure~\ref{fig:surefire-configuration} show the injected configuration
-in each \pomf{}.
-
-\input{codes/surefire}
 
@@
       \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
-      that parallelism features are underused given that only
+      that parallelism features are underused by defailt given that only
 	  \percentParallel{}
-      of projects supports parallel execution of test suites.}
+      of projects supports parallel execution of test suites without
+	  any extra parameter.}
   \end{minipage}
@@
 We considered the \numNonParallel{} subjects that do not use any
-parallel mode from Section~\ref{sec:rqC} and elaborated a
+parallel mode from Section~\ref{sec:rqC-1} and elaborated a
 quick survey to extent the comprehension about why developers do not
 use parallel configuration. \Luis{describe how we created the survey}.
-In total, we sent \emailsSent{} e-mails to developers that recently
-contributed to the project and received \emailsAnswered{} answers.
+We first retrieve the last 20 commits from the project repository and
+got the developers e-mails. In total, we sent \emailsSent{} e-mails to
+different developers that recently contributed to the project.
+There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
+those were answering the survey.
 
+The survey sent was composed by three open questions and one closed
+question: (I) How long does it take for test to run in your
+environment? Can you briefly define your setup? (II) Do you confirm
+that your project does not run in parallel? (III) Select a reason for
+not using parallelization: (a) I did not know it was possible; (b) I
+was concerned with concurrency issues; (c) I use a continuous
+integration server; (d) Some other reason. Please elaborate.
+
+\Comment{
+\begin{enumerate}
+	\item How long does it take for test to run in your
+		environment?
+	\item Can you briefly define your setup?
+	\item Do you confirm that your project does not run in
+		parallel?
+	\item Select a reason for not using paralellization:
+		\begin{enumarate}
+			\item I did not know it was possible;
+			\item I was concerned with concurrency issues;
+			\item I use a continuous integration server;
+			\item Some other reason.
+		\end{enumerate}
+\end{enumerate}
+}
 \begin{center}

### 2017-04-03 paper/evaluation.tex

@@
     \centering
-    \begin{subfigure}{0.24\textwidth}
+    \begin{subfigure}{0.182\textwidth}
         \centering
@@
     ~
-    \begin{subfigure}{0.24\textwidth}
+    \begin{subfigure}{0.25\textwidth}
         \centering
@@
     \vspace{2.5ex}
-    \begin{subfigure}{0.47\textwidth}
+    \begin{subfigure}{0.38\textwidth}
       \centering
@@
     \end{subfigure}\\
-    \vspace{2.5ex}
+    \vspace{3ex}
     \begin{subfigure}{0.5\textwidth}

### 2017-04-03 paper/modes.tex
adjusting examples

@@
 
-\Fix{unconvincing.  please, revise this.$\rightarrow$}Considering efficiency, the
-configuration \SeqClassParMeth{} may speedup the execution of test
-suites composed of large test classes since the cost of running all
-test methods is amortized by a pool of threads\Mar{$\leftarrow$
-  unclear to me.  you need to argument why one would prefer C1 over
-  C2.}. Similarly, the configuration \ParClassSeqMeth{} may speedup
-test suites composed by several small test classes.\Mar{$\leftarrow$
-  again, unclear to me (the reader).}  Finally, the configuration
-\ParClassParMeth{} does not impose any sequential execution but it is
-more likely to manifest data-races as methods from different classes
-run in parallel.
+Considering efficiency, the configuration \SeqClassParMeth{} may
+speedup the execution of test classes composed of small test methods
+involving variables that is visible within the scope of the method.
+Similarly, the configuration \ParClassSeqMeth{} may speedup
+test suites composed by several test classes with few test methods.
+Finally, the configuration \ParClassParMeth{} does not impose any 
+sequential execution but it is more likely to manifest data-races as 
+methods from different classes run in parallel.
 

### 2017-04-03 paper/modes.tex
pass on section2

@@
 (or in designing new test suites) is the possibility of race
-conditions on shared data during execution. For instance,
-configuration \ParClassSeqMeth{} may be preferable over
-\SeqClassParMeth{} when it is clear that several test methods in one
-class perform operations involving one given variable that is visible
-statically or within the scope of the test class.
-
-Considering efficiency, the configuration \SeqClassParMeth{} may
-speedup the execution of test classes composed of small test methods
-involving variables that is visible within the scope of the method.
-Similarly, the configuration \ParClassSeqMeth{} may speedup
-test suites composed by several test classes with few test methods.
-Finally, the configuration \ParClassParMeth{} does not impose any 
-sequential execution but it is more likely to manifest data-races as 
-methods from different classes run in parallel.
+conditions on shared data during execution.  Data sharing can occur
+through state that is reachable from statically-declared variables in
+the program or through variables declared within the scope of the test
+class~\cite{luo-etal-fse2014}.  Considering data race avoidance,
+intuitively, configuration \SeqClassParMeth{} is preferable over
+\ParClassSeqMeth{} when it is clear that test methods in a class do
+not manipulate shared state, which can be challenging to
+determine~\cite{bell-etal-esecfse2015}, whereas \ParClassSeqMeth{} is
+preferable over \SeqClassParMeth{} when it is clear that several test
+methods in one class perform operations involving shared data.
+Configuration \ParClassParMeth{} is more likely to manifest data races
+during execution as it does not restrict scheduling orderings. Note
+that speedups depend on several factors, including the test suite size
+and distribution of test methods per class.
 
@@
 The list below shows the choices to control parallelism through the
-build system, \eg{}, Maven.  The build system can spaw multiple JVMs,
+build system, \eg{}, Maven.  The build system can spawn multiple JVMs,
 each running on its own OS process on a given CPU and handling a
@@
 
-Several build systems support the execution of test classes in forked
-processes running a JVM. In the configuration \ForkSeq{}, each spawned
-process runs a different test class at time and the builder merges the
-results from each execution. In the configuration \ForkParMeth{}, the
-build system forwards settings to the underlying testing framework to
-enable parallel execution within each process in addition to running
-test classes on different processes.  However, some configurations
-(\eg, \ParClassSeqMeth) may not take effect since only one test class
-can run in a forked process at time.  To the best of our knowledge, we
-are unaware of any build system capable of running multiple classes at
-time within a forked process.
+%% In the configuration \ForkSeq{}, each spawned
+%% process runs a different test class at time and the builder merges the
+%% results from each execution. In the configuration \ForkParMeth{}, the
+%% build system forwards settings to the underlying testing framework to
+%% enable parallel execution within each process in addition to running
+%% test classes on different processes.
+
+Forking OS processes to run test jobs is a common feature of build
+systems as to obtain parallelism at the machine space (see
+Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
+Ant), this amounts to spawning one JVM instance (per process) per CPU,
+on a machine with potentially many virtual CPUs, and aggregating
+corresponding results when jobs finish.  Note that forking can only be
+combined with configuration \SeqClassParMeth{} (see
+Section~\ref{sec:frameworks}) as Maven only accepts one test class at
+a time per forked process.\Mar{$\leftarrow$Are you sure about this?
+  It seems silly.  Maybe, the rationale is to ``keep design simple''.}
+To attenuate the non-trivial cost of spawning new processes and JVMs on
+every test class, Maven offers an option to reuse the
+JVM.\Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
+  configuracao abaixo?}
+
+%%We are unaware of other build system capable of running multiple
+%%classes at time within a forked process.
 
@@
 %%  LocalWords:  uma por cria cada executar paralelo escapeinside
+%%  LocalWords:  xleftmargin framexleftmargin basicstyle boxpos
+%%  LocalWords:  numberstyle morekeywords threadCount forkCount
+%%  LocalWords:  perCoreThreadCount reuseFork deletekeywords groupId
+%%  LocalWords:  artifactId

### 2017-04-03 paper/evaluation.tex
pass on rq2

@@
 subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
-Python 3.4, Bash, and R to process the data and generate plots.  All
+Python 3.4, Bash, R and Ruby 2.3 to process the data and generate plots.  All
 source artifacts are publicly available for replication (on
@@
 \end{itemize}
+%\Jbc{The following steps may change $\rightarrow$}
 
-We considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
-to evaluate prevalence of projects with costly test suites.  To
-measure cost we used the following methodology. \Jbc{The following
-  steps may change $\rightarrow$} Figure~\ref{fig:mvn-execution} shows
-the commands used in our script to test each subject. The main loop
-(lines 5-11) iterates over the list of subjects and invokes Maven at
-different steps (lines 7-9) as to reduce measurement noise.  We first
-compiled the source and test files (line 7), made all dependencies
-available locally (line 8) and later, we ran the tests in offline mode
-(line 9) to bypass package updates. After the execution, we used a
-regular expression on the output log to extract the elapsed time (line
-10).
+To evaluate prevalence of projects with costly test suites, we
+considered the \numSubjs{} testable subjects from
+Figure~\ref{fig:subjects}.  Figure~\ref{fig:mvn-execution} illustrates
+the script we used to measure time.  The main loop (lines 5-11)
+iterates over the list of subjects and invokes Maven multiple
+times\Comment{ to isolate cost of running tests} (lines 7-9).  We
+first compiled the source and test files (line 7), made all
+dependencies available locally (line 8), and then we ran the tests in
+offline mode to skip the package update task (line 9). After
+execution, we used a regular expression on the output log to extract
+the elapsed time (line 10).
 
-Prior to running this script, we randomly selected a hundred projects
-to inspect corresponding execution logs.  The goal of the inspection
-was to identify tasks unrelated to testing (\eg, \emph{javadoc}
-generation and static analysis) that could interfere in our
-measurement.  These extra tasks were ignored from execution (lines
-1-3).  Furthermore, to avoid noise from operating system events, we
-configured our workstation to run only essential services.  The
-machine was dedicated to our experiments and we accessed it via
-SSH. In addition, we configured the \CodeIn{isolcpus} option from the
-Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs to
-execute our experiment and the remaining CPUs to run the operating
-system. By isolating a set of virtual CPUs, we prevent
-context-switching from experiment processes and OS-related
-processes.\Mar{can we cite this?}
+Prior to running this script, we inspected Maven execution logs from a
+sample inclduing a hundred projects.  The goal of this inspection step
+is to find tasks unrelated to testing (\eg, \emph{javadoc} generation
+and static analyses) that could interfere in our measurements.  The
+tasks we found were ignored from execution (lines 1-3).  Furthermore,
+to avoid noise from operating system events, we configured our
+workstation to run only essential services.  The machine was dedicated
+to our experiments and we accessed it via SSH. In addition, we
+configured the \CodeIn{isolcpus} option from the Linux Kernel
+\cite{linux-kernel} to isolate six virtual CPUs to execute our
+experiment, leaving the remaining CPUs to run OS
+processes~\cite{isolcpus-use}.  The rationale for this decision is to
+prevent context-switching between user processes (running the
+experiment) and OS-related processes.  Finally, to make sure our
+measurements were fair, we compared the sequential execution of tests
+using Maven with JUnit's default \CodeIn{JUnitCore} runner, invoked
+from the command line.  We observed that results were very similar.
+
+%% We executed each project's test suite for
+%% \Fix{5} times through Maven and directly through JUnit each project
 
@@
 
-We ran the test suite for each subject three times reporting their
-averages.  We grouped measurements in three time ranges: tests that
-run within a minute (\shortg{} group), tests that run in one to five
-minutes (\medg{} group), and tests that run in five or more minutes
-(\longg{} group). We based our classification from a previous work
-\cite{gligoric-etal-issta2015} and added the \medg{} group due to the
-variability of the time cost from subjects out of the \shortg{} group.
-\Jbc{these results will be updated $\rightarrow$}
-Figure~\ref{fig:rq1-boxplot} shows the time cost distribution of each
-group: the \shortg{} group is the most right skewed distribution with
-outliers closed to the \medg{} group and 50\% of the subjects run in
-less than 15 seconds; the median from the \medg{} group is nearly two
-minutes and most of the subjects run in less than four minutes; most
-of the \longg{} group runs in less than 25 minutes but has outliers
-that require more than 50 minutes to execute.
-Figure~\ref{fig:rq1-barplot} summarizes the proportion of subjects
-from each group.
+We ran the test suite for each subject three times, reporting averaged
+execution times in three ranges: tests that run within a minute
+(\shortg{} group), tests that run in one to five minutes (\medg{}
+group), and tests that run in five or more minutes (\longg{}
+group). We followed a similar methodology to group projects by time as
+Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
+regression test selection.\Comment{ and added the \medg{} group due to
+  the variability of the time cost from subjects out of the \shortg{}
+  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
+each group.  As it is to be expected, \longg{} and \medg{} projects do
+not occur as frequently as \shortg{} projects.  However, they do ocur
+in relatively high numbers.  Figure~\ref{fig:rq1-boxplot} shows cost
+distribution of test suites in each group as boxplots.  The
+distribution associated with the \shortg{} group is the most
+unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
+  group}.  The test suites in this group run in 15 or less seconds for
+over 75\% of the cases.  Such scenarios constitute the majority of the
+cases we analyzed.  Considering the groups \medg{} and \longg{},
+however, we found many costly executions.  Nearly 75\% of the projects
+from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
+the projects from the \longg{} group take $\sim$20 minutes to run.  We
+found cases in the \longg{} group were execution takes over 50 minutes
+to complete, as can be observed from the outliers (dots) in the plot.
+
+%% the median from the
+%% \medg{} group is nearly two minutes and most of the subjects run in
+%% less than four minutes; most of the \longg{} group runs in less than
+%% 25 minutes but has outliers that require more than 50 minutes to
+%% execute.
 
@@
 
-It is important to mention that Figure~\ref{fig:rq1-barplot}
-represents a lower bound estimation for time cost because some tests
-may finish earlier than expected due to existing bugs on the ongoing
-revision.  From the \numSubjs{} compiled projects, \numSubjsPass{}
-successfully executed all tests and \numSubjsFail{} reported test
-failures.  Also, some projects may omit long-running tests on their
-default execution. For instance, the project
-\CodeIn{apache.maven-surefire} runs all unit tests in a few seconds in
-our environment.  According to our criteria, this project would be
-classified as \shortg{} but we noticed that by providing additional
-parameters from the subject, the integration tests are included during
-the execution.  After including the integration tests, the tests time
-increases to nearly 30 minutes.  Since it would be impractical to
-analyze each project, we considered only the tests executed by
-default.
+%% Figure~\ref{fig:rq1-barplot} is a lower bound estimation of cost
+%% because some tests may finish earlier than expected due to existing
+%% test failures in the revision we downloaded.
+
+It is important to note that we under-estimated cost in our
+experiments for two main reasons.  First, some tests may finish
+earlier than expected due to observed test failures in some of the
+revisions we downloaded.  From the \numSubjs{} testable projects,
+\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
+reported some test failures.  Second, some projects may omit
+long-running tests on their default execution. For instance, the
+project \CodeIn{apache.maven-surefire} runs all unit tests in a few
+seconds in our environment.  According to our criteria, this project
+would be classified as \shortg{} but we noticed that only smoke test
+run by default.  The more expensive integration and system tests are
+only accessible via custom parameters.  When running the test suite
+with integration tests, the testing time goes to nearly 30 minutes.
+For simplicity, we considered only the tests executed by default.
 
@@
 \begin{minipage}{8cm}
-    \textit{Answering \numRQA{}:}~\emph{We concluded that
-    time-consuming regression test suites are relatively frequent in
-    open-source projects given that \percentMedLongRunning{} of the
-    projects are costly (\ie, \numMedLong{} projects from \medg{} and
-    \longg{}).}
+    \textit{Answering \numRQA{}:}~\emph{We conclude that
+      time-consuming test suites are relatively frequent in
+      open-source projects.  We found that \percentMedLongRunning{} of
+      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
+      projects) take at least 3 minutes to run and
+      \percentLongRunning{} take at least 5 minutes to run.\Comment{
+        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
 \end{minipage}
@@
 
-\begin{figure}[ht]
+\begin{figure}[h]
     \centering
-
     \begin{subfigure}{0.47\textwidth}
@@
       \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
-      \caption{\label{fig:longtcost}Long group}
+      \caption{\label{fig:longtcost}Long group.}
     \end{subfigure}\\
-    \vspace{2.5ex}
+    \vspace{2ex}
     \begin{subfigure}{0.47\textwidth}
@@
       \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
-      \caption{\label{fig:medtcost}Medium group}
+      \caption{\label{fig:medtcost}Medium group.}
     \end{subfigure}\\
-    \vspace{2.5ex}
-    \begin{subfigure}{0.38\textwidth}
+    \vspace{2ex}
+    \begin{subfigure}{0.47\textwidth}
       \centering
-      \includegraphics[width=\textwidth]{plots/boxplots-testcases.pdf}
-      \caption{\label{fig:medtcost}Distribution of test cases per group}
+      \includegraphics[width=.75\textwidth]{plots/boxplots-testcases.pdf}
+        \caption{\label{fig:medtcost}Distribution of test cases.}
     \end{subfigure}\\
-    \vspace{3ex}
+    \vspace{2ex}
     \begin{subfigure}{0.5\textwidth}
@@
         \midrule    
-        Long   &  9 & 14 & 5 \\
-        Medium & 17 & 20 & 7 \\
+        Long   &  7 & 15 & 12 \\
+        Medium & 22 & 19 & 7 \\
         \bottomrule
       \end{tabular}
-      \caption{\label{fig:sd}\Fix{adjust values}}    
+      \caption{\label{fig:sd}Standard deviantion of test cases}
     \end{subfigure}%
-
     \caption{\label{fig:time-distributions}Distribution of test case
-    execution cost per project.}    
+    execution cost per project.}%
 \end{figure}
 
-\sloppy Figures~\ref{fig:medtcost} and~\ref{fig:longtcost} show the
+\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
 time distribution of tests per project.  We observed that the average
 median value of execution cost for a test was relatively small (dashed
-horizontal red lines), namely \Fix{0.41s} for \medg{} projects and
-\Fix{0.23s} for \longg{} projects.  Note that correlation between cost
+horizontal red lines), namely 0.31s for \medg{} projects and
+0.23s for \longg{} projects.  Note that correlation between cost
 of test suites and cost of their individual tests is not to be
@@
 tests.  For example, the highest value of $\sigma$ occurred in project
-\CodeIn{wildfly-swarm}, whose test suite was classified as
-long-running.  This project contains only \Fix{65} tests, \Fix{62} of
+\CodeIn{uber\_chaperone}, whose test suite was classified as
+medium-running.  This project contains only \Fix{65} tests, \Fix{62} of
 which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
@@
 classified as short-running.  A closer inspection in the data
-indicates that the project \CodeIn{wildfly-swarm} was an extreme case;
+indicates that the project \CodeIn{uber\_chaperone} was an extreme case;
 we did not find projects with similar characteristics of time
-monopolization.  Project \CodeIn{jenkinsci.gerrit-trigger-plugin} is
-also classified as long-running and has the second highest value of
+monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
+classified as long-running and has the second highest value of
 $\sigma$.  For this project, however, cost is distributed more
@@
 
-\Luis{rework this $\rightarrow$}
-We considered the \numNonParallel{} subjects that do not use any
-parallel mode from Section~\ref{sec:rqC-1} and elaborated a
+To understand why developers prefer not use parallel test execution,
+we considered the \numNonParallel{} subjects that do not use any
+parallel mode from Section~\ref{sec:rqC-1} (\ie{}, \medg{} and
+\longg{}
+projects that does not run in parallel by default) and elaborated a
 quick survey to extent the comprehension about why developers do not
@@
 \end{center}
+
+\Luis{these values need macro $\rightarrow$}
+From the valid replies, we noticed that \Fix{55.2\%
+(16/\emailsTrueAnswers{})} of developers use an external continuous
+integration server to run tests, \Fix{27.6\% (8/\emailsTrueAnswers{})} run tests in the
+development machine, \Fix{13.8\% (4/\emailsTrueAnswers{})} did
+not specified the environment.
 

### 2017-04-03 paper/evaluation.tex
done with RQ1 (for now)

--- 2017-04-03 paper/evaluation.tex
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
+
     \begin{subfigure}{0.47\textwidth}
@@
       \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
-      \caption{\label{fig:longtcost}Long group.}
+      \caption{\label{fig:longtcost}Long group}
     \end{subfigure}\\
-    \vspace{2ex}
+    \vspace{2.5ex}
     \begin{subfigure}{0.47\textwidth}
@@
       \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
-      \caption{\label{fig:medtcost}Medium group.}
+      \caption{\label{fig:medtcost}Medium group}
     \end{subfigure}\\
-    \vspace{2ex}
-    \begin{subfigure}{0.47\textwidth}
+    \vspace{2.5ex}
+    \begin{subfigure}{0.38\textwidth}
       \centering
-      \includegraphics[width=.75\textwidth]{plots/boxplots-testcases.pdf}
-        \caption{\label{fig:medtcost}Distribution of test cases.}
+      \includegraphics[width=\textwidth]{plots/boxplots-testcases.pdf}
+      \caption{\label{fig:medtcost}Distribution of test cases per group}
     \end{subfigure}\\
-    \vspace{2ex}
+    \vspace{3ex}
     \begin{subfigure}{0.5\textwidth}
@@
         \midrule    
-        Long   &  7 & 15 & 12 \\
-        Medium & 22 & 19 & 7 \\
+        Long   &  9 & 14 & 5 \\
+        Medium & 17 & 20 & 7 \\
         \bottomrule
       \end{tabular}
-      \caption{\label{fig:sd}Standard deviantion of test cases}
+      \caption{\label{fig:sd}\Fix{adjust values}}    
     \end{subfigure}%
+
     \caption{\label{fig:time-distributions}Distribution of test case
-    execution cost per project.}%
+    execution cost per project.}    
 \end{figure}
 
-\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
+\sloppy Figures~\ref{fig:medtcost} and~\ref{fig:longtcost} show the
 time distribution of tests per project.  We observed that the average
 median value of execution cost for a test was relatively small (dashed
-horizontal red lines), namely 0.31s for \medg{} projects and
-0.23s for \longg{} projects.  Note that correlation between cost
+horizontal red lines), namely \Fix{0.41s} for \medg{} projects and
+\Fix{0.23s} for \longg{} projects.  Note that correlation between cost
 of test suites and cost of their individual tests is not to be
@@
 tests.  For example, the highest value of $\sigma$ occurred in project
-\CodeIn{uber\_chaperone}, whose test suite was classified as
-medium-running.  This project contains only \Fix{65} tests, \Fix{62} of
+\CodeIn{wildfly-swarm}, whose test suite was classified as
+long-running.  This project contains only \Fix{65} tests, \Fix{62} of
 which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
@@
 classified as short-running.  A closer inspection in the data
-indicates that the project \CodeIn{uber\_chaperone} was an extreme case;
+indicates that the project \CodeIn{wildfly-swarm} was an extreme case;
 we did not find projects with similar characteristics of time
-monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
-classified as long-running and has the second highest value of
+monopolization.  Project \CodeIn{jenkinsci.gerrit-trigger-plugin} is
+also classified as long-running and has the second highest value of
 $\sigma$.  For this project, however, cost is distributed more

### 2017-04-03 paper/evaluation.tex
added missing content
adjustments on rq3

--- 2017-04-03 paper/evaluation.tex
@@
 
-To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
-parallelization settings enabled by default identified in \numRQC{}
-and compared their time cost with sequential execution. We are
-interested in measuring the execution speedup (if any) when the
-parallelization settings are activated. It is important to mention
-that we ignored the remaining \Fix{??} subjects identified in
-Section~\ref{sec:rqC-2} because it would be impractical to execute
-each subject on specific conditions to measure the impact of
-parallelization.
+To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
+tested and confirmed parallelization activated by default, and
+compared their time cost with sequential execution. We are interested
+in measuring the execution speedup (if any) when the parallelization
+settings are activated.
 
-To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
-analyzed the \numProjectsPar{} subjects looking for the parallelism 
-configuration inside the \pomf{} of each module. To run the subjects
-sequentially, we manually modified the Maven Surefire configuration
-from the \numPomMatched{} identified before to not run in parallel.
+%% To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
+%% parallelization settings enabled by default identified in \numRQC{}
+%% and compared their time cost with sequential execution. We are
+%% interested in measuring the execution speedup (if any) when the
+%% parallelization settings are activated. It is important to mention
+%% that we ignored the remaining \Fix{??} subjects identified in
+%% Section~\ref{sec:rqC-2} because it would be impractical to execute
+%% each subject on specific conditions to measure the impact of
+%% parallelization.
+
+To enforce sequential execution, we analyzed the \numProjectsPar{}
+subjects looking for the parallelism configuration inside the \pomf{} 
+of each module. To run the subjects sequentially, we manually modified 
+the Maven Surefire configuration in order to force the subjects to
+execute tests in sequential mode.
 
@@
 \longg{}-running.
-\Luis{rework this... $\rightarrow$}To reduce the number of build files
+To reduce the number of build files
 to inspect, we consider only \pomf{} files that contain
@@
 value \CodeIn{maven-surefire-plugin} and a \CodeIn{configuration}
-node. This mining step, however, is not sound as a matching project may not 
+node. Figure~\ref{fig:surefire-configuration} shows an example of
+configuration node mined. This mining step, however, is not sound as a matching project may not 
 indicate a project with a valid configuration for running tests in parallel.

### 2017-04-03 paper/evaluation.tex

--- 2017-04-03 paper/evaluation.tex
@@
       \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
-      \caption{\label{fig:medtcost}Medium group}
+      \caption{\label{fig:medtcost}Medium group.}
     \end{subfigure}\\
-    \vspace{2.5ex}
-    \begin{subfigure}{0.38\textwidth}
+    \vspace{2ex}
+    \begin{subfigure}{0.47\textwidth}
       \centering
-      \includegraphics[width=\textwidth]{plots/boxplots-testcases.pdf}
-      \caption{\label{fig:medtcost}Distribution of test cases per group}
+      \includegraphics[width=.75\textwidth]{plots/boxplots-testcases.pdf}
+        \caption{\label{fig:medtcost}Distribution of test cases.}
     \end{subfigure}\\
-    \vspace{3ex}
+    \vspace{2ex}
+    \begin{subfigure}{0.47\textwidth}
+      \centering
+      \includegraphics[width=.68\textwidth]{plots/scatter-testcost.pdf}
+        \caption{\label{fig:scattercost}\Fix{maybe the coordinates should be flipped}}
+     \end{subfigure}\\
+    \vspace{2ex}
     \begin{subfigure}{0.5\textwidth}

### 2017-04-03 paper/evaluation.tex
show RQ# with question

@@
 \begin{itemize}
-    \item \textbf{\RQA}
+    \item \numRQA{}. \textbf{\RQA}
 \end{itemize}
@@
     \vspace{2ex}
-    \begin{subfigure}{0.47\textwidth}
+    \begin{subfigure}{0.15\textwidth}
       \centering
-      \includegraphics[width=.75\textwidth]{plots/boxplots-testcases.pdf}
+      \includegraphics[width=.85\textwidth]{plots/boxplots-testcases.pdf}
         \caption{\label{fig:medtcost}Distribution of test cases.}
-    \end{subfigure}\\
-    \vspace{2ex}
-    \begin{subfigure}{0.47\textwidth}
+    \end{subfigure}~
+    \begin{subfigure}{0.3\textwidth}
       \centering
-      \includegraphics[width=.68\textwidth]{plots/scatter-testcost.pdf}
-        \caption{\label{fig:scattercost}\Fix{maybe the coordinates should be flipped}}
+      \includegraphics[width=.95\textwidth]{plots/scatter-testcost.pdf}
+        \caption{\label{fig:scattercost}\Fix{legend}}
      \end{subfigure}\\
@@
 we considered the \numNonParallel{} subjects that do not use any
-parallel mode from Section~\ref{sec:rqC-1} (\ie{}, \medg{} and
-\longg{}
-projects that does not run in parallel by default) and elaborated a
+parallel mode from Section~\ref{sec:rqC-1} and elaborated a
 quick survey to extent the comprehension about why developers do not
@@
 We first retrieve the last 20 commits from the project repository and
-got the developers e-mails. In total, we sent \emailsSent{} e-mails to
-different developers that recently contributed to the project.
+got the developers e-mails. In total, we sent an e-mail to
+\emailsSent{} developers that recently contributed to the
+\numNonParallel{} projects.
 There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
@@
 }
+
+From the valid replies, we confirmed that the projects we sent the
+e-mails takes more than 1 minute to run tests and \emailsSeq{}
+confirmed that those projects do not use parallel testing using Maven
+Surefire. The other projects that we do not confirm, need and extra
+parameter to execute in parallel mode \Luis{make sure that they are
+inside the static analysis sheets made before}.
+
+We noticed that \pctEmailsCI{} of developers use an continuous integration 
+server to run tests, \pctEmailsLocal{} run tests in the
+development machine, \pctEmailsDidNotSpecify{} did not specified their
+testing setup.
+We also noticed that one project has testing enabled without parallel 
+configuration, however, the maintainers never run the test. 
+Considering developers did not know about the existence of the
+parallelism configuration \pctEmailsDoNotKnow{} of the replies
+confirmed that. Three of the developers also confirmed that they use
+another method of parallelization with distributed build machines.
+
 \begin{center}
@@
 \end{center}
-
-\Luis{these values need macro $\rightarrow$}
-From the valid replies, we noticed that \Fix{55.2\%
-(16/\emailsTrueAnswers{})} of developers use an external continuous
-integration server to run tests, \Fix{27.6\% (8/\emailsTrueAnswers{})} run tests in the
-development machine, \Fix{13.8\% (4/\emailsTrueAnswers{})} did
-not specified the environment.
 

### 2017-04-03 paper/evaluation.tex
added missing fix
wip - rq3

@@
   \end{itemize}
-\item Tradeoff
+\item Tradeoffs
   \begin{itemize}
@@
 Prior to running this script, we inspected Maven execution logs from a
-sample inclduing a hundred projects.  The goal of this inspection step
+sample including a hundred projects.  The goal of this inspection step
 is to find tasks unrelated to testing (\eg, \emph{javadoc} generation
@@
 each group.  As it is to be expected, \longg{} and \medg{} projects do
-not occur as frequently as \shortg{} projects.  However, they do ocur
+not occur as frequently as \shortg{} projects.  However, they do occur
 in relatively high numbers.  Figure~\ref{fig:rq1-boxplot} shows cost
@@
 \begin{itemize}
-    \item \textbf{\RQB}
+    \item \numRQB. \textbf{\RQB}
 \end{itemize}
@@
 not uncommon; they account to nearly \percentMedLongRunning{} of the
-\numSubjs{} projects we analyzed.  However, parallelism by itself does
-not assure speedups on those projects.  One sensible factor that is
+\numSubjs{} projects we analyzed.  This reveals the importance to
+speedup test execution not only to huge projects as those from
+Google~\cite{google-tap,google-ci} and
+Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.  However, use of
+parallelism does not imply speedups.  One sensible factor that is
 important to the effectiveness of low-level parallelism is the
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
     \centering
@@
       \caption{\label{fig:medtcost}Medium group.}
-    \end{subfigure}\\
-    \vspace{2ex}
+    \end{subfigure}
+    %% \vspace{2ex}
+    %% \begin{subfigure}{0.5\textwidth}
+    %%   \centering
+    %%   \begin{tabular}{rrrr}
+    %%     \toprule
+    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
+    %%     \midrule    
+    %%     Long   &  7 & 15 & 12 \\
+    %%     Medium & 22 & 19 & 7 \\
+    %%     \bottomrule
+    %%   \end{tabular}
+    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
+    %% \end{subfigure}
+    \caption{\label{fig:time-distributions}Time distributions.}%
+\end{figure}
+
+\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
+time distribution of individual test cases per project.  We observed
+that the average median value of execution cost for a test was
+relatively small (dashed horizontal red lines), namely 0.31s for
+\medg{} projects and 0.23s for \longg{} projects.  The standard
+deviations associated with each distribution were relatively
+low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
+  specific ranges of $\sigma$ values.}  Note that high standard
+deviations may or may not be indicative of monopolization of execution
+by a small number of tests.  For example, the highest value of
+$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
+medium group.  This project contains only \Fix{65} tests, \Fix{62} of
+which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
+\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
+an example where test suite parallelization may not be very beneficial
+as \Fix{$>$99\%} of the execution cost is dominated by only \Fix{3\%}
+of the tests.  Without these two tests this project would have been
+classified as short-running.  A closer inspection in the data
+indicates that the project \CodeIn{uber\_chaperone} was an extreme
+case.  We did not find projects with similar characteristics of time
+monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
+classified as long-running and has the second highest value of
+$\sigma$.  For this project, however, cost is distributed more
+smoothly across \Fix{529} tests, of which \Fix{119 (23\%)} take more
+than \Fix{1s} to run.
+
+\begin{figure}[t]
+  \centering
   \begin{subfigure}{0.15\textwidth}
@@
     \includegraphics[width=.85\textwidth]{plots/boxplots-testcases.pdf}
-        \caption{\label{fig:medtcost}Distribution of test cases.}
-    \end{subfigure}~
+    \caption{\label{fig:size-testsuites}Size of test suites.}
+  \end{subfigure}
+  ~
   \begin{subfigure}{0.3\textwidth}
@@
     \includegraphics[width=.95\textwidth]{plots/scatter-testcost.pdf}
-        \caption{\label{fig:scattercost}\Fix{legend}}
-     \end{subfigure}\\
-    \vspace{2ex}
-    \begin{subfigure}{0.5\textwidth}
-      \centering
-      \begin{tabular}{rrrr}
-        \toprule
-        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
-        \midrule    
-        Long   &  7 & 15 & 12 \\
-        Medium & 22 & 19 & 7 \\
-        \bottomrule
-      \end{tabular}
-      \caption{\label{fig:sd}Standard deviantion of test cases}
-    \end{subfigure}%
-    \caption{\label{fig:time-distributions}Distribution of test case
-    execution cost per project.}%
+    \caption{\label{fig:scattercost}Size versus running time of
+      test suites.}
+  \end{subfigure}
+  \caption{\label{fig:time-versus-size}Relating size and time.}%
 \end{figure}
 
-\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
-time distribution of tests per project.  We observed that the average
-median value of execution cost for a test was relatively small (dashed
-horizontal red lines), namely 0.31s for \medg{} projects and
-0.23s for \longg{} projects.  Note that correlation between cost
-of test suites and cost of their individual tests is not to be
-expected.  The standard deviation ($\sigma$) associated with each
-distribution was relatively low.  Figure~\ref{fig:sd} shows the number
-of projects within specific ranges of $\sigma$ values.  We also
-observed that projects with very high standard deviations may or may
-not be indicative of monopolization of execution by a small number of
-tests.  For example, the highest value of $\sigma$ occurred in project
-\CodeIn{uber\_chaperone}, whose test suite was classified as
-medium-running.  This project contains only \Fix{65} tests, \Fix{62} of
-which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
-\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
-an example where test suite parallelization may not be very beneficial
-as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
-tests.  Without these two tests this project would have been
-classified as short-running.  A closer inspection in the data
-indicates that the project \CodeIn{uber\_chaperone} was an extreme case;
-we did not find projects with similar characteristics of time
-monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
-classified as long-running and has the second highest value of
-$\sigma$.  For this project, however, cost is distributed more
-smoothly across \Fix{529} tests, of which \Fix{119} take more than
-\Fix{1s} to run.
+Figure~\ref{fig:time-distributions} showed that the average median
+times were similar.  A closer inspection on results indicates that the
+difference in overall running times across projects in these groups is
+mainly justified by the number of test cases.
+Figure~\ref{fig:size-testsuites} shows the difference in the
+distribution of test suite sizes across groups.\Mar{$\leftarrow$ show
+  stats to indicate discrimination of two distributions} Furthermore,
+we also noted a strong positive correlation between running time and
+number of test on projects in the \longg{} group.  The positive
+correlation between these two variables was, however, weak in the
+\medg{} group, suggesting that saving time in this group with test
+suite parallelization may be more challenging as relatively fewer
+tests dominate overall execution time.  Figure~\ref{fig:scattercost}
+shows these results.
+
+%% This 
+%% indication that it is more beneficial to parallelize long projects as
+%% cost is spread across many
 
@@
 
-%% \Jbc{I shouldn't introduce parallelization arguments here but we have
-%% to address this at some point:
 %% Regression tests that are well distributed may benefit from
@@
 To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
-tested and confirmed parallelization activated by default, and
-compared their time cost with sequential execution. We are interested
-in measuring the execution speedup (if any) when the parallelization
-settings are activated.
+tested and confirmed parallelization activated by default (see
+Section~\ref{sec:rqC-1}), and compared their time cost with sequential
+execution. We are interested in measuring the execution speedup (if
+any) when the parallelization settings are activated.
 
@@
 %%
+
+%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
+%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
+%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
+%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
+%%  LocalWords:  outliers apache uber chaperone facebookarchive
+%%  LocalWords:  linkbench

### 2017-04-04 paper/evaluation.tex
adjusting rq5
pass on eval

@@
 
+%% \Jbc{I shouldn't introduce parallelization arguments here but we have
+%% to address this at some point:
 %% Regression tests that are well distributed may benefit from
@@
 To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
-tested and confirmed parallelization activated by default (see
-Section~\ref{sec:rqC-1}), and compared their time cost with sequential
-execution. We are interested in measuring the execution speedup (if
-any) when the parallelization settings are activated.
+tested and confirmed parallelization activated by default, and
+compared their time cost with sequential execution. We are interested
+in measuring the execution speedup (if any) when the parallelization
+settings are activated.
 

### 2017-04-04 paper/modes.tex
comments on sec2

@@
 a time per forked process.\Mar{$\leftarrow$Are you sure about this?
-  It seems silly.  Maybe, the rationale is to ``keep design simple''.}
+  It seems silly.  Maybe, the rationale is to ``keep design
+  simple''.}\Jbc{I'm sure. in addition to keep design simple, I feel
+  like this was initially conceived to run tests in isolation}
 To attenuate the non-trivial cost of spawning new processes and JVMs on
@@
 JVM.\Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
-  configuracao abaixo?}
+  configuracao abaixo?}\Jbc{added...}
 
@@
     morekeywords={parallel, threadCount, perCoreThreadCount,
-    forkCount, reuseFork},
+    forkCount, reuseForks},
     deletekeywords={true}
@@
         <forkCount>1C</forkCount>
+        <reuseForks>true</reuseForks>
         <parallel>methods</parallel>
@@
 (\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
-parameter) within each forked JVM.
+parameter) within each forked JVM. After the execution of a test
+class, Maven reuses the forked JVM for the next execution
+(\CodeIn{reuseFork} parameter).
 

### 2017-04-04 paper/evaluation.tex
adjusted macro - rq3

--- 2017-04-03 paper/evaluation.tex
@@
 actual test execution.
-
 According to Maven's documentation~\cite{maven-surefire-plugin}, any
@@
 them.  \Jbc{Missing: explain how we mapped the configurations to
-parallel level.} Figure~\ref{fig:freqmodes-dynamic} summarizes our
-findings.
+parallel level.}
+
+From the \numMedLong{} projects, we identified \numProjectsPar{}
+projects with parallel execution enabled by default.
+Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.
 

### 2017-04-04 paper/evaluation.tex
complemented rq3

@@
 
-Initially, we configured Maven to output all configuration variables.
-The rationale is that, for each project's module, we can capture
-relevant configurations and classify their parallelization level (see
-Section \ref{sec:modes}) based on their values. To avoid waiting all
-tests to terminate, we just run the bootstrap phase and we skip the
-actual test execution.
-According to Maven's documentation~\cite{maven-surefire-plugin}, any
-parallelization setting depends either on (1) \CodeIn{parallel} to
-define the parallelism level within a JVM followed by
-\CodeIn{threadCount} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
-in older versions) to define the number of forked JVMs. For each test
-execution, we look for theses parameters and their values to classify
-them.  \Jbc{Missing: explain how we mapped the configurations to
-parallel level.}
+We configured Maven to output all configuration variables.  The
+rationale is that, for each project's module, we can capture relevant
+configurations and classify their parallelization level (see Section
+\ref{sec:modes}) based on their values. To avoid waiting all tests to
+terminate, we just run the bootstrap phase and we skip the actual test
+execution.  According to Maven's
+documentation~\cite{maven-surefire-plugin}, any parallelization
+setting depends either on (1) \CodeIn{parallel} to define the
+parallelism mode within a JVM followed by \CodeIn{threadCount} or (2)
+\CodeIn{forkCount} (or \CodeIn{forkMode} in older versions) to define
+the number of forked JVMs. For each test execution, we look for theses
+parameters and their values to map to one of the possible
+parallelization modes.  For instance, if a given project contains a
+module with the setting \CodeIn{<forkCount>1C</forkCount>}, the
+possible classifications are \ForkSeq{} or \ForkParMeth{} depending on
+the presence and the value of the parameter \CodeIn{parallel}.
+Large projects may contain several test suites distributed on
+different Maven modules with different configurations. In this case,
+we collect the Maven output from each module and we consider only the
+distinct configurations. For instance, if a project contains two
+modules with the same parallelism mode, we count only one occurrence
+to not inflate our final results. Finally, some projects use a value
+informed as an argument instead of adding the value statically in the
+configuration value. In this case, we consider all possible values for
+the parameterized parameter.  From the \numMedLong{} projects, we
+identified \numProjectsPar{} projects with parallel execution enabled
+by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
+findings.
 
-From the \numMedLong{} projects, we identified \numProjectsPar{}
-projects with parallel execution enabled by default.
-Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.
-
-\begin{figure}[h!]
+%\begin{figure}[h!]
+%    \centering
+%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
+%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
+%    caption}Distribution of parallel modes identified dynamically in a
+%    subset of \numProjectsPar{} projects.  A project may have support
+%    to more than one parallel mode. Also, a project may run only a
+%    subset tests in parallel by default.}
+%\end{figure}
+\begin{figure}[ht!]
     \centering
-    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
-    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
-    caption}Distribution of parallel modes identified dynamically in a
-    subset of \numProjectsPar{} projects.  A project may have support
-    to more than one parallel mode. Also, a project may run only a
-    subset tests in parallel by default.}
+    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}llll}
+        \toprule
+        Group & Subject & - & -\\%
+        \midrule%
+        long   & JenkinsCI gerrit-trigger-plugin & 1 & \ForkSeq{}\\%
+        medium & Jcabi & 1 & \ParClassParMeth{}\\%
+        medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
+        medium & Apache logging-log4J2 & 25 & \ForkSeq{}\\%
+        medium & Javaslang & 3 & \ParClassParMeth{}\\%
+        \bottomrule%
+    \end{tabular*}
+    \caption{\Fix{TODO}}
+    \label{tab:freqmodes-dynamic}
 \end{figure}

### 2017-04-04 paper/evaluation.tex
done with RQ4.1

@@
 groups). We are interested to know if developers consider low-level
-parallelism features to amortize the execution cost. More precisely,
-we investigate if there are projects with parallelism configuration
-enabled by default or if developers configure this feature to run only
-on specific scenarios (\eg, dedicated server).  We describe our
-approach as follows:
+parallelism modes to amortize the execution cost (see
+Section~\ref{sec:modes}). More precisely, we investigate if there are
+projects with parallelization modes enabled by default or if
+developers configure this feature to run only on specific scenarios
+(\eg, dedicated server).  We describe our approach as follows:
 
@@
 
-We configured Maven to output all configuration variables.  The
-rationale is that, for each project's module, we can capture relevant
-configurations and classify their parallelization level (see Section
-\ref{sec:modes}) based on their values. To avoid waiting all tests to
-terminate, we just run the bootstrap phase and we skip the actual test
-execution.  According to Maven's
-documentation~\cite{maven-surefire-plugin}, any parallelization
-setting depends either on (1) \CodeIn{parallel} to define the
-parallelism mode within a JVM followed by \CodeIn{threadCount} or (2)
-\CodeIn{forkCount} (or \CodeIn{forkMode} in older versions) to define
-the number of forked JVMs. For each test execution, we look for theses
-parameters and their values to map to one of the possible
-parallelization modes.  For instance, if a given project contains a
-module with the setting \CodeIn{<forkCount>1C</forkCount>}, the
-possible classifications are \ForkSeq{} or \ForkParMeth{} depending on
-the presence and the value of the parameter \CodeIn{parallel}.
+We re-executed the tests from the \numMedLong{} projects and we
+configured Maven to output all runtime parameters and their current
+values. We run only the test bootstrap step as the actual test
+execution is unnecessary to output the runtime parameters.  From the
+Maven output, we capture the parameters related to parallelism
+configurations and mapped these configurations to a parallelization
+mode.
+According to Maven's documentation~\cite{maven-surefire-plugin}, any
+parallelism configuration depends either on (1) the parameter
+\CodeIn{parallel} to define the parallelism mode within a JVM followed
+by the parameter \CodeIn{threadCount} or (2) the parameter
+\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
+in old versions of Maven Surefire} to define the number of forked
+JVMs. For each execution, we capture theses parameters and their
+values to map to one of the possible parallelization modes.  For
+instance, if a given project contains a module with the parameter
+\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
+\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
+of the parameter \CodeIn{parallel} (\ie, the presence of
+\CodeIn{<parallel>methods</parallel>} results in the parallel mode
+\ForkParMeth{}).
 Large projects may contain several test suites distributed on
@@
 modules with the same parallelism mode, we count only one occurrence
-to not inflate our final results. Finally, some projects use a value
-informed as an argument instead of adding the value statically in the
-configuration value. In this case, we consider all possible values for
-the parameterized parameter.  From the \numMedLong{} projects, we
+to not inflate our results.  From the \numMedLong{} projects, we
 identified \numProjectsPar{} projects with parallel execution enabled
@@
     \centering
-    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}llll}
+    \resizebox{.48\textwidth}{!}{%
+    \begin{tabular}{llcl}
         \toprule
-        Group & Subject & - & -\\%
+        Group & Subject & \# of modules & Mode\\%
         \midrule%
-        long   & JenkinsCI gerrit-trigger-plugin & 1 & \ForkSeq{}\\%
-        medium & Jcabi & 1 & \ParClassParMeth{}\\%
+        long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
+        medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
         medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
-        medium & Apache logging-log4J2 & 25 & \ForkSeq{}\\%
+        medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
         medium & Javaslang & 3 & \ParClassParMeth{}\\%
         \bottomrule%
-    \end{tabular*}
-    \caption{\Fix{TODO}}
+    \end{tabular}}
+    \caption{Subjects with test execution in parallel enabled by
+    default}
     \label{tab:freqmodes-dynamic}
 \end{figure}
-
-\Fix{Elaborate findings....}
 
@@
 indicate a project with a valid configuration for running tests in parallel.
+
+Finally, some projects use a value informed as an argument in the
+command line instead of declaring a static value in the configuration
+file (\ie, \pomf{}). In this case, we consider all valid values for
+the parameter.
 

### 2017-04-04 paper/evaluation.tex
removed unnecessary content
adjusting rq5

@@
 values. We run only the test bootstrap step as the actual test
-execution is unnecessary to output the runtime parameters.  From the
-Maven output, we capture the parameters related to parallelism
-configurations and mapped these configurations to a parallelization
-mode.
+execution is unnecessary to output the runtime parameters.
 According to Maven's documentation~\cite{maven-surefire-plugin}, any
@@
 \numNonParallel{} projects.
-There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
-those were answering the survey.
+There were \emailsAnswered{} replies from \emailsProjectsAnswered{}, 
+and \emailsFalseAnswers{} was not able to explain how the testing works.
 
@@
 
-From the valid replies, we confirmed that the projects we sent the
-e-mails takes more than 1 minute to run tests and \emailsSeq{}
-confirmed that those projects do not use parallel testing using Maven
-Surefire. The other projects that we do not confirm, need and extra
-parameter to execute in parallel mode \Luis{make sure that they are
-inside the static analysis sheets made before}.
+From the valid replies, we confirmed that the projects takes more than
+\Fix{1m} to run tests and \emailsSeq{} confirmed that those projects do not use 
+parallel testing using Maven Surefire. The other projects that we do not 
+confirm, need and extra parameter to execute in parallel mode \Luis{make 
+sure that they are inside the static analysis sheets made before}.
 
@@
 development machine, \pctEmailsDidNotSpecify{} did not specified their
-testing setup.
-We also noticed that one project has testing enabled without parallel 
-configuration, however, the maintainers never run the test. 
+testing setup. We also observed that one project has testing enabled 
+without parallelization. However the maintainers do not execute the tests.
 Considering developers did not know about the existence of the
@@
 confirmed that. Three of the developers also confirmed that they use
-another method of parallelization with distributed build machines.
+another method of parallelization with a distributed build machines.
 

### 2017-04-04 paper/evaluation.tex
pass on text

@@
 modules with the same parallelism mode, we count only one occurrence
-to not inflate our results.  From the \numMedLong{} projects, we
-identified \numProjectsPar{} projects with parallel execution enabled
-by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
-findings.
-
+to not inflate our results.
+From the \numMedLong{} projects, we identified \numProjectsPar{}
+projects with the parallel execution modes \ForkSeq{} and
+\ParClassParMeth{} enabled by default.
+Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
+``Group'' indicates the test cost group (see
+Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
+name of the project, the column ``\# of modules'' indicates the number
+of modules with tests in the default execution, and the column
+``Mode'' indicates the corresponding parallelization mode.
 %\begin{figure}[h!]
@@
         \midrule%
-        long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
-        medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
-        medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
-        medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
-        medium & Javaslang & 3 & \ParClassParMeth{}\\%
+        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
+        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
+        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
+        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
+        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
         \bottomrule%
     \end{tabular}}
-    \caption{Subjects with test execution in parallel enabled by
-    default}
+    \caption{Subjects with parallel test execution enabled by
+    default.}
     \label{tab:freqmodes-dynamic}
@@
 
-\subsubsection{Support of parallelization configuration in build files}
+\subsubsection{Presence of parallelism configurations in build files}
 \label{sec:rqC-2}
 
-To extend our initial investigation, we mined several \pomf{} files
-from all \numMedLong{} projects classified as the \medg{} and
-\longg{}-running.
-To reduce the number of build files
-to inspect, we consider only \pomf{} files that contain
-\CodeIn{plugin} tags with a child tag \CodeIn{artifactId} with the
-value \CodeIn{maven-surefire-plugin} and a \CodeIn{configuration}
-node. Figure~\ref{fig:surefire-configuration} shows an example of
-configuration node mined. This mining step, however, is not sound as a matching project may not 
-indicate a project with a valid configuration for running tests in parallel.
-
-Finally, some projects use a value informed as an argument in the
-command line instead of declaring a static value in the configuration
-file (\ie, \pomf{}). In this case, we consider all valid values for
+To extend our previous investigation, we evaluated the presence of
+parallelism configuration in several build files (\ie, \pomf{} files)
+from the same sample set of \numMedLong{} projects. The rationale is
+that some projects may have support to parallel execution but it is
+deactivated by default (\ie, require additional arguments before the
+test execution). For instance, on Maven, it is possible to create
+multiple configurations in the same build file and activate any of
+them dynamically.  To reduce the space of \Fix{x} build files, we
+considered a subset of \Fix{y} build files with the following
+criteria: the given \pomf{} file has \CodeIn{maven-surefire-plugin}
+plugin declaration and it has an explicit \CodeIn{configuration}
+declaration. We automatically parsed these \Fix{y} files and we used
+the same approach to classify the parallelization mode from the parsed
+configurations as in our previous analysis. In an initial analysis, we
+noticed that some projects do not declare a static value in some
+parameters, instead, these projects inform the actual value in the
+command line. To handle this case, we computed all valid values for
 the parameter.
@@
 
-Figure~\ref{tab:inspection-table} summarizes our results. The first
+Figure~\ref{tab:inspection-table} summarizes our results. \Fix{The first
 column indicates the group of projects according to their time cost.
@@
 The last column indicates the ratio of projects with parallelization settings.
+From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files.
+The \numPomMatched{} configurations are distributed across
+\numProjectsPar{} projects from our sample.}
 
-From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files.
-The \numPomMatched{} configurations are distributed across \numProjectsPar{} projects from our sample.
-% 
 % \emph{From these results we found that $\sim$51\% of medium and
@@
 % question}\Mar{explain this is over(under)-estimated...}
-
 \begin{figure}[ht!]
     \centering
-    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
+    \resizebox{.48\textwidth}{!}{%
+    \begin{tabular}{llcl}
         \toprule
-        \multirow{2}{*}{Group} %1st row, 1st cell
-            & \multirow{2}{*}{\# \pomf{}}
-	    & \# \pomf{} matched\\
-        % 2nd row - empty cell
-            & % empty cell
-            & / total\\%
+        Group & Subject & \# of modules & Mode\\%
         \midrule%
-	Long   & \numPomLong{} & 4 / \numLong{}\\%
-	Medium & \numPomMed{} & 6 / \numMed{}\\%
-        \midrule%
-        Total % last row, first cell
-            & \pomMedLong{}
-            & \numProjectsPar{} / \numMedLong{}\\%
+        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
+        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
+        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
+        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
+        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
         \bottomrule%
-    \end{tabular*}
-    \caption{Presence of parallelization settings in build files: the
-    first column indicates the group of projects according to their
-    time cost; the second column is the subset of files with parallelization
-    keywords; the last column indicates the ratio of projects with
-    parallelism support.}
+    \end{tabular}}
+    \caption{\Fix{This is a COPY from the previous table!}}
     \label{tab:inspection-table}
@@
 
-\Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
-identified above, we investigated further the \numPomMatched{}
-build files with parallel settings.  We analyzed the support and
-distribution of parallel modes from this subset of projects. To
-calculate the distribution of parallel modes, we considered only the
-presence of the mode in at least one of the project settings.  Recall
-that a build file may contain more than one parallel setting and a
-project may contain several sub-modules with build files.  In case the
-value of a parallel option is resolved dynamically (\eg, via
-command-line argument or system variable) we compute all modes related
-to the option. For instance, depending on the value, the
-\CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
-\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
-(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
-Figure~\ref{fig:freqmodes-static} summarizes our findings.
-\Fix{Missing conclusion: Fork the most used configuration}
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
-	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
-	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
-    identified statically in a subset of \numProjectsPar{} projects.
-    A project may have support to more than one parallel mode.}
-\end{figure}
+%% \begin{figure}[ht!]
+%%     \centering
+%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
+%%         \toprule
+%%         \multirow{2}{*}{Group} %1st row, 1st cell
+%%             & \multirow{2}{*}{\# \pomf{}}
+%% 	    & \# \pomf{} matched\\
+%%         % 2nd row - empty cell
+%%             & % empty cell
+%%             & / total\\%
+%%         \midrule%
+%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
+%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
+%%         \midrule%
+%%         Total % last row, first cell
+%%             & \pomMedLong{}
+%%             & \numProjectsPar{} / \numMedLong{}\\%
+%%         \bottomrule%
+%%     \end{tabular*}
+%%     \caption{Presence of parallelization settings in build files: the
+%%     first column indicates the group of projects according to their
+%%     time cost; the second column is the subset of files with parallelization
+%%     keywords; the last column indicates the ratio of projects with
+%%     parallelism support.}
+%%     \label{tab:inspection-table} 
+%% \end{figure}
+%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
+%% identified above, we investigated further the \numPomMatched{}
+%% build files with parallel settings.  We analyzed the support and
+%% distribution of parallel modes from this subset of projects. To
+%% calculate the distribution of parallel modes, we considered only the
+%% presence of the mode in at least one of the project settings.  Recall
+%% that a build file may contain more than one parallel setting and a
+%% project may contain several sub-modules with build files.  In case the
+%% value of a parallel option is resolved dynamically (\eg, via
+%% command-line argument or system variable) we compute all modes related
+%% to the option. For instance, depending on the value, the
+%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
+%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
+%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
+%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
+%% \Fix{Missing conclusion: Fork the most used configuration}
+%% \begin{figure}[h!]
+%%     \centering
+%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
+%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
+%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
+%%     identified statically in a subset of \numProjectsPar{} projects.
+%%     A project may have support to more than one parallel mode.}
+%% \end{figure}
 
@@
       \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
-      that parallelism features are underused by defailt given that only
-	  \percentParallel{}
-      of projects supports parallel execution of test suites without
-	  any extra parameter.}
+      that parallelism features are underused by default given that
+      only \percentParallel{} of projects  (5 out of \numMedLong)
+      supports parallel execution of test suites without any extra
+      parameter.}
   \end{minipage}

### 2017-04-04 paper/evaluation.tex
added placeholders from rq3

@@
 tested and confirmed parallelization activated by default (see
-Section~\ref{sec:rqC-1}), and compared their time cost with sequential
-execution. We are interested in measuring the execution speedup (if
-any) when the parallelization settings are activated.
-
-%% To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
-%% parallelization settings enabled by default identified in \numRQC{}
-%% and compared their time cost with sequential execution. We are
-%% interested in measuring the execution speedup (if any) when the
-%% parallelization settings are activated. It is important to mention
-%% that we ignored the remaining \Fix{??} subjects identified in
-%% Section~\ref{sec:rqC-2} because it would be impractical to execute
-%% each subject on specific conditions to measure the impact of
-%% parallelization.
-
-To enforce sequential execution, we analyzed the \numProjectsPar{}
-subjects looking for the parallelism configuration inside the \pomf{} 
-of each module. To run the subjects sequentially, we manually modified 
-the Maven Surefire configuration in order to force the subjects to
-execute tests in sequential mode.
+Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
+parallel execution, we compared the elapsed time in the default
+execution (parallelization enabled) and re-executed the tests
+sequentially.
+To enforce sequential execution,
+\Fix{elaborar metodologia}
+\Fix{dizer que verificamos que a execucao eh consistente e o
+outcome eh igual ao da execucao padrao}.
 

### 2017-04-05 paper/evaluation.tex
added missing table

@@
 execution (parallelization enabled) and re-executed the tests
-sequentially.
-To enforce sequential execution,
-\Fix{elaborar metodologia}
-\Fix{dizer que verificamos que a execucao eh consistente e o
-outcome eh igual ao da execucao padrao}.
+sequentially.  To enforce sequential execution, we modified the
+existing configurations. Also, we verified that, for each project,
+both executions (\ie, default and sequential) are consistent and
+produce the same outcome. To compute the speedup, we divide the
+sequential time by the default execution. For instance, for a project
+that runs in $10m$ sequentially and runs in $5m$ in the default execution,
+the speedup is two.
+
+\begin{figure}[ht!]
+\centering
+\resizebox{.48\textwidth}{!}{%
+\begin{tabular}{lllll}
+\toprule
+Group & Subject & T$_{\text{p}}$ & T$_{\text{s}}$ & Speedup\\%
+\midrule%
+Long   & JenkinsCI Gerrit Trigger Plugin & \Fix{?} & \Fix{?} & \Fix{?}\\%
+Medium & Apache Logging Log4J2           & \Fix{?} & \Fix{?} & \Fix{?}\\%
+Medium & Jankotek MapDB                  & \Fix{?} & \Fix{?} & \Fix{?}\\%
+Medium & Javaslang                       & \Fix{?} & \Fix{?} & \Fix{?}\\%
+Medium & Jcabi Github                    & \Fix{?} & \Fix{?} & \Fix{?}\\%
+\bottomrule%
+\end{tabular}}
+\caption{\Fix{Comparacao de tempo sequencial e paralelo}}
+\label{tab:speedup}
+\end{figure}
+
+Figure~\ref{tab:speedup} summarizes our findings.
+\Fix{falar sobre o resultado geral dos speedups - elaborar menor e
+maior speedup}
 
@@
 
-Figure~\ref{tab:inspection-table} summarizes our results. \Fix{The first
-column indicates the group of projects according to their time cost.
-The second column indicates the number of build files per group.
-The last column indicates the ratio of projects with parallelization settings.
-From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files.
-The \numPomMatched{} configurations are distributed across
-\numProjectsPar{} projects from our sample.}
+Figure~\ref{tab:inspection-table} summarizes our results.
+\Fix{The first column indicates the group of projects according to
+their time cost.  The second column indicates the number of build
+files per group.  The last column indicates the ratio of projects with
+parallelization settings.  From the \numMedLong{} subjects, we found
+\pomMedLong{} \pomf{} files.  The \numPomMatched{} configurations are
+distributed across \numProjectsPar{} projects from our sample.}
 
@@
 \end{figure}
-
 %% \begin{figure}[ht!]
@@
       only \percentParallel{} of projects  (5 out of \numMedLong)
-      supports parallel execution of test suites without any extra
-      parameter.}
+      supports parallel execution of test suites by default and
+      \Fix{?\%} (\Fix{y} out of \numMedLong{}) require additional
+      parameters to enable these features.}
   \end{minipage}

### 2017-04-05 paper/modes.tex
commenting comments

@@
 
-Forking OS processes to run test jobs is a common feature of build
-systems as to obtain parallelism at the machine space (see
+Forking OS processes to run test jobs is a popular mechanism of build
+systems to obtain parallelism at the machine space (see
 Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
@@
 Section~\ref{sec:frameworks}) as Maven only accepts one test class at
-a time per forked process.\Mar{$\leftarrow$Are you sure about this?
-  It seems silly.  Maybe, the rationale is to ``keep design
-  simple''.}\Jbc{I'm sure. in addition to keep design simple, I feel
-  like this was initially conceived to run tests in isolation}
-To attenuate the non-trivial cost of spawning new processes and JVMs on
-every test class, Maven offers an option to reuse the
-JVM.\Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
-  configuracao abaixo?}\Jbc{added...}
+a time per forked process.  To attenuate the non-trivial cost of
+spawning new processes and JVMs on every test class, Maven offers an
+option to reuse the JVM.
+
+%% \Mar{$\leftarrow$Are you sure about this?
+%%   It seems silly.  Maybe, the rationale is to ``keep design
+%%   simple''.}\Jbc{I'm sure. in addition to keep design simple, I feel
+%%   like this was initially conceived to run tests in isolation}
+
+%% \Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
+%%   configuracao abaixo?}\Jbc{added...}
 

### 2017-04-05 paper/modes.tex
final pass on modes.tex

@@
 class~\cite{luo-etal-fse2014}.  Considering data race avoidance,
-intuitively, configuration \SeqClassParMeth{} is preferable over
-\ParClassSeqMeth{} when it is clear that test methods in a class do
-not manipulate shared state, which can be challenging to
-determine~\cite{bell-etal-esecfse2015}, whereas \ParClassSeqMeth{} is
-preferable over \SeqClassParMeth{} when it is clear that several test
-methods in one class perform operations involving shared data.
-Configuration \ParClassParMeth{} is more likely to manifest data races
-during execution as it does not restrict scheduling orderings. Note
-that speedups depend on several factors, including the test suite size
-and distribution of test methods per class.
+configuration \SeqClassParMeth{} is preferable over \ParClassSeqMeth{}
+when it is clear that test methods in a class do not manipulate shared
+state, which can be challenging to
+determine~\cite{bell-etal-esecfse2015}.  Similarly, \ParClassSeqMeth{}
+is preferable over \SeqClassParMeth{} when it is clear that several
+test methods in a class perform operations involving shared data.
+Configuration \ParClassParMeth{} does not restrict scheduling
+orderings.  Consequently, it is more likely to manifest data races
+during execution. Note that speedups depend on several factors,
+including the test suite size and distribution of test methods per
+class.
 
@@
 systems to obtain parallelism at the machine space (see
-Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
-Ant), this amounts to spawning one JVM instance (per process) per CPU,
-on a machine with potentially many virtual CPUs, and aggregating
-corresponding results when jobs finish.  Note that forking can only be
-combined with configuration \SeqClassParMeth{} (see
-Section~\ref{sec:frameworks}) as Maven only accepts one test class at
-a time per forked process.  To attenuate the non-trivial cost of
-spawning new processes and JVMs on every test class, Maven offers an
-option to reuse the JVM.
+Figure~\ref{fig:levels}).  For Java-based build systems, such as Maven
+and Ant, this amounts to spawning one JVM instance to handle a test
+job and aggregating corresponding results when test jobs finish.  Note
+that forking can only be combined with configuration
+\SeqClassParMeth{} (see Section~\ref{sec:frameworks}) as Maven only
+accepts one test class at a time per forked process.  To attenuate the
+non-trivial cost of spawning new JVM processes on every test class,
+Maven offers an option to reuse the JVM.
 
@@
 options to run tests using the parallel execution mode \ForkParMeth{}.
-With this configuration, Maven~---~through its test plugin
-Surefire~\cite{maven-surefire-plugin}~---~forks one JVM per core
-(\CodeIn{forkCount} parameter) and uses five threads
-(\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
-parameter) within each forked JVM. After the execution of a test
-class, Maven reuses the forked JVM for the next execution
-(\CodeIn{reuseFork} parameter).
+Maven implements this feature through its JUnit test plugin
+Surefire~\cite{maven-surefire-plugin}.  With this configuration, Maven
+forks one JVM per core (\CodeIn{forkCount} parameter) and uses five
+threads (\CodeIn{threadCount} parameter) to run test methods
+(\CodeIn{parallel} parameter) within each forked JVM.  Maven reuses
+created JVMs on subsequent forks when execution of a test class
+terminates (\CodeIn{reuseFork} parameter).
 
@@
 %%  LocalWords:  perCoreThreadCount reuseFork deletekeywords groupId
-%%  LocalWords:  artifactId
+%%  LocalWords:  artifactId reuseForks

### 2017-04-05 paper/evaluation.tex
another pass on RQ1

@@
 update was on or after January 1st, 2016, and (4) the \emph{readme}
-file contains the string \emph{mvn}\footnote{As of now, \github{}'s
-  search API can only reflect contents from README file (not other
-  code elements).}.  We focused on Java for its popularity.  Although
-there is no clearcut limit on number of \github{}
-stars~\cite{github-stars} to define an interesting project, we
+file contains the string \emph{mvn}.  We focused on Java for its
+popularity.  Although there is no clearcut limit on the number of
+\github{} stars~\cite{github-stars} to define relevant projects, we
 observed that 100 was enough to eliminate trivial subjects. The third
-criteria is a constraint to skip projects without recent activity. The
-fourth criteria is an approximation to find Maven projects. The
-rationale is that if the string \emph{mvn} exists in the \emph{readme}
-file, it may represent a Maven call (\eg, to compile or to test the
-project). We used Maven as a reference due to its popularity on Java
-projects and to assist one of our experiments. A Maven project may
-contain several sub-modules with multiple \pomf{} files but we only
-considered projects with a \pomf{} file located in the root directory.
-Figure~\ref{fig:subject-query} illustrates the query to the \github{}
-API as an HTTP request.
+criteria serves to skip projects without recent activity. The fourth
+criteria is an approximation to find Maven projects.\Comment{ The
+  rationale is that if the string \emph{mvn} exists in the
+  \emph{readme} file, it may represent a Maven call (\eg, to compile
+  or to test the project).} We focused on Maven for its popularity on
+Java projects.  Important to highlight that, as of now, the
+\github{}'s search API can only reflect contents from README file (not
+other code elements); it does not provide a feature to search for
+projects containing certain files in the dir structure (\eg{},
+\emph{pom.xml}).  Figure~\ref{fig:subject-query} illustrates the query
+to the \github{} API as an HTTP request.  After obtaining a list of
+potential projects, we filtered those containing a \pomf{} file in the
+root directory.  A Maven project may contain several sub-modules with
+multiple \pomf{} files.  We based our methodology to select
+experimental subjects on other recent studies in testing and
+debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.
 
@@
 projects were not Maven or did not have a \pomf{} in the root
-directory and \SubjectsGithubNotTestable{} projects were untestable
+directory, \SubjectsGithubNotTestable{} projects were untestable
 (because of missing dependencies or incompatible testing environment,
-for example). To ensure that our sample set was stable, we retested
-the remaining subjects to eliminate projects with flaky tests (total of
-\SubjectsGithubFlaky{} subjects). Our final set consists of
-\numSubjs{} testable subjects.
+for example), and \SubjectsGithubFlaky{} projects were ``flaky''.  We
+executed each project's test suite for three times to identify
+projects containing flaky tests that could introduce noise in our
+experiments.  Our final set of subjects consists of \numSubjs{}
+projects.
 
@@
 subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
-Python 3.4, Bash, R and Ruby 2.3 to process the data and generate plots.  All
-source artifacts are publicly available for replication (on
-request)\Comment{ at \Fix{create gh-pages}}.  This includes supporting
-scripts (\eg, the script that test subjects and generates raw analysis
-data) and the full list of projects. \Comment{, and a
-  \emph{Vagrantfile} to emulate our hardware and all software
+Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to process the
+data and generate plots.  All source artifacts are publicly available
+for replication (on request)\Comment{ at \Fix{create gh-pages}}.  This
+includes supporting scripts (\eg, the script that test subjects and
+generates raw analysis data) and the full list of projects. \Comment{,
+  and a \emph{Vagrantfile} to emulate our hardware and all software
   dependencies.}
@@
 Figure~\ref{fig:subjects}.  Figure~\ref{fig:mvn-execution} illustrates
-the script we used to measure time.  The main loop (lines 5-11)
-iterates over the list of subjects and invokes Maven multiple
-times\Comment{ to isolate cost of running tests} (lines 7-9).  We
-first compiled the source and test files (line 7), made all
-dependencies available locally (line 8), and then we ran the tests in
-offline mode to skip the package update task (line 9). After
-execution, we used a regular expression on the output log to extract
-the elapsed time (line 10).
+the script we used to measure time.
 
-Prior to running this script, we inspected Maven execution logs from a
-sample including a hundred projects.  The goal of this inspection step
-is to find tasks unrelated to testing (\eg, \emph{javadoc} generation
-and static analyses) that could interfere in our measurements.  The
-tasks we found were ignored from execution (lines 1-3).  Furthermore,
-to avoid noise from operating system events, we configured our
-workstation to run only essential services.  The machine was dedicated
-to our experiments and we accessed it via SSH. In addition, we
-configured the \CodeIn{isolcpus} option from the Linux Kernel
-\cite{linux-kernel} to isolate six virtual CPUs to execute our
-experiment, leaving the remaining CPUs to run OS
-processes~\cite{isolcpus-use}.  The rationale for this decision is to
-prevent context-switching between user processes (running the
+We tooke the following actions to isolate our environment from
+measurement noise.  First, we observed that some test tasks called
+test-unrelated tasks (\eg, \emph{javadoc} generation and static
+analyses) that could interfere in our time measurements.  To address
+that potential issue, we inspected Maven execution logs from a sample
+including a hundred projects prior to running the script from
+Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
+execution (lines 1-3).  Furthermore, to avoid noise from operating
+system events, we configured our workstation to run only essential
+services.  The machine was dedicated to our experiments and we
+accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
+option from the Linux Kernel \cite{linux-kernel} to isolate six
+virtual CPUs to run our experiments, leaving the remaining CPUs to run
+OS processes~\cite{isolcpus-use}.  The rationale for this decision is
+to prevent context-switching between user processes (running the
 experiment) and OS-related processes.  Finally, to make sure our
-measurements were fair, we compared the sequential execution of tests
-using Maven with JUnit's default \CodeIn{JUnitCore} runner, invoked
-from the command line.  We observed that results were very similar.
+measurements were fair, we compared timings corresponding to the
+sequential execution of tests using Maven with that obtained with
+JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
+line.  Results were very close.
+
+The main loop (lines 5-11) of the script in
+Figure~\ref{fig:mvn-execution} iterates over the list of subjects and
+invokes Maven multiple times\Comment{ to isolate cost of running
+  tests} (lines 7-9).  It first compiles the source and test files
+(line 7), make all dependencies available locally (line 8), and then
+runs the tests in offline mode as to skip the package update task,
+enabled by default (line 9). After execution, we used a regular
+expression on the output log to extract elapsed time (line 10).
 
@@
   group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
-each group.  As it is to be expected, \longg{} and \medg{} projects do
-not occur as frequently as \shortg{} projects.  However, they do occur
-in relatively high numbers.  Figure~\ref{fig:rq1-boxplot} shows cost
-distribution of test suites in each group as boxplots.  The
+each group.  As expected, \longg{} and \medg{} projects do not occur
+as frequently as \shortg{} projects.  However, they do occur in
+relatively high numbers.
+
+Figure~\ref{fig:rq1-boxplot} shows cost distribution of test suites in
+each group as boxplots.  Note that the y-ranges are different.  The
 distribution associated with the \shortg{} group is the most
 unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
-  group}.  The test suites in this group run in 15 or less seconds for
+  group}.  The test suites in this group ran in 15 or less seconds for
 over 75\% of the cases.  Such scenarios constitute the majority of the
@@
 project \CodeIn{apache.maven-surefire} runs all unit tests in a few
-seconds in our environment.  According to our criteria, this project
-would be classified as \shortg{} but we noticed that only smoke test
-run by default.  The more expensive integration and system tests are
-only accessible via custom parameters.  When running the test suite
-with integration tests, the testing time goes to nearly 30 minutes.
-For simplicity, we considered only the tests executed by default.
+seconds.  According to our criteria, this project is to be classified
+as \shortg{} but a closer look reveals that only smoke tests are run
+by default in this project.  Time-consuming integration and system
+tests are only accessible via custom parameters, which we do not
+handle in our experimental setup.  We enabled such parameters for this
+specific project and observed that testing time goes to nearly 30
+minutes.  For simplicity, we considered only the tests executed by
+default.
 

### 2017-04-05 paper/evaluation.tex
pass on RQ2

@@
 
-We tooke the following actions to isolate our environment from
+We took the following actions to isolate our environment from
 measurement noise.  First, we observed that some test tasks called
@@
 Section~\ref{sec:rqA} showed that medium and long-running projects are
-not uncommon; they account to nearly \percentMedLongRunning{} of the
-\numSubjs{} projects we analyzed.  This reveals the importance to
-speedup test execution not only to huge projects as those from
-Google~\cite{google-tap,google-ci} and
-Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.  However, use of
-parallelism does not imply speedups.  One sensible factor that is
-important to the effectiveness of low-level parallelism is the
-distribution of test costs in the test suite.  In the limit, if cost
-is dominated by a single test, it is unlikely that parallelization
-will be beneficial as a test method is the smallest working unit in
-test frameworks (see Section~\ref{sec:frameworks}).
+not uncommon, accounting to nearly \percentMedLongRunning{} of the
+\numSubjs{} projects we analyzed.  It is therefore important to
+speedup regressing testing in open-source projects.\Comment{not only
+  to huge projects as those from Google~\cite{google-tap,google-ci}
+  and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
 
-\begin{figure}[t]
+Research question \numRQB{} assesses whether parallelism can help in
+those cases.  One important factor to the effectiveness of parallelism
+is the distribution of test costs in the test suite.  In the limit, if
+cost is dominated by a single test from a large test suite, it is
+unlikely that parallelization will be beneficial as a test method is
+the smallest working unit in test frameworks.  However, avoiding
+frequent context switches is another factor to consider.  For example,
+assuming there are at least two CPUs available for execution, cost can
+be cut in half if two tests in a large test suite dominate execution
+time. For the case where cost is distributed more evenly across test
+cases, one expects that speedups will be a function of the number of
+cores.
+
+%% These contradictory forces, pushing number of tests and cost
+%% of each test up and down, make prediction of effectiveness challenging.
+
+\begin{figure}[h]
     \centering
@@
 low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
-  specific ranges of $\sigma$ values.}  Note that high standard
-deviations may or may not be indicative of monopolization of execution
-by a small number of tests.  For example, the highest value of
+  specific ranges of $\sigma$ values.}  We noted a small number of
+cases of CPU monopolization.  For example, the highest value of
 $\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
-medium group.  This project contains only \Fix{65} tests, \Fix{62} of
-which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
-\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
-an example where test suite parallelization may not be very beneficial
-as \Fix{$>$99\%} of the execution cost is dominated by only \Fix{3\%}
-of the tests.  Without these two tests this project would have been
-classified as short-running.  A closer inspection in the data
-indicates that the project \CodeIn{uber\_chaperone} was an extreme
-case.  We did not find projects with similar characteristics of time
-monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
-classified as long-running and has the second highest value of
-$\sigma$.  For this project, however, cost is distributed more
-smoothly across \Fix{529} tests, of which \Fix{119 (23\%)} take more
-than \Fix{1s} to run.
+medium group.  This project contains only 65 tests, 62 of which take
+less than 0.5s to run, one of which takes nearly 3s to run, and two of
+which take $\sim$40m to run.  For this project, 99.2\% of the
+execution cost is dominated by only 3\% of the tests; without these
+two costly tests this project would have been classified as
+short-running.  A closer inspection in the data indicates that the
+project \CodeIn{uber\_chaperone} was a corner case: we did not find
+projects with such extreme time monopolization profile.  Project
+\CodeIn{facebookarchive\_linkbench} is also classified as long-running
+and has the second highest value of $\sigma$.  For this project,
+however, cost is distributed more smoothly across \Fix{529} tests, of
+which \Fix{119 (23\%)} take more than \Fix{1s} to run with the rest of
+the tests running faster.
 
@@
 
+%\Mar{$\leftarrow$ show stats to indicate discrimination of
+%  two distributions}
+
 Figure~\ref{fig:time-distributions} showed that the average median
@@
 difference in overall running times across projects in these groups is
-mainly justified by the number of test cases.
-Figure~\ref{fig:size-testsuites} shows the difference in the
-distribution of test suite sizes across groups.\Mar{$\leftarrow$ show
-  stats to indicate discrimination of two distributions} Furthermore,
-we also noted a strong positive correlation between running time and
-number of test on projects in the \longg{} group.  The positive
-correlation between these two variables was, however, weak in the
-\medg{} group, suggesting that saving time in this group with test
+mainly justified by the number of test cases as opposed to the
+individual costs of test cases.  Figure~\ref{fig:size-testsuites}
+shows the difference in the distribution of test suite sizes across
+groups.  This figure indicates that long projects, albeit having a
+wider inter-quartile range (middle 50\% projects in this group are
+less predictable), have a higher median and much higher averages.
+Furthermore, we noted a strong positive correlation between running
+time and number of test on projects in the \longg{} group.  The
+positive correlation between these two variables was, however, weak in
+the \medg{} group, suggesting that saving time in this group with test
 suite parallelization may be more challenging as relatively fewer

### 2017-04-05 paper/evaluation.tex
updated tables

@@
 
-\begin{figure}[ht!]
+\begin{figure}[h!]
 \centering
 \resizebox{.48\textwidth}{!}{%
-\begin{tabular}{lllll}
+\begin{tabular}{llrrl}
 \toprule
-Group & Subject & T$_{\text{p}}$ & T$_{\text{s}}$ & Speedup\\%
+Group & Subject & T$_{\text{d}}$ & T$_{\text{s}}$ & Speedup\\%
 \midrule%
-Long   & JenkinsCI Gerrit Trigger Plugin & \Fix{?} & \Fix{?} & \Fix{?}\\%
-Medium & Apache Logging Log4J2           & \Fix{?} & \Fix{?} & \Fix{?}\\%
-Medium & Jankotek MapDB                  & \Fix{?} & \Fix{?} & \Fix{?}\\%
-Medium & Javaslang                       & \Fix{?} & \Fix{?} & \Fix{?}\\%
-Medium & Jcabi Github                    & \Fix{?} & \Fix{?} & \Fix{?}\\%
+Medium & Jcabi GitHub & 0.30m & 2.75m & x9.01\\%
+Medium & Apache Flink & 2.57m & 10.02m & x3.90\\%
+Medium & Spotify Helios & 1.63m & 3.70m & x2.28\\%
+Medium & Hazelcast Jet & 3.67m & 8.26m & x2.25\\%
+  Long & Jenkins CI Gerrit Plugin & 40.31m & 76.32m & x1.89\\%
+Medium & Jankotek MapDB & 8.58m & 10.51m & x1.23\\%
+Medium & Javaslang & 1.82m & 2.12m & x1.16\\%
+Medium & BounceStorage Chaos HTTP Proxy & 1.47m & 1.47m & x1.00\\%
+Medium & Apache Log4J2 & 8.21m & 4.73m & x0.58\\%
 \bottomrule%
 \end{tabular}}
-\caption{\Fix{Comparacao de tempo sequencial e paralelo}}
+\caption{\Fix{Comparacao de tempo sequencial e paralelo ordenado por
+    speedup}}
 \label{tab:speedup}
@@
         Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
+        Medium & Apache Flink & - & - \\%
+        Medium & BounceStorage Chaos HTTP Proxy & - & -\\%
+        Medium & Hazelcast Jet & - & -\\%
         Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
-        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
-        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
+        Medium & Javaslang & - & \ParClassParMeth{}\\%
+        Medium & Jcabi Github & - & \ParClassParMeth{}\\%
+        Medium & Spotify Helios & - & - \\%
         \bottomrule%

### 2017-04-05 paper/evaluation.tex
pass on rq3

@@
 Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
-parallel execution, we compared the elapsed time in the default
-execution (parallelization enabled) and re-executed the tests
-sequentially.  To enforce sequential execution, we modified the
-existing configurations. Also, we verified that, for each project,
-both executions (\ie, default and sequential) are consistent and
-produce the same outcome. To compute the speedup, we divide the
-sequential time by the default execution. For instance, for a project
-that runs in $10m$ sequentially and runs in $5m$ in the default execution,
-the speedup is two.
+parallel execution, we compared the elapsed time from the default
+execution (parallelization enabled) and the elapsed time from the
+sequential execution.  For each project, we modified the existing
+configurations to disable the parallel test execution. In addition, we
+verified that both executions produce the same outcome to eliminate
+noise from failing tests.
+To compute the speedup, we divide the time obtained in the sequential
+execution by the time obtained from the default execution.  For
+instance, if a project runs the tests sequentially in $10m$ and the
+same execution runs in $5m$ with parallelization enabled (default
+execution), the speedup is two.
 
@@
 
-Figure~\ref{tab:speedup} summarizes our findings.
-\Fix{falar sobre o resultado geral dos speedups - elaborar menor e
-maior speedup}
+Figure~\ref{tab:speedup} summarizes our findings by increasing order
+of speedup. The columns ``Group'' and ``Name'' indicates the time cost
+group and the name of the subject, column ``T$_{\text{d}}$'' reports
+the elapsed time in the default execution, the column
+``T$_{\text{s}}$'' reports the elapsed time in the sequential
+execution, and the column ``Speedup'' reports the overall speedup. We
+observed that \Fix{falar sobre o resultado geral dos speedups -
+elaborar menor e maior speedup... acho que so vale a pena discutir
+quando tiver conviccao dos 2 casos}
 
@@
   \begin{minipage}{8cm}
-      \textit{Answering \numRQD{}:}~\emph{\Jbc{summarize
-      findings.....}}
+      \textit{Answering \numRQD{}:}~\emph{Overall, results indicate
+      that the speedup obtained with parallelization is
+      \Fix{$\sim$x\%} (in average) for \Fix{\%} of the projects
+      (\Fix{x} out of \Fix{w}). }
   \end{minipage}

### 2017-04-05 paper/evaluation.tex
added missing values from fig 10

@@
         Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
-        Medium & Apache Flink & - & - \\%
-        Medium & BounceStorage Chaos HTTP Proxy & - & -\\%
-        Medium & Hazelcast Jet & - & -\\%
+        Medium & Apache Flink & 74 & \ForkSeq{} \\%
+        Medium & BounceStorage Chaos HTTP Proxy & 1 & \ParClassSeqMeth{}\\%
+        Medium & Hazelcast Jet & 7 & \ForkSeq{}\\%
         Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
-        Medium & Javaslang & - & \ParClassParMeth{}\\%
-        Medium & Jcabi Github & - & \ParClassParMeth{}\\%
-        Medium & Spotify Helios & - & - \\%
+        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
+        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
+        Medium & Spotify Helios & 8 & \ForkSeq{}\\%
         \bottomrule%

### 2017-04-05 paper/evaluation.tex
added missing values from fig 11

@@
         \midrule%
-        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
-        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
-        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
-        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
-        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
+        Long   &JenkinsCI Gerrit Trigger Plugin& 1 & \ForkSeq\\%
+        Medium &Bouncestorage Chaos Http Proxy & 1 & C2\\%
+        Medium &Javaslang & 1 & C3\\%
+        Medium &Apache Flink & 1 &\ForkSeq\\%
+        Medium &Apache Logging Log4J2 & 3 & \ForkSeq{}\\%
+        Medium &Google Cloud Platform DataflowJavaSDK & 1 & C3\\%
+        Medium &Hazelcast Jet & 1 & \ForkSeq\\%
+        Medium &Jankotek MapDB & 1 & C3\\%
+        Medium &Mapstruct & 1 & \ForkSeq\\%
+        Medium &Spotify Helios & 3 & \ForkSeq\\%
         \bottomrule%
     \end{tabular}}
-    \caption{\Fix{This is a COPY from the previous table!}}
+    \caption{\Fix{legend}}
     \label{tab:inspection-table}
@@
       supports parallel execution of test suites by default and
-      \Fix{?\%} (\Fix{y} out of \numMedLong{}) require additional
+      \Fix{12\%} (\Fix{10} out of \numMedLong{}) require additional
       parameters to enable these features.}

### 2017-04-05 paper/evaluation.tex
fixed legend

@@
 From the \numMedLong{} projects, we identified \numProjectsPar{}
-projects with the parallel execution modes \ForkSeq{} and
+projects with the parallel execution modes \ForkSeq{}, \ParClassSeqMeth{} and
 \ParClassParMeth{} enabled by default.
@@
     \end{tabular}}
-    \caption{\Fix{legend}}
+    \caption{Subjects with parallelization configurations in build files.}
     \label{tab:inspection-table}

### 2017-04-05 paper/evaluation.tex
minor changes to first par. RQ3

@@
 \begin{itemize}
-    \item \textbf{\RQD}
+    \item \numRQD{}. \textbf{\RQD}
 \end{itemize}
 
-To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
-tested and confirmed parallelization activated by default (see
-Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
-parallel execution, we compared the elapsed time from the default
-execution (parallelization enabled) and the elapsed time from the
-sequential execution.  For each project, we modified the existing
-configurations to disable the parallel test execution. In addition, we
-verified that both executions produce the same outcome to eliminate
-noise from failing tests.
-To compute the speedup, we divide the time obtained in the sequential
-execution by the time obtained from the default execution.  For
-instance, if a project runs the tests sequentially in $10m$ and the
-same execution runs in $5m$ with parallelization enabled (default
+To answer \numRQD{}, we considered all \numProjectsPar{} subjects from
+our benchmark that use parallelization by default in Maven to run
+tests.  Section~\ref{sec:rqC-1} describes in detail our methodology to
+identify these subjects. For each project, the speedup (or slowdown)
+corresponds to the ratio between the elapsed time of a sequential
+execution and the elapsed time of a corresponding parallel execution,
+obtained as described in the script from
+Figure~\ref{fig:mvn-execution}.  As usual, a ratio above 1x denotes
+speedup and a ratio below 1x denotes slowdown.
+
+For each project, we modified the existing configurations to disable
+the parallel test execution. In addition, we verified that both
+executions produce the same outcome to eliminate noise from failing
+tests.  To compute the speedup, we divide the time obtained in the
+sequential execution by the time obtained from the default execution.
+For instance, if a project runs the tests sequentially in $10m$ and
+the same execution runs in $5m$ with parallelization enabled (default
 execution), the speedup is two.
@@
 
+\begin{itemize}
+    \item \textbf{\RQF{}}
+\end{itemize}
+
+\Fix{WIP}
+
+\begin{center}
+\fbox{
+\begin{minipage}{8cm}
+\textit{Answering \numRQF{}:~\emph{\Jbc{summarize findings...}}}
+\end{minipage}
+}
+\end{center}
+
 %%To evaluate the distribution of execution time per project, we sorted

### 2017-04-05 paper/evaluation.tex

@@
 
-To answer \numRQD{}, we considered all \numProjectsPar{} subjects from
-our benchmark that use parallelization by default in Maven to run
-tests.  Section~\ref{sec:rqC-1} describes in detail our methodology to
-identify these subjects. For each project, the speedup (or slowdown)
-corresponds to the ratio between the elapsed time of a sequential
-execution and the elapsed time of a corresponding parallel execution,
-obtained as described in the script from
-Figure~\ref{fig:mvn-execution}.  As usual, a ratio above 1x denotes
-speedup and a ratio below 1x denotes slowdown.
+To answer \numRQD{}, we considered \emph{all} \numProjectsPar{}
+subjects from our benchmark that use parallelization by default in
+Maven to run tests.  Section~\ref{sec:rqC-1} describes in detail the
+methodology we used to find these subjects. For each project, the
+speedup (or slowdown) corresponds to the ratio ($T_s/T_p$) between the
+elapsed time of a sequential execution ($T_s$) and the elapsed time of
+a corresponding parallel execution ($T_p$), obtained as described in
+the script from Figure~\ref{fig:mvn-execution}.  As usual, a ratio
+above 1x denotes speedup and a ratio below 1x denotes slowdown.
 
-For each project, we modified the existing configurations to disable
-the parallel test execution. In addition, we verified that both
-executions produce the same outcome to eliminate noise from failing
-tests.  To compute the speedup, we divide the time obtained in the
-sequential execution by the time obtained from the default execution.
-For instance, if a project runs the tests sequentially in $10m$ and
-the same execution runs in $5m$ with parallelization enabled (default
-execution), the speedup is two.
+%% For each project, we modified the existing configurations to disable
+%% the parallel test execution. In addition, we verified that both
+%% executions produce the same outcome to eliminate noise from failing
+%% tests.  To compute the speedup, we divide the time obtained in the
+%% sequential execution by the time obtained from the default execution.
+%% For instance, if a project runs the tests sequentially in $10m$ and
+%% the same execution runs in $5m$ with parallelization enabled (default
+%% execution), the speedup is two.
 
@@
 \toprule
-Group & Subject & T$_{\text{d}}$ & T$_{\text{s}}$ & Speedup\\%
+\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
 \midrule%
-Medium & Jcabi GitHub & 0.30m & 2.75m & x9.01\\%
-Medium & Apache Flink & 2.57m & 10.02m & x3.90\\%
-Medium & Spotify Helios & 1.63m & 3.70m & x2.28\\%
-Medium & Hazelcast Jet & 3.67m & 8.26m & x2.25\\%
-  Long & Jenkins CI Gerrit Plugin & 40.31m & 76.32m & x1.89\\%
-Medium & Jankotek MapDB & 8.58m & 10.51m & x1.23\\%
-Medium & Javaslang & 1.82m & 2.12m & x1.16\\%
-Medium & BounceStorage Chaos HTTP Proxy & 1.47m & 1.47m & x1.00\\%
-Medium & Apache Log4J2 & 8.21m & 4.73m & x0.58\\%
+Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.47m & 1.00x\\%
+Medium & Apache \textbf{Flink} & 10.02m & 2.57m & 3.90x\\%
+Long & Jenkins CI \textbf{Gerrit} Plugin & 76.32m & 40.31m &  1.89x\\%
+Medium & Spotify \textbf{Helios} & 3.70m & 1.63m & 2.28x\\%  
+Medium & \textbf{Javaslang} & 2.12m & 1.82m & 1.16x\\%
+Medium & \textbf{Jcabi} GitHub & 2.75m & 0.30m & \cellcolor{lightgray}9.01x\\%
+Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
+Medium & Apache \textbf{Log4J2} & 4.73m & 8.21m & \cellcolor{lightgray}0.58x\\%
+Medium & Jankotek \textbf{MapDB} & 10.51m & 8.58m & 1.23x\\%
+\midrule
+\textbf{total} &  &  &  & \avgSpeedup{}x\\
 \bottomrule%
 \end{tabular}}
-\caption{\Fix{Comparacao de tempo sequencial e paralelo ordenado por
-    speedup}}
+\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
+  sequential execution ($T_s$).  Default parallel configuration of
+  Maven is used.  Abbreviation of project names appear in bold face
+  and highest slowdown/speedup appear in gray color.}
 \label{tab:speedup}
@@
 
-Figure~\ref{tab:speedup} summarizes our findings by increasing order
-of speedup. The columns ``Group'' and ``Name'' indicates the time cost
-group and the name of the subject, column ``T$_{\text{d}}$'' reports
-the elapsed time in the default execution, the column
-``T$_{\text{s}}$'' reports the elapsed time in the sequential
-execution, and the column ``Speedup'' reports the overall speedup. We
-observed that \Fix{falar sobre o resultado geral dos speedups -
-elaborar menor e maior speedup... acho que so vale a pena discutir
-quando tiver conviccao dos 2 casos}
+Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
+abbreviated project names, which appear in bold.  Columns
+``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
+project group and the name of the subject.  Column ``$T_s$'' shows
+sequential execution time whereas column ``$T_p$'' shows parallel
+execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
+associated with parallel execution.
+
+Results indicate that, on average, parallel execution was
+\avgSpeedup{} times faster compared to sequential execution.  We noted
+two extreme cases: \CodeIn{JCabi} and \CodeIn{Log4J2}.  \Fix{falar
+  sobre o resultado geral dos speedups - elaborar menor e maior
+  speedup... acho que so vale a pena discutir quando tiver conviccao
+  dos 2 casos}
 

### 2017-04-05 paper/evaluation.tex
pass on RQ4 (part a)

@@
 \avgSpeedup{} times faster compared to sequential execution.  We noted
-two extreme cases: \CodeIn{JCabi} and \CodeIn{Log4J2}.  \Fix{falar
+two extreme cases: \CodeIn{JCabi} and \CodeIn{Log4J2}, which most test
+classes run one, two, or three test methods with the configuration
+\textbf{C2}, without the reutilization of JVM forks. This specific
+configuration is useful when there is the need to isolate the test
+class execution from another, which is the case.
+\Luis{$\leftarrow$ rework this} \Fix{falar
   sobre o resultado geral dos speedups - elaborar menor e maior
@@
 
+Research questions \numRQC{} and \numRQE{} investigate to which extent
+parallelization is used in practice.  It is important to investigate
+adoption as it is possible that developers may use alternative
+mechanisms to execute tests.
+
 \begin{itemize}
-    \item \emph{\RQC}
+    \item \numRQC. \emph{\RQC}
 \end{itemize}
 
-To evaluate the support of parallel execution of test suites, we
-considered the \numMedLong{} projects that ran in at least one minute
-identified in Section~\ref{sec:rqA} (\ie, \medg{} and \longg{}
-groups). We are interested to know if developers consider low-level
-parallelism modes to amortize the execution cost (see
-Section~\ref{sec:modes}). More precisely, we investigate if there are
-projects with parallelization modes enabled by default or if
-developers configure this feature to run only on specific scenarios
-(\eg, dedicated server).  We describe our approach as follows:
+To answer \numRQC{}, we selected all projects that ran in at least one
+minute, \ie, projects from the \medg{} and \longg{} groups.  This set
+includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
+looked for dynamic and static manifestations of parallelism.
+Section~\ref{sec:rqC-1} and~\ref{sec:rqC-2} report results for each of
+these cases.
 
+\vspace{1ex}
 \subsubsection{Test execution with parallelism enabled by default}
@@
 
-We re-executed the tests from the \numMedLong{} projects and we
-configured Maven to output all runtime parameters and their current
-values. We run only the test bootstrap step as the actual test
-execution is unnecessary to output the runtime parameters.
-According to Maven's documentation~\cite{maven-surefire-plugin}, any
-parallelism configuration depends either on (1) the parameter
-\CodeIn{parallel} to define the parallelism mode within a JVM followed
-by the parameter \CodeIn{threadCount} or (2) the parameter
+To find dynamic evidence of parallelism, we ran the test suites from
+our set of \numMedLong{} projects to output all key-value pairs of
+Maven parameters.  To that end, we used the option~\CodeIn{-X} to
+produce debug output and the option~\CodeIn{-DskipTests} to skip
+execution of tests.  We observed that only bootstrapping execution
+suffices to discover which parallel configuration modes Maven will
+actually use.  According to Maven's
+documentation~\cite{maven-surefire-plugin}, any parallelism
+configuration depends either on (1) the parameter \CodeIn{parallel} to
+define the parallelism mode within a JVM followed by the parameter
+\CodeIn{threadCount} or (2) the parameter
 \CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
@@
 \CodeIn{<parallel>methods</parallel>} results in the parallel mode
-\ForkParMeth{}).
-Large projects may contain several test suites distributed on
-different Maven modules with different configurations. In this case,
-we collect the Maven output from each module and we consider only the
-distinct configurations. For instance, if a project contains two
+\ForkParMeth{}).  Large projects may contain several test suites
+distributed on different Maven modules with different
+configurations. In this case, we collect the Maven output from each
+module discarding duplicates. For instance, if a project contains two
 modules with the same parallelism mode, we count only one occurrence
 to not inflate our results.
-From the \numMedLong{} projects, we identified \numProjectsPar{}
-projects with the parallel execution modes \ForkSeq{}, \ParClassSeqMeth{} and
-\ParClassParMeth{} enabled by default.
-Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
-``Group'' indicates the test cost group (see
-Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
-name of the project, the column ``\# of modules'' indicates the number
-of modules with tests in the default execution, and the column
-``Mode'' indicates the corresponding parallelization mode.
+
+%% Column
+%% ``Group'' indicates the test cost group (see
+%% Figure~\ref{fig:rq1-barplot}), the
+
+%\begin{figure}[t!]
+\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+    \footnotesize
+    \centering
+    \setlength{\tabcolsep}{2.5pt}
+%    \resizebox{.48\textwidth}{!}{%
+    \begin{tabular}{lrr}
+        \toprule
+        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
+        \midrule%
+        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1 &  \ParClassSeqMeth{}\\%
+        \Comment{Apache }Flink & 74 & \ForkSeq{} \\%        
+        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1 & \ForkSeq{}\\%
+        \Comment{Spotify }Helios & 8 & \ForkSeq{}\\%
+        Javaslang & 3 & \ParClassParMeth{}\\%
+        Jcabi\Comment{ Github} & 1 & \ParClassParMeth{}\\%        
+        \Comment{Hazelcast }Jet & 7 & \ForkSeq{}\\%
+        \Comment{Apache Logging }Log4J2 & 25 & \ForkSeq{}\\%
+        \Comment{Jankotek }MapDB & 1 & \ParClassParMeth{}\\%        
+        \bottomrule%
+    \end{tabular}
+%    }
+    \caption{Subjects with parallel test execution enabled by
+    default.}
+    \label{tab:freqmodes-dynamic}
+    %\end{figure}
+\end{wrapfigure}      
+Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
+where parallelism is enabled by default.  Column ``\emph{Subject}''
+indicates the name of the project, column ``\emph{\# of modules}''
+indicates the number of detected modules containing tests, and column
+``\emph{Mode}'' shows the parallel configuration mode used in those
+modules (see Section~\ref{sec:modes}).  It came as a surprise the
+observation that no project used distinct configurations in their
+modules.\Mar{$\leftarrow$ table indicates this.  please confirm.}
+Considering our set of \numMedLong{} projects, we found that only
+\textbf{\numProjectsPar{}} of those projects had parallelism enabled
+by default, with only configurations \ParClassSeqMeth{},
+\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
+\ParClassParMeth{} and \ForkSeq{} were the most popular among these
+cases.  Note that these results under-approximate real usage of
+parallelism as we used default parameters in our scripts to spawn the
+Maven process.  That decision could prevent execution of particular
+test modules.  To complement this experiemnt, we also looked in
+\emph{pom.xml} files for the presence of parallelism.
 %\begin{figure}[h!]
@@
 %\end{figure}
-\begin{figure}[ht!]
-    \centering
-    \resizebox{.48\textwidth}{!}{%
-    \begin{tabular}{llcl}
-        \toprule
-        Group & Subject & \# of modules & Mode\\%
-        \midrule%
-        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
-        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
-        Medium & Apache Flink & 74 & \ForkSeq{} \\%
-        Medium & BounceStorage Chaos HTTP Proxy & 1 & \ParClassSeqMeth{}\\%
-        Medium & Hazelcast Jet & 7 & \ForkSeq{}\\%
-        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
-        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
-        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
-        Medium & Spotify Helios & 8 & \ForkSeq{}\\%
-        \bottomrule%
-    \end{tabular}}
-    \caption{Subjects with parallel test execution enabled by
-    default.}
-    \label{tab:freqmodes-dynamic}
-\end{figure}
 
@@
 \label{sec:rqC-2}
+
+\Mar{----------------------- estou aqui}
 
@@
 To understand why developers prefer not use parallel test execution,
-we considered the \numNonParallel{} subjects that do not use any
-parallel mode from Section~\ref{sec:rqC-1} and elaborated a
+we considered \numNonParallel{} subjects that do not use parallel
+configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
 quick survey to extent the comprehension about why developers do not
@@
 \emailsSent{} developers that recently contributed to the 
-\numNonParallel{} projects.
-There were \emailsAnswered{} replies from \emailsProjectsAnswered{}, 
-and \emailsFalseAnswers{} was not able to explain how the testing works.
+\numNonParallel{} projects, and we did not found any e-mail from
+\Fix{??} projects using \CodeIn{git} tool.
+\Luis{Here I want to say that I could not found any valid e-mail using
+\textit{git log}}
+There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
+projects, and \emailsFalseAnswers{} developers was not able to 
+explain how the testing works or was not able to answer the survey.
 
@@
 
-\Comment{
-\begin{enumerate}
-	\item How long does it take for test to run in your
-		environment?
-	\item Can you briefly define your setup?
-	\item Do you confirm that your project does not run in
-		parallel?
-	\item Select a reason for not using paralellization:
-		\begin{enumarate}
-			\item I did not know it was possible;
-			\item I was concerned with concurrency issues;
-			\item I use a continuous integration server;
-			\item Some other reason.
-		\end{enumerate}
-\end{enumerate}
-}
+%% \begin{enumerate}
+%% 	\item How long does it take for test to run in your
+%%		environment?
+%%	\item Can you briefly define your setup?
+%%	\item Do you confirm that your project does not run in
+%%		parallel?
+%%	\item Select a reason for not using paralellization:
+%%		\begin{enumarate}
+%%			\item I did not know it was possible;
+%%			\item I was concerned with concurrency issues;
+%%			\item I use a continuous integration server;
+%%			\item Some other reason.
+%%		\end{enumerate}
+%% \end{enumerate}
 
-From the valid replies, we confirmed that the projects takes more than
-\Fix{1m} to run tests and \emailsSeq{} confirmed that those projects do not use 
-parallel testing using Maven Surefire. The other projects that we do not 
-confirm, need and extra parameter to execute in parallel mode \Luis{make 
-sure that they are inside the static analysis sheets made before}.
+Based on the answers from the developers, we confirmed that most of
+the subjects execution time was compatible with the results found at
+Section~\ref{sec:rqA}. From Question I, we noticed that \emailsCI{}
+developers confirmed the use of an continuous integration server to
+run tests, which \emailsDistributed{} of them is using a distributed
+continuous integration server as an alternative to parallelism.
+From a local development, \emailsLocal{} developers answered that they
+run tests in a local machine, and \emailsNotDescribed{} developers did
+not described their environment.
+From Question II, we noticed that \emailsSequential{} confirmed that
+they do not execute tests in parallel, and \emailsParallel{} did not
+confirmed, however, the developers confirmed the need of an extra
+parameter at the command line to execute in parallel.
+From Question III, \emailsA{} of developers do not know that
+parallelism is an available configuration for Maven Surefire,
+\emailsB{} of developers do not use parallel testing concerned with
+concurrency issues, \emailsD{} of developers uses a continuous
+integretion server for run tests while working \Luis{here I want to
+say that they use it for something like "non-blocking testing" while
+developing in a local machine}, \emailsD{} of developers thinks that
+it is not worthy the effort, and \emailsNA{} of developers did not
+answered the last question, or did not knew an answer.
 
-We noticed that \pctEmailsCI{} of developers use an continuous integration 
-server to run tests, \pctEmailsLocal{} run tests in the
-development machine, \pctEmailsDidNotSpecify{} did not specified their
-testing setup. We also observed that one project has testing enabled 
-without parallelization. However the maintainers do not execute the tests.
-Considering developers did not know about the existence of the
-parallelism configuration \pctEmailsDoNotKnow{} of the replies
-confirmed that. Three of the developers also confirmed that they use
-another method of parallelization with a distributed build machines.
+\Luis{Pie chart}
 

### 2017-04-06 paper/evaluation.tex
merge

--- 2017-04-05 paper/evaluation.tex
@@
 observation that no project used distinct configurations in their
-modules.\Mar{$\leftarrow$ table indicates this.  please confirm.}
-Considering our set of \numMedLong{} projects, we found that only
-\textbf{\numProjectsPar{}} of those projects had parallelism enabled
-by default, with only configurations \ParClassSeqMeth{},
+modules. Considering our set of \numMedLong{} projects, we found that
+only \textbf{\numProjectsPar{}} of those projects had parallelism
+enabled by default, with only configurations \ParClassSeqMeth{},
 \ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
@@
 Maven process.  That decision could prevent execution of particular
-test modules.  To complement this experiemnt, we also looked in
-\emph{pom.xml} files for the presence of parallelism.
+test modules.  
 %\begin{figure}[h!]
@@
 \label{sec:rqC-2}
-
-\Mar{----------------------- estou aqui}
-
-To extend our previous investigation, we evaluated the presence of
-parallelism configuration in several build files (\ie, \pomf{} files)
-from the same sample set of \numMedLong{} projects. The rationale is
-that some projects may have support to parallel execution but it is
-deactivated by default (\ie, require additional arguments before the
-test execution). For instance, on Maven, it is possible to create
-multiple configurations in the same build file and activate any of
-them dynamically.  To reduce the space of \Fix{x} build files, we
-considered a subset of \Fix{y} build files with the following
-criteria: the given \pomf{} file has \CodeIn{maven-surefire-plugin}
-plugin declaration and it has an explicit \CodeIn{configuration}
-declaration. We automatically parsed these \Fix{y} files and we used
-the same approach to classify the parallelization mode from the parsed
-configurations as in our previous analysis. In an initial analysis, we
-noticed that some projects do not declare a static value in some
-parameters, instead, these projects inform the actual value in the
-command line. To handle this case, we computed all valid values for
-the parameter.
+Given the inherent limitation of dynamic monitoring to find evidence
+of parallelism, we also looked for indication of parallelism in
+\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
+  projects}. In principle, some projects can use parallel execution
+although that is only activated when developers pass certain
+parameters to the build process. For instance, it is possible to
+create in Maven multiple configurations in the same build file and
+select dynamically which one should be used.
+
+\Mar{I have no clue what you mean here... Why should I care about
+  space on build files?  I thought we did this check
+  for every project and module.  $\rightarrow$}\Fix{To reduce the
+  space of \Fix{x} build files, we considered a subset of \Fix{y}
+  build files with the following criteria}: the given \pomf{} file has
+\CodeIn{maven-surefire-plugin} plugin declaration and it has an
+explicit \CodeIn{configuration} declaration. We automatically parsed
+these \Fix{y} files and we used the same approach to classify the
+parallelization mode from the parsed configurations as in our previous
+analysis. In an initial analysis, we noticed that some projects do not
+declare a static value in some parameters, instead, these projects
+inform the actual value in the command line. To handle this case, we
+computed all valid values for the parameter.
+
+We found ten projects that use parallelism using this methodology.
+Compared to the set of projects listed in Figure~\ref{tab:speedup}, we
+found two new projects, namely: \CodeIn{Google Cloud\Comment{
+    Platform} DataflowJavaSDK} (using configuration C3) and
+\CodeIn{Mapstruct} (using configuration \ForkSeq{}).  Curiously, we
+also found that project \CodeIn{Jcabi} was not detected using this
+methodology.  That happened because \Mar{please, explain why}.
+Considering the static and dynamic methods together, we found a total
+of 11 distinct projects using parallelism, corresponding to the union
+of the two subject sets.
+
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+      \textit{Answering \numRQC{}:}~\emph{Results indicate that test
+        suite parallelization is underused.  Overall, only
+        \percentParallel{} of costly projects (11 out of \numMedLong)
+        use parallelism.}
+  \end{minipage}
+}
+\end{center}
 
@@
 
-Figure~\ref{tab:inspection-table} summarizes our results.
-\Fix{The first column indicates the group of projects according to
-their time cost.  The second column indicates the number of build
-files per group.  The last column indicates the ratio of projects with
-parallelization settings.  From the \numMedLong{} subjects, we found
-\pomMedLong{} \pomf{} files.  The \numPomMatched{} configurations are
-distributed across \numProjectsPar{} projects from our sample.}
-
-% \emph{From these results we found that $\sim$51\% of medium and
-% long-running projects do not use parallel features to run test
-% suites.}\Mar{please make it consistent with research
-% question}\Mar{explain this is over(under)-estimated...}
-\begin{figure}[ht!]
-    \centering
-    \resizebox{.48\textwidth}{!}{%
-    \begin{tabular}{llcl}
-        \toprule
-        Group & Subject & \# of modules & Mode\\%
-        \midrule%
-        Long   &JenkinsCI Gerrit Trigger Plugin& 1 & \ForkSeq\\%
-        Medium &Bouncestorage Chaos Http Proxy & 1 & C2\\%
-        Medium &Javaslang & 1 & C3\\%
-        Medium &Apache Flink & 1 &\ForkSeq\\%
-        Medium &Apache Logging Log4J2 & 3 & \ForkSeq{}\\%
-        Medium &Google Cloud Platform DataflowJavaSDK & 1 & C3\\%
-        Medium &Hazelcast Jet & 1 & \ForkSeq\\%
-        Medium &Jankotek MapDB & 1 & C3\\%
-        Medium &Mapstruct & 1 & \ForkSeq\\%
-        Medium &Spotify Helios & 3 & \ForkSeq\\%
-        \bottomrule%
-    \end{tabular}}
-    \caption{Subjects with parallelization configurations in build files.}
-    \label{tab:inspection-table}
-\end{figure}
+%% Figure~\ref{tab:inspection-table} summarizes our results.
+%% \Fix{The first column indicates the group of projects according to
+%% their time cost.  The second column indicates the number of build
+%% files per group.  The last column indicates the ratio of projects with
+%% parallelization settings.  From the \numMedLong{} subjects, we found
+%% \pomMedLong{} \pomf{} files.  The \numPomMatched{} configurations are
+%% distributed across \numProjectsPar{} projects from our sample.}
+
+%% % \emph{From these results we found that $\sim$51\% of medium and
+%% % long-running projects do not use parallel features to run test
+%% % suites.}\Mar{please make it consistent with research
+%% % question}\Mar{explain this is over(under)-estimated...}
+%% \begin{figure}[ht!]
+%%     \centering
+%%     \resizebox{.48\textwidth}{!}{%
+%%     \begin{tabular}{llcl}
+%%         \toprule
+%%         Group & Subject & \# of modules & Mode\\%
+%%         \midrule%
+%%         Long   &JenkinsCI Gerrit Trigger Plugin& 1 & \ForkSeq\\%
+%%         Medium &Bouncestorage Chaos Http Proxy & 1 & C2\\%
+%%         Medium &Javaslang & 1 & C3\\%
+%%         Medium &Apache Flink & 1 &\ForkSeq\\%
+%%         Medium &Apache Logging Log4J2 & 3 & \ForkSeq{}\\%
+%%         Medium &Google Cloud Platform DataflowJavaSDK & 1 & C3\\%
+%%         Medium &Hazelcast Jet & 1 & \ForkSeq\\%
+%%         Medium &Jankotek MapDB & 1 & C3\\%
+%%         Medium &Mapstruct & 1 & \ForkSeq\\%
+%%         Medium &Spotify Helios & 3 & \ForkSeq\\%
+%%         \bottomrule%
+%%     \end{tabular}}
+%%     \caption{Subjects with parallelization configurations in build files.}
+%%     \label{tab:inspection-table}
+%% \end{figure}
+
 %% \begin{figure}[ht!]
@@
 
-\begin{center}
-\fbox{
-  \begin{minipage}{8cm}
-      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
-      that parallelism features are underused by default given that
-      only \percentParallel{} of projects  (5 out of \numMedLong)
-      supports parallel execution of test suites by default and
-      \Fix{12\%} (\Fix{10} out of \numMedLong{}) require additional
-      parameters to enable these features.}
-  \end{minipage}
-}
-\end{center}
-
 \begin{itemize}
-	\item \textbf{\RQE{}}
+	\item \numRQE{}. \textbf{\RQE{}}
 \end{itemize}

### 2017-04-06 paper/evaluation.tex
adding comments to Luis

@@
 \avgSpeedup{} times faster compared to sequential execution.  We noted
-two extreme cases: \CodeIn{JCabi} and \CodeIn{Log4J2}, which most test
+two extreme cases\Mar{note that one is a case of very high speedup and
+  another is a case of very high slowdown.  It is strange that the
+  same explanation justify both cases.  Are you only referring to
+  Log4J2 or both cases in your explanation?}: \CodeIn{Jcabi} and \CodeIn{Log4J2}, which most test
 classes run one, two, or three test methods with the configuration
-\textbf{C2}, without the reutilization of JVM forks. This specific
+\Mar{We are not using bold for these.  If you want you can change, but
+  please do so by holding all locks.}\textbf{C2}, without the
+reutilization of JVM forks\Mar{Don't understand.
+  Fork-configurations have an F in front, no?  Like FC1.  Please
+  check.  Do you mean FC0 for Log4J? (I checked Figure 10)}. This specific
 configuration is useful when there is the need to isolate the test

### 2017-04-06 paper/evaluation.tex
answering comments

@@
 \avgSpeedup{} times faster compared to sequential execution.  We noted
-two extreme cases\Mar{note that one is a case of very high speedup and
-  another is a case of very high slowdown.  It is strange that the
-  same explanation justify both cases.  Are you only referring to
-  Log4J2 or both cases in your explanation?}: \CodeIn{Jcabi} and \CodeIn{Log4J2}, which most test
+two extreme cases: \CodeIn{Jcabi} and \CodeIn{Log4J2}.
+The first when using the default parallel configuration, runs a
+\textbf{C3} configuration with small test classes and big test
+methods, allowing to run multiple methods and classes at once. The
+high slowdown happens when big methods run sequentially.
+\Comment{The second which most test
 classes run one, two, or three test methods with the configuration
@@
 configuration is useful when there is the need to isolate the test
-class execution from another, which is the case.
+class execution from another, which is the case.}
 \Luis{$\leftarrow$ rework this} \Fix{falar
@@
 
-\Luis{Pie chart}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.25\textwidth]{plots/survey.pdf}
+     \caption{\Luis{todo}}
+\end{figure}
 

### 2017-04-06 paper/evaluation.tex
fixing rq3

@@
 high slowdown happens when big methods run sequentially.
-\Comment{The second which most test
-classes run one, two, or three test methods with the configuration
-\Mar{We are not using bold for these.  If you want you can change, but
-  please do so by holding all locks.}\textbf{C2}, without the
-reutilization of JVM forks\Mar{Don't understand.
-  Fork-configurations have an F in front, no?  Like FC1.  Please
-  check.  Do you mean FC0 for Log4J? (I checked Figure 10)}. This specific
-configuration is useful when there is the need to isolate the test
-class execution from another, which is the case.}
+The second when using the default parallel configuration, runs a
+\textbf{FC0} configuration with small test classes and small test
+methods, which is slowdown by the JVM creation overhead. This
+configuration is useful to isolate each test method from each other.
 \Luis{$\leftarrow$ rework this} \Fix{falar

### 2017-04-06 paper/evaluation.tex
RQ6 - added dummmy data

@@
 
-\Fix{WIP}
+\begin{figure}[h!]
+\centering
+\resizebox{.48\textwidth}{!}{%
+\begin{tabular}{lrrrrrr}
+\toprule
+\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
+\midrule%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+\bottomrule%
+\end{tabular}}
+\caption{\Fix{Tabela de eficiencia}}
+\label{tab:rq6-efficiency}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\resizebox{.48\textwidth}{!}{%
+\begin{tabular}{lcrrrrr}
+\toprule
+\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
+\midrule%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+\bottomrule%
+\end{tabular}}
+\caption{\Fix{Tabela de flakyness}}
+\label{tab:rq6-efficiency}
+\end{figure}
 

### 2017-04-06 paper/evaluation.tex
threats to validity section and lessons learned

@@
 
+\subsection{Threats to Validity}
+
+\Fix{Jean and Luis should write this. This is really important for an
+  empirical study.  You need to undertand main sources of threat:
+  internal, external, and construct.  Read this document for the
+  basics: http://www.statsdirect.com/help/basics/validity.htm.  Read
+  this document for an example:
+  http://www.cin.ufpe.br/~damorim/publications/perez-etal-icst2017.pdf}
+
+\subsection{Lessons Learned}
+
+\Fix{Marcelo can write this...}
+
 %%To evaluate the distribution of execution time per project, we sorted

### 2017-04-06 paper/modes.tex
clarifying configuration modes

@@
 The list below shows the choices to control parallelism within one
-Java Virtual Machine (JVM), which runs in a single CPU process.  These
-options are offered by the testing framework, \eg{}, JUnit.
+Java Virtual Machine (JVM).  These options are offered by the testing
+framework (\eg{}, JUnit).
 
@@
 
-The list below shows the choices to control parallelism through the
-build system, \eg{}, Maven.  The build system can spawn multiple JVMs,
-each running on its own OS process on a given CPU and handling a
-partition of the test set.
+%% The build system can spawn multiple JVMs, each running on its own OS
+%% process on a given CPU and handling a partition of the test set.
+
+Forking OS processes to run test jobs is the basic mechanism of build
+systems to obtain parallelism at the machine space (see
+Figure~\ref{fig:levels}).  For Java-based build systems, such as Maven
+and Ant, this amounts to spawning one JVM, on a given CPU, to handle a
+test job and aggregating results when jobs finish.  The list below
+shows the choices to control parallelism through the build system
+(\eg{}, Maven).
 
@@
 \item
-    \textbf{Forked classes; sequential methods (\ForkSeq).}~This
-    configuration spawns multiple JVMs, assigning a partition of the
-    test set to each JVM.  Test methods run sequentially within each
-    JVM.
+    \textbf{Forked JVMs with sequential methods (\ForkSeq).}~The build
+    system spawns multiple JVMs with this configuration, assigning a
+    partition of the set of test classes to each JVM.  Test methods
+    run sequentially within each JVM.
 \item
-    \textbf{Forked classes; parallel methods (\ForkParMeth).}~In
-    addition to forking multiple JVMs, as \ForkSeq{} does, this
-    configuration runs tests concurrently, as \SeqClassParMeth{} does.
+    \textbf{Forked JVMs with parallel methods (\ForkParMeth).}~With
+    this configuration, the build system forks multiple JVMs, as
+    \ForkSeq{} does.  However, it runs tests concurrently, as
+    \SeqClassParMeth{} does.
 \end{itemize}
@@
 
-Forking OS processes to run test jobs is a popular mechanism of build
-systems to obtain parallelism at the machine space (see
-Figure~\ref{fig:levels}).  For Java-based build systems, such as Maven
-and Ant, this amounts to spawning one JVM instance to handle a test
-job and aggregating corresponding results when test jobs finish.  Note
-that forking can only be combined with configuration
-\SeqClassParMeth{} (see Section~\ref{sec:frameworks}) as Maven only
-accepts one test class at a time per forked process.  To attenuate the
-non-trivial cost of spawning new JVM processes on every test class,
-Maven offers an option to reuse the JVM.
+Note from the listing that forking can only be combined with
+configuration \SeqClassParMeth{} (see Section~\ref{sec:frameworks}) as
+Maven made the design choice to only accept one test class at a time
+per forked process.  Maven offers an option to reuse JVMs that can be
+used to attenuate the potentially high cost of spawning new JVM
+processes on every test class (if reuse is enabled) and also to
+achieve test isolation (if reuse is disabled).
 
@@
 options to run tests using the parallel execution mode \ForkParMeth{}.
-Maven implements this feature through its JUnit test plugin
-Surefire~\cite{maven-surefire-plugin}.  With this configuration, Maven
+Maven implements this feature through its Surefire JUnit test
+plugin~\cite{maven-surefire-plugin}.  With this configuration, Maven
 forks one JVM per core (\CodeIn{forkCount} parameter) and uses five

### 2017-04-06 paper/evaluation.tex
RQ5 - adjusted piechart
pass on RQ4

@@
 create in Maven multiple configurations in the same build file and
-select dynamically which one should be used.
-
-\Mar{I have no clue what you mean here... Why should I care about
-  space on build files?  I thought we did this check
-  for every project and module.  $\rightarrow$}\Fix{To reduce the
-  space of \Fix{x} build files, we considered a subset of \Fix{y}
-  build files with the following criteria}: the given \pomf{} file has
-\CodeIn{maven-surefire-plugin} plugin declaration and it has an
-explicit \CodeIn{configuration} declaration. We automatically parsed
-these \Fix{y} files and we used the same approach to classify the
-parallelization mode from the parsed configurations as in our previous
-analysis. In an initial analysis, we noticed that some projects do not
-declare a static value in some parameters, instead, these projects
-inform the actual value in the command line. To handle this case, we
-computed all valid values for the parameter.
+select dynamically which one should be used.  We automatically parsed
+\Fix{X} build files and we used the same approach to classify the
+parsed configurations as in our previous analysis. Initially, we
+noticed that our approach was unable to infer the parallel mode in
+some projects because these projects do not declare a static value in
+some parameters (\eg,
+\CodeIn{<parallel>\$\{parallel.type\}</parellel>}). For these projects,
+it is required to inform additional parameters to enable the parallel
+mode in the command line (\eg, \CodeIn{mvn test
+-Dparallel.type=classesAndMethods}). \Jbc{We wouldn't have FALSE
+NEGATIVES if we considered this $\rightarrow$}To handle this case, we
+considered all valid values for the parameter.
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.25\textwidth]{plots/survey.pdf}
-     \caption{\Luis{todo}}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
+    \caption{\Luis{todo}\label{fig:rq5-answers}}
 \end{figure}

### 2017-04-06 paper/evaluation.tex
pass on RQ4

@@
 
-Research questions \numRQC{} and \numRQE{} investigate to which extent
-parallelization is used in practice.  It is important to investigate
-adoption as it is possible that developers may use alternative
-mechanisms to execute tests.
+The dimension adoption focuses on the usage of parallelism in
+open-source projects.  It evaluates (\numRQC) how often open-source
+projects use parallelization schemes and (\numRQE) how developers
+involved in costly projects, not using parallelization, perceive this
+technology.
 
 \begin{itemize}
-    \item \numRQC. \emph{\RQC}
+    \item \numRQC. \textbf{\RQC{}}
 \end{itemize}
 
-To answer \numRQC{}, we selected all projects that ran in at least one
-minute, \ie, projects from the \medg{} and \longg{} groups.  This set
-includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
+To answer \numRQC{}, we selected all projects from the \medg{} and
+\longg{} groups, \ie, projects that ran in at least one minute.  This
+set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
 looked for dynamic and static manifestations of parallelism.
-Section~\ref{sec:rqC-1} and~\ref{sec:rqC-2} report results for each of
-these cases.
+
+%% The
+%% following section report results for each of these cases.
 
 \vspace{1ex}
-\subsubsection{Test execution with parallelism enabled by default}
+\subsubsection{Dynamic checking}
 \label{sec:rqC-1}
@@
 produce debug output and the option~\CodeIn{-DskipTests} to skip
-execution of tests.  We observed that only bootstrapping execution
-suffices to discover which parallel configuration modes Maven will
-actually use.  According to Maven's
-documentation~\cite{maven-surefire-plugin}, any parallelism
-configuration depends either on (1) the parameter \CodeIn{parallel} to
-define the parallelism mode within a JVM followed by the parameter
+execution of tests.  We observed that only bootstrapping the Maven
+process suffices to discover which parallel configuration modes it
+will use to run tests.  According to Maven's
+documentation~\cite{maven-surefire-plugin}, a parallel configuration
+depends either on (1) the parameter \CodeIn{parallel} to define the
+parallelism mode within a JVM followed by the parameter
 \CodeIn{threadCount} or (2) the parameter
@@
   in old versions of Maven Surefire} to define the number of forked
-JVMs. For each execution, we capture theses parameters and their
-values to map to one of the possible parallelization modes.  For
-instance, if a given project contains a module with the parameter
+JVMs.  As such, we captured, for each project, all related key-value
+pairs of Maven parameters and mapped those pairs to one of the
+possible parallelization modes.  For instance, if a given project
+contains a module with the parameter
 \CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
 \ForkSeq{} or \ForkParMeth{} depending on the presence and the value
-of the parameter \CodeIn{parallel} (\ie, the presence of
-\CodeIn{<parallel>methods</parallel>} results in the parallel mode
-\ForkParMeth{}).  Large projects may contain several test suites
-distributed on different Maven modules with different
-configurations. In this case, we collect the Maven output from each
-module discarding duplicates. For instance, if a project contains two
-modules with the same parallelism mode, we count only one occurrence
-to not inflate our results.
+of the parameter \CodeIn{parallel}.  If the parameter
+\CodeIn{parallel} is set to \CodeIn{methods} the detected mode will be
+\ForkParMeth{}.  Large projects may contain several test suites
+distributed on different Maven modules potentially using different
+configurations.  For those cases, we collected the Maven output from
+each module discarding duplicates as to avoid inflating results. For
+instance, if a project contains two modules using the same
+configuration, we counted only one occurrence.
+
+\Mar{---- estou aqui}
 

### 2017-04-06 paper/evaluation.tex
removed some dummy data

@@
 
+\vspace{1ex}
 \begin{center}
@@
 \end{center}
-
 \vspace{1ex}
+
 \begin{itemize}
@@
 \end{center}
+\vspace{1ex}
 
@@
 \midrule%
-Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.47m & 1.00x\\%
-Medium & Apache \textbf{Flink} & 10.02m & 2.57m & 3.90x\\%
-Long & Jenkins CI \textbf{Gerrit} Plugin & 76.32m & 40.31m &  1.89x\\%
-Medium & Spotify \textbf{Helios} & 3.70m & 1.63m & 2.28x\\%  
-Medium & \textbf{Javaslang} & 2.12m & 1.82m & 1.16x\\%
-Medium & \textbf{Jcabi} GitHub & 2.75m & 0.30m & \cellcolor{lightgray}9.01x\\%
+Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 
+    \cellcolor{lightgray}1.02x\\%
+Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%
+Long & Jenkins CI \textbf{Gerrit} Plugin & 51.19m & 40.31m &  1.26x\\%
+Medium & Spotify \textbf{Helios} & 4.46m & 1.63m & 2.73x\\%  
+Medium & \textbf{Javaslang} & 2.18m & 1.82m & 1.19x\\%
+Medium & \textbf{Jcabi} GitHub & 2.76m & 0.30m &
+    \cellcolor{lightgray}9.2x\\%
 Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
-Medium & Apache \textbf{Log4J2} & 4.73m & 8.21m & \cellcolor{lightgray}0.58x\\%
-Medium & Jankotek \textbf{MapDB} & 10.51m & 8.58m & 1.23x\\%
+Medium & Apache \textbf{Log4J2} & 8.24m & 8.21m & 
+    \cellcolor{lightgray}1.00x\\%
+Medium & Jankotek \textbf{MapDB} & 10.06m & 8.58m & 1.17x\\%
 \midrule
@@
 \avgSpeedup{} times faster compared to sequential execution.  We noted
-two extreme cases: \CodeIn{Jcabi} and \CodeIn{Log4J2}.
-The first when using the default parallel configuration, runs a
+three extreme cases: \CodeIn{Chaos}, \CodeIn{Jcabi} and \CodeIn{Log4J2}.
+The first, the default configuration is \textbf{C2}, however, the test is
+composed of takes $>$99\% of the test time. In this case, when running
+in sequential the execution time is almost the same as the parallel
+execution.
+The second when using the default parallel configuration, runs a
 \textbf{C3} configuration with small test classes and big test
-methods, allowing to run multiple methods and classes at once. The
-high slowdown happens when big methods run sequentially.
-The second when using the default parallel configuration, runs a
-\textbf{FC0} configuration with small test classes and small test
-methods, which is slowdown by the JVM creation overhead. This
-configuration is useful to isolate each test method from each other.
+methods. In this case, a high slowdown is noticed when running those
+big methods sequentially.
+The third, runs parallel configuration in \Fix{80\%} of the project
+modules, however, the test time is dominated by one of the
+sequentially running modules.
 \Luis{$\leftarrow$ rework this} \Fix{falar
@@
 produce debug output and the option~\CodeIn{-DskipTests} to skip
-execution of tests.  We observed that only bootstrapping the Maven
-process suffices to discover which parallel configuration modes it
-will use to run tests.  According to Maven's
+execution of tests.  We skipped execution of tests as we observed from
+sampling that only bootstrapping the Maven process suffices to infer
+which parallel configuration modes it will use to actually run the
+tests.  It is also important to point that we used the default
+configurations specified in the project.  We inferred parallel
+configurations by searching for certain configuration parameters in
+log files. According to Maven's
 documentation~\cite{maven-surefire-plugin}, a parallel configuration
@@
 \CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
-\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
+\ForkSeq{} or \ForkParMeth{}, depending on the presence and the value
 of the parameter \CodeIn{parallel}.  If the parameter
@@
 configurations.  For those cases, we collected the Maven output from
-each module discarding duplicates as to avoid inflating results. For
-instance, if a project contains two modules using the same
-configuration, we counted only one occurrence.
-
-\Mar{---- estou aqui}
+each module discarding duplicates as to avoid inflating counts for
+configuration modes that appear in several modules of the same
+project. For instance, if a project contains two modules using the
+same configuration, we counted only one occurrence.
 
@@
         \midrule%
-        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1 &  \ParClassSeqMeth{}\\%
-        \Comment{Apache }Flink & 74 & \ForkSeq{} \\%        
-        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1 & \ForkSeq{}\\%
-        \Comment{Spotify }Helios & 8 & \ForkSeq{}\\%
-        Javaslang & 3 & \ParClassParMeth{}\\%
-        Jcabi\Comment{ Github} & 1 & \ParClassParMeth{}\\%        
-        \Comment{Hazelcast }Jet & 7 & \ForkSeq{}\\%
-        \Comment{Apache Logging }Log4J2 & 25 & \ForkSeq{}\\%
-        \Comment{Jankotek }MapDB & 1 & \ParClassParMeth{}\\%        
+        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
+        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
+        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
+        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
+        Javaslang & 3/3 & \ParClassParMeth{}\\%
+        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
+        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
+        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
+        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
         \bottomrule%
@@
 Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
-where parallelism is enabled by default.  Column ``\emph{Subject}''
-indicates the name of the project, column ``\emph{\# of modules}''
-indicates the number of detected modules containing tests, and column
-``\emph{Mode}'' shows the parallel configuration mode used in those
-modules (see Section~\ref{sec:modes}).  It came as a surprise the
-observation that no project used distinct configurations in their
-modules. Considering our set of \numMedLong{} projects, we found that
-only \textbf{\numProjectsPar{}} of those projects had parallelism
-enabled by default, with only configurations \ParClassSeqMeth{},
+where parallelism is enabled by default in Maven.  Column
+``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.  We note that, considering these projects, the
+modules that do not use the configuration cited use the sequential
+configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
+use sequential configuration.
+
+It came as a surprise the observation that
+no project used distinct configurations in their modules. Considering
+our set of \numMedLong{} projects, we found that only
+\textbf{\numProjectsPar{}} of those projects had parallelism enabled
+by default, with only configurations \ParClassSeqMeth{},
 \ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
@@
 
-\subsubsection{Presence of parallelism configurations in build files}
+%% Recall that some projects can use parallel execution that is only
+%% activated when developers pass certain parameters to the build
+%% process. For instance, it is possible to create in Maven multiple
+%% configurations in the same build file and select dynamically which one
+%% should be used.
+
+\subsubsection{Static checking}
 \label{sec:rqC-2}
 Given the inherent limitation of dynamic monitoring to find evidence
-of parallelism, we also looked for indication of parallelism in
-\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
-projects}. In principle, some projects can use parallel execution
-although that is only activated when developers pass certain
-parameters to the build process. For instance, it is possible to
-create in Maven multiple configurations in the same build file and
-select dynamically which one should be used.  We automatically parsed
-\Fix{X} build files and we used the same approach to classify the
-parsed configurations as in our previous analysis. Initially, we
-noticed that our approach was unable to infer the parallel mode in
-some projects because these projects do not declare a static value in
-some parameters (\eg,
-\CodeIn{<parallel>\$\{parallel.type\}</parellel>}). For these projects,
-it is required to inform additional parameters to enable the parallel
-mode in the command line (\eg, \CodeIn{mvn test
--Dparallel.type=classesAndMethods}). \Jbc{We wouldn't have FALSE
-NEGATIVES if we considered this $\rightarrow$}To handle this case, we
-considered all valid values for the parameter.
-
-We found ten projects that use parallelism using this methodology.
-Compared to the set of projects listed in Figure~\ref{tab:speedup}, we
-found two new projects, namely: \CodeIn{Google Cloud\Comment{
-    Platform} DataflowJavaSDK} (using configuration C3) and
-\CodeIn{Mapstruct} (using configuration \ForkSeq{}).  Curiously, we
-also found that project \CodeIn{Jcabi} was not detected using this
-methodology.  That happened because \Mar{please, explain why}.
-Considering the static and dynamic methods together, we found a total
-of 11 distinct projects using parallelism, corresponding to the union
-of the two subject sets.
-
+of parallelism, we also looked for indication of parallelism in build
+files\Comment{ in the same sample set of \numMedLong{} projects}.  We
+parsed all \emph{pom.xml} files under the project's directory and used
+the same approach as in our previous analysis to classify
+configurations.  We noticed initially that our approach was unable to
+infer the configuration mode for cases where the decision depends on
+the input (\eg,
+\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
+projects, the tester needs to provide additional parameters in the
+command line to enable parallelization (\eg, \CodeIn{mvn test
+  -Dparallel.type=classesAndMethods}). To handle those case, we
+considered all possible values for the parameter (in this case,
+\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
+approach is not immune to false negatives, which can ocurr when
+\emph{pom.xml} files are encapsulated in jar files or downloaded from
+the network.  Consequently, this static checking is complementary to
+the dynamic checking, previously presented.
+
+Overall, we found, using this methodology, ten projects that use
+parallelism.  Compared to the set of projects listed in
+Figure~\ref{tab:speedup}, we found two new projects, namely:
+\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
+configuration C3) and \CodeIn{Mapstruct} (using configuration
+\ForkSeq{}).  Curiously, we also found that project \CodeIn{Jcabi} was
+not detected using this methodology.  That happened because this
+project loads its \emph{pom.xml} file from a jar file that we did not
+check.  Considering the static and dynamic methods together, we found
+a total of 11 distinct projects using parallelism, corresponding to
+the union of the two subject sets.
+
+\vspace{1ex}
 \begin{center}
@@
 
-To understand why developers prefer not use parallel test execution,
-we considered \numNonParallel{} subjects that do not use parallel
-configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
-quick survey to extent the comprehension about why developers do not
-use parallel configuration. \Luis{describe how we created the survey}.
-We first retrieve the last 20 commits from the project repository and
-got the developers e-mails. In total, we sent an e-mail to
-\emailsSent{} developers that recently contributed to the 
-\numNonParallel{} projects, and we did not found any e-mail from
-\Fix{??} projects using \CodeIn{git} tool.
-\Luis{Here I want to say that I could not found any valid e-mail using
-\textit{git log}}
-There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
-projects, and \emailsFalseAnswers{} developers was not able to 
-explain how the testing works or was not able to answer the survey.
-
-The survey sent was composed by three open questions and one closed
-question: (I) How long does it take for test to run in your
-environment? Can you briefly define your setup? (II) Do you confirm
-that your project does not run in parallel? (III) Select a reason for
-not using parallelization: (a) I did not know it was possible; (b) I
-was concerned with concurrency issues; (c) I use a continuous
-integration server; (d) Some other reason. Please elaborate.
+To answer this research question we surveyed developers involved in a
+selection of projects from our benchmark with time-consuming test
+suites.  The goal of the survey is to better comprehend developer's
+attitude towards the use of parallelism as a mechanism to speedup
+regression testing.  We surveyed developers from a total of
+\Fix{x=83-11-y} projects.  From the initial list of \numMedLong{}
+project, we discarded 11 projects that we knew a priori used
+parallelization, and \Fix{y} projects that we could not find
+developer's emails from commit logs.  From this list of projects, we
+mined potential participants for our study.  More precisely, we
+searched for developer's name and email from the last 20 commits to
+the corresponding project repository.  Using this approach, we
+identified a total of \emailsSent{} eligible participants.  Finally,
+we sent plain-text e-mails to those developers with the survey.  In
+total, \emailsAnswered{} developers replied but we discarded
+\emailsFalseAnswers{} replies with subjective answers.  Considering
+projects covered by the answers, a total of \emailsProjectsAnswered{}
+projects (\percEmailsProjectsAnswered{} of the total) were represented
+in those replies.  Note that multiple developers on each project
+received emails.  We sent the following set of questions to
+developers:
+
+\begin{enumerate}
+\item How long does it take for test to run in your environment? Can
+  you briefly define your setup?
+\item Do you confirm that your project does not run in parallel?
+\item\label{questionThree} Select a reason for not using parallelization:
+  \begin{enumerate}[label=\alph*)]
+  \item I did not know it was possible
+  \item I was concerned with concurrency issues
+  \item I use a continuous integration server
+  \item Some other reason. Please elaborate.
+  \end{enumerate}
+\end{enumerate}
 
@@
 %% \end{enumerate}
+
+\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+    \centering
+    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
+    \caption{\label{fig:rq5-answers}Summary of developer's answers to
+      question~\ref{questionThree}.}
+\end{wrapfigure}
+The goal of the first two questions is to identify potential
+discrepancies between the environment used to obtain our results and
+environment of the developers.  Overall, we found that \Fix{...}
+
+\Mar{... estou aqui ...}
 
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
-    \caption{\Luis{todo}\label{fig:rq5-answers}}
-\end{figure}
-
 \begin{center}
@@
 BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
 \bottomrule%
@@
 \midrule%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
 BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
@@
 %%  LocalWords:  outliers apache uber chaperone facebookarchive
-%%  LocalWords:  linkbench
+%%  LocalWords:  linkbench priori

### 2017-04-06 paper/evaluation.tex
adjusting times

--- 2017-04-06 paper/evaluation.tex
@@
 \midrule%
-Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.47m & 1.00x\\%
-Medium & Apache \textbf{Flink} & 10.02m & 2.57m & 3.90x\\%
-Long & Jenkins CI \textbf{Gerrit} Plugin & 76.32m & 40.31m &  1.89x\\%
-Medium & Spotify \textbf{Helios} & 3.70m & 1.63m & 2.28x\\%  
-Medium & \textbf{Javaslang} & 2.12m & 1.82m & 1.16x\\%
-Medium & \textbf{Jcabi} GitHub & 2.75m & 0.30m & \cellcolor{lightgray}9.01x\\%
+Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 1.02x\\%
+Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%
+Long & Jenkins CI \textbf{Gerrit} Plugin & 51.19m & 40.31m &  1.26x\\%
+Medium & Spotify \textbf{Helios} & 4.46m & 1.63m & 2.73x\\%  
+Medium & \textbf{Javaslang} & 2.18m & 1.82m & 1.19x\\%
+Medium & \textbf{Jcabi} GitHub & 2.76m & 0.30m &
+    \cellcolor{lightgray}9.2x\\%
 Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
-Medium & Apache \textbf{Log4J2} & 4.73m & 8.21m & \cellcolor{lightgray}0.58x\\%
-Medium & Jankotek \textbf{MapDB} & 10.51m & 8.58m & 1.23x\\%
+Medium & Apache \textbf{Log4J2} & 8.24m & 8.21m & 
+    \cellcolor{lightgray}1.00x\\%
+Medium & Jankotek \textbf{MapDB} & 10.06m & 8.58m & 1.17x\\%
 \midrule
@@
 
-The dimension adoption focuses on the usage of parallelism in
-open-source projects.  It evaluates (\numRQC) how often open-source
-projects use parallelization schemes and (\numRQE) how developers
-involved in costly projects, not using parallelization, perceive this
-technology.
+Research questions \numRQC{} and \numRQE{} investigate to which extent
+parallelization is used in practice.  It is important to investigate
+adoption as it is possible that developers may use alternative
+mechanisms to execute tests.
 
 \begin{itemize}
-    \item \numRQC. \textbf{\RQC{}}
+    \item \numRQC. \emph{\RQC}
 \end{itemize}
 
-To answer \numRQC{}, we selected all projects from the \medg{} and
-\longg{} groups, \ie, projects that ran in at least one minute.  This
-set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
+To answer \numRQC{}, we selected all projects that ran in at least one
+minute, \ie, projects from the \medg{} and \longg{} groups.  This set
+includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
 looked for dynamic and static manifestations of parallelism.
-
-%% The
-%% following section report results for each of these cases.
+Section~\ref{sec:rqC-1} and~\ref{sec:rqC-2} report results for each of
+these cases.
 
 \vspace{1ex}
-\subsubsection{Dynamic checking}
+\subsubsection{Test execution with parallelism enabled by default}
 \label{sec:rqC-1}
@@
 produce debug output and the option~\CodeIn{-DskipTests} to skip
-execution of tests.  We observed that only bootstrapping the Maven
-process suffices to discover which parallel configuration modes it
-will use to run tests.  According to Maven's
-documentation~\cite{maven-surefire-plugin}, a parallel configuration
-depends either on (1) the parameter \CodeIn{parallel} to define the
-parallelism mode within a JVM followed by the parameter
+execution of tests.  We observed that only bootstrapping execution
+suffices to discover which parallel configuration modes Maven will
+actually use.  According to Maven's
+documentation~\cite{maven-surefire-plugin}, any parallelism
+configuration depends either on (1) the parameter \CodeIn{parallel} to
+define the parallelism mode within a JVM followed by the parameter
 \CodeIn{threadCount} or (2) the parameter
@@
   in old versions of Maven Surefire} to define the number of forked
-JVMs.  As such, we captured, for each project, all related key-value
-pairs of Maven parameters and mapped those pairs to one of the
-possible parallelization modes.  For instance, if a given project
-contains a module with the parameter
+JVMs. For each execution, we capture theses parameters and their
+values to map to one of the possible parallelization modes.  For
+instance, if a given project contains a module with the parameter
 \CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
 \ForkSeq{} or \ForkParMeth{} depending on the presence and the value
-of the parameter \CodeIn{parallel}.  If the parameter
-\CodeIn{parallel} is set to \CodeIn{methods} the detected mode will be
-\ForkParMeth{}.  Large projects may contain several test suites
-distributed on different Maven modules potentially using different
-configurations.  For those cases, we collected the Maven output from
-each module discarding duplicates as to avoid inflating results. For
-instance, if a project contains two modules using the same
-configuration, we counted only one occurrence.
-
-\Mar{---- estou aqui}
+of the parameter \CodeIn{parallel} (\ie, the presence of
+\CodeIn{<parallel>methods</parallel>} results in the parallel mode
+\ForkParMeth{}).  Large projects may contain several test suites
+distributed on different Maven modules with different
+configurations. In this case, we collect the Maven output from each
+module discarding duplicates. For instance, if a project contains two
+modules with the same parallelism mode, we count only one occurrence
+to not inflate our results.
 
@@
 create in Maven multiple configurations in the same build file and
-select dynamically which one should be used.  We automatically parsed
-\Fix{X} build files and we used the same approach to classify the
-parsed configurations as in our previous analysis. Initially, we
-noticed that our approach was unable to infer the parallel mode in
-some projects because these projects do not declare a static value in
-some parameters (\eg,
-\CodeIn{<parallel>\$\{parallel.type\}</parellel>}). For these projects,
-it is required to inform additional parameters to enable the parallel
-mode in the command line (\eg, \CodeIn{mvn test
--Dparallel.type=classesAndMethods}). \Jbc{We wouldn't have FALSE
-NEGATIVES if we considered this $\rightarrow$}To handle this case, we
-considered all valid values for the parameter.
+select dynamically which one should be used.
+
+\Mar{I have no clue what you mean here... Why should I care about
+  space on build files?  I thought we did this check
+  for every project and module.  $\rightarrow$}\Fix{To reduce the
+  space of \Fix{x} build files, we considered a subset of \Fix{y}
+  build files with the following criteria}: the given \pomf{} file has
+\CodeIn{maven-surefire-plugin} plugin declaration and it has an
+explicit \CodeIn{configuration} declaration. We automatically parsed
+these \Fix{y} files and we used the same approach to classify the
+parallelization mode from the parsed configurations as in our previous
+analysis. In an initial analysis, we noticed that some projects do not
+declare a static value in some parameters, instead, these projects
+inform the actual value in the command line. To handle this case, we
+computed all valid values for the parameter.
 
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
-    \caption{\Luis{todo}\label{fig:rq5-answers}}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.25\textwidth]{plots/survey.pdf}
+     \caption{\Luis{todo}}
 \end{figure}
@@
 \end{center}
-
-\subsection{Threats to Validity}
-
-\Fix{Jean and Luis should write this. This is really important for an
-  empirical study.  You need to undertand main sources of threat:
-  internal, external, and construct.  Read this document for the
-  basics: http://www.statsdirect.com/help/basics/validity.htm.  Read
-  this document for an example:
-  http://www.cin.ufpe.br/~damorim/publications/perez-etal-icst2017.pdf}
-
-\subsection{Lessons Learned}
-
-\Fix{Marcelo can write this...}
 

### 2017-04-06 paper/evaluation.tex
adjusting cell colors

@@
 \midrule%
-Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 1.02x\\%
+Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 
+    \cellcolor{lightgray}1.02x\\%
 Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%

### 2017-04-06 paper/evaluation.tex
partial changes

@@
 
-To understand why developers prefer not use parallel test execution,
+To answer this research question we surveyed developers involved in a
+selection of projects listed in Section~\ref{sec:rqC-1}.  The goal of
+the survey is to better comprehend developer's attitude towards use of
+parallelism to speedup regression testing in open-source projects.
+
 we considered \numNonParallel{} subjects that do not use parallel
-configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
-quick survey to extent the comprehension about why developers do not
-use parallel configuration. \Luis{describe how we created the survey}.
+configuration as default test execution from
+
 We first retrieve the last 20 commits from the project repository and

### 2017-04-06 paper/evaluation.tex
first par. rq5

--- 2017-04-06 paper/evaluation.tex
@@
 
-To understand why developers prefer not use parallel test execution,
-we considered \numNonParallel{} subjects that do not use parallel
-configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
-quick survey to extent the comprehension about why developers do not
-use parallel configuration. \Luis{describe how we created the survey}.
-We first retrieve the last 20 commits from the project repository and
-got the developers e-mails. In total, we sent an e-mail to
-\emailsSent{} developers that recently contributed to the 
-\numNonParallel{} projects, and we did not found any e-mail from
-\Fix{??} projects using \CodeIn{git} tool.
-\Luis{Here I want to say that I could not found any valid e-mail using
-\textit{git log}}
-There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
-projects, and \emailsFalseAnswers{} developers was not able to 
-explain how the testing works or was not able to answer the survey.
+To answer this research question we surveyed developers involved in a
+selection of projects from our benchmark with time-consuming test
+suites.  The goal of the survey is to better comprehend developer's
+attitude towards the use of parallelism as a mechanism to speedup
+regression testing.  We surveyed developers from a total of
+\Fix{x=83-11-y} projects.  From the initial list of \numMedLong{}
+project, we discarded 11 projects that we knew a priori used
+parallelization, and \Fix{y} projects that we could not find
+developer's emails from commit logs.  From this list of projects, we
+mined potential participants for our study.  More precisely, we
+searched for developer's name and email from the last 20 commits to
+the corresponding project repository.  Using this approach, we
+identified a total of \emailsSent{} eligible participants.  Finally,
+we sent plain-text e-mails to those developers with the survey.  In
+total, \emailsAnswered{} developers replied but we discarded
+\emailsFalseAnswers{} replies with subjective answers.  Considering
+projects covered by the answers, a total of \emailsProjectsAnswered{}
+projects (\percEmailsProjectsAnswered{} of the total) were represented
+in those replies.  Note that multiple developers on each project
+received emails.
+
+\Mar{----- estou aqui}
 

### 2017-04-06 paper/evaluation.tex
second par rq5

@@
 in those replies.  Note that multiple developers on each project
-received emails.
-
-\Mar{----- estou aqui}
-
-The survey sent was composed by three open questions and one closed
-question: (I) How long does it take for test to run in your
-environment? Can you briefly define your setup? (II) Do you confirm
-that your project does not run in parallel? (III) Select a reason for
-not using parallelization: (a) I did not know it was possible; (b) I
-was concerned with concurrency issues; (c) I use a continuous
-integration server; (d) Some other reason. Please elaborate.
+received emails.  We sent the following set of questions to
+developers:
+
+\begin{enumerate}
+\item How long does it take for test to run in your environment? Can
+  you briefly define your setup?
+\item Do you confirm that your project does not run in parallel?
+\item\label{questionThree} Select a reason for not using parallelization:
+  \begin{enumerate}[label=\alph*)]
+  \item I did not know it was possible
+  \item I was concerned with concurrency issues
+  \item I use a continuous integration server
+  \item Some other reason. Please elaborate.
+  \end{enumerate}
+\end{enumerate}
 
@@
 answered the last question, or did not knew an answer.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
-    \caption{\Luis{todo}\label{fig:rq5-answers}}
-\end{figure}
 

### 2017-04-06 paper/evaluation.tex
added intro of rq6

@@
 \begin{itemize}
-    \item \textbf{\RQF{}}
+    \item \numRQF{}. \textbf{\RQF{}}
 \end{itemize}
+
+To answer \numRQF{}, we considered the top ten projects with
+long-running test suites and all parallel modes (see
+Section~\ref{sec:modes}). In this experiment, we run the test suites
+with different parallel modes and evaluated the average time cost and
+rate of failing tests. To avoid noise, we carefully selected only
+subjects with nonfailing tests to avoid noise in our measurements.
+
+\Fix{Elaborate results from efficiency}
+
+Figure~\ref{tab:rq6-efficiency} summarizes our findings.
 
@@
 \end{figure}
+
+\Fix{Elaborate results about flakiness}
+
+Figure~\ref{tab:rq6-flaky} summarizes our findings.
 
@@
 BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
 \bottomrule%
 \end{tabular}}
-\caption{\Fix{Tabela de flakyness}}
-\label{tab:rq6-efficiency}
+\caption{\Fix{Tabela de flakiness}}
+\label{tab:rq6-flaky}
 \end{figure}
+
+\Fix{discuss trade-offs and elaborate conclusion....}
 

### 2017-04-06 paper/evaluation.tex
RQ6 - subsection for tradeoffs
pass on RQ3

@@
 
-To answer \numRQD{}, we considered \emph{all} \numProjectsPar{}
-subjects from our benchmark that use parallelization by default in
-Maven to run tests.  Section~\ref{sec:rqC-1} describes in detail the
-methodology we used to find these subjects. For each project, the
-speedup (or slowdown) corresponds to the ratio ($T_s/T_p$) between the
-elapsed time of a sequential execution ($T_s$) and the elapsed time of
-a corresponding parallel execution ($T_p$), obtained as described in
-the script from Figure~\ref{fig:mvn-execution}.  As usual, a ratio
-above 1x denotes speedup and a ratio below 1x denotes slowdown.
-
-%% For each project, we modified the existing configurations to disable
-%% the parallel test execution. In addition, we verified that both
+To answer \numRQD{}, we considered \numProjectsPar{} subjects from our
+benchmark that use parallelization \emph{by default} when running
+tests.  In those projects, parallelization is active without passing
+any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
+methodology we used to find these subjects and
+Section~\ref{seq:rq6-tradeoffs}, we verified that both
 %% executions produce the same outcome to eliminate noise from failing
@@
 execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
-associated with parallel execution.
+associated with parallel execution.   As usual, a ratio
+above 1x denotes speedup and a ratio below 1x denotes slowdown.
 
 Results indicate that, on average, parallel execution was
-\avgSpeedup{} times faster compared to sequential execution.  We noted
-three extreme cases: \CodeIn{Chaos}, \CodeIn{Jcabi} and \CodeIn{Log4J2}.
-The first, the default configuration is \textbf{C2}, however, the test is
-composed of takes $>$99\% of the test time. In this case, when running
-in sequential the execution time is almost the same as the parallel
-execution.
-The second when using the default parallel configuration, runs a
-\textbf{C3} configuration with small test classes and big test
-methods. In this case, a high slowdown is noticed when running those
-big methods sequentially.
-The third, runs parallel configuration in \Fix{80\%} of the project
-modules, however, the test time is dominated by one of the
-sequentially running modules.
-\Luis{$\leftarrow$ rework this} \Fix{falar
-  sobre o resultado geral dos speedups - elaborar menor e maior
-  speedup... acho que so vale a pena discutir quando tiver conviccao
-  dos 2 casos}
+\avgSpeedup{} times faster compared to sequential execution.  Three
+cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
+\CodeIn{Log4J2}.  No significant speedup was observed in
+\CodeIn{Chaos}, a project with only three test classes, of which one
+monopolizes the bulk of test execution time.  This project uses
+configuration \ParClassSeqMeth{}, which runs test classes in parallel
+and test methods, declared in each class, sequentially.  Consequently,
+speedup cannot be obtained as the cost of the single expensive test
+class cannot be broken down with the selected configuration.  Although
+project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
+results obtained are very different compared to \CodeIn{Chaos}.  The
+speedup observed in \CodeIn{Jcabi} was the highest amongst all
+projects.  This project contains test classes with a small number of
+test methods and several methods in those classes are time-consuming.
+As result, the CPUs available for testing are kept occupied for the
+most part during test execution.  Finally, we note that parallel
+execution in \CodeIn{Log4J2} was innefective.  We found that Maven
+invokes several test modules in this project but the test modules that
+dominate execution time run sequentially by default.
+
+%% The third, runs parallel configuration in
+%% \Fix{80\%} of the project modules, however, the test time is dominated
+%% by one of the sequentially running modules.  \Luis{$\leftarrow$ rework
+%%   this} \Fix{falar sobre o resultado geral dos speedups - elaborar
+%%   menor e maior speedup... acho que so vale a pena discutir quando
+%%   tiver conviccao dos 2 casos}
 
@@
   \begin{minipage}{8cm}
-      \textit{Answering \numRQD{}:}~\emph{Overall, results indicate
-      that the speedup obtained with parallelization is
-      \Fix{$\sim$x\%} (in average) for \Fix{\%} of the projects
-      (\Fix{x} out of \Fix{w}). }
+    \textit{Answering \numRQD{}:}~\emph{ The average speedup observed
+      with default configurations of parallelization was
+      \avgSpeedup{}x.}
   \end{minipage}
@@
 
+\subsubsection{Trade-offs}
+\label{seq:rq6-tradeoffs}
 \Fix{discuss trade-offs and elaborate conclusion....}

### 2017-04-06 paper/evaluation.tex
adjusting rq5

@@
 regression testing.  We surveyed developers from a total of
-\Fix{x=83-11-y} projects.  From the initial list of \numMedLong{}
+\emailsProjects{} projects.  From the initial list of \numMedLong{}
 project, we discarded 11 projects that we knew a priori used
-parallelization, and \Fix{y} projects that we could not find
+parallelization, and \discartedProjects{} projects that we could not find
 developer's emails from commit logs.  From this list of projects, we

### 2017-04-06 paper/evaluation.tex
pass on rq6

@@
 
+\subsection{Tradeoffs}
+\label{sec:rq6-tradeoffs}
+
+This dimension assesses the impact of using distinct parallel
+configurations on test flakiness (negative impact) and speedup
+(positive impact).  Recall that increased resource contention obtained
+with parallelism can lead to concurrency issues such as data races.
+Hence, flakiness and speedup are contradictory forces that drive
+configuration selection.  Note also that Section~\ref{sec:rqD}
+evaluated variable speedup in isolation, focused on project
+configuration where parallelism is used by default.
+
 \begin{itemize}
@@
 
-To answer \numRQF{}, we considered the top ten projects with
-long-running test suites and all parallel modes (see
-Section~\ref{sec:modes}). In this experiment, we run the test suites
-with different parallel modes and evaluated the average time cost and
-rate of failing tests. To avoid noise, we carefully selected only
-subjects with nonfailing tests to avoid noise in our measurements.
+To answer this research question we selected projects as follows.  To
+avoid noise in our measurements, we first discarded projects
+containing failing tests (note that we measure flakiness).  Then, we
+sorted projects in descending order of their execution times and
+selected the top ten projects from the resulting set.
+
+In this experiment, the baseline technique is \Seq{} and the
+evaluation techniques are all the configuration modes listed in
+Section~\ref{sec:modes}.  We ran each of the technique for \Fix{X}
+times reporting elapsed time and number of failing tests each time.
+We reported average results.
 
@@
 \end{figure}
-
-\subsubsection{Trade-offs}
-\label{seq:rq6-tradeoffs}
-\Fix{discuss trade-offs and elaborate conclusion....}
 

### 2017-04-06 paper/evaluation.tex
minor change
two paragraphs dimension tradeoffs

@@
 \newcommand{\RQF}{To which extent parallel execution configurations affect testing
-  cost and flakiness?}
+  costs and flakiness?}
 
@@
 identified a total of \emailsSent{} eligible participants.  Finally,
-we sent plain-text e-mails to those developers with the survey.  In
+we sent plain-text e-mails, containing the survey, to those developers.  In
 total, \emailsAnswered{} developers replied but we discarded
@@
 To answer this research question we selected projects as follows.  To
-avoid noise in our measurements, we first discarded projects
-containing failing tests (note that we measure flakiness).  Then, we
-sorted projects in descending order of their execution times and
-selected the top ten projects from the resulting set.
-
-In this experiment, the baseline technique is \Seq{} and the
-evaluation techniques are all the configuration modes listed in
-Section~\ref{sec:modes}.  We ran each of the technique for \Fix{X}
-times reporting elapsed time and number of failing tests each time.
-We reported average results.
+avoid noise in measuring flakiness we first discarded projects
+containing failing tests.  Then, we sorted projects in descending
+order of their execution times and selected the top ten projects from
+the resulting set.  In this experiment, the baseline technique is
+sequential execution (\ie{}, configuration \Seq{}) and the evaluation
+techniques consist of all configuration modes listed in
+Section~\ref{sec:modes}.  We ran each of those techniques for \Fix{X}
+times computing elapsed time and number of failing tests in each run.
+Figures~\ref{tab:rq6-efficiency} and~\ref{tab:rq6-flaky} summarize the
+results we obtained.
 
 \Fix{Elaborate results from efficiency}
-
-Figure~\ref{tab:rq6-efficiency} summarizes our findings.
 
@@
 \end{figure}
-
-\Fix{Elaborate results about flakiness}
-
-Figure~\ref{tab:rq6-flaky} summarizes our findings.
 

### 2017-04-06 paper/evaluation.tex
quick pass on RQ5

@@
 discrepancies between the environment used to obtain our results and
-environment of the developers.  Overall, we found that \Fix{...}
-
-\Mar{... estou aqui ...}
-
-Based on the answers from the developers, we confirmed that most of
-the subjects execution time was compatible with the results found at
-Section~\ref{sec:rqA}. From Question I, we noticed that \emailsCI{}
+the environment of developers.  Overall, we found that \Fix{...}
+
+\Mar{... estou trabalhando neste texto ...}
+
+Based on the answers from developers, we confirmed that most of the
+subjects execution time was compatible with the results found at
+Section~\ref{sec:rqA}.
+
+\Fix{revise...} From Question I, we noticed that \emailsCI{}
 developers confirmed the use of an continuous integration server to
@@
 not described their environment.
-From Question II, we noticed that \emailsSequential{} confirmed that
-they do not execute tests in parallel, and \emailsParallel{} did not
-confirmed, however, the developers confirmed the need of an extra
-parameter at the command line to execute in parallel.
+
+Considering question 2, we found that \emailsSequential{} of the
+\emailsProjectsAnswered{} projects indeed did not execute tests in
+parallel.  The discrepancy is justified by cases where neither of our
+checks (static or dynamic) could detect presence of parallelism.  \Fix{elaborate}
+
+%% did not confirmed, however,
+%% the developers confirmed the need of an extra parameter at the command
+%% line to execute in parallel.
+
 From Question III, \emailsA{} of developers do not know that

### 2017-04-06 paper/evaluation.tex
another pass on rq5

@@
 \end{wrapfigure}
-The goal of the first two questions is to identify potential
-discrepancies between the environment used to obtain our results and
-the environment of developers.  Overall, we found that \Fix{...}
-
-\Mar{... estou trabalhando neste texto ...}
-
-Based on the answers from developers, we confirmed that most of the
-subjects execution time was compatible with the results found at
-Section~\ref{sec:rqA}.
-
-\Fix{revise...} From Question I, we noticed that \emailsCI{}
-developers confirmed the use of an continuous integration server to
-run tests, which \emailsDistributed{} of them is using a distributed
-continuous integration server as an alternative to parallelism.
-From a local development, \emailsLocal{} developers answered that they
-run tests in a local machine, and \emailsNotDescribed{} developers did
-not described their environment.
+%% One of the goals of the first questions is to identify potential
+%% discrepancies between our experimental environment and the environment
+%% of developers.  Overall, we found that \Fix{...}
+
+Considering question 1, we confirmed that execution time was
+compatible with the results we reported in Section~\ref{sec:rqA}.
+Furthermore, \emailsCI{} of the participants indicated the use of
+Continuous Integration (CI) to run tests, with \emailsDistributed{} of
+these participants reporting that test suites were modularized and
+those modules were tested independetly in CI servers through different
+parameters. A total of \emailsLocal{} participants answered that they
+do run tests in their local machines.  Note that CI does not preclude
+low-level parallelization.  For example, installations of open-source
+CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated servers will
+still benefit from running tests faster, using test suite
+parallelization.
+
+% \emailsNotDescribed{} developers did not described their environment.
 
@@
 \emailsProjectsAnswered{} projects indeed did not execute tests in
-parallel.  The discrepancy is justified by cases where neither of our
+parallel.  The mismatch is justified by cases where neither of our
 checks (static or dynamic) could detect presence of parallelism.  \Fix{elaborate}
-
+\Luis{i looked at those 6 weird projects, and 1 of them contains a
+false-negative from rq4, one of them considered the distributed CI
+server as parallelism, 2 of them had a custom test runner, and 2 of
+them implements parallelism inside the test (they test two+ things in
+one test method.}
 %% did not confirmed, however,

### 2017-04-07 paper/evaluation.tex
pass on rq5

@@
 %% \end{enumerate}
-
-\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
-    \centering
-    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
-    \caption{\label{fig:rq5-answers}Summary of developer's answers to
-      question~\ref{questionThree}.}
-\end{wrapfigure}
 %% One of the goals of the first questions is to identify potential
@@
 these participants reporting that test suites were modularized and
-those modules were tested independetly in CI servers through different
+those modules are tested independetly in CI servers through different
 parameters. A total of \emailsLocal{} participants answered that they
-do run tests in their local machines.  Note that CI does not preclude
-low-level parallelization.  For example, installations of open-source
-CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated servers will
-still benefit from running tests faster, using test suite
-parallelization.
+do run tests in their local machines.  Note, however, that CI does not
+preclude low-level parallelization.  For example, installations of
+open-source CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated
+servers will still benefit from running tests faster through low-level
+test suite parallelization.
 
@@
 
-Considering question 2, we found that \emailsSequential{} of the
-\emailsProjectsAnswered{} projects indeed did not execute tests in
-parallel.  The mismatch is justified by cases where neither of our
-checks (static or dynamic) could detect presence of parallelism.  \Fix{elaborate}
-\Luis{i looked at those 6 weird projects, and 1 of them contains a
-false-negative from rq4, one of them considered the distributed CI
-server as parallelism, 2 of them had a custom test runner, and 2 of
-them implements parallelism inside the test (they test two+ things in
-one test method.}
+Considering question 2, participants responded that
+\emailsSequential{} of the \emailsProjectsAnswered{} projects did not
+execute tests in parallel.  This mismatch is justified by cases where
+neither of our checks (static or dynamic) could detect presence of
+parallelism.  \Fix{elaborate} \Luis{i looked at those 6 weird
+  projects, and 1 of them contains a false-negative from rq4, one of
+  them considered the distributed CI server as parallelism, 2 of them
+  had a custom test runner, and 2 of them implements parallelism
+  inside the test (they test two+ things in one test method.}
 %% did not confirmed, however,
@@
 
-From Question III, \emailsA{} of developers do not know that
-parallelism is an available configuration for Maven Surefire,
-\emailsB{} of developers do not use parallel testing concerned with
-concurrency issues, \emailsD{} of developers uses a continuous
-integretion server for run tests while working \Luis{here I want to
-say that they use it for something like "non-blocking testing" while
-developing in a local machine}, \emailsD{} of developers thinks that
-it is not worthy the effort, and \emailsNA{} of developers did not
-answered the last question, or did not knew an answer.
+\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+    \centering
+    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
+    \caption{\label{fig:rq5-answers}Summary of developer's answers to
+      question~\ref{questionThree}.}
+\end{wrapfigure}
+Considering question 3, \emailsA{} of developers who answered the
+survery did not know that parallelism was available in Maven,
+\emailsB{} of developers mentioned that they did not use parallelism
+because of concerns with concurrency issues, \emailsD{} of developers
+uses a continuous integretion server for run tests while working
+\Luis{here I want to say that they use it for something like
+  "non-blocking testing" while developing in a local machine},
+\emailsD{} of developers thinks that it is not worthy the effort, and
+\emailsNA{} of developers did not answered the last question, or did
+not knew an answer.
 

### 2017-04-07 paper/evaluation.tex
pass on rq5

@@
 neither of our checks (static or dynamic) could detect presence of
-parallelism.  \Fix{elaborate} \Luis{i looked at those 6 weird
-  projects, and 1 of them contains a false-negative from rq4, one of
-  them considered the distributed CI server as parallelism, 2 of them
-  had a custom test runner, and 2 of them implements parallelism
-  inside the test (they test two+ things in one test method.}
+parallelism.
+
+We investigated this six projects further, and one of them contained a
+false-negative result from \numRQC{}, which means that a configuration file
+is compacted inside a Java container. One of them considered a
+distributed CI server as parallelism. Two of those projects had a
+custom JUnit test runner, which handles the parallelism itself. The
+last two projects run the parallelism inside the test method, one runs
+a manually created Thread to run some tests, and the other runs in
+parallel by using Java 8 collection streams, that allows the
+developers to iterate over a list in parallel.
+
 %% did not confirmed, however,

### 2017-04-07 paper/evaluation.tex
almost done with RQ5

@@
     \caption{\label{fig:rq5-answers}Summary of developer's answers to
-      question~\ref{questionThree}.}
+      survey question~\ref{questionThree}.}
 \end{wrapfigure}
-Considering question 3, \emailsA{} of developers who answered the
-survery did not know that parallelism was available in Maven,
-\emailsB{} of developers mentioned that they did not use parallelism
-because of concerns with concurrency issues, \emailsD{} of developers
-uses a continuous integretion server for run tests while working
-\Luis{here I want to say that they use it for something like
-  "non-blocking testing" while developing in a local machine},
-\emailsD{} of developers thinks that it is not worthy the effort, and
-\emailsNA{} of developers did not answered the last question, or did
-not knew an answer.
+Considering question 3, the distribution of answers was as follows.  A
+total of \emailsA{} of the \emailsProjectsAnswered{} developers who
+answered the survey did not know that parallelism was available in
+Maven (option ``a''), \emailsB{} of developers mentioned that they did
+not use parallelism concerned with possible concurrency issues (option
+``b''), \emailsD{} of developers mentioned that continuous integration
+services sufficed to provide timely feedback while running only smoke
+tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
+  I want to say that they use it for something like "non-blocking
+  testing" while developing in a local machine}, and \emailsD{} of
+developers who provided an alternative answer (option ``d'') mentioned
+that using parallelism was not worth the effort of preparing the test
+suites to take advantage of available processing power.  A total of
+\emailsNA{} of participants did not answer the last question of the
+survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
+the distribution of answers.
 
@@
 	\begin{minipage}{8cm}
-		\textit{Answering \numRQE{}:~\emph{\Luis{summarize
-		findings...}}}
+	  \textit{Answering \numRQE{}:}~\emph{Results suggest that dealing
+       with concurrency issues (\ie{}, the extra work to organize test
+       suite to safely explore concurrency) was the principal reason
+       for developers not investing in parallelism.  Other reasons
+       included availability of continuous integration services and
+       unfamiliarity with the technology.}
 	\end{minipage}

### 2017-04-07 paper/evaluation.tex
pass on rq5

--- 2017-04-07 paper/evaluation.tex
@@
 We investigated this six projects further, and one of them contained a
-false-negative result from \numRQC{}, which means that a configuration file
-is compacted inside a Java container. One of them considered a
+false-negative result from \numRQC{}, which means that a \pomf{}
+is compacted inside a \CodeIn{jar} file. One of them considered a
 distributed CI server as parallelism. Two of those projects had a

### 2017-04-07 paper/evaluation.tex
done rq5

@@
 
-Considering question 2, participants responded that
-\emailsSequential{} of the \emailsProjectsAnswered{} projects did not
-execute tests in parallel.  This mismatch is justified by cases where
-neither of our checks (static or dynamic) could detect presence of
-parallelism.
-
-We investigated this six projects further, and one of them contained a
-false-negative result from \numRQC{}, which means that a \pomf{}
-is compacted inside a \CodeIn{jar} file. One of them considered a
-distributed CI server as parallelism. Two of those projects had a
-custom JUnit test runner, which handles the parallelism itself. The
-last two projects run the parallelism inside the test method, one runs
-a manually created Thread to run some tests, and the other runs in
-parallel by using Java 8 collection streams, that allows the
-developers to iterate over a list in parallel.
+Considering question 2, the answers we collected show that six of the
+\emailsProjectsAnswered{} projects execute tests in parallel.  This
+mismatch is justified by cases where neither of our checks (static or
+dynamic) could detect presence of parallelism.  A closer look at these
+projects revealed that one of them contained a \emph{pom.xml} file
+encapsulated in a jar file (similar case as reported in
+Section~\ref{sec:rqC-2}), in one of the projects the particpant
+considered that distributed CI was a form of parallelism, and in four
+projects parallelism was implemented natively~---~two projects
+implemented concurrency control with custom JUnit test runners and two
+other projects implemented concurrency within test methods.  Note
+that, considering four extra cases (ignored two distributed CI cases),
+the usage of parallelization increases from \percentParallel{} to
+\percentParallelUpdated{}.  However, we do not consider this change
+significant enough to modify our conclusion about practical adoption
+of parallelization (\numRQC{}).
+
+%% , one runs a manually created Thread to run some
+%% tests, and the other runs in parallel by using Java 8 collection
+%% streams, that allows the developers to iterate over a list in
+%% parallel.
 

### 2017-04-07 paper/evaluation.tex
minor tweaks in eval.F

@@
 with parallelism can lead to concurrency issues such as data races.
-Hence, flakiness and speedup are contradictory forces that drive
-configuration selection.  Note also that Section~\ref{sec:rqD}
-evaluated variable speedup in isolation, focused on project
-configuration where parallelism is used by default.
+Flakiness and speedup are contradictory forces that drive
+configuration selection.  Furthermore, note that Section~\ref{sec:rqD}
+evaluated speedup in isolation, focused on projects configured to use
+parallelism by default.
 

### 2017-04-07 paper/intro.tex
pass on abstract and part of intro

@@
 testing infrastructures~---~led us to investigate the usage of
-parallelism for running tests in public open-source projects.
+parallelism to speed up test execution.  This paper reports on an
+empirical study we conducted to analyze the usage and impact of
+low-level parallelization in speeding up testing for open-source
+projects.  This is a relevant problem given the tremendous popularity
+of open-source development and regression testing
+research~\cite{yoo-harman-stvr2012}.
 
@@
 
-This paper reports on an empirical study we conducted to analyze the
-impact of low-level parallelization to speedup testing in open-source
-projects.  This is a relevant problem given the tremendous popularity
-of open-source development and regression testing
-research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
-considered in this study are as follows: potential, effectiveness,
-adoption, and tradeoffs.  Each dimension focuses on one aspect of our
-study.  The dimension \textbf{potential} measures the potential of
-parallelization to reduce testing costs.  In the limit,
-parallelization would be fruitless if all projects used short-running
-test suites or if the bulk of execution cost was dominated by a
-relatively small number of tests in the suite.  The dimension
+The dimensions of analysis we considered in this study are as follows:
+potential, effectiveness, adoption, and tradeoffs.  Each dimension
+focuses on one aspect of our study.  The dimension \textbf{potential}
+measures the potential of parallelization to reduce testing costs.  In
+the limit, parallelization would be fruitless if all projects used
+short-running test suites or if the bulk of execution cost was
+dominated by a single test in the suite.  The dimension
 \textbf{effectiveness} measures the observed impact of
@@
 resistance to the technology and its reasons.  Finally, the dimension
-\textbf{tradeoff} evaluates the issues and benefits associated
+\textbf{tradeoffs} evaluates the issues and benefits associated
 with\Comment{running test suites with} different parallel
@@
 test cost and test flakiness, which is caused by the non-determinism
-resulted from running tests in different schedulings. Discovering
-Pareto-efficient~\cite{hwang-masud-1979} configurations is important
-to guide practitioners and future developments in this area.
+resulted from running test methods and classes in different
+orderings.
+
+%% Discovering Pareto-efficient~\cite{hwang-masud-1979}
+%% configurations is important to guide practitioners and future
+%% developments in this area.
 

### 2017-04-07 paper/intro.tex
pass on intro

@@
 proportional to the cost reduction that parallelization brings.  In
-the limit, the overhead of spawning virtual machines or threads can
-even result in added cost.  The dimension \textbf{adoption} evaluates
-(i) how often open-source projects use parallelization schemes and
-(ii) how developers involved in costly projects (not using test suite
-parallelization) perceive this technology.  It is important to measure
-resistance to the technology and its reasons.  Finally, the dimension
-\textbf{tradeoffs} evaluates the issues and benefits associated
-with\Comment{running test suites with} different parallel
-configurations.  Note that the configuration choice can affect both
-test cost and test flakiness, which is caused by the non-determinism
-resulted from running test methods and classes in different
-orderings.
+the limit, however, the overhead of spawning virtual machines or
+threads can even result in added cost.  The dimension
+\textbf{adoption} evaluates (i) how often open-source projects use
+parallelization schemes and (ii) how developers involved in costly
+projects (not using test suite parallelization) perceive this
+technology.  It is important to measure resistance to the technology
+and its reasons.  Finally, the dimension \textbf{tradeoffs} evaluates
+the issues and benefits associated with\Comment{running test suites
+  with} different parallel configurations.  Note that the
+configuration choice can affect both test cost and test flakiness,
+which is caused by the non-determinism resulted from running test
+methods and classes in different orderings.
 
@@
 %% developments in this area.
-
-\Mar{organize according to each of these dimensions...$\rightarrow$}
 
@@
 
-%% RQ1 + RQ2
+\subsection{Summary of ``Potential'' results}
+
 We selected \numSubjs{} popular Java projects from \github{}
@@
 methodology to select subjects and to isolate our experiments from
-environmental noise.  In summary, results indicate that $\sim$21\% of
-the test suites take at least 1m to run and $\sim$8\% of the test
-suites take at least 5m to run.  Considering all the \numMedLong{}
-projects in the $>$1m group (\percentMedLongRunning{} of
-\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.}, the
-average execution time is \averageMedLongRunning{}.  Results also show
-that individual tests are typically short-running, taking often less
-than half a second to run.  Furthermore, we found that only in rare
-cases few test cases monopolize execution cost associated with each
-test suite.  Overall, these results suggest that test suite
-parallelization has the potential to optimize these test suites.
+environmental noise.  Results indicate that nearly
+\percentMedLongRunning{} of the projects take at least 1m to run their
+test suites and \percentLongRunning{} of the projects take at least 5m
+to run their suites.  Considering the \numMedLong{} projects in those
+two groups, the average execution time is \averageMedLongRunning{}.
+Results also show that individual tests are typically short-running,
+taking often less than half a second to run.  Furthermore, we found
+that only in rare cases few test cases monopolize execution cost
+associated with each test suite.  \emph{Overall, our results suggest
+  that test suite parallelization has the potential to optimize test
+  suites.}
 
-%%RQ3
-Given the high execution cost associated with a significant number of
-\github{} projects, we decided to investigate usage of test
-suite parallelization in practice.  It is important to note that modern build
-systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
-accelerate test execution (see Section~\ref{sec:modes}).  To find how
-popular these features are in practice, we first analyzed build files
-\emph{statically}.  Considering the $>$1m group of projects
-(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
-them use some parallelization option.  Considering those projects that
-take more than 5m to run (\numLong{} in total), usage of parallelism
-increases to 59\% (19/\numLong{}).  Furthermore, we found that
-``forking'' virtual machines was the most prevalent parallel mode used
-in practice.  This mode is used twice as much as any other mode used.
-Important to note that ``forking VMs'' is perhaps the simplest of the
-parallelization modes~--~it is provided by the build system as opposed
-to the testing framework.  This result suggests that datarace
-flakiness~\cite{luo-etal-fse2014} may be a concern to users as
-``forking'' does not exploit thread-level concurrency within each VM,
-which can create contention on data reachable from the static
-area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
-creates independent processes (\ie{}, Java VM instances) and executes
-tests sequentially within each process. \Mar{why 32-19 did not use
-  parallelization?}
+\subsection{Summary of ``Effectiveness'' results}
 
-\Fix{...Discuss impact...}\Mar{what about free services (jenkins)?
-  how much can you scale execution and how expensive would that be?}
+As to avoid introduction of unintended noise when measuring time, we
+evaluated effectiveness on projects that we knew a priori ran their
+test suite in parallel by default.  Results indicate that the average
+speedup of parallelization was \avgSpeedup{}x.  Although we found
+cases with very high speedups (\eg{}, 9.2x), we found some cases where
+speedups were insignificant.  \emph{Overall, our results suggest that
+  it may not be obvious to achieve huge speedups with test suite
+  parallelization.}
+
+\subsection{Summary of ``Adoption'' results}
+
+We considered two aspects in measuring adoption of the technology.
+First, we analyzed quantitatively current usage of parallelism in
+open-source projects.  Then, we investigated the key reasons that
+justify resistance of developers in using test suite parallelization.
+For the quantitative analysis we checked both statically (parsing
+build files) and dynamically (monitoring execution of build files) for
+the presence of parallelization.  Considering only those projects that
+take longer than a minute to run their test suites, we found that only
+\percentParallel{} of them use parallelism.  When considering the
+feedback received from developers involved in those projects we
+realized the proportion should was a bit higher, of
+\percentParallelUpdated{}, but still relatively low.  For the
+qualitative analysis we surveyed developers from a selection of costly
+projects that did not use parallelization.  Section~\ref{sec:rqE}
+details our selection methodology. \emph{Results indicate that dealing
+  with concurrency issues related with parallelization (in particular,
+  the extra work to organize test suite to safely explore concurrency)
+  was the main barrier for adoption.  Other reasons included
+  availability of continuous integration services and unfamiliarity
+  with the technology.}
+
+%% %%RQ3
+%% Given the high execution cost associated with a significant number of
+%% \github{} projects, we decided to investigate usage of test
+%% suite parallelization in practice.  It is important to note that modern build
+%% systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
+%% accelerate test execution (see Section~\ref{sec:modes}).  To find how
+%% popular these features are in practice, we first analyzed build files
+%% \emph{statically}.  Considering the $>$1m group of projects
+%% (\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
+%% them use some parallelization option.  Considering those projects that
+%% take more than 5m to run (\numLong{} in total), usage of parallelism
+%% increases to 59\% (19/\numLong{}).  Furthermore, we found that
+%% ``forking'' virtual machines was the most prevalent parallel mode used
+%% in practice.  This mode is used twice as much as any other mode used.
+%% Important to note that ``forking VMs'' is perhaps the simplest of the
+%% parallelization modes~--~it is provided by the build system as opposed
+%% to the testing framework.  This result suggests that datarace
+%% flakiness~\cite{luo-etal-fse2014} may be a concern to users as
+%% ``forking'' does not exploit thread-level concurrency within each VM,
+%% which can create contention on data reachable from the static
+%% area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
+%% creates independent processes (\ie{}, Java VM instances) and executes
+%% tests sequentially within each process. \Mar{why 32-19 did not use
+%%   parallelization?}
+
+\subsection{Summary of ``Tradeoff'' results}
+
+\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
+  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
+  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
+  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
+  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
+  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
+  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
+  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
+  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
+  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
+  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
+  bla bla blabla bla bla blabla bla bla blabla bla bla bla}
 

### 2017-04-07 paper/evaluation.tex
using more space than needed
broken sentence

@@
 any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
-methodology we used to find these subjects and
-Section~\ref{seq:rq6-tradeoffs}, we verified that both
+methodology we used to find these subjects.
+%and
+%Section~\ref{seq:rq6-tradeoffs}, we verified that both
 %% executions produce the same outcome to eliminate noise from failing
@@
 
-%\begin{figure}[t!]
-\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
-    \footnotesize
-    \centering
-    \setlength{\tabcolsep}{2.5pt}
+\begin{figure}[t!]
+%\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+  %    \footnotesize
+  \small
+    \centering
+%    \setlength{\tabcolsep}{2.5pt}
 %    \resizebox{.48\textwidth}{!}{%
@@
     \label{tab:freqmodes-dynamic}
-    %\end{figure}
-\end{wrapfigure}      
+\end{figure}
+%\end{wrapfigure}
+
 Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
@@
     \centering
-    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
+    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
     \caption{\label{fig:rq5-answers}Summary of developer's answers to

### 2017-04-14 paper/evaluation.tex
pass on eval
commenting rq5

@@
 
-%% Column
-%% ``Group'' indicates the test cost group (see
-%% Figure~\ref{fig:rq1-barplot}), the
-
-\begin{figure}[t!]
-%\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
-  %    \footnotesize
-  \small
-    \centering
-%    \setlength{\tabcolsep}{2.5pt}
+%\begin{figure}[t!]
+\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+  \footnotesize
+  %  \small
+  \centering
+  \setlength{\tabcolsep}{2.5pt}
 %    \resizebox{.48\textwidth}{!}{%
@@
     \label{tab:freqmodes-dynamic}
-\end{figure}
-%\end{wrapfigure}
+%\end{figure}
+\end{wrapfigure}
 
@@
 considered that distributed CI was a form of parallelism, and in four
-projects parallelism was implemented natively~---~two projects
+projects parallelism was implemented natively\Luis{$\leftarrow$ is
+this the right word?}~---~two projects
 implemented concurrency control with custom JUnit test runners and two
@@
 \end{wrapfigure}
+
 Considering question 3, the distribution of answers was as follows.  A

### 2017-04-15 paper/evaluation.tex
pass on rq5 (after Luis' pass)

@@
 
-%\begin{figure}[t!]
+Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
+where parallelism is enabled by default in Maven.  Column
+``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.  We note that, considering these projects, the
+modules that do not use the configuration cited use the sequential
+configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
+use sequential configuration.
+
+It came as a surprise the observation that
+no project used distinct configurations in their modules. Considering
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
     \end{tabular}
-%    }
     \caption{Subjects with parallel test execution enabled by
@@
     \label{tab:freqmodes-dynamic}
-%\end{figure}
 \end{wrapfigure}
-
-Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
-where parallelism is enabled by default in Maven.  Column
-``\emph{Subject}'' indicates the name of the project, column
-``\emph{\# of modules}'' indicates the fraction of modules containing
-tests that use the configuration of parallelism mentioned in column
-``\emph{Mode}''.  We note that, considering these projects, the
-modules that do not use the configuration cited use the sequential
-configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
-use sequential configuration.
-
-It came as a surprise the observation that
-no project used distinct configurations in their modules. Considering
 our set of \numMedLong{} projects, we found that only
@@
 \begin{enumerate}
-\item How long does it take for test to run in your environment? Can
+\item How long does it take for tests to run in your environment? Can
   you briefly define your setup?
-\item Do you confirm that your project does not run in parallel?
+\item Do you confirm that your regression test suite does *not* run in parallel?
 \item\label{questionThree} Select a reason for not using parallelization:
@@
 Continuous Integration (CI) to run tests, with \emailsDistributed{} of
-these participants reporting that test suites were modularized and
+these participants reporting that test suites are modularized and
 those modules are tested independetly in CI servers through different
-parameters. A total of \emailsLocal{} participants answered that they
-do run tests in their local machines.  Note, however, that CI does not
-preclude low-level parallelization.  For example, installations of
-open-source CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated
-servers will still benefit from running tests faster through low-level
-test suite parallelization.
+parameters.  Those participants argumented that such practice helps to
+reduce time to observe test failures, which is the goal of speeding up
+regression testing.  A total of \emailsLocal{} participants answered
+that they do run tests in their local machines.  Note, however, that
+CI does not preclude low-level parallelization.  For example,
+installations of open-source CI tools (\eg{}, Jenkins~\cite{jenkins})
+in dedicated servers would benefit from running tests faster through
+low-level test suite parallelization.
 
@@
 
-Considering question 2, the answers we collected show that six of the
-\emailsProjectsAnswered{} projects execute tests in parallel.  This
-mismatch is justified by cases where neither of our checks (static or
-dynamic) could detect presence of parallelism.  A closer look at these
-projects revealed that one of them contained a \emph{pom.xml} file
-encapsulated in a jar file (similar case as reported in
-Section~\ref{sec:rqC-2}), in one of the projects the particpant
-considered that distributed CI was a form of parallelism, and in four
-projects parallelism was implemented natively\Luis{$\leftarrow$ is
-this the right word?}~---~two projects
-implemented concurrency control with custom JUnit test runners and two
-other projects implemented concurrency within test methods.  Note
-that, considering four extra cases (ignored two distributed CI cases),
-the usage of parallelization increases from \percentParallel{} to
-\percentParallelUpdated{}.  However, we do not consider this change
-significant enough to modify our conclusion about practical adoption
-of parallelization (\numRQC{}).
+Considering question 2, the answers we collected indicated, to our
+surprise, that six of the \emailsProjectsAnswered{} projects execute
+tests in parallel.  This mismatch is justified by cases where neither
+of our checks (static or dynamic) could detect presence of
+parallelism.  A closer look at these projects revealed that one of
+them contained a \emph{pom.xml} file encapsulated in a jar file
+(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
+projects the particpant considered that distributed CI was a form of
+parallelism, and in four projects the team preferred to implement
+parallelization instead of using existing features from the testing
+framework and the build system~---~in two projects the team
+implemented concurrency control with custom JUnit test runners and in
+two other projects the team implemented concurrency within test
+methods.  Note that, considering these four extra cases (ignored two
+distributed CI cases), the usage of parallelization increases from
+\percentParallel{} to \percentParallelUpdated{}.  We do not consider
+this change significant enough to modify our conclusion about
+practical adoption of parallelization (\numRQC{}).
 
@@
 
+Considering question 3, the distribution of answers was as follows.  A
+total of \emailsA{} of the \emailsProjectsAnswered{} developers who
+answered the survey did not know that parallelism was available in
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 \end{wrapfigure}
-
-Considering question 3, the distribution of answers was as follows.  A
-total of \emailsA{} of the \emailsProjectsAnswered{} developers who
-answered the survey did not know that parallelism was available in
 Maven (option ``a''), \emailsB{} of developers mentioned that they did

### 2017-04-17 paper/evaluation.tex
Added note about flaky projects and fixed label in Fig9

@@
 (because of missing dependencies or incompatible testing environment,
-for example), and \SubjectsGithubFlaky{} projects were ``flaky''.  We
-executed each project's test suite for three times to identify
-projects containing flaky tests that could introduce noise in our
-experiments.  Our final set of subjects consists of \numSubjs{}
-projects.
+for example), and \SubjectsGithubFlaky{} projects were ``flaky''.
+\Jbc{Check if this is ok $\rightarrow$} We executed each project's
+test suite for three times to identify projects containing flaky tests
+and to ignore these tests (\ie, using the \CodeIn{@Ignore} annotation
+from JUnit) to avoid introducing noise in our experiments.  Our final
+set of subjects consists of \numSubjs{} projects.
 
@@
     \SubjectsGithubNotMaven{} projects without Maven support,
-    \SubjectsGithubNotTestable{} untestable projects, and
-    \SubjectsGithubFlaky{} projects with flaky tests. We considered
+    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
+    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
     \numSubjs{} projects to conduct our study.}
@@
 \midrule
-\textbf{total} &  &  &  & \avgSpeedup{}x\\
+\textbf{average} &  &  &  & \avgSpeedup{}x\\
 \bottomrule%

### 2017-04-17 paper/evaluation.tex
pass on RQ6

@@
 
-To answer this research question we selected projects as follows.  To
-avoid noise in measuring flakiness we first discarded projects
-containing failing tests.  Then, we sorted projects in descending
-order of their execution times and selected the top ten projects from
-the resulting set.  In this experiment, the baseline technique is
-sequential execution (\ie{}, configuration \Seq{}) and the evaluation
-techniques consist of all configuration modes listed in
-Section~\ref{sec:modes}.  We ran each of those techniques for \Fix{X}
-times computing elapsed time and number of failing tests in each run.
+To answer this research question, we considered all six parallel
+levels from Section~\ref{sec:modes} and we selected the top 10
+projects with long-running tests suites that satisfies the following
+criteria: (1) tests run in sequence by default and (2) test suite
+consists only by passing tests. The first criteria is to use the
+default execution (\ie, configuration \Seq{}) as a baseline to compare
+speedup with the other parallel configurations. The second criteria is
+to avoid introducing noise when measuring the rate of flakiness caused
+by the non-deterministic execution of tests. We are interested only in
+failures manifested when parallelism is enabled. Since the number of
+failing tests may vary, we run each project three times and report
+report the average elapsed time and rate of flakiness.
 Figures~\ref{tab:rq6-efficiency} and~\ref{tab:rq6-flaky} summarize the
-results we obtained.
-
-\Fix{Elaborate results from efficiency}
+results obtained.
 
@@
 
+\Fix{Elaborate results from efficiency}
+
 \begin{figure}[h!]
@@
 \end{figure}
+
+\Fix{Elaborate results from flakiness}
+
+\Fix{Conclude}
 

### 2017-04-17 paper/evaluation.tex
grammar fix

@@
 test suite for three times to identify projects containing flaky tests
-and to ignore these tests (\ie, using the \CodeIn{@Ignore} annotation
+and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
 from JUnit) to avoid introducing noise in our experiments.  Our final
@@
     projects hosted on \github{}. From this initial sample, we ignored
-    \SubjectsGithubNotMaven{} projects without Maven support,
+    \SubjectsGithubNotMaven{} projects without Maven support and
     \SubjectsGithubNotTestable{} untestable projects\Comment{, and

### 2017-04-17 paper/evaluation.tex
RQ6 - preliminar list

@@
 \midrule%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+%% BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+Snazy OHC & - & - & - & - & - & -\\%
+RoaringBitmap & - & - & - & - & - & -\\%
+Linkedin Pinot & - & - & - & - & - & -\\%
+Jenkinsci Github-Plugin & - & - & - & - & - & -\\%
+Geotools & - & - & - & - & - & -\\%
+Kite-SDK Kite & - & - & - & - & - & -\\%
+Apache Giraph & - & - & - & - & - & -\\%
+Openmrs Core & - & - & - & - & - & -\\%
+Jenkinsci Docker-Workflow-plugin & - & - & - & - & - & -\\%
+Apache Eagle & - & - & - & - & - & -\\%
 \bottomrule%
@@
 \midrule%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+%% BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+Snazy OHC & - & - & - & - & - & -\\%
+RoaringBitmap & - & - & - & - & -\\%
+Linkedin Pinot & - & - & - & - & -\\%
+Jenkinsci Github-Plugin & - & - & - & - & -\\%
+Geotools & - & - & - & - & -\\%
+Kite-SDK Kite & - & - & - & - & -\\%
+Apache Giraph & - & - & - & - & -\\%
+Openmrs Core & - & - & - & - & -\\%
+Jenkinsci Docker-Workflow-plugin & - & - & - & - & -\\%
+Apache Eagle & - & - & - & - & -\\%
 \bottomrule%

### 2017-04-18 paper/evaluation.tex
[RQ6] preliminar results

--- 2017-04-17 paper/evaluation.tex
@@
 failures manifested when parallelism is enabled. Since the number of
-failing tests may vary, we run each project three times and report
-report the average elapsed time and rate of flakiness.
-Figures~\ref{tab:rq6-efficiency} and~\ref{tab:rq6-flaky} summarize the
-results obtained.
+failing tests may vary, we run each project three times and report the
+average elapsed time and rate of flakiness.
+Figures~\ref{tab:rq6-efficiency} (ordered by time cost)
+and~\ref{tab:rq6-flaky} (ordered by the number of tests) summarize the
+obtained results.
 
@@
 \midrule%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
+Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
+Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
+Kite SDK & - & - & - & - & - & -\\%
+Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
+OpenMRS Core & - & - & - & - & - & -\\%
+Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
+Apache Eagle & - & - & - & - & - & -\\%
+Geotools & - & - & - & - & - & -\\%
+Atomix & - & - & - & - & - & -\\%
+Kuromoji & - & - & - & - & - & -\\%
+\Fix{Snazy OHC} & - & - & - & - & - & -\\%
+\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
 \bottomrule%
@@
 \midrule%
-BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
+Linkedin Pinot & - & - & - & - & - & -\\%
+Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
+Kite SDK & - & - & - & - & - & -\\%
+Apache Giraph & - & - & - & - & - & -\\%
+OpenMRS Core & - & - & - & - & - & -\\%
+Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
+Apache Eagle & - & - & - & - & - & -\\%
+Geotools & - & - & - & - & - & -\\%
+Atomix & - & - & - & - & - & -\\%
+Kuromoji & - & - & - & - & - & -\\%
+\Fix{Snazy OHC} & - & - & - & - & - & -\\%
+\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
 \bottomrule%

### 2017-04-18 paper/evaluation.tex
Adjusted format

@@
 \midrule%
-Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
-Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
+%% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
+Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
+%% Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
+Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
 Kite SDK & - & - & - & - & - & -\\%
-Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
+%% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
+Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
 OpenMRS Core & - & - & - & - & - & -\\%
-Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
+%% Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
+Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
 Apache Eagle & - & - & - & - & - & -\\%

### 2017-04-19 paper/evaluation.tex
[RQ6] - WIP

@@
 \toprule
-\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
+\emph{Subject} & \emph{\Seq{}} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
 \midrule%
 %% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
-Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
+%% Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
 %% Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
-Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
-Kite SDK & - & - & - & - & - & -\\%
+%% Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
+%% Kite SDK & - & - & - & - & - & -\\%
 %% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
-Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
-OpenMRS Core & - & - & - & - & - & -\\%
+%% \Fix{!?} Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
+%% OpenMRS Core & - & - & - & - & - & -\\%
 %% Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
-Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
-Apache Eagle & - & - & - & - & - & -\\%
-Geotools & - & - & - & - & - & -\\%
-Atomix & - & - & - & - & - & -\\%
-Kuromoji & - & - & - & - & - & -\\%
-\Fix{Snazy OHC} & - & - & - & - & - & -\\%
-\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
+%% Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
+%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
+Geotools & 8.41m & - & - & - & - & -\\%
+Atomix & 7.78m & - & - & - & - & -\\%
+Kuromoji & 7.68m & - & - & - & - & -\\%
+%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
+%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
 \bottomrule%
@@
 \toprule
-\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
+\emph{Subject} & \emph{\# of tests} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
 \midrule%
-Linkedin Pinot & - & - & - & - & - & -\\%
-Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
-Kite SDK & - & - & - & - & - & -\\%
-Apache Giraph & - & - & - & - & - & -\\%
-OpenMRS Core & - & - & - & - & - & -\\%
-Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
-Apache Eagle & - & - & - & - & - & -\\%
-Geotools & - & - & - & - & - & -\\%
-Atomix & - & - & - & - & - & -\\%
-Kuromoji & - & - & - & - & - & -\\%
-\Fix{Snazy OHC} & - & - & - & - & - & -\\%
-\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
+%% Linkedin Pinot & 664 & - & - & - & - & -\\%
+%% Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
+%% Kite SDK & - & - & - & - & - & -\\%
+%% \Fix{!?} Apache Giraph & 327 & - & - & - & - & -\\%
+%% OpenMRS Core & - & - & - & - & - & -\\%
+%% Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
+%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
+Geotools & 7701 & - & - & - & - & -\\%
+Kuromoji & 672 & - & - & - & - & -\\%
+Atomix & 99 & - & - & - & - & -\\%
+%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
+%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
 \bottomrule%

### 2017-05-02 paper/evaluation.tex
speedups
updated RQ6

@@
 experiments for two main reasons.  First, some tests may finish
-earlier than expected due to observed test failures in some of the
+earlier than expected due to the observed test failures in some of the
 revisions we downloaded.  From the \numSubjs{} testable projects,
@@
 
-To answer this research question, we considered all six parallel
-levels from Section~\ref{sec:modes} and we selected the top 10
-projects with long-running tests suites that satisfies the following
-criteria: (1) tests run in sequence by default and (2) test suite
-consists only by passing tests. The first criteria is to use the
-default execution (\ie, configuration \Seq{}) as a baseline to compare
-speedup with the other parallel configurations. The second criteria is
-to avoid introducing noise when measuring the rate of flakiness caused
-by the non-deterministic execution of tests. We are interested only in
-failures manifested when parallelism is enabled. Since the number of
-failing tests may vary, we run each project three times and report the
-average elapsed time and rate of flakiness.
-Figures~\ref{tab:rq6-efficiency} (ordered by time cost)
-and~\ref{tab:rq6-flaky} (ordered by the number of tests) summarize the
+%% The intuition is that efficiency and flakiness are inversely
+%% proportional in some cases: if too many tests depends on the state of
+%% a single external resource, several tests are likely to fail as the
+%% degree of concurrency increases by exploiting maximum CPU usage.
+
+To answer this research question, we conducted an experiment involving
+the six parallel levels from Section~\ref{sec:modes}  and the top 10
+projects with long-running tests suites from our sample set. We are
+interested in understanding how efficiency (\ie, testing cost) and
+flakiness (\ie, failing tests) are affected when we run a test suite
+with different parallel levels. \Jbc{I think we must have a sentence
+to motivate why we want to understand this relationship}.  We used as
+a \emph{control group} (\ie, baseline) the sequential execution of
+each subject's tests. Notice that for measuring flakiness, we have to
+consider only tests that failed due to the concurrency in the parallel
+execution. To this purpose, we re-executed the tests in sequence ten
+times and carefully verified that there are only passing tests in our
+baseline. We considered ten as the number of re-executions based on
+the approach used by Google reported in a previous work on test
+flakiness~\cite{luo-etal-fse2014}. For the parallelism configurations,
+we implemented a script that takes a subject and a configuration
+(\eg, \ForkSeq{}) as inputs, and the script outputs the modified
+version of the subject with the desired configuration. The workflow
+consists in copying the project directory to a new directory, finding
+all existing build files (\ie, \pomf{} files), and modifying all
+existing Maven Surefire configurations with new values for the
+parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
+\CodeIn{threadCount} using an XPath~\cite{xpath} library to manipulate
+XML documents. For configurations with forked JVMs enabled (\ie,
+\ForkSeq{} and \ForkParMeth{}), we changed the \CodeIn{forkCount} with
+the value \CodeIn{1C} (\ie, one JVM per core). To adjust the pool of
+threads for parallelism within a JVM, we changed the parameter
+\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
+number of native threads per core OR 6 as it represents 3 Cores * 2
+native threads?}.  To run the subjects and their respective variations
+(\ie, the modified versions according to the parallelism
+configuration), we used a similar approach as in
+Figure~\ref{fig:mvn-execution} except that we added a timeout of one
+hour to run the tests. We used the \CodeIn{timeout}
+command~\cite{timeout-cmd} to monitor the execution, and we configured
+the command to dispatch a \emph{kill} signal if the test execution
+exceeds the time limit. We imposed this time constraint to avoid
+hanging indefinitely the experiment execution due to some thread
+contention that may occur (\eg, deadlock). Finally, we saved each
+execution log and XML test reports generated by Maven to collect the
+execution time, the number of failing tests, and for reference to
+analyze and diagnose outliers in our results. For efficiency, we
+reported the speedup (\ie, $T_{\text{sequence}} /
+T_{\text{parallel}}$) in average, and for flakiness, we reported the
+rate of failing tests (\ie, $failures / tests$) in average.
+Figure~\ref{tab:rq6-table} (ordered by time cost) summarizes the
 obtained results.
 
-\begin{figure}[h!]
-\centering
-\resizebox{.48\textwidth}{!}{%
-\begin{tabular}{lrrrrrr}
-\toprule
-\emph{Subject} & \emph{\Seq{}} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
-\midrule%
+%% that satisfies the following criteria: (1) tests run in sequence by
+%% default and (2) test suite consists only by passing tests. The first
+%% criteria is to use the default execution (\ie, configuration \Seq{})
+%% as a baseline to compare speedup with the other parallel
+%% configurations. The second criteria is to avoid introducing noise when
+%% measuring the rate of flakiness caused by the non-deterministic
+%% execution of tests. We are interested only in failures manifested when
+%% parallelism is enabled. Since the number of failing tests may vary, we
+%% run each project three times and report the average elapsed time and
+%% rate of flakiness.
+
+%% Table header macros
+\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
+\newcommand{\subcolB}{$\%_\text{fail}$}
+\newcommand{\colheader}[1]{\multicolumn{2}{c|}{\emph{#1}}}
+\newcommand{\subcol}{\subcolA{} & \subcolB{}}
+\newcommand{\entry}[2]{#1x & #2\%}
+
+\begin{figure*}[t]
+\centering
+\begin{tabular}{|l|r|rr|rr|rr|rr|rr|}
+\hline%
+
+\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
+    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
+    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
+    \colheader{\ForkParMeth} \\ \cline{2-12}
+    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
+    & \subcol{}\\%
+
+\hline%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+
 %% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
@@
 %% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
-%% \Fix{!?} Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
+%% Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
 %% OpenMRS Core & - & - & - & - & - & -\\%
@@
 %% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
-Geotools & 8.41m & - & - & - & - & -\\%
-Atomix & 7.78m & - & - & - & - & -\\%
-Kuromoji & 7.68m & - & - & - & - & -\\%
+%% Geotools & 8.41m & - & - & - & - & -\\%
+%% Atomix & 7.78m & - & - & - & - & -\\%
+%% Kuromoji & 7.68m & - & - & - & - & -\\%
 %%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
 %%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
-\bottomrule%
-\end{tabular}}
-\caption{\Fix{Tabela de eficiencia}}
-\label{tab:rq6-efficiency}
-\end{figure}
+
+\hline%
+\end{tabular}
+\caption{\Fix{Tabela de eficiencia e flakiness}}
+\label{tab:rq6-table}
+\end{figure*}
+
+%% \begin{figure}[h!]
+%% \centering
+%% \resizebox{.48\textwidth}{!}{%
+%% \begin{tabular}{lcrrrrr}
+%% \toprule
+%% \emph{Subject} & \emph{\# of tests} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
+%% \midrule%
+%% Linkedin Pinot & 356 & - & - & - & - & -\\%
+%% %% Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
+%% %% Kite SDK & - & - & - & - & - & -\\%
+%% %% \Fix{!?} Apache Giraph & 327 & - & - & - & - & -\\%
+%% %% OpenMRS Core & - & - & - & - & - & -\\%
+%% %% Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
+%% %% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
+%% %%Geotools & 7701 & - & - & - & - & -\\%
+%% %%Kuromoji & 672 & - & - & - & - & -\\%
+%% %%Atomix & 99 & - & - & - & - & -\\%
+%% %%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
+%% %%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
+%% \bottomrule%
+%% \end{tabular}}
+%% \caption{\Fix{Tabela de flakiness}}
+%% \label{tab:rq6-flaky}
+%% \end{figure}
 
@@
 
-\begin{figure}[h!]
-\centering
-\resizebox{.48\textwidth}{!}{%
-\begin{tabular}{lcrrrrr}
-\toprule
-\emph{Subject} & \emph{\# of tests} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
-\midrule%
-%% Linkedin Pinot & 664 & - & - & - & - & -\\%
-%% Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
-%% Kite SDK & - & - & - & - & - & -\\%
-%% \Fix{!?} Apache Giraph & 327 & - & - & - & - & -\\%
-%% OpenMRS Core & - & - & - & - & - & -\\%
-%% Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
-%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
-Geotools & 7701 & - & - & - & - & -\\%
-Kuromoji & 672 & - & - & - & - & -\\%
-Atomix & 99 & - & - & - & - & -\\%
-%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
-%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
-\bottomrule%
-\end{tabular}}
-\caption{\Fix{Tabela de flakiness}}
-\label{tab:rq6-flaky}
-\end{figure}
-
 \Fix{Elaborate results from flakiness}
 
-\Fix{Conclude}
+\Fix{highlight special cases}
+
+\Fix{Draw conclusions}
 
@@
 
-\Fix{Jean and Luis should write this. This is really important for an
-  empirical study.  You need to undertand main sources of threat:
-  internal, external, and construct.  Read this document for the
-  basics: http://www.statsdirect.com/help/basics/validity.htm.  Read
-  this document for an example:
-  http://www.cin.ufpe.br/~damorim/publications/perez-etal-icst2017.pdf}
+\Fix{To appear... Elaborate CONSTRUCT, INTERNAL and EXTERNAL threats.
+I'm going to be writing this ASAP as I finish to present the results
+from RQ6}
 

### 2017-05-03 paper/evaluation.tex
minor fixes

@@
 To answer this research question, we conducted an experiment involving
-the six parallel levels from Section~\ref{sec:modes}  and the top 10
-projects with long-running tests suites from our sample set. We are
-interested in understanding how efficiency (\ie, testing cost) and
+the six parallel configurations from Section~\ref{sec:modes}  and the
+top 10 projects with long-running tests suites from our sample set. We
+are interested in understanding how efficiency (\ie, testing cost) and
 flakiness (\ie, failing tests) are affected when we run a test suite
-with different parallel levels. \Jbc{I think we must have a sentence
-to motivate why we want to understand this relationship}.  We used as
-a \emph{control group} (\ie, baseline) the sequential execution of
-each subject's tests. Notice that for measuring flakiness, we have to
-consider only tests that failed due to the concurrency in the parallel
-execution. To this purpose, we re-executed the tests in sequence ten
-times and carefully verified that there are only passing tests in our
-baseline. We considered ten as the number of re-executions based on
-the approach used by Google reported in a previous work on test
-flakiness~\cite{luo-etal-fse2014}. For the parallelism configurations,
-we implemented a script that takes a subject and a configuration
-(\eg, \ForkSeq{}) as inputs, and the script outputs the modified
-version of the subject with the desired configuration. The workflow
-consists in copying the project directory to a new directory, finding
-all existing build files (\ie, \pomf{} files), and modifying all
-existing Maven Surefire configurations with new values for the
-parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
-\CodeIn{threadCount} using an XPath~\cite{xpath} library to manipulate
-XML documents. For configurations with forked JVMs enabled (\ie,
-\ForkSeq{} and \ForkParMeth{}), we changed the \CodeIn{forkCount} with
-the value \CodeIn{1C} (\ie, one JVM per core). To adjust the pool of
-threads for parallelism within a JVM, we changed the parameter
-\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
-number of native threads per core OR 6 as it represents 3 Cores * 2
-native threads?}.  To run the subjects and their respective variations
-(\ie, the modified versions according to the parallelism
+with different parallel configurations. \Jbc{I think we must have a
+sentence to motivate why we want to understand this relationship}.  We
+used as a \emph{control group} (\ie, baseline) the sequential
+execution of each subject's tests. Notice that for measuring
+flakiness, we have to consider only tests that failed due to the
+concurrency in the parallel execution. To this purpose, we re-executed
+the tests in sequence ten times and carefully verified that there are
+only passing tests in our baseline. We considered ten as the number of
+re-executions based on the approach used by Google reported in a
+previous work on test flakiness~\cite{luo-etal-fse2014}. For the
+parallelism configurations, we implemented a script that takes a
+subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
+script outputs the modified version of the subject with the desired
+configuration. The workflow consists in copying the project directory
+to a new directory, finding all existing build files (\ie, \pomf{}
+files), and modifying all existing Maven Surefire configurations with
+new values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
+and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
+manipulate XML documents. For configurations with forked JVMs enabled
+(\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
+\CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per core).
+To adjust the pool of threads for parallelism within a JVM, we changed
+the parameter \CodeIn{threadCount} with \Jbc{should we consider 2 as
+it is the number of native threads per core OR 6 as it represents 3
+Cores * 2 native threads?}.  To run the subjects and their respective
+variations (\ie, the modified versions according to the parallelism
 configuration), we used a similar approach as in
@@
 analyze and diagnose outliers in our results. For efficiency, we
-reported the speedup (\ie, $T_{\text{sequence}} /
-T_{\text{parallel}}$) in average, and for flakiness, we reported the
-rate of failing tests (\ie, $failures / tests$) in average.
-Figure~\ref{tab:rq6-table} (ordered by time cost) summarizes the
-obtained results.
+reported the speedup (\ie, $T_{\text{s}} / T_{\text{p}}$) in average,
+and for flakiness, we reported the rate of failing tests (\ie,
+$\mathit{\%_\text{fail} = failures / tests}$) in average.
+Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
+the time cost (\ie, $T_\text{cost}$).
 
@@
 \newcommand{\subcolB}{$\%_\text{fail}$}
-\newcommand{\colheader}[1]{\multicolumn{2}{c|}{\emph{#1}}}
+\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
 \newcommand{\subcol}{\subcolA{} & \subcolB{}}
@@
 \centering
-\begin{tabular}{|l|r|rr|rr|rr|rr|rr|}
-\hline%
-
+\small
+\begin{tabular}{lccccccccccc}
+\toprule
 \multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
@@
     \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
-    \colheader{\ForkParMeth} \\ \cline{2-12}
+    \colheader{\ForkParMeth} \\ %\cline{2-12}
     & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
     & \subcol{}\\%
-
-\hline%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
-Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+\midrule%
+Choco Solver & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
 
@@
 
-\hline%
+\bottomrule%
 \end{tabular}

### 2017-05-05 paper/evaluation.tex
added vertical line for readability
preliminar values from RQ6

@@
 \small
-\begin{tabular}{lccccccccccc}
+\begin{tabular}{l|c|cccccccccc}
 \toprule
-\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
+\multirow{2}{*}{\emph{Subject (module)}} & \emph{\Seq{}} &
     \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
@@
 \midrule%
-Choco Solver & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+    OpenMRS Core (\CodeIn{api})           & 13.8m & \entry{1.04}{58.07} & \entry{1.86}{65.55} & \entry{2.01}{61.56} & \entry{1.51}{0} & \colheader{X}\\%
+Apache Flume (\CodeIn{flume-ng-core}) & 8.3m & \entry{2.82}{18.11} & \entry{1.07}{0} & \entry{2.78}{16.84} & \entry{0.98}{0} & \entry{2.87}{18.88}\\%
+Apache Giraph (\CodeIn{giraph-core})  & 7m & \entry{2.08}{5.08} & \colheader{X} & \entry{1.01}{0} & \entry{1}{B} & \colheader{X}\\%
 

### 2017-05-05 paper/evaluation.tex
missed value

--- 2017-05-03 paper/evaluation.tex
@@
 \midrule%
-Choco Solver & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+OpenMRS Core (\CodeIn{api})           & 13.8m & \entry{1.04}{58.07} & \entry{1.86}{65.55} & \entry{2.01}{61.56} & \entry{1.51}{0} & \colheader{JVM crash}\\%
+Apache Flume (\CodeIn{flume-ng-core}) & 8.3m & \entry{2.82}{18.11} & \entry{1.07}{0} & \entry{2.78}{16.84} & \entry{0.98}{0} & \entry{2.87}{18.88}\\%
+Apache Giraph (\CodeIn{giraph-core})  & 7m & \entry{2.08}{5.08} & \colheader{JVM crash} & \entry{1.01}{0} & \entry{1}{0} & \colheader{JVM crash}\\%
 

### 2017-05-06 paper/evaluation.tex
Adjusted table

--- 2017-05-03 paper/evaluation.tex
@@
 \newcommand{\subcol}{\subcolA{} & \subcolB{}}
-\newcommand{\entry}[2]{#1x & #2\%}
+\newcommand{\entry}[2]{#1 & #2}
 
@@
 \small
-\begin{tabular}{lccccccccccc}
+\begin{tabular}{l|rr|rrrrrrrrrr}
 \toprule
-\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
+\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
     \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
@@
     \colheader{\ForkParMeth} \\ %\cline{2-12}
-    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
+    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
     & \subcol{}\\%
 \midrule%
-Choco Solver & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
+OpenMRS Core (\CodeIn{api})           & \entry{13.8m}{X} & \entry{-}{58.07\%} & \entry{1.86x}{65.55\%} & \entry{2.01x}{61.56\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+Apache Flume (\CodeIn{core}) & \entry{8.3m}{Y} & \entry{2.82x}{18.11\%} & \entry{-}{0\%} & \entry{2.78x}{16.84\%} & \entry{-}{0\%} & \entry{2.87x}{18.88\%}\\%
+Apache Giraph (\CodeIn{core})  & \entry{7m}{Z} & \entry{2.08x}{5.08\%} & \colheader{\cellcolor{lightgray}JVM Crash}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+Struct (\CodeIn{rest})  & \entry{Xm}{Z} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
 

### 2017-05-06 paper/evaluation.tex
Adjusted decimals

@@
 \midrule%
-OpenMRS Core (\CodeIn{api})           & \entry{13.8m}{X} & \entry{-}{58.07\%} & \entry{1.86x}{65.55\%} & \entry{2.01x}{61.56\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Apache Flume (\CodeIn{core}) & \entry{8.3m}{Y} & \entry{2.82x}{18.11\%} & \entry{-}{0\%} & \entry{2.78x}{16.84\%} & \entry{-}{0\%} & \entry{2.87x}{18.88\%}\\%
-Apache Giraph (\CodeIn{core})  & \entry{7m}{Z} & \entry{2.08x}{5.08\%} & \colheader{\cellcolor{lightgray}JVM Crash}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+OpenMRS Core (\CodeIn{api})  & \entry{13.8m}{3436} & \entry{-}{58.7\%}     & \entry{1.86x}{65.6\%} & \entry{2.01x}{61.6\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+Apache Flume (\CodeIn{core}) & \entry{8.3m}{392}   & \entry{2.82x}{18.1\%} & \entry{-}{0\%} & \entry{2.78x}{16.8\%} & \entry{-}{0\%} & \entry{2.87x}{18.9\%}\\%
+Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}JVM Crash}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
 Struct (\CodeIn{rest})       & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

### 2017-05-06 paper/evaluation.tex
pass on rq6

@@
 configurations on test flakiness (negative impact) and speedup
-(positive impact).  Recall that increased resource contention obtained
-with parallelism can lead to concurrency issues such as data races.
-Flakiness and speedup are contradictory forces that drive
-configuration selection.  Furthermore, note that Section~\ref{sec:rqD}
+(positive impact).  Furthermore, note that Section~\ref{sec:rqD}
 evaluated speedup in isolation, focused on projects configured to use
@@
 the six parallel configurations from Section~\ref{sec:modes}  and the
-top 10 projects with long-running tests suites from our sample set. We
-are interested in understanding how efficiency (\ie, testing cost) and
-flakiness (\ie, failing tests) are affected when we run a test suite
-with different parallel configurations. \Jbc{I think we must have a
-sentence to motivate why we want to understand this relationship}.  We
-used as a \emph{control group} (\ie, baseline) the sequential
+top 10 long-running test modules from our sample
+set. The rationale for this selection criteria was to maximize the
+chances of observing speedup and flakiness, assuming that long-running
+tests also have many tests. Indeed, we confirmed that test suites in
+these projects contain at least \Fix{X} tests. Also, we preferred to
+compare the effect of a configuration over a single test module for
+projects with multiple test modules.  Recall that large projects may
+contain several test modules, and these modules may contain distinct
+characteristics that could favor one configuration and not others;
+therefore, it would be necessary to check each module individually for
+a fair comparison.  We are interested in understanding how efficiency
+(\ie, testing cost) and flakiness (\ie, failing tests) are affected
+when we run a test suite with different parallel configurations.
+Recall that increased resource contention obtained with parallelism
+can lead to concurrency issues such as data races.  Flakiness and
+speedup are contradictory forces that drive configuration selection.
+We used as a \emph{control group} (\ie, baseline) the sequential
 execution of each subject's tests. Notice that for measuring
 flakiness, we have to consider only tests that failed due to the
-concurrency in the parallel execution. To this purpose, we re-executed
-the tests in sequence ten times and carefully verified that there are
-only passing tests in our baseline. We considered ten as the number of
-re-executions based on the approach used by Google reported in a
-previous work on test flakiness~\cite{luo-etal-fse2014}. For the
-parallelism configurations, we implemented a script that takes a
-subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
+concurrency in the parallel execution.  For that reason, we
+re-executed the tests in sequence ten times and carefully verified
+that there are only passing tests in our baseline.  We considered ten
+as the number of re-executions based on the approach used by Google
+reported in a previous work on test flakiness~\cite{luo-etal-fse2014}.
+To obtain parallel configurations, we implemented a script that takes
+a subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
 script outputs the modified version of the subject with the desired
@@
 variations (\ie, the modified versions according to the parallelism
-configuration), we used a similar approach as in
+configuration), we used a similar approach as described in
 Figure~\ref{fig:mvn-execution} except that we added a timeout of one
@@
 analyze and diagnose outliers in our results. For efficiency, we
-reported the speedup (\ie, $T_{\text{s}} / T_{\text{p}}$) in average,
-and for flakiness, we reported the rate of failing tests (\ie,
-$\mathit{\%_\text{fail} = failures / tests}$) in average.
-Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
-the time cost (\ie, $T_\text{cost}$).
-
-%% that satisfies the following criteria: (1) tests run in sequence by
-%% default and (2) test suite consists only by passing tests. The first
-%% criteria is to use the default execution (\ie, configuration \Seq{})
-%% as a baseline to compare speedup with the other parallel
-%% configurations. The second criteria is to avoid introducing noise when
-%% measuring the rate of flakiness caused by the non-deterministic
-%% execution of tests. We are interested only in failures manifested when
-%% parallelism is enabled. Since the number of failing tests may vary, we
-%% run each project three times and report the average elapsed time and
-%% rate of flakiness.
+reported the speedup (\ie, $\Uparrow_\text{speed} = T_{\text{s}} /
+T_{\text{p}}$) in average, and for flakiness, we reported the rate of
+failing tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$) in
+average.  Figure~\ref{tab:rq6-table} summarizes the obtained results
+ordered by the time cost (\ie, $T_\text{cost}$).
 
@@
 OpenMRS Core (\CodeIn{api})  & \entry{13.8m}{3436} & \entry{-}{58.7\%}     & \entry{1.86x}{65.6\%} & \entry{2.01x}{61.6\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Apache Flume (\CodeIn{core}) & \entry{8.3m}{392}   & \entry{2.82x}{18.1\%} & \entry{-}{0\%} & \entry{2.78x}{16.8\%} & \entry{-}{0\%} & \entry{2.87x}{18.9\%}\\%
-Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}JVM Crash}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Struct (\CodeIn{rest})       & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-
-%% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
-%% Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
-%% Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
-%% Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
-%% Kite SDK & - & - & - & - & - & -\\%
-%% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
-%% Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
-%% OpenMRS Core & - & - & - & - & - & -\\%
-%% Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
-%% Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
-%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
-%% Geotools & 8.41m & - & - & - & - & -\\%
-%% Atomix & 7.78m & - & - & - & - & -\\%
-%% Kuromoji & 7.68m & - & - & - & - & -\\%
-%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
-%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
+Jankotek MapDB               & \entry{10m}{5218}   & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{3.9x}{0\%} & \colheader{\cellcolor{lightgray}timeout}\\%
+Apache Flume (\CodeIn{core}) & \entry{8.3m}{392}   & \entry{2.86x}{18.1\%} & \entry{-}{0\%} & \entry{2.78x}{16.8\%} & \entry{-}{0\%} & \entry{2.87x}{18.9\%}\\%
+Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+Stripe Java                  & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+Facebook Archive Linkbench   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
 
@@
 
-%%To evaluate the distribution of execution time per project, we sorted
-%%the test cases by decreasing order of elapsed time and calculated the
-%%number of tests executed in 90\% of the total time. Later, we reported
-%%the \Fix{balance} of execution time by dividing the number of tests
-%%that represents 90\% of the execution time by the number of tests
-%%cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
-%%collected the elapsed time from test cases for each generated report.
-%%Maven Surefire generates an XML report with execution information
-%%(\eg, number of skipped tests and elapsed time) per test suite
-%%\Jbc{Should I use the previous sentence as a footnote or should I
-%%delete it?}. We noticed that some test cases reported an elapsed time
-%%of zero: since the reported time is in milliseconds, some tests may
-%%execute in a shorter time. \Fix{..to be continued...}}. Results
-%%indicate that \Fix{...}.
-%%
-%%\begin{figure}[h!]
-%%    \centering
-%%    \includegraphics[width=0.4\textwidth]{results/plots/balance.pdf}
-%%    \caption{\Fix{balance}}
-%%\end{figure}
-
-%% \subsection{Answering research question RQ3}
-%% \label{sec:rqThree}
-%% 
-%% \begin{itemize}
-%%     \item \RQB
-%% \end{itemize}
-%% 
-%% To evaluate the distribution of CPU and IO intensive test suites from
-%% the sample set, we used the command \emph{sar} to monitor the system
-%% activity in background while tests ran. \emph{Sar} is a command that
-%% collects and reports statistics (\eg, percentage of IO waiting and
-%% usage of CPU in user mode) based on the kernel activity and it is
-%% highly configurable to collect detailed information (\eg, usage of a
-%% specific processor core or percentage of network interface
-%% utilization). We configured \emph{sar} to report \Fix{...explain how
-%% we executed and what fields we are interested}. \Fix{explain fields}.
-%% Figure \Fix{A} shows the distribution of subjects grouped in intervals
-%% of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}
-%% 
-%% \begin{figure}[h!]
-%%     \centering
-%%     \includegraphics[width=0.4\textwidth]{results/plots/cpuness.pdf}
-%%     \caption{\Fix{cpu usage}}
-%% \end{figure}
-%% 
-%% \Comment{we proposed the definition of \emph{cpuness}
-%% computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
-%% where \emph{user\_t} is the elapsed time of execution in \emph{user
-%% mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
-%% \emph{elapsed\_t} is the elapsed time to finish the execution. We
-%% measured the \emph{cpuness} of each regression test \Fix{...elaborate
-%% the meaning of cpuness} \Fix{Describe how I measured user, system and
-%% "wall" time}.  \Fix{Explain results}.  \Fix{show plots}}
-%%
-
 %%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th

### 2017-05-06 paper/evaluation.tex
Added missing values

@@
 Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Stripe Java                  & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-Facebook Archive Linkbench   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+Facebook Archive Linkbench   & \entry{4.6m}{392}   & \entry{-}{1\%}        & \entry{1.59x}{2\%} & \entry{-}{0\%} & \entry{1.7x}{1\%} & \entry{1.7x}{0\%}\\%
+Stripe Java                  & \entry{4.2m}{302}   & \entry{4.2x}{4.6\%}   & \entry{4.67}{4.6\%} & \entry{4.2x}{5.3\%} & \entry{-}{0\%} & \entry{4.2x}{4.6\%}\\%
 %% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

### 2017-05-06 paper/evaluation.tex
pass on rq6

@@
 the six parallel configurations from Section~\ref{sec:modes}  and the
-top 10 long-running test modules from our sample
-set. The rationale for this selection criteria was to maximize the
-chances of observing speedup and flakiness, assuming that long-running
-tests also have many tests. Indeed, we confirmed that test suites in
-these projects contain at least \Fix{X} tests. Also, we preferred to
-compare the effect of a configuration over a single test module for
-projects with multiple test modules.  Recall that large projects may
-contain several test modules, and these modules may contain distinct
-characteristics that could favor one configuration and not others;
-therefore, it would be necessary to check each module individually for
-a fair comparison.  We are interested in understanding how efficiency
-(\ie, testing cost) and flakiness (\ie, failing tests) are affected
-when we run a test suite with different parallel configurations.
-Recall that increased resource contention obtained with parallelism
-can lead to concurrency issues such as data races.  Flakiness and
-speedup are contradictory forces that drive configuration selection.
-We used as a \emph{control group} (\ie, baseline) the sequential
-execution of each subject's tests. Notice that for measuring
-flakiness, we have to consider only tests that failed due to the
-concurrency in the parallel execution.  For that reason, we
-re-executed the tests in sequence ten times and carefully verified
-that there are only passing tests in our baseline.  We considered ten
-as the number of re-executions based on the approach used by Google
-reported in a previous work on test flakiness~\cite{luo-etal-fse2014}.
-To obtain parallel configurations, we implemented a script that takes
-a subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
-script outputs the modified version of the subject with the desired
-configuration. The workflow consists in copying the project directory
-to a new directory, finding all existing build files (\ie, \pomf{}
-files), and modifying all existing Maven Surefire configurations with
-new values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
-and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
-manipulate XML documents. For configurations with forked JVMs enabled
-(\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
-\CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per core).
-To adjust the pool of threads for parallelism within a JVM, we changed
-the parameter \CodeIn{threadCount} with \Jbc{should we consider 2 as
-it is the number of native threads per core OR 6 as it represents 3
-Cores * 2 native threads?}.  To run the subjects and their respective
-variations (\ie, the modified versions according to the parallelism
+top 10 long-running test modules from our sample set. The rationale
+for this selection criteria was to maximize the chances of observing
+speedup and flakiness, assuming that long-running tests also have many
+tests. Indeed, we confirmed that test suites in these projects contain
+at least 236 tests ($1,662.7$ in average). Also, we preferred to compare the
+effect of a configuration over a single test module for projects with
+multiple test modules.  Recall that large projects may contain several
+test modules, and these modules may contain distinct characteristics
+that could favor one configuration and not others; therefore, it would
+be necessary to check each module individually for a fair comparison.
+We are interested in understanding how efficiency (\ie, testing cost)
+and flakiness (\ie, failing tests) are affected when we run a test
+suite with different parallel configurations.  Recall that increased
+resource contention obtained with parallelism can lead to concurrency
+issues such as data races.  Flakiness and speedup are contradictory
+forces that drive configuration selection.  We used as a \emph{control
+group} (\ie, baseline) the sequential execution of each subject's
+tests. Notice that for measuring flakiness, we have to consider only
+tests that failed due to the concurrency in the parallel execution.
+For that reason, we re-executed the tests in sequence ten times and
+carefully verified that there are only passing tests in our baseline.
+We considered ten as the number of re-executions based on the approach
+used by Google reported in a previous work on test
+flakiness~\cite{luo-etal-fse2014}.  To obtain parallel configurations,
+we implemented a script that takes a subject and a configuration (\eg,
+\ForkSeq{}) as inputs, and the script outputs the modified version of
+the subject with the desired configuration. The workflow consists in
+copying the project directory to a new directory, finding all existing
+build files (\ie, \pomf{} files), and modifying all existing Maven
+Surefire configurations with new values for the parameters
+\CodeIn{parallel}, \CodeIn{forkCount}, and \CodeIn{threadCount} using
+an XPath~\cite{xpath} library to manipulate XML documents. For
+configurations with forked JVMs enabled (\ie, \ForkSeq{} and
+\ForkParMeth{}), we changed the \CodeIn{forkCount} with the value
+\CodeIn{1C} (\ie, one JVM per core).  To adjust the pool of threads
+for parallelism within a JVM, we changed the parameter
+\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
+number of native threads per core OR 6 as it represents 3 Cores * 2
+native threads?}.  To run the subjects and their respective variations
+(\ie, the modified versions according to the parallelism
 configuration), we used a similar approach as described in
@@
 average.  Figure~\ref{tab:rq6-table} summarizes the obtained results
-ordered by the time cost (\ie, $T_\text{cost}$).
+ordered by the time cost (\ie, $T_\text{cost}$). \Fix{Remember to
+explain efficiency cutoff, JVM crashes and timeout}
 

### 2017-05-06 paper/evaluation.tex
Added entries for next rows

@@
 \midrule%
+Jenkins CI Github            & \multicolumn{2}{c|}{\Fix{In execution!}} &  & & & & & & & & &\\%
+Hazelcast (\CodeIn{client})  & \multicolumn{2}{c|}{\Fix{In execution!}} &  & & & & & & & & &\\%
 OpenMRS Core (\CodeIn{api})  & \entry{13.8m}{3436} & \entry{-}{58.7\%}     & \entry{1.86x}{65.6\%} & \entry{2.01x}{61.6\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%

### 2017-05-09 paper/evaluation.tex
recent updates

--- 2017-05-06 paper/evaluation.tex
@@
 \newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
+\newcommand{\blankentry}{\entry{-}{-}}
 \newcommand{\subcol}{\subcolA{} & \subcolB{}}
@@
 \midrule%
-OpenMRS Core (\CodeIn{api})  & \entry{13.8m}{3436} & \entry{-}{58.7\%}     & \entry{1.86x}{65.6\%} & \entry{2.01x}{61.6\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Jankotek MapDB               & \entry{10m}{5218}   & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{3.9x}{0\%} & \colheader{\cellcolor{lightgray}timeout}\\%
-Apache Flume (\CodeIn{core}) & \entry{8.3m}{392}   & \entry{2.86x}{18.1\%} & \entry{-}{0\%} & \entry{2.78x}{16.8\%} & \entry{-}{0\%} & \entry{2.87x}{18.9\%}\\%
-Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Facebook Archive Linkbench   & \entry{4.6m}{392}   & \entry{-}{1\%}        & \entry{1.59x}{2\%} & \entry{-}{0\%} & \entry{1.7x}{1\%} & \entry{1.7x}{0\%}\\%
-Stripe Java                  & \entry{4.2m}{302}   & \entry{4.2x}{4.6\%}   & \entry{4.67}{4.6\%} & \entry{4.2x}{5.3\%} & \entry{-}{0\%} & \entry{4.2x}{4.6\%}\\%
+OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
+Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
+Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
+Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
+Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
+AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
 %% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

### 2017-05-09 paper/intro.tex
pass on abstract and intro

@@
 provide distributed infrastructures to efficiently build massive
-amounts of code and run tests.  Building server clusters is also a
+amounts of code and run tests.  Building in-house server clusters is also a
 popular mechanism to distribute testing workloads.  For example, as of
-August 2013, the Groupon PWA system, which powers the
+August 2013, the test suite fo the Groupon PWA system, which powers the
 \url{groupon.com} website, included over 19K tests.  To run all those
@@
 infrastructures to running tests is a legitimate approach to mitigate
-the regression testing problem.  However, for projects with low
-budgets and yet relatively heavy testing workloads, this solution may
+the regression testing problem.  However, for projects with modest
+ or inexistent budgets and yet relatively heavy testing workloads, this solution may
 not be economically viable.  For these cases, the use of commodity
@@
 testing infrastructures~---~led us to investigate the usage of
-parallelism to speed up test execution.  This paper reports on an
-empirical study we conducted to analyze the usage and impact of
-low-level parallelization in speeding up testing for open-source
-projects.  This is a relevant problem given the tremendous popularity
-of open-source development and regression testing
-research~\cite{yoo-harman-stvr2012}.
+parallelism to speed up test execution.
 
@@
 
-The dimensions of analysis we considered in this study are as follows:
-potential, effectiveness, adoption, and tradeoffs.  Each dimension
-focuses on one aspect of our study.  The dimension \textbf{potential}
-measures the potential of parallelization to reduce testing costs.  In
-the limit, parallelization would be fruitless if all projects used
-short-running test suites or if the bulk of execution cost was
-dominated by a single test in the suite.  The dimension
-\textbf{effectiveness} measures the observed impact of
-parallelization\Comment{~---~when used in selected open-source
-  projects~---~} on testing costs.  Intuitively, benefits are
-proportional to the cost reduction that parallelization brings.  In
-the limit, however, the overhead of spawning virtual machines or
-threads can even result in added cost.  The dimension
-\textbf{adoption} evaluates (i) how often open-source projects use
-parallelization schemes and (ii) how developers involved in costly
-projects (not using test suite parallelization) perceive this
-technology.  It is important to measure resistance to the technology
-and its reasons.  Finally, the dimension \textbf{tradeoffs} evaluates
-the issues and benefits associated with\Comment{running test suites
-  with} different parallel configurations.  Note that the
-configuration choice can affect both test cost and test flakiness,
-which is caused by the non-determinism resulted from running test
-methods and classes in different orderings.
+This paper reports on an empirical study we conducted to analyze the
+usage and impact of low-level parallelization in speeding up testing
+in open-source projects.  This is a relevant problem given the
+tremendous popularity of open-source development and regression
+testing research~\cite{yoo-harman-stvr2012}.  Note that
+parallelization is complementary to other approaches to mitigate
+testing costs such as (safe) test
+selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
+integration~\cite{Saff:2003:RWD:951952.952340}.  The dimensions of
+analysis we considered in this study are (i) potential, (iii)
+adoption, and (iii) tradeoffs, (iv) speedups.
+
+%% Each dimension
+%% focuses on one aspect of the study.
+
+The dimension \textbf{feasibility} measures the potential of
+parallelization to reduce testing costs.  In the limit,
+parallelization would be fruitless if all projects used short-running
+test suites or if the bulk of execution cost was dominated by a single
+test in the suite.  The dimension \textbf{adoption} evaluates (i) how
+often existing open-source projects use parallelization schemes and
+(ii) how developers involved in costly projects (not using test suite
+parallelization) perceive this technology.  It is important to measure
+resistance of practicioners to the technology and to understand their
+reasons.  The dimension \textbf{tradeoffs} evaluates the issues and
+benefits associated with\Comment{running test suites with} the use of
+possible parallel configurations.  Note that the configuration choice
+affects testing cost and flakiness, caused by the non-determinism
+resulted from running different schedulings of test methods and
+classes.  Finally, the dimension \textbf{speedups} measures the
+observed impact of parallelization\Comment{~---~when used in selected
+  open-source projects~---~} in running times.  We briefly summarize
+each of these dimensions in the following.
 
@@
 
-\subsection{Summary of ``Potential'' results}
-
+\vspace{1ex}\noindent\textbf{Feasibility.}~
 We selected \numSubjs{} popular Java projects from \github{}
@@
 
-\subsection{Summary of ``Effectiveness'' results}
-
-As to avoid introduction of unintended noise when measuring time, we
-evaluated effectiveness on projects that we knew a priori ran their
-test suite in parallel by default.  Results indicate that the average
-speedup of parallelization was \avgSpeedup{}x.  Although we found
-cases with very high speedups (\eg{}, 9.2x), we found some cases where
-speedups were insignificant.  \emph{Overall, our results suggest that
-  it may not be obvious to achieve huge speedups with test suite
-  parallelization.}
-
-\subsection{Summary of ``Adoption'' results}
-
-We considered two aspects in measuring adoption of the technology.
-First, we analyzed quantitatively current usage of parallelism in
-open-source projects.  Then, we investigated the key reasons that
-justify resistance of developers in using test suite parallelization.
-For the quantitative analysis we checked both statically (parsing
-build files) and dynamically (monitoring execution of build files) for
-the presence of parallelization.  Considering only those projects that
-take longer than a minute to run their test suites, we found that only
-\percentParallel{} of them use parallelism.  When considering the
-feedback received from developers involved in those projects we
-realized the proportion should was a bit higher, of
-\percentParallelUpdated{}, but still relatively low.  For the
-qualitative analysis we surveyed developers from a selection of costly
-projects that did not use parallelization.  Section~\ref{sec:rqE}
-details our selection methodology. \emph{Results indicate that dealing
-  with concurrency issues related with parallelization (in particular,
-  the extra work to organize test suite to safely explore concurrency)
-  was the main barrier for adoption.  Other reasons included
-  availability of continuous integration services and unfamiliarity
-  with the technology.}
+\vspace{1ex}\noindent\textbf{Adoption.}~ We considered two aspects in
+measuring technology adoption.  First, we measured usage of
+parallelism in open-source projects.  Then, we ran a survey with
+developers to understand the reasons that explain resistance to using
+the technology.  For the quantitative analysis we checked both
+statically (parsing build files) and dynamically (monitoring execution
+of build files) for the presence of parallelization.  Considering only
+those projects that take longer than a minute to run their test
+suites, we found that only \percentParallel{} of them use parallelism.
+When correcting this value with the feedback obtained a posteriori
+from developers, we realized that the proportion should be higher, of
+\percentParallelUpdated{}.  For the qualitative analysis we surveyed
+developers from a selection of costly projects that did not use
+parallelization.  \emph{Results indicate that test suite
+  parallelization is underutilized and dealing with concurrency issues
+  related with parallelization (\eg{}, the extra work to organize test
+  suite to avoid concurrency errors) was the main barrier for
+  adoption.  Other reasons included availability of continuous
+  integration services and unfamiliarity with the technology.}
 
@@
 
-\subsection{Summary of ``Tradeoff'' results}
-
+\vspace{1ex}\noindent\textbf{Tradeoffs.}~
 \Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
@@
   bla bla blabla bla bla blabla bla bla blabla bla bla bla}
+
+\vspace{1ex}\noindent\textbf{Speedups.}~
+%% \Mar{move to here} Intuitively, benefits are
+%% proportional to the cost reduction that parallelization brings.  In
+%% the limit, however, the overhead of spawning virtual machines or
+%% threads can even result in added cost.
+\Mar{...revise with scalability results...}
+As to avoid introduction of unintended noise when measuring time, we
+evaluated effectiveness on projects that we knew a priori ran their
+test suite in parallel by default.  Results indicate that the average
+speedup of parallelization was \avgSpeedup{}x.  Although we found
+cases with very high speedups (\eg{}, 9.2x), we found some cases where
+speedups were insignificant.  \emph{Overall, our results suggest that
+  it may not be obvious to achieve huge speedups with test suite
+  parallelization.}
+
+\Mar{write one or two lessons learned}
 

### 2017-05-10 paper/evaluation.tex
pass on eval

@@
+\newpage
 \section{Evaluation}
@@
 \newcommand{\numRQB}{RQ2}
-\newcommand{\numRQD}{RQ3}
-\newcommand{\numRQC}{RQ4}
-\newcommand{\numRQE}{RQ5}
-\newcommand{\numRQF}{RQ6}
+\newcommand{\numRQC}{RQ3}
+\newcommand{\numRQE}{RQ4}
+\newcommand{\numRQF}{RQ5}
+\newcommand{\numRQD}{RQ6}
+\newcommand{\numRQG}{RQ7}
 
@@
 \newcommand{\RQB}{How time is distributed across test cases?}
-\newcommand{\RQC}{How prevalent is the use of test suite
+\newcommand{\RQC}{How popular is test suite
   parallelization\Comment{ in open-source projects}?}
@@
   from using test suite parallelization?}
-\newcommand{\RQF}{To which extent parallel execution configurations affect testing
+\newcommand{\RQF}{How parallel execution configurations affect testing
   costs and flakiness?}
-
+\newcommand{\RQG}{How test execution scales with the number of
+  available CPUs?}
+
+\setlist[itemize]{leftmargin=1em}
 \begin{itemize}
-\item Potential
+\item Feasibility
   \begin{itemize}
@@
   \item \textbf{\numRQB.} \RQB    
-  \end{itemize}
-\item Effectiveness
-  \begin{itemize}
-  \item \textbf{\numRQD.} \RQD
   \end{itemize}
@@
   \item \textbf{\numRQF.} \RQF    
+  \end{itemize}
+\item Speedups
+  \begin{itemize}
+  \item \textbf{\numRQD.} \RQD
+  \item \textbf{\numRQG.} \RQG
   \end{itemize}    
@@
 
-\subsection{Potential}
+\subsection{Feasibility}
 \label{sec:rqA}
@@
 not uncommon, accounting to nearly \percentMedLongRunning{} of the
-\numSubjs{} projects we analyzed.  It is therefore important to
-speedup regressing testing in open-source projects.\Comment{not only
-  to huge projects as those from Google~\cite{google-tap,google-ci}
-  and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
-
-Research question \numRQB{} assesses whether parallelism can help in
-those cases.  One important factor to the effectiveness of parallelism
-is the distribution of test costs in the test suite.  In the limit, if
-cost is dominated by a single test from a large test suite, it is
-unlikely that parallelization will be beneficial as a test method is
-the smallest working unit in test frameworks.  However, avoiding
-frequent context switches is another factor to consider.  For example,
-assuming there are at least two CPUs available for execution, cost can
-be cut in half if two tests in a large test suite dominate execution
-time. For the case where cost is distributed more evenly across test
-cases, one expects that speedups will be a function of the number of
-cores.
-
+\numSubjs{} projects we analyzed.  Research question \numRQB{}
+measures the distribution of test costs in test suites as to estimate
+(lack of) potential of obtaining speedups with parallelization.  In
+the limit, if cost is dominated by a single test from a large test
+suite, it is unlikely that parallelization will be beneficial as a
+test method is the smallest working unit in test frameworks.
+
+%% However, avoiding
+%% frequent context switches is another factor to consider.  For example,
+%% assuming there are at least two CPUs available for execution, cost can
+%% be cut in half if two tests in a large test suite dominate execution
+%% time and these tests are assigned to different CPUs.
+
+%% It is therefore important to
+%% speedup regressing testing in open-source projects.\Comment{not only
+%%   to huge projects as those from Google~\cite{google-tap,google-ci}
+%%   and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
+
+%% For the case
+%% where cost is distributed more evenly across test cases, one expects
+%% that speedups will be a function of the number of cores.
 %% These contradictory forces, pushing number of tests and cost
@@
 short-running.  A closer inspection in the data indicates that the
-project \CodeIn{uber\_chaperone} was a corner case: we did not find
-projects with such extreme time monopolization profile.  Project
+project \CodeIn{uber\_chaperone} was a corner case; we did not find
+other projects with such extreme time monopolization profile.  Project
 \CodeIn{facebookarchive\_linkbench} is also classified as long-running
@@
 Figure~\ref{fig:time-distributions} showed that the average median
-times were similar.  A closer inspection on results indicates that the
-difference in overall running times across projects in these groups is
-mainly justified by the number of test cases as opposed to the
-individual costs of test cases.  Figure~\ref{fig:size-testsuites}
-shows the difference in the distribution of test suite sizes across
-groups.  This figure indicates that long projects, albeit having a
-wider inter-quartile range (middle 50\% projects in this group are
-less predictable), have a higher median and much higher averages.
-Furthermore, we noted a strong positive correlation between running
-time and number of test on projects in the \longg{} group.  The
-positive correlation between these two variables was, however, weak in
-the \medg{} group, suggesting that saving time in this group with test
-suite parallelization may be more challenging as relatively fewer
-tests dominate overall execution time.  Figure~\ref{fig:scattercost}
-shows these results.
+times were similar for \medg{} and \longg{}-running test suites.
+Results indicate that the difference in overall running times of
+projects in those groups was mainly justified by the number of test
+cases as opposed to the individual costs of test cases.
+Figure~\ref{fig:size-testsuites} shows the difference in the
+distribution of test suite sizes across groups.  This figure indicates
+that long projects, albeit having a wider inter-quartile range (middle
+50\% projects in this group are less predictable), have a higher
+median and much higher average number of test cases.  Furthermore, we
+noted a strong positive correlation between running time and number of
+test on projects in the \longg{} group.  Considering the \medg{}
+group, the correlation between these two variables was weak.
+Figure~\ref{fig:scattercost} illustrates this correlation.
+
+%% however, weak in
+%% the suggesting that saving time in this group with test suite
+%% parallelization may be more challenging as relatively fewer tests
+%% dominate overall execution time.  Figure~\ref{fig:scattercost} shows
+%% these results.
 
@@
 %% since a small subset of test cases dominates the execution.}
-
-\subsection{Effectiveness}
-\label{sec:rqD}
-
-\begin{itemize}
-    \item \numRQD{}. \textbf{\RQD}
-\end{itemize}
-
-To answer \numRQD{}, we considered \numProjectsPar{} subjects from our
-benchmark that use parallelization \emph{by default} when running
-tests.  In those projects, parallelization is active without passing
-any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
-methodology we used to find these subjects.
-%and
-%Section~\ref{seq:rq6-tradeoffs}, we verified that both
-%% executions produce the same outcome to eliminate noise from failing
-%% tests.  To compute the speedup, we divide the time obtained in the
-%% sequential execution by the time obtained from the default execution.
-%% For instance, if a project runs the tests sequentially in $10m$ and
-%% the same execution runs in $5m$ with parallelization enabled (default
-%% execution), the speedup is two.
-
-\begin{figure}[h!]
-\centering
-\resizebox{.48\textwidth}{!}{%
-\begin{tabular}{llrrl}
-\toprule
-\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
-\midrule%
-Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 
-    \cellcolor{lightgray}1.02x\\%
-Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%
-Long & Jenkins CI \textbf{Gerrit} Plugin & 51.19m & 40.31m &  1.26x\\%
-Medium & Spotify \textbf{Helios} & 4.46m & 1.63m & 2.73x\\%  
-Medium & \textbf{Javaslang} & 2.18m & 1.82m & 1.19x\\%
-Medium & \textbf{Jcabi} GitHub & 2.76m & 0.30m &
-    \cellcolor{lightgray}9.2x\\%
-Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
-Medium & Apache \textbf{Log4J2} & 8.24m & 8.21m & 
-    \cellcolor{lightgray}1.00x\\%
-Medium & Jankotek \textbf{MapDB} & 10.06m & 8.58m & 1.17x\\%
-\midrule
-\textbf{average} &  &  &  & \avgSpeedup{}x\\
-\bottomrule%
-\end{tabular}}
-\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
-  sequential execution ($T_s$).  Default parallel configuration of
-  Maven is used.  Abbreviation of project names appear in bold face
-  and highest slowdown/speedup appear in gray color.}
-\label{tab:speedup}
-\end{figure}
-
-Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
-abbreviated project names, which appear in bold.  Columns
-``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
-project group and the name of the subject.  Column ``$T_s$'' shows
-sequential execution time whereas column ``$T_p$'' shows parallel
-execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
-associated with parallel execution.   As usual, a ratio
-above 1x denotes speedup and a ratio below 1x denotes slowdown.
-
-Results indicate that, on average, parallel execution was
-\avgSpeedup{} times faster compared to sequential execution.  Three
-cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
-\CodeIn{Log4J2}.  No significant speedup was observed in
-\CodeIn{Chaos}, a project with only three test classes, of which one
-monopolizes the bulk of test execution time.  This project uses
-configuration \ParClassSeqMeth{}, which runs test classes in parallel
-and test methods, declared in each class, sequentially.  Consequently,
-speedup cannot be obtained as the cost of the single expensive test
-class cannot be broken down with the selected configuration.  Although
-project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
-results obtained are very different compared to \CodeIn{Chaos}.  The
-speedup observed in \CodeIn{Jcabi} was the highest amongst all
-projects.  This project contains test classes with a small number of
-test methods and several methods in those classes are time-consuming.
-As result, the CPUs available for testing are kept occupied for the
-most part during test execution.  Finally, we note that parallel
-execution in \CodeIn{Log4J2} was innefective.  We found that Maven
-invokes several test modules in this project but the test modules that
-dominate execution time run sequentially by default.
-
-%% The third, runs parallel configuration in
-%% \Fix{80\%} of the project modules, however, the test time is dominated
-%% by one of the sequentially running modules.  \Luis{$\leftarrow$ rework
-%%   this} \Fix{falar sobre o resultado geral dos speedups - elaborar
-%%   menor e maior speedup... acho que so vale a pena discutir quando
-%%   tiver conviccao dos 2 casos}
-
-\begin{center}
-\fbox{
-  \begin{minipage}{8cm}
-    \textit{Answering \numRQD{}:}~\emph{ The average speedup observed
-      with default configurations of parallelization was
-      \avgSpeedup{}x.}
-  \end{minipage}
-}
-\end{center}
 
@@
 
+%% Table header macros
+\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
+\newcommand{\subcolB}{$\%_\text{fail}$}
+\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
+\newcommand{\blankentry}{\entry{-}{-}}
+\newcommand{\subcol}{\subcolA{} & \subcolB{}}
+\newcommand{\entry}[2]{#1 & #2}
+
+\begin{figure*}[t]
+\centering
+\small
+\begin{tabular}{l|rr|rrrrrrrrrr}
+\toprule
+\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
+    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
+    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
+    \colheader{\ForkParMeth} \\ %\cline{2-12}
+    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
+    & \subcol{}\\%
+\midrule%
+OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
+Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
+Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
+Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
+Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
+AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
+%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
+
+\bottomrule%
+\end{tabular}
+\caption{\Fix{Tabela de eficiencia e flakiness}}
+\label{tab:rq6-table}
+\end{figure*}
+
 To answer this research question, we conducted an experiment involving
@@
 configuration), we used a similar approach as described in
+
 Figure~\ref{fig:mvn-execution} except that we added a timeout of one
@@
 explain efficiency cutoff, JVM crashes and timeout}
-
-%% Table header macros
-\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
-\newcommand{\subcolB}{$\%_\text{fail}$}
-\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
-\newcommand{\blankentry}{\entry{-}{-}}
-\newcommand{\subcol}{\subcolA{} & \subcolB{}}
-\newcommand{\entry}[2]{#1 & #2}
-
-\begin{figure*}[t]
-\centering
-\small
-\begin{tabular}{l|rr|rrrrrrrrrr}
-\toprule
-\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
-    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
-    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
-    \colheader{\ForkParMeth} \\ %\cline{2-12}
-    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
-    & \subcol{}\\%
-\midrule%
-OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
-Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
-Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
-Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
-Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
-AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
-%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-
-\bottomrule%
-\end{tabular}
-\caption{\Fix{Tabela de eficiencia e flakiness}}
-\label{tab:rq6-table}
-\end{figure*}
 
@@
 
+\subsection{Speedups}
+\label{sec:rqD}
+
+\begin{itemize}
+    \item \numRQD{}. \textbf{\RQD}
+\end{itemize}
+
+To answer \numRQD{}, we considered \numProjectsPar{} subjects from our
+benchmark that use parallelization \emph{by default} when running
+tests.  In those projects, parallelization is active without passing
+any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
+methodology we used to find these subjects.
+%and
+%Section~\ref{seq:rq6-tradeoffs}, we verified that both
+%% executions produce the same outcome to eliminate noise from failing
+%% tests.  To compute the speedup, we divide the time obtained in the
+%% sequential execution by the time obtained from the default execution.
+%% For instance, if a project runs the tests sequentially in $10m$ and
+%% the same execution runs in $5m$ with parallelization enabled (default
+%% execution), the speedup is two.
+
+Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
+abbreviated project names, which appear in bold.  Columns
+``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
+project group and the name of the subject.  Column ``$T_s$'' shows
+sequential execution time whereas column ``$T_p$'' shows parallel
+execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
+associated with parallel execution.   As usual, a ratio
+above 1x denotes speedup and a ratio below 1x denotes slowdown.
+
+\begin{figure}[h!]
+\footnotesize
+\centering
+\resizebox{.45\textwidth}{!}{%
+\begin{tabular}{llrrr}
+\toprule
+\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
+\midrule%
+Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
+    \cellcolor{lightgray}1.01x\\%
+Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
+Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
+Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
+Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
+Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
+    \cellcolor{lightgray}9.2x\\%
+Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
+Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
+Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
+\midrule
+\textbf{average} &  &  &  & \avgSpeedup{}x\\
+\bottomrule%
+\end{tabular}}
+\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
+  sequential execution ($T_s$).  Default parallel configuration of
+  Maven is used.  Abbreviation of project names appear in bold face
+  and highest slowdown/speedup appear in gray color.}
+\label{tab:speedup}
+\end{figure}
+
+Results indicate that, on average, parallel execution was
+\avgSpeedup{} times faster compared to sequential execution.  Three
+cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
+\CodeIn{Log4J2}.  No significant speedup was observed in
+\CodeIn{Chaos}, a project with only three test classes, of which one
+monopolizes the bulk of test execution time.  This project uses
+configuration \ParClassSeqMeth{}, which runs test classes in parallel
+and test methods, declared in each class, sequentially.  Consequently,
+speedup cannot be obtained as the cost of the single expensive test
+class cannot be broken down with the selected configuration.  Although
+project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
+results obtained are very different compared to \CodeIn{Chaos}.  The
+speedup observed in \CodeIn{Jcabi} was the highest amongst all
+projects.  This project contains test classes with a small number of
+test methods and several methods in those classes are time-consuming.
+As result, the CPUs available for testing are kept occupied for the
+most part during test execution.  Finally, we note that parallel
+execution in \CodeIn{Log4J2} was innefective.  We found that Maven
+invokes several test modules in this project but the test modules that
+dominate execution time run sequentially by default.
+
+%% The third, runs parallel configuration in
+%% \Fix{80\%} of the project modules, however, the test time is dominated
+%% by one of the sequentially running modules.  \Luis{$\leftarrow$ rework
+%%   this} \Fix{falar sobre o resultado geral dos speedups - elaborar
+%%   menor e maior speedup... acho que so vale a pena discutir quando
+%%   tiver conviccao dos 2 casos}
+
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+    \textit{Answering \numRQD{}:}~\emph{ The average speedup observed
+      with default configurations of parallelization was
+      \avgSpeedup{}x.}
+  \end{minipage}
+}
+\end{center}
+
 \subsection{Threats to Validity}

### 2017-05-10 paper/evaluation.tex
restructure

@@
 \newpage
-\section{Evaluation}
-\label{sec:eval}
-
-%% We are interested in understanding the prevalence of time-consuming
-%% test suites and main sources of execution cost. We want to understand
-%% how the execution cost is distributed on test cases within a test
-%% suite and how developers approach test execution. Based on that, we
-%% study parallelization of testing frameworks and build systems.  More
-%% precisely, we investigate how prevalent test parallelization is, the
-%% potential for improving execution cost, issues of flakiness that
-%% hinders the use of parallelization, and how to address those issues.
-%% More specifically, we pose the following research questions:
-
-%% The first research question addresses the prevalence of long-running
-%% test suites. We are interested to know if costly test suites are
-%% common in open-source projects.  The second research question
-%% addresses the relationship of test cases and the overall execution
-%% cost: we are interested to investigate how the execution time is
-%% distributed among test cases.  In the third research question, we
-%% investigate if developers consider low-level parallelism features
-%% available out-of-the-box to amortize test execution (see
-%% Section~\ref{sec:modes}). In addition, we want to identify what
-%% configurations are often used and why they are more popular (if any).
-%% The fourth research question addresses the impact of low-level
-%% parallelism on test execution from projects in our sample set. We want
-%% to identify subjects that already use test parallelization and compare
-%% their performance in contrast to sequential execution. In addition, we
-%% are interested in evaluating the performance of sequential test suites
-%% with different parallelization settings.
-%% Finally, the fifth research question discusses the limitations and
-%% insights to overcome the pitfalls of parallelization.
-
-%% \Comment{
-%%     \Fix{distribution of execution time per test case. For each subject
-%%     identified in the first research question, we investigate how
-%%     balanced is the cost of the test suite in contrast to the cost of
-%%     test cases and if there are subjects where the time cost is mostly
-%%     dominated by a small fraction of test cases.} \Fix{The third research
-%%     question addresses the distribution of regression tests according
-%%     to the use of computational resources.  We are interested in
-%%     investigating if regression test suites are CPU intensive and if there
-%%     are opportunities to improve performance. The RQ4 addresses}
-%%     \Fix{...elaborate...}
-
-%%     The rationale is that if the time cost of a regression test is equally
-%%     distributed among test cases, the execution cost could be potentially
-%%     improved by running tests in parallel (in contrast to the scenario
-%%     where only one test case dominates most of the execution time).
-%% }
-
-We pose the following research questions, organized by the dimensions
-of analysis we presented in Section~\ref{sec:intro}.
-
-\newcommand{\numRQA}{RQ1}
-\newcommand{\numRQB}{RQ2}
-\newcommand{\numRQC}{RQ3}
-\newcommand{\numRQE}{RQ4}
-\newcommand{\numRQF}{RQ5}
-\newcommand{\numRQD}{RQ6}
-\newcommand{\numRQG}{RQ7}
-
-\newcommand{\RQA}{How prevalent is the occurence of time-consuming
-  test suites\Comment{ in open-source projects}?}
-\newcommand{\RQB}{How time is distributed across test cases?}
-\newcommand{\RQC}{How popular is test suite
-  parallelization\Comment{ in open-source projects}?}
-\newcommand{\RQD}{What are the speedups obtained with parallelization
-  (in projects that actually use it) on cost?}
-\newcommand{\RQE}{What are the main reasons that prevent developers
-  from using test suite parallelization?}
-\newcommand{\RQF}{How parallel execution configurations affect testing
-  costs and flakiness?}
-\newcommand{\RQG}{How test execution scales with the number of
-  available CPUs?}
-
-\setlist[itemize]{leftmargin=1em}
-\begin{itemize}
-\item Feasibility
-  \begin{itemize}
-  \item \textbf{\numRQA.} \RQA
-  \item \textbf{\numRQB.} \RQB    
-  \end{itemize}
-\item Adoption
-  \begin{itemize}
-  \item \textbf{\numRQC.} \RQC    
-  \item \textbf{\numRQE.} \RQE
-  \end{itemize}
-\item Tradeoffs
-  \begin{itemize}
-  \item \textbf{\numRQF.} \RQF    
-  \end{itemize}
-\item Speedups
-  \begin{itemize}
-  \item \textbf{\numRQD.} \RQD
-  \item \textbf{\numRQG.} \RQG
-  \end{itemize}    
-\end{itemize}
-
-%%\newcommand{\RQB}{What is the distribution of CPU and IO bound
-%%regression test suites from the sample set?}
-%%
-%%\newcommand{\RQC}{How uniformly distributed is the execution time
-%%across test cases in costly projects?}
-%%
-%%\newcommand{\RQD}{How often developers use the parallelism features
-%%from build systems to improve runtime performance?}
-
-\subsection{Subjects}
+\section{Objects of Analysis}
 \label{sec:subjects}
@@
 \emph{pom.xml}).  Figure~\ref{fig:subject-query} illustrates the query
-to the \github{} API as an HTTP request.  After obtaining a list of
-potential projects, we filtered those containing a \pomf{} file in the
-root directory.  A Maven project may contain several sub-modules with
-multiple \pomf{} files.  We based our methodology to select
-experimental subjects on other recent studies in testing and
-debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.
+to the \github{} API as an HTTP request.
 
@@
 
+After obtaining a list of
+potential projects, we filtered those containing a \pomf{} file in the
+root directory.  A Maven project may contain several sub-modules with
+multiple \pomf{} files.\Comment{  We based our methodology to select
+experimental subjects on other recent studies in testing and
+debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.}
 As of March 25th 2017, our search criteria returned \SubjectsGithub{}
-subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
-\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
-projects were not Maven or did not have a \pomf{} in the root
-directory, \SubjectsGithubNotTestable{} projects were untestable
-(because of missing dependencies or incompatible testing environment,
-for example), and \SubjectsGithubFlaky{} projects were ``flaky''.
-\Jbc{Check if this is ok $\rightarrow$} We executed each project's
-test suite for three times to identify projects containing flaky tests
-and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
-from JUnit) to avoid introducing noise in our experiments.  Our final
-set of subjects consists of \numSubjs{} projects.
+subjects. Figure~\ref{fig:subjects} summarizes our sample set.
 
@@
 \end{figure}
+
+From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
+projects were not Maven or did not have a \pomf{} in the root
+directory, \SubjectsGithubNotTestable{} projects were untestable
+because of missing dependencies or incompatible testing environment,
+for example, and \SubjectsGithubFlaky{} projects were ``flaky''.
+\Jbc{Check if this is ok $\rightarrow$} We executed each project's
+test suite for three times to identify projects containing flaky tests
+and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
+from JUnit) to avoid introducing noise in our experiments.  Our final
+set of subjects consists of \numSubjs{} projects.
 
@@
 
+\section{Evaluation}
+\label{sec:eval}
+
+%% We are interested in understanding the prevalence of time-consuming
+%% test suites and main sources of execution cost. We want to understand
+%% how the execution cost is distributed on test cases within a test
+%% suite and how developers approach test execution. Based on that, we
+%% study parallelization of testing frameworks and build systems.  More
+%% precisely, we investigate how prevalent test parallelization is, the
+%% potential for improving execution cost, issues of flakiness that
+%% hinders the use of parallelization, and how to address those issues.
+%% More specifically, we pose the following research questions:
+
+%% The first research question addresses the prevalence of long-running
+%% test suites. We are interested to know if costly test suites are
+%% common in open-source projects.  The second research question
+%% addresses the relationship of test cases and the overall execution
+%% cost: we are interested to investigate how the execution time is
+%% distributed among test cases.  In the third research question, we
+%% investigate if developers consider low-level parallelism features
+%% available out-of-the-box to amortize test execution (see
+%% Section~\ref{sec:modes}). In addition, we want to identify what
+%% configurations are often used and why they are more popular (if any).
+%% The fourth research question addresses the impact of low-level
+%% parallelism on test execution from projects in our sample set. We want
+%% to identify subjects that already use test parallelization and compare
+%% their performance in contrast to sequential execution. In addition, we
+%% are interested in evaluating the performance of sequential test suites
+%% with different parallelization settings.
+%% Finally, the fifth research question discusses the limitations and
+%% insights to overcome the pitfalls of parallelization.
+
+%% \Comment{
+%%     \Fix{distribution of execution time per test case. For each subject
+%%     identified in the first research question, we investigate how
+%%     balanced is the cost of the test suite in contrast to the cost of
+%%     test cases and if there are subjects where the time cost is mostly
+%%     dominated by a small fraction of test cases.} \Fix{The third research
+%%     question addresses the distribution of regression tests according
+%%     to the use of computational resources.  We are interested in
+%%     investigating if regression test suites are CPU intensive and if there
+%%     are opportunities to improve performance. The RQ4 addresses}
+%%     \Fix{...elaborate...}
+
+%%     The rationale is that if the time cost of a regression test is equally
+%%     distributed among test cases, the execution cost could be potentially
+%%     improved by running tests in parallel (in contrast to the scenario
+%%     where only one test case dominates most of the execution time).
+%% }
+
+We pose the following research questions, organized by the dimensions
+of analysis we presented in Section~\ref{sec:intro}.
+
+%% Feasibility
+\newcommand{\numRQFeasibilityOne}{RQ1}
+\newcommand{\RQFeasibilityOne}{How prevalent is the occurence of time-consuming
+  test suites\Comment{ in open-source projects}?}
+
+\newcommand{\numRQFeasibilityTwo}{RQ2}
+\newcommand{\RQFeasibilityTwo}{How time is distributed across test cases?}
+
+%% Adoption
+\newcommand{\numRQAdoptionOne}{RQ3}
+\newcommand{\RQAdoptionOne}{How popular is test suite
+  parallelization\Comment{ in open-source projects}?}
+
+\newcommand{\numRQAdoptionTwo}{RQ4}
+\newcommand{\RQAdoptionTwo}{What are the main reasons that prevent developers
+  from using test suite parallelization?}
+
+%% Speedups
+\newcommand{\numRQSpeedupOne}{RQ5}
+\newcommand{\RQSpeedupOne}{What are the speedups obtained with parallelization
+  (in projects that actually use it)?}
+
+\newcommand{\numRQSpeedupTwo}{RQ6}
+\newcommand{\RQSpeedupTwo}{How test execution scales with the number of
+  available CPUs?}
+
+%% Issues
+\newcommand{\numRQIssuesOne}{RQ7}
+\newcommand{\RQIssuesOne}{How parallel execution configurations affect testing
+  costs and flakiness?}
+
+\setlist[itemize]{leftmargin=1em}
+\begin{itemize}
+\item Feasibility
+  \begin{itemize}
+  \item \textbf{\numRQFeasibilityOne.} \RQFeasibilityOne
+  \item \textbf{\numRQFeasibilityTwo.} \RQFeasibilityTwo    
+  \end{itemize}
+\item Adoption
+  \begin{itemize}
+  \item \textbf{\numRQAdoptionOne.} \RQAdoptionOne    
+  \item \textbf{\numRQAdoptionTwo.} \RQAdoptionTwo
+  \end{itemize}
+\item Speedups
+  \begin{itemize}
+  \item \textbf{\numRQSpeedupOne.} \RQSpeedupOne
+  \item \textbf{\numRQSpeedupTwo.} \RQSpeedupTwo
+  \end{itemize}      
+\item Issues
+  \begin{itemize}
+  \item \textbf{\numRQIssuesOne.} \RQIssuesOne    
+  \end{itemize}
+\end{itemize}
+
+%%\newcommand{\RQFeasibilityTwo}{What is the distribution of CPU and IO bound
+%%regression test suites from the sample set?}
+%%
+%%\newcommand{\RQAdoptionOne}{How uniformly distributed is the execution time
+%%across test cases in costly projects?}
+%%
+%%\newcommand{\RQAdoptionTwo}{How often developers use the parallelism features
+%%from build systems to improve runtime performance?}
+
 \subsection{Feasibility}
@@
 \begin{itemize}
-    \item \numRQA{}. \textbf{\RQA}
+    \item \numRQFeasibilityOne{}. \textbf{\RQFeasibilityOne}
 \end{itemize}
@@
 \begin{minipage}{8cm}
-    \textit{Answering \numRQA{}:}~\emph{We conclude that
+    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
       time-consuming test suites are relatively frequent in
@@
 \begin{itemize}
-    \item \numRQB. \textbf{\RQB}
+    \item \numRQFeasibilityTwo. \textbf{\RQFeasibilityTwo}
 \end{itemize}
@@
 not uncommon, accounting to nearly \percentMedLongRunning{} of the
-\numSubjs{} projects we analyzed.  Research question \numRQB{}
+\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
 measures the distribution of test costs in test suites as to estimate
@@
 \begin{minipage}{8cm}
-    \textit{Answering \numRQB{}:}~\emph{Overall, results indicate that
+    \textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
     projects with a very small number of tests monopolizing end-to-end
@@
 %% We also evaluated the dispersion of time distributions (one
-%% distribution per project) to answer research question \numRQB{}.  To
+%% distribution per project) to answer research question \numRQFeasibilityTwo{}.  To
 %% measure dispersion \emph{across} projects we used Relative Standard
@@
 The dimension adoption focuses on the usage of parallelism in
-open-source projects.  It evaluates (\numRQC) how often open-source
-projects use parallelization schemes and (\numRQE) how developers
+open-source projects.  It evaluates (\numRQAdoptionOne) how often open-source
+projects use parallelization schemes and (\numRQSpeedupOne) how developers
 involved in costly projects, not using parallelization, perceive this
@@
 \begin{itemize}
-    \item \numRQC. \textbf{\RQC{}}
+    \item \numRQAdoptionOne. \textbf{\RQAdoptionOne{}}
 \end{itemize}
 
-To answer \numRQC{}, we selected all projects from the \medg{} and
+To answer \numRQAdoptionOne{}, we selected all projects from the \medg{} and
 \longg{} groups, \ie, projects that ran in at least one minute.  This
@@
   \begin{minipage}{8cm}
-      \textit{Answering \numRQC{}:}~\emph{Results indicate that test
+      \textit{Answering \numRQAdoptionOne{}:}~\emph{Results indicate that test
         suite parallelization is underused.  Overall, only
@@
 \begin{itemize}
-	\item \numRQE{}. \textbf{\RQE{}}
+	\item \numRQAdoptionTwo{}. \textbf{\RQAdoptionTwo{}}
 \end{itemize}
@@
 this change significant enough to modify our conclusion about
-practical adoption of parallelization (\numRQC{}).
+practical adoption of parallelization (\numRQAdoptionOne{}).
 
@@
 	\begin{minipage}{8cm}
-	  \textit{Answering \numRQE{}:}~\emph{Results suggest that dealing
+	  \textit{Answering \numRQAdoptionTwo{}:}~\emph{Results suggest that dealing
        with concurrency issues (\ie{}, the extra work to organize test
@@
 
-\subsection{Tradeoffs}
+\subsection{Speedups}
+\label{sec:rqD}
+
+\begin{itemize}
+    \item \numRQSpeedupOne{}. \textbf{\RQSpeedupOne}
+\end{itemize}
+
+To answer \numRQSpeedupOne{}, we considered \numProjectsPar{} subjects from our
+benchmark that use parallelization \emph{by default} when running
+tests.  In those projects, parallelization is active without passing
+any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
+methodology we used to find these subjects.
+%and
+%Section~\ref{seq:rq6-tradeoffs}, we verified that both
+%% executions produce the same outcome to eliminate noise from failing
+%% tests.  To compute the speedup, we divide the time obtained in the
+%% sequential execution by the time obtained from the default execution.
+%% For instance, if a project runs the tests sequentially in $10m$ and
+%% the same execution runs in $5m$ with parallelization enabled (default
+%% execution), the speedup is two.
+
+Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
+abbreviated project names, which appear in bold.  Columns
+``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
+project group and the name of the subject.  Column ``$T_s$'' shows
+sequential execution time whereas column ``$T_p$'' shows parallel
+execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
+associated with parallel execution.   As usual, a ratio
+above 1x denotes speedup and a ratio below 1x denotes slowdown.
+
+\begin{figure}[h!]
+\footnotesize
+\centering
+\resizebox{.45\textwidth}{!}{%
+\begin{tabular}{llrrr}
+\toprule
+\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
+\midrule%
+Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
+    \cellcolor{lightgray}1.01x\\%
+Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
+Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
+Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
+Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
+Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
+    \cellcolor{lightgray}9.2x\\%
+Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
+Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
+Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
+\midrule
+\textbf{average} &  &  &  & \avgSpeedup{}x\\
+\bottomrule%
+\end{tabular}}
+\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
+  sequential execution ($T_s$).  Default parallel configuration of
+  Maven is used.  Abbreviation of project names appear in bold face
+  and highest slowdown/speedup appear in gray color.}
+\label{tab:speedup}
+\end{figure}
+
+Results indicate that, on average, parallel execution was
+\avgSpeedup{} times faster compared to sequential execution.  Three
+cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
+\CodeIn{Log4J2}.  No significant speedup was observed in
+\CodeIn{Chaos}, a project with only three test classes, of which one
+monopolizes the bulk of test execution time.  This project uses
+configuration \ParClassSeqMeth{}, which runs test classes in parallel
+and test methods, declared in each class, sequentially.  Consequently,
+speedup cannot be obtained as the cost of the single expensive test
+class cannot be broken down with the selected configuration.  Although
+project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
+results obtained are very different compared to \CodeIn{Chaos}.  The
+speedup observed in \CodeIn{Jcabi} was the highest amongst all
+projects.  This project contains test classes with a small number of
+test methods and several methods in those classes are time-consuming.
+As result, the CPUs available for testing are kept occupied for the
+most part during test execution.  Finally, we note that parallel
+execution in \CodeIn{Log4J2} was innefective.  We found that Maven
+invokes several test modules in this project but the test modules that
+dominate execution time run sequentially by default.
+
+%% The third, runs parallel configuration in
+%% \Fix{80\%} of the project modules, however, the test time is dominated
+%% by one of the sequentially running modules.  \Luis{$\leftarrow$ rework
+%%   this} \Fix{falar sobre o resultado geral dos speedups - elaborar
+%%   menor e maior speedup... acho que so vale a pena discutir quando
+%%   tiver conviccao dos 2 casos}
+
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+    \textit{Answering \numRQSpeedupOne{}:}~\emph{ The average speedup observed
+      with default configurations of parallelization was
+      \avgSpeedup{}x.}
+  \end{minipage}
+}
+\end{center}
+
+\begin{itemize}
+    \item \numRQSpeedupTwo{}. \textbf{\RQSpeedupTwo}
+\end{itemize}
+
+\begin{center}
+\fbox{
+  \begin{minipage}{8cm}
+    \textit{Answering \numRQSpeedupTwo{}:}~\emph{...}
+  \end{minipage}
+}
+\end{center}
+
+\subsection{Issues}
 \label{sec:rq6-tradeoffs}
@@
 \begin{itemize}
-    \item \numRQF{}. \textbf{\RQF{}}
+    \item \numRQIssuesOne{}. \textbf{\RQIssuesOne{}}
 \end{itemize}
@@
 \begin{minipage}{8cm}
-\textit{Answering \numRQF{}:~\emph{\Jbc{summarize findings...}}}
-\end{minipage}
-}
-\end{center}
-
-\subsection{Speedups}
-\label{sec:rqD}
-
-\begin{itemize}
-    \item \numRQD{}. \textbf{\RQD}
-\end{itemize}
-
-To answer \numRQD{}, we considered \numProjectsPar{} subjects from our
-benchmark that use parallelization \emph{by default} when running
-tests.  In those projects, parallelization is active without passing
-any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
-methodology we used to find these subjects.
-%and
-%Section~\ref{seq:rq6-tradeoffs}, we verified that both
-%% executions produce the same outcome to eliminate noise from failing
-%% tests.  To compute the speedup, we divide the time obtained in the
-%% sequential execution by the time obtained from the default execution.
-%% For instance, if a project runs the tests sequentially in $10m$ and
-%% the same execution runs in $5m$ with parallelization enabled (default
-%% execution), the speedup is two.
-
-Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
-abbreviated project names, which appear in bold.  Columns
-``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
-project group and the name of the subject.  Column ``$T_s$'' shows
-sequential execution time whereas column ``$T_p$'' shows parallel
-execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
-associated with parallel execution.   As usual, a ratio
-above 1x denotes speedup and a ratio below 1x denotes slowdown.
-
-\begin{figure}[h!]
-\footnotesize
-\centering
-\resizebox{.45\textwidth}{!}{%
-\begin{tabular}{llrrr}
-\toprule
-\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
-\midrule%
-Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
-    \cellcolor{lightgray}1.01x\\%
-Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
-Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
-Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
-Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
-Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
-    \cellcolor{lightgray}9.2x\\%
-Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
-Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
-Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
-\midrule
-\textbf{average} &  &  &  & \avgSpeedup{}x\\
-\bottomrule%
-\end{tabular}}
-\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
-  sequential execution ($T_s$).  Default parallel configuration of
-  Maven is used.  Abbreviation of project names appear in bold face
-  and highest slowdown/speedup appear in gray color.}
-\label{tab:speedup}
-\end{figure}
-
-Results indicate that, on average, parallel execution was
-\avgSpeedup{} times faster compared to sequential execution.  Three
-cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
-\CodeIn{Log4J2}.  No significant speedup was observed in
-\CodeIn{Chaos}, a project with only three test classes, of which one
-monopolizes the bulk of test execution time.  This project uses
-configuration \ParClassSeqMeth{}, which runs test classes in parallel
-and test methods, declared in each class, sequentially.  Consequently,
-speedup cannot be obtained as the cost of the single expensive test
-class cannot be broken down with the selected configuration.  Although
-project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
-results obtained are very different compared to \CodeIn{Chaos}.  The
-speedup observed in \CodeIn{Jcabi} was the highest amongst all
-projects.  This project contains test classes with a small number of
-test methods and several methods in those classes are time-consuming.
-As result, the CPUs available for testing are kept occupied for the
-most part during test execution.  Finally, we note that parallel
-execution in \CodeIn{Log4J2} was innefective.  We found that Maven
-invokes several test modules in this project but the test modules that
-dominate execution time run sequentially by default.
-
-%% The third, runs parallel configuration in
-%% \Fix{80\%} of the project modules, however, the test time is dominated
-%% by one of the sequentially running modules.  \Luis{$\leftarrow$ rework
-%%   this} \Fix{falar sobre o resultado geral dos speedups - elaborar
-%%   menor e maior speedup... acho que so vale a pena discutir quando
-%%   tiver conviccao dos 2 casos}
-
-\begin{center}
-\fbox{
-  \begin{minipage}{8cm}
-    \textit{Answering \numRQD{}:}~\emph{ The average speedup observed
-      with default configurations of parallelization was
-      \avgSpeedup{}x.}
+\textit{Answering \numRQIssuesOne{}:~\emph{\Jbc{summarize findings...}}}
 \end{minipage}

### 2017-05-10 paper/intro.tex
restructure

@@
 analysis we considered in this study are (i) potential, (iii)
-adoption, and (iii) tradeoffs, (iv) speedups.
+adoption, and (iii) flakiness, (iv) speedups.
 
@@
 test suites or if the bulk of execution cost was dominated by a single
-test in the suite.  The dimension \textbf{adoption} evaluates (i) how
+test in the suite.  The dimension \textbf{adoption} evaluates how
 often existing open-source projects use parallelization schemes and
-(ii) how developers involved in costly projects (not using test suite
+how developers involved in costly projects (not using test suite
 parallelization) perceive this technology.  It is important to measure
 resistance of practicioners to the technology and to understand their
-reasons.  The dimension \textbf{tradeoffs} evaluates the issues and
-benefits associated with\Comment{running test suites with} the use of
-possible parallel configurations.  Note that the configuration choice
-affects testing cost and flakiness, caused by the non-determinism
-resulted from running different schedulings of test methods and
-classes.  Finally, the dimension \textbf{speedups} measures the
-observed impact of parallelization\Comment{~---~when used in selected
-  open-source projects~---~} in running times.  We briefly summarize
-each of these dimensions in the following.
+reasons.  The dimension \textbf{issues} reports the observed problems
+associated with running tests in parallel.  For example, test
+flakiness, which is caused by interference on shared state from
+non-deterministic executions of test methods and classes.  Finally,
+the dimension \textbf{speedups} evaluates the observed impact of
+parallelization\Comment{~---~when used in selected open-source
+  projects~---~} in running times.  We briefly summarize each of these
+dimensions in the following.
 
@@
 
-\vspace{1ex}\noindent\textbf{Tradeoffs.}~
+\vspace{1ex}\noindent\textbf{Issues.}~
 \Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla

### 2017-05-10 paper/evaluation.tex
another pass

@@
 
-To answer \numRQSpeedupOne{}, we considered \numProjectsPar{} subjects from our
-benchmark that use parallelization \emph{by default} when running
-tests.  In those projects, parallelization is active without passing
-any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
-methodology we used to find these subjects.
+To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
+subjects from our benchmark that use parallelization \emph{by default}
+(see Figure~\ref{tab:freqmodes-dynamic}).  We compared running times
+with parallelization~---~configured by project owners~---~and without
+parallelization.
+
+%% In those projects, parallelization is active without
+%% passing any extra parameters.  Section~\ref{sec:rqC-1} describes in
+%% detail the methodology we used to find these subjects.
 %and
@@
 Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
-abbreviated project names, which appear in bold.  Columns
-``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
-project group and the name of the subject.  Column ``$T_s$'' shows
-sequential execution time whereas column ``$T_p$'' shows parallel
-execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
-associated with parallel execution.   As usual, a ratio
-above 1x denotes speedup and a ratio below 1x denotes slowdown.
+abbreviated project names.  Columns ``\emph{Group}'' and
+``\emph{Name}'' indicate, respectively, the group and the name of the
+subject.  Column ``$T_s$'' shows sequential execution time and column
+``$T_p$'' shows parallel execution time. Column ``$T_s/T_p$'' shows
+the speedup or slowdown.  As usual, a ratio above 1x denotes speedup
+and a ratio below 1x denotes slowdown.
 
 \begin{figure}[h!]
-\footnotesize
 \centering
 \resizebox{.45\textwidth}{!}{%
+\scriptsize
 \begin{tabular}{llrrr}
@@
   sequential execution ($T_s$).  Default parallel configuration of
-  Maven is used.  Abbreviation of project names appear in bold face
-  and highest slowdown/speedup appear in gray color.}
+  Maven is used.  Highest slowdown/speedup appears in gray color.}
 \label{tab:speedup}
@@
   \begin{minipage}{8cm}
-    \textit{Answering \numRQSpeedupOne{}:}~\emph{ The average speedup observed
-      with default configurations of parallelization was
-      \avgSpeedup{}x.}
+    \textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
+      machine setup we used, the average speedup observed with default
+      configurations of parallelization was \avgSpeedup{}x.}
   \end{minipage}
@@
 
-\subsection{Threats to Validity}
-
-\Fix{To appear... Elaborate CONSTRUCT, INTERNAL and EXTERNAL threats.
-I'm going to be writing this ASAP as I finish to present the results
-from RQ6}
-
-\subsection{Lessons Learned}
-
-\Fix{Marcelo can write this...}
-
 %%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th

### 2017-05-10 paper/lessons.tex
another pass

\section{Lessons Learned}

\vspace{1ex}\noindent{}\textbf{The Good.}\Fix{...}

\vspace{1ex}\noindent{}\textbf{The Bad.}\Fix{...}

\vspace{1ex}\noindent{}\textbf{The Ugly.}\Fix{...}

### 2017-05-10 paper/threats.tex
another pass

\section{Threats to Validity}

\Fix{To appear... Elaborate CONSTRUCT, INTERNAL and EXTERNAL threats.
I'm going to be writing this ASAP as I finish to present the results
from RQ6}

### 2017-05-11 paper/evaluation.tex
updated mapdb and stripe rows

@@
 \midrule%
-OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
-Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
-Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
-Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
-Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
-AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
+Jankotek MapDB  & \entry{8.2m}{5324} & \entry{1.52x}{0.00\%} & \entry{2.73x}{0.00\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
+Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
+%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
+%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
+%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
+%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
+
+%% OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
+%% Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
+%% Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
+%% Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
+%% Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
+%% Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
+%% AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
+
 %% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

### 2017-05-11 paper/evaluation.tex
added aws

@@
 Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
+AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
 %%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%

### 2017-05-11 paper/evaluation.tex
added facebook linkbench
Added Javaslang
Added GoogleCloud Dataflow Java
Added reminder about slowdown of Dataflow in C3

--- 2017-05-11 paper/evaluation.tex
@@
 \midrule%
-Jankotek MapDB  & \entry{8.2m}{5324} & \entry{1.52x}{0.00\%} & \entry{2.73x}{0.00\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
+Jankotek MapDB  & \entry{8.2m}{5324} & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
 Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
+
+Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{}{} & \entry{}{}\\%
+AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
+
+GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%
+
+Javaslang (\CodeIn{core})       & \entry{1.1m}{17513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\%
+
+%%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%
 %%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
@@
 
+\Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
+dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
+Possivelmente o slowdown se deve ao tempo de resposta do servico quando
+a autentiticao falha}
+
 %% \begin{figure}[h!]

### 2017-05-11 paper/intro.tex
minor tweak

@@
 not be economically viable.  For these cases, the use of commodity
-hardware (\eg{}, existing workstations), emerges as an attractive
-solution for running tests.  Furthermore, the proliferation of
+hardware (\eg{}, existing workstations) is an attractive
+solution for running tests.  The proliferation of
 multi-core CPUs and the increasing popularization of testing
@@
 This paper reports on an empirical study we conducted to analyze the
-usage and impact of low-level parallelization in speeding up testing
+usage and impact of low-level parallelization to speed up testing
 in open-source projects.  This is a relevant problem given the
@@
 selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
-integration~\cite{Saff:2003:RWD:951952.952340}.  The dimensions of
-analysis we considered in this study are (i) potential, (iii)
-adoption, and (iii) flakiness, (iv) speedups.
+integration~\cite{Saff:2003:RWD:951952.952340}.
 
-%% Each dimension
-%% focuses on one aspect of the study.
-
-The dimension \textbf{feasibility} measures the potential of
-parallelization to reduce testing costs.  In the limit,
-parallelization would be fruitless if all projects used short-running
-test suites or if the bulk of execution cost was dominated by a single
-test in the suite.  The dimension \textbf{adoption} evaluates how
-often existing open-source projects use parallelization schemes and
-how developers involved in costly projects (not using test suite
-parallelization) perceive this technology.  It is important to measure
-resistance of practicioners to the technology and to understand their
-reasons.  The dimension \textbf{issues} reports the observed problems
-associated with running tests in parallel.  For example, test
-flakiness, which is caused by interference on shared state from
-non-deterministic executions of test methods and classes.  Finally,
-the dimension \textbf{speedups} evaluates the observed impact of
+The dimensions of analysis we considered in this study are (i)
+potential, (iii) adoption, (iv) speedup, and (iii) issues.  The
+dimension \emph{feasibility} measures the potential of parallelization
+to reduce testing costs.  In the limit, parallelization would be
+fruitless if all projects used short-running test suites or if the
+execution cost was dominated by a single test case in the suite.  The
+dimension \emph{adoption} evaluates how often existing open-source
+projects use parallelization schemes and how developers involved in
+costly projects (not using test suite parallelization) perceive this
+technology.  It is important to measure resistance of practicioners to
+the technology and to understand their reasons.  The dimension
+\emph{speedups} evaluates the observed impact of
 parallelization\Comment{~---~when used in selected open-source
-  projects~---~} in running times.  We briefly summarize each of these
-dimensions in the following.
+  projects~---~} in running times.  Finally, the dimension
+\emph{issues} reports the observed problems associated with running
+tests in parallel.  For example, test flakiness, which is caused by
+interference on shared state from non-deterministic executions of test
+methods and classes.  We briefly summarize our findings in
+the following.
 
@@
 
-\vspace{1ex}\noindent\textbf{Feasibility.}~
-We selected \numSubjs{} popular Java projects from \github{}
-containing Maven build files~\cite{maven} to assess how prevalent
-long-running test suites are.  Section~\ref{sec:eval} details our
-methodology to select subjects and to isolate our experiments from
-environmental noise.  Results indicate that nearly
-\percentMedLongRunning{} of the projects take at least 1m to run their
-test suites and \percentLongRunning{} of the projects take at least 5m
-to run their suites.  Considering the \numMedLong{} projects in those
-two groups, the average execution time is \averageMedLongRunning{}.
-Results also show that individual tests are typically short-running,
-taking often less than half a second to run.  Furthermore, we found
-that only in rare cases few test cases monopolize execution cost
-associated with each test suite.  \emph{Overall, our results suggest
-  that test suite parallelization has the potential to optimize test
-  suites.}
+\vspace{1ex}\noindent\textbf{Feasibility.}~To assess how prevalent
+long-running test suites are we selected \numSubjs{} popular Java
+projects from \github{} containing Maven build files~\cite{maven}.
+Section~\ref{sec:eval} details our methodology to select subjects and
+to isolate our experiments from environmental noise.  Results indicate
+that nearly \percentMedLongRunning{} of the projects take at least 1m
+to run their test suites and \percentLongRunning{} of the projects
+take at least 5m to run their suites.  Considering the \numMedLong{}
+projects in those two groups, the average execution time of a test
+suite was \averageMedLongRunning{}.  Results also show that test cases
+are typically short-running, typically taking less than half a second
+to run.  Furthermore, we found that only in rare cases few test cases
+monopolize execution cost associated with each test suite.
 
@@
 parallelism in open-source projects.  Then, we ran a survey with
-developers to understand the reasons that explain resistance to using
-the technology.  For the quantitative analysis we checked both
-statically (parsing build files) and dynamically (monitoring execution
-of build files) for the presence of parallelization.  Considering only
-those projects that take longer than a minute to run their test
-suites, we found that only \percentParallel{} of them use parallelism.
-When correcting this value with the feedback obtained a posteriori
-from developers, we realized that the proportion should be higher, of
+developers to understand the reasons that could explain resistance to
+using the technology.\Comment{ For the quantitative analysis we
+  checked both statically (parsing build files) and dynamically
+  (monitoring execution of build files) for the presence of
+  parallelization.}  Considering only those projects that take longer
+than a minute to run their test suites, we found that only
+\percentParallel{} of them use parallelism.  When correcting this
+value with the feedback obtained a posteriori from developers, we
+realized that the proportion should be higher, of
 \percentParallelUpdated{}.  For the qualitative analysis we surveyed
 developers from a selection of costly projects that did not use
-parallelization.  \emph{Results indicate that test suite
-  parallelization is underutilized and dealing with concurrency issues
-  related with parallelization (\eg{}, the extra work to organize test
-  suite to avoid concurrency errors) was the main barrier for
-  adoption.  Other reasons included availability of continuous
-  integration services and unfamiliarity with the technology.}
+parallelization.  Results indicate that test suite parallelization is
+underutilized.  Dealing with concurrency-related issues (\eg{}, the
+extra work to organize test suite to avoid concurrency errors) and the
+availability of continuous integration services were the most
+frequently answered reasons for not considering parallelization.
+
+%% \Mar{move to here} Intuitively, benefits are
+%% proportional to the cost reduction that parallelization brings.  In
+%% the limit, however, the overhead of spawning virtual machines or
+%% threads can even result in added cost.
+
+\vspace{1ex}\noindent\textbf{Speedups.}~We used two setups to measure
+execution speedups.  In one setup we measured the speedups obtained on
+projects that we knew a priori that ran their test suite in parallel
+by default.  We did not change parallel configurations on that setup.
+For comparison, we disabled parallel execution to obtain the running
+time of a sequential execution.  In the other setup, we evaluated how
+execution scales with the number of available cores in the machine.
+\Mar{need to repeat those!}\Fix{Considering the first setup, results
+  indicate that the average speedup of parallelization was
+  \avgSpeedup{}x.  Although we found cases with very high speedups
+  (\eg{}, 9.2x), we found some cases where speedups were
+  insignificant.}
 
@@
 
-\vspace{1ex}\noindent\textbf{Speedups.}~
-%% \Mar{move to here} Intuitively, benefits are
-%% proportional to the cost reduction that parallelization brings.  In
-%% the limit, however, the overhead of spawning virtual machines or
-%% threads can even result in added cost.
-\Mar{...revise with scalability results...}
-As to avoid introduction of unintended noise when measuring time, we
-evaluated effectiveness on projects that we knew a priori ran their
-test suite in parallel by default.  Results indicate that the average
-speedup of parallelization was \avgSpeedup{}x.  Although we found
-cases with very high speedups (\eg{}, 9.2x), we found some cases where
-speedups were insignificant.  \emph{Overall, our results suggest that
-  it may not be obvious to achieve huge speedups with test suite
-  parallelization.}
-
-\Mar{write one or two lessons learned}
+\subsection{Implications}
 

### 2017-05-11 paper/intro.tex
pass on intro

@@
   \url{https://clutch.co/cloud}} or even building proprietary
-infrastructures to running tests is a legitimate approach to mitigate
+infrastructures for running tests is a legitimate approach to mitigate
 the regression testing problem.  However, for projects with modest
@@
 frameworks and build systems, which today provide mature support for
-parallelization, enable test execution speedups through increased CPU
+parallelization, enable\Comment{ test execution} speedups through increased CPU
 usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
@@
 This paper reports on an empirical study we conducted to analyze the
-usage and impact of low-level parallelization to speed up testing
-in open-source projects.  This is a relevant problem given the
-tremendous popularity of open-source development and regression
-testing research~\cite{yoo-harman-stvr2012}.  Note that
-parallelization is complementary to other approaches to mitigate
-testing costs such as (safe) test
-selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
-integration~\cite{Saff:2003:RWD:951952.952340}.
+usage and impact of low-level parallelization to speed up testing in
+open-source projects.  This is a relevant problem given the tremendous
+popularity of open-source development and regression testing
+research~\cite{yoo-harman-stvr2012}.  Note that parallelization is
+complementary to other approaches to mitigate testing costs such as
+(safe) test
+selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
+and continuous integration~\cite{Saff:2003:RWD:951952.952340}.
 
@@
   projects~---~} in running times.  Finally, the dimension
-\emph{issues} reports the observed problems associated with running
-tests in parallel.  For example, test flakiness, which is caused by
-interference on shared state from non-deterministic executions of test
-methods and classes.  We briefly summarize our findings in
-the following.
+\emph{issues} reports the observed problems in running tests in
+parallel (\eg{}, test flakiness~\cite{luo-etal-fse2014}).  We briefly
+summarize our findings in the following.
 
@@
 execution speedups.  In one setup we measured the speedups obtained on
-projects that we knew a priori that ran their test suite in parallel
-by default.  We did not change parallel configurations on that setup.
+projects that we knew a priori ran their test suite in parallel by
+default.  We did not change parallel configurations on that setup.
 For comparison, we disabled parallel execution to obtain the running
@@
   (\eg{}, 9.2x), we found some cases where speedups were
-  insignificant.}
+  insignificant.}  Considering the second setup, results indicate that
+\Fix{...}
 
@@
 
+\newpage
+
 %% \Mar{missing connection. why parallelism?}  From these results we

### 2017-05-11 paper/evaluation.tex
pass on intro
Added JCTools

@@
-\newpage
 \section{Objects of Analysis}
@@
 Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{}{} & \entry{}{}\\%
+
 AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
+JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{}{} & \entry{}{}\\%
 
@@
 Javaslang (\CodeIn{core})     & \entry{1.1m}{17513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\%
-
 %%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%

### 2017-05-11 paper/threats.tex
minor tweaks

@@
 
-\Fix{To appear... Elaborate CONSTRUCT, INTERNAL and EXTERNAL threats.
-I'm going to be writing this ASAP as I finish to present the results
-from RQ6}
+\newcommand{\QA}{QA}
+\newcommand{\dockerfile}{dockerfile}
+\newcommand{\SO}{StackOverflow}
+
+The main threats to validity of this study are the following.
+\textit{External Validity:} Generalization of our findings is limited
+to our selection of subjects, testing framework, and build system.  To
+mitigate that issues, we selected subjects according to an objective
+criteria, described in Section~\ref{sec:subjects}.  It remains to
+evaluate the extent to which our observations would change when using
+different testing frameworks and build systems.  \Mar{Copied from
+  Fabrizio+Luis paper.  Use as reference...$\rightarrow$}
+\textit{Internal Validity:} Our results could be influenced by
+unintentional mistakes made by humans involved in this study.  For
+example, students were involved in a user study whereas developers
+manually categorized questions in difficulty levels and elaborated
+\dockerfile{}s.  All those tasks could introduce bias.  We used Card
+Sorting~\cite{lorr1983cluster} to mitigate the problem of incorrectly
+categorizing questions.  To make sure the scripts were correct,
+developers were instructed to strictly follow the instruction from
+\QA{} post preferred answers to reproduce corresponding problems.  We
+also encouraged developers to do their best to reproduce as many
+questions as possible.  As for the answer of students in the user
+study, we analyzed their answers carefully, comparing them with the
+solution prepared by the instructors.  It is important to note that
+all artifacts produced during this study are publicly available for
+scrutiny.  \textit{Construct Validity:} We considered a number of
+metrics in this study that could influence some of our
+interpretations.  For example, we used metrics of document similarity
+to assess how (dis)similar the \dockerfile{}s produced by developers
+are.  To mitigate the bias associated with metric selection we used
+multiple metrics and confirmed that the similarity was very high as to
+not compromise corresponding conclusions.

### 2017-05-11 paper/evaluation.tex
minor tweaks
minor changes

@@
 
-Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
-where parallelism is enabled by default in Maven.  Column
-``\emph{Subject}'' indicates the name of the project, column
-``\emph{\# of modules}'' indicates the fraction of modules containing
-tests that use the configuration of parallelism mentioned in column
-``\emph{Mode}''.  We note that, considering these projects, the
-modules that do not use the configuration cited use the sequential
-configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
-use sequential configuration.
-
-It came as a surprise the observation that
-no project used distinct configurations in their modules. Considering
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 \end{wrapfigure}
+Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
+where parallelism is enabled by default in Maven.  Column
+``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.  We note that, considering these projects, the
+modules that do not use the configuration cited use the sequential
+configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
+use sequential configuration.
+
+It came as a surprise the observation that
+no project used distinct configurations in their modules. Considering
 our set of \numMedLong{} projects, we found that only
@@
 answered the survey did not know that parallelism was available in
+Maven (option ``a''), \emailsB{} of developers mentioned that they did
+not use parallelism concerned with possible concurrency issues (option
+``b''), \emailsD{} of developers mentioned that continuous integration
+services sufficed to provide timely feedback while running only smoke
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 \end{wrapfigure}
-Maven (option ``a''), \emailsB{} of developers mentioned that they did
-not use parallelism concerned with possible concurrency issues (option
-``b''), \emailsD{} of developers mentioned that continuous integration
-services sufficed to provide timely feedback while running only smoke
 tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
@@
 \emailsNA{} of participants did not answer the last question of the
-survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
-the distribution of answers.
+survey.  The pie chart in Figure~\ref{fig:rq5-answers} 
+summarizes the distribution of answers.
 
@@
 Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
-abbreviated project names.  Columns ``\emph{Group}'' and
+project names.  Columns ``\emph{Group}'' and
 ``\emph{Name}'' indicate, respectively, the group and the name of the
@@
 ``$T_p$'' shows parallel execution time. Column ``$T_s/T_p$'' shows
-the speedup or slowdown.  As usual, a ratio above 1x denotes speedup
+speedup or slowdown.  As usual, a ratio above 1x denotes speedup
 and a ratio below 1x denotes slowdown.
@@
 \centering
-\resizebox{.45\textwidth}{!}{%
+\resizebox{.41\textwidth}{!}{%
   \scriptsize

### 2017-05-12 paper/evaluation.tex
pass on scalability

@@
 open-source projects.  It evaluates (\numRQAdoptionOne) how often open-source
-projects use parallelization schemes and (\numRQSpeedupOne) how developers
+projects use parallelization schemes and (\numRQAdoptionTwo) how developers
 involved in costly projects, not using parallelization, perceive this
@@
 \end{tabular}}
-\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
-  sequential execution ($T_s$).  Default parallel configuration of
-  Maven is used.  Highest slowdown/speedup appears in gray color.}
-\label{tab:speedup}
+\caption{\label{tab:speedup}Speedup (or slowdown) of parallel
+  execution ($T_p$) over sequential execution ($T_s$).  Default
+  parallel configuration of Maven is used.  Highest slowdown/speedup
+  appears in gray color.}
 \end{figure}
@@
 \end{itemize}
+
+\newcommand{\subjectScalability}{MapDB}
+
+This experiment evaluates the impact of making available to the build
+system a growing number of CPUs for testing.  For that reason, we used
+a \Fix{...describe machine...}  We focused on configuration \ForkSeq{}
+\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+    \centering
+    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
+    \caption{\label{fig:scalability}Scalability.}
+\end{wrapfigure}
+as the goal is to evaluate the impact of spawning a growing number of
+JVMs, running on different CPUs.  We selected the subject
+\subjectScalability{} in this experiment as it represents the case of
+a long-running test suite (see Figure~\ref{tab:speedup}) distributed
+across many test classes (\Fix{X} test classes for
+\subjectScalability{}).  Note that a test class is the smallest unit
+that can be used to spawn a test job on a JVM.
+
+Figure~\ref{fig:scalability} shows the reduction of running times as
+more CPUs contribute to the execution.  \Fix{elaborate...}
 

### 2017-05-12 paper/R/scalability/scalability.r

@@ -1,7 +1,7 @@
-pdf(file = "scalability.pdf", width = 5, height = 3)
+pdf(file = "scalability.pdf", width = 7, height = 4)
 
 dataframe <- read.csv(file="scalability.data", header=TRUE, sep=",")
 
-boxplot(time~numcores, data=dataframe, ylab="Time (m)", xlab="# Cores", ylim=c(0,max(dataframe$time)))
+boxplot(time~numcores, data=dataframe, ylab="time (m)", xlab="# cores", ylim=c(0,max(dataframe$time)), cex.lab=1.8, cex.axis=1.8)
 
 aux <- dev.off()

### 2017-05-12 paper/evaluation.tex
minor tweaks scalability discussion

@@
 system a growing number of CPUs for testing.  For that reason, we used
-a \Fix{...describe machine...}  We focused on configuration \ForkSeq{}
+a more poweful machine. \Fix{...describe machine...}  We focused on
+configuration \ForkSeq{}
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 \end{wrapfigure}
-as the goal is to evaluate the impact of spawning a growing number of
-JVMs, running on different CPUs.  We selected the subject
-\subjectScalability{} in this experiment as it represents the case of
-a long-running test suite (see Figure~\ref{tab:speedup}) distributed
-across many test classes (\Fix{X} test classes for
+as the goal of this experiment is to evaluate the impact of spawning a
+growing number of JVMs, running on different CPUs.  Furthremore, we
+selected the subject \subjectScalability{} as it represents the case
+of a long-running test suite (see Figure~\ref{tab:speedup}) with test
+cases distributed across many test classes (\Fix{X} test classes for
 \subjectScalability{}).  Note that a test class is the smallest unit
-that can be used to spawn a test job on a JVM.
+that can be used to spawn a test job on a JVM and that we have no
+control over which test classes will be assigned to which JVM that the
+build system forks.
 

### 2017-05-12 paper/related.tex
pass on intro
minor tweaks in related work

@@
 \label{sec:related}
-
-\Fix{elaborate...}
 
@@
 computes which tests have been impacted by changes.  A test is
-discarded for execution if it does not depend on any changed file.
+discarded for execution if it does not depend on any
+changed file dynamically reachable from execution.
+%% this may reveal/suggest identity.  wait for CR
+\Comment{
 Similar approach to regression test selection has been recently
 applied in the context of the GCC~\cite{gcc} configurable
-system~\cite{souto-damorim-jss}.
+system~\cite{souto-damorim-jss}.}
+
+\Fix{elaborate...}As another example, a recent paper from the
+automotive industry reported that test suites can take days to
+run~\cite{artl-etal-icst2015}.

### 2017-05-12 paper/evaluation.tex
update evaluation table
update table
update scalability plot

@@
 of a long-running test suite (see Figure~\ref{tab:speedup}) with test
-cases distributed across many test classes (\Fix{X} test classes for
+cases distributed across many test classes (194 test classes for
 \subjectScalability{}).  Note that a test class is the smallest unit
@@
 \small
-\begin{tabular}{l|rr|rrrrrrrrrr}
+\setlength{\tabcolsep}{5pt}
+\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
 \toprule
@@
 \midrule%
-Jankotek MapDB  & \entry{8.2m}{5324} & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
+Jankotek MapDB  & \entry{8.2m}{5,324} & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
 Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
@@
 
-GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%
-
-Javaslang (\CodeIn{core})     & \entry{1.1m}{17513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\%
+GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%
+
+Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\
+
+RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\
+
+JCabi Github                  & \entry{2.6m}{634} & \entry{2.1x}{0\%} & \entry{17.7x}{0\%} & \entry{28.8x}{0\%} & \entry{}{} & \entry{}{} \\
+
+	Moquette & \entry{3.5m}{x} & \entry{4.2x}{x} & \entry{2.9x}{} & \entry{13.5x}{} & \entry{}{} & \entry{}{} \\
+
+\midrule
+
+\textbf{Average}   & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-}
+& \entry{-}{-} & \entry{-}{-} \\%
+
 %%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%

### 2017-05-13 paper/R/scalability/scalability.r
pass on scalability scripts and pdf

@@ -1,7 +1,7 @@
 pdf(file = "scalability.pdf", width = 7, height = 4)
 
-dataframe <- read.csv(file="scalability.data", header=TRUE, sep=",")
+dataframe <- read.csv(file="scalability_reduced.data", header=TRUE, sep=",")
 
-boxplot(time~numcores, data=dataframe, ylab="time (m)", xlab="# cores", ylim=c(0,max(dataframe$time)), cex.lab=1.8, cex.axis=1.8)
+boxplot(time~numcores, data=dataframe, ylab="time (m)", xlab="# cores", ylim=c(0,max(dataframe$time)+1), cex.lab=1.8, cex.axis=1.6)
 
 aux <- dev.off()

### 2017-05-13 paper/evaluation.tex
Updated table and ordered by name

@@
 \midrule%
-Jankotek MapDB  & \entry{8.2m}{5,324} & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
+AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
+
+Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{}{} & \entry{}{}\\%
+
+GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%
+
+Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\ 
+JCabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{}{} & \entry{}{} \\
+JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{}{} & \entry{}{}\\%
+MapDB  & \entry{8.2m}{5,324}  & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
+Moquette                      & \entry{3.7m}{169} & \entry{4.62x}{65.64\%} & \entry{3.36x}{32.92\%} & \entry{12.33x}{77.78\%} & \entry{}{} & \entry{}{} \\
+RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\
 Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
-
-Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{}{} & \entry{}{}\\%
-
-AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
-JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{}{} & \entry{}{}\\%
-
-GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%
-
-Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\
-
-RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\
-
-JCabi Github                  & \entry{2.6m}{634} & \entry{2.1x}{0\%} & \entry{17.7x}{0\%} & \entry{28.8x}{0\%} & \entry{}{} & \entry{}{} \\
-
-	Moquette & \entry{3.5m}{x} & \entry{4.2x}{x} & \entry{2.9x}{} & \entry{13.5x}{} & \entry{}{} & \entry{}{} \\
 

### 2017-05-13 paper/evaluation.tex
minor comments on RQ6

@@
 system a growing number of CPUs for testing.  For that reason, we used
-a more poweful machine. \Fix{...describe machine...}  We focused on
-configuration \ForkSeq{}
+a machine with more cores compared to the one described in
+Section~\ref{sec:setup}.  We used a \Fix{...describe machine...}  This
+experiment uses configuration \ForkSeq{}
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 \end{wrapfigure}
-as the goal of this experiment is to evaluate the impact of spawning a
-growing number of JVMs, running on different CPUs.  Furthremore, we
-selected the subject \subjectScalability{} as it represents the case
-of a long-running test suite (see Figure~\ref{tab:speedup}) with test
-cases distributed across many test classes (194 test classes for
-\subjectScalability{}).  Note that a test class is the smallest unit
-that can be used to spawn a test job on a JVM and that we have no
-control over which test classes will be assigned to which JVM that the
-build system forks.
+as the goal is to evaluate the impact on runtime of spawning a growing number of
+JVMs in different CPUs.  Furthremore, we selected subject
+\subjectScalability{} as it represents the case of a long-running test
+suite (see Figure~\ref{tab:speedup}) with test cases distributed
+across many test classes (194 test classes for \subjectScalability{}).
+Note that a test class is the smallest unit that can be used to spawn
+a test job on a JVM and that we have no control over which test
+classes will be assigned to which JVM that the build system forks.
 

### 2017-05-13 paper/evaluation.tex
pass on table

@@
 %% Table header macros
-\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
+% $\Uparrow_\text{speed}$
+\newcommand{\subcolA}{$\text{speedup}$}
 \newcommand{\subcolB}{$\%_\text{fail}$}
@@
 \small
-\setlength{\tabcolsep}{5pt}
+\setlength{\tabcolsep}{3pt}
 \begin{tabular}{l|rr|rr|rr|rr|rr|rr}
@@
     \colheader{\ForkParMeth} \\ %\cline{2-12}
-    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
+    & $T$ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
     & \subcol{}\\%
@@
 \end{tabular}
-\caption{\Fix{Tabela de eficiencia e flakiness}}
+\caption{Speedup versus Flakiness (\subcolB). Configuration
+  \emph{\Seq{}} denotes the comparison baseline, which runs tests
+  sequentially.  Columns $T$ and $N$ indicate time and number of
+  tests, respectively.  Other columns show speedup and percentage of
+  failing tests in different configurations, compared to
+  \emph{\Seq{}}.\Mar{Can you please add name of module for all subjects?}}
 \label{tab:rq6-table}

### 2017-05-13 paper/intro.tex
abstract

@@
   (monitoring execution of build files) for the presence of
-  parallelization.}  Considering only those projects that take longer
-than a minute to run their test suites, we found that only
+  parallelization.}  Considering only those projects whose test suites
+that longer than a minute to run, we found that only
 \percentParallel{} of them use parallelism.  When correcting this

### 2017-05-13 paper/intro.tex
pass on intro

@@
 popular mechanism to distribute testing workloads.  For example, as of
-August 2013, the test suite fo the Groupon PWA system, which powers the
+August 2013, the test suite of the Groupon PWA system, which powers the
 \url{groupon.com} website, included over 19K tests.  To run all those
@@
 the regression testing problem.  However, for projects with modest
- or inexistent budgets and yet relatively heavy testing workloads, this solution may
+ or nonexistent budgets and yet relatively heavy testing workloads, this solution may
 not be economically viable.  For these cases, the use of commodity
@@
 costly projects (not using test suite parallelization) perceive this
-technology.  It is important to measure resistance of practicioners to
+technology.  It is important to measure resistance of practitioners to
 the technology and to understand their reasons.  The dimension
@@
   projects~---~} in running times.  Finally, the dimension
-\emph{issues} reports the observed problems in running tests in
-parallel (\eg{}, test flakiness~\cite{luo-etal-fse2014}).  We briefly
-summarize our findings in the following.
+\emph{issues} considers the problems in running tests in parallel
+(\eg{}, test flakiness~\cite{luo-etal-fse2014}).  We briefly summarize
+our findings in the following.
 
@@
 
-\vspace{1ex}\noindent\textbf{Feasibility.}~To assess how prevalent
+\vspace{1ex}\noindent\emph{Feasibility.}~To assess how prevalent
 long-running test suites are we selected \numSubjs{} popular Java
@@
 
-\vspace{1ex}\noindent\textbf{Adoption.}~ We considered two aspects in
+\vspace{1ex}\noindent\emph{Adoption.}~ We considered two aspects in
 measuring technology adoption.  First, we measured usage of
@@
 
-\vspace{1ex}\noindent\textbf{Speedups.}~We used two setups to measure
+\vspace{1ex}\noindent\emph{Speedups.}~We used two setups to measure
 execution speedups.  In one setup we measured the speedups obtained on
 projects that we knew a priori ran their test suite in parallel by
-default.  We did not change parallel configurations on that setup.
-For comparison, we disabled parallel execution to obtain the running
-time of a sequential execution.  In the other setup, we evaluated how
-execution scales with the number of available cores in the machine.
-\Mar{need to repeat those!}\Fix{Considering the first setup, results
+default.  In the other setup, we evaluated how execution scales with
+the number of available cores in the machine.\Comment{We did not
+  change parallel configurations on that setup.  For comparison, we
+  disabled parallel execution to obtain the running time of a
+  sequential execution.}  Considering the first setup, results
 indicate that the average speedup of parallelization was
-  \avgSpeedup{}x.  Although we found cases with very high speedups
-  (\eg{}, 9.2x), we found some cases where speedups were
-  insignificant.}  Considering the second setup, results indicate that
-\Fix{...}
+\avgSpeedup{}x.  Although we found cases with very high speedups (9.2x
+for project Jcabi), we found cases where speedups were not very
+significant.  Considering the scalability experiment, we noticed,
+perhaps as expected, that speedups are bounded by long-running test
+classes.
 
@@
 
-\vspace{1ex}\noindent\textbf{Issues.}~
+\vspace{1ex}\noindent\emph{Issues.}~
 \Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
@@
 
-\subsection{Implications}
-
-\newpage
+\vspace{1ex}\noindent\textbf{Potential Implications}...
 
@@
 %%  LocalWords:  jenkins API VMs datarace tradeoffs tradeoff Paretto
-%%  LocalWords:  schedulings
+%%  LocalWords:  schedulings posteriori priori bla blabla

### 2017-05-13 paper/evaluation.tex
pass section III

@@
 directory, \SubjectsGithubNotTestable{} projects were untestable
-because of missing dependencies or incompatible testing environment,
-for example, and \SubjectsGithubFlaky{} projects were ``flaky''.
-\Jbc{Check if this is ok $\rightarrow$} We executed each project's
-test suite for three times to identify projects containing flaky tests
-and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
-from JUnit) to avoid introducing noise in our experiments.  Our final
-set of subjects consists of \numSubjs{} projects.
+because of missing dependencies or incompatible testing environment.
+We also found \SubjectsGithubFlaky{} projects with ``flaky'' tests.
+We considered those projects but ignored their tests (using JUnit's
+\CodeIn{@Ignore} annotation) as to avoid measurement noise.  To detect
+those projects, we executed every test suite for three times.  Our
+final set of subjects consists of \numSubjs{} projects.
 

### 2017-05-13 paper/intro.tex
pass on intro (discussing tradeoffs)

@@
 The dimensions of analysis we considered in this study are (i)
-potential, (iii) adoption, (iv) speedup, and (iii) issues.  The
+potential, (iii) adoption, (iv) speedup, and (iii) tradeoffs.  The
 dimension \emph{feasibility} measures the potential of parallelization
@@
   projects~---~} in running times.  Finally, the dimension
-\emph{issues} considers the problems in running tests in parallel
-(\eg{}, test flakiness~\cite{luo-etal-fse2014}).  We briefly summarize
-our findings in the following.
+\emph{tradeoffs} considers the problems in running tests in parallel,
+including test flakiness~\cite{luo-etal-fse2014}.  We briefly
+summarize our findings in the following.
 
@@
 execution speedups.  In one setup we measured the speedups obtained on
-projects that we knew a priori ran their test suite in parallel by
+projects that we knew a priori ran their test suites in parallel by
 default.  In the other setup, we evaluated how execution scales with
@@
 indicate that the average speedup of parallelization was
-\avgSpeedup{}x.  Although we found cases with very high speedups (9.2x
-for project Jcabi), we found cases where speedups were not very
-significant.  Considering the scalability experiment, we noticed,
-perhaps as expected, that speedups are bounded by long-running test
-classes.
+\avgSpeedup{}x.  Although we found cases with very high speedups
+(\eg{}, 9.2x for project Jcabi), we found cases where speedups were
+not very significant.  Considering the scalability experiment, we
+noticed, perhaps as expected, that speedups are bounded by
+long-running test classes.
 
@@
 
-\vspace{1ex}\noindent\emph{Issues.}~
-\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
-  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
-  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
-  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
-  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
-  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
-  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
-  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
-  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
-  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
-  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
-  bla bla blabla bla bla blabla bla bla blabla bla bla bla}
+\vspace{1ex}\noindent\emph{Tradeoffs.}~Test flakiness is a central
+issue that can arise when running tests in parallel.  Dependent tests
+can be affected by different schedulings of test methods and classes.
+This dimension of the study measures the impact of different parallel
+configurations on test flakiness and speedup.  Overall, results
+indicate that parallel configurations that fork JVMs do not achieve
+speedups as high as configurations that parallelize test classes and
+methods, however they manifest much lower flakiness ratios.
 

### 2017-05-13 paper/evaluation.tex
issues => tradeoffs

@@
 
-After obtaining a list of
-potential projects, we filtered those containing a \pomf{} file in the
-root directory.  A Maven project may contain several sub-modules with
-multiple \pomf{} files.\Comment{  We based our methodology to select
-experimental subjects on other recent studies in testing and
-debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.}
-As of March 25th 2017, our search criteria returned \SubjectsGithub{}
+After obtaining a list of potential projects, we filtered those
+containing a \pomf{} file in the root directory.  A Maven project may
+contain several sub-modules with multiple \pomf{} files.\Comment{  We
+based our methodology to select experimental subjects on other recent
+studies in testing and
+debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.} As of
+March 25th 2017, our search criteria returned \SubjectsGithub{}
 subjects. Figure~\ref{fig:subjects} summarizes our sample set.
@@
     \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
-    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
-    projects hosted on \github{}. From this initial sample, we ignored
-    \SubjectsGithubNotMaven{} projects without Maven support and
+    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
+    hosted on \github{}. From this initial sample, we ignored
+    \SubjectsGithubNotMaven{} projects without Maven support,
+    \SubjectsGithubNotCompilable{} were unable to compile, and
     \SubjectsGithubNotTestable{} untestable projects\Comment{, and
@@
 projects were not Maven or did not have a \pomf{} in the root
-directory, \SubjectsGithubNotTestable{} projects were untestable
-because of missing dependencies or incompatible testing environment.
-We also found \SubjectsGithubFlaky{} projects with ``flaky'' tests.
-We considered those projects but ignored their tests (using JUnit's
+directory, \SubjectsGithubNotCompilable{} were unable to compile due
+to missing dependencies, and \SubjectsGithubNotTestable{} projects
+were untestable due to incompatible testing environment.  We also
+found \SubjectsGithubFlaky{} projects with ``flaky'' tests.  We
+considered those projects but ignored their tests (using JUnit's
 \CodeIn{@Ignore} annotation) as to avoid measurement noise.  To detect
@@
 
-%% Issues
+%% Tradeoffs
 \newcommand{\numRQIssuesOne}{RQ7}
@@
   \end{itemize}      
-\item Issues
+\item Tradeoffs
   \begin{itemize}
@@
 a machine with more cores compared to the one described in
-Section~\ref{sec:setup}.  We used a \Fix{...describe machine...}  This
-experiment uses configuration \ForkSeq{}
+Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
+processor machine with 80 virtual CPUs (40 cores with two native
+threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
+Tarr (64-bit version). This experiment uses configuration \ForkSeq{}
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 
-\subsection{Issues}
+\subsection{Tradeoffs}
 \label{sec:rq6-tradeoffs}

### 2017-05-13 paper/intro.tex
done with intro

@@
 
-\vspace{1ex}\noindent\textbf{Potential Implications}...
+Our observations may trigger several actions:
+
+\begin{itemize}
+\item \emph{Incentivize forking.}~Forked JVMs manifest very low rates
+  of test flakiness.  Developers of projects with long-running test
+  suites should consider using that feature, which is available in
+  modern build systems today (\eg{}, Maven).
+\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
+  impressive speedups at the expense of sometimes impressive rates of
+  flakiness.  Breaking test dependencies to avoid flakiness and take
+  full advantage of those options is advised for developers with
+  greater interest in efficiency.
+\item \emph{Refactor tests for load balancing.}~Forked JVMs scales
+  better with the number of cores when the test workload is balanced
+  across testing classes.  To balance the workload, automated
+  user-oblivious refactoring can help in scenarios where developers
+  are not willing to change test code but have access to machines with
+  a high number of cores.
+\item \emph{Improve debugging for build systems.}~While preparing our
+  experiments, we found scenarios\Comment{, related to test
+    parallelization,} where Maven's executions did not reflect
+  corresponding JUnit's executions. (Docker reproduction scripts
+  available.) Those issues can hinder developers from using parallel
+  testing. Better debugging infrastructure is important.
+\end{itemize}
+
+The artifacts we produced as results of this study are available from
+the following web page \webpage{}.
 
@@
 %%  LocalWords:  jenkins API VMs datarace tradeoffs tradeoff Paretto
-%%  LocalWords:  schedulings posteriori priori bla blabla
+%%  LocalWords:  schedulings posteriori priori bla blabla Jcabi
+%%  LocalWords:  scalability parallelize Incentivize Refactor JUnit's
+%%  LocalWords:  refactoring

### 2017-05-13 paper/evaluation.tex
Fixed # of untestable and piechart
update la02 specs
Fixed subjs section - 115 projects didn't compiled
consistency
Updated methodology of rq7

@@
     \SubjectsGithubNotMaven{} projects without Maven support,
-    \SubjectsGithubNotCompilable{} were unable to compile, and
+    \SubjectsGithubNotCompilable{} uncompilable projects, and
     \SubjectsGithubNotTestable{} untestable projects\Comment{, and
@@
 \label{sec:rq6-tradeoffs}
-
+\Jbc{Check $\rightarrow$}
 This dimension assesses the impact of using distinct parallel
-configurations on test flakiness (negative impact) and speedup
-(positive impact).  Furthermore, note that Section~\ref{sec:rqD}
-evaluated speedup in isolation, focused on projects configured to use
-parallelism by default.
+configurations on test flakiness (negative impact) and speedup We are
+interested in understanding how efficiency (\ie, testing cost) and
+flakiness (\ie, failing tests) are affected when we run a test suite
+with different parallel configurations.  Recall that increased
+resource contention obtained with parallelism can lead to concurrency
+issues such as data races.  Flakiness and speedup are contradictory
+forces that drive configuration selection.  (positive impact).
+Furthermore, note that Section~\ref{sec:rqD} evaluated speedup in
+isolation, focused on projects configured to use parallelism by
+default.
 
@@
 
-\textbf{Average}   & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-}
-& \entry{-}{-} & \entry{-}{-} \\%
+\textbf{Average}   & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} \\%
 
@@
 To answer this research question, we conducted an experiment involving
-the six parallel configurations from Section~\ref{sec:modes}  and the
-top 10 long-running test modules from our sample set. The rationale
-for this selection criteria was to maximize the chances of observing
-speedup and flakiness, assuming that long-running tests also have many
-tests. Indeed, we confirmed that test suites in these projects contain
-at least 236 tests ($1,662.7$ in average). Also, we preferred to compare the
-effect of a configuration over a single test module for projects with
-multiple test modules.  Recall that large projects may contain several
-test modules, and these modules may contain distinct characteristics
-that could favor one configuration and not others; therefore, it would
-be necessary to check each module individually for a fair comparison.
-We are interested in understanding how efficiency (\ie, testing cost)
-and flakiness (\ie, failing tests) are affected when we run a test
-suite with different parallel configurations.  Recall that increased
-resource contention obtained with parallelism can lead to concurrency
-issues such as data races.  Flakiness and speedup are contradictory
-forces that drive configuration selection.  We used as a \emph{control
-group} (\ie, baseline) the sequential execution of each subject's
-tests. Notice that for measuring flakiness, we have to consider only
-tests that failed due to the concurrency in the parallel execution.
-For that reason, we re-executed the tests in sequence ten times and
-carefully verified that there are only passing tests in our baseline.
-We considered ten as the number of re-executions based on the approach
-used by Google reported in a previous work on test
-flakiness~\cite{luo-etal-fse2014}.  To obtain parallel configurations,
-we implemented a script that takes a subject and a configuration (\eg,
-\ForkSeq{}) as inputs, and the script outputs the modified version of
-the subject with the desired configuration. The workflow consists in
-copying the project directory to a new directory, finding all existing
-build files (\ie, \pomf{} files), and modifying all existing Maven
-Surefire configurations with new values for the parameters
-\CodeIn{parallel}, \CodeIn{forkCount}, and \CodeIn{threadCount} using
-an XPath~\cite{xpath} library to manipulate XML documents. For
-configurations with forked JVMs enabled (\ie, \ForkSeq{} and
-\ForkParMeth{}), we changed the \CodeIn{forkCount} with the value
-\CodeIn{1C} (\ie, one JVM per core).  To adjust the pool of threads
-for parallelism within a JVM, we changed the parameter
-\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
-number of native threads per core OR 6 as it represents 3 Cores * 2
-native threads?}.  To run the subjects and their respective variations
-(\ie, the modified versions according to the parallelism
-configuration), we used a similar approach as described in
-
-Figure~\ref{fig:mvn-execution} except that we added a timeout of one
-hour to run the tests. We used the \CodeIn{timeout}
-command~\cite{timeout-cmd} to monitor the execution, and we configured
-the command to dispatch a \emph{kill} signal if the test execution
-exceeds the time limit. We imposed this time constraint to avoid
-hanging indefinitely the experiment execution due to some thread
-contention that may occur (\eg, deadlock). Finally, we saved each
-execution log and XML test reports generated by Maven to collect the
-execution time, the number of failing tests, and for reference to
-analyze and diagnose outliers in our results. For efficiency, we
-reported the speedup (\ie, $\Uparrow_\text{speed} = T_{\text{s}} /
-T_{\text{p}}$) in average, and for flakiness, we reported the rate of
-failing tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$) in
-average.  Figure~\ref{tab:rq6-table} summarizes the obtained results
-ordered by the time cost (\ie, $T_\text{cost}$). \Fix{Remember to
-explain efficiency cutoff, JVM crashes and timeout}
-
-\Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
-dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
-Possivelmente o slowdown se deve ao tempo de resposta do servico quando
-a autentiticao falha}
+the six parallel configurations from Section~\ref{sec:modes}, and we
+randomly selected 10 subjects from the medium and long groups (\ie,
+tests suites that ran in at least one minute) identified in
+\numRQFeasibilityOne{}. \Jbc{Is this legit/acceptable/convincing?
+$\rightarrow$}The rationale for this criteria was to maximize the
+diversity of domains from the subjects, assuming these subjects have
+test suites with different characteristics (\eg, architectural design
+and rate of cpu/io-bound operations).
+\Comment{
+    The rationale for this selection criteria was to maximize the chances
+    of observing speedup and flakiness, assuming that long-running tests
+    also have many tests. Indeed, we confirmed that test suites in these
+    projects contain at least 236 tests ($1,662.7$ in average).
+}
+To compare flakiness and efficiency, we used the sequential execution
+of each subject's test suite as the \emph{control group} (\ie,
+baseline). Notice that with parallelism enabled, the number of failing
+tests may vary on different runs due to the non-deterministic
+scheduling of threads and processes.  For that reason, we re-executed
+the experiment and computed the average speedup and flakiness on each
+scenario. 
+In a first attempt of this experiment, we considered using Maven to
+run the subjects on the different parallel configurations. However, we
+noticed that some executions using parallelism within a JVM did not
+reflect the desired behavior although we carefully verified the
+library versions from the subjects tested to avoid compatibility
+issues.
+To make the experiment viable and obtain the parallel configurations,
+we implemented a script and a JUnit runner to emulate the effect of
+parallel configurations from Maven Surefire.
+Our script takes a list o tests classes to run as an input and outputs
+the results (\ie, number of test methods, failures, skips, and elapsed
+time) for each parallel configuration. Initially, we use an existing
+Maven log to identify the test classes to run, and we use the Maven
+dependency plugin~\cite{maven-dep} to build the project's classpath with
+the command \CodeIn{mvn dependency:build-classpath}. Once we have the
+classpath and the tests to run, we invoke our JUnit runner that runs
+the test classes with different parallel configurations at once. For
+the sequential execution, we ivonke the default JUnit test runner. For
+parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
+\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
+runner with ParallelComputer~\cite{junit-parallel} that internally uses a pool of
+threads with cache to run test classes and methods. For the
+configurations with forked JVMs (\ie, \ForkSeq{} and \ForkParMeth{}),
+we have a queue of test classes and a pool of three threads that
+``consumes'' the next test class and spawns a JVM to run it.
+Recall that in our setup (see Section~\ref{sec:setup}), we limited our
+kernel to use only three cores and reserved one for OS-related
+processes.
+To verify that our approach satisfies the purpose of this experiment,
+we executed some subjects on Maven and compared the performance with
+our artifacts and observed nonsignificant differences (a fraction of
+seconds in most cases).
+\Comment{
+    To obtain parallel configurations, we implemented a script that
+    takes a subject and a configuration label as inputs (\eg
+    \CodeIn{mapdb "c0"}), and the script outputs the modified version
+    of the subject with the desired configuration. The workflow
+    consists in copying the project directory to a new directory,
+    finding all existing build files (\ie, \pomf{} files), and
+    modifying all existing Maven Surefire configurations with new
+    values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
+    and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
+    manipulate XML documents. For configurations with forked JVMs
+    enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
+    \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
+    core).  To adjust the pool of threads for parallelism within a
+    JVM, we changed the parameter \CodeIn{threadCount} with
+    \Jbc{should we consider 2 as it is the number of native threads
+    per core OR 6 as it represents 3 Cores * 2 native threads?}.To run
+    the subjects and their respective variations (\ie, the modified
+    versions according to the parallelism configuration), we used a
+    similar approach as described in Figure~\ref{fig:mvn-execution}
+    except that...
+}
+Also, we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our
+scripts to monitor the execution, and we configured the command to
+dispatch a \emph{kill} signal if the test execution exceeds a given
+time limit. We imposed this time constraint to avoid hanging
+indefinitely the experiment execution due to some thread contention
+that may occur (\eg, deadlock or livelock).  Finally, we saved each
+execution log and stack traces generated outputed from JUnit to
+collect the execution time, the number of failing tests, and for
+reference to analyze and diagnose outliers in our results.  For
+efficiency, we reported the speedup (\ie, $T_{\text{s}} /
+T_{\text{p}}$), and for flakiness, we reported the rate of failing
+tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
+Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
+subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
+VALORES DE DESVIO PADRAO!}.
 
@@
 
+\Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
+dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
+Possivelmente o slowdown se deve ao tempo de resposta do servico quando
+a autentiticao falha}
+
 \Fix{Elaborate results from efficiency}

### 2017-05-13 paper/evaluation.tex
Added aws
Added missing values

@@
 \toprule
-\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
+\multirow{2}{*}{\emph{Subject}} & \multicolumn{2}{c|}{\emph{\Seq}} &
     \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
@@
 \midrule%
-AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
-
-Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{}{} & \entry{}{}\\%
-
-GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%
+AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{1.85x}{0.23\%} & \entry{3.36x}{3.1\%}\\%
+
+Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{1.54x}{0\%} & \entry{1.59x}{0\%}\\%
+
+GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{0.80x}{1.70\%} & \entry{0.80x}{1.70\%}\\%
 
@@
 JCabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{}{} & \entry{}{} \\
-JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{}{} & \entry{}{}\\%
-MapDB  & \entry{8.2m}{5,324}  & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
-Moquette                      & \entry{3.7m}{169} & \entry{4.62x}{65.64\%} & \entry{3.36x}{32.92\%} & \entry{12.33x}{77.78\%} & \entry{}{} & \entry{}{} \\
+JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{2.77x}{0\%} & \entry{9.00x}{0\%}\\%
+MapDB  & \entry{8.2m}{5,324}  & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{1.71x}{0.98\%} & \entry{3.42x}{0.98\%}\\%
+Moquette                      & \entry{3.7m}{169} & \entry{4.62x}{65.64\%} & \entry{3.36x}{32.92\%} & \entry{12.33x}{77.78\%} & \entry{2.47x}{22.53\%} & \entry{9.25x}{69.44\%} \\
 RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\
-Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
+Stripe Java                   & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{2.69x}{0\%} & \entry{8.60x}{11.63\%}\\%
 

### 2017-05-13 paper/threats.tex
threats

--- 2017-05-10 paper/threats.tex
@@
 
-\Fix{To appear... Elaborate CONSTRUCT, INTERNAL and EXTERNAL threats.
-I'm going to be writing this ASAP as I finish to present the results
-from RQ6}
+The main threats to validity of this study are the following.
+\textit{External Validity:} Generalization of our findings is limited
+to our selection of subjects, testing framework, and build system.  To
+mitigate that issue, we selected subjects according to an objective
+criteria, described in Section~\ref{sec:subjects}.  It remains to
+evaluate the extent to which our observations would change when using
+different testing frameworks and build systems.  \textit{Internal
+  Validity:} Our results could be influenced by unintentional mistakes
+made by humans who interpreted survey data and implemented scripts to
+collect and analyze data. All those tasks could introduce bias.  To
+mitigate those threats, we worked in pairs as to increase chances of
+capturing unintentional mistakes.  \textit{Construct Validity:} We
+considered a number of metrics in this study that could influence some
+of our interpretations.  For example, we measured number of test cases
+per suite, distribution of test costs in a suite, time to run a suite,
+etc.  In principle, these metrics may not reflect the main problems
+associated with test efficiency.\Mar{...elaborate...}
+
+%%  LocalWords:  QA dockerfile StackOverflow

### 2017-05-13 paper/evaluation.tex
added missing values

@@
 
-Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\ 
-JCabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{}{} & \entry{}{} \\
+Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{1.38x}{0\%} & \entry{1.57x}{0\%}\\ 
+JCabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{2.00x}{0\%} & \entry{2.89x}{0\%} \\%
 JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{2.77x}{0\%} & \entry{9.00x}{0\%}\\%

### 2017-05-13 paper/intro.tex
minor tweak intro
fix intro

@@
 The dimensions of analysis we considered in this study are (i)
-potential, (iii) adoption, (iv) speedup, and (iii) tradeoffs.  The
+feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
 dimension \emph{feasibility} measures the potential of parallelization
@@
 \avgSpeedup{}x.  Although we found cases with very high speedups
-(\eg{}, 9.2x for project Jcabi), we found cases where speedups were
+(\eg{}, 28.0x for project Jcabi), we found cases where speedups were
 not very significant.  Considering the scalability experiment, we
@@
 
-Our observations may trigger several actions:
+Our observations may trigger multiple actions:
 

### 2017-05-13 paper/evaluation.tex
first par RQ7

@@
 
-To answer this research question, we conducted an experiment involving
-the six parallel configurations from Section~\ref{sec:modes}, and we
-randomly selected 10 subjects from the medium and long groups (\ie,
-tests suites that ran in at least one minute) identified in
-\numRQFeasibilityOne{}. \Jbc{Is this legit/acceptable/convincing?
-$\rightarrow$}The rationale for this criteria was to maximize the
-diversity of domains from the subjects, assuming these subjects have
-test suites with different characteristics (\eg, architectural design
-and rate of cpu/io-bound operations).
-\Comment{
-    The rationale for this selection criteria was to maximize the chances
-    of observing speedup and flakiness, assuming that long-running tests
-    also have many tests. Indeed, we confirmed that test suites in these
-    projects contain at least 236 tests ($1,662.7$ in average).
-}
+To answer this research question, we ran ten different subjects
+against all configurations described in Section~\ref{sec:modes} and
+compared their running times and rate of test flakiness.  We selected
+subjects from the medium and long groups listed in
+Section~\ref{sec:rqA} and ran their longest test module for testing.
+The rationale is to obtain a diverse set of subjects exposing a wide
+range of running times (range observed 1.1m-8.2m) and number of test
+cases (range observed 54-17,513).  The rationale for fixing the number
+of subjects in ten was to be able to finish execution in reasonable
+time.  We ran each project on each configuration with ten seeds and
+reported averages of time and flakiness.  Overall, we need to reran
+test suites 600 times, 60 times (10x6 configurations) on each project.
+
+%% \Jbc{Is this
+%%   legit/acceptable/convincing?  $\rightarrow$}The rationale for this
+%% criteria was to maximize the diversity of domains from the subjects,
+%% assuming these subjects have test suites with different
+%% characteristics (\eg, architectural design and rate of cpu/io-bound
+%% operations).
+
 To compare flakiness and efficiency, we used the sequential execution
@@
 scenario.
+
+\Comment{
+    The rationale for this selection criteria was to maximize the chances
+    of observing speedup and flakiness, assuming that long-running tests
+    also have many tests. Indeed, we confirmed that test suites in these
+    projects contain at least 236 tests ($1,662.7$ in average).
+}
+
 In a first attempt of this experiment, we considered using Maven to

### 2017-05-13 paper/evaluation.tex
pass on RQ7

@@
 against all configurations described in Section~\ref{sec:modes} and
-compared their running times and rate of test flakiness.  We selected
-subjects from the medium and long groups listed in
-Section~\ref{sec:rqA} and ran their longest test module for testing.
-The rationale is to obtain a diverse set of subjects exposing a wide
-range of running times (range observed 1.1m-8.2m) and number of test
-cases (range observed 54-17,513).  The rationale for fixing the number
-of subjects in ten was to be able to finish execution in reasonable
-time.  We ran each project on each configuration with ten seeds and
-reported averages of time and flakiness.  Overall, we need to reran
-test suites 600 times, 60 times (10x6 configurations) on each project.
+compared their running times and rate of test flakiness.  We used the
+sequential execution (configuration \emph{\Seq{}}) associated with
+each project as the comparison baseline in this experiment.  We
+selected subjects from the medium and long groups from
+Section~\ref{sec:rqA} and further selected their longest test module
+for testing.  The rationale is to obtain a diverse set of subjects
+exposing a wide range of running times (range observed 1.1m-8.2m) and
+number of test cases (range observed 54-17,513) and yet be able to run
+the experiment in reasonable time.  We ran each project on each
+configuration with ten seeds.  Overall, we needed to reran test suites
+600 times, 60 times (10x6 configurations) on each project.  Given the
+low standard deviations observed in our measurements we consider ten
+seeds reasonable for this experiment.
 
@@
 
-To compare flakiness and efficiency, we used the sequential execution
-of each subject's test suite as the \emph{control group} (\ie,
-baseline). Notice that with parallelism enabled, the number of failing
-tests may vary on different runs due to the non-deterministic
-scheduling of threads and processes.  For that reason, we re-executed
-the experiment and computed the average speedup and flakiness on each
-scenario.
+%% Notice that with parallelism enabled, the
+%% number of failing tests may vary on different runs due to the
+%% non-deterministic scheduling of threads and processes.  For that
+%% reason, we re-executed the experiment and computed the average speedup
+%% and flakiness on each scenario.
 
@@
 }
+
+\Mar{...estou aqui...}
 

### 2017-05-13 paper/evaluation.tex
Added values from avg
fixed values

@@
 Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{1.38x}{0\%} & \entry{1.57x}{0\%}\\ 
-JCabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{2.00x}{0\%} & \entry{2.89x}{0\%} \\%
+Jcabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{2.00x}{0\%} & \entry{2.89x}{0\%} \\%
 JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{2.77x}{0\%} & \entry{9.00x}{0\%}\\%
@@
 
-\textbf{Average}   & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} \\%
+\textbf{Average}   & \entry{30.3m}{2,897.6} & \entry{2.40x}{7.59\%} & \entry{4.10x}{4.51\%} & \entry{9.45x}{10.32\%} & \entry{1.86x}{2.54\%} & \entry{4.19x}{8.68\%} \\%
 

### 2017-05-13 paper/evaluation.tex
updates

--- 2017-05-13 paper/evaluation.tex
@@
 and has the second highest value of $\sigma$.  For this project,
-however, cost is distributed more smoothly across \Fix{529} tests, of
-which \Fix{119 (23\%)} take more than \Fix{1s} to run with the rest of
+however, cost is distributed more smoothly across \Fix{98} tests, of
+which \Fix{8 (8.1\%)} take more than \Fix{1s} to run with the rest of
 the tests running faster.

### 2017-05-13 paper/evaluation.tex
anotacao de problema do maven
pass on rq7 (not done); going back to rq6

@@
 \label{sec:rq6-tradeoffs}
-\Jbc{Check $\rightarrow$}
+
+%%  We are
+%% interested in understanding how efficiency (\ie, testing cost) and
+%% flakiness (\ie, failing tests) are affected when we run a test suite
+%% with different parallel configurations.
+
 This dimension assesses the impact of using distinct parallel
-configurations on test flakiness (negative impact) and speedup We are
-interested in understanding how efficiency (\ie, testing cost) and
-flakiness (\ie, failing tests) are affected when we run a test suite
-with different parallel configurations.  Recall that increased
+configurations on test flakiness and speedup.  Recall that increased
 resource contention obtained with parallelism can lead to concurrency
-issues such as data races.  Flakiness and speedup are contradictory
-forces that drive configuration selection.  (positive impact).
-Furthermore, note that Section~\ref{sec:rqD} evaluated speedup in
-isolation, focused on projects configured to use parallelism by
-default.
+issues such as data races that could interfere in results of dependent
+tests~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  Flakiness and
+speedup are contradictory forces that drive configuration selection.
+Note that Section~\ref{sec:rqD} evaluated speedup in isolation.
 
@@
 
-To answer this research question, we ran ten different subjects
-against all configurations described in Section~\ref{sec:modes} and
-compared their running times and rate of test flakiness.  We used the
-sequential execution (configuration \emph{\Seq{}}) associated with
-each project as the comparison baseline in this experiment.  We
-selected subjects from the medium and long groups from
-Section~\ref{sec:rqA} and further selected their longest test module
-for testing.  The rationale is to obtain a diverse set of subjects
-exposing a wide range of running times (range observed 1.1m-8.2m) and
-number of test cases (range observed 54-17,513) and yet be able to run
-the experiment in reasonable time.  We ran each project on each
-configuration with ten seeds.  Overall, we needed to reran test suites
-600 times, 60 times (10x6 configurations) on each project.  Given the
-low standard deviations observed in our measurements we consider ten
-seeds reasonable for this experiment.
+To answer this research question, we selected ten different subjects,
+ran their test suites against all configurations described in
+Section~\ref{sec:modes}, and compared their running times and rate of
+test flakiness.  We used the sequential execution (configuration
+\emph{\Seq{}}) associated with each project as the comparison baseline
+in this experiment.  We selected subjects from the medium and long
+groups from Section~\ref{sec:rqA} and further selected their longest
+test module for testing.  The rationale for this selection was to
+obtain a diverse set of subjects exposing a wide range of running
+times (range observed 1.1m-8.2m) and number of test cases (range
+observed 54-17,513) and yet be able to run the experiment in
+reasonable time.  We ran each project on each configuration with ten
+seeds.  Overall, we needed to reran test suites 600 times, 60 times
+(10x6 configurations) on each project.  Given the low standard
+deviations observed in our measurements we consider ten seeds
+reasonable for this experiment.
 
@@
 
-\Mar{...estou aqui...}
-
-In a first attempt of this experiment, we considered using Maven to
-run the subjects on the different parallel configurations. However, we
-noticed that some executions using parallelism within a JVM did not
-reflect the desired behavior although we carefully verified the
-library versions from the subjects tested to avoid compatibility
-issues.
-To make the experiment viable and obtain the parallel configurations,
-we implemented a script and a JUnit runner to emulate the effect of
+%% In a first attempt of this experiment, we considered using Maven to
+%% run the subjects on the different parallel configurations. However,
+
+\noindent\textbf{JUnit.} It is worth mentioning that we used JUnit as
+opposed to Maven to run configurations \emph{C*}.  After carefully
+verifying library versions for compatibility issues and comparing
+results with JUnit's we observed that several of Maven's executions
+exposed problems (\eg{} timeouts).  These issues are documented in our
+website~\cite{ourwebpage} through Docker containers.  To address those
+issues we implemented basic JUnit runner reflecting the effects of
 parallel configurations from Maven Surefire.
-Our script takes a list o tests classes to run as an input and outputs
-the results (\ie, number of test methods, failures, skips, and elapsed
-time) for each parallel configuration. Initially, we use an existing
-Maven log to identify the test classes to run, and we use the Maven
-dependency plugin~\cite{maven-dep} to build the project's classpath with
-the command \CodeIn{mvn dependency:build-classpath}. Once we have the
+
+\Mar{estou aqui...}
+
+Our script takes a list
+o tests classes to run as an input and outputs the results (\ie,
+number of test methods, failures, skips, and elapsed time) for each
+parallel configuration. Initially, we use an existing Maven log to
+identify the test classes to run, and we use the Maven dependency
+plugin~\cite{maven-dep} to build the project's classpath with the
+command \CodeIn{mvn dependency:build-classpath}. Once we have the
 classpath and the tests to run, we invoke our JUnit runner that runs
@@
 \ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
-runner with ParallelComputer~\cite{junit-parallel} that internally uses a pool of
-threads with cache to run test classes and methods. For the
-configurations with forked JVMs (\ie, \ForkSeq{} and \ForkParMeth{}),
-we have a queue of test classes and a pool of three threads that
-``consumes'' the next test class and spawns a JVM to run it.
-Recall that in our setup (see Section~\ref{sec:setup}), we limited our
-kernel to use only three cores and reserved one for OS-related
-processes.
-To verify that our approach satisfies the purpose of this experiment,
-we executed some subjects on Maven and compared the performance with
-our artifacts and observed nonsignificant differences (a fraction of
-seconds in most cases).
-\Comment{
-    To obtain parallel configurations, we implemented a script that
-    takes a subject and a configuration label as inputs (\eg
-    \CodeIn{mapdb "c0"}), and the script outputs the modified version
-    of the subject with the desired configuration. The workflow
-    consists in copying the project directory to a new directory,
-    finding all existing build files (\ie, \pomf{} files), and
-    modifying all existing Maven Surefire configurations with new
-    values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
-    and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
+runner with ParallelComputer~\cite{junit-parallel} that internally
+uses a pool of threads with cache to run test classes and methods. For
+the configurations with forked JVMs (\ie, \ForkSeq{} and
+\ForkParMeth{}), we have a queue of test classes and a pool of three
+threads that ``consumes'' the next test class and spawns a JVM to run
+it.  Recall that in our setup (see Section~\ref{sec:setup}), we
+limited our kernel to use only three cores and reserved one for
+OS-related processes.  To verify that our approach satisfies the
+purpose of this experiment, we executed some subjects on Maven and
+compared the performance with our artifacts and observed
+nonsignificant differences (a fraction of seconds in most cases).
+\Comment{ To obtain parallel configurations, we implemented a script
+  that takes a subject and a configuration label as inputs (\eg
+  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
+  the subject with the desired configuration. The workflow consists in
+  copying the project directory to a new directory, finding all
+  existing build files (\ie, \pomf{} files), and modifying all
+  existing Maven Surefire configurations with new values for the
+  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
+  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
   manipulate XML documents. For configurations with forked JVMs
@@
   \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
-    core).  To adjust the pool of threads for parallelism within a
-    JVM, we changed the parameter \CodeIn{threadCount} with
-    \Jbc{should we consider 2 as it is the number of native threads
-    per core OR 6 as it represents 3 Cores * 2 native threads?}.To run
-    the subjects and their respective variations (\ie, the modified
-    versions according to the parallelism configuration), we used a
-    similar approach as described in Figure~\ref{fig:mvn-execution}
-    except that...
-}
-Also, we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our
-scripts to monitor the execution, and we configured the command to
-dispatch a \emph{kill} signal if the test execution exceeds a given
-time limit. We imposed this time constraint to avoid hanging
-indefinitely the experiment execution due to some thread contention
-that may occur (\eg, deadlock or livelock).  Finally, we saved each
-execution log and stack traces generated outputed from JUnit to
-collect the execution time, the number of failing tests, and for
-reference to analyze and diagnose outliers in our results.  For
+  core).  To adjust the pool of threads for parallelism within a JVM,
+  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
+    consider 2 as it is the number of native threads per core OR 6 as
+    it represents 3 Cores * 2 native threads?}.To run the subjects and
+  their respective variations (\ie, the modified versions according to
+  the parallelism configuration), we used a similar approach as
+  described in Figure~\ref{fig:mvn-execution} except that...  } Also,
+we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our scripts
+to monitor the execution, and we configured the command to dispatch a
+\emph{kill} signal if the test execution exceeds a given time
+limit. We imposed this time constraint to avoid hanging indefinitely
+the experiment execution due to some thread contention that may occur
+(\eg, deadlock or livelock).  Finally, we saved each execution log and
+stack traces generated outputed from JUnit to collect the execution
+time, the number of failing tests, and for reference to analyze and
+diagnose outliers in our results.
+
+For
 efficiency, we reported the speedup (\ie, $T_{\text{s}} /
@@
 
-\Fix{Draw conclusions}
+\Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
+jvm - maven surefire nao tratava algumas exceptions que aconteciam na
+execucao do teste, (3) timeout}
 

### 2017-05-13 paper/threats.tex
pass on rq7 (not done); going back to rq6

@@
   Validity:} Our results could be influenced by unintentional mistakes
-made by humans who interpreted survey data and implemented scripts to
-collect and analyze data. All those tasks could introduce bias.  To
-mitigate those threats, we worked in pairs as to increase chances of
-capturing unintentional mistakes.  \textit{Construct Validity:} We
-considered a number of metrics in this study that could influence some
-of our interpretations.  For example, we measured number of test cases
-per suite, distribution of test costs in a suite, time to run a suite,
-etc.  In principle, these metrics may not reflect the main problems
-associated with test efficiency.\Mar{...elaborate...}
+made by humans who interpreted survey data and implemented scripts and
+code to collect and analyze data. For example, we developed JUnit
+runners to reproduce Maven's parallel configurations.  All those tasks
+could introduce bias.  To mitigate those threats, we worked in pairs
+as to increase chances of capturing unintentional mistakes.
+\textit{Construct Validity:} We considered a number of metrics in this
+study that could influence some of our interpretations.  For example,
+we measured number of test cases per suite, distribution of test costs
+in a suite, time to run a suite, etc.  In principle, these metrics may
+not reflect the main problems associated with test
+efficiency.\Mar{...elaborate...}
 

### 2017-05-13 paper/evaluation.tex
minor change to rq6
pass on eval

@@
 threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
-Tarr (64-bit version). This experiment uses configuration \ForkSeq{}
+Tarr (64-bit version). This experiment uses configuration \emph{\ForkSeq{}}
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 as the goal is to evaluate the impact on runtime of spawning a growing number of
-JVMs in different CPUs.  Furthremore, we selected subject
-\subjectScalability{} as it represents the case of a long-running test
+JVMs in different CPUs.  We selected subject
+\subjectScalability{} in this experiment as it represents the case of a long-running test
 suite (see Figure~\ref{tab:speedup}) with test cases distributed
@@
 
-Figure~\ref{fig:scalability} shows the reduction of running times as
-more CPUs contribute to the execution.  \Fix{elaborate...}
+Figure~\ref{fig:scalability} shows the reduction in running times as
+more CPUs contribute to the execution.  We ran this experiment for a
+growing number of cores 1, 3, ..., 39.  The plot shows results up to
+17 cores as it is clear the tendency.  We noticed that improvements
+are marginal after three cores, which is the basic setup we used in
+other experiments.  This saturation is justified by the presence of a
+single test class, \CodeIn{org.mapdb.WALTruncat}, containing 15 test
+cases that take over four minutes to run.
 
@@
   \begin{minipage}{8cm}
-    \textit{Answering \numRQSpeedupTwo{}:}~\emph{...}
+    \textit{Answering \numRQSpeedupTwo{}:}~\emph{Results suggest that
+      execution FC0 scales with additional cores but there is a bound
+      on the speedup one can get related to how well the test suite is
+      balanced across test classes.}
   \end{minipage}

### 2017-05-13 paper/evaluation.tex
fixes

@@
 threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
-Tarr (64-bit version). This experiment uses configuration \emph{\ForkSeq{}}
+Tahr (64-bit version). This experiment uses configuration \emph{\ForkSeq{}}
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 single test class, \CodeIn{org.mapdb.WALTruncat}, containing 15 test
-cases that take over four minutes to run.
+cases that take over two minutes to run.
 

### 2017-05-13 paper/evaluation.tex
pass

@@
 
-\noindent\textbf{JUnit.} It is worth mentioning that we used JUnit as
-opposed to Maven to run configurations \emph{C*}.  After carefully
-verifying library versions for compatibility issues and comparing
-results with JUnit's we observed that several of Maven's executions
-exposed problems (\eg{} timeouts).  These issues are documented in our
-website~\cite{ourwebpage} through Docker containers.  To address those
-issues we implemented basic JUnit runner reflecting the effects of
-parallel configurations from Maven Surefire.
-
-\Mar{estou aqui...}
-
-Our script takes a list
-o tests classes to run as an input and outputs the results (\ie,
-number of test methods, failures, skips, and elapsed time) for each
-parallel configuration. Initially, we use an existing Maven log to
-identify the test classes to run, and we use the Maven dependency
+It is worth mentioning that we used JUnit as opposed to Maven to run
+configurations \emph{C*}.  After carefully verifying library versions
+for compatibility issues and comparing results with JUnit's we
+observed that several of Maven's executions exposed problems.  For
+example, Maven incorrectly counts the number of test cases executed
+for some cases where test flakiness are observed.  These issues are
+categorized and documented on our website~\cite{ourwebpage} with
+Docker containers (for reproduction).  To address those issues we
+implemented basic JUnit test runners (one for each \emph{C*}
+configuration), reflecting the effects of parallel configurations from
+Maven Surefire.  To write those runners we used Maven log files to
+identify test classes to run and used the Maven dependency
 plugin~\cite{maven-dep} to build the project's classpath with the
@@
 compared the performance with our artifacts and observed
-nonsignificant differences (a fraction of seconds in most cases).
+nonsignificant differences (a fraction of seconds in most cases).  To
+assure that our experiments terminate (recall tha deadlock or livelock
+could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
+configured to dispatch a \emph{kill} signal if test execution exceeds
+a given time limit. Finally, we saved each execution log and stack
+traces generated outputed from JUnit to collect the execution time,
+the number of failing tests, and for reference to analyze and diagnose
+outliers in our results.
+
+%% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
+%% jvm - maven surefire nao tratava algumas exceptions que aconteciam na
+%% execucao do teste, (3) timeout}
+
+%% The script we implemented to measure time and flakiness takes a list
+%% of tests classes to run as input and outputs the results (\ie, number
+%% of test methods, failures, skips, and elapsed time) for each parallel
+%% configuration.
+
 \Comment{ To obtain parallel configurations, we implemented a script
@@
   the parallelism configuration), we used a similar approach as
-  described in Figure~\ref{fig:mvn-execution} except that...  } Also,
-we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our scripts
-to monitor the execution, and we configured the command to dispatch a
-\emph{kill} signal if the test execution exceeds a given time
-limit. We imposed this time constraint to avoid hanging indefinitely
-the experiment execution due to some thread contention that may occur
-(\eg, deadlock or livelock).  Finally, we saved each execution log and
-stack traces generated outputed from JUnit to collect the execution
-time, the number of failing tests, and for reference to analyze and
-diagnose outliers in our results.
-
-For
-efficiency, we reported the speedup (\ie, $T_{\text{s}} /
-T_{\text{p}}$), and for flakiness, we reported the rate of failing
-tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
+  described in Figure~\ref{fig:mvn-execution} except that...  }
+
+%% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /
+%% T_{\text{p}}$), and for flakiness, we reported the rate of failing
+%% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
+
+\Mar{estou aqui...}
+
 Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
@@
 
-\Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
-jvm - maven surefire nao tratava algumas exceptions que aconteciam na
-execucao do teste, (3) timeout}
-
 \begin{center}

### 2017-05-13 paper/evaluation.tex
fix

@@
 and has the second highest value of $\sigma$.  For this project,
-however, cost is distributed more smoothly across \Fix{98} tests, of
-which \Fix{8 (8.1\%)} take more than \Fix{1s} to run with the rest of
+however, cost is distributed more smoothly across 98 tests, of
+which 8 (8.1\%) take more than 1s to run with the rest of
 the tests running faster.
@@
         \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
-        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
+        \Comment{Jankotek }MapDB & 1/1 & \ParClassParMeth{}\\%        
         \bottomrule%

### 2017-05-13 paper/evaluation.tex
rq7 (best I can do for the time)

@@
 \small
-\setlength{\tabcolsep}{3pt}
+\setlength{\tabcolsep}{2pt}
 \begin{tabular}{l|rr|rr|rr|rr|rr|rr}
@@
   failing tests in different configurations, compared to
-  \emph{\Seq{}}.\Mar{Can you please add name of module for all subjects?}}
+  \emph{\Seq{}}.}
 \label{tab:rq6-table}
@@
 
-\Mar{estou aqui...}
-
-Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
-subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
-  VALORES DE DESVIO PADRAO!}.
+Figure~\ref{tab:rq6-table} summarizes results ordered by subject's
+name. Recall that we only executed one module for each subject.
+Values are averaged across multiple executions.  We did not report
+standard deviations as they are very small in all cases.  Considering
+flakiness, results show that 0\% of flakiness have been reported in 26
+of the 60 combinations analyzed (43\% of the total) and that for seven
+of the ten projects 0\% flakiness was reported in at least one of the
+configurations.  The projects with flakiness in all configurations
+were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.
+It is worth highlighting the unfortunate case of \CodeIn{Moquette},
+which manifested more than 20\% flaky tests in every configuration.
+Considering time, it is noticeable from the averages, perhaps as
+expected, an increasing speedup from configuration
+\emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and from
+configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
+worth mentioning that some combinations manifested slowdown instead of
+speedup.  Recall that parallel execution introduces the overhead of
+spawning and managing JVMs and threads.
+
+\begin{center}
+\fbox{
+\begin{minipage}{8cm}
+\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
+  test suites of 70\% of the projects we analyzed could be run in
+  parallel without manifesting any flaky tests.  In some of these
+  cases, speedups were significant, ranging from 1x to 28.8x.}
+\end{minipage}
+}
+\end{center}
 
@@
 
-\Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
-dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
-Possivelmente o slowdown se deve ao tempo de resposta do servico quando
-a autentiticao falha}
-
-\Fix{Elaborate results from efficiency}
-
-\Fix{Elaborate results from flakiness}
-
-\Fix{highlight special cases}
-
-\begin{center}
-\fbox{
-\begin{minipage}{8cm}
-\textit{Answering \numRQIssuesOne{}:~\emph{\Jbc{summarize findings...}}}
-\end{minipage}
-}
-\end{center}
+%% \Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
+%% dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
+%% Possivelmente o slowdown se deve ao tempo de resposta do servico quando
+%% a autentiticao falha}
+
+%% \Fix{Elaborate results from efficiency}
+
+%% \Fix{Elaborate results from flakiness}
+
+%% \Fix{highlight special cases}
 
@@
 %%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
-%%  LocalWords:  outliers apache uber chaperone facebookarchive
-%%  LocalWords:  linkbench priori
+%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
+%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs

### 2017-05-13 paper/lessons.tex
minor tweaks
pass

@@
-\section{Lessons Learned}
+\section{Discussion}
 
-\vspace{1ex}\noindent{}\textbf{The Good.}\Fix{...}
+This paper reports our finding on a study to evaluate impact and usage
+of test suite parallelization, enabled by modern build systems and
+testing frameworks.  This study is important given the importance to
+speedup testing.  Note that test suite parallelization is
+complementary to alternative approach to speedup testing
+(see~Section~\ref{sec:related}).  The observations we made in this
+study trigger multiple actions:
 
-\vspace{1ex}\noindent{}\textbf{The Bad.}\Fix{...}
+\begin{itemize}
+\item \emph{Incentivize forking.}~Forked JVMs manifest low rates of
+  test flakiness.  For instance, in \emph{\ForkSeq{}}, only 4 of 10
+  projects manifest flakiness and, excluding the extreme case of
+  \CodeIn{Moquette}, projects manifest flaky tests in low rates 0.23\%
+  to 1.70\%.  Developers of projects with long-running test suites
+  should consider using that feature, which is available in modern
+  build systems today (\eg{}, Maven).\Mar{review from here...$\rightarrow$}
+\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
+  impressive speedups at the expense of sometimes impressive rates of
+  flakiness.  Breaking test dependencies to avoid flakiness and take
+  full advantage of those options is advised for developers with
+  greater interest in efficiency.
+\item \emph{Refactor tests for load balancing.}~Forked JVMs scales
+  better with the number of cores when the test workload is balanced
+  across testing classes.  To balance the workload, automated
+  user-oblivious refactoring can help in scenarios where developers
+  are not willing to change test code but have access to machines with
+  a high number of cores.
+\item \emph{Improve debugging for build systems.}~While preparing our
+  experiments, we found scenarios\Comment{, related to test
+    parallelization,} where Maven's executions did not reflect
+  corresponding JUnit's executions. (Docker reproduction scripts
+  available.) Those issues can hinder developers from using parallel
+  testing. Better debugging infrastructure is important.
+\end{itemize}
 
-\vspace{1ex}\noindent{}\textbf{The Ugly.}\Fix{...}
+This study brings to light the benefits and burdens of test suite
+parallelization to improve test efficiency. It provides
+recommendations to practicioners and developers of new techniques and
+tools aiming to speed up test execution with parallelization.

### 2017-05-13 paper/related.tex
wip - working on related

@@
 \label{sec:related}
-
-Several approaches have been proposed in the literature to optimize
-regression testing.  Research has focused mostly on test suite
-minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
-unsound (\ie{}, they do not guarantee that fault-revealing tests will
-be selected), however, more recently, sound techniques have been
+Researchers and practitioners have been shedding light to the to the
+demand of techniques for optimizing test execution. For instance, a
+recent paper from the automotive industry reported that test suites
+can take days to run~\cite{artl-etal-icst2015}.  There are different
+aspects to consider and when dealing with the challenge of reducing
+test cost. 
+Research has focused mostly on test suite minimization,
+prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
+Most of these techniques are unsound (\ie{}, they do not guarantee
+that fault-revealing tests will be selected), however, more recently,
+sound techniques have been
 proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
 example, to soundly select tests for execution,
-Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
+Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
 computes which tests have been impacted by changes.  A test is
-discarded for execution if it does not depend on any
-changed file dynamically reachable from execution.
+discarded for execution if it does not depend on any changed file
+dynamically reachable from execution. \Jbc{Elaborate...}
 %% this may reveal/suggest identity.  wait for CR
@@
 system~\cite{souto-damorim-jss}.}
-
-\Fix{elaborate...}As another example, a recent paper from the
-automotive industry reported that test suites can take days to
-run~\cite{artl-etal-icst2015}.
+\Jbc{Acho que o trabalho de Luo et al~\cite{luo-etal-fse2014} que eh
+uma analise empirica de testes de flaky se relaciona com o nosso no
+aspecto de falar dentre as demais categorias, sobre flakiness que se
+manifestam em situacoes de concorrencias. Este trabalho eh
+complementar ao nosso, uma vez que ele elabora as causas e solucoes
+para algumas falhas que se manifestaram em concorrencia.
+concorrencias.
+O Trabalho de Hilton et al~\cite{hilton-etal-ase2016}, embora tenha
+como objetivo entender o uso de CI, mostra que existe uma demanda em
+acelerar o build e execucao de testes em servidores de integracao
+    continua
+}

### 2017-05-13 paper/conclusions.tex
conclusions (best i can do for now)

@@
 
-\Fix{...}
+Testing is expensive.  Despite all advances in regression testing
+research, dealing with high testing costs remains an important problem
+in Software Engineering.  This paper reports our findings on the usage
+and impact of test execution parallelization in open-source projects.
+Multicore CPUs, as well as testing frameworks and build systems to
+capitalize on them, are widely available today.  Despite some
+resistance observed from practicioners, our results suggest that
+parallelization can be done in many cases without sacrificing
+reliability and more research needs to be done to improve automation
+(\eg{}, breaking test dependencies and refactoring test suites) as to
+safely optimize parallel execution.  The artifacts we produced as
+result of this study are available from the following web
+page \webpage{}.
 
-These tools can be used out-of-the-box to support \emph{system}
-testing of applications that have been designed to handle concurrent
-user accesses\cite{selenium-hq}.
+%% Overall, this study brings to light the benefits and burdens of test
+%% suite parallelization to improve test efficiency. It provides
+%% recommendations to practicioners and developers of new techniques and
+%% tools aiming to speed up test execution with parallelization.
+
+%% Considering a set of \numSubjs{} popular Java projects we analyzed, we
+%% found that \percentMedLongRunning{} of the projects contain costly
+%% test suites but parallelization features still seem underutilized in
+%% practice~---~only \percentParallelUpdated{} of costly projects use
+%% parallelization.  The main reported reason for adoption resistance was
+%% the concern to deal with concurrency issues.  Results suggest that, on
+%% average, developers prefer high predictability than high performance
+%% in running tests.

### 2017-05-13 paper/intro.tex
fix intro
conclusions (best i can do for now)

@@
 \avgSpeedup{}x.  Although we found cases with very high speedups
-(\eg{}, 28.0x for project Jcabi), we found cases where speedups were
+(\eg{}, 28.8x for project Jcabi), we found cases where speedups were
 not very significant.  Considering the scalability experiment, we
@@
 
-The artifacts we produced as results of this study are available from
+The artifacts we produced as result of this study are available from
 the following web page \webpage{}.

### 2017-05-13 paper/evaluation.tex
fix
pass

@@
 data and generate plots.  All source artifacts are publicly available
-for replication (on request)\Comment{ at \Fix{create gh-pages}}.  This
+for replication (on our website~\cite{ourwebpage})\Comment{ at \Fix{create gh-pages}}.  This
 includes supporting scripts (\eg, the script that test subjects and
@@
 each module discarding duplicates as to avoid inflating counts for
-configuration modes that appear in several modules of the same
-project. For instance, if a project contains two modules using the
-same configuration, we counted only one occurrence.
-
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
@@
 \end{wrapfigure}
+configuration modes that appear in several modules of the same
+project. For instance, if a project contains two modules using the
+same configuration, we counted only one occurrence.
+
 Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
@@
 Tahr (64-bit version). This experiment uses configuration \emph{\ForkSeq{}}
-\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
-    \centering
-    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
-    \caption{\label{fig:scalability}Scalability.}
-\end{wrapfigure}
 as the goal is to evaluate the impact on runtime of spawning a growing number of
@@
 classes will be assigned to which JVM that the build system forks.
+
+%\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=.35\textwidth]{R/scalability/scalability.pdf}
+    \caption{\label{fig:scalability}Scalability.}
+\end{figure}
 

### 2017-05-13 paper/lessons.tex
pass

@@
   should consider using that feature, which is available in modern
-  build systems today (\eg{}, Maven).\Mar{review from here...$\rightarrow$}
+  build systems today (\eg{}, Maven).
 \item \emph{Break test dependencies.}~Non-forked JVMs can achieve
@@
 parallelization to improve test efficiency. It provides
-recommendations to practicioners and developers of new techniques and
+recommendations to practitioners and developers of new techniques and
 tools aiming to speed up test execution with parallelization.
+
+%%  LocalWords:  parallelization Incentivize JVMs Moquette Refactor
+%%  LocalWords:  refactoring JUnit's

### 2017-05-13 paper/related.tex
some notes on related work

@@
 discarded for execution if it does not depend on any changed file
-dynamically reachable from execution. \Jbc{Elaborate...}
+dynamically reachable from execution. Although Ekstazi is focused on
+regression test selection, it highlights the importance of parallelism
+as a complement to test selection. In fact, as in their evaluation, we
+also discovered subjects with parallelism enabled by default.
 %% this may reveal/suggest identity.  wait for CR
@@
 system~\cite{souto-damorim-jss}.}
-\Jbc{Acho que o trabalho de Luo et al~\cite{luo-etal-fse2014} que eh
-uma analise empirica de testes de flaky se relaciona com o nosso no
+The work of Luo et al~\cite{luo-etal-fse2014} reports and empirical
+analysis on test flakiness. \Jbc{se relaciona com o nosso no
 aspecto de falar dentre as demais categorias, sobre flakiness que se

### 2017-05-13 paper/evaluation.tex
spell checking

@@
 
-Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
+Figure~\ref{tab:freqmodes-dynamic} shows the projects we identified
 where parallelism is enabled by default in Maven.  Column
@@
 \CodeIn{\$\{parallel.type\}}).  It is also important to note that this
-approach is not immune to false negatives, which can ocurr when
+approach is not immune to false negatives, which can occur when
 \emph{pom.xml} files are encapsulated in jar files or downloaded from
@@
 Furthermore, \emailsCI{} of the participants indicated the use of
-Continuous Integration (CI) to run tests, with \emailsDistributed{} of
+Continuous Integration (CI) to run tests, with \emailsDiistributed{} of
 these participants reporting that test suites are modularized and
-those modules are tested independetly in CI servers through different
-parameters.  Those participants argumented that such practice helps to
+those modules are tested independently in CI servers through different
+parameters.  Those participants explained that such practice helps to
 reduce time to observe test failures, which is the goal of speeding up
@@
 (similar case as reported in Section~\ref{sec:rqC-2}), in one of the
-projects the particpant considered that distributed CI was a form of
+projects the participant considered that distributed CI was a form of
 parallelism, and in four projects the team preferred to implement
@@
 most part during test execution.  Finally, we note that parallel
-execution in \CodeIn{Log4J2} was innefective.  We found that Maven
+execution in \CodeIn{Log4J2} was ineffective.  We found that Maven
 invokes several test modules in this project but the test modules that
@@
 the test classes with different parallel configurations at once. For
-the sequential execution, we ivonke the default JUnit test runner. For
+the sequential execution, we invoke the default JUnit test runner. For
 parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
@@
 compared the performance with our artifacts and observed
-nonsignificant differences (a fraction of seconds in most cases).  To
-assure that our experiments terminate (recall tha deadlock or livelock
+insignificant differences (a fraction of seconds in most cases).  To
+assure that our experiments terminate (recall that deadlock or livelock
 could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
@@
 a given time limit. Finally, we saved each execution log and stack
-traces generated outputed from JUnit to collect the execution time,
+traces generated from JUnit to collect the execution time,
 the number of failing tests, and for reference to analyze and diagnose
@@
 %%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
-%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
+%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
 %%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
 %%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
-%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs
+%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
+%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
+%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
+%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
+%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
+%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
+%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
+%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
+%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock
+%%  LocalWords:  mapdb workflow XPath

### 2017-05-13 paper/evaluation.tex
fix

@@
 Furthermore, \emailsCI{} of the participants indicated the use of
-Continuous Integration (CI) to run tests, with \emailsDiistributed{} of
+Continuous Integration (CI) to run tests, with \emailsDistributed{} of
 these participants reporting that test suites are modularized and

### 2017-05-13 paper/related.tex
fix
omitted my comment

@@
 can take days to run~\cite{artl-etal-icst2015}.  There are different
-aspects to consider and when dealing with the challenge of reducing
+aspects to consider when dealing with the challenge of reducing
 test cost. 
@@
 as a complement to test selection.  In fact, as in their evaluation, we
-also discovered subjects with parallelism enabled by default.
-%% this may reveal/suggest identity.  wait for CR
+also discovered subjects with parallelism enabled by default.  Test
+suite parallelization is complementary to regression testing techniques.
+
+\Comment{
 \Comment{
@@
 }
+}

### 2017-07-25 paper/evaluation.tex
Minor grammar fix
Fixed error in RQ1 conclusion - 1min instead of 3min

@@
 \newcommand{\numRQFeasibilityTwo}{RQ2}
-\newcommand{\RQFeasibilityTwo}{How time is distributed across test cases?}
+\newcommand{\RQFeasibilityTwo}{How is time distributed across test cases?}
 
@@
       the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
-      projects) take at least 3 minutes to run and
+      projects) take at least 1 minute to run and
       \percentLongRunning{} take at least 5 minutes to run.\Comment{

### 2017-07-26 paper/evaluation.tex
Addressed reviewer 1's comments about C* configs

@@
 
-It is worth mentioning that we used JUnit as opposed to Maven to run
-configurations \emph{C*}.  After carefully verifying library versions
+It is worth mentioning that we used \Jbc{custom} JUnit \Jbc{runners}
+as opposed to Maven to run \Comment{configurations \emph{C*}}test
+suites with different parallel configurations (see
+Section~\ref{sec:modes})\Jbc{$\leftarrow$ Reviewer 1 was confused with
+the notation \emph{C*} AND the original sentence was not accurate to
+this paragraph}.
+After carefully verifying library versions
 for compatibility issues and comparing results with JUnit's we
@@
 Docker containers (for reproduction).  To address those issues we
-implemented basic JUnit test runners (one for each \emph{C*}
+implemented basic JUnit test runners (one for each \Jbc{parallel}
 configuration), reflecting the effects of parallel configurations from

### 2017-07-26 paper/evaluation.tex
minor changes

--- 2017-07-25 paper/evaluation.tex
@@
 
-This experiment evaluates the impact of making available to the build
-system a growing number of CPUs for testing.  For that reason, we used
-a machine with more cores compared to the one described in
+This experiment evaluates the impact of making a growing number of
+CPUs for testing available to the build system.  For that reason, we
+used a machine with more cores compared to the one described in
 Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
@@
 threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
-Tahr (64-bit version). This experiment uses configuration \emph{\ForkSeq{}}
-as the goal is to evaluate the impact on runtime of spawning a growing number of
-JVMs in different CPUs.  We selected subject
-\subjectScalability{} in this experiment as it represents the case of a long-running test
-suite (see Figure~\ref{tab:speedup}) with test cases distributed
-across many test classes (194 test classes for \subjectScalability{}).
-Note that a test class is the smallest unit that can be used to spawn
-a test job on a JVM and that we have no control over which test
-classes will be assigned to which JVM that the build system forks.
-
-%\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=.35\textwidth]{R/scalability/scalability.pdf}
+Tahr (64-bit version). This experiment uses configuration
+\emph{\ForkSeq{}} as the goal is to evaluate the impact on runtime of
+\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  
+  %\begin{figure}[h]
+  \centering
+  \includegraphics[width=.25\textwidth]{R/scalability/scalability.pdf}
   \caption{\label{fig:scalability}Scalability.}
-\end{figure}
+  %\end{figure}
+%  \vspace{-1ex}    
+\end{wrapfigure}
+spawning a growing number of JVMs in different CPUs.  We selected
+subject \subjectScalability{} in this experiment as it represents the
+case of a long-running test suite (see Figure~\ref{tab:speedup}) with
+test cases distributed across many test classes~--~194.  Note that a
+test class is the smallest unit that can be used to spawn a test job
+on a JVM and that we have no control over which test classes will be
+assigned to which JVM that the build system forks.
 
@@
 
-It is worth mentioning that we used JUnit as opposed to Maven to run
-configurations \emph{C*}.  After carefully verifying library versions
-for compatibility issues and comparing results with JUnit's we
-observed that several of Maven's executions exposed problems.  For
-example, Maven incorrectly counts the number of test cases executed
-for some cases where test flakiness are observed.  These issues are
-categorized and documented on our website~\cite{ourwebpage} with
-Docker containers (for reproduction).  To address those issues we
-implemented basic JUnit test runners (one for each \emph{C*}
-configuration), reflecting the effects of parallel configurations from
-Maven Surefire.  To write those runners we used Maven log files to
-identify test classes to run and used the Maven dependency
-plugin~\cite{maven-dep} to build the project's classpath with the
-command \CodeIn{mvn dependency:build-classpath}. Once we have the
-classpath and the tests to run, we invoke our JUnit runner that runs
-the test classes with different parallel configurations at once. For
-the sequential execution, we invoke the default JUnit test runner. For
-parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
-\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
-runner with ParallelComputer~\cite{junit-parallel} that internally
-uses a pool of threads with cache to run test classes and methods. For
-the configurations with forked JVMs (\ie, \ForkSeq{} and
-\ForkParMeth{}), we have a queue of test classes and a pool of three
-threads that ``consumes'' the next test class and spawns a JVM to run
-it.  Recall that in our setup (see Section~\ref{sec:setup}), we
-limited our kernel to use only three cores and reserved one for
-OS-related processes.  To verify that our approach satisfies the
-purpose of this experiment, we executed some subjects on Maven and
-compared the performance with our artifacts and observed
-insignificant differences (a fraction of seconds in most cases).  To
-assure that our experiments terminate (recall that deadlock or livelock
-could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
-configured to dispatch a \emph{kill} signal if test execution exceeds
-a given time limit. Finally, we saved each execution log and stack
-traces generated from JUnit to collect the execution time,
-the number of failing tests, and for reference to analyze and diagnose
-outliers in our results.
+It is worth mentioning that we used custom JUnit runners as opposed to
+Maven to run \Comment{configurations \emph{C*}}test suites with
+different parallel configurations (see Section~\ref{sec:modes}).
+After carefully checking library versions for compatibility issues and
+comparing results with JUnit's we observed that several of Maven's
+executions exposed problems.  For example, Maven incorrectly counts
+the number of test cases executed for some cases where test flakiness
+are observed.  These issues are categorized and documented on our
+website~\cite{ourwebpage} with Docker containers (for reproduction).
+To address those issues we implemented basic JUnit test runners (one
+for each parallel configuration), reflecting the effects of parallel
+configurations from Maven Surefire.  To write those runners we used
+Maven log files to identify test classes to run and used the Maven
+dependency plugin~\cite{maven-dep} to build the project's classpath
+with the command \CodeIn{mvn dependency:build-classpath}. Once we have
+the classpath and the tests to run, we invoke our JUnit runner that
+runs the test classes with different parallel configurations at
+once. For the sequential execution, we invoke the default JUnit test
+runner. For parallelism within a JVM (\ie, the configurations
+\SeqClassParMeth{}, \ParClassSeqMeth{}, and \ParClassParMeth{}), we
+configured the JUnit runner with
+ParallelComputer~\cite{junit-parallel} that internally uses a pool of
+threads with cache to run test classes and methods. For the
+configurations with forked JVMs (\ie, \ForkSeq{} and \ForkParMeth{}),
+we have a queue of test classes and a pool of three threads that
+``consumes'' the next test class and spawns a JVM to run it.  Recall
+that in our setup (see Section~\ref{sec:setup}), we limited our kernel
+to use only three cores and reserved one for OS-related processes.  To
+verify that our approach satisfies the purpose of this experiment, we
+executed some subjects on Maven and compared the performance with our
+artifacts and observed insignificant differences (a fraction of
+seconds in most cases).  To assure that our experiments terminate
+(recall that deadlock or livelock could occur) we used the
+\CodeIn{timeout} command~\cite{timeout-cmd} configured to dispatch a
+\emph{kill} signal if test execution exceeds a given time
+limit. Finally, we saved each execution log and stack traces generated
+from JUnit to collect the execution time, the number of failing tests,
+and for reference to analyze and diagnose outliers in our results.
 

### 2017-07-27 paper/evaluation.tex
Addressed more comments from reviewer 1

@@
 \ForkParMeth{}.  Large projects may contain several test suites
-distributed on different Maven modules potentially using different
-configurations.  For those cases, we collected the Maven output from
-each module discarding duplicates as to avoid inflating counts for
-\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+\begin{wraptable}{r}{0pt}%0.525\linewidth
   \footnotesize
@@
 %    \resizebox{.48\textwidth}{!}{%
-    \begin{tabular}{lrr}
+    \begin{tabular}{llcr}
         \toprule
-        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
+        \multirow{2}{*}{\emph{Group}} & \multirow{2}{*}{\emph{Subject}} & \emph{\# of} & \multirow{2}{*}{\emph{Mode}}\\%
+                                      &                                 & \emph{modules} &\\%
         \midrule%
-        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
-        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
-        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
-        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
-        Javaslang & 3/3 & \ParClassParMeth{}\\%
-        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
-        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
-        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
-        \Comment{Jankotek }MapDB & 1/1 & \ParClassParMeth{}\\%        
+        Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 & \ParClassSeqMeth{}\\%
+        Medium & \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%
+        Long & \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
+        Medium & \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
+        Medium & Javaslang & 3/3 & \ParClassParMeth{}\\%
+        Medium & Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%
+        Medium & \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
+        Long & \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
+        Long & \Comment{Jankotek }MapDB & 1/1 & \ParClassParMeth{}\\%
         \bottomrule%
@@
     \label{tab:freqmodes-dynamic}
-\end{wrapfigure}
+\end{wraptable}
+distributed on different Maven modules potentially using different
+configurations.  For those cases, we collected the Maven output from
+each module discarding duplicates as to avoid inflating counts for
 configuration modes that appear in several modules of the same
@@
 same configuration, we counted only one occurrence.
-
-Figure~\ref{tab:freqmodes-dynamic} shows the projects we identified
+Table~\ref{tab:freqmodes-dynamic} shows the projects we identified
 where parallelism is enabled by default in Maven.  Column
@@
 parallelism.  Compared to the set of projects listed in
-Figure~\ref{tab:speedup}, we found two new projects, namely:
+Table~\ref{tab:speedup}, we found two new projects, namely:
 \CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
@@
 subjects from our benchmark that use parallelization \emph{by default}
-(see Figure~\ref{tab:freqmodes-dynamic}).  We compared running times
+(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
 with parallelization~---~configured by project owners~---~and without
@@
 
-Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
+Table~\ref{tab:speedup} summarizes results.  Lines are sorted by
 project names.  Columns ``\emph{Group}'' and
@@
 
-\begin{figure}[h!]
+\begin{table}[h!]
 \centering
@@
   appears in gray color.}
-\end{figure}
+\end{table}
 
@@
 subject \subjectScalability{} in this experiment as it represents the
-case of a long-running test suite (see Figure~\ref{tab:speedup}) with
+case of a long-running test suite (see Table~\ref{tab:speedup}) with
 test cases distributed across many test classes~--~194.  Note that a
@@
 
-\begin{figure*}[t]  
+\begin{table*}[t]
 \centering
@@
 \label{tab:rq6-table}
-\end{figure*}
+\end{table*}
 
@@
 
-Figure~\ref{tab:rq6-table} summarizes results ordered by subject's
+Table~\ref{tab:rq6-table} summarizes results ordered by subject's
 name. Recall that we only executed one module for each subject.

### 2017-08-15 paper/codes/evaluation.tex
Adjusted vspace and deleted unnecessary comment in RQ1
pass on intro and evaluation (up to and including III.A)
Removed unnecessary comment
Uploading preliminar updates

@@
 \begin{lstlisting}[language=Bash]
-MAVEN_IGNORES="-Dmaven.javadoc.skip=true -Drat.skip=true \
+MAVEN_SKIPS="-Drat.skip=true -Dmaven.javadoc.skip=true \
     -Djacoco.skip=true -Dcheckstyle.skip=true \
-    -Dfindbugs=true -Dcobertura.skip=true"
+    -Dfindbugs.skip=true -Dcobertura.skip=true \
+    -Dpmd.skip=true -Dcpd.skip=true"
 
@@
     cd $SUBJECTS_HOME/$subj
-    mvn clean install -DskipTests $MAVEN_IGNORES
-    mvn dependency:go-offline
-    mvn -o test $MAVEN_IGNORES &> $LOG
-    cat $LOG | grep "\[INFO\] Total time:"
+    mvn clean dependency:go-offline
+    mvn test-compile install -DskipTests $MAVEN_SKIPS \
+        &> compile.log
+    mvn test -o -fae $MAVEN_SKIP &> testing.log
+    cat testing.log \
+        | grep --text "\[INFO\] Total time:" \
+        | tail -n 1
 done
 \end{lstlisting}
-\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
-    test suites. For each subject, we compile the source and test files, fetch
-    all dependencies, and execute the tests in offline mode ignoring
-    non-related tasks. Unnecessary commands are omitted for simplicity.}
+\caption{\label{fig:mvn-execution} Bash script to measure time cost of
+  test suites. For each subject, we fetch all dependencies,
+  compile the source and test files, and execute the tests in
+  offline mode ignoring non-related tasks. Test-unrelated tasks
+  are omitted.}
 \end{figure}

### 2017-08-15 paper/evaluation.tex
Uploading preliminar updates

@@
 Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
-execution (lines 1-3).  Furthermore, to avoid noise from operating
+execution (lines 1-4).  Furthermore, to avoid noise from operating
 system events, we configured our workstation to run only essential
@@
 line.  Results were very close.
-
-The main loop (lines 5-11) of the script in
+\Jbc{This is not true for projects running tests in parallel by defaut.
+Recall from RQ3 that some projects run tests in parallel by default.
+How should we address this?}
+
+The main loop (lines 6-15) of the script in
 Figure~\ref{fig:mvn-execution} iterates over the list of subjects and
 invokes Maven multiple times\Comment{ to isolate cost of running
-  tests} (lines 7-9).  It first compiles the source and test files
-(line 7), make all dependencies available locally (line 8), and then
-runs the tests in offline mode as to skip the package update task,
-enabled by default (line 9). After execution, we used a regular
-expression on the output log to extract elapsed time (line 10).
-
-%% We executed each project's test suite for
-%% \Fix{5} times through Maven and directly through JUnit each project
+tests} (lines 8-11).  It first makes all dependencies available locally
+(line 8), compiles the source and test files (line 9), and then runs
+the tests in offline mode as to skip the package update task, enabled
+by default (line 11). After execution, we used a regular expression on
+the output log to extract the elapsed time (line 12-14).
 
@@
     %% \end{subfigure}
-    \caption{\label{fig:time-distributions}Time distributions.}%
+    \caption{\label{fig:time-distributions}Time distributions. X-axis
+        denote projects appearing in arbitrary order.}%
 \end{figure}

### 2017-08-15 paper/threats.tex
pass
Uploading preliminar updates

@@
 code to collect and analyze data. For example, we developed JUnit
-runners to reproduce Maven's parallel configurations.  All those tasks
-could introduce bias.  To mitigate those threats, we worked in pairs
-as to increase chances of capturing unintentional mistakes.
+runners to reproduce Maven's parallel configurations and implemented
+several scripts to automate our experiments.  All those tasks
+could introduce bias in our results.  To mitigate those threats, we
+worked in pairs as to increase chances of capturing unintentional
+mistakes. Also, we re-executed our experiments on different machines
+with different hardware to ensure that our results are consistent.
 \textit{Construct Validity:} We considered a number of metrics in this
@@
 not reflect the main problems associated with test
-efficiency.\Mar{...elaborate...}
+efficiency.
+ \Jbc{remember to mention failing tests and how we mitigate
+this threat}
 

### 2017-08-15 paper/plots/older-2/cropall.sh

@@ -1,0 +1,2 @@
+#!/bin/bash
+for f in `ls | grep pdf`; do pdfcrop $f $f; done;

### 2017-08-25 paper/evaluation.tex
pass o subjects section

@@
 Java projects.  Important to highlight that, as of now, the
-\github{}'s search API can only reflect contents from README file (not
-other code elements); it does not provide a feature to search for
-projects containing certain files in the dir structure (\eg{},
-\emph{pom.xml}).  Figure~\ref{fig:subject-query} illustrates the query
-to the \github{} API as an HTTP request.
+\github{}'s search API can only reflect contents from repository
+statistics (\eg, number of forks, main programming language); it does
+not provide a feature to search for projects containing certain files
+in the dir structure (\eg{}, \emph{pom.xml}).
+Figure~\ref{fig:subject-query} illustrates the query to the \github{}
+API as an HTTP request.
 
@@
 https://api.github.com/search/repositories?q=language:java
-        +stars:>=100+pushed:>=2016-01-01
-        +mvn%20in:readme+sort:stars
+        +stars:>=100+pushed:>=2016+mvn%20in:readme
+        &sort=stars
 \end{lstlisting}
@@
 studies in testing and
-debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.} As of
-March 25th 2017, our search criteria returned \SubjectsGithub{}
-subjects. Figure~\ref{fig:subjects} summarizes our sample set.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
-    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
-    hosted on \github{}. From this initial sample, we ignored
-    \SubjectsGithubNotMaven{} projects without Maven support,
-    \SubjectsGithubNotCompilable{} uncompilable projects, and
-    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
-    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
-    \numSubjs{} projects to conduct our study.}
-\end{figure}
-
+debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.}
+Also, to avoid bias in our experiments, we executed multiple times all
+test suites from our sample set to detect and discard subjects with
+\emph{flaky tests}. \Fix{Discuss briefly test flakiness}.
+As of August 25th 2017, our search criteria returned \SubjectsGithub{}
+subjects. 
 From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
 projects were not Maven or did not have a \pomf{} in the root
-directory, \SubjectsGithubNotCompilable{} were unable to compile due
-to missing dependencies, and \SubjectsGithubNotTestable{} projects
+directory, \Comment{ were unable to compile due
+to missing dependencies,} and \SubjectsGithubNotTestable{} projects
 were untestable due to incompatible testing environment.  We also
@@
 final set of subjects consists of \numSubjs{} projects.
+Figure~\ref{fig:subjects} summarizes our sample set.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
+    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
+    hosted on \github{}. From this initial sample, we ignored
+    \SubjectsGithubNotMaven{} projects without Maven support,
+    \SubjectsGithubNotTestable{} untestable projects, and
+    \SubjectsGithubFlaky{} projects with flaky tests. We considered
+    \numSubjs{} projects to conduct our study.}
+\end{figure}
 

### 2017-08-25 paper/evaluation.tex
Done with Sec III

@@
 containing a \pomf{} file in the root directory.  A Maven project may
-contain several sub-modules with multiple \pomf{} files.\Comment{  We
-based our methodology to select experimental subjects on other recent
-studies in testing and
-debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.}
-Also, to avoid bias in our experiments, we executed multiple times all
-test suites from our sample set to detect and discard subjects with
-\emph{flaky tests}. \Fix{Discuss briefly test flakiness}.
+contain several sub-modules with multiple \pomf{} files.
+To avoid introducing noise in our experiments, for each project, we
+executed the tests \SubjectsReruns{} times to filter projects with
+deterministic outcome.
 As of August 25th 2017, our search criteria returned \SubjectsGithub{}
 subjects.
-From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
-projects were not Maven or did not have a \pomf{} in the root
-directory, \Comment{ were unable to compile due
-to missing dependencies,} and \SubjectsGithubNotTestable{} projects
-were untestable due to incompatible testing environment.  We also
-found \SubjectsGithubFlaky{} projects with ``flaky'' tests.  We
-considered those projects but ignored their tests (using JUnit's
-\CodeIn{@Ignore} annotation) as to avoid measurement noise.  To detect
-those projects, we executed every test suite for three times.  Our
-final set of subjects consists of \numSubjs{} projects.
+
+From these \SubjectsGithub{} downloaded projects,
+\SubjectsGithubNotMaven{} projects were not Maven or did not have a
+\pomf{} in the root directory and \SubjectsGithubNotTestable{}
+projects were unable to test due to incompatible environment (\eg,
+missing required web browser or database management system).
+In addition, we identified \SubjectsGithubFlaky{} projects with flaky
+tests.
+As some of our experiments consist in running tests in a multithreaded
+configuration, we ignored these projects as it would be impractical
+for us to identify whether a test failed due to a race condition.
+Our final set of subjects consists of \numSubjs{} projects.
 Figure~\ref{fig:subjects} summarizes our sample set.
@@
   \SubjectsGithubNotMaven{} projects without Maven support,
-    \SubjectsGithubNotTestable{} untestable projects, and
+  \SubjectsGithubNotTestable{} projects unable to test, and
   \SubjectsGithubFlaky{} projects with flaky tests. We considered

### 2017-08-25 paper/intro.tex
Done with Sec III

@@
   projects~---~} in running times.  Finally, the dimension
-\emph{tradeoffs} considers the problems in running tests in parallel,
-including test flakiness~\cite{luo-etal-fse2014}.  We briefly
-summarize our findings in the following.
+\emph{tradeoffs} considers the problems in running tests in parallel.
+\Fix{
+Non-deterministic outcome for
+For tests that change the state of a shared resources (\eg, file or
+in-memory collection), data races are likely to occurr.
+
+Data races are likely to occurr in a multithread execution as 
+different threare favors data races when Some tests may produce non-deterministic
+outcomes in a multithreaded ex when
+executed in 
+including test flakiness~\cite{luo-etal-fse2014}. A test case with
+non-deterministic outcome is also known as ``flaky test''.  are
+known as test with non-deterministic outcome and
+}
+We briefly summarize our findings in the following.
 

### 2017-08-28 paper/intro.tex
Added some content related to test flakiness

--- 2017-05-13 paper/intro.tex
@@
   projects~---~} in running times.  Finally, the dimension
-\emph{tradeoffs} considers the problems in running tests in parallel,
-including test flakiness~\cite{luo-etal-fse2014}.  We briefly
-summarize our findings in the following.
+\emph{tradeoffs} considers the problems in running tests in parallel.
+\Jbc{
+In practice, some test suites may not be prepared for a multithreaded
+execution.
+For instance, developers may unconsciously create tests assuming an
+specific order of execution.
+While parallelism may speed up tests, in those cases,
+tests may yield non-deterministic results due to data races.
+In general, a test that either pass or fail under the same conditions
+is known as a ``flaky test''~\cite{luo-etal-fse2014}. It is important
+to measure the presence of test flakiness and the trade-offs to
+overcome this issue.}
+We briefly summarize our findings in the following.
 

### 2017-08-30 paper/related.tex
adding note on related work
Added notes about SIMD architecture (related)

@@
 test cost.
+
+\textbf{Test selection vs. parallelism:}
 Research has focused mostly on test suite minimization,
@@
 also discovered subjects with parallelism enabled by default.  Test
-suite parallelization is complementary to regression testing techniques.
+suite parallelization is complementary to regression testing
+techniques.
+
+\textbf{Usage of massively parallel hardware:}
+Previous research investigated the feasibility of testing embedded
+software on \emph{Graphics Processing Units} (GPUs) as an alternative
+to multicore CPUs~\cite{rajan-etal-ase2014}.
+The \emph{Simple Instruction Multiple Data} (SIMD) architecture of
+modern GPUs allows to run the same test case with different test data
+over several threads.
+Although benchmarks indicate far superior performance over traditional
+multicore CPUs, existing GPU programming-models (\eg,
+CUDA~\cite{cuda}, and OpenCL~\cite{opencl}) are compatible only with a
+subset of the C/C++ language.
+Recent work proposed a compiler-assisted approach to make programs
+compatible to the relying programming
+model~\cite{yaneva-etal-issta2017}; however, \Jbc{Justify they are out
+of scope for our subjects...}.
+
+\Fix{Please:
+  (i) consider categorizing related work in sections  
+  (ii) list papers that need to be discussed
+  (iii) discuss papers that use multi-execution (SIMD cpus like GPUs)
+  to speedup testing
+  }
 
 \Comment{
+Running
+tests incompatible complex test suites on GPUs remains a challenge.
 \Comment{

### 2017-08-30 paper/evaluation.tex
Removed outdated comment
Moved content about flaky tests from intro to sec III

@@
 missing required web browser or database management system).
-In addition, we identified \SubjectsGithubFlaky{} projects with flaky
-tests.
-As some of our experiments consist in running tests in a multithreaded
-configuration, we ignored these projects as it would be impractical
-for us to identify whether a test failed due to a race condition.
+In addition, we identified \SubjectsGithubFlaky{} projects with
+non-deterministic test results.
+In general, a test that either pass or fail under the same circumstances
+is known as a ``flaky test''~\cite{luo-etal-fse2014}.
+\Comment{While there are several causes that may introduce randomness on test
+results, our concern is on flakiness caused by
+parallel execution.}
+As some of our experiments consist in running tests on different
+threads, we ignored these projects as it would be impractical
+to identify whether a test failed due to a race condition or some
+other source of flakiness.
 Our final set of subjects consists of \numSubjs{} projects.
@@
 line.  Results were very close.
-\Jbc{This is not true for projects running tests in parallel by defaut.
-Recall from RQ3 that some projects run tests in parallel by default.
-How should we address this?}
 

### 2017-08-30 paper/related.tex
Moved content about flaky tests from intro to sec III

@@
 The \emph{Simple Instruction Multiple Data} (SIMD) architecture of
-modern GPUs allows to run the same test case with different test data
+modern GPUs allows running the same test case with different test data
 over several threads.
@@
 Recent work proposed a compiler-assisted approach to make programs
-compatible to the relying programming
+compatible with the relying programming
 model~\cite{yaneva-etal-issta2017}; however, \Jbc{Justify they are out

### 2017-08-30 paper/threats.tex
Removed unnecessary sentence
Moved content about flaky tests from intro to sec III

@@
 evaluate the extent to which our observations would change when using
-different testing frameworks and build systems.  \textit{Internal
-  Validity:} Our results could be influenced by unintentional mistakes
-made by humans who interpreted survey data and implemented scripts and
-code to collect and analyze data. For example, we developed JUnit
-runners to reproduce Maven's parallel configurations and implemented
-several scripts to automate our experiments.  All those tasks
-could introduce bias in our results.  To mitigate those threats, we
-worked in pairs as to increase chances of capturing unintentional
-mistakes. Also, we re-executed our experiments on different machines
-with different hardware to ensure that our results are consistent.
+different testing frameworks and build systems.
+\textit{Internal Validity:} Our results could be influenced by
+unintentional mistakes made by humans who interpreted survey data and
+implemented scripts and code to collect and analyze data.
+For example, we developed JUnit runners to reproduce Maven's parallel
+configurations and implemented several scripts to automate our
+experiments (\eg, run tests and detect parallelism enabled by default
+in the subjects).
+All those tasks could introduce bias in our results.
+To mitigate those threats, we worked in pairs as to increase chances
+of capturing unintentional mistakes.
 \textit{Construct Validity:} We considered a number of metrics in this
@@
 efficiency.
- \Jbc{remember to mention failing tests and how we mitigate
-this threat}
 

### 2017-08-31 paper/evaluation.tex
Updated RQ1 and RQ2

@@
 \numSubjsPass{} successfully executed all tests and \numSubjsFail{}
-reported some test failures.  Second, some projects may omit
-long-running tests on their default execution. For instance, the
-project \CodeIn{apache.maven-surefire} runs all unit tests in a few
-seconds.  According to our criteria, this project is to be classified
-as \shortg{} but a closer look reveals that only smoke tests are run
-by default in this project.  Time-consuming integration and system
-tests are only accessible via custom parameters, which we do not
-handle in our experimental setup.  We enabled such parameters for this
-specific project and observed that testing time goes to nearly 30
-minutes.  For simplicity, we considered only the tests executed by
-default.
+reported some test failures.
+\Jbc{
+From these \numSubjsFail{} subjects, 67 projects have less than 10\%
+of failing tests.
+}
+Second, some projects may omit long-running tests on their default
+execution. For instance, the project \CodeIn{apache.maven-surefire}
+runs all unit tests in a few seconds.  According to our criteria, this
+project is to be classified as \shortg{} but a closer look reveals
+that only smoke tests are run by default in this project.
+Time-consuming integration and system tests are only accessible via
+custom parameters, which we do not handle in our experimental setup.
+We enabled such parameters for this specific project and observed that
+testing time goes to nearly 30 minutes.  For simplicity, we considered
+only the tests executed by default.
 
@@
       open-source projects.  We found that \percentMedLongRunning{} of
-      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
+      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 6
       projects) take at least 1 minute to run and

### 2017-08-31 paper/evaluation.tex
Fixed issues on RQ2

@@
 $\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
-medium group.  This project contains only 65 tests, 62 of which take
-less than 0.5s to run, one of which takes nearly 3s to run, and two of
-which take $\sim$40m to run.  For this project, 99.2\% of the
-execution cost is dominated by only 3\% of the tests; without these
+\longg{} group.  This project contains only 26 tests, 17 of which take
+less than 0.5s to run, one of which takes nearly 3s to run, two of
+which take nearly 11s to run, four which takes in average 3m to run, and two of
+which take $\sim$8m to run.  For this project, 98.4\% of the
+execution cost is dominated by 20\% of the tests; without these
 two costly tests this project would have been classified as
@@
 project \CodeIn{uber\_chaperone} was a corner case; we did not find
-other projects with such extreme time monopolization profile.  Project
-\CodeIn{facebookarchive\_linkbench} is also classified as long-running
-and has the second highest value of $\sigma$.  For this project,
-however, cost is distributed more smoothly across 98 tests, of
-which 8 (8.1\%) take more than 1s to run with the rest of
+other projects with such extreme time monopolization profile.
+Project \CodeIn{facebookarchive\_linkbench} is also classified as
+long-running and has the second highest value of $\sigma$.
+For this project, however, cost is distributed more smoothly across 98
+tests, of which 8 (8.1\%) take more than 1s to run with the rest of
 the tests running faster.

### 2017-09-01 paper/evaluation.tex
dir rename
Pass on text

@@
 other source of flakiness.
+\Jbc{From the \SubjectsGithubConsistant{} projects with
+deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
+projects with more than \SuiteFailingThreshold{} of tests failing to
+reduce bias in our dataset.}
 Our final set of subjects consists of \numSubjs{} projects.
@@
   \centering
-  \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
+  \includegraphics[width=0.25\textwidth]{results/piechart-subjs.pdf}
   \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
@@
   \SubjectsGithubNotMaven{} projects without Maven support,
-  \SubjectsGithubNotTestable{} projects unable to test, and
-  \SubjectsGithubFlaky{} projects with flaky tests. We considered
+  \SubjectsGithubNotTestable{} projects unable to test,
+  \SubjectsGithubFlaky{} projects with flaky tests, and
+  \SubjectsGithubTooManyFailures{} projects had at least
+  \SuiteFailingThreshold{} of failing tests. We considered
   \numSubjs{} projects to conduct our study.}
@@
         \centering
-        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
+        \includegraphics[width=\textwidth]{results/barplot-timecost.pdf}
         \caption{\label{fig:rq1-barplot}}
@@
         \centering
-        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
+        \includegraphics[width=\textwidth]{results/boxplot-timecost.pdf}
         \caption{\label{fig:rq1-boxplot}}
@@
 It is important to note that we under-estimated cost in our
-experiments for two main reasons.  First, some tests may finish
-earlier than expected due to the observed test failures in some of the
-revisions we downloaded. From the \numSubjs{} testable projects,
-\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
-reported some test failures.
-\Jbc{
-From these \numSubjsFail{} subjects, 67 projects have less than 10\%
-of failing tests.
-}
-Second, some projects may omit long-running tests on their default
+experiments for one main reason.
+Some projects may omit long-running tests on their default
 execution. For instance, the project \CodeIn{apache.maven-surefire}
@@
 only the tests executed by default.
-
+\Jbc{
+Although failing tests may introduce noise in our measurements, we
+carefully eliminated subjects with more than \SuiteFailingThreshold{} of
+test failures. 
+From the \numSubjs{} testable projects, \numSubjsPass{} successfully
+executed all tests and \numSubjsFail{} reported some test failure.
+Furthermore, from these \numSubjsFail{} subjects, only 11 subjects
+have more than 5\% of failing tests (7.3\% in average).
+}
 \vspace{1ex}
@@
       open-source projects.  We found that \percentMedLongRunning{} of
-      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 6
+      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
       projects) take at least 1 minute to run and
@@
       \centering
-      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
+      \includegraphics[width=\textwidth]{results/testcost-long.pdf}
       \caption{\label{fig:longtcost}Long group.}
@@
       \centering
-      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
+      \includegraphics[width=\textwidth]{results/testcost-medium.pdf}
       \caption{\label{fig:medtcost}Medium group.}
@@
     \centering
-    \includegraphics[width=.85\textwidth]{plots/boxplots-testcases.pdf}
+    \includegraphics[width=.85\textwidth]{results/boxplots-testcases.pdf}
     \caption{\label{fig:size-testsuites}Size of test suites.}
@@
     \centering
-    \includegraphics[width=.95\textwidth]{plots/scatter-testcost.pdf}
+    \includegraphics[width=.95\textwidth]{results/scatter-testcost.pdf}
     \caption{\label{fig:scattercost}Size versus running time of
@@
 %    \centering
-%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
+%    \includegraphics[width=0.32\textwidth]{results/barplot-modes-dynamic.pdf}
 %    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
@@
 %%     \centering
-%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
+%%     \includegraphics[width=0.32\textwidth]{results/barplot-modes-static.pdf}
 %% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
@@
     \centering
-    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
+    \includegraphics[width=.18\textwidth]{results/survey.pdf}
     \caption{\label{fig:rq5-answers}Summary of developer's answers to

### 2017-09-01 paper/threats.tex
Pass on text

@@
 different testing frameworks and build systems.
+\Jbc{Also, some of the selected subjects contain failing tests. Test
+failures may shrink the expected running due to an early termination
+or even inflate the running time (\eg, test waiting indefinitely for
+an unavailable resources). To mitigate this threat, we filtered
+projects with at least 90\% of the tests passing. Only 17\% of our
+subjects have failing tests. We carefully inspected our rawdata to
+ensure that there is no failing test inflating our results.}
 \textit{Internal Validity:} Our results could be influenced by

### 2017-09-01 paper/intro.tex
Moved content about flaky tests from intro to sec III
minor tweaks

--- 2017-05-13 paper/intro.tex
@@
 At large organizations, the alternative of renting cloud
-services\footnote{List of popular hosting cloud services:
-  \url{https://clutch.co/cloud}} or even building proprietary
+services~\cite{cloud-services} or even building proprietary
 infrastructures for running tests is a legitimate approach to mitigate
@@
 \emph{tradeoffs} considers the problems in running tests in parallel,
-including test flakiness~\cite{luo-etal-fse2014}.  We briefly
-summarize our findings in the following.
+including test flakiness~\cite{luo-etal-fse2014}.
+We briefly summarize our findings in the following.
 
@@
 that nearly \percentMedLongRunning{} of the projects take at least 1m
-to run their test suites and \percentLongRunning{} of the projects
-take at least 5m to run their suites.  Considering the \numMedLong{}
+to run and \percentLongRunning{} of the projects
+take at least 5m to run.  Considering the \numMedLong{}
 projects in those two groups, the average execution time of a test
@@
 
+\setlist[itemize]{leftmargin=1.1em}
 \begin{itemize}
@@
   greater interest in efficiency.
-\item \emph{Refactor tests for load balancing.}~Forked JVMs scales
+\item \emph{Refactor tests for load balancing.}~Forked JVMs scale
   better with the number of cores when the test workload is balanced
-  across testing classes.  To balance the workload, automated
-  user-oblivious refactoring can help in scenarios where developers
-  are not willing to change test code but have access to machines with
-  a high number of cores.
+  across testing classes.  Automated refactoring could help balance
+  the workload in scenarios where developers are not willing to change
+  test code but have access to machines with a high number of cores.
 \item \emph{Improve debugging for build systems.}~While preparing our

### 2017-09-01 paper/evaluation.tex
Minor fixes on RQ2

@@
 two costly tests this project would have been classified as
-short-running.  A closer inspection in the data indicates that the
-project \CodeIn{uber\_chaperone} was a corner case; we did not find
-other projects with such extreme time monopolization profile.
+short-running.
+We did not find other projects with such extreme time monopolization
+profile.
 Project \CodeIn{facebookarchive\_linkbench} is also classified as
@@
 
-Figure~\ref{fig:time-distributions} showed that the average median
-times were similar for \medg{} and \longg{}-running test suites.
-Results indicate that the difference in overall running times of
-projects in those groups was mainly justified by the number of test
-cases as opposed to the individual costs of test cases.
+Figure~\ref{fig:time-distributions} shows that the average median
+times are similar for \medg{} and \longg{}-running test suites.
+The difference in overall running times of projects in those groups
+is mainly justified by the number of test cases as opposed to the
+individual costs of test cases.
 Figure~\ref{fig:size-testsuites} shows the difference in the
@@
 group, the correlation between these two variables was weak.
-Figure~\ref{fig:scattercost} illustrates this correlation.
+Figure~\ref{fig:scattercost} illustrates this regression line.
 
@@
   projects with a very small number of tests monopolizing end-to-end
-    execution time were rare.}
+  execution time were rare. Time most often is distribuited evenly
+  across test cases.}
 \end{minipage}

### 2017-09-01 paper/related.tex
pass on threats and related work

--- 2017-05-13 paper/related.tex
@@
 test cost.
+
+\textit{Test Selection vs. Parallelism:}
 Research has focused mostly on test suite minimization,
@@
 also discovered subjects with parallelism enabled by default.  Test
-suite parallelization is complementary to regression testing techniques.
+suite parallelization is complementary to regression testing
+techniques.
+
+\Jbc{
+\textit{Usage of massively parallel hardware:}
+Previous research investigated the feasibility of testing embedded
+software on Graphics Processing Units (GPUs) as an alternative
+to multicore CPUs~\cite{rajan-etal-ase2014}.
+The Simple Instruction Multiple Data (SIMD) architecture of
+modern GPUs allows running the same test case with different test data
+over several threads.
+Although benchmarks indicate far superior performance over traditional
+multicore CPUs, existing GPU programming-models (\eg,
+CUDA~\cite{cuda}, and OpenCL~\cite{opencl}) are compatible only with a
+subset of the C/C++ language.
+Recent work proposed a compiler-assisted approach to make programs
+compatible with the relying programming
+model~\cite{yaneva-etal-issta2017}; however, }\Jbc{...Justify they are out
+of scope for our subjects...}.
+
+\Jbc{Missing work about testing in the cloud and Jon Bell}
 
 \Comment{
+\Fix{Please:
+  (i) consider categorizing related work in sections  
+  (ii) list papers that need to be discussed
+  (iii) discuss papers that use multi-execution (SIMD cpus like GPUs)
+  to speedup testing
+  }
+}
 \Comment{
@@
 applied in the context of the GCC~\cite{gcc} configurable
-system~\cite{souto-damorim-jss}.}
-The work of Luo et al~\cite{luo-etal-fse2014} reports and empirical
-analysis on test flakiness. \Jbc{se relaciona com o nosso no
-aspecto de falar dentre as demais categorias, sobre flakiness que se
-manifestam em situacoes de concorrencias. Este trabalho eh
-complementar ao nosso, uma vez que ele elabora as causas e solucoes
-para algumas falhas que se manifestaram em concorrencia.
-concorrencias.
+system~\cite{souto-damorim-jss}.
 O Trabalho de Hilton et al~\cite{hilton-etal-ase2016}, embora tenha
@@
 }
-}

### 2017-09-04 paper/evaluation.tex
Updated RQ3 and Macros

@@
         \midrule%
-        Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 & \ParClassSeqMeth{}\\%
-        Medium & \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%
-        Long & \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
-        Medium & \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
-        Medium & Javaslang & 3/3 & \ParClassParMeth{}\\%
-        Medium & Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%
-        Medium & \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
-        Long & \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
-        Long & \Comment{Jankotek }MapDB & 1/1 & \ParClassParMeth{}\\%
+%%      Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 & \ParClassSeqMeth{}\\%
+%%      Medium & \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%
+%%      Long & \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
+%%      Medium & \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
+%%      Medium & Javaslang & 3/3 & \ParClassParMeth{}\\%
+%%      Medium & Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%
+%%      Medium & \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
+%%      Long & \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
+%%      Long & \Comment{Jankotek }MapDB & 1/1 & \ParClassParMeth{}\\%
+        Medium & Californium & 2/20 & C2\\%
+        Medium & Chaos & 1/1 & C2\\%
+        Long & \Comment{apache} Flink & 66/74 & FC0\\%
+        Long & \Comment{apache logging-}Log4J2 & 25/28 & FC0\\%
+        Long & \Comment{javaslang }Javaslang & 3/3 & C3\\%
+        Medium & Jcabi \Comment{jcabi-github} & 1/1 & C3\\%
+        Long & \Comment{hazelcast hazelcast-}Jet & 6/7 & FC0\\%
+        Long & \Comment{apache} Mahout & 8/9 & FC0\\%
+        Long & \Comment{jankotek} MapDB & 1/1 & C3\\%
+        Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
+        Medium & \Comment{yegor256} Rultor & 1/1 & C3\\%
+        Medium & \Comment{yegor256} Takes & 1/1 & C3\\%
+        Long & \Comment{vavr-io} Vavr & 3/3 & C3\\%
         \bottomrule%
@@
 modules that do not use the configuration cited use the sequential
-configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
+configuration \Seq{}.  For example, three modules (=28-25) from Log4J2
 use sequential configuration.
@@
 test modules.
-%\begin{figure}[h!]
-%    \centering
-%    \includegraphics[width=0.32\textwidth]{results/barplot-modes-dynamic.pdf}
-%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
-%    caption}Distribution of parallel modes identified dynamically in a
-%    subset of \numProjectsPar{} projects.  A project may have support
-%    to more than one parallel mode. Also, a project may run only a
-%    subset tests in parallel by default.}
-%\end{figure}
-
-%% Recall that some projects can use parallel execution that is only
-%% activated when developers pass certain parameters to the build
-%% process. For instance, it is possible to create in Maven multiple
-%% configurations in the same build file and select dynamically which one
-%% should be used.
 
@@
 the dynamic checking, previously presented.
-
-Overall, we found, using this methodology, ten projects that use
-parallelism.  Compared to the set of projects listed in
-Table~\ref{tab:speedup}, we found two new projects, namely:
+Overall, we found, using this methodology, \numProjectsParStatic{}
+projects that use parallelism.
+Compared to the set of projects listed in
+Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
 \CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
-configuration C3) and \CodeIn{Mapstruct} (using configuration
-\ForkSeq{}).  Curiously, we also found that project \CodeIn{Jcabi} was
-not detected using this methodology.  That happened because this
-project loads its \emph{pom.xml} file from a jar file that we did not
-check.  Considering the static and dynamic methods together, we found
-a total of 11 distinct projects using parallelism, corresponding to
-the union of the two subject sets.
+configuration C3), \CodeIn{Mapstruct} (using configuration
+\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
+\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
+Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
+and \CodeIn{Takes} were not detected using this methodology.
+That happened because these projects loaded a \emph{pom.xml} file from
+a jar file that we did not check.  Considering the static and dynamic
+methods together, we found a total of \numProjectsParTotal{} distinct
+projects using parallelism, corresponding to the union of the two
+subject sets.
 
@@
     suite parallelization is underused.  Overall, only
-        \percentParallel{} of costly projects (11 out of \numMedLong)
+    \percentParallel{} of costly projects (\numProjectsParTotal{} out of \numMedLong)
     use parallelism.}

### 2017-09-04 paper/evaluation.tex
Using macro
Removed outdated comments
Added some new lines

@@
 \CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
-configuration C3), \CodeIn{Mapstruct} (using configuration
+configuration \ParClassParMeth), \CodeIn{Mapstruct} (using configuration
 \ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
@@
 \vspace{1ex}
-
-%False positive can happen because of comments, for instance.  
-%To eliminate the cases of false positives and also to categorize 
-%true positive cases, we complemented the initial mining step with a 
-%manual inspection of files.
-%% settings); the second step (inspection) consists in a manual
-%% inspection to confirm the presence of parallelism settings in the
-%% build file and classify them according to the parallelism level.
-%% Figure \Fix{removed} describes the discovery step: we list the paths
-%% of all build files and filter only the files that contain any of the
-
-%% Figure~\ref{tab:inspection-table} summarizes our results.
-%% \Fix{The first column indicates the group of projects according to
-%% their time cost.  The second column indicates the number of build
-%% files per group.  The last column indicates the ratio of projects with
-%% parallelization settings.  From the \numMedLong{} subjects, we found
-%% \pomMedLong{} \pomf{} files.  The \numPomMatched{} configurations are
-%% distributed across \numProjectsPar{} projects from our sample.}
-
-%% % \emph{From these results we found that $\sim$51\% of medium and
-%% % long-running projects do not use parallel features to run test
-%% % suites.}\Mar{please make it consistent with research
-%% % question}\Mar{explain this is over(under)-estimated...}
-%% \begin{figure}[ht!]
-%%     \centering
-%%     \resizebox{.48\textwidth}{!}{%
-%%     \begin{tabular}{llcl}
-%%         \toprule
-%%         Group & Subject & \# of modules & Mode\\%
-%%         \midrule%
-%%         Long   &JenkinsCI Gerrit Trigger Plugin& 1 & \ForkSeq\\%
-%%         Medium &Bouncestorage Chaos Http Proxy & 1 & C2\\%
-%%         Medium &Javaslang & 1 & C3\\%
-%%         Medium &Apache Flink & 1 &\ForkSeq\\%
-%%         Medium &Apache Logging Log4J2 & 3 & \ForkSeq{}\\%
-%%         Medium &Google Cloud Platform DataflowJavaSDK & 1 & C3\\%
-%%         Medium &Hazelcast Jet & 1 & \ForkSeq\\%
-%%         Medium &Jankotek MapDB & 1 & C3\\%
-%%         Medium &Mapstruct & 1 & \ForkSeq\\%
-%%         Medium &Spotify Helios & 3 & \ForkSeq\\%
-%%         \bottomrule%
-%%     \end{tabular}}
-%%     \caption{Subjects with parallelization configurations in build files.}
-%%     \label{tab:inspection-table}
-%% \end{figure}
-
-%% \begin{figure}[ht!]
-%%     \centering
-%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
-%%         \toprule
-%%         \multirow{2}{*}{Group} %1st row, 1st cell
-%%             & \multirow{2}{*}{\# \pomf{}}
-%% 	    & \# \pomf{} matched\\
-%%         % 2nd row - empty cell
-%%             & % empty cell
-%%             & / total\\%
-%%         \midrule%
-%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
-%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
-%%         \midrule%
-%%         Total % last row, first cell
-%%             & \pomMedLong{}
-%%             & \numProjectsPar{} / \numMedLong{}\\%
-%%         \bottomrule%
-%%     \end{tabular*}
-%%     \caption{Presence of parallelization settings in build files: the
-%%     first column indicates the group of projects according to their
-%%     time cost; the second column is the subset of files with parallelization
-%%     keywords; the last column indicates the ratio of projects with
-%%     parallelism support.}
-%%     \label{tab:inspection-table} 
-%% \end{figure}
-%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
-%% identified above, we investigated further the \numPomMatched{}
-%% build files with parallel settings.  We analyzed the support and
-%% distribution of parallel modes from this subset of projects. To
-%% calculate the distribution of parallel modes, we considered only the
-%% presence of the mode in at least one of the project settings.  Recall
-%% that a build file may contain more than one parallel setting and a
-%% project may contain several sub-modules with build files.  In case the
-%% value of a parallel option is resolved dynamically (\eg, via
-%% command-line argument or system variable) we compute all modes related
-%% to the option. For instance, depending on the value, the
-%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
-%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
-%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
-%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
-%% \Fix{Missing conclusion: Fork the most used configuration}
-%% \begin{figure}[h!]
-%%     \centering
-%%     \includegraphics[width=0.32\textwidth]{results/barplot-modes-static.pdf}
-%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
-%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
-%%     identified statically in a subset of \numProjectsPar{} projects.
-%%     A project may have support to more than one parallel mode.}
-%% \end{figure}
 
@@
 \midrule%
-Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
-    \cellcolor{lightgray}1.01x\\%
+Medium & Californium & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
+Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.01x\\%
 Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
-Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
-Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
+Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
 Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
-Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
-    \cellcolor{lightgray}9.2x\\%
-Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
-Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
+Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & \cellcolor{lightgray}9.2x\\%
+Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
+Long & \Comment{apache} Mahout & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
 Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
+Medium & \Comment{apache} OpenNLP & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
+Medium & \Comment{yegor256} Rultor & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
+Medium & \Comment{yegor256} Takes & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
+Long & \Comment{vavr-io} Vavr & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
 \midrule

### 2017-09-04 paper/evaluation.tex
Updated RQ3

@@
 \midrule%
-Medium & Californium & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
-Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.01x\\%
+Medium & Californium & 1.45m & 1.40m & 1.04x\\%
+Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
 Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
 Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
-Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
-Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & \cellcolor{lightgray}9.2x\\%
+Medium &Javaslang& 2.18m & 1.82m & 1.20x\\%
+Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & 9.20x\\%
 Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
-Long & \Comment{apache} Mahout & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
+Long & \Comment{apache} Mahout & 27.38m & 18.15m & 1.51x\\%
 Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
-Medium & \Comment{apache} OpenNLP & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
-Medium & \Comment{yegor256} Rultor & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
-Medium & \Comment{yegor256} Takes & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
-Long & \Comment{vavr-io} Vavr & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
+Medium & \Comment{apache} OpenNLP & 1.30m & 0.55m & 2.36x\\%
+Medium & \Comment{yegor256} Rultor & 2.30m & 0.27m & 8.52x\\%
+Medium & \Comment{yegor256} Takes & 2.00m & 0.19m & \cellcolor{lightgray}10.53x\\%
+Long & \Comment{vavr-io} Vavr & 3.26m & 2.25m & 1.45x\\%
 \midrule
@@
 \avgSpeedup{} times faster compared to sequential execution.  Three
-cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
+cases worth special attention: \CodeIn{Chaos}, \CodeIn{Takes} and
 \CodeIn{Log4J2}.  No significant speedup was observed in
@@
 speedup cannot be obtained as the cost of the single expensive test
-class cannot be broken down with the selected configuration.  Although
-project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
+class cannot be broken down with the selected configuration. \Fix{Although
+project \CodeIn{Takes} also uses configuration \ParClassParMeth{},
 results obtained are very different compared to \CodeIn{Chaos}.  The
@@
 As result, the CPUs available for testing are kept occupied for the
-most part during test execution.  Finally, we note that parallel
+most part during test execution.} Finally, we note that parallel
 execution in \CodeIn{Log4J2} was ineffective.  We found that Maven

### 2017-09-05 paper/evaluation.tex
Pass on RQ5

@@
 data and generate plots.  All source artifacts are publicly available
-for replication (on our website~\cite{ourwebpage})\Comment{ at \Fix{create gh-pages}}.  This
+for replication (on our website~\cite{ourwebpage}).  This
 includes supporting scripts (\eg, the script that test subjects and
@@
 speedup cannot be obtained as the cost of the single expensive test
-class cannot be broken down with the selected configuration. \Fix{Although
-project \CodeIn{Takes} also uses configuration \ParClassParMeth{},
-results obtained are very different compared to \CodeIn{Chaos}.  The
-speedup observed in \CodeIn{Jcabi} was the highest amongst all
-projects.  This project contains test classes with a small number of
-test methods and several methods in those classes are time-consuming.
+class cannot be broken down with the selected configuration.
+\Jbc{
+On the other hand, the speedup observed in project \CodeIn{Takes} was
+the highest amongst all projects. This subject uses configuration
+\ParClassParMeth{} and contains 419 test methods distributed nearly
+equally among 148 test classes with a small number of test methods.
+Furthermore, several methods in those classes are time-consuming.
 As result, the CPUs available for testing are kept occupied for the
-most part during test execution.} Finally, we note that parallel
-execution in \CodeIn{Log4J2} was ineffective.  We found that Maven
-invokes several test modules in this project but the test modules that
-dominate execution time run sequentially by default.
+most part during test execution.}
+Finally, we note that parallel execution in \CodeIn{Log4J2} was
+ineffective.  We found that Maven invokes several test modules in this
+project but the test modules that dominate execution time run
+sequentially by default.
 
@@
       machine setup we used, the average speedup observed with default
-      configurations of parallelization was \avgSpeedup{}x.}
+      configurations of parallelization was \avgSpeedup{}x.
+      \Jbc{The design of the test suite impacts the speedup obtained
+      in a given parallel configuration.}
+      }
   \end{minipage}

### 2017-09-06 paper/evaluation.tex
Removed a comment
Minor fixes from past review

@@
 \SubjectsGithubNotMaven{} projects were not Maven or did not have a
-\pomf{} in the root directory and \SubjectsGithubNotTestable{}
-projects were unable to test due to incompatible environment (\eg,
-missing required web browser or database management system).
+\pomf{} in the root directory, and we were unable to test
+\SubjectsGithubNotTestable{} projects  due to incompatible environment
+(\eg, missing required web browser or database management system).
 In addition, we identified \SubjectsGithubFlaky{} projects with
-non-deterministic test results.
-In general, a test that either pass or fail under the same circumstances
-is known as a ``flaky test''~\cite{luo-etal-fse2014}.
+``flaky tests''~\cite{luo-etal-fse2014}.
+In general, a ``flaky test'' is a test that either pass or fail under
+the same circumstances leading to non-deterministic results.
 \Comment{While there are several causes that may introduce randomness on test
@@
   \centering
-  \includegraphics[width=0.25\textwidth]{results/piechart-subjs.pdf}
+  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
   \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
@@
   \SubjectsGithubNotMaven{} projects without Maven support,
-  \SubjectsGithubNotTestable{} projects unable to test,
+  \SubjectsGithubNotTestable{} with missing dependencies,
   \SubjectsGithubFlaky{} projects with flaky tests, and
@@
 threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
-(64-bit version).  Software settings include \Comment{the Linux
-  \emph{sysstat} package to measure performance, }git to fetch
-subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
-Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to process the
-data and generate plots.  All source artifacts are publicly available
-for replication (on our website~\cite{ourwebpage}).  This
-includes supporting scripts (\eg, the script that test subjects and
-generates raw analysis data) and the full list of projects. \Comment{,
-  and a \emph{Vagrantfile} to emulate our hardware and all software
-  dependencies.}
+(64-bit version).  Software settings include Git, Java 8, and Maven
+3.3.9.
+We used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to
+process test results and generate plots.  All source artifacts are
+publicly available for replication on our website~\cite{ourwebpage}.
+This includes supporting scripts (\eg, the script that test subjects
+and generates raw analysis data) and the full list of projects.
+\Comment{, and a \emph{Vagrantfile} to emulate our hardware and all
+software dependencies.}
 
@@
 We took the following actions to isolate our environment from
-measurement noise.  First, we observed that some test tasks called
-test-unrelated tasks (\eg, \emph{javadoc} generation and static
-analyses) that could interfere in our time measurements.  To address
-that potential issue, we inspected Maven execution logs from a sample
-including a hundred projects prior to running the script from
-Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
-execution (lines 1-4).  Furthermore, to avoid noise from operating
-system events, we configured our workstation to run only essential
-services.  The machine was dedicated to our experiments and we
+measurement noise.
+First, we observed that some test tasks called test-unrelated tasks
+(\eg, \emph{javadoc} generation and static analyses) that could
+interfere in our time measurements.
+To address that potential issue, we inspected Maven execution logs
+from a sample including a hundred projects prior to running the script
+from Figure~\ref{fig:mvn-execution}.
+The tasks we found were ignored from execution (lines 1-4).
+Furthermore, to avoid noise from unrelated OS events, we configured
+our workstation to only run essential services.
+The machine was dedicated to our experiments and we
 accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
@@
 group), and tests that run in five or more minutes (\longg{}
-group). We followed a similar methodology to group projects by time as
+group).
+\Comment{We followed a similar methodology to group projects by time as
 Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
-regression test selection.\Comment{ and added the \medg{} group due to
-  the variability of the time cost from subjects out of the \shortg{}
-  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
+regression test selection.}
+\Comment{ and added the \medg{} group due to the variability of the
+time cost from subjects out of the \shortg{} group}
+Figure~\ref{fig:rq1-barplot} shows the number of projects in
 each group.  As expected, \longg{} and \medg{} projects do not occur
@@
 
-Figure~\ref{fig:rq1-boxplot} shows cost distribution of test suites in
-each group as boxplots.  Note that the y-ranges are different.  The
-distribution associated with the \shortg{} group is the most
+Figure~\ref{fig:rq1-boxplot} shows as boxplots distribution of cost of
+test suites in each group.
+Note that the y-ranges are different.
+The distribution associated with the \shortg{} group is the most
 unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
-  group}.  The test suites in this group ran in 15 or less seconds for
+group}.
+The test suites in this group ran in 15 or less seconds for
 over 75\% of the cases.  Such scenarios constitute the majority of the
@@
 however, we found many costly executions.  Nearly 75\% of the projects
-from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
-the projects from the \longg{} group take $\sim$20 minutes to run.  We
+from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
+the projects from the \longg{} group took $\sim$20 minutes to run.  We
 found cases in the \longg{} group were execution takes over 50 minutes
@@
 runs all unit tests in a few seconds.  According to our criteria, this
-project is to be classified as \shortg{} but a closer look reveals
+project is classified as \shortg{} but a closer look reveals
 that only smoke tests are run by default in this project.
@@
       open-source projects.  We found that \percentMedLongRunning{} of
-      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
+      the \numSubjs{} projects we analyzed (\ie{}, nearly 1 in every 4
       projects) take at least 1 minute to run and
@@
 less than 0.5s to run, one of which takes nearly 3s to run, two of
-which take nearly 11s to run, four which takes in average 3m to run, and two of
+which take nearly 11s to run, four of which takes on average 3m to run, and two of
 which take $\sim$8m to run.  For this project, 98.4\% of the
@@
 times are similar for \medg{} and \longg{}-running test suites.
-The difference in overall running times of projects in those groups
-is mainly justified by the number of test cases as opposed to the
-individual costs of test cases.
+The difference in overall running times is mainly justified by the
+number of test cases as opposed to the individual costs of test cases.
 Figure~\ref{fig:size-testsuites} shows the difference in the
@@
       configurations of parallelization was \avgSpeedup{}x.
-      \Jbc{The design of the test suite impacts the speedup obtained
-      in a given parallel configuration.}
       }

### 2017-09-06 paper/related.tex

@@
 \label{sec:related}
-Researchers and practitioners have been shedding light to the to the
-demand of techniques for optimizing test execution. For instance, a
-recent paper from the automotive industry reported that test suites
-can take days to run~\cite{artl-etal-icst2015}.  There are different
-aspects to consider when dealing with the challenge of reducing
-test cost.
+Researchers and practitioners have been shedding light to the demand
+of techniques for optimizing test execution.
 
-\textit{Test Selection vs. Parallelism:}
+%% For instance, a recent paper from the automotive industry reported
+%% that test suites can take days to run~\cite{artl-etal-icst2015}.
+%% There are different aspects to consider when dealing with the
+%% challenge of reducing test cost.
+
+\textit{Test Selection:}
 Research has focused mostly on test suite minimization,
@@
 
-\Jbc{
-\textit{Usage of massively parallel hardware:}
-Previous research investigated the feasibility of testing embedded
-software on Graphics Processing Units (GPUs) as an alternative
-to multicore CPUs~\cite{rajan-etal-ase2014}.
-The Simple Instruction Multiple Data (SIMD) architecture of
-modern GPUs allows running the same test case with different test data
-over several threads.
-Although benchmarks indicate far superior performance over traditional
-multicore CPUs, existing GPU programming-models (\eg,
-CUDA~\cite{cuda}, and OpenCL~\cite{opencl}) are compatible only with a
-subset of the C/C++ language.
-Recent work proposed a compiler-assisted approach to make programs
-compatible with the relying programming
-model~\cite{yaneva-etal-issta2017}; however, }\Jbc{...Justify they are out
-of scope for our subjects...}.
+%% \textit{Usage of massively parallel hardware:}
+\textit{Hardware level parallelization:} Previous research
+investigated the feasibility of testing embedded software on Graphics
+Processing Units (GPUs) as an alternative to multicore
+CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
+(SIMD) architecture of modern GPUs allows running the same test case
+with different test data over several threads.  Although benchmarks
+indicate far superior performance over traditional multicore CPUs.
+%% , existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
+%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
+%% language.
+Recent work proposed a compiler-assisted approach to make
+programs compatible with the relying programming
+model~\cite{yaneva-etal-issta2017};
+
+\Jbc{...Justify they are out of scope for our subjects...}.
 

### 2017-09-06 paper/related.tex
pass on related work

@@
 
-\textit{Test Selection:}
-Research has focused mostly on test suite minimization,
-prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
-Most of these techniques are unsound (\ie{}, they do not guarantee
-that fault-revealing tests will be selected), however, more recently,
-sound techniques have been
-proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
-example, to soundly select tests for execution,
-Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
-computes which tests have been impacted by changes.  A test is
+\textit{Test Selection:} Research has focused mostly on test suite
+minimization, prioritization, reduction, and
+selection~\cite{yoo-harman-stvr2012}.  \Fix{...} Most of these
+techniques are unsound (\ie{}, they do not guarantee that
+fault-revealing tests will be selected), however, more recently, sound
+techniques have been
+proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}. Recent work
+for test selection introduced
+Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} that conservatively
+computes which tests have been impacted by file changes.  A test is
 discarded for execution if it does not depend on any changed file
@@
 regression test selection, it highlights the importance of parallelism
-as a complement to test selection.  In fact, as in their evaluation, we
-also discovered subjects with parallelism enabled by default.  Test
+as a complement to test selection.  In fact, as in their evaluation,
+we also discovered subjects with parallelism enabled by default.  Test
 suite parallelization is complementary to regression testing
@@
 with different test data over several threads.  Although benchmarks
-indicate far superior performance over traditional multicore CPUs.
-%% , existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
+indicate far superior performance over traditional multicore CPUs,
+there are severe limitations. Control-flow branching in source code
+can impact performance negatively while violating the lock-step
+execution during the divergence of instructions~\cite{rajan-etal-ase2017}
+%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
 %% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
@@
 programs compatible with the relying programming
-model~\cite{yaneva-etal-issta2017};
+model~\cite{yaneva-etal-issta2017}.
 
@@
 
-\Jbc{Missing work about testing in the cloud and Jon Bell}
+\textit{Cloud based build tools:}
+
+%% \Jbc{Missing work about testing in the cloud and Jon Bell}
 

### 2017-09-07 paper/related.tex
pass on related work

@@
 selection~\cite{yoo-harman-stvr2012}.  \Fix{...} Most of these
-techniques are unsound (\ie{}, they do not guarantee that
+techniques are unsoud (\ie{}, they do not guarantee that
 fault-revealing tests will be selected), however, more recently, sound
@@
 can impact performance negatively while violating the lock-step
-execution during the divergence of instructions~\cite{rajan-etal-ase2017}
+execution during the divergence of instructions~\cite{rajan-etal-ase2014}
 %% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
@@
 %% language.
-Recent work proposed a compiler-assisted approach to make
-programs compatible with the relying programming
-model~\cite{yaneva-etal-issta2017}.
+Recent work proposed a compiler-assisted approach to make programs
+compatible with the relying programming-model used by
+GPUs to parallelize tests~\cite{yaneva-etal-issta2017}.
 
@@
 
-\textit{Cloud based build tools:}
+\textit{Continuous integration services:}
+Recent work showed us that Continuous Integration Services are widely
+used and improve the productivity~\Fix{ref ref ref}.
 

### 2017-09-07 paper/related.tex
pass on related work

@@
 %% \textit{Usage of massively parallel hardware:}
-\textit{Hardware level parallelization:} Previous research
+\textit{Hardware level massive parallelization:} Previous research
 investigated the feasibility of testing embedded software on Graphics
@@
 GPUs to parallelize tests~\cite{yaneva-etal-issta2017}.
-
 \Jbc{...Justify they are out of scope for our subjects...}.

### 2017-09-07 paper/related.tex
pass on related work

@@
 
-\textit{Test Selection:} Research has focused mostly on test suite
+\textit{Test selection:} Research has focused mostly on test suite
 minimization, prioritization, reduction, and
@@
 as a complement to test selection.  In fact, as in their evaluation,
-we also discovered subjects with parallelism enabled by default.  Test
-suite parallelization is complementary to regression testing
+we also discovered subjects with parallelism enabled by default.
+Test suite parallelization is complementary to regression testing
 techniques.
+\Luis{maybe we should create another division for test acceleration}
+Bell et al.\Fix{ref} introduced ElectricTest, a tool for detecting
+data dependencies between real world tests. A technique was introduced
+to observe global resources read and write between tests, instead of
+executing every possible permutation of all tests to detect data
+dependencies. Dependency detection can be combined with test suite
+parallelization to efficiently accelerate test execution.
 

### 2017-09-08 paper/related.tex
pass

--- 2017-09-07 paper/related.tex
@@
 \label{sec:related}
-Researchers and practitioners have been shedding light to the demand
-of techniques for optimizing test execution.
+We discuss most related work in the following.
+%% Researchers and practitioners have been shedding light to the demand
+%% of techniques for optimizing test execution.
 
@@
 
-\textit{Test Selection:} Research has focused mostly on test suite
-minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  \Fix{...} Most of these
+%\textit{Test selection:}
+Regression testing research has focused
+mostly on test suite minimization, prioritization, reduction, and
+selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
 techniques are unsoud (\ie{}, they do not guarantee that
-fault-revealing tests will be selected), however, more recently, sound
-techniques have been
-proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}. Recent work
-for test selection introduced
-Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} that conservatively
-computes which tests have been impacted by file changes.  A test is
-discarded for execution if it does not depend on any changed file
-dynamically reachable from execution. Although Ekstazi is focused on
-regression test selection, it highlights the importance of parallelism
-as a complement to test selection.  In fact, as in their evaluation,
-we also discovered subjects with parallelism enabled by default.  Test
-suite parallelization is complementary to regression testing
-techniques.
+fault-revealing tests will be considered for testing).  The test
+selection technique Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015}
+is an example of a sound regression testing technique. It
+conservatively computes which tests have been impacted by file
+changes.  A test is discarded for execution if it does not depend on
+any changed file dynamically reachable from execution.\Comment{ Curiously
+Ekstazi's evaluation discovered subjects with parallelism enabled by
+default.} \c{C}elik~\etal{}~\cite{celik-etal-fse2017} recently extended
+Ekstazi to track files accessed outside JVM boundaries.  Important to
+note that regression testing techniques, including test selection, is
+complementary to test suite parallelization.
+
+%\Luis{maybe we should create another division for test acceleration}
+
+ElectricTest~\cite{bell-etal-esecfse2015} is a tool for efficiently
+detecting data dependencies across test cases.  Dependency tracking is
+important as to avoid test flakiness when parallelizing test
+suites. ElectricTest observes reads and writes on global resources
+made by tests to identify these dependencies at low cost. We remain to
+investigate the impact of ElectricTest to reduce flakiness in
+unrestricted test suite parallelization.
 
 %% \textit{Usage of massively parallel hardware:}
-\textit{Hardware level parallelization:} Previous research
-investigated the feasibility of testing embedded software on Graphics
-Processing Units (GPUs) as an alternative to multicore
-CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
-(SIMD) architecture of modern GPUs allows running the same test case
-with different test data over several threads.  Although benchmarks
-indicate far superior performance over traditional multicore CPUs,
-there are severe limitations. Control-flow branching in source code
-can impact performance negatively while violating the lock-step
-execution during the divergence of instructions~\cite{rajan-etal-ase2014}
+%\textit{Hardware level massive parallelization:}
+
+The use of the Simple Instruction Multiple Data (SIMD) design has been
+previoulsy explored to accelerate test
+execution~\cite{damorim-etal-issta2007,damorim-etal-tse2008,kim-etal-issre2012,nguyen-etal-icse2014,rajan-etal-ase2014,sen-etal-fse2015,yaneva-etal-issta2017}. The
+SIMD architecture, as implemented in modern GPUs for instance, allows
+the execution of a given instruction simultaneously against multiple
+data.  For that reason, in principle, a test could be ran
+simulteneously against multiple inputs.  Recent
+work~\cite{rajan-etal-ase2014,yaneva-etal-issta2017} explored the
+feasibility of testing embedded software using GPUs.  Although
+benchmarks indicate superior performance compared to traditional
+multicore CPUs, the use of the technology in broader settings is
+unfortunately limited. For example, execution of more general programs
+can violate SIMD's lock-step assumption on the control-flow of threads
+affecting negatively performance. In contrast to the datasets used in
+those papers, often each test is associated with a single input
+(instead of many).  Furthermore, handling complex data is challenging
+in SIMD~\cite{damorim-etal-issta2007,damorim-etal-tse2008}.
+
 %% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
@@
 %% language.
-Recent work proposed a compiler-assisted approach to make programs
-compatible with the relying programming-model used by
-GPUs to parallelize tests~\cite{yaneva-etal-issta2017}.
+%% Recent work proposed a compiler-assisted approach to make programs
+%% compatible with the relying programming-model used by
+%% GPUs to parallelize tests~\cite{}.
+%% \Jbc{...Justify they are out of scope for our subjects...}.
 
-\Jbc{...Justify they are out of scope for our subjects...}.
+\Mar{can you complete this AND add text on high-level paralellism?}
 

### 2017-09-08 paper/related.tex
pass on related work

--- 2017-09-07 paper/related.tex
@@
 Recent work showed us that Continuous Integration Services are widely
-used and improve the productivity~\Fix{ref ref ref}.
+used and improve the productivity~\cite{hilton-etal-ase2016}.
 

### 2017-09-08 paper/related.tex
pass on related work

--- 2017-09-08 paper/related.tex
@@
 
-%\textit{Test selection:}
-Regression testing research has focused
-mostly on test suite minimization, prioritization, reduction, and
+%ekstazi-web,
+Regression testing research has focused mostly on test suite
+minimization, prioritization, reduction, and
 selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
@@
 fault-revealing tests will be considered for testing).  The test
-selection technique Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015}
-is an example of a sound regression testing technique. It
-conservatively computes which tests have been impacted by file
-changes.  A test is discarded for execution if it does not depend on
-any changed file dynamically reachable from execution.\Comment{ Curiously
-Ekstazi's evaluation discovered subjects with parallelism enabled by
-default.} \c{C}elik~\etal{}~\cite{celik-etal-fse2017} recently extended
-Ekstazi to track files accessed outside JVM boundaries.  Important to
-note that regression testing techniques, including test selection, is
-complementary to test suite parallelization.
+selection technique
+Ekstazi~\cite{gligoric-etal-issta2015,celik-etal-fse2017} is an
+example of a sound regression testing technique. It conservatively
+computes which tests have been impacted by file changes.  A test is
+discarded for execution if it does not depend on any changed file
+dynamically reachable from execution.\Comment{ Curiously Ekstazi's
+  evaluation discovered subjects with parallelism enabled by
+  default.}\Comment{ \c{C}elik~\etal{}~\cite{} recently extended
+  Ekstazi to track files accessed outside JVM boundaries.} Important
+to note that regression testing techniques, including test selection,
+is complementary to test suite parallelization.
 
@@
 
-The use of the Simple Instruction Multiple Data (SIMD) design has been
-previoulsy explored to accelerate test
+The use of the Single Instruction Multiple Data (SIMD) design has been
+previoulsy explored in research to accelerate test
 execution~\cite{damorim-etal-issta2007,damorim-etal-tse2008,kim-etal-issre2012,nguyen-etal-icse2014,rajan-etal-ase2014,sen-etal-fse2015,yaneva-etal-issta2017}. The
-SIMD architecture, as implemented in modern GPUs for instance, allows
+SIMD architecture, as implemented in modern GPUs, for instance, allows
 the execution of a given instruction simultaneously against multiple
-data.  For that reason, in principle, a test could be ran
-simulteneously against multiple inputs.  Recent
-work~\cite{rajan-etal-ase2014,yaneva-etal-issta2017} explored the
-feasibility of testing embedded software using GPUs.  Although
-benchmarks indicate superior performance compared to traditional
-multicore CPUs, the use of the technology in broader settings is
-unfortunately limited. For example, execution of more general programs
-can violate SIMD's lock-step assumption on the control-flow of threads
-affecting negatively performance. In contrast to the datasets used in
-those papers, often each test is associated with a single input
-(instead of many).  Furthermore, handling complex data is challenging
-in SIMD~\cite{damorim-etal-issta2007,damorim-etal-tse2008}.
+data.  For that reason, in principle, one test could be ran
+simulteneously against multiple inputs provided that multiple test
+inputs exist associated to that one test.  Recent
+work~\cite{rajan-etal-ase2014,yaneva-etal-issta2017} explored that
+idea to speedup test execution of embedded software using graphic
+cards. Although benchmarks indicate superior performance compared to
+traditional multicore CPUs, the use of the technology in broader
+settings is limited. For example, execution of more general programs
+can violate the SIMD's lock-step assumption on the control-flow of
+threads.  This violation would affect negatively performance.
+Furthermore, handling complex data is challenging in
+SIMD~\cite{damorim-etal-issta2007,damorim-etal-tse2008}.  The approach
+is promising when multiple input vectors exist for each test and the
+testing code heavily manipulates scalar data types.  The datasets used
+in those papers satisfied those constraints.
 

### 2017-09-08 paper/related.tex
pass on related work

--- 2017-09-08 paper/related.tex
@@
 
-\textit{Continuous integration services:}
-Recent work showed us that Continuous Integration Services are widely
-used and improve the productivity~\cite{hilton-etal-ase2016}.
+Continuous Integration Services are widely used by the open-source
+community~\cite{hilton-etal-ase2016,vasilescu-etal-fse2015}. Travis
+CI~\cite{travis} is an example of one of these services. Recent work
+by Hilton~\etal{}~\cite{hilton-etal-ase2016} showed that there is a
+high acceptance rate for CI services. The average build time for those
+projects using CI is under $\sim$8.3 min~\cite{hilton-etal-ase2016}.
 

### 2017-09-08 paper/evaluation.tex

@@
 
-%% Table header macros
-% $\Uparrow_\text{speed}$
-\newcommand{\subcolA}{$\text{speedup}$}
-\newcommand{\subcolB}{$\%_\text{fail}$}
-\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
-\newcommand{\blankentry}{\entry{-}{-}}
-\newcommand{\subcol}{\subcolA{} & \subcolB{}}
-\newcommand{\entry}[2]{#1 & #2}
-
-\begin{table*}[t]
-\centering
-\small
-\setlength{\tabcolsep}{2pt}
-\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
-\toprule
-\multirow{2}{*}{\emph{Subject}} & \multicolumn{2}{c|}{\emph{\Seq}} &
-    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
-    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
-    \colheader{\ForkParMeth} \\ %\cline{2-12}
-    & $T$ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
-    & \subcol{}\\%
-\midrule%
-AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{1.85x}{0.23\%} & \entry{3.36x}{3.1\%}\\%
-
-Facebook Linkbench   & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{1.54x}{0\%} & \entry{1.59x}{0\%}\\%
-
-GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{0.80x}{1.70\%} & \entry{0.80x}{1.70\%}\\%
-
-Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{1.38x}{0\%} & \entry{1.57x}{0\%}\\ 
-Jcabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{2.00x}{0\%} & \entry{2.89x}{0\%} \\%
-JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{2.77x}{0\%} & \entry{9.00x}{0\%}\\%
-MapDB  & \entry{8.2m}{5,324}  & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{1.71x}{0.98\%} & \entry{3.42x}{0.98\%}\\%
-Moquette                      & \entry{3.7m}{169} & \entry{4.62x}{65.64\%} & \entry{3.36x}{32.92\%} & \entry{12.33x}{77.78\%} & \entry{2.47x}{22.53\%} & \entry{9.25x}{69.44\%} \\
-RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\
-Stripe Java                   & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{2.69x}{0\%} & \entry{8.60x}{11.63\%}\\%
-
-\midrule
-
-\textbf{Average}   & \entry{30.3m}{2,897.6} & \entry{2.40x}{7.59\%} & \entry{4.10x}{4.51\%} & \entry{9.45x}{10.32\%} & \entry{1.86x}{2.54\%} & \entry{4.19x}{8.68\%} \\%
-
-%%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%
-%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
-%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
-%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
-%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
-
-%% OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
-%% Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
-%% Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
-%% Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
-%% Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
-%% Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
-%% AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
-
-%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
-
-\bottomrule%
-\end{tabular}
-\caption{Speedup versus Flakiness (\subcolB). Configuration
-  \emph{\Seq{}} denotes the comparison baseline, which runs tests
-  sequentially.  Columns $T$ and $N$ indicate time and number of
-  tests, respectively.  Other columns show speedup and percentage of
-  failing tests in different configurations, compared to
-  \emph{\Seq{}}.}
-\label{tab:rq6-table}
-\end{table*}
+\input{flakiness-speedup-table}
 

### 2017-09-09 paper/evaluation.tex
Incorporated some comments from @damorim

@@
 other source of flakiness.
-\Jbc{From the \SubjectsGithubConsistant{} projects with
+From the \SubjectsGithubConsistant{} projects with
 deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
 projects with more than \SuiteFailingThreshold{} of tests failing to
-reduce bias in our dataset.}
+reduce bias in our dataset.
+We ignored failing tests with JUnit's
+\CodeIn{@Ignore} annotation on the remaining projects.
 Our final set of subjects consists of \numSubjs{} projects.
@@
 only the tests executed by default.
-\Jbc{
+\Comment{
 Although failing tests may introduce noise in our measurements, we
@@
 test failures. 
+}
 From the \numSubjs{} testable projects, \numSubjsPass{} successfully
@@
 have more than 5\% of failing tests (7.3\% in average).
-}
 \vspace{1ex}
@@
 measures the distribution of test costs in test suites as to estimate
-(lack of) potential of obtaining speedups with parallelization.  In
+potential of obtaining speedups with parallelization.  In
 the limit, if cost is dominated by a single test from a large test
@@
     \end{subfigure}
-    %% \vspace{2ex}
-    %% \begin{subfigure}{0.5\textwidth}
-    %%   \centering
-    %%   \begin{tabular}{rrrr}
-    %%     \toprule
-    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
-    %%     \midrule    
-    %%     Long   &  7 & 15 & 12 \\
-    %%     Medium & 22 & 19 & 7 \\
-    %%     \bottomrule
-    %%   \end{tabular}
-    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
-    %% \end{subfigure}
     \caption{\label{fig:time-distributions}Time distributions. X-axis
@@
 
-The dimension adoption focuses on the usage of parallelism in
-open-source projects.  It evaluates (\numRQAdoptionOne) how often open-source
-projects use parallelization schemes and (\numRQAdoptionTwo) how developers
-involved in costly projects, not using parallelization, perceive this
-technology.
-
+%% Commented as we don't follow this pattern on the other RQs
+\Comment{
+Adoption concerns with the popularity of  parallelization schemes and
+(\numRQAdoptionTwo) how developers involved in costly projects, not
+using parallelization, perceive this technology.
+}
 \begin{itemize}
@@
 sampling that only bootstrapping the Maven process suffices to infer
-which parallel configuration modes it will use to actually run the
+which parallel configuration modes it uses to run the
 tests.  It is also important to point that we used the default
@@
 same configuration, we counted only one occurrence.
-Table~\ref{tab:freqmodes-dynamic} shows the projects we identified
-where parallelism is enabled by default in Maven.  Column
-``\emph{Subject}'' indicates the name of the project, column
-``\emph{\# of modules}'' indicates the fraction of modules containing
-tests that use the configuration of parallelism mentioned in column
-``\emph{Mode}''.  We note that, considering these projects, the
-modules that do not use the configuration cited use the sequential
-configuration \Seq{}.  For example, three modules (=28-25) from Log4J2
-use sequential configuration.
-
 It came as a surprise the observation that
@@
 our set of \numMedLong{} projects, we found that only
-\textbf{\numProjectsPar{}} of those projects had parallelism enabled
+\numProjectsPar{} of those projects had parallelism enabled
 by default, with only configurations \ParClassSeqMeth{},
@@
 
+Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
+we identified where parallelism is enabled by default in Maven.
+Column ``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.
+We note that, considering these projects, the modules that do not use
+the configuration cited use the sequential configuration \Seq{}.
+For example, three modules (=28-25) from Log4J2 use sequential
+configuration.
+
 \subsubsection{Static checking}
 \label{sec:rqC-2}
-Given the inherent limitation of dynamic monitoring to find evidence
-of parallelism, we also looked for indication of parallelism in build
+As our previous approach cannot detect parallelism in non-default
+configurations, we also looked for indication of parallelism in build
 files\Comment{ in the same sample set of \numMedLong{} projects}.  We
@@
 command line to enable parallelization (\eg, \CodeIn{mvn test
-  -Dparallel.type=classesAndMethods}). To handle those case, we
+  -Dparallel.type=classesAndMethods}). To handle those cases, we
 considered all possible values for the parameter (in this case,
@@
 approach is not immune to false negatives, which can occur when
-\emph{pom.xml} files are encapsulated in jar files or downloaded from
+\emph{pom.xml} files are encapsulated in jar files or files downloaded from
 the network.  Consequently, this static checking is complementary to
 the dynamic checking, previously presented.
-Overall, we found, using this methodology, \numProjectsParStatic{}
-projects that use parallelism.
+This methodology founds \numProjectsParStatic{} projects.
 Compared to the set of projects listed in
@@
 \end{enumerate}
-
 %% \begin{enumerate}
@@
 low-level test suite parallelization.
-
 % \emailsNotDescribed{} developers did not described their environment.
@@
 practical adoption of parallelization (\numRQAdoptionOne{}).
-
 %% , one runs a manually created Thread to run some
@@
 %% parallel.
-
 %% did not confirmed, however,

### 2017-09-09 paper/evaluation.tex
Removed some extra space

@@
   \numSubjs{} projects to conduct our study.}
+  \vspace{-2ex}
 \end{figure}
@@
 and generates raw analysis data) and the full list of projects.
-\Comment{, and a \emph{Vagrantfile} to emulate our hardware and all
-software dependencies.}
 
@@
 
-%% the median from the
-%% \medg{} group is nearly two minutes and most of the subjects run in
-%% less than four minutes; most of the \longg{} group runs in less than
-%% 25 minutes but has outliers that require more than 50 minutes to
-%% execute.
-
 \begin{figure}[ht]
@@
     Distribution of time cost by group.}
+    \vspace{-2ex}
 \end{figure}
-
-%% Figure~\ref{fig:rq1-barplot} is a lower bound estimation of cost
-%% because some tests may finish earlier than expected due to existing
-%% test failures in the revision we downloaded.
 
@@
 have more than 5\% of failing tests (7.3\% in average).
+\begin{center}
 \vspace{1ex}
-\begin{center}
 \fbox{
@@
 }
+\vspace{1ex}
 \end{center}
-\vspace{1ex}
 
@@
   \caption{\label{fig:time-versus-size}Relating size and time.}%
+  \vspace{-3ex}
 \end{figure}
-
-%\Mar{$\leftarrow$ show stats to indicate discrimination of
-%  two distributions}
 
@@
 
-%% however, weak in
-%% the suggesting that saving time in this group with test suite
-%% parallelization may be more challenging as relatively fewer tests
-%% dominate overall execution time.  Figure~\ref{fig:scattercost} shows
-%% these results.
-
-%% This 
-%% indication that it is more beneficial to parallelize long projects as
-%% cost is spread across many
-
+\begin{center}
 \vspace{1ex}
-\begin{center}
 \fbox{
@@
 \ForkParMeth{}.  Large projects may contain several test suites
+distributed on different Maven modules potentially using different
+configurations.  For those cases, we collected the Maven output from
+each module discarding duplicates as to avoid inflating counts for
+configuration modes that appear in several modules of the same
+project. For instance, if a project contains two modules using the
+same configuration, we counted only one occurrence.
+It came as a surprise the observation that
+no project used distinct configurations in their modules. Considering
+our set of \numMedLong{} projects, we found that only
+\numProjectsPar{} of those projects had parallelism enabled
+by default, with only configurations \ParClassSeqMeth{},
+\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
+\ParClassParMeth{} and \ForkSeq{} were the most popular among these
+cases.  Note that these results under-approximate real usage of
+parallelism as we used default parameters in our scripts to spawn the
+Maven process.  That decision could prevent execution of particular
+test modules.
 \begin{wraptable}{r}{0pt}%0.525\linewidth
   \footnotesize
-  %  \small
   \centering
   \setlength{\tabcolsep}{2.5pt}
-%    \resizebox{.48\textwidth}{!}{%
     \begin{tabular}{llcr}
@@
         \midrule%
-%%      Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 & \ParClassSeqMeth{}\\%
-%%      Medium & \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%
-%%      Long & \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
-%%      Medium & \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
-%%      Medium & Javaslang & 3/3 & \ParClassParMeth{}\\%
-%%      Medium & Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%
-%%      Medium & \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
-%%      Long & \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
-%%      Long & \Comment{Jankotek }MapDB & 1/1 & \ParClassParMeth{}\\%
         Medium & Californium & 2/20 & C2\\%
@@
     \label{tab:freqmodes-dynamic}
+    \vspace{-1ex}
 \end{wraptable}
-distributed on different Maven modules potentially using different
-configurations.  For those cases, we collected the Maven output from
-each module discarding duplicates as to avoid inflating counts for
-configuration modes that appear in several modules of the same
-project. For instance, if a project contains two modules using the
-same configuration, we counted only one occurrence.
-It came as a surprise the observation that
-no project used distinct configurations in their modules. Considering
-our set of \numMedLong{} projects, we found that only
-\numProjectsPar{} of those projects had parallelism enabled
-by default, with only configurations \ParClassSeqMeth{},
-\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
-\ParClassParMeth{} and \ForkSeq{} were the most popular among these
-cases.  Note that these results under-approximate real usage of
-parallelism as we used default parameters in our scripts to spawn the
-Maven process.  That decision could prevent execution of particular
-test modules.
-
 Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
@@
 
+\begin{center}
 \vspace{1ex}
-\begin{center}
 \fbox{
@@
 \begin{center}
+\vspace{-1ex}
 \fbox{
@@
 }
+\vspace{1ex}
 \end{center}
@@
 
-\begin{table}[h!]
+\begin{table}[ht!]
 \centering
@@
 \bottomrule%
+\vspace{-5ex}
 \end{tabular}}
@@
 %%   tiver conviccao dos 2 casos}
-
 \begin{center}
+\vspace{1ex}
 \fbox{
@@
 Tahr (64-bit version). This experiment uses configuration
-\emph{\ForkSeq{}} as the goal is to evaluate the impact on runtime of
-\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  
-  %\begin{figure}[h]
-  \centering
-  \includegraphics[width=.25\textwidth]{R/scalability/scalability.pdf}
-  \caption{\label{fig:scalability}Scalability.}
-  %\end{figure}
-%  \vspace{-1ex}    
-\end{wrapfigure}
 spawning a growing number of JVMs in different CPUs.  We selected
@@
 test cases distributed across many test classes~--~194.  Note that a
+\emph{\ForkSeq{}} as the goal is to evaluate the impact on runtime of
 test class is the smallest unit that can be used to spawn a test job
@@
 assigned to which JVM that the build system forks.
-
 Figure~\ref{fig:scalability} shows the reduction in running times as
-more CPUs contribute to the execution.  We ran this experiment for a
-growing number of cores 1, 3, ..., 39.  The plot shows results up to
-17 cores as it is clear the tendency.  We noticed that improvements
-are marginal after three cores, which is the basic setup we used in
-other experiments.  This saturation is justified by the presence of a
-single test class, \CodeIn{org.mapdb.WALTruncat}, containing 15 test
-cases that take over two minutes to run.
+more CPUs contribute to the execution.
+We ran this experiment for a growing number of cores 1, 3, ..., 39. 
+\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  \centering
+  \includegraphics[width=.25\textwidth]{R/scalability/scalability.pdf}
+  \caption{\label{fig:scalability}Scalability.}
+  \vspace{-1ex}
+\end{wrapfigure}
+The plot shows results up to 17 cores as it is clear the tendency.
+We noticed that improvements are marginal after three cores, which is
+the basic setup we used in other experiments.
+This saturation is justified by the presence of a single test class,
+\CodeIn{org.mapdb.WALTruncat}, containing 15 test cases that take over
+two minutes to run.
 
 \begin{center}
+\vspace{1ex}
 \fbox{

### 2017-09-09 paper/related.tex

--- 2017-09-08 paper/related.tex
@@
 
-\textit{Continuous integration services:}
-Recent work showed us that Continuous Integration Services are widely
-used and improve the productivity~\Fix{ref ref ref}.
+Continuous Integration Services are widely used by the open-source
+community~\cite{hilton-etal-ase2016,vasilescu-etal-fse2015}. Travis
+CI~\cite{travis} is an example of one of these services. Recent work
+by Hilton~\etal{}~\cite{hilton-etal-ase2016} showed that there is a
+high acceptance rate for CI services. The average build time for those
+projects using CI is under $\sim$8.3 min~\cite{hilton-etal-ase2016}.
 

### 2017-09-09 paper/evaluation.tex
Removed unnecessary comments
pass on eval

@@
 test method is the smallest working unit in test frameworks.
-
 %% However, avoiding
@@
 %% time and these tests are assigned to different CPUs.
-
 %% It is therefore important to
@@
 %%   and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
-
 %% For the case
@@
 
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{results/testcost-long.pdf}
-      \caption{\label{fig:longtcost}Long group.}
-    \end{subfigure}\\
-    \vspace{2ex}
-    \begin{subfigure}{0.47\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{results/testcost-medium.pdf}
-      \caption{\label{fig:medtcost}Medium group.}
-    \end{subfigure}
-    \caption{\label{fig:time-distributions}Time distributions. X-axis
-        denote projects appearing in arbitrary order.}%
-\end{figure}
-
-\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
-time distribution of individual test cases per project.  We observed
-that the average median value of execution cost for a test was
-relatively small (dashed horizontal red lines), namely 0.31s for
-\medg{} projects and 0.23s for \longg{} projects.  The standard
-deviations associated with each distribution were relatively
-low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
-  specific ranges of $\sigma$ values.}  We noted a small number of
-cases of CPU monopolization.  For example, the highest value of
-$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
-\longg{} group.  This project contains only 26 tests, 17 of which take
-less than 0.5s to run, one of which takes nearly 3s to run, two of
-which take nearly 11s to run, four of which takes on average 3m to run, and two of
-which take $\sim$8m to run.  For this project, 98.4\% of the
-execution cost is dominated by 20\% of the tests; without these
-two costly tests this project would have been classified as
-short-running.
+Figure~\ref{fig:time-distributions} shows the time distribution of
+individual test cases per project (x-axis denote projects appearing in
+arbitrary order).
+We observed that the average median value of execution cost for a
+test was relatively small (dashed horizontal red lines), namely 0.08s
+for \medg{} projects and 0.16s for \longg{} projects.
+The standard deviations associated with each distribution were
+relatively low.\Comment{ Figure~\ref{fig:sd} shows the number of
+projects within specific ranges of $\sigma$ values.}  We noted a small
+number of cases of CPU monopolization.
+For example, the highest value of $\sigma$ occurred in
+\CodeIn{uber\_chaperone}, a project from the \longg{} group.
+This project contains only 26 tests, 17 of which take less than 0.5s
+to run, one of which takes nearly 3s to run, two of which take nearly
+11s to run, four of which takes on average 3m to run, and two of which
+take $\sim$8m to run.
+For this project, 98.4\% of the execution cost is dominated by 20\% of
+the tests; without these two costly tests this project would have been
+classified as short-running.
 We did not find other projects with such extreme time monopolization
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
+  \caption{\label{fig:time-distributions}Time distributions per projects.}%
+\end{figure}
+\begin{figure}[t!]
   \centering
@@
   \end{subfigure}
-  \caption{\label{fig:time-versus-size}Relating size and time.}%
-  \vspace{-3ex}
+  \caption{\label{fig:time-versus-size}Relating size and time.
+  }%
 \end{figure}
-
 Figure~\ref{fig:time-distributions} shows that the average median
@@
 test modules.
+Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
+we identified where parallelism is enabled by default in Maven.
 \begin{wraptable}{r}{0pt}%0.525\linewidth
@@
 \end{wraptable}
-Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
-we identified where parallelism is enabled by default in Maven.
 Column ``\emph{Subject}'' indicates the name of the project, column
@@
 We ran this experiment for a growing number of cores 1, 3, ..., 39. 
+The plot shows results up to 17 cores as it is clear the tendency.
+We noticed that improvements are marginal after three cores, which is
+the basic setup we used in other experiments.
 \begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  \centering
@@
   \caption{\label{fig:scalability}Scalability.}
-  \vspace{-1ex}
 \end{wrapfigure}
-The plot shows results up to 17 cores as it is clear the tendency.
-We noticed that improvements are marginal after three cores, which is
-the basic setup we used in other experiments.
 This saturation is justified by the presence of a single test class,
@@
 \begin{center}
-\vspace{1ex}
 \fbox{
@@
 
-%% \begin{figure}[h!]
-%% \centering
-%% \resizebox{.48\textwidth}{!}{%
-%% \begin{tabular}{lcrrrrr}
-%% \toprule
-%% \emph{Subject} & \emph{\# of tests} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
-%% \midrule%
-%% Linkedin Pinot & 356 & - & - & - & - & -\\%
-%% %% Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
-%% %% Kite SDK & - & - & - & - & - & -\\%
-%% %% \Fix{!?} Apache Giraph & 327 & - & - & - & - & -\\%
-%% %% OpenMRS Core & - & - & - & - & - & -\\%
-%% %% Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
-%% %% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
-%% %%Geotools & 7701 & - & - & - & - & -\\%
-%% %%Kuromoji & 672 & - & - & - & - & -\\%
-%% %%Atomix & 99 & - & - & - & - & -\\%
-%% %%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
-%% %%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
-%% \bottomrule%
-%% \end{tabular}}
-%% \caption{\Fix{Tabela de flakiness}}
-%% \label{tab:rq6-flaky}
-%% \end{figure}
-
 %% \Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
@@
 %% a autentiticao falha}
-
-%% \Fix{Elaborate results from efficiency}
-
-%% \Fix{Elaborate results from flakiness}
-
-%% \Fix{highlight special cases}
 

### 2017-09-09 paper/evaluation.tex
Added our url and removed a useless sentence

@@
 distribution of test suite sizes across groups.  This figure indicates
-that long projects, albeit having a wider inter-quartile range (middle
-50\% projects in this group are less predictable), have a higher
-median and much higher average number of test cases.  Furthermore, we
-noted a strong positive correlation between running time and number of
-test on projects in the \longg{} group.  Considering the \medg{}
-group, the correlation between these two variables was weak.
+that long projects, have a higher median and much higher average
+number of test cases.
+Furthermore, we noted a strong positive correlation between running
+time and number of test on projects in the \longg{} group.
+Considering the \medg{} group, the correlation between these two
+variables was weak.
 Figure~\ref{fig:scattercost} illustrates this regression line.

### 2017-09-09 paper/evaluation.tex
Some cleanup

@@
 \label{sec:subjects}
-
-%% We evaluated the characteristics of test suites in open-source
-%% development from a sample set of Java projects from \github{}.  We are
-%% interested to evaluate non-trivial test suites from popular projects
-%% that are in activity.
-
-%% , which is used on
-%% \github{} to indicate appreciation of a user to a
-%% project~\cite{github-stars},
 
@@
 the same circumstances leading to non-deterministic results.
-\Comment{While there are several causes that may introduce randomness on test
-results, our concern is on flakiness caused by
-parallel execution.}
 As some of our experiments consist in running tests on different
@@
 \end{itemize}
-%\Jbc{The following steps may change $\rightarrow$}
 
@@
 \input{codes/evaluation}
+\vspace{-1ex}
 
@@
   \end{subfigure}%
-    ~
+  \hfill
   \begin{subfigure}{0.25\textwidth}
@@
   Distribution of time cost by group.}
-    \vspace{-2ex}
+  \vspace{-3ex}
 \end{figure}
@@
 %% of each test up and down, make prediction of effectiveness challenging.
-
 Figure~\ref{fig:time-distributions} shows the time distribution of
@@
 number of cases of CPU monopolization.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
+  \caption{\label{fig:time-distributions}Time distributions per projects.}%
+  \vspace{-3ex}
+\end{figure}
+
 For example, the highest value of $\sigma$ occurred in
@@
 the tests running faster.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
-  \caption{\label{fig:time-distributions}Time distributions per projects.}%
-\end{figure}
-\begin{figure}[t!]
-  \centering
-  \begin{subfigure}{0.15\textwidth}
-    \centering
-    \includegraphics[width=.85\textwidth]{results/boxplots-testcases.pdf}
-    \caption{\label{fig:size-testsuites}Size of test suites.}
-  \end{subfigure}
-  ~
-  \begin{subfigure}{0.3\textwidth}
-    \centering
-    \includegraphics[width=.95\textwidth]{results/scatter-testcost.pdf}
-    \caption{\label{fig:scattercost}Size versus running time of
-      test suites.}
-  \end{subfigure}
-  \caption{\label{fig:time-versus-size}Relating size and time.
-  }%
-\end{figure}
 Figure~\ref{fig:time-distributions} shows that the average median
@@
 number of test cases as opposed to the individual costs of test cases.
+
 Figure~\ref{fig:size-testsuites} shows the difference in the
@@
 }
-\vspace{1ex}
+\begin{figure}[h!]
+  \centering
+  \begin{subfigure}{0.13\textwidth}
+    \centering
+    \includegraphics[width=.9\textwidth]{results/boxplots-testcases.pdf}
+    \caption{\label{fig:size-testsuites}}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.28\textwidth}
+    \centering
+    \includegraphics[width=.9\textwidth]{results/scatter-testcost.pdf}
+    \caption{\label{fig:scattercost}}
+  \end{subfigure}
+  \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
+    Size versus running time of test suites.}%
+\end{figure}
 \end{center}
@@
 we identified where parallelism is enabled by default in Maven.
+Column ``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.
+We note that, considering these projects, the modules that do not use
+the configuration cited use the sequential configuration \Seq{}.
+For example, three modules (=28-25) from Log4J2 use sequential
+configuration.
 \begin{wraptable}{r}{0pt}%0.525\linewidth
@@
 \end{wraptable}
-Column ``\emph{Subject}'' indicates the name of the project, column
-``\emph{\# of modules}'' indicates the fraction of modules containing
-tests that use the configuration of parallelism mentioned in column
-``\emph{Mode}''.
-We note that, considering these projects, the modules that do not use
-the configuration cited use the sequential configuration \Seq{}.
-For example, three modules (=28-25) from Log4J2 use sequential
-configuration.
 
@@
 the dynamic checking, previously presented.
+
 This methodology founds \numProjectsParStatic{} projects.
@@
 That happened because these projects loaded a \emph{pom.xml} file from
-a jar file that we did not check.  Considering the static and dynamic
-methods together, we found a total of \numProjectsParTotal{} distinct
-projects using parallelism, corresponding to the union of the two
-subject sets.
+a jar file that we did not check.
+Considering the static and dynamic methods together, we found a total
+of \numProjectsParTotal{} distinct projects using parallelism,
+corresponding to the union of the two subject sets.
 
 \begin{center}
-\vspace{1ex}
 \fbox{
@@
 }
-\vspace{1ex}
 \end{center}
@@
 (see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
-with parallelization~---~configured by project owners~---~and without
+with parallelization~---~configured by project owners and without
 parallelization.
@@
 
-Table~\ref{tab:speedup} summarizes results.  Lines are sorted by
-project names.  Columns ``\emph{Group}'' and
-``\emph{Name}'' indicate, respectively, the group and the name of the
-subject.  Column ``$T_s$'' shows sequential execution time and column
-``$T_p$'' shows parallel execution time. Column ``$T_s/T_p$'' shows
-speedup or slowdown.  As usual, a ratio above 1x denotes speedup
-and a ratio below 1x denotes slowdown.
+Table~\ref{tab:speedup} summarizes results.
+Lines are sorted by project names.
+Columns ``\emph{Group}'' and ``\emph{Name}'' indicate, respectively,
+the group and the name of the subject.
+Column ``$T_s$'' shows sequential execution time and column ``$T_p$''
+shows parallel execution time.
+Column ``$T_s/T_p$'' shows speedup or slowdown.
+As usual, a ratio above 1x indicates speedup and a ratio below 1x
+indicates slowdown.
+
+Results show that, on average, parallel execution was
+\avgSpeedup{} times faster compared to sequential execution.
+Three cases worth special attention: \CodeIn{Log4J2}, \CodeIn{Chaos},
+and \CodeIn{Takes}.
+We note that parallel execution in \CodeIn{Log4J2} was
+ineffective.  We found that Maven invokes several test modules in this
+project but the test modules that dominate execution time run
+sequentially by default. This was also the case of the highlighted
+project \CodeIn{Californium}.
+No significant speedup was observed in \CodeIn{Chaos}, a project with
+only three test classes, of which one monopolizes the bulk of test
+execution time.
 
@@
 \midrule%
-Medium & Californium & 1.45m & 1.40m & 1.04x\\%
+Medium & Californium & 1.45m & 1.40m & \cellcolor{lightgray}1.04x\\%
 Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
@@
 \end{table}
-
-Results indicate that, on average, parallel execution was
-\avgSpeedup{} times faster compared to sequential execution.  Three
-cases worth special attention: \CodeIn{Chaos}, \CodeIn{Takes} and
-\CodeIn{Log4J2}.  No significant speedup was observed in
-\CodeIn{Chaos}, a project with only three test classes, of which one
-monopolizes the bulk of test execution time.  This project uses
-configuration \ParClassSeqMeth{}, which runs test classes in parallel
-and test methods, declared in each class, sequentially.  Consequently,
-speedup cannot be obtained as the cost of the single expensive test
-class cannot be broken down with the selected configuration.
-\Jbc{
-On the other hand, the speedup observed in project \CodeIn{Takes} was
+This project uses configuration \ParClassSeqMeth{}, which runs test
+classes in parallel but runs test methods, declared in each class,
+sequentially.
+Consequently, speedup cannot be obtained as the cost of the single
+expensive test class cannot be broken down with the selected
+configuration.
+Finally, the speedup observed in project \CodeIn{Takes} was
 the highest amongst all projects. This subject uses configuration
@@
 As result, the CPUs available for testing are kept occupied for the
-most part during test execution.}
-Finally, we note that parallel execution in \CodeIn{Log4J2} was
-ineffective.  We found that Maven invokes several test modules in this
-project but the test modules that dominate execution time run
-sequentially by default.
+most part during test execution.
 
@@
 We ran this experiment for a growing number of cores 1, 3, ..., 39. 
+\begin{wrapfigure}{r}{0.23\textwidth}
+  \vspace{-1ex}
+  \includegraphics[width=0.23\textwidth]{R/scalability/scalability.pdf}
+  \caption{\label{fig:scalability}Scalability.}
+  \vspace{-2ex}
+\end{wrapfigure}
 The plot shows results up to 17 cores as it is clear the tendency.
@@
 the basic setup we used in other experiments.
-\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  \centering
-  \includegraphics[width=.25\textwidth]{R/scalability/scalability.pdf}
-  \caption{\label{fig:scalability}Scalability.}
-\end{wrapfigure}
 This saturation is justified by the presence of a single test class,
@@
 reasonable for this experiment.
-
 %% \Jbc{Is this
@@
 %% operations).
-
 %% Notice that with parallelism enabled, the
@@
 %% and flakiness on each scenario.
-
-\Comment{
-    The rationale for this selection criteria was to maximize the chances
-    of observing speedup and flakiness, assuming that long-running tests
-    also have many tests. Indeed, we confirmed that test suites in these
-    projects contain at least 236 tests ($1,662.7$ in average).
-}
-
+%%    The rationale for this selection criteria was to maximize the chances
+%%    of observing speedup and flakiness, assuming that long-running tests
+%%    also have many tests. Indeed, we confirmed that test suites in these
+%%    projects contain at least 236 tests ($1,662.7$ in average).
+%% 
 %% In a first attempt of this experiment, we considered using Maven to
@@
 and for reference to analyze and diagnose outliers in our results.
-
 %% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
@@
 %% execucao do teste, (3) timeout}
-
 %% The script we implemented to measure time and flakiness takes a list
@@
 %% configuration.
-
-\Comment{ To obtain parallel configurations, we implemented a script
-  that takes a subject and a configuration label as inputs (\eg
-  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
-  the subject with the desired configuration. The workflow consists in
-  copying the project directory to a new directory, finding all
-  existing build files (\ie, \pomf{} files), and modifying all
-  existing Maven Surefire configurations with new values for the
-  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
-  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
-  manipulate XML documents. For configurations with forked JVMs
-  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
-  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
-  core).  To adjust the pool of threads for parallelism within a JVM,
-  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
-    consider 2 as it is the number of native threads per core OR 6 as
-    it represents 3 Cores * 2 native threads?}.To run the subjects and
-  their respective variations (\ie, the modified versions according to
-  the parallelism configuration), we used a similar approach as
-  described in Figure~\ref{fig:mvn-execution} except that...  }
-
+%%\Comment{ To obtain parallel configurations, we implemented a script
+%%  that takes a subject and a configuration label as inputs (\eg
+%%  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
+%%  the subject with the desired configuration. The workflow consists in
+%%  copying the project directory to a new directory, finding all
+%%  existing build files (\ie, \pomf{} files), and modifying all
+%%  existing Maven Surefire configurations with new values for the
+%%  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
+%%  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
+%%  manipulate XML documents. For configurations with forked JVMs
+%%  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
+%%  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
+%%  core).  To adjust the pool of threads for parallelism within a JVM,
+%%  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
+%%    consider 2 as it is the number of native threads per core OR 6 as
+%%    it represents 3 Cores * 2 native threads?}.To run the subjects and
+%%  their respective variations (\ie, the modified versions according to
+%%  the parallelism configuration), we used a similar approach as
+%%  described in Figure~\ref{fig:mvn-execution} except that...  }
 %% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /

### 2017-09-09 paper/evaluation.tex

@@
 services sufficed to provide timely feedback while running only smoke
-\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
+\begin{wrapfigure}{r}{0.15\textwidth}
     \centering
-    \includegraphics[width=.18\textwidth]{results/survey.pdf}
+    \includegraphics[width=.15\textwidth]{results/survey.pdf}
     \caption{\label{fig:rq5-answers}Summary of developer's answers to
@@
 \begin{center}
-\vspace{-1ex}
+\vspace{1ex}
 \fbox{
@@
 We ran this experiment for a growing number of cores 1, 3, ..., 39. 
+The plot shows results up to 17 cores as it is clear the tendency.
+We noticed that improvements are marginal after three cores, which is
 \begin{wrapfigure}{r}{0.23\textwidth}
@@
 \end{wrapfigure}
-The plot shows results up to 17 cores as it is clear the tendency.
-We noticed that improvements are marginal after three cores, which is
 the basic setup we used in other experiments.

### 2017-09-09 paper/intro.tex

@@
 
-As software evolves it is expected that the number of tests and the
-length of test runs increase.  Both components can add up to the
-aggregate cost of running a test suite.  Dealing with high testing
-costs is an important problem in software engineering research and
-industrial practice.
+%% As software evolves it is expected that the number of tests and the
+%% length of test runs increase.  Both components can add up to the
+%% aggregate cost of running a test suite.
 
-Several approaches have been proposed in the research literature to
-address the regression testing problem, with the focus mainly on test
-suite minimization, prioritization, reduction, and
-selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
-mainly on distributing the testing workload.  Evidence of this are the
-Google TAP system~\cite{google-tap,google-ci} and the Microsoft
-CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
-provide distributed infrastructures to efficiently build massive
-amounts of code and run tests.  Building in-house server clusters is also a
+Dealing with high testing costs has been an important problem in
+software engineering research and industrial practice.  Several
+approaches have been proposed in the research literature to address
+this problem, with the focus mainly on test suite minimization,
+prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
+In industry, the focus has been mainly on distributing the testing
+workload.  Evidence of this are the Google TAP
+system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
+system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
+distributed infrastructures to efficiently build massive amounts of
+code and run tests.  Building in-house server clusters is also a
 popular mechanism to distribute testing workloads.  For example, as of
-August 2013, the test suite of the Groupon PWA system, which powers the
-\url{groupon.com} website, included over 19K tests.  To run all those
-tests under 10m, Groupon used a cluster of 4 computers with 24 cores
-each~\cite{kim-etal-fse2013}.
+August 2013, the test suite of the Groupon PWA system, which powers
+the \url{groupon.com} website, included over 19K tests.  To run all
+those tests under 10m, Groupon used a cluster of 4 computers with 24
+cores each~\cite{kim-etal-fse2013}.
 
@@
 not be economically viable.  For these cases, the use of commodity
-hardware (\eg{}, existing workstations) is an attractive
+hardware\Comment{ (\eg{}, existing workstations)} is an attractive
 solution for running tests.  The proliferation of
@@
 for cost-effective test execution and supply of relatively inexpensive
-testing infrastructures~---~led us to investigate the usage of
-parallelism to speed up test execution.
+testing infrastructures~---~inspired us to investigate 
+test suite parallelization in practice.
 
@@
 to reduce testing costs.  In the limit, parallelization would be
-fruitless if all projects used short-running test suites or if the
+fruitless if all projects had short-running test suites or if the
 execution cost was dominated by a single test case in the suite.  The
@@
 the technology and to understand their reasons.  The dimension
-\emph{speedups} evaluates the observed impact of
+\emph{speedup} evaluates the observed impact of
 parallelization\Comment{~---~when used in selected open-source
   projects~---~} in running times.  Finally, the dimension
-\emph{tradeoffs} considers the problems in running tests in parallel,
-including test flakiness~\cite{luo-etal-fse2014}.
-We briefly summarize our findings in the following.
+\emph{tradeoffs} evaluates the relationship between speedups obtained
+with parallelization and issues that arise 
+when running tests in parallel, including test
+flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly summarize our findings
+in the following.
 
@@
 
-\vspace{1ex}\noindent\emph{Feasibility.}~To assess how prevalent
+\noindent\emph{Feasibility.}~To assess how prevalent
 long-running test suites are we selected \numSubjs{} popular Java
@@
 take at least 5m to run.  Considering the \numMedLong{}
-projects in those two groups, the average execution time of a test
+projects with test suites taking longer than a minute to run, the average execution time of a test
 suite was \averageMedLongRunning{}.  Results also show that test cases
@@
 to run.  Furthermore, we found that only in rare cases few test cases
-monopolize execution cost associated with each test suite.
+monopolize the overall time to run a test suite.
 
-\vspace{1ex}\noindent\emph{Adoption.}~ We considered two aspects in
+\noindent\emph{Adoption.}~ We considered two aspects in
 measuring technology adoption.  First, we measured usage of
@@
   (monitoring execution of build files) for the presence of
-  parallelization.}  Considering only those projects whose test suites
-that longer than a minute to run, we found that only
-\percentParallel{} of them use parallelism.  When correcting this
-value with the feedback obtained a posteriori from developers, we
-realized that the proportion should be higher, of
-\percentParallelUpdated{}.  For the qualitative analysis we surveyed
+  parallelization.}  Considering only the projects whose test suites
+take longer than a minute to run, we found that
+only \percentParallelUpdated{} of them use parallelism.
+%% To sum, results indicate that test suite parallelization is
+%% underutilized.
+%% only
+%% \percentParallel{} of them use parallelism.  When correcting this
+%% value with the feedback obtained a posteriori from developers, we
+%% realized that the proportion should be higher, of
+%% \percentParallelUpdated{}.
+%%For the qualitative analysis
+We also contacted 
 developers from a selection of costly projects that did not use
-parallelization.  Results indicate that test suite parallelization is
-underutilized.  Dealing with concurrency-related issues (\eg{}, the
+parallelization to understand the reasons for not using parallelization.  Dealing with concurrency-related issues (\eg{}, the
 extra work to organize test suite to avoid concurrency errors) and the
@@
 
-\vspace{1ex}\noindent\emph{Speedups.}~We used two setups to measure
-execution speedups.  In one setup we measured the speedups obtained on
-projects that we knew a priori ran their test suites in parallel by
+\noindent\emph{Speedups.}~We used two setups to measure
+speedups.  In one setup we measured speedups obtained on
+projects that run test suites in parallel by
 default.  In the other setup, we evaluated how execution scales with
@@
 \avgSpeedup{}x.  Although we found cases with very high speedups
-(\eg{}, 28.8x for project Jcabi), we found cases where speedups were
+(\eg{}, 28.8x for project Jcabi), we also found cases where the speedups were
 not very significant.  Considering the scalability experiment, we
-noticed, perhaps as expected, that speedups are bounded by
+noticed, perhaps as expected, that parallelization obtained with forking JVMs scales with the number
+of cores but the speedups are bounded by
 long-running test classes.
@@
 
-\vspace{1ex}\noindent\emph{Tradeoffs.}~Test flakiness is a central
-issue that can arise when running tests in parallel.  Dependent tests
+\noindent\emph{Tradeoffs.}~Test flakiness is a central
+concern when running tests in parallel.  Dependent tests
 can be affected by different schedulings of test methods and classes.
@@
 configurations on test flakiness and speedup.  Overall, results
-indicate that parallel configurations that fork JVMs do not achieve
-speedups as high as configurations that parallelize test classes and
-methods, however they manifest much lower flakiness ratios.
+indicate that configurations that fork JVMs do not achieve
+speedups as high as other more-agressive configurations, but they
+manifest much lower flakiness ratios.
 
-Our observations may trigger multiple actions:
+Our observations may trigger different actions:
 
@@
   impressive speedups at the expense of sometimes impressive rates of
-  flakiness.  Breaking test dependencies to avoid flakiness and take
-  full advantage of those options is advised for developers with
+  flakiness.  Breaking test dependencies (with
+  ElectricTest~\cite{bell-etal-esecfse2015}, for example) to avoid flakiness is advised for developers with
   greater interest in efficiency.
-\item \emph{Refactor tests for load balancing.}~Forked JVMs scale
-  better with the number of cores when the test workload is balanced
+\item \emph{Refactor tests for load balancing.}~The configuration with
+  forked JVMs scales
+  better\Comment{ with the number of cores} when the test workload is balanced
   across testing classes.  Automated refactoring could help balance
@@
   available.) Those issues can hinder developers from using parallel
-  testing. Better debugging infrastructure is important.
+  testing. Better debugging support for build systems could help
+  on that. 
 \end{itemize}

### 2017-09-09 paper/modes.tex
minor tweaks with Luis
pass on intro
Some cleanup

@@
-\newcommand{\Seq}{C0}
-\newcommand{\SeqClassParMeth}{C1}
-\newcommand{\ParClassSeqMeth}{C2}
-\newcommand{\ParClassParMeth}{C3}
-\newcommand{\Fork}{F}
-\newcommand{\ForkSeq}{\Fork{}\Seq{}}
-\newcommand{\ForkParMeth}{\Fork{}\SeqClassParMeth{}}
-
 \section{Parallel Execution of Test Suites}
@@
 
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}
-  \vspace{-1ex}
-  \caption{\label{fig:levels}Levels of parallelism.}
-\end{figure}
-
-Figure~\ref{fig:levels} illustrates the different levels where
+Figure~\ref{fig:levels} illustrates different levels where
 parallelism in test execution can be obtained.
@@
 network.  For instance, using virtual machines from a cloud service to
+\begin{wrapfigure}{r}{0.15\textwidth}  
+  \centering
+  %  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}    
+  \includegraphics[width=0.08\textwidth]{figs/parallel-levels-short.pdf}  
+  \caption{\label{fig:levels}Levels of parallelism.}
+  \vspace{-2ex}
+\end{wrapfigure}
 distribute test execution.  The lowest levels denote parallelism
@@
 nodes whereas the highest level leverages the aggregate processing
-power of the farm.
-
+power of a network of machines.
 This paper focuses on low-level parallelism, where computation can be
@@
 In the following, we elaborate relevant features of testing frameworks
-and build systems.  We focused on Java, Maven, and JUnit but the
+and build systems for parallelization.  We focused on Java, Maven, and JUnit but the
 discussion can be generalized to other language and tools.
@@
     \textbf{Parallel classes; Parallel methods
-      (\ParClassParMeth).}~This configuration corresponds to the
-    combination of \SeqClassParMeth{} and \ParClassSeqMeth{}.  
+      (\ParClassParMeth).}~This configuration runs test classes and
+    methods concurrently.\Comment{corresponds to the
+    combination of \SeqClassParMeth{} and \ParClassSeqMeth{}.  }
 \end{itemize}
@@
 (or in designing new test suites) is the possibility of race
-conditions on shared data during execution.  Data sharing can occur
-through state that is reachable from statically-declared variables in
+conditions on shared data during execution.  Data sharing can occur,
+for example, through state that is reachable from statically-declared variables in
 the program or through variables declared within the scope of the test
-class~\cite{luo-etal-fse2014}.  Considering data race avoidance,
+class or even through resources available on the file system and the network~\cite{luo-etal-fse2014}.  Considering data race avoidance,
 configuration \SeqClassParMeth{} is preferable over \ParClassSeqMeth{}
@@
 %% process on a given CPU and handling a partition of the test set.
-
 Forking OS processes to run test jobs is the basic mechanism of build
@@
   system spawns multiple JVMs with this configuration, assigning a
-    partition of the set of test classes to each JVM.  Test methods
+  partition of the set of test classes to each JVM.  Test classes and methods
   run sequentially within each JVM.
@@
   this configuration, the build system forks multiple JVMs, as
-    \ForkSeq{} does.  However, it runs tests concurrently, as
+  \ForkSeq{} does, but it runs test methods concurrently, as
   \SeqClassParMeth{} does.
@@
 %%   like this was initially conceived to run tests in isolation}
-
 %% \Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
 %%   configuracao abaixo?}\Jbc{added...}
-
 %%We are unaware of other build system capable of running multiple
 %%classes at time within a forked process.
-
 %%  to
@@
 %% plugins.
-
 %% \Jbc{falar do surefire e explicar a
@@
 %% pool de 5 threads em cada JVM para executar testes em paralelo.}
-
 \begin{figure}[h!]
@@
 \end{figure}
+\vspace{-2ex}
 

### 2017-09-09 paper/evaluation.tex
pass on section 3 (objects of analysis)

@@
 \github{} stars~\cite{github-stars} to define relevant projects, we
-observed that 100 was enough to eliminate trivial subjects. The third
+observed that one hundred stars was enough to eliminate trivial subjects. The third
 criteria serves to skip projects without recent activity. The fourth
@@
 not provide a feature to search for projects containing certain files
-in the dir structure (\eg{}, \emph{pom.xml}).
+(\eg{}, \emph{pom.xml}) in the directory structure.
 Figure~\ref{fig:subject-query} illustrates the query to the \github{}
-API as an HTTP request.
+API as an HTTP request.   The result set is sorted
+in descending order of stars.
 
 \vspace{1ex}
-\begin{figure}[h!]
+\begin{figure}[t!]
 \centering
@@
 https://api.github.com/search/repositories?q=language:java
-        +stars:>=100+pushed:>=2016+mvn%20in:readme
-        &sort=stars
+ +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
 \end{lstlisting}
   \caption{\label{fig:subject-query} Query to the \github{} API for
-  projects with the following criteria: (1) Java, (2) at least 100
-  stars, (3) updated on January 1st, 2016 (or later), (4) contains
-  the string \emph{mvn} in the \emph{readme} file. Output is
-  paginated in descending order of stars.}
+  projects that (1) use Java, (2) contains at least 100
+  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
+  the string \emph{mvn} in the \emph{readme} file.}
+  \vspace{-5ex}  
 \end{figure}
 
-After obtaining a list of potential projects, we filtered those
-containing a \pomf{} file in the root directory.  A Maven project may
-contain several sub-modules with multiple \pomf{} files.
-To avoid introducing noise in our experiments, for each project, we
-executed the tests \SubjectsReruns{} times to filter projects with
-deterministic outcome.
-As of August 25th 2017, our search criteria returned \SubjectsGithub{}
+We used the following methodology to select projects for
+analysis. After obtaining the list of potential projects from GitHub, we filtered those
+containing a \pomf{} file in the root directory.\Comment{  A Maven project may
+contain several sub-modules with multiple \pomf{} files.}
+Then, considering this set of Maven projects, we
+executed the tests for \SubjectsReruns{} times to discard those projects with
+issues
+in the build file and nondeterministic results observed from sequential executions.
+As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
 subjects.
-
-From these \SubjectsGithub{} downloaded projects,
+From this set of projects,
 \SubjectsGithubNotMaven{} projects were not Maven or did not have a
-\pomf{} in the root directory, and we were unable to test
-\SubjectsGithubNotTestable{} projects  due to incompatible environment
-(\eg, missing required web browser or database management system).
-In addition, we identified \SubjectsGithubFlaky{} projects with
-``flaky tests''~\cite{luo-etal-fse2014}.
-In general, a ``flaky test'' is a test that either pass or fail under
+\pomf{} in the root directory, 
+\SubjectsGithubNotTestable{} projects were not considered because of
+environment incompatibility
+(\eg, missing\Comment{ required web browser or database management system}~DBMS),
+\SubjectsGithubFlaky{} projects were discarded because of
+``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes or fails under
 the same circumstances leading to non-deterministic results.
-As some of our experiments consist in running tests on different
+As some of our experiments consist of running tests on different
 threads, we ignored these projects as it would be impractical
@@
 other source of flakiness.
-From the \SubjectsGithubConsistant{} projects with
+From the remaining \SubjectsGithubConsistant{} projects with
 deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
-projects with more than \SuiteFailingThreshold{} of tests failing to
-reduce bias in our dataset.
-We ignored failing tests with JUnit's
-\CodeIn{@Ignore} annotation on the remaining projects.
-Our final set of subjects consists of \numSubjs{} projects.
+projects with \SuiteFailingThreshold{} or more failing tests as to
+reduce bias. For the
+remaining projects with failing tests, we used the JUnit's
+\CodeIn{@Ignore} annotation to ignore failing tests.
+Our final set of subjects contains \numSubjs{} projects.
 Figure~\ref{fig:subjects} summarizes our sample set.

### 2017-09-09 paper/evaluation.tex
minor tweaks

@@
   \numSubjs{} projects to conduct our study.}
-  \vspace{-2ex}
+  \vspace{-1ex}
 \end{figure}
 
-\subsection{Setup and Replication}
+%\subsection{Setup and Replication}
 \label{sec:setup}
@@
 threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
-(64-bit version).  Software settings include Git, Java 8, and Maven
-3.3.9.
-We used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to
-process test results and generate plots.  All source artifacts are
+(64-bit version).  We used\Comment{ Git,} Java 8 and Maven
+3.3.9 to build projects and run test suites. To
+process test results and generate plots
+we used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are
 publicly available for replication on our website~\cite{ourwebpage}.
-This includes supporting scripts (\eg, the script that test subjects
-and generates raw analysis data) and the full list of projects.
+This includes supporting scripts\Comment{ (\eg, the scripts to run the tests
+and generate raw analysis data)} and the full list of projects.
 

### 2017-09-09 paper/evaluation.tex
pass on RQ1

@@
 \newcommand{\numRQFeasibilityOne}{RQ1}
-\newcommand{\RQFeasibilityOne}{How prevalent is the occurence of time-consuming
+\newcommand{\RQFeasibilityOne}{How prevalent are time-consuming
   test suites\Comment{ in open-source projects}?}
@@
 
-To evaluate prevalence of projects with costly test suites, we
-considered the \numSubjs{} testable subjects from
+To evaluate prevalence of projects with time-consuming test suites, we
+considered the \numSubjs{} projects, appearing in 
 Figure~\ref{fig:subjects}.  Figure~\ref{fig:mvn-execution} illustrates
@@
 The tasks we found were ignored from execution (lines 1-4).
-Furthermore, to avoid noise from unrelated OS events, we configured
-our workstation to only run essential services.
+Furthermore, we configured
+our workstation to only run essential services as to avoid noise from unrelated OS events.
 The machine was dedicated to our experiments and we
@@
 line.  Results were very close.
-
 The main loop (lines 6-15) of the script in
@@
 \input{codes/evaluation}
-\vspace{-1ex}
-
-We ran the test suite for each subject three times, reporting averaged
-execution times in three ranges: tests that run within a minute
-(\shortg{} group), tests that run in one to five minutes (\medg{}
-group), and tests that run in five or more minutes (\longg{}
-group).
+
 \Comment{We followed a similar methodology to group projects by time as
@@
 time cost from subjects out of the \shortg{} group}
-Figure~\ref{fig:rq1-barplot} shows the number of projects in
+
+We ran the test suite for each subject three times, reporting averaged
+execution times in three ranges: tests that run within a minute
+(\shortg{}), tests that run in one to five minutes (\medg{}), and
+tests that run in five or more minutes (\longg{}). Figure~\ref{fig:rq1-barplot} shows the number of projects in
 each group.  As expected, \longg{} and \medg{} projects do not occur
@@
 relatively high numbers.
-
-Figure~\ref{fig:rq1-boxplot} shows as boxplots distribution of cost of
-test suites in each group.
+Figure~\ref{fig:rq1-boxplot} shows the distribution of execution time of
+test suites in each of these groups.
 Note that the y-ranges are different.
@@
 The test suites in this group ran in 15 or less seconds for
-over 75\% of the cases.  Such scenarios constitute the majority of the
-cases we analyzed.  Considering the groups \medg{} and \longg{},
+over 75\% of the cases.\Comment{  Such scenarios constitute the majority of the
+cases we analyzed.} Considering the groups \medg{} and \longg{},
 however, we found many costly executions.  Nearly 75\% of the projects
 from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
-the projects from the \longg{} group took $\sim$20 minutes to run.  We
+the projects from the \longg{} group take $\sim$20 minutes to run.  We
 found cases in the \longg{} group were execution takes over 50 minutes
-to complete, as can be observed from the outliers (dots) in the plot.
+to complete, as can be observed from the outliers in the boxplot.
 
@@
   \end{subfigure}%
-  \caption{(a) Subjects grouped by time cost ($t$): short run ($t <
-  1m$), medium run ($1m \le t < 5m$), and long run ($5m \le t$); (b)
-  Distribution of time cost by group.}
-  \vspace{-3ex}
+  \caption{(a)\Comment{ Testing time grouped by time cost ($t$): short run
+    ($t<1m$), medium run ($1m \le t < 5m$), and long run ($5m \le{}
+    t$);}~Number of projects in each cost group and
+    (b)~Distribution of running times per cost group.}
+  \vspace{-1ex}
 \end{figure}
 
-It is important to note that we under-estimated cost in our
-experiments for one main reason.
-Some projects may omit long-running tests on their default
-execution. For instance, the project \CodeIn{apache.maven-surefire}
+It is important to note that we under-estimated running times as we missed test modules not enabled for
+execution in the root \emph{pom.xml}.\Comment{Some projects may omit long-running tests on their default
+execution.} For instance, the project \CodeIn{apache.maven-surefire}
 runs all unit tests in a few seconds.  According to our criteria, this
 project is classified as \shortg{} but a closer look reveals
-that only smoke tests are run by default in this project.
-Time-consuming integration and system tests are only accessible via
+that only smoke tests are executed in this project by default.
+In this project, integration and system tests, which take longer to run, are only accessible via
 custom parameters, which we do not handle in our experimental setup.
@@
 executed all tests and \numSubjsFail{} reported some test failure.
-Furthermore, from these \numSubjsFail{} subjects, only 11 subjects
-have more than 5\% of failing tests (7.3\% in average).
+From these \numSubjsFail{} subjects, only 11 subjects
+have more than 5\% of failing tests (7.3\% on average).
 \begin{center}
@@
     projects) take at least 1 minute to run and
-    \percentLongRunning{} take at least 5 minutes to run.\Comment{
+    \percentLongRunning{} of them take at least 5 minutes to run.\Comment{
       (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}

### 2017-09-09 paper/evaluation.tex

@@
 the projects from the \longg{} group take $\sim$20 minutes to run.  We
-found cases in the \longg{} group were execution takes over 50 minutes
+found cases in the \longg{} group were execution takes more than 50 minutes
 to complete, as can be observed from the outliers in the boxplot.
@@
 
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
+  \caption{\label{fig:time-distributions}Distribution of test case time per project.}%
+  \vspace{-3ex}
+\end{figure}
+
 Section~\ref{sec:rqA} showed that medium and long-running projects are
@@
 \numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
-measures the distribution of test costs in test suites as to estimate
-potential of obtaining speedups with parallelization.  In
+measures the distribution of test costs in test suites.\Comment{ as to estimate
+potential of obtaining speedups with parallelization.}  In
 the limit, if cost is dominated by a single test from a large test
@@
 Figure~\ref{fig:time-distributions} shows the time distribution of
-individual test cases per project (x-axis denote projects appearing in
-arbitrary order).
-We observed that the average median value of execution cost for a
-test was relatively small (dashed horizontal red lines), namely 0.08s
-for \medg{} projects and 0.16s for \longg{} projects.
-The standard deviations associated with each distribution were
+individual test cases per project.
+We observed that the average median times (see dashed horizontal red
+lines) were small, namely 0.08s
+for \medg{} projects and 0.16s for \longg{} projects, and the standard deviations associated with each distribution were
 relatively low.\Comment{ Figure~\ref{fig:sd} shows the number of
-projects within specific ranges of $\sigma$ values.}  We noted a small
-number of cases of CPU monopolization.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
-  \caption{\label{fig:time-distributions}Time distributions per projects.}%
-  \vspace{-3ex}
-\end{figure}
-
-For example, the highest value of $\sigma$ occurred in
+  projects within specific ranges of $\sigma$ values.} High values of
+$\sigma$ are indicative of CPU monopolization. We found only a small number
+of those. The highest value of $\sigma$ occurred in
 \CodeIn{uber\_chaperone}, a project from the \longg{} group.
@@
 the tests running faster.
-Figure~\ref{fig:time-distributions} shows that the average median
-times are similar for \medg{} and \longg{}-running test suites.
-The difference in overall running times is mainly justified by the
-number of test cases as opposed to the individual costs of test cases.
 
@@
 distribution of test suite sizes across groups.  This figure indicates
-that long projects, have a higher median and much higher average
+that long projects have a higher median and much higher average
 number of test cases.
@@
 variables was weak.
-Figure~\ref{fig:scattercost} illustrates this regression line.
+Figure~\ref{fig:scattercost} illustrates the regression lines between
+these the variables test suite cost and number of test cases.
+To sum, we observed that for projects with long-running test suites
+running time is typically
+justified by the number of test cases as opposed to the cost of individual test cases.
+
+%% Figure~\ref{fig:time-distributions} shows that the average median
+%% times are similar for \medg{} and \longg{}-running test suites.
 
@@
   \end{subfigure}
-  \hfill
+  \hspace{3ex}
   \begin{subfigure}{0.28\textwidth}
@@
 \CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
-  in old versions of Maven Surefire} to define the number of forked
+  in old versions of Maven Surefire.} to define the number of forked
 JVMs.  As such, we captured, for each project, all related key-value

### 2017-09-09 paper/evaluation.tex
pass on survey

--- 2017-09-09 paper/evaluation.tex
@@
 \github{} stars~\cite{github-stars} to define relevant projects, we
-observed that one hundred stars was enough to eliminate trivial subjects. The third
+observed that 100 was enough to eliminate trivial subjects. The third
 criteria serves to skip projects without recent activity. The fourth
@@
 not provide a feature to search for projects containing certain files
-(\eg{}, \emph{pom.xml}) in the directory structure.
+in the dir structure (\eg{}, \emph{pom.xml}).
 Figure~\ref{fig:subject-query} illustrates the query to the \github{}
-API as an HTTP request.   The result set is sorted
-in descending order of stars.
+API as an HTTP request.
 
 \vspace{1ex}
-\begin{figure}[t!]
+\begin{figure}[h!]
 \centering
@@
 https://api.github.com/search/repositories?q=language:java
- +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
+        +stars:>=100+pushed:>=2016+mvn%20in:readme
+        &sort=stars
 \end{lstlisting}
   \caption{\label{fig:subject-query} Query to the \github{} API for
-  projects that (1) use Java, (2) contains at least 100
-  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
-  the string \emph{mvn} in the \emph{readme} file.}
-  \vspace{-5ex}  
+  projects with the following criteria: (1) Java, (2) at least 100
+  stars, (3) updated on January 1st, 2016 (or later), (4) contains
+  the string \emph{mvn} in the \emph{readme} file. Output is
+  paginated in descending order of stars.}
 \end{figure}
 
-We used the following methodology to select projects for
-analysis. After obtaining the list of potential projects from GitHub, we filtered those
-containing a \pomf{} file in the root directory.\Comment{  A Maven project may
-contain several sub-modules with multiple \pomf{} files.}
-Then, considering this set of Maven projects, we
-executed the tests for \SubjectsReruns{} times to discard those projects with
-issues
-in the build file and nondeterministic results observed from sequential executions.
-As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
+After obtaining a list of potential projects, we filtered those
+containing a \pomf{} file in the root directory.  A Maven project may
+contain several sub-modules with multiple \pomf{} files.
+To avoid introducing noise in our experiments, for each project, we
+executed the tests \SubjectsReruns{} times to filter projects with
+deterministic outcome.
+As of August 25th 2017, our search criteria returned \SubjectsGithub{}
 subjects.
-From this set of projects,
+
+From these \SubjectsGithub{} downloaded projects,
 \SubjectsGithubNotMaven{} projects were not Maven or did not have a
-\pomf{} in the root directory, 
-\SubjectsGithubNotTestable{} projects were not considered because of
-environment incompatibility
-(\eg, missing\Comment{ required web browser or database management system}~DBMS),
-\SubjectsGithubFlaky{} projects were discarded because of
-``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes or fails under
+\pomf{} in the root directory, and we were unable to test
+\SubjectsGithubNotTestable{} projects  due to incompatible environment
+(\eg, missing required web browser or database management system).
+In addition, we identified \SubjectsGithubFlaky{} projects with
+``flaky tests''~\cite{luo-etal-fse2014}.
+In general, a ``flaky test'' is a test that either pass or fail under
 the same circumstances leading to non-deterministic results.
-As some of our experiments consist of running tests on different
+As some of our experiments consist in running tests on different
 threads, we ignored these projects as it would be impractical
@@
 other source of flakiness.
-From the remaining \SubjectsGithubConsistant{} projects with
+From the \SubjectsGithubConsistant{} projects with
 deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
-projects with \SuiteFailingThreshold{} or more failing tests as to
-reduce bias. For the
-remaining projects with failing tests, we used the JUnit's
-\CodeIn{@Ignore} annotation to ignore failing tests.
-Our final set of subjects contains \numSubjs{} projects.
+projects with more than \SuiteFailingThreshold{} of tests failing to
+reduce bias in our dataset.
+We ignored failing tests with JUnit's
+\CodeIn{@Ignore} annotation on the remaining projects.
+Our final set of subjects consists of \numSubjs{} projects.
 Figure~\ref{fig:subjects} summarizes our sample set.
@@
   \numSubjs{} projects to conduct our study.}
-  \vspace{-1ex}
+  \vspace{-2ex}
 \end{figure}
 
-%\subsection{Setup and Replication}
+\subsection{Setup and Replication}
 \label{sec:setup}
@@
 threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
-(64-bit version).  We used\Comment{ Git,} Java 8 and Maven
-3.3.9 to build projects and run test suites. To
-process test results and generate plots
-we used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are
+(64-bit version).  Software settings include Git, Java 8, and Maven
+3.3.9.
+We used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to
+process test results and generate plots.  All source artifacts are
 publicly available for replication on our website~\cite{ourwebpage}.
-This includes supporting scripts\Comment{ (\eg, the scripts to run the tests
-and generate raw analysis data)} and the full list of projects.
+This includes supporting scripts (\eg, the script that test subjects
+and generates raw analysis data) and the full list of projects.
 
@@
 projects (\percEmailsProjectsAnswered{} of the total) were represented
-in those replies.  Note that multiple developers on each project
+in those replies. \Luis{In one specific case, one developer worked in
+  multiple projects, and we consider it as a different answer.}
+Note that multiple developers on each project
 received emails.  We sent the following set of questions to

### 2017-09-09 paper/evaluation.tex
pass on RQ3

--- 2017-09-09 paper/evaluation.tex
@@
 issues
-in the build file and nondeterministic results observed from sequential executions.
+in the build file and non-deterministic results observed from sequential executions.
 As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
@@
   projects with a very small number of tests monopolizing end-to-end
-  execution time were rare. Time most often is distribuited evenly
+  execution time were rare. Time most often is distributed evenly
   across test cases.}
@@
 
-To answer \numRQAdoptionOne{}, we selected all projects from the \medg{} and
-\longg{} groups, \ie, projects that ran in at least one minute.  This
-set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
-looked for dynamic and static manifestations of parallelism.
-
-%% The
-%% following section report results for each of these cases.
+To answer \numRQAdoptionOne{} we used projects from the \medg{} and
+\longg{} groups where parallelization can be more helpful. We used a
+dynamic and a static approach to find manifestations of
+parallelism. We discuss results obtained with these complementary
+approaches in the following.
 
@@
 same configuration, we counted only one occurrence.
-It came as a surprise the observation that
-no project used distinct configurations in their modules. Considering
+Considering
 our set of \numMedLong{} projects, we found that only
@@
 Maven process.  That decision could prevent execution of particular
-test modules.
-Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
-we identified where parallelism is enabled by default in Maven.
-Column ``\emph{Subject}'' indicates the name of the project, column
-``\emph{\# of modules}'' indicates the fraction of modules containing
-tests that use the configuration of parallelism mentioned in column
-``\emph{Mode}''.
-We note that, considering these projects, the modules that do not use
-the configuration cited use the sequential configuration \Seq{}.
-For example, three modules (=28-25) from Log4J2 use sequential
-configuration.
+test modules. Table~\ref{tab:freqmodes-dynamic} shows the
+\numProjectsPar{} projects we identified where parallelism is enabled by default in Maven.
 \begin{wraptable}{r}{0pt}%0.525\linewidth
@@
     \label{tab:freqmodes-dynamic}
-    \vspace{-1ex}
+%    \vspace{-1ex}
 \end{wraptable}
+Column ``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.
+We note that, considering these projects, the modules that do not use
+the configuration cited use the sequential configuration \Seq{}.
+For example, three modules (=28-25) from Log4J2 use sequential
+configuration. It came as a surprise the observation that
+no project used distinct configurations in their modules.
 
@@
 \label{sec:rqC-2}
-As our previous approach cannot detect parallelism in non-default
-configurations, we also looked for indication of parallelism in build
+Given that the dynamic approach cannot detect parallelism manifested
+through the default
+configuration of projects, we also searched for indications of parallelism in build
 files\Comment{ in the same sample set of \numMedLong{} projects}.  We
@@
 \emph{pom.xml} files are encapsulated in jar files or files downloaded from
-the network.  Consequently, this static checking is complementary to
-the dynamic checking, previously presented.
-
-This methodology founds \numProjectsParStatic{} projects.
+the network.  Consequently, this approach complements the
+the dynamic approach. Overall, we found \numProjectsParStatic{}
+projects manifesting parallelism with this approach.
 Compared to the set of projects listed in
@@
 That happened because these projects loaded a \emph{pom.xml} file from
-a jar file that we did not check.
+a jar file that we missed.
 Considering the static and dynamic methods together, we found a total
@@
 %%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
-%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock
-%%  LocalWords:  mapdb workflow XPath
+%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
+%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
+%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
+%%  LocalWords:  Vavr SNE Urbanairship Datacube

### 2017-09-09 paper/evaluation.tex
pass on RQ4

@@
 projects (\percEmailsProjectsAnswered{} of the total) were represented
-in those replies. \Luis{In one specific case, one developer worked in
-  multiple projects, and we consider it as a different answer.}
-Note that multiple developers on each project
-received emails.  We sent the following set of questions to
+in those replies. Note that multiple developers on each project
+received emails. In one specific case, one developer worked in
+  multiple projects, and we consider it as a different answer. We sent the following set of questions to
 developers:
@@
 ``b''), \emailsD{} of developers mentioned that continuous integration
-services sufficed to provide timely feedback while running only smoke
+suffices to provide timely feedback while running only smoke
 \begin{wrapfigure}{r}{0.15\textwidth}
@@
 
-To answer this research question, we selected ten different subjects,
+To answer this research question, we selected 15 different subjects,
 ran their test suites against all configurations described in
 Section~\ref{sec:modes}, and compared their running times and rate of
-test flakiness.  We used the sequential execution (configuration
-\emph{\Seq{}}) associated with each project as the comparison baseline
-in this experiment.  We selected subjects from the medium and long
-groups from Section~\ref{sec:rqA} and further selected their longest
-test module for testing.  The rationale for this selection was to
-obtain a diverse set of subjects exposing a wide range of running
-times (range observed 1.1m-8.2m) and number of test cases (range
-observed 54-17,513) and yet be able to run the experiment in
-reasonable time.  We ran each project on each configuration with ten
-seeds.  Overall, we needed to reran test suites 600 times, 60 times
-(10x6 configurations) on each project.  Given the low standard
-deviations observed in our measurements we consider ten seeds
-reasonable for this experiment.
+test flakiness.  We used the sequential execution associated with each
+project as the comparison baseline in this experiment.  We sorted the
+subjects by decreasing order of execution time and selected the first
+15 projects that uses JUnit 4.7 or later.  The rationale for this
+criteria is to ensure compatibility with parallel configuration since
+older versions of JUnit does not support parallel testing.  We ran
+each project on each configuration for \SubjectsReruns{} times.
+Overall, we needed to reran test suites 270 times, 18 times (3x6
+configurations) on each project.  Given the low standard deviations
+observed in our measurements and the aggregated time cost of 270 test
+executions, we consider \SubjectsReruns{} reruns reasonable for this
+experiment.
 %% \Jbc{Is this
@@
 %% run the subjects on the different parallel configurations. However,
-
 It is worth mentioning that we used custom JUnit runners as opposed to
-Maven to run \Comment{configurations \emph{C*}}test suites with
-different parallel configurations (see Section~\ref{sec:modes}).
+Maven to run test suites with different parallel configurations (see
+Section~\ref{sec:modes}).
 After carefully checking library versions for compatibility issues and
@@
 are observed.  These issues are categorized and documented on our
-website~\cite{ourwebpage} with Docker containers (for reproduction).
+website~\cite{ourwebpage} and can be reproduced with our scripts.
 To address those issues we implemented basic JUnit test runners (one
@@
 dependency plugin~\cite{maven-dep} to build the project's classpath
-with the command \CodeIn{mvn dependency:build-classpath}. Once we have
-the classpath and the tests to run, we invoke our JUnit runner that
-runs the test classes with different parallel configurations at
-once. For the sequential execution, we invoke the default JUnit test
-runner. For parallelism within a JVM (\ie, the configurations
+with the command \CodeIn{mvn dependency:build-classpath}.
+Once we have the classpath and the tests to run, we invoke our JUnit
+custom runner to run the test classes with different parallel
+configurations. For the sequential execution, we invoke the
+default JUnit test runner.
+\Fix{
+For parallelism within a JVM (\ie, the configurations
 \SeqClassParMeth{}, \ParClassSeqMeth{}, and \ParClassParMeth{}), we
@@
 we have a queue of test classes and a pool of three threads that
-``consumes'' the next test class and spawns a JVM to run it.  Recall
-that in our setup (see Section~\ref{sec:setup}), we limited our kernel
-to use only three cores and reserved one for OS-related processes.  To
-verify that our approach satisfies the purpose of this experiment, we
-executed some subjects on Maven and compared the performance with our
-artifacts and observed insignificant differences (a fraction of
-seconds in most cases).  To assure that our experiments terminate
-(recall that deadlock or livelock could occur) we used the
-\CodeIn{timeout} command~\cite{timeout-cmd} configured to dispatch a
-\emph{kill} signal if test execution exceeds a given time
-limit. Finally, we saved each execution log and stack traces generated
-from JUnit to collect the execution time, the number of failing tests,
-and for reference to analyze and diagnose outliers in our results.
+``consumes'' the next test class and spawns a JVM to run it.}
+Recall that in our setup (see Section~\ref{sec:setup}), we limited our
+kernel to use only three cores and reserved one for OS-related
+processes.  To assure that our experiments terminate (recall that
+deadlock or livelock could occur) we used the \CodeIn{timeout}
+command~\cite{timeout-cmd} configured to dispatch a \emph{kill} signal
+if test execution exceeds a given time limit. Finally, we saved each
+execution log and stack traces generated from JUnit to collect the
+execution time, the number of failing tests, and to diagnose outliers
+in our results.
+\Jbc{Parei aqui}
 %% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de

### 2017-09-09 paper/evaluation.tex
Working on RQ7

--- 2017-09-09 paper/evaluation.tex
@@
 issues
-in the build file and non-deterministic results observed from sequential executions.
+in the build file and nondeterministic results observed from sequential executions.
 As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
@@
   projects with a very small number of tests monopolizing end-to-end
-  execution time were rare. Time most often is distributed evenly
+  execution time were rare. Time most often is distribuited evenly
   across test cases.}
@@
 
-To answer \numRQAdoptionOne{} we used projects from the \medg{} and
-\longg{} groups where parallelization can be more helpful. We used a
-dynamic and a static approach to find manifestations of
-parallelism. We discuss results obtained with these complementary
-approaches in the following.
+To answer \numRQAdoptionOne{}, we selected all projects from the \medg{} and
+\longg{} groups, \ie, projects that ran in at least one minute.  This
+set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
+looked for dynamic and static manifestations of parallelism.
+
+%% The
+%% following section report results for each of these cases.
 
@@
 same configuration, we counted only one occurrence.
-Considering
+It came as a surprise the observation that
+no project used distinct configurations in their modules. Considering
 our set of \numMedLong{} projects, we found that only
@@
 Maven process.  That decision could prevent execution of particular
-test modules. Table~\ref{tab:freqmodes-dynamic} shows the
-\numProjectsPar{} projects we identified where parallelism is enabled by default in Maven.
+test modules.
+Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
+we identified where parallelism is enabled by default in Maven.
+Column ``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.
+We note that, considering these projects, the modules that do not use
+the configuration cited use the sequential configuration \Seq{}.
+For example, three modules (=28-25) from Log4J2 use sequential
+configuration.
 \begin{wraptable}{r}{0pt}%0.525\linewidth
@@
     \label{tab:freqmodes-dynamic}
-%    \vspace{-1ex}
+    \vspace{-1ex}
 \end{wraptable}
-Column ``\emph{Subject}'' indicates the name of the project, column
-``\emph{\# of modules}'' indicates the fraction of modules containing
-tests that use the configuration of parallelism mentioned in column
-``\emph{Mode}''.
-We note that, considering these projects, the modules that do not use
-the configuration cited use the sequential configuration \Seq{}.
-For example, three modules (=28-25) from Log4J2 use sequential
-configuration. It came as a surprise the observation that
-no project used distinct configurations in their modules.
 
@@
 \label{sec:rqC-2}
-Given that the dynamic approach cannot detect parallelism manifested
-through the default
-configuration of projects, we also searched for indications of parallelism in build
+As our previous approach cannot detect parallelism in non-default
+configurations, we also looked for indication of parallelism in build
 files\Comment{ in the same sample set of \numMedLong{} projects}.  We
@@
 \emph{pom.xml} files are encapsulated in jar files or files downloaded from
-the network.  Consequently, this approach complements the
-the dynamic approach. Overall, we found \numProjectsParStatic{}
-projects manifesting parallelism with this approach.
+the network.  Consequently, this static checking is complementary to
+the dynamic checking, previously presented.
+
+This methodology founds \numProjectsParStatic{} projects.
 Compared to the set of projects listed in
@@
 That happened because these projects loaded a \emph{pom.xml} file from
-a jar file that we missed.
+a jar file that we did not check.
 Considering the static and dynamic methods together, we found a total
@@
 projects (\percEmailsProjectsAnswered{} of the total) were represented
-in those replies. \Luis{In one specific case, one developer worked in
-  multiple projects, and we consider it as a different answer.}
-Note that multiple developers on each project
+in those replies.  Note that multiple developers on each project
 received emails.  We sent the following set of questions to
@@
 
-To answer this research question, we selected ten different subjects,
+To answer this research question, we selected 20 different subjects,
 ran their test suites against all configurations described in
 Section~\ref{sec:modes}, and compared their running times and rate of
-test flakiness.  We used the sequential execution (configuration
-\emph{\Seq{}}) associated with each project as the comparison baseline
-in this experiment.  We selected subjects from the medium and long
-groups from Section~\ref{sec:rqA} and further selected their longest
-test module for testing.  The rationale for this selection was to
-obtain a diverse set of subjects exposing a wide range of running
-times (range observed 1.1m-8.2m) and number of test cases (range
-observed 54-17,513) and yet be able to run the experiment in
-reasonable time.  We ran each project on each configuration with ten
-seeds.  Overall, we needed to reran test suites 600 times, 60 times
-(10x6 configurations) on each project.  Given the low standard
-deviations observed in our measurements we consider ten seeds
-reasonable for this experiment.
+test flakiness.
+We used the sequential execution associated with each project as the
+comparison baseline in this experiment.
+We sorted the subjects by decreasing order of execution time and
+selected the first 20 projects that uses JUnit 4.7 or later.
+The rationale for this criteria was to ensure compatibility with
+parallel configuration since older versions of JUnit does not support
+parallel testing.
+We ran each project on each configuration for 10 times with with ten seeds.
+Overall, we needed to reran test suites 600 times, 60 times (10x6
+configurations) on each project.
+Given the low standard deviations observed in our measurements we
+consider ten seeds reasonable for this experiment.
 %% \Jbc{Is this
@@
 %%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
-%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
-%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
-%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
-%%  LocalWords:  Vavr SNE Urbanairship Datacube
+%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock
+%%  LocalWords:  mapdb workflow XPath

### 2017-09-09 paper/related.tex
pass on related

@@
 
+High-level parallelism \Fix{...}
+CUT~\cite{gambi-etal-issta2017} is a tool to automatically parallelize
+unit tests across a distributed environment. \Fix{...}
+CUT allows the developer to control resource allocation, and deal with
+the project specific test dependencies.
+Important to note that high-level parallelism techniques is
+complementary to test suite parallelization.
+
 Continuous Integration Services are widely used by the open-source
@@
 projects using CI is under $\sim$8.3 min~\cite{hilton-etal-ase2016}.
-
-%% \Jbc{Missing work about testing in the cloud and Jon Bell}
 

### 2017-09-09 paper/evaluation.tex
pass on RQ5

--- 2017-09-09 paper/evaluation.tex
@@
 
-To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
-subjects from our benchmark that use parallelization \emph{by default}
-(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
-with parallelization~---~configured by project owners and without
-parallelization.
-
 %% In those projects, parallelization is active without
@@
 
+To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
+subjects from our benchmark that use parallelization \emph{by default}
+(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
+of test suites with enabled parallelization, as configured by project
+developers, and without parallelization.
 Table~\ref{tab:speedup} summarizes results.
 Lines are sorted by project names.
-Columns ``\emph{Group}'' and ``\emph{Name}'' indicate, respectively,
-the group and the name of the subject.
+Columns ``\emph{Group}'' and ``\emph{Subject}'' indicate, respectively,
+the cost group and the name of the project.
 Column ``$T_s$'' shows sequential execution time and column ``$T_p$''
@@
 
-Results show that, on average, parallel execution was
-\avgSpeedup{} times faster compared to sequential execution.
-Three cases worth special attention: \CodeIn{Log4J2}, \CodeIn{Chaos},
-and \CodeIn{Takes}.
-We note that parallel execution in \CodeIn{Log4J2} was
-ineffective.  We found that Maven invokes several test modules in this
-project but the test modules that dominate execution time run
-sequentially by default. This was also the case of the highlighted
-project \CodeIn{Californium}.
-No significant speedup was observed in \CodeIn{Chaos}, a project with
-only three test classes, of which one monopolizes the bulk of test
-execution time.
-
-\begin{table}[ht!]
+\begin{table}[t!]
 \centering
@@
 \end{table}
+
+Results show that, on average, parallel execution was
+\avgSpeedup{} times faster compared to sequential execution.
+Three cases worth special attention: \CodeIn{Log4J2}, \CodeIn{Chaos},
+and \CodeIn{Takes}.
+We note that parallel execution in \CodeIn{Log4J2} was
+ineffective.  We found that Maven invokes several test modules in this
+project but the test modules that dominate execution time run
+sequentially by default. This was also the case for the highlighted
+project \CodeIn{Californium}.
+No significant speedup was observed in \CodeIn{Chaos}, a project with
+only three test classes, of which one monopolizes the bulk of test
+execution time.
 This project uses configuration \ParClassSeqMeth{}, which runs test

### 2017-09-09 paper/evaluation.tex
pass on RQ6

@@
 This experiment evaluates the impact of making a growing number of
-CPUs for testing available to the build system.  For that reason, we
-used a machine with more cores compared to the one described in
+CPUs available to the build system for testing.  For this reason, we
+used a different machine, with more cores, compared to the one described in
 Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
@@
 threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
-Tahr (64-bit version). This experiment uses configuration
-spawning a growing number of JVMs in different CPUs.  We selected
+Tahr (64-bit version). This experiment
+spawns a growing number of JVMs in different CPUs, using parallel
+configuration \emph{\ForkSeq{}}. We selected
 subject \subjectScalability{} in this experiment as it represents the
 case of a long-running test suite (see Table~\ref{tab:speedup}) with
-test cases distributed across many test classes~--~194.  Note that a
-\emph{\ForkSeq{}} as the goal is to evaluate the impact on runtime of
-test class is the smallest unit that can be used to spawn a test job
+test cases distributed across many test classes~--~194.  
+Recall that a test class is the smallest unit that can be used to spawn a test job
 on a JVM and that we have no control over which test classes will be
@@
 We ran this experiment for a growing number of cores 1, 3, ..., 39. 
-The plot shows results up to 17 cores as it is clear the tendency.
+The plot omits results beyond 17 cores as the tendency for higher
+values is clear.
 We noticed that improvements are marginal after three cores, which is
@@
       execution FC0 scales with additional cores but there is a bound
-      on the speedup one can get related to how well the test suite is
+      on the speedup that one can get related to how well the test suite is
       balanced across test classes.}

### 2017-09-09 paper/evaluation.tex
RQ7 intro

--- 2017-09-09 paper/evaluation.tex
@@
 selected the first 20 projects that uses JUnit 4.7 or later.
-The rationale for this criteria was to ensure compatibility with
+The rationale for this criteria is to ensure compatibility with
 parallel configuration since older versions of JUnit does not support
 parallel testing.
-We ran each project on each configuration for 10 times with with ten seeds.
-Overall, we needed to reran test suites 600 times, 60 times (10x6
-configurations) on each project.
-Given the low standard deviations observed in our measurements we
-consider ten seeds reasonable for this experiment.
+We ran each project on each configuration for \SubjectsReruns{} times.
+Overall, we needed to reran test suites 360 times, 18 times (3x6
+configurations) on each project.  Given the low standard deviations
+observed in our measurements and the aggregated time cost of 360 test
+executions, we consider \SubjectsReruns{} reruns reasonable for this
+experiment.
 %% \Jbc{Is this
@@
 %% run the subjects on the different parallel configurations. However,
+\Jbc{Parei aqui}
 It is worth mentioning that we used custom JUnit runners as opposed to

### 2017-09-09 paper/evaluation.tex
Adjusts on RQ7

@@
 
-To answer this research question, we selected 20 different subjects,
+To answer this research question, we selected 15 different subjects,
 ran their test suites against all configurations described in
 Section~\ref{sec:modes}, and compared their running times and rate of
-test flakiness.
-We used the sequential execution associated with each project as the
-comparison baseline in this experiment.
-We sorted the subjects by decreasing order of execution time and
-selected the first 20 projects that uses JUnit 4.7 or later.
-The rationale for this criteria is to ensure compatibility with
-parallel configuration since older versions of JUnit does not support
-parallel testing.
-We ran each project on each configuration for \SubjectsReruns{} times.
-Overall, we needed to reran test suites 360 times, 18 times (3x6
+test flakiness.  We used the sequential execution associated with each
+project as the comparison baseline in this experiment.  We sorted the
+subjects by decreasing order of execution time and selected the first
+15 projects that uses JUnit 4.7 or later.  The rationale for this
+criteria is to ensure compatibility with parallel configuration since
+older versions of JUnit does not support parallel testing.  We ran
+each project on each configuration for \SubjectsReruns{} times.
+Overall, we needed to reran test suites 270 times, 18 times (3x6
 configurations) on each project.  Given the low standard deviations
-observed in our measurements and the aggregated time cost of 360 test
+observed in our measurements and the aggregated time cost of 270 test
 executions, we consider \SubjectsReruns{} reruns reasonable for this

### 2017-09-09 paper/evaluation.tex
Fixes and added my progress mark

@@
 %% run the subjects on the different parallel configurations. However,
-\Jbc{Parei aqui}
 It is worth mentioning that we used custom JUnit runners as opposed to

### 2017-09-09 paper/evaluation.tex
updated methodology

@@
 default JUnit test runner.
-\Fix{
 For parallelism within a JVM (\ie, the configurations
@@
 configured the JUnit runner with
-ParallelComputer~\cite{junit-parallel} that internally uses a pool of
-threads with cache to run test classes and methods. For the
-configurations with forked JVMs (\ie, \ForkSeq{} and \ForkParMeth{}),
-we have a queue of test classes and a pool of three threads that
-``consumes'' the next test class and spawns a JVM to run it.}
+ParallelComputer~\cite{junit-parallel}.
+For the configurations with forked JVMs (\ie, \ForkSeq{} and
+\ForkParMeth{}), we spawn a JVM with our JUnit custom runner to
+execute a test class in an individual process. We configured this
+experiment to run at most three JVMs in parallel.
 Recall that in our setup (see Section~\ref{sec:setup}), we limited our
 kernel to use only three cores and reserved one for OS-related
-processes.  To assure that our experiments terminate (recall that
+processes.  To ensure that our experiments terminate (recall that
 deadlock or livelock could occur) we used the \CodeIn{timeout}
 command~\cite{timeout-cmd} configured to dispatch a \emph{kill} signal
-if test execution exceeds a given time limit. Finally, we saved each
+if test execution exceeds a given time limit. Finally, we save each
 execution log and stack traces generated from JUnit to collect the
@@
 in our results.
-\Jbc{Parei aqui}
 %% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
@@
 %% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
-
+\Jbc{Falta atualizar essa discussao....
 Table~\ref{tab:rq6-table} summarizes results ordered by subject's
@@
 spawning and managing JVMs and threads.
+}
 

### 2017-09-09 paper/evaluation.tex
pass on RQ7

@@
 This dimension assesses the impact of using distinct parallel
-configurations on test flakiness and speedup.  Recall that increased
-resource contention obtained with parallelism can lead to concurrency
-issues such as data races that could interfere in results of dependent
+configurations on test flakiness and speedup.  Increased parallelism
+can increase resource contention leading to concurrency issues such as
+data races across dependent
 tests~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  Flakiness and
-speedup are contradictory forces that drive configuration selection.
-Note that Section~\ref{sec:rqD} evaluated speedup in isolation.
+speedup are contradictory forces that could influence the decision of
+practitioners about which parallel configuration should be used for
+testing.  Note that Section~\ref{sec:rqD} evaluated speedup in
+isolation.
 
@@
 Section~\ref{sec:modes}, and compared their running times and rate of
-test flakiness.  We used the sequential execution associated with each
-project as the comparison baseline in this experiment.  We sorted the
-subjects by decreasing order of execution time and selected the first
-15 projects that uses JUnit 4.7 or later.  The rationale for this
+test flakiness.  We used the sequential execution configuration,
+\emph{\Seq{}}, as the comparison baseline in this experiment.  To
+select subjects, we sorted projects whose test suites run in 1m or
+more by decreasing order of execution time and selected the first
+fifteen projects that use JUnit 4.7 or later.  The rationale for this
 criteria is to ensure compatibility with parallel configuration since
@@
 It is worth mentioning that we used custom JUnit runners as opposed to
-Maven to run test suites with different parallel configurations (see
-Section~\ref{sec:modes}).
-After carefully checking library versions for compatibility issues and
-comparing results with JUnit's we observed that several of Maven's
-executions exposed problems.  For example, Maven incorrectly counts
-the number of test cases executed for some cases where test flakiness
-are observed.  These issues are categorized and documented on our
-website~\cite{ourwebpage} and can be reproduced with our scripts.
-To address those issues we implemented basic JUnit test runners (one
-for each parallel configuration), reflecting the effects of parallel
-configurations from Maven Surefire.  To write those runners we used
-Maven log files to identify test classes to run and used the Maven
-dependency plugin~\cite{maven-dep} to build the project's classpath
-with the command \CodeIn{mvn dependency:build-classpath}.
-Once we have the classpath and the tests to run, we invoke our JUnit
-custom runner to run the test classes with different parallel
-configurations. For the sequential execution, we invoke the
-default JUnit test runner.
-For parallelism within a JVM (\ie, the configurations
-\SeqClassParMeth{}, \ParClassSeqMeth{}, and \ParClassParMeth{}), we
-configured the JUnit runner with
-ParallelComputer~\cite{junit-parallel}.
-For the configurations with forked JVMs (\ie, \ForkSeq{} and
-\ForkParMeth{}), we spawn a JVM with our JUnit custom runner to
-execute a test class in an individual process. We configured this
-experiment to run at most three JVMs in parallel.
-Recall that in our setup (see Section~\ref{sec:setup}), we limited our
-kernel to use only three cores and reserved one for OS-related
-processes.  To ensure that our experiments terminate (recall that
-deadlock or livelock could occur) we used the \CodeIn{timeout}
+Maven to run the test suites with different parallel configurations
+(see Section~\ref{sec:modes}).  After carefully checking library
+versions for compatibility issues and comparing results with JUnit's
+we observed that several of Maven's executions exposed problems.  For
+example, Maven incorrectly counts the number of test cases executed
+for some cases where test flakiness are observed. These issues are
+categorized and documented on our website~\cite{ourwebpage} and can be
+reproduced with our scripts.  To address those issues we implemented
+custom test runners for configurations \emph{\SeqClassParMeth{}},
+\emph{\ParClassSeqMeth{}}, and \emph{\ParClassParMeth{}} and
+implemented a bash script that coordinates the creation of JVMs and
+invokes corresponding custom runners for configurations
+\emph{\ForkSeq{}} and \emph{\ForkParMeth{}}.  As to faithfully reflect
+Maven's behavior in our scripts, we carefully analyzed the source
+code~\cite{maven-surefire-source} of the Maven Surefire plugin. We
+implemented test runners using the ParallelComputer class from
+JUnit~\cite{junit-parallel}.
+
+%% For the sequential execution, we invoke the
+%% default JUnit test runner.
+%% For parallel execution with forked JVMs\Comment{ (\ie, \emph{\ForkSeq{}} and
+%% \emph{\ForkParMeth{}})}, we wrote bash scripts to spawn a JVM with our
+%% custom runner, mentioned above, to
+%% execute a test class in an individual process.
+
+We used Maven log files to identify test classes to run and used the
+Maven dependency plugin~\cite{maven-dep} to build the project's
+classpath (with the command \CodeIn{mvn dependency:build-classpath}).
+Once we find the tests suite to run and the corresponding classpath,
+we invoke the test runners mentioned above on them.  We configured
+this experiment to run at most three JVMs in parallel.  Recall that in
+our setup (see Section~\ref{sec:setup}), we limited our kernel to use
+only three cores and reserved one core for OS-related processes.  To
+ensure that our experiments terminate (recall that deadlock or
+livelock could occur) we used the \CodeIn{timeout}
 command~\cite{timeout-cmd} configured to dispatch a \emph{kill} signal
@@
 in our results.
+
 %% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de

### 2017-09-09 paper/evaluation.tex
pass on RQ7

@@
 configurations) on each project.  Given the low standard deviations
-observed in our measurements and the aggregated time cost of 270 test
-executions, we consider \SubjectsReruns{} reruns reasonable for this
+observed in our measurements\Comment{ and the aggregated time cost of 270 test
+executions}, we considered \SubjectsReruns{} reruns reasonable for this
 experiment.
@@
 %% run the subjects on the different parallel configurations. However,
+
 It is worth mentioning that we used custom JUnit runners as opposed to
@@
 example, Maven incorrectly counts the number of test cases executed
-for some cases where test flakiness are observed. These issues are
+for some of the cases where test flakiness are observed. These issues are
 categorized and documented on our website~\cite{ourwebpage} and can be
@@
 custom test runners for configurations \emph{\SeqClassParMeth{}},
-\emph{\ParClassSeqMeth{}}, and \emph{\ParClassParMeth{}} and
+\emph{\ParClassSeqMeth{}}, and \emph{\ParClassParMeth{}} and,  for configurations
+\emph{\ForkSeq{}} and \emph{\ForkParMeth{}}, we
 implemented a bash script that coordinates the creation of JVMs and
-invokes corresponding custom runners for configurations
-\emph{\ForkSeq{}} and \emph{\ForkParMeth{}}.  As to faithfully reflect
+invokes corresponding custom runners.  As to faithfully reflect
 Maven's behavior in our scripts, we carefully analyzed the source
 code~\cite{maven-surefire-source} of the Maven Surefire plugin. We
-implemented test runners using the ParallelComputer class from
+implemented test runners using the \CodeIn{ParallelComputer} class from
 JUnit~\cite{junit-parallel}.

### 2017-09-10 paper/related.tex
pass on related work

--- 2017-09-09 paper/related.tex
@@
 selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
-techniques are unsoud (\ie{}, they do not guarantee that
+techniques are unsound (\ie{}, they do not guarantee that
 fault-revealing tests will be considered for testing).  The test
@@
 The use of the Single Instruction Multiple Data (SIMD) design has been
-previoulsy explored in research to accelerate test
+previously explored in research to accelerate test
 execution~\cite{damorim-etal-issta2007,damorim-etal-tse2008,kim-etal-issre2012,nguyen-etal-icse2014,rajan-etal-ase2014,sen-etal-fse2015,yaneva-etal-issta2017}. The
@@
 data.  For that reason, in principle, one test could be ran
-simulteneously against multiple inputs provided that multiple test
+simultaneously against multiple inputs provided that multiple test
 inputs exist associated to that one test.  Recent
@@
 
-\Mar{can you complete this AND add text on high-level paralellism?}
+\Mar{Luis, por favor, revise$\rightarrow$}
 
-Continuous Integration Services are widely used by the open-source
-community~\cite{hilton-etal-ase2016,vasilescu-etal-fse2015}. Travis
-CI~\cite{travis} is an example of one of these services. Recent work
-by Hilton~\etal{}~\cite{hilton-etal-ase2016} showed that there is a
-high acceptance rate for CI services. The average build time for those
-projects using CI is under $\sim$8.3 min~\cite{hilton-etal-ase2016}.
+Google~\cite{google-tap,google-ci} and
+Microsoft~\cite{prasad-shulte-ieee-microsoft-ci} have been creating
+distributed infrastructures to efficiently build massive amounts of
+code and run massive amounts of tests.  Those scenarios bring
+different and challenging problems such as deciding when to trigger
+the build under multiple file
+updates~\cite{memon-etal-icse17}. Although such distributed systems
+are targeted to extremely large scale code and test bases, the same
+ideas can be applied to handle the build process of large, albeit not
+as large, projects.  For example,
+Gambi~\etal{}~\cite{gambi-etal-issta2017} recently proposed CUT, a
+tool to automatically parallelize unit tests on the cloud. CUT allows
+the developer to control resource allocation and deal with the project
+specific test dependencies.  Note that test suite parallelization is
+complementary to these high-level parallelism schemes.
 
-%% \Jbc{Missing work about testing in the cloud and Jon Bell}
+Continuous Integration (CI) services, such as Travis CI~\cite{travis},
+are becoming widely used in the open-source
+community~\cite{hilton-etal-ase2016,vasilescu-etal-fse2015}. Accelerating
+time to run tests in CI is important as to reduce the period between
+test report updates.  Test failures are more common in CI compared to
+an overnight run or a local run, for instance.  This can happen
+because of semantic merge conflicts~\cite{brun-etal-fse11}, for
+instance.  As such effect can impact developer's perception and
+tolerance towards failures, we are curious to know if developers would
+be willing to receive more frequent test reports at the expense of
+potentially increasing failure rates due to flakiness caused by
+parallelism.
 
@@
 system~\cite{souto-damorim-jss}.
-O Trabalho de Hilton et al~\cite{hilton-etal-ase2016}, embora tenha
+O Trabalho de Hilton ext al~\cite{hilton-etal-ase2016}, embora tenha
 como objetivo entender o uso de CI, mostra que existe uma demanda em
@@
 }
+
+%%  LocalWords:  Ekstazi Ekstazi's elik JVM parallelization SIMD GPUs
+%%  LocalWords:  ElectricTest parallelizing multicore CPUs SIMD's
+%%  LocalWords:  datasets Gambi parallelize

### 2017-09-10 paper/evaluation.tex
adding one-sentence explanation for RQ5
Added statistics of failures

@@
 of test suites with enabled parallelization, as configured by project
-developers, and without parallelization.
+developers, and without parallelization. It is important to note that
+there are no observed failures in either execution.
 Table~\ref{tab:speedup} summarizes results.
@@
 %% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
-\Jbc{Falta atualizar essa discussao....
 Table~\ref{tab:rq6-table} summarizes results ordered by subject's
-name. Recall that we only executed one module for each subject.
+name.
 Values are averaged across multiple executions.  We did not report
 standard deviations as they are very small in all cases.  Considering
-flakiness, results show that 0\% of flakiness have been reported in 26
-of the 60 combinations analyzed (43\% of the total) and that for seven
-of the ten projects 0\% flakiness was reported in at least one of the
-configurations.  The projects with flakiness in all configurations
-were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.
-It is worth highlighting the unfortunate case of \CodeIn{Moquette},
-which manifested more than 20\% flaky tests in every configuration.
+flakiness, we inspected a sample of 1000 logs to identify the causes
+of flakiness manifested in 45 executions. Most of the cases occurred
+by a race condition: approximately 97.5\% of the failures were caused
+by a null reference and 1.6\% were caused by concurrent access of
+unsyncronized data structures. More precisely, the manifested
+exceptions were \CodeIn{ConcurrentModificationException} (0.8\%),
+\CodeIn{NoSuchElementException} (0.7\%), and
+\CodeIn{ArrayIndexOutOfBoundsException} (0.7\%).  In addition, we
+identified 0.9\% cases of file dependencies manifested on
+\CodeIn{EOFException} (0.2\%),
+\CodeIn{FileSystemAlreadyExistsException} (0.2\%), and
+\CodeIn{BufferOverflowException} (0.4\%).
+The projects with flakiness in all configurations were \CodeIn{AWS
+SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.  It is worth
+highlighting the unfortunate case of \CodeIn{Moquette}, which
+manifested more than 20\% flaky tests in every configuration.
 Considering time, it is noticeable from the averages, perhaps as
@@
 \emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and from
-configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
-worth mentioning that some combinations manifested slowdown instead of
-speedup.  Recall that parallel execution introduces the overhead of
+configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.
+It is also worth mentioning that some combinations manifested slowdown
+instead of speedup.
+Recall that parallel execution introduces the overhead of
 spawning and managing JVMs and threads.
-}
+Overall, results show that 0\% of flakiness have been reported in 30
+of the 75 (=5x15) parallelism combinations analyzed (40\% of the
+total) and that for 11 of the 15 projects 0\% flakiness was
+reported in at least one of the configurations.
 
@@
 \textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
-  test suites of 70\% of the projects we analyzed could be run in
+  test suites of 73.33\% of the projects we analyzed could be run in
   parallel without manifesting any flaky tests.  In some of these

### 2017-09-10 paper/conclusions.tex
pass on spellchecker (make check)

@@
 capitalize on them, are widely available today.  Despite some
-resistance observed from practicioners, our results suggest that
+resistance observed from practitioners, our results suggest that
 parallelization can be done in many cases without sacrificing

### 2017-09-10 paper/intro.tex
pass on spellchecker (make check)

@@
 indicate that configurations that fork JVMs do not achieve
-speedups as high as other more-agressive configurations, but they
+speedups as high as other more-aggressive configurations, but they
 manifest much lower flakiness ratios.

### 2017-09-10 paper/evaluation.tex
pass on evaluation

--- 2017-09-09 paper/evaluation.tex
@@
 %% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
-\Jbc{Falta atualizar essa discussao....
-Table~\ref{tab:rq6-table} summarizes results ordered by subject's
-name. Recall that we only executed one module for each subject.
-Values are averaged across multiple executions.  We did not report
-standard deviations as they are very small in all cases.  Considering
-flakiness, results show that 0\% of flakiness have been reported in 26
-of the 60 combinations analyzed (43\% of the total) and that for seven
-of the ten projects 0\% flakiness was reported in at least one of the
-configurations.  The projects with flakiness in all configurations
-were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.
-It is worth highlighting the unfortunate case of \CodeIn{Moquette},
-which manifested more than 20\% flaky tests in every configuration.
-Considering time, it is noticeable from the averages, perhaps as
-expected, an increasing speedup from configuration
-\emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and from
-configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
+
+\sloppy Table~\ref{tab:rq6-table} summarizes results ordered by
+subject's name.  Values are averaged across multiple executions.  We
+did not report standard deviations as they are very small in all
+cases.  As to identify the potential causes of flakiness, we inspected
+the exceptions reported in execution logs. We found that, in most
+of the cases, flakiness was caused by race conditions: approximately
+97.5\% of the failures were caused by a \CodeInF{null} dereference and 1.6\% were
+caused by concurrent access on unsynchronized data structures.\Comment{
+  More precisely, the manifested exceptions were
+  \CodeInF{ConcurrentModificationException} (0.8\%),
+  \CodeInF{NoSuchElementException} (0.7\%), and
+  \CodeInF{ArrayIndexOutOfBoundsException} (0.7\%).}  Cases of likely
+broken test dependencies were not as prevalent as race conditions
+(0.8\% of the total): \CodeInF{EOFException} (0.2\%),
+\CodeInF{FileSystemAlreadyExistsException} (0.2\%), and
+\CodeInF{BufferOverflowException} (0.4\%). Results suggest that
+anticipating race conditions to schedule test executions would have
+higher impact compared to breaking test dependencies using a tool such
+as TestElectric~\cite{bell-etal-esecfse2015}.
+
+The projects with flakiness
+in all configurations were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and
+\CodeIn{Moquette}.  It is worth highlighting the unfortunate case of
+\CodeIn{Moquette}, which manifested more than 20\% flaky tests in
+every configuration.  Considering time, it is noticeable from the
+averages, perhaps as expected, an increasing speedup from
+configuration \emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and
+from configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
 worth mentioning that some combinations manifested slowdown instead of
 speedup.  Recall that parallel execution introduces the overhead of
-spawning and managing JVMs and threads.
-}
+spawning and managing JVMs and threads.  Overall, results show that
+0\% of flakiness have been reported in 30 of the 75 (=5x15)
+pairs of project and configuration we analyzed (40\% of the total).
+In for 4 of the 15 projects flakiness was not manifested in 
+any combination pairs.  We noticed with some surprise that the average speedup of
+configuration \emph{\SeqClassParMeth} was higher compared to
+\emph{\ForkParMeth} indicating that it is not always the case that
+using more CPUs pays off. Important to note that the cost of spawning
+new JVMs can be significant in \emph{\ForkParMeth}.
 
@@
 %%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
-%%  LocalWords:  Vavr SNE Urbanairship Datacube
+%%  LocalWords:  Vavr SNE Urbanairship Datacube dereference
+%%  LocalWords:  unsynchronized ConcurrentModificationException
+%%  LocalWords:  NoSuchElementException EOFException TestElectric
+%%  LocalWords:  ArrayIndexOutOfBoundsException
+%%  LocalWords:  FileSystemAlreadyExistsException
+%%  LocalWords:  BufferOverflowException

### 2017-09-10 paper/related.tex
syllables check
pass on related work

@@
 
-\Mar{Luis, por favor, revise$\rightarrow$}
+%% \Mar{Luis, por favor, revise$\rightarrow$}
 
@@
 Gambi~\etal{}~\cite{gambi-etal-issta2017} recently proposed CUT, a
-tool to automatically parallelize unit tests on the cloud. CUT allows
+tool to automatically parallelize JUnit tests on the cloud. The tool allows
 the developer to control resource allocation and deal with the project
@@
 time to run tests in CI is important as to reduce the period between
-test report updates.  Test failures are more common in CI compared to
-an overnight run or a local run, for instance.  This can happen
-because of semantic merge conflicts~\cite{brun-etal-fse11}, for
-instance.  As such effect can impact developer's perception and
+test report updates.  Module-level regression
+testing~\cite{vasic-etal-fse2017}, for example, can be helpful in that
+setting. It is important to note that test failures are more common in
+CI compared to an overnight run or a local run, for instance.  This
+can happen because of semantic merge conflicts~\cite{brun-etal-fse11},
+for instance.  As such effect can impact developer's perception and
 tolerance towards failures, we are curious to know if developers would
@@
 %%  LocalWords:  Ekstazi Ekstazi's elik JVM parallelization SIMD GPUs
-%%  LocalWords:  ElectricTest parallelizing multicore CPUs SIMD's
-%%  LocalWords:  datasets Gambi parallelize
+%%  LocalWords:  ElectricTest parallelizing multicore CPUs SIMD's GCC
+%%  LocalWords:  datasets Gambi parallelize JUnit

### 2017-09-10 paper/evaluation.tex
Fixed mispelling (ElectricTest, not TestElectric)

@@
 higher impact compared to breaking test dependencies using a tool such
-as TestElectric~\cite{bell-etal-esecfse2015}.
+as ElectricTest~\cite{bell-etal-esecfse2015}.
 
@@
 %%  LocalWords:  unsynchronized ConcurrentModificationException
-%%  LocalWords:  NoSuchElementException EOFException TestElectric
+%%  LocalWords:  NoSuchElementException EOFException ElectricTest
 %%  LocalWords:  ArrayIndexOutOfBoundsException

### 2017-09-10 paper/modes.tex
Removed numbers and border

@@
   escapeinside={@}{@},
-  numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+  numbers=none,xleftmargin=1em,frame=none,framexleftmargin=0.5em,
   basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
@@
 \end{lstlisting}
-  \caption{\label{fig:surefire} Configuration \ForkParMeth{} on Maven.}
+  \caption{\label{fig:surefire} Configuration \ForkParMeth{} on
+    Maven.}
+\vspace{-1ex}  
 \end{figure}
-\vspace{-2ex}
 

### 2017-09-10 paper/evaluation.tex
Fixed annoying captions (one remaining...)

@@
 
-\vspace{1ex}
 \begin{figure}[t!]
@@
     basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-  deletekeywords={true}
+    showstringspaces=false
 }
+\vspace{2mm}
 \begin{lstlisting}
@@
 the tests in offline mode as to skip the package update task, enabled
-by default (line 11). After execution, we used a regular expression on
-the output log to extract the elapsed time (line 12-14).
+by default (line 11). After that, we used a regular expression on
+the output log to find elapsed times (line 12-14).
 
@@
 \begin{wraptable}{r}{0pt}%0.525\linewidth
+
   \footnotesize
@@
     \end{tabular}
-    \caption{Subjects with parallel test execution enabled by
-    default.}
+    \caption{Subjects with parallel test execution enabled by default.}
     \label{tab:freqmodes-dynamic}
@@
 \centering
+\vspace{2mm}
+\caption{
+\label{tab:speedup}
+Speedup (or slowdown) of parallel execution ($T_p$)
+over sequential execution ($T_s$).  Default parallel configuration of
+Maven is used.  Highest slowdown/speedup appears in gray color.}
 \resizebox{.41\textwidth}{!}{%
@@
 \bottomrule%
-\vspace{-5ex}
 \end{tabular}}
-\caption{\label{tab:speedup}Speedup (or slowdown) of parallel
-  execution ($T_p$) over sequential execution ($T_s$).  Default
-  parallel configuration of Maven is used.  Highest slowdown/speedup
-  appears in gray color.}
+\vspace{-4ex}
 \end{table}

### 2017-10-13 paper/evaluation.tex
Pre-print version
Fixed overwritten latex rules

@@
-\section{Objects of Analysis}
-\label{sec:subjects}
-
-We used \github{}'s search API~\cite{githubsearch} to identify
-projects that satisfy the following criteria: (1) the primary language
-is Java\footnote{In case of projects in multiple languages, the
-  \github{} API considers the predominant language as the primary
-  language.}, (2) the project has at least 100 stars, (3) the latest
-update was on or after January 1st, 2016, and (4) the \emph{readme}
-file contains the string \emph{mvn}.  We focused on Java for its
-popularity.  Although there is no clearcut limit on the number of
-\github{} stars~\cite{github-stars} to define relevant projects, we
-observed that one hundred stars was enough to eliminate trivial subjects. The third
-criteria serves to skip projects without recent activity. The fourth
-criteria is an approximation to find Maven projects.\Comment{ The
-  rationale is that if the string \emph{mvn} exists in the
-  \emph{readme} file, it may represent a Maven call (\eg, to compile
-or to test the project).} We focused on Maven for its popularity on
-Java projects.  Important to highlight that, as of now, the
-\github{}'s search API can only reflect contents from repository
-statistics (\eg, number of forks, main programming language); it does
-not provide a feature to search for projects containing certain files
-(\eg{}, \emph{pom.xml}) in the directory structure.
-Figure~\ref{fig:subject-query} illustrates the query to the \github{}
-API as an HTTP request.   The result set is sorted
-in descending order of stars.
-
-\begin{figure}[t!]
-\centering
-\scriptsize
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    showstringspaces=false
-}
-\vspace{2mm}
-\begin{lstlisting}
-https://api.github.com/search/repositories?q=language:java
- +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
-\end{lstlisting}
-  \caption{\label{fig:subject-query} Query to the \github{} API for
-  projects that (1) use Java, (2) contains at least 100
-  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
-  the string \emph{mvn} in the \emph{readme} file.}
-  \vspace{-5ex}  
-\end{figure}
-
-We used the following methodology to select projects for
-analysis. After obtaining the list of potential projects from GitHub, we filtered those
-containing a \pomf{} file in the root directory.\Comment{  A Maven project may
-contain several sub-modules with multiple \pomf{} files.}
-Then, considering this set of Maven projects, we
-executed the tests for \SubjectsReruns{} times to discard those projects with
-issues
-in the build file and non-deterministic results observed from sequential executions.
-As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
-subjects.
-From this set of projects,
-\SubjectsGithubNotMaven{} projects were not Maven or did not have a
-\pomf{} in the root directory, 
-\SubjectsGithubNotTestable{} projects were not considered because of
-environment incompatibility
-(\eg, missing\Comment{ required web browser or database management system}~DBMS),
-\SubjectsGithubFlaky{} projects were discarded because of
-``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes or fails under
-the same circumstances leading to non-deterministic results.
-As some of our experiments consist of running tests on different
-threads, we ignored these projects as it would be impractical
-to identify whether a test failed due to a race condition or some
-other source of flakiness.
-From the remaining \SubjectsGithubConsistant{} projects with
-deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
-projects with \SuiteFailingThreshold{} or more failing tests as to
-reduce bias. For the
-remaining projects with failing tests, we used the JUnit's
-\CodeIn{@Ignore} annotation to ignore failing tests.
-Our final set of subjects contains \numSubjs{} projects.
-Figure~\ref{fig:subjects} summarizes our sample set.
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
-  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
-  hosted on \github{}. From this initial sample, we ignored
-  \SubjectsGithubNotMaven{} projects without Maven support,
-  \SubjectsGithubNotTestable{} with missing dependencies,
-  \SubjectsGithubFlaky{} projects with flaky tests, and
-  \SubjectsGithubTooManyFailures{} projects had at least
-  \SuiteFailingThreshold{} of failing tests. We considered
-  \numSubjs{} projects to conduct our study.}
-  \vspace{-1ex}
-\end{figure}
-
-%\subsection{Setup and Replication}
+\section{Setup and Replication}
 \label{sec:setup}
 
-To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
-processor machine with eight virtual CPUs (four cores with two native
-threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
-(64-bit version).  We used\Comment{ Git,} Java 8 and Maven
-3.3.9 to build projects and run test suites. To
-process test results and generate plots
-we used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are
-publicly available for replication on our website~\cite{ourwebpage}.
-This includes supporting scripts\Comment{ (\eg, the scripts to run the tests
-and generate raw analysis data)} and the full list of projects.
+To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
+machine with eight virtual CPUs (four cores with two native threads each) and
+16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
+used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
+suites. To process test results and generate plots we used Python\Comment{ 3.4},
+Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
+replication on our website~\cite{ourwebpage}.  This includes supporting
+scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
+data)} and the full list of projects.
 
@@
 \label{sec:eval}
-
-%% We are interested in understanding the prevalence of time-consuming
-%% test suites and main sources of execution cost. We want to understand
-%% how the execution cost is distributed on test cases within a test
-%% suite and how developers approach test execution. Based on that, we
-%% study parallelization of testing frameworks and build systems.  More
-%% precisely, we investigate how prevalent test parallelization is, the
-%% potential for improving execution cost, issues of flakiness that
-%% hinders the use of parallelization, and how to address those issues.
-%% More specifically, we pose the following research questions:
-
-%% The first research question addresses the prevalence of long-running
-%% test suites. We are interested to know if costly test suites are
-%% common in open-source projects.  The second research question
-%% addresses the relationship of test cases and the overall execution
-%% cost: we are interested to investigate how the execution time is
-%% distributed among test cases.  In the third research question, we
-%% investigate if developers consider low-level parallelism features
-%% available out-of-the-box to amortize test execution (see
-%% Section~\ref{sec:modes}). In addition, we want to identify what
-%% configurations are often used and why they are more popular (if any).
-%% The fourth research question addresses the impact of low-level
-%% parallelism on test execution from projects in our sample set. We want
-%% to identify subjects that already use test parallelization and compare
-%% their performance in contrast to sequential execution. In addition, we
-%% are interested in evaluating the performance of sequential test suites
-%% with different parallelization settings.
-%% Finally, the fifth research question discusses the limitations and
-%% insights to overcome the pitfalls of parallelization.
-
-%% \Comment{
-%%     \Fix{distribution of execution time per test case. For each subject
-%%     identified in the first research question, we investigate how
-%%     balanced is the cost of the test suite in contrast to the cost of
-%%     test cases and if there are subjects where the time cost is mostly
-%%     dominated by a small fraction of test cases.} \Fix{The third research
-%%     question addresses the distribution of regression tests according
-%%     to the use of computational resources.  We are interested in
-%%     investigating if regression test suites are CPU intensive and if there
-%%     are opportunities to improve performance. The RQ4 addresses}
-%%     \Fix{...elaborate...}
-
-%%     The rationale is that if the time cost of a regression test is equally
-%%     distributed among test cases, the execution cost could be potentially
-%%     improved by running tests in parallel (in contrast to the scenario
-%%     where only one test case dominates most of the execution time).
-%% }
 
@@
 
-%%\newcommand{\RQFeasibilityTwo}{What is the distribution of CPU and IO bound
-%%regression test suites from the sample set?}
-%%
-%%\newcommand{\RQAdoptionOne}{How uniformly distributed is the execution time
-%%across test cases in costly projects?}
-%%
-%%\newcommand{\RQAdoptionTwo}{How often developers use the parallelism features
-%%from build systems to improve runtime performance?}
-
 \subsection{Feasibility}
@@
 
+\begin{figure}[ht]%
+  \centering
+  \subfigure[\label{fig:rq1-barplot}]{
+  \includegraphics[height=4cm,width=3cm]{results/barplot-timecost.pdf}
+  }
+  \qquad
+  \subfigure[\label{fig:rq1-boxplot}]{
+    \includegraphics[height=4cm,width=4.2cm]{results/boxplot-timecost.pdf}
+  }%
+  \caption{(a)\Comment{ Testing time grouped by time cost ($t$): short run
+    ($t<1m$), medium run ($1m \le t < 5m$), and long run ($5m \le{}
+    t$);}~Number of projects in each cost group and
+    (b)~Distribution of running times per cost group.}
+\vspace{-5mm}
+\end{figure}
+
 \Comment{We followed a similar methodology to group projects by time as
@@
 
-\begin{figure}[ht]
-  \centering
-  \begin{subfigure}{0.182\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{results/barplot-timecost.pdf}
-    \caption{\label{fig:rq1-barplot}}
-  \end{subfigure}%
-  \hfill
-  \begin{subfigure}{0.25\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{results/boxplot-timecost.pdf}
-    \caption{\label{fig:rq1-boxplot}}
-  \end{subfigure}%
-  \caption{(a)\Comment{ Testing time grouped by time cost ($t$): short run
-    ($t<1m$), medium run ($1m \le t < 5m$), and long run ($5m \le{}
-    t$);}~Number of projects in each cost group and
-    (b)~Distribution of running times per cost group.}
-  \vspace{-1ex}
-\end{figure}
-
 It is important to note that we under-estimated running times as we missed test modules not enabled for
@@
 only the tests executed by default.
-\Comment{
-Although failing tests may introduce noise in our measurements, we
-carefully eliminated subjects with more than \SuiteFailingThreshold{} of
-test failures. 
-}
 From the \numSubjs{} testable projects, \numSubjsPass{} successfully
@@
   \caption{\label{fig:time-distributions}Distribution of test case time per project.}%
-  \vspace{-3ex}
+  \vspace{-5mm}
 \end{figure}
@@
 test method is the smallest working unit in test frameworks.
-%% However, avoiding
-%% frequent context switches is another factor to consider.  For example,
-%% assuming there are at least two CPUs available for execution, cost can
-%% be cut in half if two tests in a large test suite dominate execution
-%% time and these tests are assigned to different CPUs.
-%% It is therefore important to
-%% speedup regressing testing in open-source projects.\Comment{not only
-%%   to huge projects as those from Google~\cite{google-tap,google-ci}
-%%   and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
-%% For the case
-%% where cost is distributed more evenly across test cases, one expects
-%% that speedups will be a function of the number of cores.
-%% These contradictory forces, pushing number of tests and cost
-%% of each test up and down, make prediction of effectiveness challenging.
 Figure~\ref{fig:time-distributions} shows the time distribution of
@@
 
+\begin{figure}[t!]%
+  \centering
+  \subfigure[\label{fig:size-testsuites}]{
+  \includegraphics[height=4.25cm, width=2.1cm]{results/boxplots-testcases.pdf}
+  }
+  \qquad
+  \subfigure[\label{fig:scattercost}]{
+    \includegraphics[height=4.25cm]{results/scatter-testcost.pdf}
+  }%
+  \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
+    Size versus running time of test suites.}%
+  \vspace{-5mm}
+\end{figure}
+
 Figure~\ref{fig:size-testsuites} shows the difference in the
 distribution of test suite sizes across groups.  This figure indicates
-that long projects have a higher median and much higher average
-number of test cases.
+that long projects have a higher median and much higher average number of test cases.
 Furthermore, we noted a strong positive correlation between running
@@
 
-%% Figure~\ref{fig:time-distributions} shows that the average median
-%% times are similar for \medg{} and \longg{}-running test suites.
-
 \begin{center}
@@
 }
-\begin{figure}[h!]
-  \centering
-  \begin{subfigure}{0.13\textwidth}
-    \centering
-    \includegraphics[width=.9\textwidth]{results/boxplots-testcases.pdf}
-    \caption{\label{fig:size-testsuites}}
-  \end{subfigure}
-  \hspace{3ex}
-  \begin{subfigure}{0.28\textwidth}
-    \centering
-    \includegraphics[width=.9\textwidth]{results/scatter-testcost.pdf}
-    \caption{\label{fig:scattercost}}
-  \end{subfigure}
-  \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
-    Size versus running time of test suites.}%
-\end{figure}
 \end{center}
-
-%% We are interested to know whether
-%% most of the execution cost of a subject is dominated by a small subset
-%% of test cases or if the cost is nearly equally distributed.
-
-%% We also evaluated the dispersion of time distributions (one
-%% distribution per project) to answer research question \numRQFeasibilityTwo{}.  To
-%% measure dispersion \emph{across} projects we used Relative Standard
-%% Deviation (RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were
-%% to analyze each project in isolation, the standard deviation of a
-%% distribution ($\sigma$) would suffice to quantify how dispersed the
-%% (time) distribution is.  However, in our case, we would like to be
-%% able to compare and summarize dispersion across projects.  The RSD,
-%% which is obtained dividing the standard deviation by the mean ($\mu$)
-%% of a distribution, provides such normalization effect.  This metric
-%% provides a lower bound (zero) but not an upper bound (somewhere close
-%% to 1).  The smaller (larger) the value of RSD the more (less) uniform
-%% the distribution is.  Consequently, the lower the value of RSD the
-%% more parallelizable a test suite should be.
-
-%% \begin{figure}[h!]
-%%   \centering
-%%   \includegraphics[width=0.5\textwidth]{R/testcost.pdf}  
-%%   \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
-%%     across projects.}
-%% \end{figure}
-
-%% Figure~\ref{fig:relativesd} shows the distribution of RSD across
-%% medium and long-running projects.  Results show that the distribution
-%% is skewed to the right indicating that test costs are relatively well
-%% distributed in most costly projects we analyzed \Fix{$\leftarrow$
-%%   confirm}.
-
-%% analyzed the execution time
-%% for the \numMedLong{} projects from the \longg{} and \medg{} groups
-%% (see Section~\ref{sec:rqA}).
-%% For each subject we calculated the
-%% relative standard deviation of the test cases: we collected the
-%% elapsed time of each individual test, calculated the standard
-%% deviation, and divided by the mean. \Jbc{I need to clarify the
-%%   relationship "well/bad-balanced" regression test and relative
-%%   standard deviation}
-
-%% Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
-%% different groups of subjects}\Fix{TODO: collect data + compute the
-%% statistic, create a scatter plot to identify groups of subjects}
-
-%% Regression tests that are well distributed may benefit from
-%% parallelism since more tests executes at the same time while the
-%% opposite scenario may require a different approach. In the later
-%% scenario, executing tests in parallel may have insignificant impact
-%% since a small subset of test cases dominates the execution.}
 
@@
 
-%% Commented as we don't follow this pattern on the other RQs
-\Comment{
-Adoption concerns with the popularity of  parallelization schemes and
-(\numRQAdoptionTwo) how developers involved in costly projects, not
-using parallelization, perceive this technology.
-}
 \begin{itemize}
@@
 
-\vspace{1ex}
 \subsubsection{Dynamic checking}
@@
 \numProjectsPar{} projects we identified where parallelism is enabled by default in Maven.
-\begin{wraptable}{r}{0pt}%0.525\linewidth
 
+Column ``\emph{Subject}'' indicates the name of the project, column
+\begin{wraptable}{r}{5cm}
+\caption{Subjects with parallel test execution enabled by default.}
+\label{tab:freqmodes-dynamic}
 \footnotesize
@@
 \end{tabular}
-    \caption{Subjects with parallel test execution enabled by default.}
-    \label{tab:freqmodes-dynamic}
-%    \vspace{-1ex}
 \end{wraptable}
-Column ``\emph{Subject}'' indicates the name of the project, column
 ``\emph{\# of modules}'' indicates the fraction of modules containing
@@
 
-\vspace{1ex}
 \begin{center}
@@
 \end{center}
-\vspace{1ex}
 
@@
 \end{enumerate}
-%% \begin{enumerate}
-%% 	\item How long does it take for test to run in your
-%%		environment?
-%%	\item Can you briefly define your setup?
-%%	\item Do you confirm that your project does not run in
-%%		parallel?
-%%	\item Select a reason for not using paralellization:
-%%		\begin{enumarate}
-%%			\item I did not know it was possible;
-%%			\item I was concerned with concurrency issues;
-%%			\item I use a continuous integration server;
-%%			\item Some other reason.
-%%		\end{enumerate}
-%% \end{enumerate}
-%% One of the goals of the first questions is to identify potential
-%% discrepancies between our experimental environment and the environment
-%% of developers.  Overall, we found that \Fix{...}
 
@@
 low-level test suite parallelization.
-% \emailsNotDescribed{} developers did not described their environment.
 
@@
 practical adoption of parallelization (\numRQAdoptionOne{}).
-%% , one runs a manually created Thread to run some
-%% tests, and the other runs in parallel by using Java 8 collection
-%% streams, that allows the developers to iterate over a list in
-%% parallel.
-%% did not confirmed, however,
-%% the developers confirmed the need of an extra parameter at the command
-%% line to execute in parallel.
 
@@
 \end{itemize}
-
-%% In those projects, parallelization is active without
-%% passing any extra parameters.  Section~\ref{sec:rqC-1} describes in
-%% detail the methodology we used to find these subjects.
-%and
-%Section~\ref{seq:rq6-tradeoffs}, we verified that both
-%% executions produce the same outcome to eliminate noise from failing
-%% tests.  To compute the speedup, we divide the time obtained in the
-%% sequential execution by the time obtained from the default execution.
-%% For instance, if a project runs the tests sequentially in $10m$ and
-%% the same execution runs in $5m$ with parallelization enabled (default
-%% execution), the speedup is two.
 
@@
 \centering
-\vspace{2mm}
 \caption{
@@
 Maven is used.  Highest slowdown/speedup appears in gray color.}
-\resizebox{.41\textwidth}{!}{%
-  \scriptsize
+%\resizebox{.41\textwidth}{!}{%
+%  \scriptsize
 \begin{tabular}{llrrr}
@@
 \midrule
-\textbf{average} &  &  &  & \avgSpeedup{}x\\
+Average &  &  &  & \avgSpeedup{}x\\
 \bottomrule%
-\end{tabular}}
-\vspace{-4ex}
+\end{tabular}
 \end{table}
@@
 
-%% The third, runs parallel configuration in
-%% \Fix{80\%} of the project modules, however, the test time is dominated
-%% by one of the sequentially running modules.  \Luis{$\leftarrow$ rework
-%%   this} \Fix{falar sobre o resultado geral dos speedups - elaborar
-%%   menor e maior speedup... acho que so vale a pena discutir quando
-%%   tiver conviccao dos 2 casos}
 \begin{center}
-\vspace{1ex}
 \fbox{
@@
 \begin{wrapfigure}{r}{0.23\textwidth}
-  \vspace{-1ex}
   \includegraphics[width=0.23\textwidth]{R/scalability/scalability.pdf}
   \caption{\label{fig:scalability}Scalability.}
-  \vspace{-2ex}
 \end{wrapfigure}
@@
 \label{sec:rq6-tradeoffs}
-
-%%  We are
-%% interested in understanding how efficiency (\ie, testing cost) and
-%% flakiness (\ie, failing tests) are affected when we run a test suite
-%% with different parallel configurations.
 
@@
 \end{itemize}
-
-%% The intuition is that efficiency and flakiness are inversely
-%% proportional in some cases: if too many tests depends on the state of
-%% a single external resource, several tests are likely to fail as the
-%% degree of concurrency increases by exploiting maximum CPU usage.
 
@@
 experiment.
-%% \Jbc{Is this
-%%   legit/acceptable/convincing?  $\rightarrow$}The rationale for this
-%% criteria was to maximize the diversity of domains from the subjects,
-%% assuming these subjects have test suites with different
-%% characteristics (\eg, architectural design and rate of cpu/io-bound
-%% operations).
-%% Notice that with parallelism enabled, the
-%% number of failing tests may vary on different runs due to the
-%% non-deterministic scheduling of threads and processes.  For that
-%% reason, we re-executed the experiment and computed the average speedup
-%% and flakiness on each scenario.
-%%    The rationale for this selection criteria was to maximize the chances
-%%    of observing speedup and flakiness, assuming that long-running tests
-%%    also have many tests. Indeed, we confirmed that test suites in these
-%%    projects contain at least 236 tests ($1,662.7$ in average).
-%% 
-%% In a first attempt of this experiment, we considered using Maven to
-%% run the subjects on the different parallel configurations. However,
 
@@
 
-%% For the sequential execution, we invoke the
-%% default JUnit test runner.
-%% For parallel execution with forked JVMs\Comment{ (\ie, \emph{\ForkSeq{}} and
-%% \emph{\ForkParMeth{}})}, we wrote bash scripts to spawn a JVM with our
-%% custom runner, mentioned above, to
-%% execute a test class in an individual process.
-
 We used Maven log files to identify test classes to run and used the
@@
 in our results.
-
-%% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
-%% jvm - maven surefire nao tratava algumas exceptions que aconteciam na
-%% execucao do teste, (3) timeout}
-%% The script we implemented to measure time and flakiness takes a list
-%% of tests classes to run as input and outputs the results (\ie, number
-%% of test methods, failures, skips, and elapsed time) for each parallel
-%% configuration.
-%%\Comment{ To obtain parallel configurations, we implemented a script
-%%  that takes a subject and a configuration label as inputs (\eg
-%%  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
-%%  the subject with the desired configuration. The workflow consists in
-%%  copying the project directory to a new directory, finding all
-%%  existing build files (\ie, \pomf{} files), and modifying all
-%%  existing Maven Surefire configurations with new values for the
-%%  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
-%%  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
-%%  manipulate XML documents. For configurations with forked JVMs
-%%  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
-%%  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
-%%  core).  To adjust the pool of threads for parallelism within a JVM,
-%%  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
-%%    consider 2 as it is the number of native threads per core OR 6 as
-%%    it represents 3 Cores * 2 native threads?}.To run the subjects and
-%%  their respective variations (\ie, the modified versions according to
-%%  the parallelism configuration), we used a similar approach as
-%%  described in Figure~\ref{fig:mvn-execution} except that...  }
-%% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /
-%% T_{\text{p}}$), and for flakiness, we reported the rate of failing
-%% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
 
@@
 
-%% \Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
-%% dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
-%% Possivelmente o slowdown se deve ao tempo de resposta do servico quando
-%% a autentiticao falha}
-
 %%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th

### 2017-10-13 paper/modes.tex
Fixed overwritten latex rules

@@
   \caption{\label{fig:levels}Levels of parallelism.}
-  \vspace{-2ex}
 \end{wrapfigure}
@@
 
-%% The configuration \Seq{} is a proper fit for short-running test suites
-%% since this is the default configuration and the execution provides
-%% feedback in an acceptable time. However, for costly suites, it is
-%% impractical for developers to wait long-running executions to take
-%% action.  In this scenario, the remaining configuration may help to
-%% amortize the execution cost depending on how the test suite was
-%% designed. For instance,
-
-Notice that an important aspect in deciding which configuration to use
-(or in designing new test suites) is the possibility of race
-conditions on shared data during execution.  Data sharing can occur,
-for example, through state that is reachable from statically-declared variables in
-the program or through variables declared within the scope of the test
-class or even through resources available on the file system and the network~\cite{luo-etal-fse2014}.  Considering data race avoidance,
-configuration \SeqClassParMeth{} is preferable over \ParClassSeqMeth{}
-when it is clear that test methods in a class do not manipulate shared
-state, which can be challenging to
-determine~\cite{bell-etal-esecfse2015}.  Similarly, \ParClassSeqMeth{}
-is preferable over \SeqClassParMeth{} when it is clear that several
-test methods in a class perform operations involving shared data.
-Configuration \ParClassParMeth{} does not restrict scheduling
-orderings.  Consequently, it is more likely to manifest data races
-during execution. Note that speedups depend on several factors,
-including the test suite size and distribution of test methods per
-class.
+Notice that an important aspect in deciding which configuration to use (or in
+designing new test suites) is the possibility of race conditions on shared data
+during execution.  Data sharing can occur, for example, through state that is
+reachable from statically-declared variables in the program or through variables
+declared within the scope of the test class or even through resources available
+on the file system and the network~\cite{luo-etal-fse2014}.  Considering data
+race avoidance, configuration \SeqClassParMeth{} is preferable over
+\ParClassSeqMeth{} when it is clear that test methods in a class do not
+manipulate shared state, which can be challenging to
+determine~\cite{bell-etal-esecfse2015}.  Similarly, \ParClassSeqMeth{} is
+preferable over \SeqClassParMeth{} when it is clear that several test methods in
+a class perform operations involving shared data.  Configuration
+\ParClassParMeth{} does not restrict scheduling orderings.  Consequently, it is
+more likely to manifest data races during execution. Note that speedups depend
+on several factors, including the test suite size and distribution of test
+methods per class.
 
@@
 }
+\vspace{-4ex}
 \begin{lstlisting}
@@
 \end{lstlisting}
+  \vspace{-4ex}
   \caption{\label{fig:surefire} Configuration \ForkParMeth{} on
     Maven.}
-\vspace{-1ex}  
 \end{figure}

### 2017-10-13 paper/evaluation.tex
added missing tex file

@@
-\section{Setup and Replication}
-\label{sec:setup}
-
-To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
-machine with eight virtual CPUs (four cores with two native threads each) and
-16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
-used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
-suites. To process test results and generate plots we used Python\Comment{ 3.4},
-Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
-replication on our website~\cite{ourwebpage}.  This includes supporting
-scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
-data)} and the full list of projects.
-
 \section{Evaluation}

### 2017-10-13 paper/subjects.tex
added missing tex file

\section{Objects of Analysis}
\label{sec:subjects}

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The
third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.   The result set is sorted
in descending order of stars.

\begin{figure}[t!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
 +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
\end{lstlisting}
  \caption{\label{fig:subject-query} Query to the \github{} API for
  projects that (1) use Java, (2) contains at least 100
  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
  the string \emph{mvn} in the \emph{readme} file.}
  \vspace{-5mm}
\end{figure}

We used the following methodology to select projects for
analysis. After obtaining the list of potential projects from GitHub, we
filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential
executions.
As of August 25th 2017, our search criteria returned a total of
\SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management
system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \vspace{-2mm}
  \centering
  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

\label{sec:setup}
To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
machine with eight virtual CPUs (four cores with two native threads each) and
16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
suites. To process test results and generate plots we used Python\Comment{ 3.4},
Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
replication on our website~\cite{ourwebpage}.  This includes supporting
scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
data)} and the full list of projects.

### 2017-10-13 paper/evaluation.tex
Updated files

@@
 \begin{figure}[ht]%
+  \vspace{-3mm}
   \centering
@@
   }%
+  \vspace{-2mm}
   \caption{(a)\Comment{ Testing time grouped by time cost ($t$): short run
@@
 have more than 5\% of failing tests (7.3\% on average).
-\begin{center}
-\fbox{
-\begin{minipage}{8cm}
-  \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
+\begin{mdframed}
+\noindent\textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
     time-consuming test suites are relatively frequent in
@@
       (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
-\end{minipage}
-}
-\end{center}
+\end{mdframed}
 
@@
   \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
+  \vspace{-2mm}
   \caption{\label{fig:time-distributions}Distribution of test case time per project.}%
@@
   }%
+  \vspace{-2mm}
   \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
@@
 
-\begin{center}
-\fbox{
-\begin{minipage}{8cm}
-  \textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
+\begin{mdframed}
+  \noindent\textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
   projects with a very small number of tests monopolizing end-to-end
@@
   across test cases.}
-\end{minipage}
-}
-\end{center}
+\end{mdframed}
 
@@
 \begin{wraptable}{r}{5cm}
+\vspace{-4mm}
 \caption{Subjects with parallel test execution enabled by default.}
@@
 
-\begin{center}
-\fbox{
-\begin{minipage}{8cm}
-  \textit{Answering \numRQAdoptionOne{}:}~\emph{Results indicate that test
+\begin{mdframed}
+  \noindent\textit{Answering \numRQAdoptionOne{}:}~\emph{Results indicate that test
   suite parallelization is underused.  Overall, only
@@
   use parallelism.}
-\end{minipage}
-}
-\end{center}
+\end{mdframed}
 
@@
 answered the survey did not know that parallelism was available in
+\begin{wrapfigure}{r}{0.13\textwidth}
+%\begin{figure}[b]
+  \centering
+  \includegraphics[width=2cm]{results/survey.pdf}
+  \caption{\label{fig:rq5-answers}Summary of developer's answers to
+    survey question~\ref{questionThree}.}
+\end{wrapfigure}
 Maven (option ``a''), \emailsB{} of developers mentioned that they did
@@
 suffices to provide timely feedback while running only smoke
-\begin{wrapfigure}{r}{0.15\textwidth}
-    \centering
-    \includegraphics[width=.15\textwidth]{results/survey.pdf}
-    \caption{\label{fig:rq5-answers}Summary of developer's answers to
-      survey question~\ref{questionThree}.}
-\end{wrapfigure}
 tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
@@
 
-\begin{center}
-\fbox{
-\begin{minipage}{8cm}
-  \textit{Answering \numRQAdoptionTwo{}:}~\emph{Results suggest that dealing
+\begin{mdframed}
+\noindent\textit{Answering \numRQAdoptionTwo{}:}~\emph{Results suggest that dealing
   with concurrency issues (\ie{}, the extra work to organize test
@@
   unfamiliarity with the technology.}
-\end{minipage}
-}
-\end{center}
+\end{mdframed}
 
@@
 indicates slowdown.
-
-\begin{table}[t!]
-\centering
-\caption{
-\label{tab:speedup}
-Speedup (or slowdown) of parallel execution ($T_p$)
-over sequential execution ($T_s$).  Default parallel configuration of
-Maven is used.  Highest slowdown/speedup appears in gray color.}
-%\resizebox{.41\textwidth}{!}{%
-%  \scriptsize
-\begin{tabular}{llrrr}
-\toprule
-\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
-\midrule%
-Medium & Californium & 1.45m & 1.40m & \cellcolor{lightgray}1.04x\\%
-Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
-Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
-Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
-Medium &Javaslang& 2.18m & 1.82m & 1.20x\\%
-Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & 9.20x\\%
-Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
-Long & \Comment{apache} Mahout & 27.38m & 18.15m & 1.51x\\%
-Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
-Medium & \Comment{apache} OpenNLP & 1.30m & 0.55m & 2.36x\\%
-Medium & \Comment{yegor256} Rultor & 2.30m & 0.27m & 8.52x\\%
-Medium & \Comment{yegor256} Takes & 2.00m & 0.19m & \cellcolor{lightgray}10.53x\\%
-Long & \Comment{vavr-io} Vavr & 3.26m & 2.25m & 1.45x\\%
-\midrule
-Average &  &  &  & \avgSpeedup{}x\\
-\bottomrule%
-\end{tabular}
-\end{table}
 
@@
 
-\begin{center}
-\fbox{
-  \begin{minipage}{8cm}
-    \textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
+\begin{table}[t!]
+\centering
+\caption{
+\label{tab:speedup}
+Speedup (or slowdown) of parallel execution ($T_p$)
+over sequential execution ($T_s$).  Default parallel configuration of
+Maven is used.  Highest slowdown/speedup appears in gray color.}
+\resizebox{.41\textwidth}{!}{%
+%  \scriptsize
+\begin{tabular}{llrrr}
+\toprule
+\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
+\midrule%
+Medium & Californium & 1.45m & 1.40m & \cellcolor{lightgray}1.04x\\%
+Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
+Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
+Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
+Medium &Javaslang& 2.18m & 1.82m & 1.20x\\%
+Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & 9.20x\\%
+Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
+Long & \Comment{apache} Mahout & 27.38m & 18.15m & 1.51x\\%
+Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
+Medium & \Comment{apache} OpenNLP & 1.30m & 0.55m & 2.36x\\%
+Medium & \Comment{yegor256} Rultor & 2.30m & 0.27m & 8.52x\\%
+Medium & \Comment{yegor256} Takes & 2.00m & 0.19m & \cellcolor{lightgray}10.53x\\%
+Long & \Comment{vavr-io} Vavr & 3.26m & 2.25m & 1.45x\\%
+\midrule
+Average &  &  &  & \avgSpeedup{}x\\
+\bottomrule%
+\end{tabular}
+}
+\end{table}
+
+\begin{mdframed}
+ \noindent\textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
   machine setup we used, the average speedup observed with default
-      configurations of parallelization was \avgSpeedup{}x.
-      }
-  \end{minipage}
-}
-\end{center}
+  configurations of parallelization was \avgSpeedup{}x.}
+\end{mdframed}
 
@@
 subject \subjectScalability{} in this experiment as it represents the
+\begin{wrapfigure}{r}{0.23\textwidth}
+  \includegraphics[width=0.23\textwidth]{R/scalability/scalability.pdf}
+  \caption{\label{fig:scalability}Scalability.}
+  \vspace{-4mm}
+\end{wrapfigure}
 case of a long-running test suite (see Table~\ref{tab:speedup}) with
@@
 We noticed that improvements are marginal after three cores, which is
-\begin{wrapfigure}{r}{0.23\textwidth}
-  \includegraphics[width=0.23\textwidth]{R/scalability/scalability.pdf}
-  \caption{\label{fig:scalability}Scalability.}
-\end{wrapfigure}
 the basic setup we used in other experiments.
@@
 
-\begin{center}
-\fbox{
-  \begin{minipage}{8cm}
-    \textit{Answering \numRQSpeedupTwo{}:}~\emph{Results suggest that
+\begin{mdframed}
+\noindent\textit{Answering \numRQSpeedupTwo{}:}~\emph{Results suggest that
   execution FC0 scales with additional cores but there is a bound
@@
   balanced across test classes.}
-  \end{minipage}
-}
-\end{center}
+\end{mdframed}
 
@@
 
-\begin{center}
-\fbox{
-\begin{minipage}{8cm}
-\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
+\begin{mdframed}
+\noindent\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
   test suites of 73.33\% of the projects we analyzed could be run in
@@
   cases, speedups were significant, ranging from 1x to 28.8x.}
-\end{minipage}
-}
-\end{center}
+\end{mdframed}
 

### 2017-11-21 ase17/conclusions.tex
Renamed dir of ASE'17 paper to a proper name

--- 2017-09-10 paper/conclusions.tex
@@
 and impact of test execution parallelization in open-source projects.
-Multicore CPUs, as well as testing frameworks and build systems to
-capitalize on them, are widely available today.  Despite some
-resistance observed from practitioners, our results suggest that
-parallelization can be done in many cases without sacrificing
-reliability and more research needs to be done to improve automation
-(\eg{}, breaking test dependencies and refactoring test suites) as to
-safely optimize parallel execution.  The artifacts we produced as
-result of this study are available from the following web
-page \webpage{}.
+Multicore CPUs are widely available today.  Testing frameworks and
+build systems that capitalize on these machines also became popular.
+Despite some resistance observed from practitioners, our results
+suggest that parallelization can be used in many cases without
+sacrificing reliability. More research needs to be done to improve
+automation (\eg{}, breaking test dependencies, refactoring test
+suites, enforcing safe test schedules) as to safely optimize parallel
+execution.  The artifacts we produced as result of this study are
+available from the following web page:
+
+\begin{center}
+  \webpage{}
+\end{center}
 
@@
 %% in running tests.
+
+%%  LocalWords:  parallelization Multicore CPUs refactoring

### 2017-11-21 ase17/intro.tex
Renamed dir of ASE'17 paper to a proper name

--- 2017-09-10 paper/intro.tex
@@
 \label{sec:intro}
-
-%% . which can disrupt the development
-%% process~\cite{hilton-etal-ase2016}.\Comment{  This is often referred to as the
-%% ``regression testing problem''.}
-
-%% As software evolves it is expected that the number of tests and the
-%% length of test runs increase.  Both components can add up to the
-%% aggregate cost of running a test suite.
 
@@
 
-%% \Mar{Fan Long
-%%   (http://people.csail.mit.edu/fanl/) often uses a plot to show the
-%%   exponential rise of projects in github.  Please check if you can
-%%   find a reference to that or ask Fan Long what source he used (maybe
-%%   browsed with public API).}
-
-%% \begin{enumerate}
-%% \item \textbf{Prevalence of long-running test suites.}
-%% \item \textbf{Prevalence of test suite parallelization.}
-%% \item \textbf{Developer's opinion (when parallelization not used).}    
-%% \item \textbf{Speedups of parallelization (when used).}
-%% \item \textbf{Issues versus benefits on using parallelization modes.}
-%% \end{enumerate}
-
 This paper reports on an empirical study we conducted to analyze the
@@
 
-%% Discovering Pareto-efficient~\cite{hwang-masud-1979}
-%% configurations is important to guide practitioners and future
-%% developments in this area.
+\noindent\emph{Feasibility.}~To assess how prevalent long-running test suites
+are we selected \numSubjs{} popular Java projects from \github{} containing
+Maven build files~\cite{maven}.  Section~\ref{sec:eval} details our methodology
+to select subjects and to isolate our experiments from environmental noise.
+Results indicate that nearly \percentMedLongRunning{} of the projects take at
+least 1m to run and \percentLongRunning{} of the projects take at least 5m to
+run.  Considering the \numMedLong{} projects with test suites taking longer than
+a minute to run, the average execution time of a test suite was
+\averageMedLongRunning{}.  Results also show that test cases are typically
+short-running, typically taking less than half a second to run.  Furthermore, we
+found that only in rare cases few test cases monopolize the overall time to run
+a test suite.
 
-%% papers also indicate the important of speeding up the testing process
-%% in other industrial domain, e.g., in 
-%% \Mar{Ask Milos if he can share stories on how prevalent regression
-%%   testing is at Microsoft and Google, if he can explain how they run
-%%   tests, and how prevalent is parallelization (in contrast to
-%%   regression testing).}
+\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
+adoption.  First, we measured usage of parallelism in open-source projects.
+Then, we ran a survey with developers to understand the reasons that could
+explain resistance to using the technology.\Comment{ For the quantitative
+analysis we checked both statically (parsing build files) and dynamically
+(monitoring execution of build files) for the presence of parallelization.}
+Considering only the projects whose test suites take longer than a minute to
+run, we found that only \percentParallelUpdated{} of them use parallelism.  We
+also contacted developers from a selection of costly projects that did not use
+parallelization to understand the reasons for not using parallelization.
+Dealing with concurrency-related issues (\eg{}, the extra work to organize test
+suite to avoid concurrency errors) and the availability of continuous
+integration services were the most frequently answered reasons for not
+considering parallelization.
 
-%Motivated by this potential gap in regression testing,
-%% More specifically, we studied how often long-running test suites occur
-%% in this setting, how frequently parallelization features are used, if
-%% not used why, and what are the associated drawbacks.
+\noindent\emph{Speedups.}~We used two setups to measure speedups.  In one setup
+we measured speedups obtained on projects that run test suites in parallel by
+default.  In the other setup, we evaluated how execution scales with the number
+of available cores in the machine.\Comment{We did not change parallel
+configurations on that setup.  For comparison, we disabled parallel execution to
+obtain the running time of a sequential execution.}  Considering the first
+setup, results indicate that the average speedup of parallelization was
+\avgSpeedup{}x.  Although we found cases with very high speedups (\eg{}, 28.8x
+for project Jcabi), we also found cases where the speedups were not very
+significant.  Considering the scalability experiment, we noticed, perhaps as
+expected, that parallelization obtained with forking JVMs scales with the number
+of cores but the speedups are bounded by long-running test classes.
 
-%% To run each test suite, we used a
-%% 16GB memory Intel i7 machine\Comment{ i7-4790 Intel processor} with
-%% eight virtual CPUs (four cores with two native threads each) and the
-%% default Maven configuration of each project.
-
-\noindent\emph{Feasibility.}~To assess how prevalent
-long-running test suites are we selected \numSubjs{} popular Java
-projects from \github{} containing Maven build files~\cite{maven}.
-Section~\ref{sec:eval} details our methodology to select subjects and
-to isolate our experiments from environmental noise.  Results indicate
-that nearly \percentMedLongRunning{} of the projects take at least 1m
-to run and \percentLongRunning{} of the projects
-take at least 5m to run.  Considering the \numMedLong{}
-projects with test suites taking longer than a minute to run, the average execution time of a test
-suite was \averageMedLongRunning{}.  Results also show that test cases
-are typically short-running, typically taking less than half a second
-to run.  Furthermore, we found that only in rare cases few test cases
-monopolize the overall time to run a test suite.
-
-\noindent\emph{Adoption.}~ We considered two aspects in
-measuring technology adoption.  First, we measured usage of
-parallelism in open-source projects.  Then, we ran a survey with
-developers to understand the reasons that could explain resistance to
-using the technology.\Comment{ For the quantitative analysis we
-  checked both statically (parsing build files) and dynamically
-  (monitoring execution of build files) for the presence of
-  parallelization.}  Considering only the projects whose test suites
-take longer than a minute to run, we found that
-only \percentParallelUpdated{} of them use parallelism.
-%% To sum, results indicate that test suite parallelization is
-%% underutilized.
-%% only
-%% \percentParallel{} of them use parallelism.  When correcting this
-%% value with the feedback obtained a posteriori from developers, we
-%% realized that the proportion should be higher, of
-%% \percentParallelUpdated{}.
-%%For the qualitative analysis
-We also contacted 
-developers from a selection of costly projects that did not use
-parallelization to understand the reasons for not using parallelization.  Dealing with concurrency-related issues (\eg{}, the
-extra work to organize test suite to avoid concurrency errors) and the
-availability of continuous integration services were the most
-frequently answered reasons for not considering parallelization.
-
-%% \Mar{move to here} Intuitively, benefits are
-%% proportional to the cost reduction that parallelization brings.  In
-%% the limit, however, the overhead of spawning virtual machines or
-%% threads can even result in added cost.
-
-\noindent\emph{Speedups.}~We used two setups to measure
-speedups.  In one setup we measured speedups obtained on
-projects that run test suites in parallel by
-default.  In the other setup, we evaluated how execution scales with
-the number of available cores in the machine.\Comment{We did not
-  change parallel configurations on that setup.  For comparison, we
-  disabled parallel execution to obtain the running time of a
-  sequential execution.}  Considering the first setup, results
-indicate that the average speedup of parallelization was
-\avgSpeedup{}x.  Although we found cases with very high speedups
-(\eg{}, 28.8x for project Jcabi), we also found cases where the speedups were
-not very significant.  Considering the scalability experiment, we
-noticed, perhaps as expected, that parallelization obtained with forking JVMs scales with the number
-of cores but the speedups are bounded by
-long-running test classes.
-
-%% %%RQ3
-%% Given the high execution cost associated with a significant number of
-%% \github{} projects, we decided to investigate usage of test
-%% suite parallelization in practice.  It is important to note that modern build
-%% systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
-%% accelerate test execution (see Section~\ref{sec:modes}).  To find how
-%% popular these features are in practice, we first analyzed build files
-%% \emph{statically}.  Considering the $>$1m group of projects
-%% (\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
-%% them use some parallelization option.  Considering those projects that
-%% take more than 5m to run (\numLong{} in total), usage of parallelism
-%% increases to 59\% (19/\numLong{}).  Furthermore, we found that
-%% ``forking'' virtual machines was the most prevalent parallel mode used
-%% in practice.  This mode is used twice as much as any other mode used.
-%% Important to note that ``forking VMs'' is perhaps the simplest of the
-%% parallelization modes~--~it is provided by the build system as opposed
-%% to the testing framework.  This result suggests that datarace
-%% flakiness~\cite{luo-etal-fse2014} may be a concern to users as
-%% ``forking'' does not exploit thread-level concurrency within each VM,
-%% which can create contention on data reachable from the static
-%% area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
-%% creates independent processes (\ie{}, Java VM instances) and executes
-%% tests sequentially within each process. \Mar{why 32-19 did not use
-%%   parallelization?}
-
-\noindent\emph{Tradeoffs.}~Test flakiness is a central
-concern when running tests in parallel.  Dependent tests
-can be affected by different schedulings of test methods and classes.
-This dimension of the study measures the impact of different parallel
-configurations on test flakiness and speedup.  Overall, results
-indicate that configurations that fork JVMs do not achieve
-speedups as high as other more-aggressive configurations, but they
-manifest much lower flakiness ratios.
+\noindent\emph{Tradeoffs.}~Test flakiness is a central concern when running
+tests in parallel.  Dependent tests can be affected by different schedulings of
+test methods and classes.  This dimension of the study measures the impact of
+different parallel configurations on test flakiness and speedup.  Overall,
+results indicate that configurations that fork JVMs do not achieve speedups as
+high as other more-aggressive configurations, but they manifest much lower
+flakiness ratios.
 
@@
 
-\setlist[itemize]{leftmargin=1.1em}
+%\setlist[itemize]{leftmargin=1.1em}
 \begin{itemize}
@@
     parallelization,} where Maven's executions did not reflect
-  corresponding JUnit's executions. (Docker reproduction scripts
-  available.) Those issues can hinder developers from using parallel
+  corresponding JUnit's executions.\Comment{(Docker reproduction scripts
+  available.)} Those issues can hinder developers from using parallel
   testing. Better debugging support for build systems could help

### 2017-11-21 ase17/main.tex
Renamed dir of ASE'17 paper to a proper name

\documentclass[conference]{IEEEtran}

\pdfpagewidth=8.5in
\pdfpageheight=11in

%% our macros and included packages
\input{macros}

\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{balance}
\usepackage{float}
\usepackage{url}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{amsmath} 
\usepackage{subfigure} 
\usepackage{multirow}
\usepackage{mdframed}

% *** CITATION PACKAGES ***
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option % requires cite.sty v4.0 or later (November 2003) \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor or-gan-ize}

\def\denseitems{
  \itemsep1pt plus1pt minus1pt
  \parsep0pt plus0pt
  \parskip0pt\topsep0pt}

\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

\pagenumbering{gobble}
\begin{document}

\title{Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact}

\author{\IEEEauthorblockN{Jeanderson Candido\qquad{}Luis Melo\qquad{}Marcelo d'Amorim}
\IEEEauthorblockA{Federal University of Pernambuco\\
Pernambuco, Brazil\\
\{jbc5,lhsm,damorim\}@cin.ufpe.br}}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
Dealing with high testing costs remains an important problem in
Software Engineering.  Test suite parallelization is an important
approach to address this problem.  This paper reports our findings on
the usage and impact of test suite parallelization in open-source
projects.\Comment{ This study brings to light the benefits and burdens
  of that approach.} It provides recommendations to practitioners and
tool developers to speed up test execution.

Considering a set of \numSubjs{} popular Java projects we analyzed, we
found that \percentMedLongRunning{} of the projects contain costly
test suites but parallelization features still seem underutilized in
practice~---~only \percentParallelUpdated{} of costly projects use
parallelization.  The main reported reason for adoption resistance was
the concern to deal with concurrency issues.  Results suggest that, on
average, developers prefer high predictability than high performance
in running tests.
\end{abstract}

\IEEEpeerreviewmaketitle

\input{intro}
\input{modes}
\input{subjects}
\input{evaluation}
\input{lessons}
\input{threats}
\input{related}
\input{conclusions}

%% uncomment for camera-ready
%% % use section* for acknowledgment
\ifCLASSOPTIONcompsoc
% The Computer Society usually uses the plural form
\section*{Acknowledgments}
\else
% regular IEEE prefers the singular form
\section*{Acknowledgment}
\fi

Jean(derson) and Luis are supported by FACEPE scholarphips
IBPG-0632-1.03/15 and IBPG-1175-1.03/16, respectively.  This work was
partially supported by CNPq grants 457756/2014-4 and 203981/2014-6.
%\newpage
% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

\balance
\bibliographystyle{plain}
\bibliography{tmp}

% that's all folks
\end{document}

%%  LocalWords:  Parallelization multi parallelization tmp tradeoffs

### 2017-11-21 ase17/threats.tex
Renamed dir of ASE'17 paper to a proper name

--- 2017-08-30 paper/threats.tex
@@
 The main threats to validity of this study are the following.
+
 \textit{External Validity:} Generalization of our findings is limited
@@
 different testing frameworks and build systems.
+Also, some of the selected subjects contain failing tests. Test
+failures may reduce the testing time due to early termination
+or even inflate the time (\eg, test waiting indefinitely for
+an unavailable resources).
+To mitigate this threat, we eliminated subjects with flaky tests and
+filtered projects with at least 90\% of the tests passing.
+Only 17\% of our subjects have failing tests.
+We carefully inspected our rawdata to identify and ignore these
+failures with JUnit's \CodeIn{@Ignore} annotation.
+
 \textit{Internal Validity:} Our results could be influenced by
 unintentional mistakes made by humans who interpreted survey data and
-implemented scripts and code to collect and analyze data.
+implemented scripts and code to collect and analyze the data.
 For example, we developed JUnit runners to reproduce Maven's parallel
@@
 in the subjects).
-All those tasks could introduce bias in our results.
-To mitigate those threats, we worked in pairs as to increase chances
-of capturing unintentional mistakes.
+All those tasks could bias our results.
+To mitigate those threats, the first two authors of this paper
+validated/inspected each other to increase chances of capturing
+unintentional mistakes.
+
 \textit{Construct Validity:} We considered a number of metrics in this

### 2017-12-10 journal/anatomy.tex
Added IEEE Journal formatting

--- 2016-07-11 paper/icse2017/anatomy.tex
@@
 
-\noindent\textbf{Detecting flakiness.}  Modern build systems provide
-mechanisms to reveal test flakiness. The typical approach is to
-iteratively re-execute the test suite marking as flaky those tests
-that produce both pass and failing outputs.  Considering the
-Maven\Fix{is this maven or maven's surefire
+\subsection{Detecting flakiness.}
+\label{sec:detect-flakiness-build}
+
+A popular approach to detect test flakiness is to iteratively
+re-execute (parts of) the test suite multiple times marking as flaky
+those tests that produce both pass and failing outputs.  We refer to
+this process as IRE (for Iterative RE-execution).
+
+Considering the Maven\Fix{is this maven or maven's surefire
   plugin~\cite{maven-surefire-plugin}?} build system, the process
@@
 eventually pass or when the bound N is reached.  Note that every
-iteration runs a subset of the tests from the previous iteration so
-execution cost is lower compared to executing the entire test suite N
-times.
+iteration runs a subset of the tests from the previous iteration so,
+assuming most tests will pass in the first iterations, execution cost
+is much lower compared to executing the entire test suite N times.
+However, note also that this method can particularly miss flaky tests
+for the following reasons: \Fix{elaborate: (1) passing tests can fail
+  in subsequent iterations and (2) ignoring tests may prevent
+  manifestations of read-write conflicts.}
 
-\Fix{Ideally, one would like to eliminate \pef{}s and avoid the need
-  for re-executing the test suite multiple times.}
+\Fix{explain other method...}
+
+%%  LocalWords:  iteratively

### 2017-12-10 journal/related.tex
Added IEEE Journal formatting

--- 2017-09-10 paper/related.tex
@@
 \label{sec:related}
-We discuss most related work in the following.
-%% Researchers and practitioners have been shedding light to the demand
-%% of techniques for optimizing test execution.
 
-%% For instance, a recent paper from the automotive industry reported
-%% that test suites can take days to run~\cite{artl-etal-icst2015}.
-%% There are different aspects to consider when dealing with the
-%% challenge of reducing test cost.
-
-%ekstazi-web,
 Regression testing research has focused mostly on test suite
@@
 
-%\Luis{maybe we should create another division for test acceleration}
-
 ElectricTest~\cite{bell-etal-esecfse2015} is a tool for efficiently
@@
 unrestricted test suite parallelization.
-
-%% \textit{Usage of massively parallel hardware:}
-%\textit{Hardware level massive parallelization:}
 
@@
 in those papers satisfied those constraints.
-
-%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
-%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
-%% language.
-%% Recent work proposed a compiler-assisted approach to make programs
-%% compatible with the relying programming-model used by
-%% GPUs to parallelize tests~\cite{}.
-%% \Jbc{...Justify they are out of scope for our subjects...}.
-
-%% \Mar{Luis, por favor, revise$\rightarrow$}
 
@@
 
-\Comment{
-\Fix{Please:
-  (i) consider categorizing related work in sections  
-  (ii) list papers that need to be discussed
-  (iii) discuss papers that use multi-execution (SIMD cpus like GPUs)
-  to speedup testing
-  }
-}
-\Comment{
-Similar approach to regression test selection has been recently
-applied in the context of the GCC~\cite{gcc} configurable
-system~\cite{souto-damorim-jss}.
-O Trabalho de Hilton ext al~\cite{hilton-etal-ase2016}, embora tenha
-como objetivo entender o uso de CI, mostra que existe uma demanda em
-acelerar o build e execucao de testes em servidores de integracao
-    continua
-}
-
 %%  LocalWords:  Ekstazi Ekstazi's elik JVM parallelization SIMD GPUs

### 2017-12-10 journal/study.tex
Added IEEE Journal formatting

\section{Empirical Study}

Table~\ref{table:cost}...\Fix{Why Forked JVM-L1 is (in some cases) so much better
compared to Forked JVM-L0? (io?)}\Fix{Why Forked JVM seems to be
  superior to all other Single JVM methods?  Are all CPUs in use?  If
  not, why one would use Single JVM (given that Forked JVM is faster
  and reduces flakiness)?}

Table~\ref{table:failures}...\Fix{I expected ``Single JVM + L3'' to
  find most flaky tests.}\Fix{Need to compute these results with
  another IRE method.}

\begin{table*}[t]
  \centering
  \begin{tabular}{|c|r|r|r|r|r|r|r|}
    \hline
    \multirow{2}{*}{\emph{Subject}} & \multirow{2}{*}{\emph{\# Tests}} &  \multicolumn{6}{c|}{\emph{Time}}\\
    \cline{3-8}
    & & \multicolumn{4}{c|}{\emph{Single JVM}} & \multicolumn{2}{c|}{\emph{Forked JVMs}} \\
%    & & \multicolumn{1}{c|}{\forkSeq{}} &
%    \multicolumn{1}{c|}{\forkDia{}} &
%    \multicolumn{1}{c|}{\singleJVMSeq{}} &
%    \multicolumn{1}{c|}{\singleJVMDia{}} &
%    \multicolumn{1}{c|}{\singleJVMClass{}} &
    %    \multicolumn{1}{c|}{\singleJVMMethod{}}\\
    \cline{3-8}
    & &  \multicolumn{1}{c|}{\Seq{}} &
    \multicolumn{1}{c|}{\ParClassSeqMeth{}} &
    \multicolumn{1}{c|}{\SeqClassParMeth{}} &
    \multicolumn{1}{c|}{\ParClassParMeth{}} &
    \multicolumn{1}{c|}{\Seq{}} &
    \multicolumn{1}{c|}{\ParClassSeqMeth{}}\\
    \hline
    \hline
    \multicolumn{8}{|c|}{\emph{Longer executions}} \\
    \hline
    camel-core & 5,683 & 24m:52s & 1.00x & 1.00x & 1.00x & 5.88x & 5.82x \\
    \hline
    jetty.project & 543 & 4m:14s & 2.41x & 2.97x & 5.61x & 2.44x & 13.70x \\
    \hline
    jgit & 3,422 & 3m:59s & 2.68x & 2.37x & 1.95x & 2.31x & 4.50x \\
    \hline
    okhttp & 1545 & 1m:16s & crash I & crash II & crash II & 3.40x & TIMEOUT \\
    \hline    
    \hline
    \multicolumn{8}{|c|}{\emph{Shorter executions}} \\
    \hline
    graphhopper & 1,259 & 12s & 0.92x & 1.01x & 0.53x & 1.72x & 1.17x \\
    \hline
    junit4 & 791 & 10s & 0m10.08s & 0m10.32s & 0m10.49s & 0m10.13s & 0m9.96s \\
    junit4** & <TESTCASES> & 10s & TIMEOUT & crash II & crash II & 0.99x & FIX \\
    \hline
    retrofit & 263 & 6s & 1.25x & 1.08x & 1.22x & 1.11x & 1.14x \\
    \hline
  \end{tabular}
  \caption{\label{table:cost}Test execution time.}
\end{table*}

\Fix{junit4 - need to look more carefully the log file}
\Fix{FIX - I used a wrong configuration in the pom.xml file}
\Fix{Camel - still couldn't find an explanation to unexpected behavior with parallel settings}
\Fix{Crash I - Surefire internal error (NullPointerException)}
\Fix{Crash II - JVM Crash (e.g. System.exit)}
\Fix{TIMEOUT - Possibly a deadlock: Execution could not finish within 30min}

\begin{table*}[t]
  \centering
  \begin{tabular}{|c|r|r|r|r|r|r|r|}
    \hline
    \multirow{2}{*}{\emph{Subject}} & \multirow{2}{*}{\emph{\# Tests}} &  \multicolumn{6}{c|}{\emph{Time}}\\
    \cline{3-8}
    & & \multicolumn{4}{c|}{\emph{Single JVM}} & \multicolumn{2}{c|}{\emph{Forked JVM}s} \\
    \cline{3-8}
    & & \multicolumn{1}{c|}{\Seq{}} &
    \multicolumn{1}{c|}{\ParClassSeqMeth{}} &
    \multicolumn{1}{c|}{\SeqClassParMeth{}} &
    \multicolumn{1}{c|}{\ParClassParMeth{}} &
    \multicolumn{1}{c|}{\Seq{}} &
    \multicolumn{1}{c|}{\ParClassSeqMeth{}} \\
    \hline
    \hline
    \multicolumn{8}{|c|}{\emph{Longer executions}} \\
    \hline
    camel (core) & 5,979 & 0 & ! & ! & ! & 75 & 70 \\
    \hline
    jetty (client) & 535 & 0 & 106** & 0 & 76** & 0 & 111 \\
    \hline
    jgit & 3,364 & 0 & 75 & 57* & 99* & 1 & 79 \\
    \hline
    okhttp & 1,525 & 0 & - & - & ! & 0 & ! \\    
    \hline
    \hline
    \multicolumn{8}{|c|}{\emph{Shorter executions}} \\
    \hline
    graphhopper & 1,259 & 0 & 152 & 55 & 347 & 14 & 67 \\
    \hline    
    junit4 & 791 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    \hline
    retrofit & 261 & 0 & 1 & 0 & 1 & 0 & 1 \\
    \hline
  \end{tabular}
  \caption{\label{table:failures}Number of flaky tests obtained with
    Maven's IRE (see Section~\ref{sec:detect-flakiness-build}) using
    bound of \Fix{?}.\Fix{* = Contains a skipped test. I don't know
      yet why a failing test may be skipped when it is executed
      individually}\Fix{Reminder: To not be confused with Sequential
      Flakiness. Sequential Flakiness must not be considered}}
\end{table*}

### 2017-12-10 journal/scalability/genplot.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+Rscript --vanilla scalability.r
+pdfcrop scalability.pdf scalability.pdf

### 2017-12-15 journal/subjects.tex
Added IEEE Journal formatting
Moved sections AS IS from our ase17 paper to here
Pass on subject section

--- 2017-10-13 paper/subjects.tex
@@
   \github{} API considers the predominant language as the primary
-  language.}, (2) the project has at least 100 stars, (3) the latest
-update was on or after January 1st, 2016, and (4) the \emph{readme}
-file contains the string \emph{mvn}.  We focused on Java for its
-popularity.  Although there is no clearcut limit on the number of
-\github{} stars~\cite{github-stars} to define relevant projects, we
-observed that one hundred stars was enough to eliminate trivial subjects. The
-third
-criteria serves to skip projects without recent activity. The fourth
-criteria is an approximation to find Maven projects.\Comment{ The
-  rationale is that if the string \emph{mvn} exists in the
-  \emph{readme} file, it may represent a Maven call (\eg, to compile
-or to test the project).} We focused on Maven for its popularity on
-Java projects.  Important to highlight that, as of now, the
-\github{}'s search API can only reflect contents from repository
-statistics (\eg, number of forks, main programming language); it does
-not provide a feature to search for projects containing certain files
-(\eg{}, \emph{pom.xml}) in the directory structure.
-Figure~\ref{fig:subject-query} illustrates the query to the \github{}
-API as an HTTP request.   The result set is sorted
-in descending order of stars.
+  language.}, (2) the project has at least 100 stars, and (3) the latest
+update was on or after \Jbc{January 1st, 2017}.
+Although there is no clearcut limit on the number of \github{}
+stars~\cite{github-stars} to define relevant projects, we observed that one
+hundred stars was enough to eliminate trivial subjects.
+The third criteria serves to skip projects without recent activity.
+\Jbc{We focused on Java for its popularity.
+It is important to highlight that the \github{}'s search API imposes a limit of
+returning only the top 1000 results for a single query.
+To overcome this limitation and have a larger sample set, we divided our
+original query into multiple queries over subsequent periods of time and
+considered the union the results.}
+% Important to highlight that, as of now, the \github{}'s search API can only
+% reflect contents from repository statistics (\eg, number of forks, main
+% programming language); it does not provide a feature to search for projects
+% containing certain files (\eg{}, \emph{pom.xml}) in the directory structure.
+Figure~\ref{fig:subject-query} illustrates a query to the \github{} API as
+an HTTP request.
 
@@
 \centering
-\scriptsize
+\tiny
 \lstset{
@@
 https://api.github.com/search/repositories?q=language:java
- +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
+ +stars:>=100+pushed:2017-01-01..2017-02-01&page=1
 \end{lstlisting}
-  \caption{\label{fig:subject-query} Query to the \github{} API for
-  projects that (1) use Java, (2) contains at least 100
-  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
-  the string \emph{mvn} in the \emph{readme} file.}
+  \vspace{-3mm}
+  \caption{\label{fig:subject-query} Query to the \github{} API for projects
+  that (1) use Java, (2) contains at least 100 stars, (3) has been updated
+  between January 1st and February 1st of 2017.}
   \vspace{-5mm}
@@
 
-We used the following methodology to select projects for
-analysis. After obtaining the list of potential projects from GitHub, we
-filtered those
-containing a \pomf{} file in the root directory.\Comment{  A Maven project may
-contain several sub-modules with multiple \pomf{} files.}
-Then, considering this set of Maven projects, we
-executed the tests for \SubjectsReruns{} times to discard those projects with
-issues
-in the build file and non-deterministic results observed from sequential
-executions.
-As of August 25th 2017, our search criteria returned a total of
-\SubjectsGithub{}
-subjects.
-From this set of projects,
-\SubjectsGithubNotMaven{} projects were not Maven or did not have a
-\pomf{} in the root directory, 
-\SubjectsGithubNotTestable{} projects were not considered because of
-environment incompatibility
-(\eg, missing\Comment{ required web browser or database management
-system}~DBMS),
-\SubjectsGithubFlaky{} projects were discarded because of
-``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
-or fails under
-the same circumstances leading to non-deterministic results.
-As some of our experiments consist of running tests on different
-threads, we ignored these projects as it would be impractical
-to identify whether a test failed due to a race condition or some
+We used the following methodology to select projects for analysis.
+After obtaining the list of potential projects from GitHub, we filtered those
+with Maven support (\ie, contains a \pomf{} file in the root directory).
+We focused on Maven for its popularity in Java projects.
+Then, considering this set of Maven projects, we executed the tests for
+\SubjectsReruns{} times to discard those projects with issues in the build file
+and non-deterministic results observed from sequential executions.
+
+As of December 12th 2017, our search criteria returned a total of
+\SubjectsGithub{} projects, and we identified \SubjectsMaven{} Maven projects.
+\Fix{From this set of projects, \SubjectsGithubNotTestable{} projects were not
+considered because of environment incompatibility (\eg, missing DBMS) and
+\SubjectsGithubFlaky{} projects were discarded because of ``flaky
+tests''~\cite{luo-etal-fse2014}.
+A ``flaky'' test is a test that passes or fails under the same circumstances
+leading to non-deterministic results.  As some of our experiments consist of
+running tests on different threads, we ignored these projects as it would be
+impractical to identify whether a test failed due to a race condition or some
 other source of flakiness.
-From the remaining \SubjectsGithubConsistant{} projects with
-deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
-projects with \SuiteFailingThreshold{} or more failing tests as to
-reduce bias. For the
-remaining projects with failing tests, we used the JUnit's
+From the remaining \SubjectsGithubConsistant{} projects with deterministic
+results, we eliminated \SubjectsGithubTooManyFailures{} projects with
+\SuiteFailingThreshold{} or more failing tests as to reduce bias.
+For the remaining projects with failing tests, we used the JUnit's
 \CodeIn{@Ignore} annotation to ignore failing tests.
-Our final set of subjects contains \numSubjs{} projects.
-Figure~\ref{fig:subjects} summarizes our sample set.
+Our final set of subjects
+contains \numSubjs{} projects.
+Figure~\ref{fig:subjects} summarizes our sample set.}
 
-\begin{figure}[ht]
-  \vspace{-2mm}
+\begin{figure}[h!]
   \centering
@@
 machine with eight virtual CPUs (four cores with two native threads each) and
-16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
-used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
-suites. To process test results and generate plots we used Python\Comment{ 3.4},
-Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
-replication on our website~\cite{ourwebpage}.  This includes supporting
-scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
-data)} and the full list of projects.
+16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).
+We used Java 8 and Maven 3.5.2 to build projects and run test suites.  To
+process test results and generate plots we used Python, Bash, R and Ruby.
+All source artifacts are publicly available for replication on our
+website~\cite{ourwebpage}.
+This includes supporting scripts and the full list of projects.

### 2018-11-01 ase17/intro.tex
Added uncommited changes

@@
 those tests under 10m, Groupon used a cluster of 4 computers with 24
-cores each~\cite{kim-etal-fse2013}.
+cores each~\citep{kim-etal-fse2013}.
 
 At large organizations, the alternative of renting cloud
-services~\cite{cloud-services} or even building proprietary
+services~\citep{cloud-services} or even building proprietary
 infrastructures for running tests is a legitimate approach to mitigate

### 2018-11-01 ms-dissertation/abstract.tex
Added uncommited changes

Testing is a costly process but mandatory in the development process.
Complex systems may require hours to run several test suites.
To mitigate this cost, a popular strategy in large companies is the usage of a
distributed execution environment at global scale.
In this approach, the workload is divided among several servers, and tests
run simultaneously on different machines.
Another approach explored by researchers and practitioners is the usage of
regression testing techniques such as test selection and minimization.
Test suite parallelization is an important approach to address costly
executions and a complementary approach to existing techniques.
With the popularization of multi-core processors in the last years, build tools
and testing frameworks added support to parallel execution in different
granularities to speedup test execution by leveraging the underlying hardware.
In this approach, tests can run on different processes and even in multiple
threads within a process.

This work reports our findings on the usage and impact of test suite
parallelization in open-source projects, and it provides recommendations to
practitioners and tool developers.
Considering a set of \numSubjs{} popular Java projects, we observed that
\percentMedLongRunning{} of these projects contain costly test suites.
However, only \percentParallelUpdated{} of costly projects use some form of
parallelization to speedup test execution.
The main reported reason for adoption resistance was dealing with concurrency
issues.
Results suggest that, on average, developers prefer high predictability than
high performance in running tests.

\begin{keywords}
Software Engineering, Software Testing, Parallelism
\end{keywords}

### 2018-11-01 ms-dissertation/chapters/background.tex
Added uncommited changes

--- 2017-10-13 paper/modes.tex
@@
-\section{Parallel Execution of Test Suites}
+\chapter{Background}
 \label{sec:modes}
+
+This chapter presents background material related to \Fix{...}, which are
+important for the rest of this thesis, and an illustrative example to
+\Fix{...}.
+
+\section{Introduction}
 
@@
 network.  For instance, using virtual machines from a cloud service to
-\begin{wrapfigure}{r}{0.15\textwidth}  
-  \centering
-  %  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}    
-  \includegraphics[width=0.08\textwidth]{figs/parallel-levels-short.pdf}  
-  \caption{\label{fig:levels}Levels of parallelism.}
-\end{wrapfigure}
 distribute test execution.  The lowest levels denote parallelism
@@
 
-\subsection{Testing Frameworks}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.5\textwidth]{figs/parallel-levels.pdf}    
+  \caption{\label{fig:levels}Levels of parallelism.}
+\end{figure}
+
+\section{Testing Frameworks}
 \label{sec:frameworks}
@@
 
-\subsection{Build Systems}
+\section{Build Systems}
 \label{sec:builder}
@@
 %% pool de 5 threads em cada JVM para executar testes em paralelo.}
+
+\section{Illustrative Example}
+
 \begin{figure}[h!]
 \centering
+\begin{minipage}{0.6\textwidth}
 \scriptsize
@@
   escapeinside={@}{@},
-  numbers=none,xleftmargin=1em,frame=none,framexleftmargin=0.5em,
-  basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+  framexleftmargin=0em,frame=single,
+  basicstyle=\ttfamily, boxpos=c, numbers=left, numberstyle=\tiny,
   morekeywords={parallel, threadCount, perCoreThreadCount,
@@
 }
-\vspace{-4ex}
 \begin{lstlisting}
@@
 \end{lstlisting}
-  \vspace{-4ex}
-  \caption{\label{fig:surefire} Configuration \ForkParMeth{} on
-    Maven.}
+\end{minipage}
+  \caption{\label{fig:surefire} Configuration \ForkParMeth{} on Maven.}
 \end{figure}
 
-\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
+Figure~\ref{fig:surefire} shows a
 fragment of a Maven configuration file, known as \pomf{}, highlighting

### 2018-11-01 ms-dissertation/chapters/evaluation.tex
Added uncommited changes

--- 2017-10-13 paper/evaluation.tex
@@
-\section{Evaluation}
+\chapter{Evaluation}
 \label{sec:eval}
+
+\section{Introduction}
 
@@
 
-\subsection{Feasibility}
+\section{Feasibility}
 \label{sec:rqA}
@@
 
-\begin{itemize}
-  \item \numRQFeasibilityOne{}. \textbf{\RQFeasibilityOne}
-\end{itemize}
+\subsection{\RQFeasibilityOne}
 
@@
 \begin{figure}[ht]%
-  \vspace{-3mm}
   \centering
@@
   }%
-  \vspace{-2mm}
   \caption{(a)\Comment{ Testing time grouped by time cost ($t$): short run
@@
     (b)~Distribution of running times per cost group.}
-\vspace{-5mm}
 \end{figure}
@@
 
-\begin{itemize}
-  \item \numRQFeasibilityTwo. \textbf{\RQFeasibilityTwo}
-\end{itemize}
+\subsection{\RQFeasibilityTwo}
 
@@
 
-\subsection{Adoption}
-\label{sec:rqC}
-\label{sec:rqE}
+\section{Adoption}
 
-\begin{itemize}
-    \item \numRQAdoptionOne. \textbf{\RQAdoptionOne{}}
-\end{itemize}
+\subsection{\RQAdoptionOne{}}
 
@@
 Column ``\emph{Subject}'' indicates the name of the project, column
+``\emph{\# of modules}'' indicates the fraction of modules containing
+tests that use the configuration of parallelism mentioned in column
+``\emph{Mode}''.
+We note that, considering these projects, the modules that do not use
+the configuration cited use the sequential configuration \Seq{}.
+For example, three modules (=28-25) from Log4J2 use sequential
+configuration. It came as a surprise the observation that
+no project used distinct configurations in their modules.
+
+%% XXX
+\Comment{
 \begin{wraptable}{r}{5cm}
@@
 \end{wraptable}
-``\emph{\# of modules}'' indicates the fraction of modules containing
-tests that use the configuration of parallelism mentioned in column
-``\emph{Mode}''.
-We note that, considering these projects, the modules that do not use
-the configuration cited use the sequential configuration \Seq{}.
-For example, three modules (=28-25) from Log4J2 use sequential
-configuration. It came as a surprise the observation that
-no project used distinct configurations in their modules.
+}
 
@@
 
-\begin{itemize}
-  \item \numRQAdoptionTwo{}. \textbf{\RQAdoptionTwo{}}
-\end{itemize}
+\subsection{\RQAdoptionTwo{}}
 
@@
 
-Considering question 3, the distribution of answers was as follows.  A
-total of \emailsA{} of the \emailsProjectsAnswered{} developers who
-answered the survey did not know that parallelism was available in
+% XXX
+\Comment{
 \begin{wrapfigure}{r}{0.13\textwidth}
@@
 \end{wrapfigure}
+}
+Considering question 3, the distribution of answers was as follows.  A
+total of \emailsA{} of the \emailsProjectsAnswered{} developers who
+answered the survey did not know that parallelism was available in
 Maven (option ``a''), \emailsB{} of developers mentioned that they did
@@
 
-\subsection{Speedups}
+\section{Speedups}
 \label{sec:rqD}
 
-\begin{itemize}
-    \item \numRQSpeedupOne{}. \textbf{\RQSpeedupOne}
-\end{itemize}
+\subsection{\RQSpeedupOne}
 
@@
 
-\begin{itemize}
-    \item \numRQSpeedupTwo{}. \textbf{\RQSpeedupTwo}
-\end{itemize}
+\subsection{\RQSpeedupTwo}
 
 \newcommand{\subjectScalability}{MapDB}
+
+% XXX
+\Comment{
+\begin{wrapfigure}{r}{0.23\textwidth}
+  \includegraphics[width=0.23\textwidth]{R/scalability/scalability.pdf}
+  \caption{\label{fig:scalability}Scalability.}
+  \vspace{-4mm}
+\end{wrapfigure}
+}
 
@@
 subject \subjectScalability{} in this experiment as it represents the
-\begin{wrapfigure}{r}{0.23\textwidth}
-  \includegraphics[width=0.23\textwidth]{R/scalability/scalability.pdf}
-  \caption{\label{fig:scalability}Scalability.}
-  \vspace{-4mm}
-\end{wrapfigure}
 case of a long-running test suite (see Table~\ref{tab:speedup}) with
@@
 
-\subsection{Tradeoffs}
+\section{Tradeoffs}
 \label{sec:rq6-tradeoffs}
@@
 
-\begin{itemize}
-  \item \numRQIssuesOne{}. \textbf{\RQIssuesOne{}}
-\end{itemize}
+\subsection{\RQIssuesOne{}}
 

### 2018-11-01 ms-dissertation/discovery.tex
Added uncommited changes

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
KEYWORDS_REGEX="parallel\|forkMode\|forkCount"
for subj in $SUBJECTS; do
    subject_path="$SUBJECTS_HOME/$subj"
    build_files=`find $subject_path -name pom.xml`
    for build_file in $build_files; do
        output=`cat $build_file | grep $KEYWORDS_REGEX`
        if [[ -n "$output" ]]; then echo $build_file; fi
done
\end{lstlisting}
    \caption{\label{fig:discovery-step} Bash script to filter build
    files for inspeciton: line 4 lists all \pomf{} files from a
    subject; for each path, the  \CodeIn{cat} command lists the file
    content and uses \CodeIn{grep} to filter only the matching lines
    with the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
    \CodeIn{forkCount} (line 6); if the output is not empty (line
    7), we print the current path.}
\end{figure}

### 2018-11-01 ms-dissertation/resumo.tex
Added uncommited changes

Teste de software é um processo custoso mas mandatório no processo de
desenvolvimento. Sistemas complexos podem demandar horas para executar várias
suítes de testes. Para mitigar os custos, uma estratégia popular em grandes
corporações é o uso de um ambiente de execução distribuído em escala global.
Desta forma, a carga de testes é dividida entre diversos servidores e os testes
são executados simultaneamente em diferentes máquinas. Outra estratégia
explorada por pesquisadores e desenvolvedores é a aplicação de técnicas de teste
de regressão, como seleção e minimização de testes. Uma outra forma igualmente
relevante e complementar a estratégias existentes é a execução paralela de
suítes de testes em uma mesma máquina. Nos últimos anos, com a popularização de
processadores com múltiplos núcleos, ferramentas de build e bibliotecas de
teste adicionaram suporte a execução paralela de testes em diferentes
granularidades com o objetivo de prover a máxima utilização dos recursos
computacionais de uma máquina e diminuir o tempo execução. Desta forma, testes
podem ser executados em diferentes processos e até mesmo em múltiplas threads
em um mesmo processo.

Este trabalho reporta nossas descobertas sobre a utilização e o impacto de
execução paralela de testes em projetos de código aberto e provê recomendações
a programadores e desenvolvedores de ferramentas que pretendem utilizar ou
prover esta funcionalidade. Considerando um conjunto de \numSubjs{} projetos
populares escritos em Java, observamos que \percentMedLongRunning{} destes
projetos possuem suítes de teste custosas. Apesar disto, apenas
\percentParallelUpdated{} utilizam alguma forma de paralelismo para acelerar a
execução dos testes.
O principal motivo de resistência para adoção de execução paralela é o receio
de introduzir problemas de concorrência. Os resultados sugerem que, em média,
desenvolvedores preferem manter a previsibilidade de uma execução
determinística ao invés de alta performance.

\begin{keywords}
Engenharia de Software, Teste de Software, Paralelismo
\end{keywords}

### 2019-05-14 scripts/analysis_subjects/check_gradle/github_filter_gradle.py
update

@@ -1,0 +1,120 @@
+# This version of the miner searches for projects based in a search criteria
+# over multiple time windows.
+#
+# This approach is necessary to increase the number of potential subjects to
+# analyze because the GitHub Search API v3 limits the query response to the
+# top 1000 results. The miner overcomes this limit by querying over multiple
+# time windows and returning the union of all results.
+#
+# Author: Jeanderson Candido <http://jeandersonbc.github.io>
+import os, re, csv
+
+from shutil import rmtree
+from subprocess import call, check_output
+
+from utils import TimeInterval, CSVOutput, Query, verify_maven_support
+
+
+def git_revision(project_path):
+    if not os.path.exists(project_path):
+        return ""
+    basedir = os.path.abspath(os.curdir)
+    os.chdir(project_path)
+    try:
+        revision = check_output("git rev-parse HEAD", shell=True).decode().strip()
+    except:
+        revision = ""
+    os.chdir(basedir)
+    return revision
+
+
+def git_clone(full_name, branch="master", download_dir=os.curdir):
+    """
+    Clones a project hosted on Github based on the given project full name.
+
+    The project full name is the suffix of the GitHub url "{user}/{repo_name}".
+    For instance, in "www.github.com/foo/bar", the full name is "foo/bar".
+    By default, this function considers the latests 50 commits.
+    """
+    dir_name = re.sub("/", "_", full_name)
+    output_dir = os.path.join(download_dir, dir_name)
+    if not os.path.exists(output_dir):
+        git_cmd = "git clone http://github.com/{} -b {} --depth {} --recursive {}"
+        call(git_cmd.format(full_name, branch, 50, output_dir), shell=True)
+
+    return output_dir
+
+
+def fetcher(query_fields, output_dir):
+    download_dir = os.path.join(os.curdir, output_dir)
+    if not os.path.exists(download_dir):
+        os.mkdir(download_dir)
+
+    output_header = ["full_name", "fork", "size", "stargazers_count",
+                     "default_branch", "created_at", "pushed_at",
+                     "ismaven", "rev"]
+
+
+    output = CSVOutput("fetched-projects.csv", sorted(output_header))
+
+    output_is_maven = CSVOutput("is-maven-projects.csv", sorted(output_header))
+
+    output_not_maven = CSVOutput("not-maven-projects.csv", sorted(output_header))
+
[…]

### 2019-05-14 scripts/analysis_subjects/check_parallel_subjects/find-interesting.py

@@ -1,0 +1,220 @@
+# This version of the miner searches for projects based in a search criteria
+# over multiple time windows.
+#
+# This approach is necessary to increase the number of potential subjects to
+# analyze because the GitHub Search API v3 limits the query response to the
+# top 1000 results. The miner overcomes this limit by querying over multiple
+# time windows and returning the union of all results.
+#
+# Author: Jeanderson Candido <http://jeandersonbc.github.io>, Sotero Junior <https://soterojunior.github.io/>
+
+import os, re, csv
+import time
+import logging
+import json
+from shutil import rmtree
+from subprocess import call, check_output
+from urllib.request import urlopen, HTTPError
+from utils import CSVOutput, create_logger, SLEEP_TIME
+
+find_interesting_logger = create_logger("find-interesting","find-interesting.log")
+
+from datetime import date, timedelta
+class TimeInterval:
+    def __init__(self, since, until=None, delta=30):
+        self.starting_date = self.datefromstr(since)
+        self.ending_date = self.datefromstr(until) if until else date.today()
+        self.delta = timedelta(days=delta)
+
+    @staticmethod
+    def datefromstr(datestr):
+        fields = [int(e) for e in datestr.split("-")]
+        return date(fields[0], fields[1], fields[2])
+
+    def __iter__(self):
+        return self
+
+    def __next__(self):
+        if self.starting_date > self.ending_date:
+            raise StopIteration
+        next_date = self.starting_date + self.delta
+        interval = (self.starting_date.isoformat(), next_date.isoformat())
+        self.starting_date = next_date + timedelta(days=1)
+        return interval
+
+class Query:
+    """
+    Represents a paginated query to the GitHub's Search API for repositories.
+    Query fields are represented as a key-value map like the following:
+
+        query_fields = {"language": "java", "stars": ">=1000"}
+
+    Basic Usage:
+
+        q = Query({"language": "java", "stars": ">=1000"})
+        while (q.has_next()):
+            q.fetch()
+    """
+    def __init__(self, fields):
+        self.__url_template = "https://api.github.com/search/repositories?q={query}&per_page=100&page={page}"
+        self.__fields = "+".join(["{}:{}".format(k, v) for k, v in fields.items()])
+        self.__page = 1
+        self.__max_page = Query.__request_handler(self.__get_last_page)
+
+    def has_next(self):
+        return self.__page <= self.__max_page
+
+    def fetch(self):
+        if not self.has_next():
+            raise Exception("Query has exhausted")
[…]

### 2019-05-14 scripts/analysis_subjects/check_parallel_subjects/utils.py

@@ -1,0 +1,48 @@
+import csv
+import os
+import re
+import logging
+
+## this is a hack to fool github servers in believing that this is not a robot
+SLEEP_TIME=60
+
+class CSVOutput:
+    def __init__(self, file_name, header):
+        self.__file_name = self.__verify(file_name)
+        self.__file_path = os.path.abspath(self.__file_name)
+        self.__fields = header
+        with open(self.__file_path, "w", newline="") as f:
+            writer = csv.DictWriter(f, fieldnames=self.__fields)
+            writer.writeheader()
+
+    def name(self):
+        return self.__file_name
+
+    def write(self, entry):
+        with open(self.__file_path, "a", newline="") as f:
+            writer = csv.DictWriter(f, fieldnames=self.__fields)
+            writer.writerow({k: v for k, v in entry.items() if k in self.__fields})
+
+    def __verify(self, file_name, counter=1):
+        if not os.path.exists(file_name):
+            return file_name
+        file_name = re.sub("(-[0-9]+)?\.", "-{}.".format(counter), file_name)
+        return self.__verify(file_name, counter=counter + 1)
+
+
+def create_logger(name, log_file):
+    # Function setup as many loggers as you want
+    formatter = logging.Formatter('[%(asctime)-15s] %(message)s')
+    logger    = logging.getLogger(name)
+
+    handler = logging.FileHandler(log_file,mode='a')
+    handler.setFormatter(formatter)
+
+    streamHandler = logging.StreamHandler()
+    streamHandler.setFormatter(formatter)
+
+    logger.setLevel(logging.DEBUG)
+    logger.addHandler(handler)
+    logger.addHandler(streamHandler)
+
+    return logger

### 2019-05-14 scripts/analysis_subjects/scripts/github-miner.py

@@ -1,0 +1,115 @@
+# This version of the miner searches for projects based in a search criteria
+# over multiple time windows.
+#
+# This approach is necessary to increase the number of potential subjects to
+# analyze because the GitHub Search API v3 limits the query response to the
+# top 1000 results. The miner overcomes this limit by querying over multiple
+# time windows and returning the union of all results.
+#
+# Author: Jeanderson Candido <http://jeandersonbc.github.io>
+# Modified: Sotero Junior <https://soterojunior.github.io/> 
+
+import os, re, csv
+
+from shutil import rmtree
+from subprocess import call, check_output
+
+from utils import TimeInterval, CSVOutput, Query, verify_maven_support
+
+
+def git_revision(project_path):
+    if not os.path.exists(project_path):
+        return ""
+    basedir = os.path.abspath(os.curdir)
+    os.chdir(project_path)
+    try:
+        revision = check_output("git rev-parse HEAD", shell=True).decode().strip()
+    except:
+        revision = ""
+    os.chdir(basedir)
+    return revision
+
+
+def git_clone(full_name, branch="master", download_dir=os.curdir):
+    """
+    Clones a project hosted on Github based on the given project full name.
+
+    The project full name is the suffix of the GitHub url "{user}/{repo_name}".
+    For instance, in "www.github.com/foo/bar", the full name is "foo/bar".
+    By default, this function considers the latests 50 commits.
+    """
+    dir_name = re.sub("/", "_", full_name)
+    output_dir = os.path.join(download_dir, dir_name)
+    if not os.path.exists(output_dir):
+        git_cmd = "git clone http://github.com/{} -b {} --depth {} --recursive {}"
+        call(git_cmd.format(full_name, branch, 50, output_dir), shell=True)
+
+    return output_dir
+
+
+def fetcher(query_fields, output_dir):
+    download_dir = os.path.join(os.curdir, output_dir)
+    if not os.path.exists(download_dir):
+        os.mkdir(download_dir)
+
+    output_header = ["full_name", "fork", "size", "stargazers_count",
+                     "default_branch", "created_at", "pushed_at",
+                     "ismaven", "rev"]
+
+
+    output = CSVOutput("fetched-projects.csv", sorted(output_header))
+
+    output_is_maven = CSVOutput("is-maven-projects.csv", sorted(output_header))
+
+    output_not_maven = CSVOutput("not-maven-projects.csv", sorted(output_header))
+
[…]

### 2019-05-14 scripts/auxiliary_script/download.py

@@ -1,0 +1,43 @@
+#!/usr/bin/env python3
+import csv, os
+from subprocess import call
+
+
+output_dir = "downloads"
+if not os.path.exists(output_dir):
+    os.mkdir(output_dir)
+
+
+input_csv = os.path.join("csv", "interesting.csv")
+with open(input_csv, newline="") as out:
+    reader = csv.DictReader(out)
+    entries = [e for e in reader]
+
+
+clone_cmd = "git clone https://github.com/{} --recursive {}"
+reset_cmd = "git reset --hard {}"
+
+
+cnt = 0 # XXX download subset only
+ordered_entries = sorted(entries, key=lambda e: int(e["size"]), reverse=True)
+for e in ordered_entries:
+    dirname = e["full_name"].replace("/", "_")
+    target = os.path.join(output_dir, dirname)
+    curdir = os.path.abspath(os.path.curdir)
+
+    rev = e["rev"]
+    if not os.path.exists(target):
+        call(clone_cmd.format(e["full_name"], target), shell=True)
+        os.chdir(target)
+        call(reset_cmd.format(rev), shell=True)
+    
+    print(curdir)
+    #os.chdir(target)
+    #call(reset_cmd.format(rev), shell=True)
+    os.chdir(curdir)
+
+    # XXX download subset only
+    cnt += 1
+    if (cnt >= 957):
+        break
+

### 2019-05-14 scripts/auxiliary_script/download_subjects.py

@@ -1,0 +1,42 @@
+import os, re, csv, logging, datetime
+
+from shutil import rmtree
+from subprocess import call, check_output
+
+'''
+This script takes on input the file interesting.csv and produces as output 
+file testing.csv. The input file contains potential projects (containing 
+directives of test parallelization in pom.xml) whereas the output file contains
+a subset of those projects that compile and successfully run all tests.
+'''
+
+
+def main():
+
+    scripts_dir = os.getcwd()
+    ## create download directory if it does not exit
+    download_dir = "downloads"    
+    download_dir = os.path.join(os.curdir, download_dir)
+    if not os.path.exists(download_dir):
+        os.mkdir(download_dir)
+
+    # iterating through interesting.csv rows
+    with open('long_medium_subject.csv') as csvfile:
+        reader = csv.DictReader(csvfile)
+        for row in reader:
+            full_name = row['name']
+            branch = row['default_branch']
+            depth = 1
+            # destination directory for the project (fully-qualified name)
+            dest_dir = os.path.join(os.path.join(os.getcwd(), download_dir), full_name.replace(os.sep, "_"))
+            
+            # clone only the head of the project into download directory
+            git_cmd = "git clone http://github.com/{} -b {} --depth {} --recursive {}".format(full_name, branch, depth, dest_dir)
+            call(git_cmd, shell=True)
+            print("cloned project")
+            
+            
+            
+
+if __name__ == "__main__":
+   main()

### 2019-05-14 scripts/auxiliary_script/move_files_results.py

@@ -1,0 +1,55 @@
+#!/usr/bin/env python3
+import csv
+import os
+import re 
+import xml.etree.ElementTree as etree
+import time, datetime
+import shutil
+
+from collections import Counter
+from subprocess import check_output, CalledProcessError
+from sys import argv
+
+
+def extract_data_from(project_path):
+    date_create  = datetime.date.today().strftime("%d%m%Y{}".format(time.strftime("%H%M%S")))
+    project_name = os.path.basename(project_path)
+    scripts_dir  = os.getcwd()
+    
+    print("{}".format(datetime.date.today().strftime("%d%m%Y{}".format(time.strftime("%H%M%S")))))
+    print(project_path)
+
+    os.chdir(project_path)
+    date_create_dir = os.path.join(os.curdir, date_create)
+    if not os.path.exists(date_create_dir):
+        os.mkdir(date_create_dir)
+
+
+    #destination = os.path.join(os.curdir, date_create_dir)
+    os.chdir(scripts_dir)
+    destination = os.path.join(project_path, date_create)
+
+    print("destination: {}".format(destination))
+
+    for files in os.listdir(project_path):
+        print(files)
+        if files.endswith(tuple([".xml",".log"])):
+            shutil.move(os.path.abspath("logs/{}/{}".format(project_name,files)),destination)
+
+    
+
+    return "OK"
+
+
+if __name__ == "__main__":
+    LOGS_DIR = "./logs"
+    if not os.path.exists(LOGS_DIR):
+        print("Could not find directory \"%s\"\nExiting..." % LOGS_DIR)
+
+    ENTRIES = []
+    for project in os.listdir(LOGS_DIR):
+        project_path = os.path.join(LOGS_DIR, project)
+        ENTRIES.extend(extract_data_from(project_path))
+
+    #print("Moving files...{}".format(project_path))
+

### 2019-05-14 scripts/auxiliary_script/old_script/find-testable.py

@@ -1,0 +1,93 @@
+import os, re, csv, logging, datetime
+
+from shutil import rmtree
+from subprocess import call, check_output
+from utils import CSVOutput, create_logger
+
+logger = create_logger("find-testable", "find-testable.log")
+
+'''
+This script takes on input the file interesting.csv and produces as output 
+file testing.csv. The input file contains potential projects (containing 
+directives of test parallelization in pom.xml) whereas the output file contains
+a subset of those projects that compile and successfully run all tests.
+'''
+
+def git_revision(project_path):
+    """
+    Given a directory (or any child) associated with a cloned git repository, 
+    this command returns the hash (SHA) associated with that project.
+    """
+    if not os.path.exists(project_path):
+        return ""
+    basedir = os.path.abspath(os.curdir)
+    os.chdir(project_path)
+    try:
+        revision = check_output("git rev-parse HEAD", shell=True).decode().strip()
+    except:
+        revision = ""
+    os.chdir(basedir)
+    return revision
+
+def main():
+
+    scripts_dir = os.getcwd()
+    ## create download directory if it does not exit
+    download_dir = "downloads"    
+    download_dir = os.path.join(os.curdir, download_dir)
+    if not os.path.exists(download_dir):
+        os.mkdir(download_dir)
+
+    # layout of csv file
+    output_header = ["full_name", "sha", "date"]
+    testable_csv_output= CSVOutput("testable.csv", sorted(output_header))
+
+    logger.info('starting...')
+    # iterating through interesting.csv rows
+    with open('interesting.csv') as csvfile:
+        reader = csv.DictReader(csvfile)
+        for row in reader:
+            full_name = row['full_name']
+            branch = row['default_branch']
+            depth = 1
+            # destination directory for the project (fully-qualified name)
+            dest_dir = os.path.join(os.path.join(os.getcwd(), download_dir), full_name.replace(os.sep, "_"))
+            logger.warning("processing project {}".format(full_name))
+            # clone only the head of the project into download directory
+            git_cmd = "git clone http://github.com/{} -b {} --depth {} --recursive {}".format(full_name, branch, depth, dest_dir)
+            call(git_cmd, shell=True)
+            logger.warning("  cloned project")
+            # clean project and download all dependencies
+            os.chdir(dest_dir)
+            clean_command = "mvn clean dependency:go-offline"
+            #TODO: check if we should interrupt if some depedencies are not satisfied
[…]

### 2019-05-14 scripts/auxiliary_script/old_script/move-test-reports.sh

@@ -1,0 +1,22 @@
+#!/bin/bash
+PROJECT_DIR=$1 # the project directory with contents after running test suite
+
+if [ -z ${PROJECT_DIR} ] || [ ! -d ${PROJECT_DIR} ];
+then
+    echo "Could not find project directory"
+    exit -1    
+fi
+
+# return the directory where this file is located regardless from where it is called from
+# https://stackoverflow.com/questions/59895/getting-the-source-directory-of-a-bash-script-from-within
+THISDIR="$( cd "$( dirname "${BASH_SOURCE[0]}" )" >/dev/null && pwd )"
+
+OUTPUT_DIR=${THISDIR}/$(basename $PROJECT_DIR)-testreports
+
+## create directory if it does not exist
+mkdir -p ${OUTPUT_DIR}
+
+# move reports from surefire dir to some directory for later processing
+for REPORT in `find ${PROJECT_DIR} | grep --text "target/surefire-reports/TEST" | grep -v "junitreports\|resources\|test-classes"`; do
+    mv $REPORT ${OUTPUT_DIR}
+done

### 2019-05-14 scripts/auxiliary_script/old_script/rq2/rq2.r

@@ -1,0 +1,72 @@
+library(ggplot2)
+library(dplyr)
+library(grDevices)
+
+# Figure 7
+df_med <- read.csv("dataset-testcases-medium.csv") %>% mutate(group = "medium")
+df_long <- read.csv("dataset-testcases-long.csv") %>% mutate(group = "long")
+df <- rbind(df_long, df_med)
+
+df_stats <- df %>%
+  group_by(project, group) %>%
+    summarize(t = median(time)) %>%
+        group_by(group) %>%
+           summarise(avg = mean(t),
+                     std = sd(t))
+
+df_stats
+
+cairo_pdf("testcost-distribution.pdf", width = 5, height = 2.5)
+ggplot(df, aes(x = project, y = time)) +
+  geom_boxplot(outlier.shape=NA) +
+  geom_hline(
+    data = df_stats,
+    aes(yintercept = avg),
+    colour = "red",
+    linetype = 2,
+    size = 0.3
+  ) +
+  theme_bw() +
+  theme(strip.background = element_blank(),
+    legend.background = element_rect(),
+    legend.margin = margin(0),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank()) +
+  facet_wrap( ~ group, scales = "free", ncol = 1) +
+  labs(y = "Time cost (in secs)") +
+  coord_cartesian(ylim = c(0, 7))
+
+dat <- summarise(group_by(df, project, group),
+         n = length(time),
+         time = sum(time))
+
+# Figure 8.b
+cairo_pdf("scatter-testcost.pdf", height = 3, width = 3)
+ggplot(dat, aes(x = n / 100, y = time / 60)) +
+  geom_point(size = 0.5, shape = 1) +
+  facet_wrap( ~ group, nrow = 1, ncol = 2, scales = 'free') +
+  labs(x = bquote(Number~of~test~cases~(x10^{2})), y = "Time cost (in minutes)") +
+  theme_bw() +
+  theme(strip.background = element_blank(),
+    legend.background = element_rect(),
+    legend.margin = margin(0),
+    legend.title = element_blank(),
+    legend.position = "top") +
+  geom_smooth(method = lm)
+
+# Figure 8.a
+cairo_pdf("boxplots-testcases.pdf", height = 3, width = 1.5)
+ggplot(dat, aes(x = group, y = n / 100)) +
+  geom_boxplot() +
+  theme_bw() +
[…]

### 2019-05-14 scripts/auxiliary_script/remove_subfolder.py

@@ -1,0 +1,42 @@
+#!/usr/bin/env python3
+import csv
+import os
+import re 
+import xml.etree.ElementTree as etree
+import time, datetime
+import shutil
+from shutil import rmtree
+
+from collections import Counter
+from subprocess import check_output, CalledProcessError
+from sys import argv
+
+
+
+
+if __name__ == "__main__":
+    LOGS_DIR = "./rawdata"
+    if not os.path.exists(LOGS_DIR):
+        print("Could not find directory \"%s\"\nExiting..." % LOGS_DIR)
+
+    ENTRIES = []
+    for project in os.listdir(LOGS_DIR):
+        project_path = os.path.join(LOGS_DIR, project)
+        print("PROJETO: {}".format(project_path))
+        if not project_path == "./rawdata/.DS_Store":
+
+            for files in os.listdir(project_path):
+                print(files)
+                print("{}/{}".format(project_path,files))
+                if files == "0329094641": #0329094641 #0331025746
+                    if os.path.isdir(files):
+                        print("é diretorio!")
+                        if os.path.exists("{}/{}".format(project_path,files)):
+                            rmtree("{}/{}".format(project_path,files))
+                    else:
+                        print("não é diretorio!")
+                        rmtree("{}/{}".format(project_path,files))
+        #ENTRIES.extend(extract_data_from(project_path))
+
+    #print("Moving files...{}".format(project_path))
+

### 2019-05-14 scripts/result_rq5/compile-test.sh

@@ -1,0 +1,54 @@
+#!/bin/bash
+#
+# Invokes maven compile and test for projects from a given directory
+#
+# Usage:   ./compile-test.sh <TIMEOUT> <PROJECTS_DIR> <OUTPUT_DIR>
+# Example: ./compile-test.sh 90m ./downloads/projects ./rawdata
+#
+TIMEOUT=$1
+
+INPUT_DIR=$2
+if [[ ! -d "$INPUT_DIR" ]]; then
+    echo "Invalid path download"
+    exit 1
+fi
+
+OUTPUT_DIR="`readlink -e $3`"
+if [[ ! -d "$OUTPUT_DIR" ]]; then
+    echo "Invalid path rawdata"
+    exit 1
+fi
+
+MAVEN_SKIPS="-Drat.skip=true -Dmaven.javadoc.skip=true -Djacoco.skip=true \
+             -Dcheckstyle.skip=true -Dfindbugs.skip=true -Dcobertura.skip=true \
+             -Dpmd.skip=true -Dcpd.skip=true -Denforcer.skip=true"
+
+TS="`date +"%m%d%H%M%S"`"
+
+for PROJECT in `ls "$INPUT_DIR"`; do
+
+    # Watch out for ending slash
+    PROJECT_PATH="$INPUT_DIR/$PROJECT"
+    if [[ ! -d "$PROJECT_PATH" ]]; then
+        echo "Invalid path \"$PROJECT_PATH\". Skipping..."
+        continue
+    fi
+
+    PROJECT_OUTPUT="$OUTPUT_DIR/$PROJECT/$TS"
+    if [[ ! -d "$PROJECT_OUTPUT" ]]; then
+        mkdir -p "$PROJECT_OUTPUT"
+    fi
+ 
+    pushd $PROJECT_PATH
+    mvn clean dependency:go-offline 2>&1
+    mvn compile test-compile package -DskipTests $MAVEN_SKIPS 2>&1 \
+        | tee $PROJECT_OUTPUT/compile.log
+    timeout -s SIGKILL $TIMEOUT mvn verify -fae $MAVEN_SKIP 2>&1 \
+        | tee $PROJECT_OUTPUT/testing.log
+
+    # Get reports from surefire dir
+    for REPORT in `find . | grep --text "target/surefire-reports/TEST" | grep -v "junitreports\|resources\|test-classes"`; do
+        mv $REPORT $PROJECT_OUTPUT
+    done
+    popd
+done

### 2019-05-14 scripts/result_rq5/run_script.sh

@@ -1,0 +1,17 @@
+
+SCRIPTS=./src
+PROJECTS_DIR=./src/downloads
+OUTPUT_DIR=./src/rawdata
+RERUNS=3
+
+echo "Started at `date`" >> runs.txt
+for run in `seq 1 $RERUNS`; do
+    $SCRIPTS/compile-test.sh 90m $PROJECTS_DIR $OUTPUT_DIR && echo "Finished run #$RERUNS at `date`" >> runs.txt
+done
+
+#echo "Generating variables at `date`"
+#$SCRIPTS/dynamic-variables.rb -p $PROJECTS_DIR
+#$SCRIPTS/static-variables.rb -p $PROJECTS_DIR
+
+#echo "Speedup at `date`"
+#bash speedup.sh

### 2019-05-14 scripts/result_rq5/speedup.sh

@@ -1,0 +1,47 @@
+#!/bin/bash
+#
+# This script is related to the RQ5. It compares test execution with
+# default settings (assuming some parallel configuration) and
+# sequential execution.
+#
+# This script depends on the "dynamic-variables.csv" file to know
+# which projects have parallelism enabled by default (generated by the
+# parsettings.sh script).
+#
+# Author: Jeanderson Candido <http://jeandersonbc.github.io>
+#
+SCRIPTS=./src
+PROJECTS_DIR=./src/downloads
+INPUT_CSV=./src/dynamic-variables.csv
+
+if [ ! -f "$INPUT_CSV" ]; then
+    echo "This script depends on the \"dynamic-variables.csv\" file to know which projects "
+    echo "have parallelism enabled by default (generated by the echo \"parsettings.sh\" script)."
+    echo "MISSING FILE!"
+    exit 1
+fi
+
+MAVEN_SKIPS="-Drat.skip=true -Dmaven.javadoc.skip=true \
+             -Djacoco.skip=true -Dcheckstyle.skip=true \
+             -Dfindbugs.skip=true -Dcobertura.skip=true \
+             -Dpmd.skip=true -Dcpd.skip=true"
+
+BASEDIR="`pwd`"
+for subject in `cat $INPUT_CSV | sed "s/,.*//g" | uniq`; do
+    project_path=$PROJECTS_DIR/$subject
+    [[ ! -d "$project_path" ]] && continue
+
+    # "sequentialize" pom files
+    $SCRIPTS/sequentializer.rb -p "$project_path"
+
+    cd $project_path
+
+    mvn clean dependency:go-offline 2>&1
+    mvn compile test-compile -DskipTests $MAVEN_SKIPS 2>&1
+    timeout -s SIGKILL 90m mvn test -fae $MAVEN_SKIP 2>&1 | tee sequential.log
+
+    # undo changes on this subject
+    git reset --hard HEAD
+
+    cd $BASEDIR
+done

### 2019-05-14 scripts/result_rq5/static-variables.rb

@@ -1,0 +1,162 @@
+#!/usr/bin/env ruby
+require 'csv'
+require 'optparse'
+require 'ostruct'
+require 'rexml/document'
+include REXML
+
+require_relative 'rbcommon.rb'
+
+def get_test_variables project_path
+  configs = {'C0'=>[], 'C1'=>[], 'C2'=>[], 'C3'=>[], 'FC0'=>[], 'FC1'=>[]}
+  project_name = File.basename project_path
+  poms = `find #{project_path} -name "pom.*xml" -type f`
+  poms.each_line do |pom|
+
+    next if pom.include? '/resources/'
+    next if pom.include? '/test/'
+    next if pom.include? '/target/'
+
+    xml = Document.new IO.read(pom.strip)
+    plugins = XPath.match xml, "//plugin/artifactId[. = 'maven-surefire-plugin']/../configuration"
+    if not plugins.nil? and plugins.to_a.size > 0
+      plugins.each do |configuration|
+        dict = {}
+        dict['parallel'] = get_element configuration, 'parallel'
+        dict['reuseForks'] = get_element configuration, 'reuseForks'
+        dict['useUnlimitedThreads'] = get_element configuration, 'useUnlimitedThreads'
+        dict['threadCount'] = get_element configuration, 'threadCount'
+        dict['perCoreThreadCount'] = get_element configuration, 'perCoreThreadCount'
+        dict['threadCountClasses'] = get_element configuration, 'threadCountClasses'
+        dict['parallelOptimized'] = get_element configuration, 'parallelOptimized'
+        dict['threadCountMethods'] = get_element configuration, 'threadCountMethods'
+        dict['forkCount'] = get_element configuration, 'forkCount'
+        dict.keys.to_a.each do |key|
+          if dict[key].nil?
+            dict.delete key
+          end
+        end
+
+        has_var = false
+        dict.keys.each do |k|
+          if dict[k].include? '{'
+            has_var = true
+            break
+          end
+        end
+
+        dict['inferred'] = false
+        possible = []
+        if has_var
+          if dict['parallel'] != nil and dict['parallel'].include? '{'
+            ['methods', 'classes', 'both', 'suites', 'suitesAndClasses', 'suitesAndMethods', 'classesAndMethods', 'all'].each do |v|
+              c = dict.clone
+              c['inferred'] = true
+              c['parallel'] = p
+              possible << c
+            end
+          end
[…]

### 2019-05-14 scripts/result_rq7/new-flakiness-speedup.py

@@ -1,0 +1,138 @@
+#!/usr/bin/env python3
+'''
+This script is related to the RQ7. It compares test execution with
+several different parallel settings.
+@author: Jeanderson Candido <http://jeandersonbc.github.io>
+'''
+import csv
+import os
+import re
+import shutil
+
+from subprocess import Popen, PIPE, call
+
+
+SUBJECTS_DIR = os.path.abspath(os.path.join("projects", "downloads"))
+EXPERIMENT_DIR = os.path.abspath("./flakiness-speedup-experiment-2")
+RAWDATA_DIR = os.path.abspath("./flakiness-speedup-rawdata-2")
+SUBJECTS_NUM = 50
+
+
+def minversion(dependency, reference):
+    semantic_fields = lambda e:[int(v) for v in e.split(".")]
+    try:
+        ver = semantic_fields(dependency.split(":")[-2])
+        print("Version subject:")
+        print(ver)
+
+        reffields = semantic_fields(reference)
+        print("Version reference:")
+        print(reffields)
+        for i in range(len(reffields)):
+            print("range:")
+            print(i)
+            if reffields[i] > ver[i]:
+                return False
+
+    except ValueError:
+        return False
+
+    return True
+
+
+def criteria(entry):
+    condition = entry["timecost_group"] != "short" \
+                and entry["compiled"] == entry["tested"] == "SUCCESS" \
+                and entry["perc_failures"] == "0"
+
+    if not condition:
+        print("Subject without condition ", entry["name"])
+        return False
+
+    print("Checking", entry["name"])
+    project_path = os.path.join(SUBJECTS_DIR, entry["name"])
+    if not os.path.exists(project_path):
+        print("Project Path not found! ", entry["name"])
+        return False
+
+    p1 = Popen("cd \"%s\" && mvn dependency:list" % project_path, shell=True, stdout=PIPE)
+    stdout, stderr = p1.communicate()
+    p1.wait()
+    if p1.returncode == 1:
+        rawdeps = stdout.decode().split("\n")
+        dependencies = [re.sub(".* ", "", d) for d in rawdeps if "junit:jar:" in d]
+        for d in dependencies:
+            if ("testng" in d) or ("junit" in d and not minversion(d, "4.7")):
+                print("Old version JUnit in Error show dependency!")
+                return False
[…]

### 2019-05-14 scripts/result_subjects_parallel/find-interesting.py

@@ -1,0 +1,257 @@
+# This version of the miner searches for projects based in a search criteria
+# over multiple time windows.
+#
+# This approach is necessary to increase the number of potential subjects to
+# analyze because the GitHub Search API v3 limits the query response to the
+# top 1000 results. The miner overcomes this limit by querying over multiple
+# time windows and returning the union of all results.
+#
+# Author: Jeanderson Candido <http://jeandersonbc.github.io>, Sotero Junior <srsj2@cin.ufpe.br>
+import os, re, csv
+import time
+import logging
+import json
+from shutil import rmtree
+from subprocess import call, check_output
+from urllib.request import urlopen, HTTPError
+from utils import CSVOutput, create_logger, SLEEP_TIME
+
+find_interesting_logger = create_logger("find-interesting","find-interesting.log")
+
+from datetime import date, timedelta
+class TimeInterval:
+    def __init__(self, since, until=None, delta=30):
+        self.starting_date = self.datefromstr(since)
+        self.ending_date = self.datefromstr(until) if until else date.today()
+        self.delta = timedelta(days=delta)
+
+    @staticmethod
+    def datefromstr(datestr):
+        fields = [int(e) for e in datestr.split("-")]
+        return date(fields[0], fields[1], fields[2])
+
+    def __iter__(self):
+        return self
+
+    def __next__(self):
+        if self.starting_date > self.ending_date:
+            raise StopIteration
+        next_date = self.starting_date + self.delta
+        interval = (self.starting_date.isoformat(), next_date.isoformat())
+        self.starting_date = next_date + timedelta(days=1)
+        return interval
+
+class Query:
+    """
+    Represents a paginated query to the GitHub's Search API for repositories.
+    Query fields are represented as a key-value map like the following:
+
+        query_fields = {"language": "java", "stars": ">=1000"}
+
+    Basic Usage:
+
+        q = Query({"language": "java", "stars": ">=1000"})
+        while (q.has_next()):
+            q.fetch()
+    """
+    def __init__(self, fields):
+        self.__url_template = "https://api.github.com/search/repositories?q={query}&per_page=100&page={page}"
+        self.__fields = "+".join(["{}:{}".format(k, v) for k, v in fields.items()])
+        self.__page = 1
+        self.__max_page = Query.__request_handler(self.__get_last_page)
+
+    def has_next(self):
+        return self.__page <= self.__max_page
+
+    def fetch(self):
+        if not self.has_next():
+            raise Exception("Query has exhausted")
[…]

### 2019-05-14 scripts/result_subjects_parallel/rq1.r

@@ -1,0 +1,38 @@
+library("ggplot2")
+library("dplyr")
+library("grDevices")
+
+df <- read.csv("dataset-sanitized.csv")
+
+print("DISTRIBUTION ACCORDING TO THRESHOLD")
+df %>%
+  group_by(timecost_group, below_threshold) %>%
+    summarise(n = length(perc_failures),
+              avg = mean(perc_failures),
+              sd = sd(perc_failures))
+
+# Subject barplot - Fig 6.a
+cairo_pdf("barplot-timecost.pdf", height = 3, width = 2.2)
+ggplot(filter(df, below_threshold == T), aes(x = timecost_group)) +
+  geom_bar(width = .8, position = "dodge", colour = "black", fill = "white") +
+  geom_text(
+    size = 3,
+    stat = "count",
+    aes(label = ..count..),
+    position = position_stack(),vjust = 0.5) +
+  theme_bw() +
+  labs(y = "Number of projects", x = "Group")
+ 
+# Subject boxplot - Fig 6.b
+cairo_pdf("boxplot-timecost.pdf", height = 3, width = 3)
+ggplot(filter(df, below_threshold == T), aes(x = timecost_group, y = xml_time_avg / 60)) +
+  geom_boxplot() +
+  theme_bw() +
+  theme(strip.text = element_blank(),
+    strip.background = element_blank(),
+    legend.background = element_rect(),
+    legend.margin = margin(0),
+    legend.title = element_blank(),
+    legend.position = "top") +
+  facet_wrap( ~ timecost_group, scales = "free") +
+  labs(y = "Time cost (in minutes)", x = "Group")

### 2019-05-14 scripts/result_subjects_parallel/subjects.r

@@ -1,0 +1,19 @@
+library("ggplot2")
+library("stats")
+library("dplyr")
+library("grDevices")
+
+df <- read.csv("dataset-subjects.csv")
+
+# Subjects piechart
+cairo_pdf("piechart-subjs.pdf", width = 3.65, height = 3)
+ggplot(df, aes(x = factor(1), y = value, fill = type)) +
+  geom_bar(width = 1, stat = "identity", colour = "black") +
+  theme_void() +
+  scale_fill_manual(values = c("#000000", "#AAAAAA", "#777777", "#333333", "#FFFFFF")) +
+  theme(legend.title = element_blank()) +
+  geom_text(
+    aes(x = 1.7, label = value),
+    position = position_stack(),vjust = 0.5,
+    size = 3) +
+  coord_polar("y")

### 2019-05-20 tse19/main.tex
added tse 2019

--- 2017-10-13 paper/evaluation.tex
@@
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+
+\usepackage{graphicx}
+% *** CITATION PACKAGES ***
+%
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage{cite}
+\fi
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+
+\input{macros}
+
+\usepackage[T1]{fontenc}
+\usepackage{microtype}
+\usepackage{graphicx}
+\usepackage{listings}
+\usepackage{wrapfig}
+\usepackage{enumitem}
+\usepackage{balance}
+\usepackage{float}
+\usepackage{url}
+\usepackage{tabularx}
+\usepackage[table]{xcolor}
+\usepackage{booktabs}
+\usepackage{amsmath} 
+\usepackage{subfigure} 
+\usepackage{multirow}
+\usepackage{mdframed}
+\usepackage{xcolor}
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\begin{document}
+
+\title{Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact}
+
+\author{Sotero Junior, Jeanderson Candido, Marcio Ribeiro
+        and~Marcelo d'Amorim
+
+% <-this % stops a space
+\IEEEcompsocitemizethanks{
+\IEEEcompsocthanksitem 
+S. Junior and M. d'Amorim are with the Informatics Center, Federal Univer- sity of Pernambuco, Recife, PE 50732-970, Brazil.
+
+E-mail: \{srsj2, damorim\}@cin.ufpe.br
+
+\IEEEcompsocthanksitem 
+M. Ribeiro was with the Computing Institute, Federal University of Alagoas, Maceio, AL 57072-900, Brazil.
+
+E-mail: marcio@ic.ufal.br
+}% <-this % stops an unwanted space
+\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+
+% The paper headers
+\markboth{Journal of \LaTeX\ Class Files,~Vol.~45, No.~6, June~2019}%
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+
+\IEEEtitleabstractindextext{%
+\begin{abstract}
+Dealing with high testing costs remains an important problem in
+Software Engineering.  Test suite parallelization is an important
+approach to address this problem.  This paper reports our findings on
+the usage and impact of test suite parallelization in open-source
+projects.\Comment{ This study brings to light the benefits and burdens
+  of that approach.} It provides recommendations to practitioners and
+tool developers to speed up test execution.
+
+Considering a set of \numSubjs{} popular Java projects we analyzed, we
+found that \percentMedLongRunning{} of the projects contain costly
+test suites but parallelization features still seem underutilized in
+practice~---~only \percentParallelUpdated{} of costly projects use
+parallelization.  The main reported reason for adoption resistance was
+the concern to deal with concurrency issues.  Results suggest that, on
+average, developers prefer high predictability than high performance
+in running tests.
+\end{abstract}
+
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+test suite, parallelization, Maven, Java, Software Engineering.
+\end{IEEEkeywords}}
+
+% make the title area
+\maketitle
+\IEEEdisplaynontitleabstractindextext
+\IEEEpeerreviewmaketitle
+
+\IEEEraisesectionheading{
+\section{Introduction}
+\label{sec:introduction}}
+
+\input{intro}
+
+%\hfill lorem ipsum
+
+%\hfill August 26, 2015
+
+% SECTION 2
+\section{Parallel Execution of Test Suites}
+Figure~\ref{fig:levels} illustrates different levels where
+parallelism in test execution can be obtained.
+The highest level indicates
+parallelism obtained through different machines on the
+network.  For instance, using virtual machines from a cloud service to
+\begin{wrapfigure}{r}{0.13\textwidth}  
+  \vspace{-2mm}
+  \centering
+  %  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}    
+  \includegraphics[width=2cm]{figs/parallel-levels-short.pdf}  
+  \caption{\label{fig:levels}Levels of parallelism.}
+  \vspace{-2mm}
+\end{wrapfigure}
+
+distribute test execution.  The lowest levels denote parallelism
+obtained within a single machine.  These levels are complementary:
+the lowest levels leverage the computing power of server
+nodes whereas the highest level leverages the aggregate processing
+power of a network of machines.
+This paper focuses on low-level parallelism, where computation can be
+offloaded at different CPUs within a machine and at different threads
+within each CPU.  This form of parallelism is enabled through build
+systems (spawning processes in different CPUs) and testing frameworks
+(spawning threads in one given CPU).  It is important to note that a variety
+of testing frameworks provide today support for parallel test
+execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng}, and
+NUnit~\cite{nunit}) as to benefit from the available power of popular multi-core processors.
+In the following, we elaborate relevant features of testing frameworks
+and build systems for parallelization.  We focused on Java, Maven, and JUnit but the
+discussion can be generalized to other language and tools.
+
+\subsection{Testing Frameworks}
+\label{sec:frameworks}
+
+The list below shows the choices to control parallelism within one
+Java Virtual Machine (JVM).  These options are offered by the testing
+framework (\eg{}, JUnit).
+
+\begin{itemize}
+\item
+    \textbf{Sequential (\Seq).}~No parallelism is involved.
+\item
+    \textbf{Sequential classes; parallel methods
+      (\SeqClassParMeth).}~This configuration corresponds to running
+    test classes sequentially, but running test methods from those
+    classes concurrently.
+\item
+    \textbf{Parallel classes; sequential methods
+      (\ParClassSeqMeth{}).}~This configuration corresponds to running
+    test classes concurrently, but running test methods sequentially.
+\item
+    \textbf{Parallel classes; Parallel methods
+      (\ParClassParMeth).}~This configuration runs test classes and
+    methods concurrently.\Comment{corresponds to the
+    combination of \SeqClassParMeth{} and \ParClassSeqMeth{}.  }
+\end{itemize}
+
+Notice that an important aspect in deciding which configuration to use (or in
+designing new test suites) is the possibility of race conditions on shared data
+during execution.  Data sharing can occur, for example, through state that is
+reachable from statically-declared variables in the program or through variables
+declared within the scope of the test class or even through resources available
+on the file system and the network~\cite{luo-etal-fse2014}.  Considering data
+race avoidance, configuration \SeqClassParMeth{} is preferable over
+\ParClassSeqMeth{} when it is clear that test methods in a class do not
+manipulate shared state, which can be challenging to
+determine~\cite{bell-etal-esecfse2015}.  Similarly, \ParClassSeqMeth{} is
+preferable over \SeqClassParMeth{} when it is clear that several test methods in
+a class perform operations involving shared data.  Configuration
+\ParClassParMeth{} does not restrict scheduling orderings.  Consequently, it is
+more likely to manifest data races during execution. Note that speedups depend
+on several factors, including the test suite size and distribution of test
+methods per class.
+
+\subsection{Build Systems}
+\label{sec:builder}
+
+%% The build system can spawn multiple JVMs, each running on its own OS
+%% process on a given CPU and handling a partition of the test set.
+Forking OS processes to run test jobs is the basic mechanism of build
+systems to obtain parallelism at the machine space (see
+Figure~\ref{fig:levels}).  For Java-based build systems, such as Maven
+and Ant, this amounts to spawning one JVM, on a given CPU, to handle a
+test job and aggregating results when jobs finish.  The list below
+shows the choices to control parallelism through the build system
+(\eg{}, Maven).
+
+\begin{itemize}
+\item
+  \textbf{Forked JVMs with sequential methods (\ForkSeq).}~The build
+  system spawns multiple JVMs with this configuration, assigning a
+  partition of the set of test classes to each JVM.  Test classes and methods
+  run sequentially within each JVM.
+\item
+  \textbf{Forked JVMs with parallel methods (\ForkParMeth).}~With
+  this configuration, the build system forks multiple JVMs, as
+  \ForkSeq{} does, but it runs test methods concurrently, as
+  \SeqClassParMeth{} does.
+\end{itemize}
+
+%% In the configuration \ForkSeq{}, each spawned
+%% process runs a different test class at time and the builder merges the
+%% results from each execution. In the configuration \ForkParMeth{}, the
+%% build system forwards settings to the underlying testing framework to
+%% enable parallel execution within each process in addition to running
+%% test classes on different processes.
+
+Note from the listing that forking can only be combined with
+configuration \SeqClassParMeth{} (see Section~\ref{sec:frameworks}) as
+Maven made the design choice to only accept one test class at a time
+per forked process.  Maven offers an option to reuse JVMs that can be
+used to attenuate the potentially high cost of spawning new JVM
+processes on every test class (if reuse is enabled) and also to
+achieve test isolation (if reuse is disabled).
+
+%% \Mar{$\leftarrow$Are you sure about this?
+%%   It seems silly.  Maybe, the rationale is to ``keep design
+%%   simple''.}\Jbc{I'm sure. in addition to keep design simple, I feel
+%%   like this was initially conceived to run tests in isolation}
+%% \Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
+%%   configuracao abaixo?}\Jbc{added...}
+%%We are unaware of other build system capable of running multiple
+%%classes at time within a forked process.
+%%  to
+%% define tasks related to the project building and these tasks are
+%% performed several plugins.This file
+%% contains defintions of tasks, which are implemented by a collection of
+%% plugins.
+%% \Jbc{falar do surefire e explicar a
+%% configuracao ilustrada - Surefire levanta uma JVM por core e cria uma
+%% pool de 5 threads em cada JVM para executar testes em paralelo.}
+\begin{figure}[h!]
+\centering
+\scriptsize
+\lstset{
+  escapeinside={@}{@},
+  numbers=none,xleftmargin=1em,frame=none,framexleftmargin=0.5em,
+  basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+  morekeywords={parallel, threadCount, perCoreThreadCount,
+  forkCount, reuseForks},
+  deletekeywords={true}
+}
+\vspace{-4ex}
+\begin{lstlisting}
+<plugin>
+    <groupId>org.apache.maven.plugins</groupId>
+    <artifactId>maven-surefire-plugin</artifactId>
+    <configuration>
+        <forkCount>1C</forkCount>
+        <reuseForks>true</reuseForks>
+        <parallel>methods</parallel>
+        <threadCount>5</threadCount>
+    </configuration>
+</plugin>
+\end{lstlisting}
+  \vspace{-4ex}
+  \caption{\label{fig:surefire} Configuration \ForkParMeth{} on
+    Maven.}
+\end{figure}
+
+\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
+fragment of a Maven configuration file, known as \pomf{}, highlighting
+options to run tests using the parallel execution mode \ForkParMeth{}.
+Maven implements this feature through its Surefire JUnit test
+plugin~\cite{maven-surefire-plugin}.  With this configuration, Maven
+forks one JVM per core (\CodeIn{forkCount} parameter) and uses five
+threads (\CodeIn{threadCount} parameter) to run test methods
+(\CodeIn{parallel} parameter) within each forked JVM.  Maven reuses
+created JVMs on subsequent forks when execution of a test class
+terminates (\CodeIn{reuseFork} parameter).
+
+% SECTION 3
+
+\section{Objects of Analysis}
+\label{sec:subjects}
+
+We used \github{}'s search API~\cite{githubsearch} to identify
+projects that satisfy the following criteria: (1) the primary language
+is Java\footnote{In case of projects in multiple languages, the
+  \github{} API considers the predominant language as the primary
+  language.}, (2) the project has at least 100 stars, (3) the latest
+update was on or after January 1st, 2016, and (4) the \emph{readme}
+file contains the string \emph{mvn}.  We focused on Java for its
+popularity.  Although there is no clearcut limit on the number of
+\github{} stars~\cite{github-stars} to define relevant projects, we
+observed that one hundred stars was enough to eliminate trivial subjects. The
+third
+criteria serves to skip projects without recent activity. The fourth
+criteria is an approximation to find Maven projects.\Comment{ The
+  rationale is that if the string \emph{mvn} exists in the
+  \emph{readme} file, it may represent a Maven call (\eg, to compile
+or to test the project).} We focused on Maven for its popularity on
+Java projects.  Important to highlight that, as of now, the
+\github{}'s search API can only reflect contents from repository
+statistics (\eg, number of forks, main programming language); it does
+not provide a feature to search for projects containing certain files
+(\eg{}, \emph{pom.xml}) in the directory structure.
+
+Figure~\ref{fig:subject-query} illustrates the query to the \github{}
+API as an HTTP request.   The result set is sorted
+in descending order of stars.
+
+\begin{figure}[t!]
+\centering
+\tiny
+\lstset{
+    escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
+    showstringspaces=false
+}
+\begin{lstlisting}
+https://api.github.com/search/repositories?q=language:java
+ +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
+\end{lstlisting}
+  \vspace{-3mm}
+  \caption{\label{fig:subject-query} Query to the \github{} API for
+  projects that (1) use Java, (2) contains at least 100
+  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
+  the string \emph{mvn} in the \emph{readme} file.}
+  \vspace{-3mm}
+\end{figure}
+
+We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
+filtered those
+containing a \pomf{} file in the root directory.\Comment{  A Maven project may
+contain several sub-modules with multiple \pomf{} files.}
+Then, considering this set of Maven projects, we
+executed the tests for \SubjectsReruns{} times to discard those projects with
+issues
+in the build file and non-deterministic results observed from sequential
+executions.
+As of August 25th 2017, our search criteria returned a total of
+\SubjectsGithub{}
+subjects.
+From this set of projects,
+\SubjectsGithubNotMaven{} projects were not Maven or did not have a
+\pomf{} in the root directory, 
+\SubjectsGithubNotTestable{} projects were not considered because of
+environment incompatibility
+(\eg, missing\Comment{ required web browser or database management
+system}~DBMS),
+\SubjectsGithubFlaky{} projects were discarded because of
+``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
+or fails under
+the same circumstances leading to non-deterministic results.
+As some of our experiments consist of running tests on different
+threads, we ignored these projects as it would be impractical
+to identify whether a test failed due to a race condition or some
+other source of flakiness.
+From the remaining \SubjectsGithubConsistant{} projects with
+deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
+projects with \SuiteFailingThreshold{} or more failing tests as to
+reduce bias. For the
+remaining projects with failing tests, we used the JUnit's
+\CodeIn{@Ignore} annotation to ignore failing tests.
+Our final set of subjects contains \numSubjs{} projects.
+
+ Figure~\ref{fig:subjects} summarizes our sample set.
+
+\begin{figure}[ht]
+  \vspace{-5mm}
+  \centering
+  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
+  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
+  hosted on \github{}. From this initial sample, we ignored
+  \SubjectsGithubNotMaven{} projects without Maven support,
+  \SubjectsGithubNotTestable{} with missing dependencies,
+  \SubjectsGithubFlaky{} projects with flaky tests, and
+  \SubjectsGithubTooManyFailures{} projects had at least
+  \SuiteFailingThreshold{} of failing tests. We considered
+  \numSubjs{} projects to conduct our study.}
+\end{figure}
+
+\label{sec:setup}
+
+To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
+machine with eight virtual CPUs (four cores with two native threads each) and
+16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
+used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
+suites. To process test results and generate plots we used Python\Comment{ 3.4},
+Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
+replication on our website~\cite{ourwebpage}.  This includes supporting
+scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
+data)} and the full list of projects.
+
+% SECTION 4
+
 \section{Evaluation}
@@
 
-%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
-%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
-%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
-%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
-%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
-%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
-%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
-%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
-%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
-%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
-%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
-%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
-%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
-%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
-%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
-%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
-%%  LocalWords:  Vavr SNE Urbanairship Datacube dereference
-%%  LocalWords:  unsynchronized ConcurrentModificationException
-%%  LocalWords:  NoSuchElementException EOFException ElectricTest
-%%  LocalWords:  ArrayIndexOutOfBoundsException
-%%  LocalWords:  FileSystemAlreadyExistsException
-%%  LocalWords:  BufferOverflowException
+% SECTION 5
+
+\section{Discussion}
+
+This paper reports our finding on a study to evaluate impact and usage
+of test suite parallelization, enabled by modern build systems and
+testing frameworks.  This study is important given the importance to
+speedup testing.  Note that test suite parallelization is
+complementary to alternative approach to speedup testing
+(see~Section~\ref{sec:related}).  The observations we made in this
+study trigger multiple actions:
+
+\begin{itemize}
+\item \emph{Incentivize forking.}~Forked JVMs manifest low rates of
+  test flakiness.  For instance, in \emph{\ForkSeq{}}, only 4 of 10
+  projects manifest flakiness and, excluding the extreme case of
+  \CodeIn{Moquette}, projects manifest flaky tests in low rates 0.23\%
+  to 1.70\%.  Developers of projects with long-running test suites
+  should consider using that feature, which is available in modern
+  build systems today (\eg{}, Maven).
+\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
+  impressive speedups at the expense of sometimes impressive rates of
+  flakiness.  Breaking test dependencies to avoid flakiness and take
+  full advantage of those options is advised for developers with
+  greater interest in efficiency.
+\item \emph{Refactor tests for load balancing.}~Forked JVMs scales
+  better with the number of cores when the test workload is balanced
+  across testing classes.  To balance the workload, automated
+  user-oblivious refactoring can help in scenarios where developers
+  are not willing to change test code but have access to machines with
+  a high number of cores.
+\item \emph{Improve debugging for build systems.}~While preparing our
+  experiments, we found scenarios\Comment{, related to test
+    parallelization,} where Maven's executions did not reflect
+  corresponding JUnit's executions. \Comment{(Docker reproduction scripts
+  available.)} Those issues can hinder developers from using parallel
+  testing. Better debugging infrastructure is important.
+\end{itemize}
+
+This study brings to light the benefits and burdens of test suite
+parallelization to improve test efficiency. It provides
+recommendations to practitioners and developers of new techniques and
+tools aiming to speed up test execution with parallelization.
+
+% SECTION 6
+%%
+
+\section{Threats to Validity}
+
+The main threats to validity of this study are the following.
+
+\textit{External Validity:} Generalization of our findings is limited
+to our selection of subjects, testing framework, and build system.  To
+mitigate that issue, we selected subjects according to an objective
+criteria, described in Section~\ref{sec:subjects}.  It remains to
+evaluate the extent to which our observations would change when using
+different testing frameworks and build systems.
+Also, some of the selected subjects contain failing tests. Test
+failures may reduce the testing time due to early termination
+or even inflate the time (\eg, test waiting indefinitely for
+an unavailable resources).
+To mitigate this threat, we eliminated subjects with flaky tests and
+filtered projects with at least 90\% of the tests passing.
+Only 17\% of our subjects have failing tests.
+We carefully inspected our rawdata to identify and ignore these
+failures with JUnit's \CodeIn{@Ignore} annotation.
+
+\textit{Internal Validity:} Our results could be influenced by
+unintentional mistakes made by humans who interpreted survey data and
+implemented scripts and code to collect and analyze the data.
+For example, we developed JUnit runners to reproduce Maven's parallel
+configurations and implemented several scripts to automate our
+experiments (\eg, run tests and detect parallelism enabled by default
+in the subjects).
+All those tasks could bias our results.
+To mitigate those threats, the first two authors of this paper
+validated/inspected each other to increase chances of capturing
+unintentional mistakes.
+
+\textit{Construct Validity:} We considered a number of metrics in this
+study that could influence some of our interpretations.  For example,
+we measured number of test cases per suite, distribution of test costs
+in a suite, time to run a suite, etc.  In principle, these metrics may
+not reflect the main problems associated with test
+efficiency.
+
+% SECTION 7
+%%
+
+\section{Related Work}
+\label{sec:related}
+
+Regression testing research has focused mostly on test suite
+minimization, prioritization, reduction, and
+selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
+techniques are unsound (\ie{}, they do not guarantee that
+fault-revealing tests will be considered for testing).  The test
+selection technique
+Ekstazi~\cite{gligoric-etal-issta2015,celik-etal-fse2017} is an
+example of a sound regression testing technique. It conservatively
+computes which tests have been impacted by file changes.  A test is
+discarded for execution if it does not depend on any changed file
+dynamically reachable from execution.\Comment{ Curiously Ekstazi's
+  evaluation discovered subjects with parallelism enabled by
+  default.}\Comment{ \c{C}elik~\etal{}~\cite{} recently extended
+  Ekstazi to track files accessed outside JVM boundaries.} Important
+to note that regression testing techniques, including test selection,
+is complementary to test suite parallelization.
+
+ElectricTest~\cite{bell-etal-esecfse2015} is a tool for efficiently
+detecting data dependencies across test cases.  Dependency tracking is
+important as to avoid test flakiness when parallelizing test
+suites. ElectricTest observes reads and writes on global resources
+made by tests to identify these dependencies at low cost. We remain to
+investigate the impact of ElectricTest to reduce flakiness in
+unrestricted test suite parallelization.
+
+The use of the Single Instruction Multiple Data (SIMD) design has been
+previously explored in research to accelerate test
+execution~\cite{damorim-etal-issta2007,damorim-etal-tse2008,kim-etal-issre2012,nguyen-etal-icse2014,rajan-etal-ase2014,sen-etal-fse2015,yaneva-etal-issta2017}. The
+SIMD architecture, as implemented in modern GPUs, for instance, allows
+the execution of a given instruction simultaneously against multiple
+data.  For that reason, in principle, one test could be ran
+simultaneously against multiple inputs provided that multiple test
+inputs exist associated to that one test.  Recent
+work~\cite{rajan-etal-ase2014,yaneva-etal-issta2017} explored that
+idea to speedup test execution of embedded software using graphic
+cards. Although benchmarks indicate superior performance compared to
+traditional multicore CPUs, the use of the technology in broader
+settings is limited. For example, execution of more general programs
+can violate the SIMD's lock-step assumption on the control-flow of
+threads.  This violation would affect negatively performance.
+Furthermore, handling complex data is challenging in
+SIMD~\cite{damorim-etal-issta2007,damorim-etal-tse2008}.  The approach
+is promising when multiple input vectors exist for each test and the
+testing code heavily manipulates scalar data types.  The datasets used
+in those papers satisfied those constraints.
+
+Google~\cite{google-tap,google-ci} and
+Microsoft~\cite{prasad-shulte-ieee-microsoft-ci} have been creating
+distributed infrastructures to efficiently build massive amounts of
+code and run massive amounts of tests.  Those scenarios bring
+different and challenging problems such as deciding when to trigger
+the build under multiple file
+updates~\cite{memon-etal-icse17}. Although such distributed systems
+are targeted to extremely large scale code and test bases, the same
+ideas can be applied to handle the build process of large, albeit not
+as large, projects.  For example,
+Gambi~\etal{}~\cite{gambi-etal-issta2017} recently proposed CUT, a
+tool to automatically parallelize JUnit tests on the cloud. The tool allows
+the developer to control resource allocation and deal with the project
+specific test dependencies.  Note that test suite parallelization is
+complementary to these high-level parallelism schemes.
+
+Continuous Integration (CI) services, such as Travis CI~\cite{travis},
+are becoming widely used in the open-source
+community~\cite{hilton-etal-ase2016,vasilescu-etal-fse2015}. Accelerating
+time to run tests in CI is important as to reduce the period between
+test report updates.  Module-level regression
+testing~\cite{vasic-etal-fse2017}, for example, can be helpful in that
+setting. It is important to note that test failures are more common in
+CI compared to an overnight run or a local run, for instance.  This
+can happen because of semantic merge conflicts~\cite{brun-etal-fse11},
+for instance.  As such effect can impact developer's perception and
+tolerance towards failures, we are curious to know if developers would
+be willing to receive more frequent test reports at the expense of
+potentially increasing failure rates due to flakiness caused by
+parallelism.
+
+% SECTION 8
+%%
+
+\section{Conclusions}
+
+Testing is expensive.  Despite all advances in regression testing
+research, dealing with high testing costs remains an important problem
+in Software Engineering.  This paper reports our findings on the usage
+and impact of test execution parallelization in open-source projects.
+Multicore CPUs are widely available today.  Testing frameworks and
+build systems that capitalize on these machines also became popular.
+Despite some resistance observed from practitioners, our results
+suggest that parallelization can be used in many cases without
+sacrificing reliability. More research needs to be done to improve
+automation (\eg{}, breaking test dependencies, refactoring test
+suites, enforcing safe test schedules) as to safely optimize parallel
+execution.  The artifacts we produced as result of this study are
+available from the following web page:
+
+\begin{center}
+  \webpage{}
+\end{center}
+
+%\appendices
+%\section{Proof of the First Zonklar Equation}
+%Appendix one text goes here.
+
+% you can choose not to have a title for an appendix
+% if you want by leaving the argument blank
+%\section{}
+%Appendix two text goes here.
+
+% use section* for acknowledgment
+%\ifCLASSOPTIONcompsoc
+  % The Computer Society usually uses the plural form
+%  \section*{Acknowledgments}
+%\else
+  % regular IEEE prefers the singular form
+%  \section*{Acknowledgment}
+%\fi
+
+%The authors would like to thank...
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+\balance
+\bibliographystyle{plain}
+\bibliography{tmp}
+
+\begin{IEEEbiography}{Michael Shell}
+Biography text here.
+\end{IEEEbiography}
+
+% if you will not have a photo at all:
+\begin{IEEEbiographynophoto}{John Doe}
+Biography text here.
+\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+\begin{IEEEbiographynophoto}{Jane Doe}
+Biography text here.
+\end{IEEEbiographynophoto}
+
+% that's all folks
+\end{document}

### 2019-05-20 tse19/R/genplot.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+NAME="testcost"
+Rscript --vanilla ${NAME}.r "testcost-med"
+Rscript --vanilla ${NAME}.r "testcost-long"
+

### 2019-05-20 tse19/R/relativeSD.r

@@ -1,0 +1,18 @@
+library(ggplot2)
+
+pdf(file = "relativeSD.pdf", width = 5, height = 2.5)
+
+dat <- read.csv("testcost.csv", header = T) 
+
+p <- ggplot(dat, aes(x=", y=dat$V2))
+
+p +
+geom_boxplot() +
+coord_flip() +
+theme(axis.title.y=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks.y=element_blank()
+) +
+labs(y="Relative Standard Deviation (RSD)")
+
+aux <- dev.off()

### 2019-05-20 tse19/R/scalability/scalability.r

@@ -1,0 +1,14 @@
+library("ggplot2")
+library("grDevices")
+
+cairo_pdf(file = "scalability.pdf", width = 3, height = 1.5)
+dataframe <- read.csv(file="scalability_reduced.data", header=TRUE, sep=",")
+
+#boxplot(time~numcores, data=dataframe, ylab="time (m)", xlab="# cores", ylim=c(0,max(dataframe$time)+1), cex.lab=1.8, cex.axis=1.6)
+ggplot(dataframe, aes(numcores, time, group = numcores)) +
+  geom_boxplot(outlier.shape = NA) +
+  theme_bw() +
+  scale_x_continuous(breaks = dataframe$numcores, labels = dataframe$numcores) +
+  labs(x = "# cores", y = "Time (m)")
+
+aux <- dev.off()

### 2019-05-20 tse19/main.tex
Added Comment

@@
 (\eg{}, \emph{pom.xml}) in the directory structure. 
+\textcolor{red}{[S.J: Hoje em dia ja e possivel buscar projeto que contenha determinado arquivo pelo Github API (ex.: pom.xml), SearchCode, foi utilizado PyGithub para filtrar os projetos ]}
 
@@
 Our final set of subjects contains \numSubjs{} projects. 
+ \textcolor{red}{[S.J: Utilizando o script desse experimento, Foram encontrado um total de 4111, onde 3154 nao eram Maven e 957 eram Maven. Dos 3154 que nao eram Maven, 2302 eram Gradle (73\%) ]}
 

### 2019-05-21 OLD/journal/paper.tex
moving dirs

--- 2019-05-20 tse19/main.tex
@@
 \documentclass[10pt,journal,compsoc]{IEEEtran}
-
-\usepackage{graphicx}
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage{cite}
-\fi
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-
-\input{macros}
 
@@
 \usepackage{booktabs}
-\usepackage{amsmath} 
 \usepackage{subfigure} 
@@
 \usepackage{mdframed}
-\usepackage{xcolor}
-
-% correct bad hyphenation here
+
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage{cite}
+\fi
+\usepackage{amsmath}
+\interdisplaylinepenalty=2500
+
 \hyphenation{op-tical net-works semi-conduc-tor}
 
+\input{macros}
+
 \begin{document}
 
-\title{Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact}
-
-\author{Sotero Junior, Jeanderson Candido, Marcio Ribeiro
-        and~Marcelo d'Amorim
-
-% <-this % stops a space
-\IEEEcompsocitemizethanks{
-\IEEEcompsocthanksitem 
-S. Junior and M. d'Amorim are with the Informatics Center, Federal Univer- sity of Pernambuco, Recife, PE 50732-970, Brazil.
-
-E-mail: \{srsj2, damorim\}@cin.ufpe.br
-
-\IEEEcompsocthanksitem 
-M. Ribeiro was with the Computing Institute, Federal University of Alagoas, Maceio, AL 57072-900, Brazil.
-
-E-mail: marcio@ic.ufal.br
-}% <-this % stops an unwanted space
-\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-
-% The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~45, No.~6, June~2019}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+\title{Test Suite Parallelization in Open-Source Projects: A Study on Its Usage and Impact}
+
+\author{Jeanderson~Candido,
+        Luis~Melo,
+        and~Marcelo~d'Amorim% <-this % stops a space
+\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J. Candido, L. Melo, and M. d'Amorim
+are affiliated to the Department of Computer Science, Federal University of
+Pernambuco, Recife, PE, 50740-560 Brazil.\protect\\
+% note need leading \protect in front of \\ to get a newline within \thanks as
+% \\ is fragile and will error, could use \hfil\break instead.
+E-mail: \{jbc5, lhsm, damorim\}@cin.ufpe.br}
+\Comment{\thanks{Manuscript received \Fix{April 19, 2005}; revised \Fix{August 26, 2015}.}}}
 
@@
 in running tests.
-\end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-test suite, parallelization, Maven, Java, Software Engineering.
-\end{IEEEkeywords}}
+\end{abstract}}
 
@@
 \maketitle
+
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEtitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
+% or transmag modes are not selected <OR> if conference mode is selected 
+% - because all conference papers position the abstract like regular
+% papers do.
 \IEEEdisplaynontitleabstractindextext
+% \IEEEdisplaynontitleabstractindextext has no effect when using
+% compsoc or transmag under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
 
-\IEEEraisesectionheading{
-\section{Introduction}
-\label{sec:introduction}}
-
-\input{intro}
-
-%\hfill lorem ipsum
-
-%\hfill August 26, 2015
-
-% SECTION 2
+\IEEEraisesectionheading{\section{Introduction}\label{sec:intro}}
+
+Dealing with high testing costs has been an important problem in
+software engineering research and industrial practice.  Several
+approaches have been proposed in the research literature to address
+this problem, with the focus mainly on test suite minimization,
+prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
+In industry, the focus has been mainly on distributing the testing
+workload.  Evidence of this are the Google TAP
+system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
+system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
+distributed infrastructures to efficiently build massive amounts of
+code and run tests.  Building in-house server clusters is also a
+popular mechanism to distribute testing workloads.  For example, as of
+August 2013, the test suite of the Groupon PWA system, which powers
+the \url{groupon.com} website, included over 19K tests.  To run all
+those tests under 10m, Groupon used a cluster of 4 computers with 24
+cores each~\cite{kim-etal-fse2013}.
+
+At large organizations, the alternative of renting cloud
+services~\cite{cloud-services} or even building proprietary
+infrastructures for running tests is a legitimate approach to mitigate
+the regression testing problem.  However, for projects with modest
+ or nonexistent budgets and yet relatively heavy testing workloads, this solution may
+not be economically viable.  For these cases, the use of commodity
+hardware\Comment{ (\eg{}, existing workstations)} is an attractive
+solution for running tests.  The proliferation of
+multi-core CPUs and the increasing popularization of testing
+frameworks and build systems, which today provide mature support for
+parallelization, enable\Comment{ test execution} speedups through increased CPU
+usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
+for cost-effective test execution and supply of relatively inexpensive
+testing infrastructures~---~inspired us to investigate 
+test suite parallelization in practice.
+
+This paper reports on an empirical study we conducted to analyze the
+usage and impact of low-level parallelization to speed up testing in
+open-source projects.  This is a relevant problem given the tremendous
+popularity of open-source development and regression testing
+research~\cite{yoo-harman-stvr2012}.  Note that parallelization is
+complementary to other approaches to mitigate testing costs such as
+(safe) test
+selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
+and continuous integration~\cite{Saff:2003:RWD:951952.952340}.
+
+The dimensions of analysis we considered in this study are (i)
+relevance, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
+dimension \emph{relevance} focuses on the potential of parallelization
+to reduce testing costs. In the limit, parallelization would be
+fruitless if all projects had short-running test suites, for example.  The
+dimension \emph{adoption} evaluates how often existing open-source
+projects use parallelization schemes and how developers involved in
+costly projects (not using test suite parallelization) perceive this
+technology.  It is important to measure resistance of practitioners to
+the technology and to understand their reasons.  The dimension
+\emph{speedup} evaluates the observed impact of
+parallelization\Comment{~---~when used in selected open-source
+  projects~---~} in running times.  Finally, the dimension
+\emph{tradeoffs} evaluates the relationship between speedups obtained
+with parallelization and issues that arise 
+when running tests in parallel, including test
+flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly summarize our findings
+in the following.
+
+\noindent\emph{Relevance.}~To assess how prevalent long-running test suites
+are we selected \numSubjs{} popular Java projects from \github{} containing
+Maven build files~\cite{maven}.  Section~\ref{sec:eval} details our methodology
+to select subjects and to isolate our experiments from environmental noise.
+Results indicate that nearly \percentMedLongRunning{} of the projects take at
+least 1m to run and \percentLongRunning{} of the projects take at least 5m to
+run.  Considering the \numMedLong{} projects with test suites taking longer than
+a minute to run, the average execution time of a test suite was
+\averageMedLongRunning{}.  Results also show that test cases are typically
+short-running, typically taking less than half a second to run.  Furthermore, we
+found that only in rare cases few test cases monopolize the overall time to run
+a test suite.
+
+\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
+adoption.  First, we measured usage of parallelism in open-source projects.
+Then, we ran a survey with developers to understand the reasons that could
+explain resistance to using the technology.\Comment{ For the quantitative
+analysis we checked both statically (parsing build files) and dynamically
+(monitoring execution of build files) for the presence of parallelization.}
+Considering only the projects whose test suites take longer than a minute to
+run, we found that only \percentParallelUpdated{} of them use parallelism.  We
+also contacted developers from a selection of costly projects that did not use
+parallelization to understand the reasons for not using parallelization.
+Dealing with concurrency-related issues (\eg{}, the extra work to organize test
+suite to avoid concurrency errors) and the availability of continuous
+integration services were the most frequently answered reasons for not
+considering parallelization.
+
+\noindent\emph{Speedups.}~We used two setups to measure speedup.  In
+one setup we selected projects that run test suites in parallel by
+default, used a machine with eight virtual CPUs, and compared
+execution times of test suites with and withouth (default) parallelism
+enabled. In the other setup, we evaluated how execution scales with
+the number of available cores in the machine. For that, we used a more
+powerful machine with 80 virtual CPUs (40 cores with two native
+threads on each core). Considering the first setup, results indicate
+that the average speedup of parallelization was \avgSpeedup{}x.
+Although we found cases with very high speedups (\eg{}, 28.8x for
+project Jcabi), we also found cases where the speedups were not very
+significant.  Considering the scalability experiment, we noticed,
+perhaps as expected, that parallelization obtained with forking JVMs
+scales with the number of cores but the speedup is bounded by
+long-running test classes.
+
+\noindent\emph{Tradeoffs.}~Test flakiness is a central concern when running
+tests in parallel.  Dependent tests can be affected by different schedulings of
+test methods and classes.  This dimension of the study measures the impact of
+different parallel configurations on test flakiness and speedup.  Overall,
+results indicate that configurations that fork JVMs do not achieve speedups as
+high as other more-aggressive configurations, but they manifest much lower
+flakiness ratios.
+
+Our observations may trigger different actions:
+
+%\setlist[itemize]{leftmargin=1.1em}
+\begin{itemize}
+\item \emph{Incentivize forking.}~Forked JVMs manifest very low rates
+  of test flakiness.  Developers of projects with long-running test
+  suites should consider using that feature, which is available in
+  modern build systems today (\eg{}, Maven).
+\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
+  impressive speedups at the expense of sometimes impressive rates of
+  flakiness.  Breaking test dependencies (with
+  ElectricTest~\cite{bell-etal-esecfse2015}, for example) to avoid flakiness is advised for developers with
+  greater interest in efficiency.
+\item \emph{Refactor tests for load balancing.}~The configuration with
+  forked JVMs scales
+  better\Comment{ with the number of cores} when the test workload is balanced
+  across testing classes.  Automated refactoring could help balance
+  the workload in scenarios where developers are not willing to change
+  test code but have access to machines with a high number of cores.
+\item \emph{Improve debugging for build systems.}~While preparing our
+  experiments, we found scenarios\Comment{, related to test
+    parallelization,} where Maven's executions did not reflect
+  corresponding JUnit's executions.\Comment{(Docker reproduction scripts
+  available.)} Those issues can hinder developers from using parallel
+  testing. Better debugging support for build systems could help
+  on that. 
+\end{itemize}
+
+The artifacts we produced as result of this study are available from
+the following web page \webpage{}.
+
 \section{Parallel Execution of Test Suites}
+\label{sec:modes}
+
 Figure~\ref{fig:levels} illustrates different levels where
@@
 \end{wrapfigure}
-
 distribute test execution.  The lowest levels denote parallelism
@@
 
-% SECTION 3
-
 \section{Objects of Analysis}
@@
   \github{} API considers the predominant language as the primary
-  language.}, (2) the project has at least 100 stars, (3) the latest
-update was on or after January 1st, 2016, and (4) the \emph{readme}
-file contains the string \emph{mvn}.  We focused on Java for its
-popularity.  Although there is no clearcut limit on the number of
-\github{} stars~\cite{github-stars} to define relevant projects, we
-observed that one hundred stars was enough to eliminate trivial subjects. The
-third
-criteria serves to skip projects without recent activity. The fourth
-criteria is an approximation to find Maven projects.\Comment{ The
-  rationale is that if the string \emph{mvn} exists in the
-  \emph{readme} file, it may represent a Maven call (\eg, to compile
-or to test the project).} We focused on Maven for its popularity on
-Java projects.  Important to highlight that, as of now, the
-\github{}'s search API can only reflect contents from repository
-statistics (\eg, number of forks, main programming language); it does
-not provide a feature to search for projects containing certain files
-(\eg{}, \emph{pom.xml}) in the directory structure.
-
-Figure~\ref{fig:subject-query} illustrates the query to the \github{}
-API as an HTTP request.   The result set is sorted
-in descending order of stars.
+  language.}, (2) the project has at least 100 stars, and (3) the latest
+update was on or after \Jbc{January 1st, 2017}.
+Although there is no clearcut limit on the number of \github{}
+stars~\cite{github-stars} to define relevant projects, we observed that one
+hundred stars was enough to eliminate trivial subjects.
+The third criteria serves to skip projects without recent activity.
+\Jbc{We focused on Java for its popularity.
+It is important to highlight that the \github{}'s search API imposes a limit of
+returning only the top 1000 results for a single query.
+To overcome this limitation and have a larger sample set, we divided our
+original query into multiple queries over subsequent periods of time and
+considered the union the results.}
+% Important to highlight that, as of now, the \github{}'s search API can only
+% reflect contents from repository statistics (\eg, number of forks, main
+% programming language); it does not provide a feature to search for projects
+% containing certain files (\eg{}, \emph{pom.xml}) in the directory structure.
+Figure~\ref{fig:subject-query} illustrates a query to the \github{} API as
+an HTTP request.
 
@@
 https://api.github.com/search/repositories?q=language:java
- +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
+ +stars:>=100+pushed:2017-01-01..2017-02-01&page=1
 \end{lstlisting}
   \vspace{-3mm}
-  \caption{\label{fig:subject-query} Query to the \github{} API for
-  projects that (1) use Java, (2) contains at least 100
-  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
-  the string \emph{mvn} in the \emph{readme} file.}
-  \vspace{-3mm}
+  \caption{\label{fig:subject-query} Query to the \github{} API for projects
+  that (1) use Java, (2) contains at least 100 stars, (3) has been updated
+  between January 1st and February 1st of 2017.}
+  \vspace{-5mm}
 \end{figure}
 
-We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
-filtered those
-containing a \pomf{} file in the root directory.\Comment{  A Maven project may
-contain several sub-modules with multiple \pomf{} files.}
-Then, considering this set of Maven projects, we
-executed the tests for \SubjectsReruns{} times to discard those projects with
-issues
-in the build file and non-deterministic results observed from sequential
-executions.
-As of August 25th 2017, our search criteria returned a total of
-\SubjectsGithub{}
-subjects.
-From this set of projects,
-\SubjectsGithubNotMaven{} projects were not Maven or did not have a
-\pomf{} in the root directory, 
-\SubjectsGithubNotTestable{} projects were not considered because of
-environment incompatibility
-(\eg, missing\Comment{ required web browser or database management
-system}~DBMS),
-\SubjectsGithubFlaky{} projects were discarded because of
-``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
-or fails under
-the same circumstances leading to non-deterministic results.
-As some of our experiments consist of running tests on different
-threads, we ignored these projects as it would be impractical
-to identify whether a test failed due to a race condition or some
+We used the following methodology to select projects for analysis.
+After obtaining the list of potential projects from GitHub, we filtered those
+with Maven support (\ie, contains a \pomf{} file in the root directory).
+We focused on Maven for its popularity in Java projects.
+Then, considering this set of Maven projects, we executed the tests for
+\SubjectsReruns{} times to discard those projects with issues in the build file
+and non-deterministic results observed from sequential executions.
+
+As of December 12th 2017, our search criteria returned a total of
+\SubjectsGithub{} projects, and we identified \SubjectsMaven{} Maven projects.
+\Fix{From this set of projects, \SubjectsGithubNotTestable{} projects were not
+considered because of environment incompatibility (\eg, missing DBMS) and
+\SubjectsGithubFlaky{} projects were discarded because of ``flaky
+tests''~\cite{luo-etal-fse2014}.
+A ``flaky'' test is a test that passes or fails under the same circumstances
+leading to non-deterministic results.  As some of our experiments consist of
+running tests on different threads, we ignored these projects as it would be
+impractical to identify whether a test failed due to a race condition or some
 other source of flakiness.
-From the remaining \SubjectsGithubConsistant{} projects with
-deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
-projects with \SuiteFailingThreshold{} or more failing tests as to
-reduce bias. For the
-remaining projects with failing tests, we used the JUnit's
+From the remaining \SubjectsGithubConsistant{} projects with deterministic
+results, we eliminated \SubjectsGithubTooManyFailures{} projects with
+\SuiteFailingThreshold{} or more failing tests as to reduce bias.
+For the remaining projects with failing tests, we used the JUnit's
 \CodeIn{@Ignore} annotation to ignore failing tests.
-Our final set of subjects contains \numSubjs{} projects.
-
- Figure~\ref{fig:subjects} summarizes our sample set.
-
-\begin{figure}[ht]
-  \vspace{-5mm}
+Our final set of subjects
+contains \numSubjs{} projects.
+Figure~\ref{fig:subjects} summarizes our sample set.}
+
+\begin{figure}[h!]
   \centering
@@
 \label{sec:setup}
-
 To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
 machine with eight virtual CPUs (four cores with two native threads each) and
-16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
-used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
-suites. To process test results and generate plots we used Python\Comment{ 3.4},
-Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
-replication on our website~\cite{ourwebpage}.  This includes supporting
-scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
-data)} and the full list of projects.
-
-% SECTION 4
+16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).
+We used Java 8 and Maven 3.5.2 to build projects and run test suites.  To
+process test results and generate plots we used Python, Bash, R and Ruby.
+All source artifacts are publicly available for replication on our
+website~\cite{ourwebpage}.
+This includes supporting scripts and the full list of projects.
 
@@
 \begin{itemize}
-\item Feasibility
+\item Relevance
   \begin{itemize}
@@
 
-\subsection{Feasibility}
+\subsection{Relevance}
 \label{sec:rqA}
@@
 
-% SECTION 5
-
 \section{Discussion}
@@
 
-% SECTION 6
-%%
-
 \section{Threats to Validity}
@@
 efficiency.
-
-% SECTION 7
-%%
 
@@
 
-% SECTION 8
-%%
-
 \section{Conclusions}
@@
 
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section{}
-%Appendix two text goes here.
-
-% use section* for acknowledgment
-%\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-%  \section*{Acknowledgments}
-%\else
-  % regular IEEE prefers the singular form
-%  \section*{Acknowledgment}
-%\fi
-
-%The authors would like to thank...
+%% \section*{Acknowledgements}
+%% Jean(derson) and Luis are supported by FACEPE scholarphips
+%% IBPG-0632-1.03/15 and IBPG-1175-1.03/16, respectively.  This work was
+%% partially supported by CNPq grants 457756/2014-4 and 203981/2014-6.
 
@@
 \balance
-\bibliographystyle{plain}
-\bibliography{tmp}
-
-\begin{IEEEbiography}{Michael Shell}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% that's all folks
+\bibliographystyle{IEEEtran}
+\bibliography{tmp.bib}
+
 \end{document}

### 2019-05-21 tse19/main.tex
quick pass on text

@@
 
-\author{Sotero Junior, Jeanderson Candido, Marcio Ribeiro
-        and~Marcelo d'Amorim
+\author{Sotero Junior, Jeanderson Candido, Marcio Ribeiro and~Marcelo d'Amorim
 
@@
 \IEEEcompsocthanksitem 
-S. Junior and M. d'Amorim are with the Informatics Center, Federal Univer- sity of Pernambuco, Recife, PE 50732-970, Brazil.
-
+S. Junior and M. d'Amorim are with the Universidade Federal de
+Pernambuco, Recife, PE, Brazil.
 E-mail: \{srsj2, damorim\}@cin.ufpe.br
@@
 \IEEEcompsocthanksitem 
-M. Ribeiro was with the Computing Institute, Federal University of Alagoas, Maceio, AL 57072-900, Brazil.
-
+J. Candido is with the Delft University of Technology, The Netherlands.
+E-mail: jeandersonbc@gmail.com
+
+\IEEEcompsocthanksitem 
+M. Ribeiro is with the Computing Institute, Federal University of Alagoas, Maceio, AL 57072-900, Brazil.
 E-mail: marcio@ic.ufal.br
@@
 Software Engineering.  Test suite parallelization is an important
-approach to address this problem.  This paper reports our findings on
+approach to address this problem. \Mar{Sotero, vc. atualizou estas
+  macros?}  Considering a set of \numSubjs{} Java projects we analyzed
+from \github\, we found that \percentMedLongRunning{} of the them
+contain long-running test suites, but parallelization features still
+seem underutilized in practice~---~only \percentParallelUpdated{} of
+projects with long-running test suites parallelize test
+execution. According to a survey we conducted, the main reason for
+adoption resistance was the concern to deal with concurrency issues
+that could result in test flakiness.
+%% This Results suggest that, on
+%% average, developers prefer high predictability than high performance
+%% in running tests.
+
+\Fix{revise...}
+This paper reports our findings on
 the usage and impact of test suite parallelization in open-source
-projects.\Comment{ This study brings to light the benefits and burdens
-  of that approach.} It provides recommendations to practitioners and
-tool developers to speed up test execution.
-
-Considering a set of \numSubjs{} popular Java projects we analyzed, we
-found that \percentMedLongRunning{} of the projects contain costly
-test suites but parallelization features still seem underutilized in
-practice~---~only \percentParallelUpdated{} of costly projects use
-parallelization.  The main reported reason for adoption resistance was
-the concern to deal with concurrency issues.  Results suggest that, on
-average, developers prefer high predictability than high performance
-in running tests.
+projects. It provides recommendations to practitioners and
+tool developers to speed up test execution. A tool is available to \Fix{...}.
+
 \end{abstract}
@@
 
-\input{intro}
+\IEEEPARstart{D}{ealing}
+with high testing costs has been an important problem in
+software engineering research and industrial practice.  Several
+approaches have been proposed in the research literature to address
+this problem, with the focus mainly on test suite minimization,
+prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
+In industry, the focus has been mainly on distributing the testing
+workload.  Evidence of this are the Google TAP
+system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
+system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
+distributed infrastructures to efficiently build massive amounts of
+code and run tests.  Building in-house server clusters is also a
+popular mechanism to distribute testing workloads.  For example, as of
+August 2013, the test suite of the Groupon PWA system, which powers
+the \url{groupon.com} website, included over 19K tests.  To run all
+those tests under 10m, Groupon used a cluster of 4 computers with 24
+cores each~\cite{kim-etal-fse2013}.
+
+At large organizations, the alternative of renting cloud
+services~\cite{cloud-services} or even building proprietary
+infrastructures for running tests is a legitimate approach to mitigate
+the regression testing problem.  However, for projects with modest
+ or nonexistent budgets and yet relatively heavy testing workloads, this solution may
+not be economically viable.  For these cases, the use of commodity
+hardware\Comment{ (\eg{}, existing workstations)} is an attractive
+solution for running tests.  The proliferation of
+multi-core CPUs and the increasing popularization of testing
+frameworks and build systems, which today provide mature support for
+parallelization, enable\Comment{ test execution} speedups through increased CPU
+usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
+for cost-effective test execution and supply of relatively inexpensive
+testing infrastructures~---~inspired us to investigate 
+test suite parallelization in practice.
+
+This paper reports on an empirical study we conducted to analyze the
+usage and impact of low-level parallelization to speed up testing in
+open-source projects.  This is a relevant problem given the tremendous
+popularity of open-source development and regression testing
+research~\cite{yoo-harman-stvr2012}.  Note that parallelization is
+complementary to other approaches to mitigate testing costs such as
+(safe) test
+selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
+and continuous integration~\cite{Saff:2003:RWD:951952.952340}.
+
+The dimensions of analysis we considered in this study are (i)
+feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
+dimension \emph{feasibility} measures the potential of parallelization
+to reduce testing costs.  In the limit, parallelization would be
+fruitless if all projects had short-running test suites or if the
+execution cost was dominated by a single test case in the suite.  The
+dimension \emph{adoption} evaluates how often existing open-source
+projects use parallelization schemes and how developers involved in
+costly projects (not using test suite parallelization) perceive this
+technology.  It is important to measure resistance of practitioners to
+the technology and to understand their reasons.  The dimension
+\emph{speedup} evaluates the observed impact of
+parallelization\Comment{~---~when used in selected open-source
+  projects~---~} in running times.  Finally, the dimension
+\emph{tradeoffs} evaluates the relationship between speedups obtained
+with parallelization and issues that arise 
+when running tests in parallel, including test
+flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly summarize our findings
+in the following.
+
+\noindent\emph{Feasibility.}~To assess how prevalent long-running test suites
+are we selected \numSubjs{} popular Java projects from \github{} containing
+Maven build files~\cite{maven}.  Section~\ref{sec:eval} details our methodology
+to select subjects and to isolate our experiments from environmental noise.
+Results indicate that nearly \percentMedLongRunning{} of the projects take at
+least 1m to run and \percentLongRunning{} of the projects take at least 5m to
+run.  Considering the \numMedLong{} projects with test suites taking longer than
+a minute to run, the average execution time of a test suite was
+\averageMedLongRunning{}.  Results also show that test cases are typically
+short-running, typically taking less than half a second to run.  Furthermore, we
+found that only in rare cases few test cases monopolize the overall time to run
+a test suite.
+
+\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
+adoption.  First, we measured usage of parallelism in open-source projects.
+Then, we ran a survey with developers to understand the reasons that could
+explain resistance to using the technology.\Comment{ For the quantitative
+analysis we checked both statically (parsing build files) and dynamically
+(monitoring execution of build files) for the presence of parallelization.}
+Considering only the projects whose test suites take longer than a minute to
+run, we found that only \percentParallelUpdated{} of them use parallelism.  We
+also contacted developers from a selection of costly projects that did not use
+parallelization to understand the reasons for not using parallelization.
+Dealing with concurrency-related issues (\eg{}, the extra work to organize test
+suite to avoid concurrency errors) and the availability of continuous
+integration services were the most frequently answered reasons for not
+considering parallelization.
+
+\noindent\emph{Speedups.}~We used two setups to measure speedups.  In one setup
+we measured speedups obtained on projects that run test suites in parallel by
+default.  In the other setup, we evaluated how execution scales with the number
+of available cores in the machine.\Comment{We did not change parallel
+configurations on that setup.  For comparison, we disabled parallel execution to
+obtain the running time of a sequential execution.}  Considering the first
+setup, results indicate that the average speedup of parallelization was
+\avgSpeedup{}x.  Although we found cases with very high speedups (\eg{}, 28.8x
+for project Jcabi), we also found cases where the speedups were not very
+significant.  Considering the scalability experiment, we noticed, perhaps as
+expected, that parallelization obtained with forking JVMs scales with the number
+of cores but the speedups are bounded by long-running test classes.
+
+\noindent\emph{Tradeoffs.}~Test flakiness is a central concern when running
+tests in parallel.  Dependent tests can be affected by different schedulings of
+test methods and classes.  This dimension of the study measures the impact of
+different parallel configurations on test flakiness and speedup.  Overall,
+results indicate that configurations that fork JVMs do not achieve speedups as
+high as other more-aggressive configurations, but they manifest much lower
+flakiness ratios.
+
+Our observations may trigger different actions:
+
+%\setlist[itemize]{leftmargin=1.1em}
+\begin{itemize}
+\item \emph{Incentivize forking.}~Forked JVMs manifest very low rates
+  of test flakiness.  Developers of projects with long-running test
+  suites should consider using that feature, which is available in
+  modern build systems today (\eg{}, Maven).
+\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
+  impressive speedups at the expense of sometimes impressive rates of
+  flakiness.  Breaking test dependencies (with
+  ElectricTest~\cite{bell-etal-esecfse2015}, for example) to avoid flakiness is advised for developers with
+  greater interest in efficiency.
+\item \emph{Refactor tests for load balancing.}~The configuration with
+  forked JVMs scales
+  better\Comment{ with the number of cores} when the test workload is balanced
+  across testing classes.  Automated refactoring could help balance
+  the workload in scenarios where developers are not willing to change
+  test code but have access to machines with a high number of cores.
+\item \emph{Improve debugging for build systems.}~While preparing our
+  experiments, we found scenarios\Comment{, related to test
+    parallelization,} where Maven's executions did not reflect
+  corresponding JUnit's executions.\Comment{(Docker reproduction scripts
+  available.)} Those issues can hinder developers from using parallel
+  testing. Better debugging support for build systems could help
+  on that. 
+\end{itemize}
+
+The artifacts we produced as result of this study are available from
+the following web page \webpage{}.
 

### 2019-05-21 tse19/main.tex
quick pass on intro

@@
 \begin{abstract}
-Dealing with high testing costs remains an important problem in
+Dealing with high costs of testing remains an important problem in
 Software Engineering.  Test suite parallelization is an important
@@
 
-\IEEEPARstart{D}{ealing}
-with high testing costs has been an important problem in
-software engineering research and industrial practice.  Several
-approaches have been proposed in the research literature to address
+\IEEEPARstart{D}{ealing} with high testing costs has been an important
+problem in software engineering research and industrial practice.
+Several approaches have been proposed in the literature to address
 this problem, with the focus mainly on test suite minimization,
@@
 distributed infrastructures to efficiently build massive amounts of
-code and run tests.  Building in-house server clusters is also a
-popular mechanism to distribute testing workloads.  For example, as of
-August 2013, the test suite of the Groupon PWA system, which powers
+code and run tests.
+
+%Distributing testing workloads in-house is also a
+%viable solution at smaller-size organizations.
+
+At large organizations, the alternative of renting cloud
+services~\cite{cloud-services} or even building proprietary
+infrastructures for building and running tests is a legitimate
+approach to mitigate the regression testing problem.  For example, as
+of August 2013, the test suite of the Groupon PWA system, which powers
 the \url{groupon.com} website, included over 19K tests.  To run all
 those tests under 10m, Groupon used a cluster of 4 computers with 24
-cores each~\cite{kim-etal-fse2013}.
-
-At large organizations, the alternative of renting cloud
-services~\cite{cloud-services} or even building proprietary
-infrastructures for running tests is a legitimate approach to mitigate
-the regression testing problem.  However, for projects with modest
- or nonexistent budgets and yet relatively heavy testing workloads, this solution may
-not be economically viable.  For these cases, the use of commodity
-hardware\Comment{ (\eg{}, existing workstations)} is an attractive
-solution for running tests.  The proliferation of
+cores each~\cite{kim-etal-fse2013}. However, for projects with modest
+or nonexistent budgets and yet relatively heavy testing workloads,
+this solution may not be economically viable.  For these cases, the
+use of commodity hardware\Comment{ (\eg{}, existing workstations)} is
+an attractive solution for running tests.  The proliferation of
 multi-core CPUs and the increasing popularization of testing
 frameworks and build systems, which today provide mature support for
-parallelization, enable\Comment{ test execution} speedups through increased CPU
-usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
-for cost-effective test execution and supply of relatively inexpensive
-testing infrastructures~---~inspired us to investigate 
-test suite parallelization in practice.
+parallelization, enable speedups through
+increased CPU usage~(see Section~\ref{sec:background}).  These two
+elements~---~demand for cost-effective test execution and supply of
+relatively inexpensive testing infrastructures~---~inspired us to
+investigate test suite parallelization in practice.
 
@@
 selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
-and continuous integration~\cite{Saff:2003:RWD:951952.952340}.
-
-The dimensions of analysis we considered in this study are (i)
-feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
-dimension \emph{feasibility} measures the potential of parallelization
-to reduce testing costs.  In the limit, parallelization would be
-fruitless if all projects had short-running test suites or if the
-execution cost was dominated by a single test case in the suite.  The
-dimension \emph{adoption} evaluates how often existing open-source
-projects use parallelization schemes and how developers involved in
-costly projects (not using test suite parallelization) perceive this
-technology.  It is important to measure resistance of practitioners to
-the technology and to understand their reasons.  The dimension
-\emph{speedup} evaluates the observed impact of
-parallelization\Comment{~---~when used in selected open-source
-  projects~---~} in running times.  Finally, the dimension
+and continuous
+integration~\cite{Saff:2003:RWD:951952.952340}.\Mar{revisit this later
+  on...} In addition, we propose a solution to unleash the power of
+test parallelization reducing (\Fix{eliminating?}) test flakiness due
+to race conditions.
+
+This study covers the following dimensions of interest
+(i)~feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.
+The dimension \emph{feasibility} measures the potential of
+parallelization to reduce testing costs.  In the limit,
+parallelization would be fruitless if all projects had short-running
+test suites or if the execution cost was dominated by a single test
+case in the suite.  The dimension \emph{adoption} evaluates how often
+existing open-source projects use parallelization schemes and how
+developers involved in costly projects---\ie{}, project not using test suite
+parallelization---perceive this technology.  It is important to evaluate
+resistance of practitioners to the technology and to understand their
+reasons.  The \emph{speedup} dimension evaluates the observed impact
+of parallelization in running times on projects that already use it.  Finally, the dimension
 \emph{tradeoffs} evaluates the relationship between speedups obtained
-with parallelization and issues that arise 
-when running tests in parallel, including test
-flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly summarize our findings
-in the following.
+with parallelization and issues that arise when running tests in
+parallel, including test
+flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly
+summarize our findings in the following.
+
+\Mar{We need to reorganize this a bit as to accomodate the new
+  addition to the paper...}
 
@@
 % SECTION 2
-\section{Parallel Execution of Test Suites}
+\section{\label{sec:background}Parallel Execution of Test Suites}
 Figure~\ref{fig:levels} illustrates different levels where

### 2019-05-22 tse19/main.tex
pass on section 2

@@
 \Mar{We need to reorganize this a bit as to accomodate the new
-  addition to the paper...}
+  addition to the paper...Revisit this later...}
 
@@
 \section{\label{sec:background}Parallel Execution of Test Suites}
-Figure~\ref{fig:levels} illustrates different levels where
-parallelism in test execution can be obtained.
-The highest level indicates
-parallelism obtained through different machines on the
-network.  For instance, using virtual machines from a cloud service to
+
 \begin{wrapfigure}{r}{0.13\textwidth}  
@@
 \end{wrapfigure}
-
-distribute test execution.  The lowest levels denote parallelism
-obtained within a single machine.  These levels are complementary:
-the lowest levels leverage the computing power of server
-nodes whereas the highest level leverages the aggregate processing
-power of a network of machines.
-This paper focuses on low-level parallelism, where computation can be
-offloaded at different CPUs within a machine and at different threads
-within each CPU.  This form of parallelism is enabled through build
-systems (spawning processes in different CPUs) and testing frameworks
-(spawning threads in one given CPU).  It is important to note that a variety
-of testing frameworks provide today support for parallel test
-execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng}, and
-NUnit~\cite{nunit}) as to benefit from the available power of popular multi-core processors.
-In the following, we elaborate relevant features of testing frameworks
-and build systems for parallelization.  We focused on Java, Maven, and JUnit but the
-discussion can be generalized to other language and tools.
+This section explains basic concepts related to test parallelization
+in Java projects. Figure~\ref{fig:levels} illustrates different levels
+of parallelism in test execution.  The highest level indicates
+parallelism obtained through different machines on the network. For
+instance, using virtual machines from a cloud service to distribute
+test workload. The Google TAP~\cite{google-tap,google-ci} and the
+Microsoft CloudBuild~\cite{prasad-shulte-ieee-microsoft-ci} systems
+are examples of this kind of parallelization. The lowest levels
+illustrate parallelism obtained within a single machine. These levels
+are complementary to each other: the lowest levels leverage the
+computing power of individual nodes whereas the highest level
+leverages the aggregate processing power of a network of
+machines. This paper focuses on low-level parallelism, where
+computation can be offloaded at different CPUs within a machine and at
+different threads within each CPU.  This form of parallelism is
+enabled through build systems---by spawning processes in different
+CPUs---and testing frameworks---by spawning threads in one given CPU.
+It is important to note that a variety of testing frameworks provide
+today support for parallel test execution (e.g.,
+JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit})
+as to benefit from the available power of popular multi-core
+processors.  In the following, we elaborate relevant features of
+testing frameworks and build systems for parallelization.  We focused
+on Java, Maven, and JUnit but the discussion can be generalized to
+other language and tools.
 
@@
       (\SeqClassParMeth).}~This configuration corresponds to running
-    test classes sequentially, but running test methods from those
+    test classes sequentially, but running the test methods from those
     classes concurrently.
@@
 
-Notice that an important aspect in deciding which configuration to use (or in
-designing new test suites) is the possibility of race conditions on shared data
-during execution.  Data sharing can occur, for example, through state that is
-reachable from statically-declared variables in the program or through variables
-declared within the scope of the test class or even through resources available
-on the file system and the network~\cite{luo-etal-fse2014}.  Considering data
-race avoidance, configuration \SeqClassParMeth{} is preferable over
-\ParClassSeqMeth{} when it is clear that test methods in a class do not
-manipulate shared state, which can be challenging to
-determine~\cite{bell-etal-esecfse2015}.  Similarly, \ParClassSeqMeth{} is
-preferable over \SeqClassParMeth{} when it is clear that several test methods in
-a class perform operations involving shared data.  Configuration
-\ParClassParMeth{} does not restrict scheduling orderings.  Consequently, it is
-more likely to manifest data races during execution. Note that speedups depend
-on several factors, including the test suite size and distribution of test
-methods per class.
+An important aspect to consider when designing new test suites or when
+deciding which configuration to use for existing test suites is the
+possibility of race conditions on shared data during test
+execution. Although conceptually test cases are independent, they
+often share data\Fix{cite Mike's paper, bell-etal-esecfse2015}. Data
+sharing can occur, for example, through state that is reachable from
+statically-declared variables in the program or through variables
+declared within the scope of the test class or even through resources
+available on the file system and the network~\cite{luo-etal-fse2014}.
+
+Test flakiness and execution speedups depend on a number of
+factors. Considering flakiness, a configuration may be preferrable to
+another depending on the characteristics of the project and its test
+suite. For example, configuration \ParClassSeqMeth{} may be preferable
+over \SeqClassParMeth{} when it is clear that several test methods in
+a given class perform operations involving shared data. As
+configuration \ParClassParMeth{} does not restrict scheduling
+orderings, it is more likely to manifest data races during execution
+if there are sources of data sharing across test classes and their
+methods. Note also that speedups depend on several factors, including
+the test suite size and the distribution of test methods per class.
 
@@
   partition of the set of test classes to each JVM.  Test classes and methods
-  run sequentially within each JVM.
+  run sequentially within each JVM as \Seq\ does.
 \item
-  \textbf{Forked JVMs with parallel methods (\ForkParMeth).}~With
-  this configuration, the build system forks multiple JVMs, as
-  \ForkSeq{} does, but it runs test methods concurrently, as
-  \SeqClassParMeth{} does.
+  \textbf{Forked JVMs with parallel methods (\ForkParMeth).}~As
+  \ForkSeq{}, the build system forks multiple JVMs with this
+  configuration, but it runs test methods concurrently, as
+  \SeqClassParMeth{}.
 \end{itemize}
@@
 Maven made the design choice to only accept one test class at a time
-per forked process.  Maven offers an option to reuse JVMs that can be
-used to attenuate the potentially high cost of spawning new JVM
-processes on every test class (if reuse is enabled) and also to
-achieve test isolation (if reuse is disabled).
+per forked process. Intuitively, this option enables safe execution of
+tests when dependent methods exist across different classes\Fix{cite
+  Mike's work}. For the cases the developer prepared code against that
+threat, Maven offers an option to ``reuse'' JVMs as to avoid the
+non-negligible cost of creating JVM instances.
 
@@
         <forkCount>1C</forkCount>
+        <threadCount>5</threadCount>    
+        <parallel>methods</parallel>
         <reuseForks>true</reuseForks>        
-        <parallel>methods</parallel>
-        <threadCount>5</threadCount>
     </configuration>
@@
   \vspace{-4ex}
-  \caption{\label{fig:surefire} Configuration \ForkParMeth{} on
-    Maven.}
+  \caption{\label{fig:surefire} Fragment of a Maven pom.xml file with
+    an \ForkParMeth{} configuration.}
 \end{figure}
@@
 threads (\CodeIn{threadCount} parameter) to run test methods
-(\CodeIn{parallel} parameter) within each forked JVM.  Maven reuses
+(\CodeIn{parallel} parameter) within each forked JVM. In addition, Maven reuses
 created JVMs on subsequent forks when execution of a test class
-terminates (\CodeIn{reuseFork} parameter).
+terminates (\CodeIn{reuseFork} parameter). This is an example of a
+very aggressive setup, \ie{}, a setup that could substantially speedup
+execution but could introduce test flakiness if test code is not
+prepared for parallel execution.
 

### 2019-05-22 tse19/main.tex
pass on section 3 (leaving comments)

@@
 
+\Mar{Sotero, por favor, verifique que os numeros que estao aparecendo
+  no texto (usados nas macros) estao corretos! Vc. nao precisa
+  atualizar o ingles, mas se os dados nao estiverem corretos e vc. nao
+  explicar as mudanca (em portugues mesmo) nao vamos ter condicoes de
+  revisar.}
+
 We used \github{}'s search API~\cite{githubsearch} to identify
-projects that satisfy the following criteria: (1) the primary language
+projects that satisfy the following criteria:\Mar{alguma restricao
+  sobre o numero minimo de testes por projeto?$\rightarrow$} (1) the primary language
 is Java\footnote{In case of projects in multiple languages, the
@@
 update was on or after January 1st, 2016, and (4) the \emph{readme}
-file contains the string \emph{mvn}.  We focused on Java for its
+file contains the string \emph{mvn}\Mar{ver comentario abaixo}.  We focused on Java for its
 popularity.  Although there is no clearcut limit on the number of
@@
 (\eg{}, \emph{pom.xml}) in the directory structure. 
-\textcolor{red}{[S.J: Hoje em dia ja e possivel buscar projeto que contenha determinado arquivo pelo Github API (ex.: pom.xml), SearchCode, foi utilizado PyGithub para filtrar os projetos ]}
+\textcolor{red}{[S.J: Hoje em dia ja e possivel buscar projeto que
+    contenha determinado arquivo pelo Github API (ex.: pom.xml),
+    SearchCode, foi utilizado PyGithub para filtrar os projetos
+]}\Mar{Sotero, vc. usou ou nao usou este recurso da API do GitHub? Estou muito cofuso
+  aqui (por isto tive que interromper revisao). Se vc usou, este
+  quarto criterio precisa sair e entrar outro dizendo
+  explicitamente que usamos isto. Fora isto, logo abaixo vc. diz que
+  de um total de 4111, 3154 *nao* eram Maven. Mas, como eh possivel,
+  se vc. garante (atraves deste recurso) a presenca de um arquivo pom.xml?}
 
@@
   projects that (1) use Java, (2) contains at least 100
-  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
-  the string \emph{mvn} in the \emph{readme} file.}
+  stars, (3) has been updated on January 1st, 2016 (or later), (4) \Fix{contains
+  the string \emph{mvn} in the \emph{readme} file.}\Mar{Please revise.}}
   \vspace{-3mm}
@@
   \SuiteFailingThreshold{} of failing tests. We considered
-  \numSubjs{} projects to conduct our study.}
+  \numSubjs{} projects to conduct our study.\Mar{Sotero, este plot e
+    macros estao atualizados?}}
 \end{figure}
@@
 
+\Mar{Por que isto esta em uma secao ``Objects of Analysis''? Eh esta
+  mesmo a configuracao de maquina que vc. usou.}
 To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor

### 2019-05-28 tse19/main.tex
update section 2 and 3

@@
 approach to address this problem. \Mar{Sotero, vc. atualizou estas
-  macros?}  Considering a set of \numSubjs{} Java projects we analyzed
+  macros?} \textcolor{red}{[S.J: atualizado.]} Considering a set of \numSubjs{} Java projects we analyzed
 from \github\, we found that \percentMedLongRunning{} of the them
@@
 also contacted developers from a selection of costly projects that did not use
-parallelization to understand the reasons for not using parallelization.
+parallelization to understand the reasons for not using parallelization.\textcolor{red}{[S.J: nao fizemos isso.]}
 Dealing with concurrency-related issues (\eg{}, the extra work to organize test
@@
 setup, results indicate that the average speedup of parallelization was
-\avgSpeedup{}x.  Although we found cases with very high speedups (\eg{}, 28.8x
-for project Jcabi), we also found cases where the speedups were not very
+\avgSpeedup{}x.  Although we found cases with very high speedups (\eg{}, 5.77x
+for project Twilio Java), we also found cases where the speedups were not very
 significant.  Considering the scalability experiment, we noticed, perhaps as
@@
 
-\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
+\noindent\emph{Example:} Figure~\ref{fig:surefire} shows a
 fragment of a Maven configuration file, known as \pomf{}, highlighting
@@
   revisar.}
-
+\textcolor{red}{[S.J: Ok.]}
 We used \github{}'s search API~\cite{githubsearch} to identify
 projects that satisfy the following criteria:\Mar{alguma restricao
-  sobre o numero minimo de testes por projeto?$\rightarrow$} (1) the primary language
+  sobre o numero minimo de testes por projeto?$\rightarrow$}  \textcolor{red}{[S.J: Nao, mantemos as mesmas restricoes por ordem descendentes das stars]} (1) the primary language
 is Java\footnote{In case of projects in multiple languages, the
@@
 (\eg{}, \emph{pom.xml}) in the directory structure. 
-\textcolor{red}{[S.J: Hoje em dia ja e possivel buscar projeto que
-    contenha determinado arquivo pelo Github API (ex.: pom.xml),
-    SearchCode, foi utilizado PyGithub para filtrar os projetos
-]}\Mar{Sotero, vc. usou ou nao usou este recurso da API do GitHub? Estou muito cofuso
+\Mar{Sotero, vc. usou ou nao usou este recurso da API do GitHub? Estou muito cofuso
   aqui (por isto tive que interromper revisao). Se vc usou, este
@@
   se vc. garante (atraves deste recurso) a presenca de um arquivo pom.xml?}
+
+\textcolor{red}{[S.J: Tivemos dois momentos, o primeiro momento, usamos os mesmos criterios e script do paper ase17 para minerar os subjects.
+No segundo momento, usamos uma library python chamado PyGithub, ``https://github.com/PyGithub/PyGithub``, para gerenciar recursos do Github API.
+Utilizamos a funcao search\_code, que busca por especifico arquivo em repositorios ``pygithub.search\_code(pom in:pom.xml filename:pom.xml,order=desc)``, curl Github API ``https://api.github.com/search/code?q=pom in:pom.xml+filename:pom.xml``, e em seguida filtramos esses subjects com os crietrios (2) e (3) do paper.
+]}
 
@@
 executions.
-As of August 25th 2017, our search criteria returned a total of
+As of March 5th 2019, our search criteria returned a total of
 \SubjectsGithub{}
@@
 Our final set of subjects contains \numSubjs{} projects. 
- \textcolor{red}{[S.J: Utilizando o script desse experimento, Foram encontrado um total de 4111, onde 3154 nao eram Maven e 957 eram Maven. Dos 3154 que nao eram Maven, 2302 eram Gradle (73\%) ]}
+ \textcolor{red}{[S.J: Foi possivel observar que houve uma consideravel conversao de ferramenta de automacao, do Maven para Gradle,  dos 3154 subject que nao eram Maven, 2302 eram Gralde (73\%).
+Projeto como o MapDB, que e bastante citado no paper de ase17, atualmente converteu-se a Gradle.
+]}
 
@@
   \centering
-  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
+  \includegraphics[width=0.37\textwidth]{results/piechart-subjs.pdf}
   \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
@@
   \numSubjs{} projects to conduct our study.\Mar{Sotero, este plot e
-    macros estao atualizados?}}
+    macros estao atualizados?}} \textcolor{red}{[S.J:Atualizado.]}
 \end{figure}
@@
 \Mar{Por que isto esta em uma secao ``Objects of Analysis''? Eh esta
-  mesmo a configuracao de maquina que vc. usou.}
-To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
-machine with eight virtual CPUs (four cores with two native threads each) and
-16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
+  mesmo a configuracao de maquina que vc. usou.} \textcolor{red}{[S.J:Atualizado.]}
+To run our experiments, we used a Intel Xeon ES-2650 v4 (2.20 GHz)
+with eight virtual CPUs (four cores with two native threads each) and
+16GB of memory, running Ubuntu 18.10 Cosmic Cuttlefish (64-bit version).  We
 used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test

### 2019-06-02 tse19/main.tex
pass up to description of RQs

@@
 \IEEEraisesectionheading{
-\section{Introduction}
-\label{sec:introduction}}
+\section{Introduction}\label{sec:introduction}}
 
@@
 
-\Mar{Sotero, por favor, verifique que os numeros que estao aparecendo
-  no texto (usados nas macros) estao corretos! Vc. nao precisa
-  atualizar o ingles, mas se os dados nao estiverem corretos e vc. nao
-  explicar as mudanca (em portugues mesmo) nao vamos ter condicoes de
-  revisar.}
-\textcolor{red}{[S.J: Ok.]}
-We used \github{}'s search API~\cite{githubsearch} to identify
-projects that satisfy the following criteria:\Mar{alguma restricao
-  sobre o numero minimo de testes por projeto?$\rightarrow$}  \textcolor{red}{[S.J: Nao, mantemos as mesmas restricoes por ordem descendentes das stars]} (1) the primary language
-is Java\footnote{In case of projects in multiple languages, the
-  \github{} API considers the predominant language as the primary
-  language.}, (2) the project has at least 100 stars, (3) the latest
-update was on or after January 1st, 2016, and (4) the \emph{readme}
-file contains the string \emph{mvn}\Mar{ver comentario abaixo}.  We focused on Java for its
-popularity.  Although there is no clearcut limit on the number of
-\github{} stars~\cite{github-stars} to define relevant projects, we
-observed that one hundred stars was enough to eliminate trivial subjects. The
-third
-criteria serves to skip projects without recent activity. The fourth
-criteria is an approximation to find Maven projects.\Comment{ The
-  rationale is that if the string \emph{mvn} exists in the
-  \emph{readme} file, it may represent a Maven call (\eg, to compile
-or to test the project).} We focused on Maven for its popularity on
-Java projects.  Important to highlight that, as of now, the
-\github{}'s search API can only reflect contents from repository
-statistics (\eg, number of forks, main programming language); it does
-not provide a feature to search for projects containing certain files
-(\eg{}, \emph{pom.xml}) in the directory structure. 
-\Mar{Sotero, vc. usou ou nao usou este recurso da API do GitHub? Estou muito cofuso
-  aqui (por isto tive que interromper revisao). Se vc usou, este
-  quarto criterio precisa sair e entrar outro dizendo
-  explicitamente que usamos isto. Fora isto, logo abaixo vc. diz que
-  de um total de 4111, 3154 *nao* eram Maven. Mas, como eh possivel,
-  se vc. garante (atraves deste recurso) a presenca de um arquivo pom.xml?}
-
-\textcolor{red}{[S.J: Tivemos dois momentos, o primeiro momento, usamos os mesmos criterios e script do paper ase17 para minerar os subjects.
-No segundo momento, usamos uma library python chamado PyGithub, ``https://github.com/PyGithub/PyGithub``, para gerenciar recursos do Github API.
-Utilizamos a funcao search\_code, que busca por especifico arquivo em repositorios ``pygithub.search\_code(pom in:pom.xml filename:pom.xml,order=desc)``, curl Github API ``https://api.github.com/search/code?q=pom in:pom.xml+filename:pom.xml``, e em seguida filtramos esses subjects com os crietrios (2) e (3) do paper.
-]}
-
-Figure~\ref{fig:subject-query} illustrates the query to the \github{}
-API as an HTTP request.   The result set is sorted
-in descending order of stars.
-
-\begin{figure}[t!]
+\begin{figure}[t]
+%  \vspace{-5mm}
   \centering
-\tiny
-\lstset{
-    escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
-    showstringspaces=false
-}
-\begin{lstlisting}
-https://api.github.com/search/repositories?q=language:java
- +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
-\end{lstlisting}
-  \vspace{-3mm}
-  \caption{\label{fig:subject-query} Query to the \github{} API for
-  projects that (1) use Java, (2) contains at least 100
-  stars, (3) has been updated on January 1st, 2016 (or later), (4) \Fix{contains
-  the string \emph{mvn} in the \emph{readme} file.}\Mar{Please revise.}}
-  \vspace{-3mm}
+  \includegraphics[width=0.37\textwidth]{results/piechart-subjs.pdf}
+  \caption{\label{fig:subjects}Breakdown of project by sources of
+    issues.}
 \end{figure}
 
-We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
-filtered those
-containing a \pomf{} file in the root directory.\Comment{  A Maven project may
-contain several sub-modules with multiple \pomf{} files.}
-Then, considering this set of Maven projects, we
-executed the tests for \SubjectsReruns{} times to discard those projects with
-issues
-in the build file and non-deterministic results observed from sequential
-executions.
-As of March 5th 2019, our search criteria returned a total of
-\SubjectsGithub{}
-subjects.
-From this set of projects,
-\SubjectsGithubNotMaven{} projects were not Maven or did not have a
-\pomf{} in the root directory, 
-\SubjectsGithubNotTestable{} projects were not considered because of
-environment incompatibility
-(\eg, missing\Comment{ required web browser or database management
-system}~DBMS),
-\SubjectsGithubFlaky{} projects were discarded because of
-``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
-or fails under
-the same circumstances leading to non-deterministic results.
-As some of our experiments consist of running tests on different
-threads, we ignored these projects as it would be impractical
-to identify whether a test failed due to a race condition or some
-other source of flakiness.
-From the remaining \SubjectsGithubConsistant{} projects with
-deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
-projects with \SuiteFailingThreshold{} or more failing tests as to
-reduce bias. For the
-remaining projects with failing tests, we used the JUnit's
-\CodeIn{@Ignore} annotation to ignore failing tests.
-Our final set of subjects contains \numSubjs{} projects. 
- \textcolor{red}{[S.J: Foi possivel observar que houve uma consideravel conversao de ferramenta de automacao, do Maven para Gradle,  dos 3154 subject que nao eram Maven, 2302 eram Gralde (73\%).
+\label{sec:setup}
+
+We used the Python library PyGitHub~\Fix{cite}, which uses the
+\github{}'s search API~\cite{githubsearch}, to identify projects that
+satisfy the following criteria: (1) the primary language is
+Java\footnote{In case of projects in multiple languages, the \github{}
+  API considers the predominant language as the primary language.},
+(2) the project has at least 100 stars, and (3) the latest update was
+on or after January 1st, 2016. Although there is no clearcut limit on
+the number of \github{} stars~\cite{github-stars} to define relevant
+projects, we observed that one hundred stars was enough to eliminate
+trivial subjects. The third criteria serves to skip projects without
+recent activity.
+
+To sum up, after obtaining the list of potential projects from GitHub,
+we filtered those containing a \pomf{} file in the root
+directory.\Comment{ A Maven project may contain several sub-modules
+  with multiple \pomf{} files.}  Then, considering this set of Maven
+projects, we executed the test suite for \SubjectsReruns{} times
+discarding those projects with issues. Figure~\ref{fig:subjects}
+shows the breakdown of projects by source of issue. As of
+March 2019, our search returned a total of \SubjectsGithub{}
+subjects.  We found that \SubjectsGithubNotMaven{}
+projects in this set were not Maven. Compared with our previous
+experiment~\cite{Candido:2017:TSP:3155562.3155667}, executed nearly 2
+years ago, we observed  that many more
+projects now use Gradle---73\% of the \SubjectsGithubNotMaven{} non-Maven
+projects use Gradle. Although parallelization can
+be used in Gradle, we decided to keep using using Maven for
+consistency with the previous experiment. From the remaining set of
+projects, \SubjectsGithubNotTestable{} were discarded
+because of environment incompatibility (\eg, missing\Comment{ required
+  web browser or database management system}~DBMS) and
+\SubjectsGithubFlaky{} projects were discarded because of flaky
+tests~\cite{luo-etal-fse2014}. A flaky test is a test that passes or
+fails non-deterministically resulting in wasted effort.  As some of our experiments consist of running tests on
+different threads, we ignored these projects as it would be
+impractical to identify whether a test failed due to a race condition
+or some other source of flakiness. Note that existing techniques exist to
+detect and mitigate flakiness~\Fix{cite cite}, so we considered this
+problem out of scope. From the remaining
+\SubjectsGithubConsistant{} projects with test execution
+manifesting deterministic results, we
+eliminated \SubjectsGithubTooManyFailures{} projects that contain
+\SuiteFailingThreshold{} or more failing tests as to reduce
+bias. For projects with less failing tests, we used the JUnit's
+\CodeIn{@Ignore} annotation to discard the failing tests as we did not
+want a premature termination of test run to influence in timings.  Our final set of
+subjects include  \numSubjs{} projects.
+
+ %% \textcolor{red}{[S.J: Foi possivel observar que houve uma consideravel conversao de ferramenta de automacao, do Maven para Gradle,  dos 3154 subject que nao eram Maven, 2302 eram Gralde (73\%).
 Projeto como o MapDB, que e bastante citado no paper de ase17, atualmente converteu-se a Gradle.
@@
 
- Figure~\ref{fig:subjects} summarizes our sample set.
-
-\begin{figure}[ht]
-  \vspace{-5mm}
-  \centering
-  \includegraphics[width=0.37\textwidth]{results/piechart-subjs.pdf}
-  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
-  hosted on \github{}. From this initial sample, we ignored
-  \SubjectsGithubNotMaven{} projects without Maven support,
-  \SubjectsGithubNotTestable{} with missing dependencies,
-  \SubjectsGithubFlaky{} projects with flaky tests, and
-  \SubjectsGithubTooManyFailures{} projects had at least
-  \SuiteFailingThreshold{} of failing tests. We considered
-  \numSubjs{} projects to conduct our study.\Mar{Sotero, este plot e
-    macros estao atualizados?}} \textcolor{red}{[S.J:Atualizado.]}
-\end{figure}
-
-\label{sec:setup}
-
-\Mar{Por que isto esta em uma secao ``Objects of Analysis''? Eh esta
-  mesmo a configuracao de maquina que vc. usou.} \textcolor{red}{[S.J:Atualizado.]}
-To run our experiments, we used a Intel Xeon ES-2650 v4 (2.20 GHz)
-with eight virtual CPUs (four cores with two native threads each) and
-16GB of memory, running Ubuntu 18.10 Cosmic Cuttlefish (64-bit version).  We
-used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
-suites. To process test results and generate plots we used Python\Comment{ 3.4},
-Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
-replication on our website~\cite{ourwebpage}.  This includes supporting
-scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
-data)} and the full list of projects.
-
 % SECTION 4
@@
 We pose the following research questions, organized by the dimensions
-of analysis we presented in Section~\ref{sec:intro}.
+of analysis we presented in Section~\ref{sec:introduction}.
 
@@
 \end{itemize}
+
+To run our experiments, we used an Intel Xeon ES-2650 v4 (2.20 GHz)
+with eight virtual CPUs (four cores with two native threads each) and
+16GB of memory, running Ubuntu 18.10 Cosmic Cuttlefish (64-bit version).  We
+used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
+suites. To process test results and generate plots we used Python\Comment{ 3.4},
+Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
+replication on our website~\cite{ourwebpage}.  This includes supporting
+scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
+data)} and the full list of projects.
 

### 2019-06-11 tse19/main.tex
update

@@
 also contacted developers from a selection of costly projects that did not use
-parallelization to understand the reasons for not using parallelization.\textcolor{red}{[S.J: nao fizemos isso.]}
+parallelization to understand the reasons for not using parallelization.\textcolor{red}{[S.J: nao teremos essa dimensao.]}
 Dealing with concurrency-related issues (\eg{}, the extra work to organize test
@@
 The test suites in this group ran in 15 or less seconds for
-over 75\% of the cases.\Comment{  Such scenarios constitute the majority of the
+over 84.73\% of the cases.\Comment{  Such scenarios constitute the majority of the
 cases we analyzed.} Considering the groups \medg{} and \longg{},
-however, we found many costly executions.  Nearly 75\% of the projects
-from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
+however, we found many costly executions.  Nearly 21.84\% of the projects
+from the \medg{} group take 3.5 or more minutes to run and nearly 81.40\% of
 the projects from the \longg{} group take $\sim$20 minutes to run.  We
@@
 \midrule%
-Medium & Californium & 2/20 & C2\\%
+Medium & \Comment{alibaba} Nacos & 1/10 & C1\\%
+Long & \Comment{apache} Avro & 7/18 & C3\\%
+Medium & \Comment{apache} Flink & 108/123 & FC0\\%
+Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
+Medium & \Comment{atmosphere} Nettosphere & 2/2 & FC0\\%
 Medium & Chaos & 1/1 & C2\\%
-Long & \Comment{apache} Flink & 66/74 & FC0\\%
-Long & \Comment{apache logging-}Log4J2 & 25/28 & FC0\\%
-Long & \Comment{javaslang }Javaslang & 3/3 & C3\\%
+Medium & Cache2k & 10/10 & C2\\%
+Medium & \Comment{dropwizard} Metrics & 1/23 & C2\\%
+Medium & \Comment{eclipse} Leshan & 11/11 & C2\\%
+Medium & \Comment{facebook} Jcommon & 16/16 & FC0\\%
+Long & Search Guard & 1/1 & FC0\\%
+Long & \Comment{Hazelcast} Jet & 8/8 & FC0\\%
+Long & Javaparser & 1/9 & C1\\%
 Medium & Jcabi \Comment{jcabi-github} & 1/1 & C3\\%
-Long & \Comment{hazelcast hazelcast-}Jet & 6/7 & FC0\\%
-Long & \Comment{apache} Mahout & 8/9 & FC0\\%
-Long & \Comment{jankotek} MapDB & 1/1 & C3\\%
-Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
-Medium & \Comment{yegor256} Rultor & 1/1 & C3\\%
-Medium & \Comment{yegor256} Takes & 1/1 & C3\\%
-Long & \Comment{vavr-io} Vavr & 3/3 & C3\\%
+Long & Optaplanner & 1/13 & FC0\\%
+Medium & \Comment{spring-data-cassandra}  Cassandra & 1/1 & C1\\%
+Medium & Togglz & 1/34 & C1\\%
+Long & Twilio Java & 1/1 & FC0\\%
+Long & Vavr & 4/4 & C3\\%
+Medium & Rultor & 1/1 & C3\\%
+Medium & \Comment{problem-spring-web}  Spring Web & 4/4 & C3\\%
+Medium & Zxing & 4/4 & FC0\\%
 \bottomrule%
@@
 the configuration cited use the sequential configuration \Seq{}.
-For example, three modules (=28-25) from Log4J2 use sequential
+For example, eleven modules (=18-7) from Avro use sequential
 configuration. It came as a surprise the observation that

### 2019-06-18 tse19/main.tex
minor changes

@@
 projects now use Gradle---73\% of the \SubjectsGithubNotMaven{} non-Maven
-projects use Gradle. Although parallelization can
-be used in Gradle, we decided to keep using using Maven for
+projects use Gradle. Although parallelization could
+be used in Gradle, we decided to keep using Maven for
 consistency with the previous experiment. From the remaining set of
@@
 \SuiteFailingThreshold{} or more failing tests as to reduce
-bias. For projects with less failing tests, we used the JUnit's
+bias. For projects with fewer failing tests, we used the JUnit's
 \CodeIn{@Ignore} annotation to discard the failing tests as we did not
-want a premature termination of test run to influence in timings.  Our final set of
+want a premature termination of a test run to influence in time measurements.  Our final set of
 subjects include  \numSubjs{} projects.

### 2019-06-18 tse19/main.tex
adjustment

--- 2019-06-11 tse19/main.tex
@@
 execution in the root \emph{pom.xml}.\Comment{Some projects may omit long-running tests on their default
-execution.} For instance, the project \CodeIn{apache.maven-surefire}
+execution.} For instance, the project \CodeIn{springboot-security-jwt}
 runs all unit tests in a few seconds.  According to our criteria, this
@@
 executed all tests and \numSubjsFail{} reported some test failure.
-From these \numSubjsFail{} subjects, only 11 subjects
+From these \numSubjsFail{} subjects, only 9 subjects
 have more than 5\% of failing tests (7.3\% on average).

### 2019-06-19 tse19/main.tex
updates and comments

--- 2019-06-18 tse19/main.tex
@@
 
-\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
+\noindent\emph{Adoption.}~ \textcolor{red}{[S.J: nao teremos essa dimensao.]}We considered two aspects in measuring technology
 adoption.  First, we measured usage of parallelism in open-source projects.
@@
 also contacted developers from a selection of costly projects that did not use
-parallelization to understand the reasons for not using parallelization.\textcolor{red}{[S.J: nao teremos essa dimensao.]}
+parallelization to understand the reasons for not using parallelization.
 Dealing with concurrency-related issues (\eg{}, the extra work to organize test
@@
 The test suites in this group ran in 15 or less seconds for
-over 84.73\% of the cases.\Comment{  Such scenarios constitute the majority of the
+over 77.53\% of the cases.\Comment{  Such scenarios constitute the majority of the
 cases we analyzed.} Considering the groups \medg{} and \longg{},
-however, we found many costly executions.  Nearly 21.84\% of the projects
-from the \medg{} group take 3.5 or more minutes to run and nearly 81.40\% of
+however, we found many costly executions.  Nearly 26.44\% of the projects
+from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
 the projects from the \longg{} group take $\sim$20 minutes to run.  We
@@
 execution in the root \emph{pom.xml}.\Comment{Some projects may omit long-running tests on their default
-execution.} For instance, the project \CodeIn{springboot-security-jwt}
+execution.}  \textcolor{red}{[S.J: @Marcio existe alguma caracteristica comum, para que eu possa identificar atraves de script no pom.xml raiz, quais projetos tem testes habilitados por custom params?
+@Marcelo @Marcio voces acham interessante colocar esse dado aqui ?
+quantos projetos possuem essa caracteristica?
+]}For instance, the project \CodeIn{springboot-security-jwt}
 runs all unit tests in a few seconds.  According to our criteria, this
@@
 From these \numSubjsFail{} subjects, only 9 subjects
-have more than 5\% of failing tests (7.3\% on average).
+have more than 5\% of failing tests (5.1\% on average).
 \begin{mdframed}
@@
 Figure~\ref{fig:time-distributions} shows the time distribution of
-individual test cases per project.
+individual test cases per project.\textcolor{red}{[S.J nao teremos mais esse plot.]}
 We observed that the average median times (see dashed horizontal red

### 2019-06-24 tse19/main.tex
updates

@@
 execution in the root \emph{pom.xml}.\Comment{Some projects may omit long-running tests on their default
-execution.}  \textcolor{red}{[S.J: @Marcio existe alguma caracteristica comum, para que eu possa identificar atraves de script no pom.xml raiz, quais projetos tem testes habilitados por custom params?
-@Marcelo @Marcio voces acham interessante colocar esse dado aqui ?
-quantos projetos possuem essa caracteristica?
+execution.}  \textcolor{red}{[S.J: existe a possibilidade de criar uma script que identifica no pom.xml raiz, quais projetos tem testes habilitados por custom params?
+@Marcelo @Marcio voces acham interessante colocar esses dados aqui ?
+quantos projetos possuem essa caracteristica.
 ]}For instance, the project \CodeIn{springboot-security-jwt}
@@
     time-consuming test suites are relatively frequent in
-    open-source projects.  We found that \percentMedLongRunning{} of
+    open-source projects.  We found that \percentMedRunning{} of
     the \numSubjs{} projects we analyzed (\ie{}, nearly 1 in every 4
@@
 Figure~\ref{fig:time-distributions} shows the time distribution of
-individual test cases per project.\textcolor{red}{[S.J nao teremos mais esse plot.]}
+individual test cases per project.
 We observed that the average median times (see dashed horizontal red
@@
 variables was weak.
-Figure~\ref{fig:scattercost} illustrates the regression lines between
+Figure~\ref{fig:scattercost} \textcolor{red}{[S.J nao teremos mais esse plot. falta confirmar com @marcelo ]} illustrates the regression lines between
 these the variables test suite cost and number of test cases.

### 2019-06-28 tse19/main.tex
updates

@@
 \midrule%
-Medium & Californium & 1.45m & 1.40m & \cellcolor{lightgray}1.04x\\%
-Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
-Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
-Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
-Medium &Javaslang& 2.18m & 1.82m & 1.20x\\%
-Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & 9.20x\\%
-Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
-Long & \Comment{apache} Mahout & 27.38m & 18.15m & 1.51x\\%
-Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
-Medium & \Comment{apache} OpenNLP & 1.30m & 0.55m & 2.36x\\%
-Medium & \Comment{yegor256} Rultor & 2.30m & 0.27m & 8.52x\\%
-Medium & \Comment{yegor256} Takes & 2.00m & 0.19m & \cellcolor{lightgray}10.53x\\%
-Long & \Comment{vavr-io} Vavr & 3.26m & 2.25m & 1.45x\\%
+Medium & \Comment{ Apache } Avro & 13.65m & 11.39m & \cellcolor{lightgray}1.20x\\%
+Long & \Comment{ Apache } Oozie & 4.59m & 4.03m & \cellcolor{lightgray} 1.14x\\%
+Medium & \Comment{ BounceStorage } Chaos & 1.54m & 1.44m & \cellcolor{lightgray} 1.07x\\%
+Medium & \Comment{ Apache } OpenNLP & 3.59m & 2.36m & \cellcolor{lightgray} 1.52x\\%
+%Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%%
+Medium & Cache2k & 1.56m & 1.47m & 1.06x\\%
+Medium & Eclipse Leshan & 1.32m & 0.58m & 2.27x\\%
+Long & Search Guard & 13.54m & 6.53m & 2.07x\\%
+Long & Javaparser & 5.98m & 4.45m & 1.34x\\%
+Long & Opta Planner & 12.55m & 10.07m & 1.25x\\%
+Medium & Togglz & 4.01m & 3.65m & 1.10x\\%
+Long & Twilio Java & 13.04m & 2.26m & 5.77x\\%
+Medium & Vavr & 5.21m & 4.37m & \cellcolor{lightgray}1.26x\\%
+Medium & Zxing & 1.33m & 2.61m & 1.26x\\%
 \midrule

### 2019-06-28 tse19/paralleltest-pag-maven-plugin/src/main/java/paralleltest-pag-maven-plugin/MyMojo.java

@@ -30,6 +30,9 @@ import java.io.IOException;
  * 
  * @phase process-sources
  */
+
+@Mojo(name = "testing")
+
 public class MyMojo
     extends AbstractMojo
 {

### 2019-07-10 tse19/main.tex
updates table

@@
 execution in the root \emph{pom.xml}.\Comment{Some projects may omit long-running tests on their default
-execution.}  \textcolor{red}{[S.J: existe a possibilidade de criar uma script que identifica no pom.xml raiz, quais projetos tem testes habilitados por custom params?
-@Marcelo @Marcio voces acham interessante colocar esses dados aqui ?
-quantos projetos possuem essa caracteristica.
-]}For instance, the project \CodeIn{springboot-security-jwt}
+execution.}  For instance, the project \CodeIn{springboot-security-jwt}
 runs all unit tests in a few seconds.  According to our criteria, this

### 2019-07-10 tse19/main.tex
updates tables

@@
 \midrule%
-Medium & \Comment{alibaba} Nacos & 1/10 & C1\\%
 Long & \Comment{apache} Avro & 7/18 & C3\\%
+Medium & Cache2k & 10/10 & C2\\%
+Medium & \Comment{spring-data-cassandra}  Cassandra & 1/1 & C1\\%
+Medium & Chaos & 1/1 & C2\\%
 Medium & \Comment{apache} Flink & 108/123 & FC0\\%
-Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
-Medium & \Comment{atmosphere} Nettosphere & 2/2 & FC0\\%
-Medium & Chaos & 1/1 & C2\\%
-Medium & Cache2k & 10/10 & C2\\%
-Medium & \Comment{dropwizard} Metrics & 1/23 & C2\\%
-Medium & \Comment{eclipse} Leshan & 11/11 & C2\\%
-Medium & \Comment{facebook} Jcommon & 16/16 & FC0\\%
-Long & Search Guard & 1/1 & FC0\\%
-Long & \Comment{Hazelcast} Jet & 8/8 & FC0\\%
 Long & Javaparser & 1/9 & C1\\%
 Medium & Jcabi \Comment{jcabi-github} & 1/1 & C3\\%
+Medium & \Comment{facebook} Jcommon & 16/16 & FC0\\%
+Long & \Comment{Hazelcast} Jet & 8/8 & FC0\\%
+Medium & \Comment{eclipse} Leshan & 11/11 & C2\\%
+Medium & \Comment{dropwizard} Metrics & 1/23 & C2\\%
+Medium & \Comment{alibaba} Nacos & 1/10 & C1\\%
+Medium & \Comment{atmosphere} Nettosphere & 2/2 & FC0\\%
+Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
 Long & Optaplanner & 1/13 & FC0\\%
-Medium & \Comment{spring-data-cassandra}  Cassandra & 1/1 & C1\\%
+Medium & Rultor & 1/1 & C3\\%
+Long & Search Guard & 1/1 & FC0\\%
+Medium & \Comment{problem-spring-web}  Spring Web & 4/4 & C3\\%
 Medium & Togglz & 1/34 & C1\\%
@@
 Long & Vavr & 4/4 & C3\\%
-Medium & Rultor & 1/1 & C3\\%
-Medium & \Comment{problem-spring-web}  Spring Web & 4/4 & C3\\%
 Medium & Zxing & 4/4 & FC0\\%

### 2019-07-11 tse19/main.tex
minor adjusts

@@
 approach to address this problem. \Mar{Sotero, vc. atualizou estas
-  macros?} \textcolor{red}{[S.J: atualizado.]} Considering a set of \numSubjs{} Java projects we analyzed
+  macros?} \textcolor{red}{[Sotero: atualizado.]} Considering a set of \numSubjs{} Java projects we analyzed
 from \github\, we found that \percentMedLongRunning{} of the them
@@
 
-\noindent\emph{Adoption.}~ \textcolor{red}{[S.J: nao teremos essa dimensao.]}We considered two aspects in measuring technology
+\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
 adoption.  First, we measured usage of parallelism in open-source projects.
@@
 Considering only the projects whose test suites take longer than a minute to
-run, we found that only \percentParallelUpdated{} of them use parallelism.  We
+run, we found that only \percentParallelUpdated{} of them use parallelism.  \textcolor{red}{[Sotero: nao fizemos isso.]}We
 also contacted developers from a selection of costly projects that did not use
@@
 variables was weak.
-Figure~\ref{fig:scattercost} \textcolor{red}{[S.J nao teremos mais esse plot. falta confirmar com @marcelo ]} illustrates the regression lines between
+Figure~\ref{fig:scattercost} \textcolor{red}{[Sotero:  nao teremos mais esse plot. falta confirmar com @marcelo ]} illustrates the regression lines between
 these the variables test suite cost and number of test cases.
@@
 Compared to the set of projects listed in
-Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
-\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
-configuration \ParClassParMeth), \CodeIn{Mapstruct} (using configuration
-\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
-\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
-Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
-and \CodeIn{Takes} were not detected using this methodology.
+Table~\ref{tab:freqmodes-dynamic}, we found 8 new projects, namely:
+\CodeIn{\Comment{ Apache} Hadoop} (using
+configuration \ForkSeq), \CodeIn{\Comment{ Apache} Hadoop-common} (using configuration
+\ForkSeq{}), \CodeIn{\Comment{ Apache} Tajo} (using configuration \ForkSeq), \CodeIn{\Comment{ Apache} Hawkbit} (using configuration \ForkSeq), \CodeIn{\Comment{ kiegroup} Optaplanner} (using configuration \ForkSeq), \CodeIn{\Comment{ lejon} T-SNE-Java} (using configuration \ForkSeq), \CodeIn{Kubernetes Java Client} (using configuration \SeqClassParMeth)   and
+\CodeIn{Netflix Curator} (using configuration \ForkSeq).
+Curiously, we also found that project \CodeIn{Alibaba Nacos}, \CodeIn{Rultor},
+and \CodeIn{Jcabi} were not detected using this methodology.
 That happened because these projects loaded a \emph{pom.xml} file from
@@
 
-To answer this research question we surveyed developers involved in a
+\textcolor{red}{[Sotero: nao teremos mais essa RQ4. confirmar com @marcelo ]} To answer this research question we surveyed developers involved in a
 selection of projects from our benchmark with time-consuming test

### 2019-07-15 tse19/main.tex
updates RQ7

@@
 
-To answer this research question, we selected 15 different subjects,
+To answer this research question, we selected 21 different subjects,
 ran their test suites against all configurations described in
@@
 \emph{\Seq{}}, as the comparison baseline in this experiment.  To
-select subjects, we sorted projects whose test suites run in 1m or
+select subjects, we sorted projects whose test suites run in 5m or
 more by decreasing order of execution time and selected the first
-fifteen projects that use JUnit 4.7 or later.  The rationale for this
+twenty one projects that use JUnit 4.7 or later.  The rationale for this
 criteria is to ensure compatibility with parallel configuration since
 older versions of JUnit does not support parallel testing.  We ran
-each project on each configuration for \SubjectsReruns{} times.
-Overall, we needed to reran test suites 270 times, 18 times (3x6
+each project on each configuration for twelve times.
+Overall, we needed to reran test suites 1,512 times, 72 times (12x6
 configurations) on each project.  Given the low standard deviations
 observed in our measurements\Comment{ and the aggregated time cost of 270 test
-executions}, we considered \SubjectsReruns{} reruns reasonable for this
+executions}, we considered twelve reruns reasonable for this
 experiment.
@@
 we invoke the test runners mentioned above on them.  We configured
-this experiment to run at most three JVMs in parallel.  Recall that in
+this experiment to run at most twelve JVMs in parallel.  Recall that in
 our setup (see Section~\ref{sec:setup}), we limited our kernel to use
@@
 of the cases, flakiness was caused by race conditions: approximately
-97.5\% of the failures were caused by a \CodeInF{null} dereference and 1.6\% were
-caused by concurrent access on unsynchronized data structures.\Comment{
-  More precisely, the manifested exceptions were
-  \CodeInF{ConcurrentModificationException} (0.8\%),
-  \CodeInF{NoSuchElementException} (0.7\%), and
-  \CodeInF{ArrayIndexOutOfBoundsException} (0.7\%).}  Cases of likely
+95.8\% of the failures were caused by a \CodeInF{null} dereference and 2.7\% were
+caused by concurrent access on unsynchronized data structures. Cases of likely
 broken test dependencies were not as prevalent as race conditions
-(0.8\% of the total): \CodeInF{EOFException} (0.2\%),
-\CodeInF{FileSystemAlreadyExistsException} (0.2\%), and
-\CodeInF{BufferOverflowException} (0.4\%). Results suggest that
+(1.5\% of the total): \CodeInF{EOFException} (0.2\%),
+\CodeInF{FileSystemAlreadyExistsException} (0.5\%), and
+\CodeInF{BufferOverflowException} (0.8\%). Results suggest that
 anticipating race conditions to schedule test executions would have
@@
 The projects with flakiness
-in all configurations were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and
-\CodeIn{Moquette}.  It is worth highlighting the unfortunate case of
-\CodeIn{Moquette}, which manifested more than 20\% flaky tests in
+in all configurations were \CodeIn{Activity}, \CodeIn{Incubator Dubbo}, \CodeIn{DROID}, and
+\CodeIn{Hawkbit}.  It is worth highlighting the unfortunate case of
+\CodeIn{Hawkbit}, which manifested more than 9\% flaky tests in
 every configuration.  Considering time, it is noticeable from the
@@
 spawning and managing JVMs and threads.  Overall, results show that
-0\% of flakiness have been reported in 30 of the 75 (=5x15)
-pairs of project and configuration we analyzed (40\% of the total).
-In for 4 of the 15 projects flakiness was not manifested in 
+0\% of flakiness have been reported in 47 of the 105 (=5x15)
+pairs of project and configuration we analyzed (44.76\% of the total).
+In for 6 of the 21 projects flakiness was not manifested in 
 any combination pairs.  We noticed with some surprise that the average speedup of
-configuration \emph{\SeqClassParMeth} was higher compared to
-\emph{\ForkParMeth} indicating that it is not always the case that
+configuration \emph{\SeqClassParMeth} was higher compared to \emph{\ParClassSeqMeth}{C2} and \emph{\ParClassParMeth}{C3},
+indicating that it is not always the case that
 using more CPUs pays off. Important to note that the cost of spawning
@@
 \noindent\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
-  test suites of 73.33\% of the projects we analyzed could be run in
+  test suites of 44.76\% of the projects we analyzed could be run in
   parallel without manifesting any flaky tests.  In some of these

### 2019-07-16 tse19/main.tex
updates

@@
 lines) were small, namely 0.08s
-for \medg{} projects and 0.16s for \longg{} projects, and the standard deviations associated with each distribution were
+for \medg{} projects and 0.31s for \longg{} projects, and the standard deviations associated with each distribution were
 relatively low.\Comment{ Figure~\ref{fig:sd} shows the number of
@@
 of those. The highest value of $\sigma$ occurred in
-\CodeIn{uber\_chaperone}, a project from the \longg{} group.
-This project contains only 26 tests, 17 of which take less than 0.5s
-to run, one of which takes nearly 3s to run, two of which take nearly
-11s to run, four of which takes on average 3m to run, and two of which
+\CodeIn{T-SNE-Java}, a project from the \longg{} group.
+This project contains only 20 tests, 16 of which take less than 0.6s
+to run, one of which takes nearly 4s to run, two of which take nearly
+14s to run, four of which takes on average 3m to run, and two of which
 take $\sim$8m to run.
@@
 
-Figure~\ref{fig:size-testsuites} shows the difference in the
+Figure~\ref{fig:size-testsuites}  \textcolor{red}{[Sotero:  nao teremos mais esse plot. falta confirmar com @marcelo ]}  shows the difference in the
 distribution of test suite sizes across groups.  This figure indicates
@@
 \numProjectsPar{} of those projects had parallelism enabled
-by default, with only configurations \ParClassSeqMeth{},
+by default, with only configurations \SeqClassParMeth{}, \ParClassSeqMeth{},
 \ParClassParMeth{}, and \ForkSeq{} being used. Configurations
@@
 subjects from our benchmark that use parallelization \emph{by default}
-(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
+(see Table~\ref{tab:freqmodes-dynamic}). From this set, we discarded 6 subjects because of failures in sequential execution and selected only 16 subjects remaining. We compared running times
 of test suites with enabled parallelization, as configured by project
@@
 \avgSpeedup{} times faster compared to sequential execution.
-Three cases worth special attention: \CodeIn{Log4J2}, \CodeIn{Chaos},
-and \CodeIn{Takes}.
-We note that parallel execution in \CodeIn{Log4J2} was
+Three cases worth special attention: \CodeIn{Togglz}, \CodeIn{Chaos} and \CodeIn{Cache2k}.
+We note that parallel execution in \CodeIn{Togglz} was
 ineffective.  We found that Maven invokes several test modules in this
 project but the test modules that dominate execution time run
-sequentially by default. This was also the case for the highlighted
-project \CodeIn{Californium}.
+sequentially by default. This was also observed in the projects \CodeIn{Zxing}, \CodeIn{Optaplanner}, \CodeIn{OpenNLP} and \CodeIn{Leshan}.
 No significant speedup was observed in \CodeIn{Chaos}, a project with
-only three test classes, of which one monopolizes the bulk of test
+only two test classes, of which one monopolizes the bulk of test
 execution time.
@@
 configuration.
-Finally, the speedup observed in project \CodeIn{Takes} was
+Finally, the speedup observed in projects \CodeIn{Cache2k}  was
 the highest amongst all projects. This subject uses configuration
-\ParClassParMeth{} and contains 419 test methods distributed nearly
-equally among 148 test classes with a small number of test methods.
+\ParClassSeqMeth{} and contains 5120 test methods distributed nearly
+equally among 101 test classes with a small number of test methods.
 Furthermore, several methods in those classes are time-consuming.
@@
 \midrule%
-Medium & \Comment{ Apache } Avro & 13.65m & 11.39m & \cellcolor{lightgray}1.20x\\%
-Long & \Comment{ Apache } Oozie & 4.59m & 4.03m & \cellcolor{lightgray} 1.14x\\%
-Medium & \Comment{ BounceStorage } Chaos & 1.54m & 1.44m & \cellcolor{lightgray} 1.07x\\%
-Medium & \Comment{ Apache } OpenNLP & 3.59m & 2.36m & \cellcolor{lightgray} 1.52x\\%
-%Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%%
-Medium & Cache2k & 1.56m & 1.47m & 1.06x\\%
-Medium & Eclipse Leshan & 1.32m & 0.58m & 2.27x\\%
-Long & Search Guard & 13.54m & 6.53m & 2.07x\\%
-Long & Javaparser & 5.98m & 4.45m & 1.34x\\%
-Long & Opta Planner & 12.55m & 10.07m & 1.25x\\%
-Medium & Togglz & 4.01m & 3.65m & 1.10x\\%
-Long & Twilio Java & 13.04m & 2.26m & 5.77x\\%
-Medium & Vavr & 5.21m & 4.37m & \cellcolor{lightgray}1.26x\\%
-Medium & Zxing & 1.33m & 2.61m & 1.26x\\%
+Long & \Comment{ Apache } Avro & 14.91m & 13.50m & 1.10x\\%
+Medium & \Comment{ Cache2k } Cache2k & 4.58m & 2.24m & \cellcolor{lightgray}2.04x\\%
+Medium & \Comment{ spring-data-cassandra } Cassandra & 4.43m & 4.02m & 1.10x\\%
+Medium & \Comment{ Bounces } Chaos & 1.64m & 1.54m & \cellcolor{lightgray}1.06x\\%
+Long & \Comment{ Javaparse } Javaparser & 7.04m & 6.16m & 1.14x\\%
+Medium & \Comment{ Jcabi Github } Jcabi & 2.33m & 1.31m & 1.77x\\%
+Medium & \Comment{ Facebook } Jcommon & 1.59m & 1.44m & 1.10x\\%
+Medium & \Comment{ Eclipse } Leshan & 1.66m & 1.53m & 1.08x\\%
+Medium & \Comment{ Atmosphere } Nettosphere & 2.40m & 2.07m & 1.16x\\%
+Medium & \Comment{ Apache } OpenNLP & 3.52m & 3.24m & 1.08x\\%
+Long & \Comment{ Kiegroup } Optaplanner & 10.79m & 10.06m & 1.07x\\%
+Long & \Comment{ Floraguncom } Search Guard & 13.24m & 6.53m & \cellcolor{lightgray} 2.02x\\%
+Medium & \Comment{ Togglz } Togglz & 4.11m & 4.04m & \cellcolor{lightgray}1.01x\\%
+Long & \Comment{ Twilio } Twilio Java & 12.57m & 11.38m & 1.10x\\%
+Long & \Comment{ Vavr io } Vavr & 5.73m & 5.09m & 1.12x\\%
+Medium & \Comment{ Zxing } Zxing & 4.61m & 4.28m & 1.07x\\%
+
 \midrule
@@
 any combination pairs.  We noticed with some surprise that the average speedup of
-configuration \emph{\SeqClassParMeth} was higher compared to \emph{\ParClassSeqMeth}{C2} and \emph{\ParClassParMeth}{C3},
+configuration \emph{\SeqClassParMeth} was higher compared to \emph{\ParClassSeqMeth} and \emph{\ParClassParMeth},
 indicating that it is not always the case that
@@
 \item \emph{Incentivize forking.}~Forked JVMs manifest low rates of
-  test flakiness.  For instance, in \emph{\ForkSeq{}}, only 4 of 10
+  test flakiness.  For instance, in \emph{\ForkSeq{}}, only 4 of 21
   projects manifest flakiness and, excluding the extreme case of
-  \CodeIn{Moquette}, projects manifest flaky tests in low rates 0.23\%
+  \CodeIn{Hawkbit}, projects manifest flaky tests in low rates 0.23\%
   to 1.70\%.  Developers of projects with long-running test suites

### 2019-08-14 tse19/main.tex
Added new RQ

@@
 
-\newcommand{\numRQAdoptionTwo}{RQ4}
-\newcommand{\RQAdoptionTwo}{What are the main reasons that prevent developers
-  from using test suite parallelization?}
-
 %% Speedups
-\newcommand{\numRQSpeedupOne}{RQ5}
+\newcommand{\numRQSpeedupOne}{RQ4}
 \newcommand{\RQSpeedupOne}{What are the speedups obtained with parallelization
@@
 
-\newcommand{\numRQSpeedupTwo}{RQ6}
+\newcommand{\numRQSpeedupTwo}{RQ5}
 \newcommand{\RQSpeedupTwo}{How test execution scales with the number of
@@
 %% Tradeoffs
-\newcommand{\numRQIssuesOne}{RQ7}
+\newcommand{\numRQIssuesOne}{RQ6}
 \newcommand{\RQIssuesOne}{How parallel execution configurations affect testing
@@
 
+\newcommand{\numRQIssuesTwo}{RQ7}
+\newcommand{\RQIssuesTwo}{How effective is selective re-execution in mitigating flakiness??}
+
 \setlist[itemize]{leftmargin=1em}
@@
   \item \textbf{\numRQAdoptionOne.} \RQAdoptionOne    
-  \item \textbf{\numRQAdoptionTwo.} \RQAdoptionTwo
   \end{itemize}
@@
   \item \textbf{\numRQIssuesOne.} \RQIssuesOne 
+  \item \textbf{\numRQIssuesTwo.} \RQIssuesTwo    
   \end{itemize}
@@
 
-\begin{itemize}
-  \item \numRQAdoptionTwo{}. \textbf{\RQAdoptionTwo{}}
-\end{itemize}
-
-\textcolor{red}{[Sotero: nao teremos mais essa RQ4. confirmar com @marcelo ]} To answer this research question we surveyed developers involved in a
-selection of projects from our benchmark with time-consuming test
-suites.  The goal of the survey is to better comprehend developer's
-attitude towards the use of parallelism as a mechanism to speedup
-regression testing.  We surveyed developers from a total of
-\emailsProjects{} projects.  From the initial list of \numMedLong{}
-project, we discarded 11 projects that we knew a priori used
-parallelization, and \discartedProjects{} projects that we could not find
-developer's emails from commit logs.  From this list of projects, we
-mined potential participants for our study.  More precisely, we
-searched for developer's name and email from the last 20 commits to
-the corresponding project repository.  Using this approach, we
-identified a total of \emailsSent{} eligible participants.  Finally,
-we sent plain-text e-mails, containing the survey, to those developers.  In
-total, \emailsAnswered{} developers replied but we discarded
-\emailsFalseAnswers{} replies with subjective answers.  Considering
-projects covered by the answers, a total of \emailsProjectsAnswered{}
-projects (\percEmailsProjectsAnswered{} of the total) were represented
-in those replies. Note that multiple developers on each project
-received emails. In one specific case, one developer worked in
-  multiple projects, and we consider it as a different answer. We sent the following set of questions to
-developers:
-
-\begin{enumerate}
-\item How long does it take for tests to run in your environment? Can
-  you briefly define your setup?
-\item Do you confirm that your regression test suite does *not* run in parallel?
-\item\label{questionThree} Select a reason for not using parallelization:
-  \begin{enumerate}[label=\alph*)]
-  \item I did not know it was possible
-  \item I was concerned with concurrency issues
-  \item I use a continuous integration server
-  \item Some other reason. Please elaborate.
-  \end{enumerate}
-\end{enumerate}
-
-Considering question 1, we confirmed that execution time was
-compatible with the results we reported in Section~\ref{sec:rqA}.
-Furthermore, \emailsCI{} of the participants indicated the use of
-Continuous Integration (CI) to run tests, with \emailsDistributed{} of
-these participants reporting that test suites are modularized and
-those modules are tested independently in CI servers through different
-parameters.  Those participants explained that such practice helps to
-reduce time to observe test failures, which is the goal of speeding up
-regression testing.  A total of \emailsLocal{} participants answered
-that they do run tests in their local machines.  Note, however, that
-CI does not preclude low-level parallelization.  For example,
-installations of open-source CI tools (\eg{}, Jenkins~\cite{jenkins})
-in dedicated servers would benefit from running tests faster through
-low-level test suite parallelization.
-
-Considering question 2, the answers we collected indicated, to our
-surprise, that six of the \emailsProjectsAnswered{} projects execute
-tests in parallel.  This mismatch is justified by cases where neither
-of our checks (static or dynamic) could detect presence of
-parallelism.  A closer look at these projects revealed that one of
-them contained a \emph{pom.xml} file encapsulated in a jar file
-(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
-projects the participant considered that distributed CI was a form of
-parallelism, and in four projects the team preferred to implement
-parallelization instead of using existing features from the testing
-framework and the build system~---~in two projects the team
-implemented concurrency control with custom JUnit test runners and in
-two other projects the team implemented concurrency within test
-methods.  Note that, considering these four extra cases (ignored two
-distributed CI cases), the usage of parallelization increases from
-\percentParallel{} to \percentParallelUpdated{}.  We do not consider
-this change significant enough to modify our conclusion about
-practical adoption of parallelization (\numRQAdoptionOne{}).
-
-Considering question 3, the distribution of answers was as follows.  A
-total of \emailsA{} of the \emailsProjectsAnswered{} developers who
-answered the survey did not know that parallelism was available in
-\begin{wrapfigure}{r}{0.13\textwidth}
-%\begin{figure}[b]
-  \centering
-  \includegraphics[width=2cm]{results/survey.pdf}
-  \caption{\label{fig:rq5-answers}Summary of developer's answers to
-    survey question~\ref{questionThree}.}
-\end{wrapfigure}
-Maven (option ``a''), \emailsB{} of developers mentioned that they did
-not use parallelism concerned with possible concurrency issues (option
-``b''), \emailsD{} of developers mentioned that continuous integration
-suffices to provide timely feedback while running only smoke
-tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
-  I want to say that they use it for something like "non-blocking
-  testing" while developing in a local machine}, and \emailsD{} of
-developers who provided an alternative answer (option ``d'') mentioned
-that using parallelism was not worth the effort of preparing the test
-suites to take advantage of available processing power.  A total of
-\emailsNA{} of participants did not answer the last question of the
-survey.  The pie chart in Figure~\ref{fig:rq5-answers} 
-summarizes the distribution of answers.
-
-\begin{mdframed}
-\noindent\textit{Answering \numRQAdoptionTwo{}:}~\emph{Results suggest that dealing
-  with concurrency issues (\ie{}, the extra work to organize test
-  suite to safely explore concurrency) was the principal reason
-  for developers not investing in parallelism.  Other reasons
-  included availability of continuous integration services and
-  unfamiliarity with the technology.}
-\end{mdframed}
-
 \subsection{Speedups}
@@
 ran their test suites against all configurations described in
-Section~\ref{sec:modes}, and compared their running times and rate of
+Section II, and compared their running times and rate of
 test flakiness.  We used the sequential execution configuration,
@@
   cases, speedups were significant, ranging from 1x to 28.8x.}
+\end{mdframed}
+
+\begin{itemize}
+  \item \numRQIssuesTwo{}. \textbf{\RQIssuesTwo{}}
+\end{itemize}
+
+\input{mitigating-flakiness-speedup-table}
+
+To answer the RQ7, we selects to this experiment 15 subjects of the Table III from RQ6, that manifested flakiness in any combination pairs.
+
+\begin{mdframed}
+\noindent\textit{Answering \numRQIssuesTwo{}:~Overall results indicate ...}
 \end{mdframed}

### 2019-08-14 tse19/mitigating-flakiness-speedup-table.tex
Added new RQ

%% Table header macros
% $\Uparrow_\text{speed}$

\begin{table*}[t]
\centering
\setlength{\tabcolsep}{4.5pt}
\caption{Speedup versus Flakiness (\subcolB). Configuration
  \emph{\Seq{}} denotes the comparison baseline.  Columns $T$
and $N$ indicate time and number of tests, respectively.  Other columns show
speedup and percentage of failing tests in different configurations, compared to
\emph{\Seq{}}.}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T$ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%

Activiti & \entry{8.46m}{2093}  & \textcolor{blue}{ 2.49x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.81x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.72x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.02x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 2.87x } & \textcolor{blue}{ 0\%}\\%

Apache Avro & \entry{13.65m}{3765}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%

Apache Incubator Dubbo & \entry{14.33m}{2663}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%

Content ExtRactor and MINEr & \entry{8.10m}{132}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%

DataStax Java Driver & \entry{5.23m}{1377}  & \entry{8.30x}{1.17\%} & \entry{9.34x}{0.75\%} & \entry{9.33x}{1.15\%} & \entry{1.03x}{0\%} & \entry{6.22x}{1.41\%}\\%

DROID & \entry{6.00m}{386}  & \entry{2.32x}{15.79\%} & \entry{7.90x}{2.02\%} & \entry{4.02x}{5.33\%} & \entry{9.67x}{2.3\%} & \entry{4.76x}{6\%}\\%

Eclipse Hawkbit & \entry{17.28m}{1111}  & \entry{2.63x}{29.12\%} & \entry{2.90x}{33.22\%} & \entry{2.52x}{26.52\%} & \entry{2.49x}{9.23\%} & \entry{3.00x}{33.91\%}\\%

Facebook Linkbench & 7.16m & 98 & 1.02x & 0\% & 1.70x & 1.27\% & 1.00x & 1.00\% & 1.70x & 0.09\% & 1.69x & 0.93\%\\%

Kafka Streams & \entry{11.38m}{79}  & \entry{1.13x}{11\%} & \entry{1.02x}{0\%} & \entry{1.12x}{11.49\%} & \entry{2.63x}{1.37\%} & \entry{1.02x}{0.2\%}\\%

Rapidoid & \entry{11.68m}{476}  & \entry{1.06x}{0\%} & \entry{1.24x}{0\%} & \entry{1.10x}{0\%} & \entry{18.54x}{10.15\%} & \entry{17.17x}{9.57\%}\\%

Search Guard & \entry{13.32m}{111}  & \entry{1.78x}{0\%} & \textcolor{blue}{ 1.62x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.43x } & \textcolor{blue}{ 0\%} & \entry{2.04x}{0\%} & \entry{2.45x}{0\%}\\%

T SNE Java & \entry{6.38m}{20}  & \textcolor{blue}{ 2.02x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 1.22x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 1.21x } & \textcolor{blue}{ 0\%}\\%

Twilio Java & \entry{12.60m}{2529}  & \entry{1.47x}{1.37\%} & \entry{2.15x}{21\%} & \entry{3.08x}{2.18\%} & \entry{3.47x}{0\%} & \entry{2.60x}{5.54\%}\\%

Urban Airship Datacube & 11.84m & 45 & 2.31x & 20.91\% & 3.35x & 34.06\% & 1.92x & 21.46\% & 1.21x & 0\% & 2.26x & 21\%\\%

Vaadin Framework & \entry{8.97}{3683}  & \textcolor{blue}{ 2.19x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.91x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 2.01x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 2.53x } & \textcolor{blue}{ 0\%}\\%

\midrule
Average & 10.42m & 1,237.86 & -x & -\% &  -x & -\%  & -x  & -\% & -x & -\% & -x & -\%\\%

\bottomrule%
\end{tabular}
\label{tab:rq6-table}
\end{table*}

### 2019-09-04 tse19/main.tex
added script

@@
 spawning and managing JVMs and threads.  Overall, results show that
-0\% of flakiness have been reported in 47 of the 105 (=5x15)
+0\% of flakiness have been reported in 47 of the 105 (=5x21)
 pairs of project and configuration we analyzed (44.76\% of the total).

### 2019-09-04 scripts/result_rq8/analyze_flakiness.py

@@ -1,0 +1,62 @@
+#!/usr/bin/env python3
+import csv
+import os
+import re
+import shutil
+import xml.etree.ElementTree as etree
+import subprocess
+
+from subprocess import Popen, PIPE, call
+
+
+def serialize_data_for(projects):
+    entries = []
+    listOfCheck = []
+    for project_info in projects:
+        if project_info["path_classname_error"]:
+            split_result = project_info["path_classname_error"].split(",")
+            for r in split_result:
+                name_class = r.split(".")[-1]
+                string_results = "./find_pom.rb --path ./projects/%s --file %s" % (project_info["name"],name_class)
+                out = subprocess.Popen([string_results], stdout=subprocess.PIPE, stderr=subprocess.STDOUT, shell=True)
+                stdout,stderr = out.communicate()
+                result_pom = stdout.split()[0].decode('ascii')
+                
+                if listOfCheck:
+                    if not result_pom in listOfCheck:
+                        entries.append({"project": project_info["name"], "class": name_class,"pom": result_pom})
+                else:
+                    listOfCheck.append(result_pom)
+                    entries.append({"project": project_info["name"], "class": name_class,"pom": result_pom})
+           
+    #print(entries)
+    #print(list(set(entries)))
+    fname = "dataset-flakiness.csv"
+    with open(fname, "w", newline="") as out:
+        writer = csv.DictWriter(out, fieldnames=["project", "class","pom"])
+        writer.writeheader()
+        writer.writerows(entries)
+
+def analyze_data_result(projects):
+    check_class_error = 0
+    for project_info in projects:
+        if project_info["path_classname_error"]:
+            check_class_error += 1
+            
+    if check_class_error > 0:
+        serialize_data_for(projects)
+    else:
+        print("Project without flakiness!")
+
+
+if __name__ == "__main__":
+    input_csv = "dataset-rawdata-mode.csv"
+    if (not os.path.exists(input_csv)):
+        print("Could not find path \"%s\"\nExiting..." % input_csv)
+
+    with open(input_csv, newline="") as f:
+        reader = csv.DictReader(f)
+        projects = [e for e in reader]
+
+    analyze_data_result(projects)
+

### 2019-09-04 scripts/result_rq8/analyze_transformed_subj.py

@@ -1,0 +1,33 @@
+#!/usr/bin/env python3
+import csv
+import os
+import re
+import shutil
+import xml.etree.ElementTree as etree
+import subprocess
+
+from subprocess import Popen, PIPE, call
+
+
+def analyze_data_result(projects):
+    for project_info in projects:
+        pom_str = project_info["pom"]
+        split_str = pom_str.split("/")
+        index_elem = split_str.index("projects")
+        split_str[index_elem] = "project_transformed"
+        result_path = "/".join(split_str)
+        call("./transform_seq.rb --path \"%s\"" % result_path, shell=True)
+        print("Generated modified pom.xml of the subject")
+            
+
+if __name__ == "__main__":
+    input_csv = "dataset-flakiness.csv"
+    if (not os.path.exists(input_csv)):
+        print("Could not find path \"%s\"\nExiting..." % input_csv)
+
+    with open(input_csv, newline="") as f:
+        reader = csv.DictReader(f)
+        projects = [e for e in reader]
+
+    analyze_data_result(projects)
+

### 2019-09-04 scripts/result_rq8/compile-test.sh

@@ -1,0 +1,54 @@
+#!/bin/bash
+#
+# Invokes maven compile and test for projects from a given directory
+#
+# Usage:   ./compile-test.sh <TIMEOUT> <PROJECTS_DIR> <OUTPUT_DIR>
+# Example: ./compile-test.sh 90m ./downloads/projects ./rawdata
+#
+TIMEOUT=$1
+
+INPUT_DIR=$2
+if [[ ! -d "$INPUT_DIR" ]]; then
+    echo "Invalid path project"
+    exit 1
+fi
+
+OUTPUT_DIR="`readlink -e $3`"
+if [[ ! -d "$OUTPUT_DIR" ]]; then
+    echo "Invalid path rawdata"
+    exit 1
+fi
+
+MAVEN_SKIPS="-Drat.skip=true -Dmaven.javadoc.skip=true -Djacoco.skip=true \
+             -Dcheckstyle.skip=true -Dfindbugs.skip=true -Dcobertura.skip=true \
+             -Dpmd.skip=true -Dcpd.skip=true -Denforcer.skip=true"
+
+TS="`date +"%m%d%H%M%S"`"
+
+for PROJECT in `ls "$INPUT_DIR"`; do
+
+    # Watch out for ending slash
+    PROJECT_PATH="$INPUT_DIR/$PROJECT"
+    if [[ ! -d "$PROJECT_PATH" ]]; then
+        echo "Invalid path \"$PROJECT_PATH\". Skipping..."
+        continue
+    fi
+
+    PROJECT_OUTPUT="$OUTPUT_DIR/$PROJECT/$TS"
+    if [[ ! -d "$PROJECT_OUTPUT" ]]; then
+        mkdir -p "$PROJECT_OUTPUT"
+    fi
+ 
+    pushd $PROJECT_PATH
+    mvn clean dependency:go-offline 2>&1
+    mvn compile test-compile package -DskipTests $MAVEN_SKIPS 2>&1 \
+        | tee $PROJECT_OUTPUT/compile.log
+    timeout -s SIGKILL $TIMEOUT mvn verify -fae $MAVEN_SKIP 2>&1 \
+        | tee $PROJECT_OUTPUT/testing.log
+
+    # Get reports from surefire dir
+    for REPORT in `find . | grep --text "target/surefire-reports/TEST" | grep -v "junitreports\|resources\|test-classes"`; do
+        mv $REPORT $PROJECT_OUTPUT
+    done
+    popd
+done

### 2019-09-04 scripts/result_rq8/find_pom.rb

@@ -1,0 +1,45 @@
+#!/usr/bin/env ruby
+require "optparse"
+require "rexml/document"
+include REXML
+
+
+options = {}
+OptionParser.new do |parser|
+  parser.on("--path PATH", "The path to directory") do |v|
+    options[:path] = v
+  end
+  parser.on("--file FILE", "The file path to directory") do |v|
+    options[:file] = v
+  end
+end.parse!
+
+target_path = options[:path]
+file_path = options[:file]
+
+if !target_path.nil? and Dir.exists? target_path
+  poms = `find #{target_path} -name "#{file_path}.java" -type f`
+  line_file = ""
+  poms.each_line do |pom|
+  	split_file = pom.strip.split("/")
+    position_file = split_file.index("src") - 1	
+    result_url = split_file[0..position_file].join("/")
+    line_file = "#{result_url}/pom.xml"
+  end
+
+  poms_cmd = `find #{target_path} -name "pom.*xml" -type f`
+  flag_line = false
+  poms_cmd.each_line do |pom|
+  	if pom.strip == line_file
+  	  flag_line = true
+  	end
+  end
+
+  if flag_line
+  	puts line_file
+  else
+  	puts ""
+  end
+
+  
+end

### 2019-09-04 scripts/result_rq8/parse-rawdata-reexecutation.py

@@ -1,0 +1,124 @@
+#!/usr/bin/env python3
+import csv
+import os
+import re 
+import xml.etree.ElementTree as etree
+
+from collections import Counter
+from subprocess import check_output, CalledProcessError
+from sys import argv
+
+
+def extract_last_field(log_path, field, default="?"):
+    try:
+        cmd = "cat %s | grep --text \"%s\""
+        out = check_output(cmd % (log_path, field), shell=True)
+        out = out.decode().strip().split("\n")[-1]
+        value = re.sub(".*%s" % field.strip(), "", out).strip()
+    except CalledProcessError as e:
+        print("Warning: unable to extract requested field \"%s\"" % field)
+        print("  Possible cause: Unfinished execution")
+        print("  File: \"%s\"" % log_path)
+        print("  Value assigned: \"%s\"" % default)
+        value = default
+    except Exception as e:
+        print(e)
+        print(log_path)
+        value = default
+    return value
+
+
+def parse_xml_reports(xml_files):
+    summary = Counter(tests=0, time=0, failures=0, suites=len(xml_files), classname="")
+    for f in xml_files:
+        if os.path.basename(f) == "TEST-results.xml":
+            continue
+        try:
+            root = etree.parse(f).getroot()
+
+            # The comma replacement is required for high timestamps (eg 1,529.43)
+            time_attr = float(root.get("time").replace(",", ""))
+            tests_attr = int(root.get("tests"))
+            failures_attr = int(root.get("failures"))
+            if root.get("errors"):
+                failures_attr += int(root.get("errors"))
+
+            summary.update(tests=tests_attr, time=time_attr, failures=failures_attr)
+
+        except (ValueError, TypeError) as e:
+            print(e)
+            print(f)
+
+        except:
+            # fail-fast
+            import traceback
+            traceback.print_exc()
+            print("A problem occurred while parsing", f)
+            exit(1)
+
+    return summary
+
+
+def normalize(timestamp):
+    if "min" in timestamp:
+        fields = [int(t) for t in re.sub(" .*", "", timestamp).split(":")]
+        return fields[0]*60 + fields[1]
+    elif "s" in timestamp:
+        return float(re.sub(" .*", "", timestamp))
+    elif "h" in timestamp:
+        fields = [int(t) for t in re.sub(" .*", "", timestamp).split(":")]
+        return (fields[0]*60 + fields[1])*60
+
+    return timestamp
+
[…]

### 2019-09-04 scripts/result_rq8/parse-rawdata.py

@@ -1,0 +1,155 @@
+#!/usr/bin/env python3
+import csv
+import os
+import re 
+import xml.etree.ElementTree as etree
+
+from collections import Counter
+from subprocess import check_output, CalledProcessError
+from sys import argv
+
+
+def extract_last_field(log_path, field, default="?"):
+    try:
+        cmd = "cat %s | grep --text \"%s\""
+        out = check_output(cmd % (log_path, field), shell=True)
+        out = out.decode().strip().split("\n")[-1]
+        value = re.sub(".*%s" % field.strip(), "", out).strip()
+    except CalledProcessError as e:
+        print("Warning: unable to extract requested field \"%s\"" % field)
+        print("  Possible cause: Unfinished execution")
+        print("  File: \"%s\"" % log_path)
+        print("  Value assigned: \"%s\"" % default)
+        value = default
+    except Exception as e:
+        print(e)
+        print(log_path)
+        value = default
+    return value
+
+
+def parse_xml_reports(xml_files):
+    summary = Counter(tests=0, time=0, failures=0, suites=len(xml_files), classname="")
+    for f in xml_files:
+        if os.path.basename(f) == "TEST-results.xml":
+            continue
+        try:
+            root = etree.parse(f).getroot()
+
+            # The comma replacement is required for high timestamps (eg 1,529.43)
+            time_attr = float(root.get("time").replace(",", ""))
+            tests_attr = int(root.get("tests"))
+            failures_attr = int(root.get("failures"))
+            if root.get("errors"):
+                failures_attr += int(root.get("errors"))
+
+            summary.update(tests=tests_attr, time=time_attr, failures=failures_attr)
+
+        except (ValueError, TypeError) as e:
+            print(e)
+            print(f)
+
+        except:
+            # fail-fast
+            import traceback
+            traceback.print_exc()
+            print("A problem occurred while parsing", f)
+            exit(1)
+
+    return summary
+
+def parse_xml_reports_classname_error(xml_files):
+    date_classname = []
+    str_class_name = []
+    for f in xml_files:
+        if os.path.basename(f) == "TEST-results.xml":
+            continue
+        try:
+            root = etree.parse(f).getroot()
+            failures_attr = int(root.get("failures"))
+            if root.get("errors"):
+                failures_attr += int(root.get("errors"))
+
+            if failures_attr > 0:
[…]

### 2019-09-04 scripts/result_rq8/run_plugin.sh

@@ -1,0 +1,124 @@
+#!/bin/bash
+#
+# RQ7 - How effective is selective re-execution in mitigating flakiness?
+#
+# This script generates analisys about test flaykiness and adjust subjects
+# with parallel test.
+# <MODE>: C1 - C2 - C3 - FC0 - FC1
+#
+# Author: Sotero Junior <https://soterojunior.github.io/>
+#
+# Usage:   ./run_plugin.sh <PROJECT_DIR> <MODE> 
+# Example: bash ./run_plugin.sh ./your_subjects FC0 
+#
+#
+MODES=(C1 C2 C3 FC0 FC1)
+PROJECTS_DIR=./projects
+PROJECT=$1
+MODE=$2
+BACKUP_FOLDER=./backup_original
+OUTPUT_DIR=./rawdata
+RERUNS=12
+
+# Check if MODES is correct
+if [[ ! " ${MODES[*]} " == *" $MODE "* ]]; then
+    echo "Insert a Mode or Mode Incorrect"
+    exit 1
+fi
+
+# Check if folder project is valid
+if [[ ! -d "$PROJECTS_DIR" ]]; then
+    echo "Invalid path projects"
+    exit 1
+fi
+
+# Check if folder rawdata is valid
+if [[ ! -d "$OUTPUT_DIR" ]]; then
+    echo "Invalid path rawdata"
+    exit 1
+fi
+
+# Check if exists folder backup original exists
+if [[ ! -d "$BACKUP_FOLDER" ]]; then
+    echo "Invalid path backup folder"
+    exit 1
+fi
+
+# Check if project was copied to folder backup
+CHECK_FOLDER=`find $BACKUP_FOLDER -maxdepth 1 -type d | wc -l`
+if [ $CHECK_FOLDER -eq 2 ]
+then
+    echo "Project has been copied."
+else
+    echo "Copying project..."
+    cp -R $PROJECT $BACKUP_FOLDER
+    echo "Project copied."
+fi
+
+# New project name with mode parallel
+NEW_PROJECT="${PROJECT}_${MODE}"
+
+# Change folder name project to start the transformation
+echo "Changing the project name..."
+mv $PROJECT $NEW_PROJECT
+
+# Transform project in Mode
+./transform.rb --path $NEW_PROJECT
+
+# After that transform move to ./projects folder
+echo "Moving project to folder analisys..."
+mv $NEW_PROJECT $PROJECTS_DIR
+
+# Run the project with params Mode defined
[…]

### 2019-09-04 scripts/result_rq8/transform.rb

@@ -1,0 +1,142 @@
+#!/usr/bin/env ruby
+require "optparse"
+require "rexml/document"
+include REXML
+
+def get_element xml, name
+  child = xml.elements[name]
+  if child.nil?
+    child = Element.new name
+    xml << child
+  end
+  child
+end
+
+def set_value xml, name, value
+  element = get_element xml, name
+  element.text = value
+end
+
+def poolSettings configuration
+  set_value configuration, 'forkCount', '1'
+  set_value configuration, 'useUnlimitedThreads', 'false'
+  set_value configuration, 'perCoreThreadCount', 'true'
+  set_value configuration, 'threadCount', '1'
+end
+
+def c0 configuration
+  set_value configuration, 'forkCount', '1'
+  set_value configuration, 'useUnlimitedThreads', 'false'
+  set_value configuration, 'perCoreThreadCount', 'false'
+  set_value configuration, 'threadCount', '0'
+  set_value configuration, 'parallel', 'none'
+end
+
+def c1 configuration
+  poolSettings configuration
+  set_value configuration, 'parallel', 'methods'
+end
+
+def c2 configuration
+  poolSettings configuration
+  set_value configuration, 'parallel', 'classes'
+end
+
+def c3 configuration
+  poolSettings configuration
+  set_value configuration, 'parallel', 'both'
+end
+
+def fc0 configuration
+  set_value configuration, 'forkCount', '1C'
+  set_value configuration, 'useUnlimitedThreads', 'false'
+  set_value configuration, 'perCoreThreadCount', 'false'
+  set_value configuration, 'threadCount', '0'
+  set_value configuration, 'parallel', 'none'
+end
+
+def fc1 configuration
+  c1 configuration
+  set_value configuration, 'forkCount', '1C'
+end
+
+def check pom
+  xml = Document.new IO.read(pom.strip)
+  puts "Loading pom: #{pom.strip}"
+  plugins = XPath.match xml, "//plugin/artifactId[. = 'maven-surefire-plugin']/"
+  if not plugins.nil? and plugins.to_a.size > 0
+    plugins.each do |node|
+      puts get_element node.parent, "version"
+    end
+  end
+end
+
+# Copied from luis' code
+def transform pom
+  xml = Document.new IO.read(pom.strip)
+  puts "Loading pom: #{pom.strip}"
+  plugins = XPath.match xml, "//plugin/artifactId[. = 'maven-surefire-plugin']"
[…]

### 2019-09-04 scripts/result_rq8/transform_seq.rb

@@ -1,0 +1,79 @@
+#!/usr/bin/env ruby
+require 'optparse'
+require 'ostruct'
+require 'rexml/document'
+include REXML
+
+
+def get_element xml, name
+  child = xml.elements[name]
+  if child.nil?
+    child = Element.new name
+    xml << child
+  end
+  child
+end
+
+
+def set_value xml, name, value
+  element = get_element xml, name
+  element.text = value
+end
+
+
+options = {}
+OptionParser.new do |parser|
+  parser.on("--path PATH", "The path to directory") do |v|
+    options[:path] = v
+  end
+end.parse!
+
+target_path = options[:path]
+
+begin
+  xml = Document.new IO.read(target_path)
+  puts "Loading pom: #{target_path}"
+  plugins = XPath.match xml, "//plugin/artifactId[. = 'maven-surefire-plugin']"
+  if not plugins.nil? and plugins.to_a.size > 0
+    plugins.each do |plugin|
+      puts "Changing plugin in pom: #{target_path}"
+      surefire = plugin.parent
+      configuration = get_element surefire, 'configuration'
+      set_value configuration, 'parallel', 'none'
+      set_value configuration, 'forkCount', '1'
+      set_value configuration, 'reuseForks', 'true'
+      set_value configuration, 'useUnlimitedThreads', 'false'
+      set_value configuration, 'threadCount', '1'
+      set_value configuration, 'perCoreThreadCount', 'false'
+    end
+  else
+    project = get_element xml, 'project'
+    build = get_element project, 'build'
+    plugins = get_element build, 'plugins'
+    plugin = Element.new 'plugin'
+    set_value plugin, 'groupId', 'org.apache.maven.plugins'
+    set_value plugin, 'artifactId', 'maven-surefire-plugin'
+    configuration = get_element plugin, 'configuration'
+    set_value configuration, 'parallel', 'none'
+    set_value configuration, 'forkCount', '1'
+    set_value configuration, 'reuseForks', 'true'
+    set_value configuration, 'useUnlimitedThreads', 'false'
+    set_value configuration, 'threadCount', '1'
+    set_value configuration, 'perCoreThreadCount', 'false'
+    set_value configuration, 'fork', 'false'
+    set_value configuration, 'forkMode', 'once'
+    plugins << plugin
+  end
+
+  puts "Removing pom: #{target_path}"
+  File.delete target_path
+  file = ''
[…]

### 2019-09-10 tse19/mitigating-flakiness-speedup-table.tex
fix table

@@
 
-Activiti & \entry{8.46m}{2093}  & \textcolor{blue}{ 2.49x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.81x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.72x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.02x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 2.87x } & \textcolor{blue}{ 0\%}\\%
+Activiti & \entry{8.46m}{2093}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%
 
-Apache Avro & \entry{13.65m}{3765}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%
+Apache Avro & \entry{13.65m}{3765}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%
 
-Apache Incubator Dubbo & \entry{14.33m}{2663}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%
+Apache Incubator Dubbo & \entry{14.33m}{2663}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%
 
-Content ExtRactor and MINEr & \entry{8.10m}{132}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%
+Content ExtRactor and MINEr & \entry{8.10m}{132}  & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%
 
-DataStax Java Driver & \entry{5.23m}{1377}  & \entry{8.30x}{1.17\%} & \entry{9.34x}{0.75\%} & \entry{9.33x}{1.15\%} & \entry{1.03x}{0\%} & \entry{6.22x}{1.41\%}\\%
+DataStax Java Driver & \entry{5.23m}{1377}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{-----}{-----} & \entry{0x}{0\%}\\%
 
-DROID & \entry{6.00m}{386}  & \entry{2.32x}{15.79\%} & \entry{7.90x}{2.02\%} & \entry{4.02x}{5.33\%} & \entry{9.67x}{2.3\%} & \entry{4.76x}{6\%}\\%
+DROID & \entry{6.00m}{386}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%
 
-Eclipse Hawkbit & \entry{17.28m}{1111}  & \entry{2.63x}{29.12\%} & \entry{2.90x}{33.22\%} & \entry{2.52x}{26.52\%} & \entry{2.49x}{9.23\%} & \entry{3.00x}{33.91\%}\\%
+Eclipse Hawkbit & \entry{17.28m}{1111}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%
 
-Facebook Linkbench & 7.16m & 98 & 1.02x & 0\% & 1.70x & 1.27\% & 1.00x & 1.00\% & 1.70x & 0.09\% & 1.69x & 0.93\%\\%
+Facebook Linkbench & 7.16m & 98 & ----- & ----- & 0x & 0\% & 0x & 0\% & 0x & 0\% & 0x & 0\%\\%
 
-Kafka Streams & \entry{11.38m}{79}  & \entry{1.13x}{11\%} & \entry{1.02x}{0\%} & \entry{1.12x}{11.49\%} & \entry{2.63x}{1.37\%} & \entry{1.02x}{0.2\%}\\%
+Kafka Streams & \entry{11.38m}{79}  & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%
 
-Rapidoid & \entry{11.68m}{476}  & \entry{1.06x}{0\%} & \entry{1.24x}{0\%} & \entry{1.10x}{0\%} & \entry{18.54x}{10.15\%} & \entry{17.17x}{9.57\%}\\%
+Rapidoid & \entry{11.68m}{476}  & \entry{-----}{-----} & \entry{-----}{-----} & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%
 
-Search Guard & \entry{13.32m}{111}  & \entry{1.78x}{0\%} & \textcolor{blue}{ 1.62x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.43x } & \textcolor{blue}{ 0\%} & \entry{2.04x}{0\%} & \entry{2.45x}{0\%}\\%
+Search Guard & \entry{13.32m}{111}  & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{-----}{-----}\\%
 
-T SNE Java & \entry{6.38m}{20}  & \textcolor{blue}{ 2.02x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 1.22x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 1.21x } & \textcolor{blue}{ 0\%}\\%
+T SNE Java & \entry{6.38m}{20}  & \entry{1.26x}{0\%} & \entry{-----}{-----} & \entry{1.24x}{0\%} & \entry{-----}{-----} & \entry{1.23x}{0\%} \\%
 
-Twilio Java & \entry{12.60m}{2529}  & \entry{1.47x}{1.37\%} & \entry{2.15x}{21\%} & \entry{3.08x}{2.18\%} & \entry{3.47x}{0\%} & \entry{2.60x}{5.54\%}\\%
+Twilio Java & \entry{12.60m}{2529}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%
 
-Urban Airship Datacube & 11.84m & 45 & 2.31x & 20.91\% & 3.35x & 34.06\% & 1.92x & 21.46\% & 1.21x & 0\% & 2.26x & 21\%\\%
+Urban Airship Datacube & 11.84m & 45 & 0x & 0\% & 0x & 0\% & 0x & 0\% & ----- & ----- & 0x & 0\%\\%
 
-Vaadin Framework & \entry{8.97}{3683}  & \textcolor{blue}{ 2.19x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.91x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 2.01x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 2.53x } & \textcolor{blue}{ 0\%}\\%
+Vaadin Framework & \entry{8.97}{3683}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%
 
 \midrule
-Average & 10.42m & 1,237.86 & -x & -\% &  -x & -\%  & -x  & -\% & -x & -\% & -x & -\%\\%
+Average & 10.42m & 1,237.86 & ----- & ----- &  ----- & -----  & -----  & ----- & ----- & ----- & ----- & ----- \\%
 
